### 2015-10-19 ch01-intro/introduction.tex
Basic file structure

\chapter{Introduction}

  \section{System idenfication}
   \section{Contributions}

### 2015-10-19 ch05-initvals/initial-values.tex
Basic file structure

\chapter{Initialization of parametric estimators}

### 2015-10-19 ch06-concl/conclusions.tex
Extended publications

\chapter{Conclusions}

\section{Future research}
  \subsection{Excitation design}
  \TODO{MIMO}

### 2015-10-20 ch02-qlogms/excitation-design.tex
More structure

\chapter{Design of excitation signals}
\researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}

\section{\TODO{Robust vs optimal}}
\section{\TODO{Robust QLog MS}}
\subsection{\TODO{Constraints: time and power}}
\subsection{\TODO{Informativity of experiment}}
\subsection{\TODO{Normalized design w.r.t. damping}}
\subsection{\TODO{Grid misalignment effects}}
\subsection{\TODO{qLog design rules}}

### 2015-10-20 front-and-back-matter/frontmatter.tex
More structure

\maketitle

\tableofcontents
%TODO: make sure all these appear in TOC
%TODO: \listoffigures
%TODO: \listoftables
%TODO: list of symbols
%TODO: list of acronyms
\newpage

### 2015-10-25 ch02-qlogms/gridDefs.inc.tex
Import QLogMS TIM paper

\definecolor{model}{named}{blue}
\definecolor{truesys}{named}{TangoAluminium5}

\definecolor{linms}{named}{TangoScarletRed3}
\definecolor{logms}{named}{TangoChameleon2}
\definecolor{qlogms}{named}{TangoPlum3}
\definecolor{clogms}{named}{TangoSkyBlue3}
\definecolor{plogms}{named}{black}

\definecolor{sigmalinms}{named}{linms}
\definecolor{sigmaqlogms}{named}{qlogms}
\definecolor{sigmaclogms}{named}{clogms}

\definecolor{biaslinms}{named}{TangoScarletRed1}
\definecolor{biasqlogms}{named}{TangoPlum1}
\definecolor{biasclogms}{named}{TangoSkyBlue1}

\definecolor{dbacolor}{named}{TangoScarletRed2}
\definecolor{dbbcolor}{named}{TangoSkyBlue2}
\definecolor{dbccolor}{named}{TangoChameleon2}
\definecolor{dbdcolor}{named}{TangoOrange2}

\pgfplotsset{linmsgrid/.style={ycomb,color=linms,solid,line width=0.7pt,mark size=1pt,mark=square*,mark options={solid}}}
\pgfplotsset{logmsgrid/.style={ycomb,color=logms,solid,line width=0.7pt,mark size=1pt,mark=*,mark options={solid}}}
\pgfplotsset{clogmsgrid/.style={ycomb,color=clogms,solid,line width=0.7pt,mark size=2pt,mark=x,mark options={solid}}}
\pgfplotsset{plogmsgrid/.style={ycomb,color=plogms,solid,line width=0.7pt,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}

\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
\pgfplotsset{truesys/.style={color=truesys,line width=1.0pt}}

\newcommand{\linmsmarker}{mark=square,mark options={solid}}
\newcommand{\qlogmsmarker}{mark=triangle,mark options={solid}}
\newcommand{\clogmsmarker}{mark=x,mark size=10pt,mark options={solid}}

\newcommand{\dbamarker}{mark=x       ,mark options={solid}}
\newcommand{\dbbmarker}{mark=o       ,mark options={solid}}
\newcommand{\dbcmarker}{mark=square  ,mark options={solid}}
\newcommand{\dbdmarker}{mark=triangle,mark options={solid}}

\pgfplotsset{sigmalinms/.append style={color=sigmalinms,solid,line width=0.8pt}}
\pgfplotsset{sigmaqlogms/.append style={color=sigmaqlogms,solid,line width=0.8pt}}
\pgfplotsset{sigmaclogms/.append style={color=sigmaclogms,solid,line width=0.8pt}}

\pgfplotsset{biaslinms/.style={color=biaslinms,only marks,mark=x,mark options={solid}}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,only marks,mark=triangle,mark options={solid,rotate=180}}}
\pgfplotsset{biasclogms/.style={color=biasclogms,only marks,mark=o,mark options={solid}}}

\pgfplotsset{linms/.style={color=linms,solid,line width=0.5pt}}
\pgfplotsset{qlogms/.style={color=qlogms,solid,line width=0.5pt}}
\pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}

\pgfplotsset{linmsconnect/.style={color=linms,%
                                  solid,
                                  line width=1pt,
                                  mark=square*,
                                  mark size=1pt,
                                  mark options={solid}}}
\pgfplotsset{qlogmsconnect/.style={color=qlogms,%
                                  solid,
                                  line width=1pt,%
                                  mark=*,%
                                  mark size=1pt,
                                  mark options={solid}}}
\pgfplotsset{clogmsconnect/.style={color=clogms,%
                                   solid,
                                   line width=1pt,%
                                   mark=x,%
                                   mark size=1pt,
                                   mark options={solid}}}

\pgfplotsset{dbavar/.style={color=dbacolor,solid,line width=1.0pt}}
\pgfplotsset{dbbvar/.style={color=dbbcolor,solid,line width=1.0pt}}
\pgfplotsset{dbcvar/.style={color=dbccolor,solid,line width=1.0pt}}
\pgfplotsset{dbdvar/.style={color=dbdcolor,solid,line width=1.0pt}}

\pgfplotsset{dbamin/.style={color=dbacolor,dashed,line width=1.0pt}}
\pgfplotsset{dbbmin/.style={color=dbbcolor,dashed,line width=1.0pt}}
\pgfplotsset{dbcmin/.style={color=dbccolor,dashed,line width=1.0pt}}
\pgfplotsset{dbdmin/.style={color=dbdcolor,dashed,line width=1.0pt}}

\pgfplotsset{dbamax/.style={color=dbacolor,solid,line width=1.0pt,mark=x ,mark options={solid}}}
\pgfplotsset{dbbmax/.style={color=dbbcolor,solid,line width=1.0pt,mark=o ,mark options={solid}}}
\pgfplotsset{dbcmax/.style={color=dbccolor,solid,line width=1.0pt,mark=square  ,mark options={solid}}}
\pgfplotsset{dbdmax/.style={color=dbdcolor,solid,line width=1.0pt,mark=triangle,mark options={solid}}}

### 2015-10-25 ch02-qlogms/grids.inc.tex
Import QLogMS TIM paper

%% Colors
  \definecolor{tangored}{named}{TangoScarletRed1}
  \definecolor{tangoblue}{rgb}{0.203922,0.396078,0.643137}
  \definecolor{tangogreen}{named}{TangoChameleon2}
  \definecolor{tangogrey}{named}{TangoAluminium5}

  \definecolor{meas}{named}{TangoPlum2}

  \definecolor{goallight}{named}{TangoChameleon1}
  \definecolor{goal}{named}{TangoChameleon2}
  \definecolor{goaldark}{named}{TangoChameleon3}

  \definecolor{obtainedlight}{named}{TangoScarletRed1}
  \definecolor{obtained}{named}{TangoScarletRed2}
  \definecolor{obtaineddark}{named}{TangoScarletRed3}

  \definecolor{model}{named}{tangogrey}
  \definecolor{bg}{named}{TangoAluminium2}

\definecolor{linms}{named}{TangoScarletRed3}
\definecolor{logms}{named}{TangoChameleon2}
\definecolor{qlogms}{named}{TangoPlum3}
\definecolor{clogms}{named}{TangoSkyBlue3}
\definecolor{plogms}{named}{black}

  \definecolor{compen}{rgb}{0.729,0.741,0.714}
  \definecolor{signal}{named}{TangoSkyBlue2}
  \definecolor{misalign}{named}{TangoScarletRed2}

  \definecolor{dbacolor}{named}{TangoScarletRed2}
  \definecolor{dbbcolor}{named}{TangoSkyBlue2}
  \definecolor{dbccolor}{named}{TangoChameleon2}
  \definecolor{dbdcolor}{named}{TangoOrange2}

%% TikZ styles
  \tikzset{obtainedarrow/.style={color=obtaineddark,line width=1.0pt,->}}
  \tikzset{goalarrow/.style={color=goaldark,line width=1.0pt,->}}
  \tikzset{arrow/.style={color=TangoAluminium5,line width=1pt,->,>={triangle 45}}}

%% marker styles
  \definecolor{bwfill}{named}{TangoAluminium1}
  \definecolor{bwline}{named}{TangoAluminium5}

  \definecolor{safezone}{named}{bwfill}

%% pgfplots styles
\pgfplotsset{goal/.style={color=goallight,dashed,line width=0.75pt}}
\pgfplotsset{obtained/.style={color=obtainedlight,line width=0.75pt}}

\pgfplotsset{signalrectangle/.style={fill=signal!60!black,fill opacity=0.8,color=signal!30}}
\pgfplotsset{signalrectanglerobust/.style={fill=signal!50,fill opacity=0.5,color=signal!30}}

\pgfplotsset{safezone/.style={fill=safezone,fill opacity=0.5,color=safezone}}

\tikzset{showdistance/.style={|-|,line width=1pt}}

\pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
\pgfplotsset{bw/.style={fill=bwfill,draw=bwline}}
\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}

\pgfplotsset{dbvariance/.style={solid,line width=1.0pt}}
\pgfplotsset{dbvariancemin/.style={dashed,line width=1.0pt}}
\pgfplotsset{dbvariancemax/.style={dbvariance}}

\pgfplotsset{dbavar/.style={color=dbacolor,dbvariance}}
\pgfplotsset{dbbvar/.style={color=dbbcolor,dbvariance}}
\pgfplotsset{dbcvar/.style={color=dbccolor,dbvariance}}
\pgfplotsset{dbdvar/.style={color=dbdcolor,dbvariance}}

\pgfplotsset{dbamin/.style={color=dbacolor,dbvariancemin}}
\pgfplotsset{dbbmin/.style={color=dbbcolor,dbvariancemin}}
\pgfplotsset{dbcmin/.style={color=dbccolor,dbvariancemin}}
\pgfplotsset{dbdmin/.style={color=dbdcolor,dbvariancemin}}

\pgfplotsset{dbamax/.style={color=dbacolor,dbvariancemax,mark=diamond*}}
\pgfplotsset{dbbmax/.style={color=dbbcolor,dbvariancemax,mark=*}}
\pgfplotsset{dbcmax/.style={color=dbccolor,dbvariancemax,mark=square*}}
\pgfplotsset{dbdmax/.style={color=dbdcolor,dbvariancemax,mark=triangle*}}

\pgfplotsset{linmsmarker/.style={mark=*,mark options={solid},mark size=1pt}}
\pgfplotsset{logmsmarker/.style={mark=pentagon*,mark options={solid},mark size=1pt}}
\pgfplotsset{clogmsmarker/.style={mark=triangle*,mark options={solid},mark size=1pt}}
\pgfplotsset{qlogmsmarker/.style={mark=square*,mark options={solid},mark size=1pt}}
\pgfplotsset{plogmsmarker/.style={mark=diamond*,mark options={solid},mark size=1pt}}

\pgfplotsset{model/.style={color=model,line width=1.0pt}}

\pgfplotsset{gridline/.style={ycomb,solid,line width=0.7pt,mark size=1pt}}
\pgfplotsset{biggrid/.style={ycomb,solid,line width=1pt,mark size=1pt}}

\pgfplotsset{linmsgrid/.style={color=linms,gridline,mark=square*,mark options={solid}}}
\pgfplotsset{logmsgrid/.style={color=logms,gridline,mark=*,mark options={solid}}}
\pgfplotsset{clogmsgrid/.style={color=clogms,gridline,mark size=2pt,mark=x,mark options={solid}}}
\pgfplotsset{plogmsgrid/.style={color=plogms,gridline,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}

\pgfplotsset{linms/.style={color=linms}}
\pgfplotsset{clogms/.style={color=clogms}}
\pgfplotsset{rlogms/.style={color=rlogms}}
\pgfplotsset{qlogms/.style={color=qlogms}}
\pgfplotsset{plogms/.style={color=plogms}}

\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
\pgfplotsset{truesys/.style={color=tangogrey,line width=0.9pt}}

\pgfplotsset{meas/.style={color=meas,only marks,mark=*,mark options={solid},mark size=1pt}}

\pgfplotsset{results/.style={solid,line width=0.7pt}}
\pgfplotsset{linmsres/.style={color=linms,results}}
\pgfplotsset{qlogmsres/.style={color=qlogms,results}}
\pgfplotsset{clogmsres/.style={color=clogms,results}}
\pgfplotsset{plogmsres/.style={color=plogms,results}}

\pgfplotsset{linmsmeas/.style={color=linms,densely dashed,line width=0.7pt}}
\pgfplotsset{qlogmsmeas/.style={color=qlogms,densely dotted,line width=0.7pt}}
\pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}
\pgfplotsset{plogmsmeas/.style={color=plogms,solid,line width=0.7pt}}

\pgfplotsset{connectline/.style={solid,line width=1.0pt}}
\pgfplotsset{linmsconnect/.style={color=linms,connectline,linmsmarker}}
\pgfplotsset{qlogmsconnect/.style={color=qlogms,connectline,qlogmsmarker}}
\pgfplotsset{clogmsconnect/.style={color=clogms,connectline,clogmsmarker}}
\pgfplotsset{plogmsconnect/.style={color=plogms,connectline,plogmsmarker}}

\pgfplotsset{sigmalinms/.style={linms,connectline}}
\pgfplotsset{sigmaqlogms/.style={qlogms,connectline}}
\pgfplotsset{sigmaclogms/.style={clogms,connectline}}
\pgfplotsset{sigmaplogms/.style={plogms,connectline}}

\pgfplotsset{linrect/.style={fill=linms,draw=linms,line width=1pt}}

### 2015-10-25 ch02-qlogms/logMS_IMTC.tex
Import QLogMS TIM paper

\def\thisDir{ch02-qlogms}
% \begin{abstract}
% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
% Periodic signals are very popular in many advanced dynamic signal analyzers.
% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
% \end{abstract}

\section{Introduction} \label{sec:intro}
  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades \cite{bragos2001characterisation,sanchez2011optimal,niedostatkiewicz2009,VanGheem2004}.
  Of course, we also want to attain a specified uncertainty level over the full frequency span.

  Any LTI system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\cite{Oppenheim1983}.
  Therefore the performance of the proposed method is assessed on a prototype system of second order.
  This does not limit the generality of the approach as we can add several of such systems to construct a general LTI system.

  To ensure that any second order system with its resonance frequency in the specified frequency range is measured with an equal accuracy, the system output should contain a comparable power level irrespective of its resonance frequency.
  For a system with a sufficiently low damping, one can intuitively understand that most of the information is contained within the $3 \unit{dB}$ bandwidth of the system.
  Remember that an LTI system is naturally described in a logarithmic frequency axis (the slopes of such a system are specified in $\unit{dB}/\text{decade}$).
  Hence, an excitation with a flat power spectrum and a linearly spaced frequency grid will over-excite the high end of the band at the cost of the low frequencies.
  To restore equal excitation signal levels over the complete range of frequencies, we will need to distribute the power in $1/\omega$ over the frequency band.
  In a noise excitation context, this results in pink noise.
  In a periodic setting, this results in a multisine whose frequency components are spaced equidistantly on a logarithmic axis.

  The main problem is that network and dynamic signal analyzers typically
  rely on an equidistant frequency grid that comes with the Discrete Fourier Transform (DFT).
  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
  This problem was already discussed in \cite{GeerardynIMTC2012}.

  We will also present a simple method to determine a suitable density of a logarithmically spaced signal for a predefined minimal damping of the system to be tested.

  In the first section of this paper, we start from a generic transfer function model and discuss a decomposition thereof in second order subsystems and their properties.
  We provide a comparison between several possible implementations of the frequency grids.
  We discuss their applicability to multisine signals.
  We also introduce a compensation method for the problems of the quasi-logarithmic grid and propose a novel $1/f$ `pink' quasi-logarithmic multisine.
  The second section describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant quality (signal to noise ratio (SNR)) is obtained.

  In the third section, the presented techniques are illustrated on a simulation example.
  Finally, we verify our results experimentally on the measurements of a band-pass filter.

\section{Methodology} \label{sec:method}

  \subsection{The system under consideration}
  We consider the transfer function models of generic linear time-invariant systems of arbitrary but finite orders $n_a\times n_b$:
  \begin{align}
    G\left( \Omega, \theta \right) = \frac{B\left( \Omega,\theta \right)}
                                          {A\left( \Omega,\theta \right)}
                                   = \frac{\sum\limits_{i=0}^{n_b-1} b_i \Omega^i}
                                          {\sum\limits_{i=0}^{n_a-1} a_i \Omega^i}
    \text{.} \label{eq:model}
  \end{align}

  The model is parametrized in the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
  For a continuous time model $\Omega = s$, while for the discrete time case $\Omega = z$.

  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
  To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
  In continuous time such a system can be described by a transfer function of the form
  \begin{equation}
    G\left(s \right) = \frac{\dc}
                            {             \frac{s^2}
                                               {\wn^2} 
                             + 2 \damping \frac{s}
                                               {\wn}
                             + 1
                            }
  \text{.}
  \label{eq:secondOrderSystemCT}
  \end{equation}
  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
  The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
  The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.

  When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in
  the amplitude of the transfer function \cite{Oppenheim1983}:
  \begin{align}
   \left| G\left(\wM \right) \right| & \isdef
          \max_{\omega} \left| G\left( \omega \right)  \right|
        = \frac{\dc}
               {2 \damping \sqrt{1-\damping^2}}
               \label{eq:peakAmplitude}\\
   \wM &
        = \sqrt{1-2\damping^2} \wn
        \label{eq:peakFrequency}
    \text{.}
  \end{align}

\subsection{System and noise model}
  In this paper, an output error (OE) system setup is used.
  Denote
    $U  \left(\omega\right)$ as the excitation signal,
    $Y_0\left(\omega\right)$ the exact, unperturbed system output,
    $E  \left(\omega\right)$ for the output noise source,
    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal.

  The output noise is assumed to be zero-mean and white with a
  standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.

\subsection{Multisine Excitations}
  To excite the system under test we will use multisine excitations \cite{Pintelon2001} with $F$ commensurate frequency components:
  \begin{equation}
    u \left( t\right) = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(2\pi f_k t + \phi_k \right)
  \text{.}
  \label{eq:MultisineCT}
  \end{equation}
  In this expression, $f_k$ represents the $k^{\text{th}}$ excited frequency component.
  $A_k$ is the amplitude and $\phi_k$ the phase of the $k^{\text{th}}$ spectral line.
  We limit ourselves, without loss of generality, to random phase multisines.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
    the amplitude of the spectral lines $A_k$ and
    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.

\subsection{Equidistant (Linear) Grid Multisine}
  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \cite{OppenheimDT,Mandal2007}. It allows to analyze periodic signals on an equidistant frequency grid very efficiently.

  An equidistant frequency grid $\set{f_1, \ldots, f_F}$ with spacing $\Delta f$
  consisting of $F$ lines conforms to the following relation:
  \begin{equation}
    f_k = k \Delta f + k_0 \Delta f
    \emspace \forall k \in \set{1,\ldots,F},
    \emspace k_0 \in \NN
    \text{.}
  \label{eq:linGrid}
  \end{equation}

  Using such linear grid, we can easily construct a representation of a multisine
  in discrete time that is suited for use with the DFT by sampling at a given sampling rate $f_s$:
  \begin{equation}
     u \left[ n\right] = \frac{1}{\sqrt{F}}
     \sum_{k=1}^{F} 
       A_k 
       \sin 
         \left(\frac{2\pi n \left( k + k_0 \right) \Delta f}{f_s} + \phi_k \right)
    \label{eq:MultiSineDT}
  \end{equation}

  Such an equidistant grid is a very common choice.
  Note that it has more frequency lines per decade (or octave) at higher frequencies.
  Therefore, the excitation power per octave is larger at higher frequencies
  when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
  For a constant amplitude spectrum, this means the dynamics that are present at lower frequencies are plagued by a higher uncertainty than the ones located at higher frequencies.

  Therefore a signal with an equidistant frequency grid is undesirable for
  our situation as it wastes signal power at high frequencies at the cost of an increased variance in the lower side of the band.

\subsection{(Ideal) Logarithmic Grid Multisine}
  For a logarithmic frequency grid $\set{f_1, \ldots, f_F}$ of $F$ lines,
  the following relation holds between excited frequencies:
  \begin{equation}
    f_k = \alpha \cdot f_{k-1}
    \emspace \forall k \in \set{1,\ldots,F}
  \label{eq:logGrid}
  \end{equation}
  for a given lowest frequency $f_0$ and frequency ratio $\alpha > 1$.

  When designing an excitation signal, it is common only to specify a (large) frequency band
  by its boundary frequencies $f_{\min}$ and $f_{\max}$.
  For a given $\alpha$ it is easy to determine the number of excited lines
  within the frequency range of interest:
    \begin{equation}
      F = \floor{
                  \frac{\log{f_{\max}} - \log{f_{\min}}}
                       {\log{\alpha}}
                }
    \end{equation}
  where $\floor{\bullet}$ denotes rounding towards zero.
  In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.

  Each decade within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains the same number of frequency components such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.

  To return to the FRF, in Section \ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
  As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
  bandwidth, one expects an equal variance for each system, as will be shown in Section \ref{sec:bestFrequencyResolution}.

  For that reason, a log multisine is a good candidate for our purposes.
  However, it is more involved both to generate and to analyze such a signal,
  as the excited frequencies no longer lie on a commensurate grid.
  It is therefore not practical to use a perfectly logarithmically spaced frequency grid as the DFT is no longer usable as a tool.

\subsection{Quasi-Logarithmic Grid Multisine}
  Since most measurement equipment and analysis methods rely on signals with an equidistant frequency grid, we will create a frequency grid
  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:logGrid} is approximately 
  valid but with the strict constraint that the frequencies must be a subset 
  of an equidistant frequency grid. This yields the following relation for 
  subsequent frequency lines:
  \begin{equation}
    f_k \approx \alpha \cdot f_{k-1}
    \emspace \forall k \in \set{1,\ldots,F}
  \label{eq:qlogGrid}
  \end{equation}
  under the constraint that
  \begin{equation}
    f_k = N \cdot \Delta f,\; N \in \NN
    \text{.}
    \label{eq:constraintLinGrid}
  \end{equation}
  Such a grid is called a quasi-logarithmic (quasi-log) grid \cite{Pintelon2001}.

  At the low edge of the frequency band, the desired frequency ratio between two
  frequencies is not attained when the frequency spacing $\Delta f$ is large
  compared to $\left(\alpha -1 \right) f_{k-1}$.
  This causes the power spectrum to be less dense at these low frequencies than that of an ideal logarithmic frequency grid.

  As this signal approximates a logarithmically spaced signal,
  we expect that it will exhibit comparable properties.
  On the other hand, by imposing \eqref{eq:constraintLinGrid}, it remains
  possible to use signal techniques which rely on a commensurate frequency grid.

\subsection{Compensated Quasi-Logarithmic Grid Multisine}
  The power density of the quasi-log multisine at the low frequencies is reduced in comparison to that of the logarithmic grid multisine.
  This is due to the limited available frequency resolution.
  To compensate for this loss in power spectral density (PSD), we can increase the amplitude spectrum $A_k$ at these lines.
  Note that we are not able to restore the frequency resolution, only the power in a certain band is made equal to the power in the logarithmic multisine in the same band.

  First of all, we need to determine the factor $A_k$ needed to correct the power spectrum to match that of a log grid multisine.
  To this end, one first constructs a log frequency grid $\LOGGRID = \set{\f_1, \ldots, \f_{F'}}$ for a given factor $\alpha$ and the corresponding quasi-log grid $\QLOGGRID = \set{f_1, \ldots, f_F}$ for a resolution $\Delta f$.
  For each frequency $f_k$ in the quasi-log grid, we define $n\left(f_k\right)$
  as the number of frequencies in the log grid that are nearer to $f_k$
  than to any other grid line in the quasi-log grid:

  \begin{equation}
    n\left(f_k\right) = \numberOf \mathrm{nearestLines}_{f_k}
    \label{eq:nfk}
  \end{equation}
  \begin{equation}
    \mathrm{nearestLines}_{f_k} =
      \left\{ 
        \f_l \given{\begin{aligned} 
                       \f_l \in \LOGGRID, \\
                       \norm{\f_l - f_k} < \norm{\f_l - f_{k'}},\\
                       \forall k' \neq k: f_k, f_{k'} \in \QLOGGRID
                    \end{aligned}}
      \right\}
    \label{eq:nearestLines}
  \end{equation}

  When approximating a log multisine with constant amplitude spectrum $A_{\mathrm{in}}$, we choose the amplitude spectrum of the compensated quasi-log multisine as follows
  \begin{equation}
    A_k = A_{\mathrm{in}} \cdot \sqrt{n\left(f_k\right)}\emspace \forall k \in \set{1,\ldots,F}
  \text{.}
  \label{eq:compensationAk}
  \end{equation}
  This effectively concentrates the total power of the $n\left( f_k \right)$ surrounding lines in the log grid multisine at the frequency $f_k$ in the compensated quasi-log multisine.

  The power spectrum of this compensated signal approximates the one of the log grid multisine better than an uncompensated quasi-log grid.
  As the power spectrum approximates the power spectrum of the log grid multisine, the uncertainty of the frequency response function will be approximately independent of the frequency within the measured frequency band.

  \subsection{Pink Quasi-Logarithmic Multisine}
  In \cite{Rojas2007} it is suggested that band-limited $1/f$ noise is a reasonable, albeit not optimal, robust excitation signal.

  For $1/f$ noise (`pink noise'), the power spectral density $S(f)$ is proportional to $1/f$.
  We can again approximate such a signal by means of a quasi-logarithmic grid multisine.
  To do so, we excite a quasi-logarithmic frequency grid $\set{f_1,\ldots,f_k,\ldots,f_F}$ and determine the corresponding amplitude spectrum $A_k$ such that each excited line carries the same power as the corresponding frequency band does for pink noise.

  This allows to define the amplitude spectrum $A_k$ as
  \begin{equation}
    A_k = A_{\mathrm{in}}
                 \sqrt{\int_{\fMin{k}}
                     ^{\fMax{k}}
                     \limits
                     \frac{1}
                          {f}
                     \,\dd{f}}
          = A_{\mathrm{in}}
                \cdot
                \sqrt{
                \ln \frac{\;\fMax{k}\;}{\fMin{k}}
                }
  \end{equation}
  where $\left[ \fMin{k}, \fMax{k} \right] $ denote the frequency range over which PSD of the pink noise is to be approximated by the power at frequency line $f_k$.

  To reduce the complexity of the expressions for $\fMin{k}$ and $\fMax{k}$, we extend the frequency grid by one component to the left and to the right by means of the grid relation (equations \eqref{eq:qlogGrid} and \eqref{eq:constraintLinGrid}) to obtain the grid $\set{f_0, f_1, \ldots, f_F, f_{F+1}}$.

  Using this extension, the frequency range covered by $f_k$ can then be calculated as
    \begin{align}
      \fMin{k} = \mean{f_{k-1}}{f_k}
      \quad \text{ and } \quad 
      \fMax{k} = \mean{f_{k+1}}{f_k}
    \label{eq:fRange}
    \text{.}
    \end{align}
  This range can be seen as the power spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
  Note that instead of the geometric mean, the arithmetic mean can be used in \eqref{eq:fRange} to calculate almost identical boundaries.

  \subsection{Comparison of the frequency grids}
  To gain some insight into these different grids, \figref{fig:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
  For this example, a frequency spacing $\Delta f = 1\unit{Hz}$ and frequency ratio $\alpha = 1.05$ are used.

  \begin{figure}[ht]
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \label{fig:freqGrids}
  \end{figure}

  At the lowest frequencies the quasi-log grid and the linear grid frequencies do coincide and each line in the quasi-log grid is surrounded by many lines of the log grid.
  The amplitudes of the compensated and pink quasi-log lines show that the compensation only has effect at the lower frequencies since the uncompensated counterpart has an amplitude spectrum close to $1$.
  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.

\section{Optimization of the frequency spacing} \label{sec:optimAlpha}
  \subsection{Calculation of the model uncertainty}
  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing factor $\alpha$, has not been designed for.
  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
  Doing so will allow to determine a suitable value for the frequency spacing $\alpha$.

  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \cite{Pintelon2001, Gallager2008, matrixcookbook} to be approximately equal to
  \begin{align}
    \C_{G\left( \omega_{\interest}\right) } \approx
      \InnerQuadraticForm[\HT]
                         {\jac{\interest}}
                         {\FisherInformation_{\theta}^{-1}}
     \label{eq:varPeak}
  \end{align}
  with 
  \begin{equation}
    \FisherInformation_{\theta} =
    2
    \real{
          \InnerQuadraticForm[\HT]
                              {\jac{\excited}}
                              {\C_{X}}
          }
    \label{eq:FisherInfo}
  \end{equation}
  the Fisher information matrix \cite{Pintelon2001}.

  In these expressions, the Jacobian $\jac{\interest}$ matrix of the transfer function evaluated at the frequency of interest $\omega_{\interest}$ with respect to the model parameters $\theta$ is defined as
  \begin{equation}
    \jac{\interest} \isdef
         \PartialDerivative{G\left( \omega_{\interest}, \theta \right) }
                           {\theta}
    \text{.}
  \end{equation}
  Similarly, $\jac{\excited}$ is the Jacobian calculated at the excited frequency lines $\omega_{\excited} = \set{\omega_1, \ldots, \omega_F}$.

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \cite{Pintelon2001}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
                 0 & \ddots & 0 \\
                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}

  In this paper, we select a single frequency of interest $\omega_{\interest}$
  to obtain a scalar performance measure.
  This is allowed as the matrix $\C_{X}$ is diagonal.

  \subsection{Relation between the frequency grid and the system resonance} \label{sec:relationLogGridSystem}
  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated FRFs of a set of prototype second-order systems excited by logarithmically spaced excitation signals.

  Define $G_{1}$ for a second-order system with resonance frequency $\wn$, damping $\damping$ and DC gain $\dc$.
  Denote $G_m$ a second-order system with the same $\damping$ and $\dc$ but a resonance frequency of $m\wn$.
  If one calculates their FRFs by evaluating \eqref{eq:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
  Both FRFs share the same `shape', but are `located' at different frequencies.

  Let's select a logarithmic frequency grid with an infinite number of grid lines
  \begin{equation}
    \vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}
    \label{eq:freqGridLog}
    \text{.}
  \end{equation}
  Consider a second grid, defined as a multiple of this grid, $m\vec{\omega} = \set{m \cdot \alpha^k \omega_0 \given{k \in \ZN}}$; both grids share the same frequency ratio $\alpha$.

  It is easy to show that for $m = \alpha^N$ the following relation holds:
  \begin{equation}
    G_1\left( \vec{\omega} \right)
    \stackrel{(a)}{=} G_{\alpha^N} \left( \alpha^N \vec{\omega} \right)
    \stackrel{(b)}{=} G_{\alpha^N} \left( \vec{\omega} \right)
    \label{eq:gridPeriodicity}
  \end{equation}
  since
  \begin{itemize}
   \item[(a)] the numerical values of the FRFs $G_1(\vec{\omega})$ and $G_m(m\vec{\omega})$ are equal and,
   \item[(b)] the grids $\alpha^N \vec{\omega} = \set{\alpha^{k+N} \omega_0 \given{k \in \ZN}}$ and $\vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}$ coincide for integer values of $N$.
  \end{itemize}

  This shows that systems with equal $\damping$ and $\dc$ but resonance frequencies that differ by a factor $\alpha^N$, will share an identical `shape` of their response at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.

  Taking this into account allows to limit the study of second order systems to a small set of systems that should be considered in the search for a suitable grid spacing $\alpha$.
  We can limit the evaluation of the theoretical uncertainty \eqref{eq:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
  \begin{equation}
    \wn \alpha^{N+\gamma}\qquad \text{ with } 0 \leq \gamma < 1\text{.}
    \label{eq:theoreticalBestVariationOmega}
  \end{equation}
  The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
  The value $N$ will not influence the `shape` (and uncertainty) of the FRF.

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test can be considered within the `bulk' of the frequency grid with finite support.
  I.e. there should be a few excited frequency lines that are logarithmically spaced, outside of the resonance peak of the actual system.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

  \subsection{Setup for selecting $\alpha$}
  When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
  Note that $\dc$ is a scaling factor for the FRF.
  Hence the results for different values of $\dc$ only differ by a scaling factor.
  So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.

  The choice of the damping is more important.
  Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:peakAmplitude} to study the effect of differently damped systems.

  Since the damping influences the $3\unit{dB}$ bandwidths, it will become important when one has to determine the grid spacing $\alpha$.
  To deal with this, we introduce the normalized frequency ratio
  \begin{equation}
    \tilde{\alpha} = \frac{\alpha - 1}
                          {\damping}
                   \propto \frac{\omega_{k+1} - \omega_k}
                                {\wdB}
                           \cdot
                           \frac{\wn}{\omega_k}
    \text{.}
    \label{eq:normAlpha} 
  \end{equation}
  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the bandwidth is approximately $2\damping\wn$.
  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:normAlpha} can safely be neglected.

  To determine a suitable value of the frequency spacing ratio $\alpha$ for the logarithmic and (compensated) quasi-logarithmic grid, we construct a logarithmic multisine signal in the frequency domain for a given frequency band (in this example, $\left[ 0.01 \unit{rad/s}, 100 \unit{rad/s}\right]$ was used).
  In the previous section we saw that systems with equal damping and DC gain, will behave very similarly when excited by a log signal with spacing $\alpha$.

  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $[0,1]$.
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

  We normalize the root mean square (RMS) value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
  The noise level is kept constant, which causes the signal-to-noise ratio (SNR) per excited line to drop for more finely spaced excitation signals.
  % SNR correct: Pnoise ~ sE^2
  %              Psignal ~F*U^2 = 1 ==> U^2 = 1/F
  %              SNR = Psignal / Pnoise = 1/(sE^2 * F)
  %          ==> SNR decreases as F increases

  We then calculate the theoretical variance on the magnitude of the peak in the FRF ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:varPeak} for a coarse grid.
  A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked by such an FRF.

  For each set of second order systems, we determine for which value of the misalignment coefficient $\beta$ the maximum variance on the FRF is obtained.

  For these worst cases, we study how the frequency spacing $\alpha$ influences the uncertainty by decreasing $\alpha$ until no further improvement can be obtained.

  \subsection{Discussion} \label{sec:bestFrequencyResolution}
  As stated above, we start by evaluating the variance $\sigma_G\left( \wM\right)$ for a coarse frequency spacing $\tilde{\alpha} = 10$ for each of the prototype systems.
  This is shown by the solid lines in \figref{fig:worstCaseBeta}.
  One immediately notices that the variance depends strongly on the misalignment $\beta$ of the system and the frequency grid.

  \begin{figure}
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.65\columnwidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:optimAlpha}).}
    \label{fig:worstCaseBeta}
  \end{figure}

  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will entail a large increase in the uncertainty of estimate.

  For a large peak amplitude of the FRF (low damping), the worst case increase (marked with a cross) is approximately centered around $\beta = 0.5$ (i.e. midway between the nearest excited lines).
  In systems with a higher damping, this symmetry is lost.
  This can be explained intuitively as the $3\unit{dB}$ bandwidth is less symmetric for highly damped systems than in lightly damped systems with a very narrow resonance peak.
  Also note that the value of $\sigma_G\left(\wM \right)$ is practically identical for $\beta=0$ and $\beta=1$.
  This is in accordance with the claim that in the bulk of the grid, a shift over an integer number of lines will only marginally influence the uncertainty.

  We explore the systems which have the worst uncertainty (as marked by a cross in \figref{fig:worstCaseBeta}).
  For the corresponding values of the misalignment $\beta$, we evaluate the uncertainty when the frequency ratio $\alpha$ of the signal is decreased, while the total signal power is kept identical.
  The results are displayed in \figref{fig:worstCaseAlpha}, where the marked points correspond to the marked points in \figref{fig:worstCaseBeta}.

  \begin{figure}[ht]
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.65\columnwidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:worstCaseAlpha}
  \end{figure}

  We notice that for sufficiently low $\tilde{\alpha}$, the variance on $G\left( \omega_M \right)$ is roughly independent of $\alpha$.
  We will choose the optimal grid spacing
  \begin{equation}
    \alpha^{\star} = 1 + \damping
    \label{eq:optimAlpha}
  \end{equation}
  such that it represents the coarsest frequency spacing for which the variance is approximately equal to that constant value.
  This choice is indicated by the dashed line in \figref{fig:worstCaseAlpha}.

  Choosing a finer grid will not improve the estimated $G\left( \wM \right)$ significantly.
  But, on the other hand, a coarser grid will significantly decrease the quality of the measurement.
  A grid that is too coarse will overlook the resonance peak.
  Hence little information can be extracted from such a measurement (i.e. the variance on the estimate will be large).

  If we determine the effect of the misalignment factor $\beta$ for a grid with frequency ratio $\alpha^{\star}$, we see that misalignment has a negligible effect on the uncertainty as shown by the dashed lines in \figref{fig:worstCaseBeta} for each of the prototype systems.
  Note that these values do indeed coincide with the limiting values found in \figref{fig:worstCaseAlpha}.

  Now we can interpret \figref{fig:worstCaseBeta} in more detail.
  We see that for $\beta \in \set{0,1}$ (i.e. perfect alignment), the variance of a course grid (full lines) is lower than it is for a fine grid (dashed lines).
  This is to be expected as a coarse grid places more power at each individual line.
  Thereby it yields a smaller variance at those lines.
  It is better tailored to systems which are closely aligned to the excited frequency grid.
  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance will increase significantly and very fast.
  This effect is more important for lowly damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.

  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the FRF of the system are visualized in \figref{fig:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
  The $3\unit{dB}$ bandwidth of the system is highlighted in gray together with the excited frequency lines that lie within that bandwidth.

  \begin{figure}%
    \centering
      \setlength\figureheight{4cm}
      \setlength\figurewidth{0.7\columnwidth}
    \input{\thisDir/figs/SignalAndSystem.tikz}
    \caption{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$. The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
    \label{fig:signalAndSystem}
  \end{figure}

  We see that to attain this, four frequency components are needed within this bandwidth in order to be almost completely independent of misalignment.

  In this section, we have shown that signals with a logarithmic frequency spacing allow to identify systems with equal damping equally well, when the frequency spacing is dense enough.
  Practically, four frequency lines in the $3\unit{dB}$ bandwidth of each second order subsystem suffice to suppress the effect of misalignment of such a subsystem and the frequency grid of the excitation signal.

\section{Simulations} \label{sec:simulation}
In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:secondOrderSystemDTidentifiable}
  \end{equation}

  This form can also be obtained by applying Tustin's method or bilinear transform \cite{Oppenheim1983} to the continuous time system \eqref{eq:secondOrderSystemCT}.

  The input signal has an equidistant frequency grid with a resolution $\Delta f = 1\unit{Hz}$ between $1 \unit{Hz}$ and $16\,384\unit{Hz}$.
  The sampling frequency $f_s$ is set to $65\,536\unit{Hz}$ to prevent aliasing.
  For the quasi-log grid multisine, the compensated and pink quasi-log multisine, we chose a frequency ratio $\alpha = 1.05$.
  According to \eqref{eq:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the FRF $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
  Each of these signals is constructed to have an RMS value of $1$.
  The amplitude spectra of these signals are displayed in \figref{fig:freqGrids} for identical signal power.

  At the output of the systems, white Gaussian noise $e[n]$ is added such that its standard deviation is approximately $10\%$ of the RMS value of the output.

  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT \cite{FDIDENT} for \matlab.
  This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
  To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.

  Such an experiment is repeated $R=1000$ times with a different random phase
  spectrum $\phi_k$ and a different noise realization $e[n]$ for each experiment.

  \subsection{Systems with a `high' damping}
  To test the signals for systems with a high damping with respect to the frequency ratio in the excitation signal, systems with a damping $\damping = 0.2$ are used.
  White Gaussian noise $e[n]$ with a standard deviation $\sigma_e \approx 0.0678$ added to the output.

  The resulting frequency response function $\hat{G}$ for one such system is shown in \figref{fig:FRF1} together with the standard deviation $\sigma_{\hat{G}}$ of the estimated parametric model for each of the different excitation signals.
  The bias is at least $20\unit{dB}$ smaller than the standard  deviation.
  Therefore the mean squared error (MSE) will be determined mainly by the variance of the estimate instead of the bias.

  \begin{figure}[th]
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
             along with the corresponding variance and bias.}%
    \label{fig:FRF1}
  \end{figure}

  \figref{fig:damping02} displays the estimated transfer functions and their uncertainty in the vicinity of their corresponding resonances for the whole set of considered systems.
  Using this condensed representation and the displayed envelopes of the uncertainty, we can deduce the frequency-dependent behavior of the model variance obtained by the different excitation signals.

  \begin{figure}%
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption{FRFs for different second order systems with constant damping
             $\damping=0.2$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping02}
  \end{figure}

  For the linear grid multisine, the uncertainty is strongly dependent on the frequency, and is proportional to $1/\fR$.
  The uncertainty is generally higher than the uncertainty obtained with logarithmically spaced multisines, as the power has been divided over more excited lines.

  The quasi-log multisine already shows a fairly flat uncertainty of about $-52 \unit{dB}$ at the higher frequency ranges.
  Yet at the lowest frequencies, the $1/\fR$ dependence can be observed again.
  This is caused by the linear distribution of excited frequencies in this range, as shown in \figref{fig:freqGrids}.

  The compensated quasi-log multisine shows a more constant variance of about $-51 \unit{dB}$ even at these low frequencies.
  As more power is placed at low frequencies, less power can be placed at the higher ones.
  This causes a slightly increased variance compared to the regular quasi-log multisine.
  At the studied system with the lowest resonance frequency, the compensation fails to completely compensate the effects of the reduced number of lines in the $3\unit{dB}$ bandwidth of that system.
  Nevertheless an improvement of about $5\unit{dB}$ is obtained with respect to the regular quasi-log multisine.

  \subsection{Systems with a lower damping}
  Given the optimal frequency ratio \eqref{eq:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
  In this set of simulations, we check this by repeating the previous set for such systems.
  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the SNR of $20\unit{dB}$.
  The corresponding results are shown in \figref{fig:damping005}.

  \begin{figure}%
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption{FRFs for different second order systems with constant damping
             $\damping=0.05$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping005}
  \end{figure}

  At the higher frequency bands, an approximately constant quality is still obtained for the (compensated) quasi-logarithmic signals.
  At lower frequencies, however, the logarithmically spaced signals perform only slightly better than the linearly spaced excitation signal.
  This is due to the fact that as the damping $\damping$ decreases, the $3\unit{dB}$ bandwidth of the resonance decreases and therefore less points can be fitted in this bandwidth at the lower frequencies.
  In our case, only $1$ line was excited in the $3 \unit{dB}$ bandwidth (respectively $0.4 \unit{Hz}$ and $0.8\unit{Hz}$ wide) of the systems with the lowest resonance frequencies.
  It is clearly unfeasible to estimate the five parameters in
  \eqref{eq:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
  In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
  We do see, however, that the variance in the vicinity of the resonance is lower than in the case of a linearly spaced excitation.

\section{Measurements} \label{sec:measurement}
  \subsection{Setup}
    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.

    The BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
    According to its manual \cite{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \cite{Zverev1967} for which the poles have a damping that is larger than $0.09$.
    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy comparison between the different filters of the model uncertainty.

    As excitation signals, a linear grid multisine, an uncompensated quasi-log multisine and pink quasi-log multisine with excited frequencies between $1 \unit{Hz}$ and $64 \unit{kHz}$ were used.
    These multisines were sampled at $\fs = 256\unit{kHz}$ and had a frequency resolution of $\Delta f = 1 \unit{Hz}$, a frequency spacing $\alpha = 1.05$ and identical RMS values of approximately $0.25 \unit{V}$.
    This amplitude was chosen such that the peak amplitude $\max \abs{u(t)}$ was approximately $1 \unit{V}$.

    $R=50$ periods of the multisine were measured, from which the first period was discarded to suppress transient effects.
    For each of the remaining periods, the FRF of the filter is calculated and its average $G\left(\omega \right)$ over the periods is calculated.
    We also calculate the corresponding standard deviation $\sigma_G\left( \omega \right)$ of the FRF and normalize it for a single period of the excitation signal.
    We denote $G\left(\omega \right)$ the non-parametric FRF and $\sigma_G\left( \omega \right)$ its standard deviation, as these measures are determined completely nonparametrically from the measurements.

    For the parametric model, on the other hand, a continuous time LTI model of the form
    \begin{equation}
      G(s) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis} \cite{FDIDENT}.
    The initial estimate was a third-order band-pass type I Chebyshev filter \cite{Zverev1967} that conformed to the information given in the datasheet \cite{datasheet_bk1613}.

    We summarize the behavior of these parametric models by their average $G\left(\theta,\omega \right)$ over the different periods and their standard deviation $\sigma_G\left(\theta,\omega \right)$.

    \subsection{Results}
    In \figref{fig:measurements} the nonparametric FRF and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.

    \begin{figure}%
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
      \label{fig:measurements}
    \end{figure}

    The uncertainty $\sigma_G\left(\theta,\omega\right)$ on the parametric model in its pass-band is observed to be nearly constant for most of the filters when excited by the (pink) quasi-log multisine.
    For the linear grid multisine excitation, $\sigma_G\left(\theta,\omega\right)$ in the pass-band is clearly decreasing proportional to $1 / f$ for the different octave filters.
    One can see that the performance of both uncompensated quasi-log and pink quasi-log multisines is practically identical.
    This can be explained by the fact that in this experiment, $f_0$ was chosen low enough to ensure that all the second-order subsystems had their $3\unit{dB}$ bandwidth within the bulk of logarithmic part of the excited grid.
    This observation also shows that in this practical application, the increase in uncertainty between the uncompensated and compensated quasi-log multisines is negligible, as was observed earlier in the simulations.
    However, if the system under test would have a lower resonance frequency, a quasi-log multisine with power compensation would perform better as was seen in the simulations.

\section{Conclusion} \label{sec:conclusion}
The suggested compensation method allows the user to measure a parametric LTI model for systems in a wide frequency band with a constant uncertainty.
The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
In practical applications, this slight increase is likely to be negligible.
The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.

We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equidamped set of systems.
The presented method allows to select a maximal value for the frequency factor $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.
In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.

### 2015-10-25 ch02-qlogms/logMS_IMTC.tex
Some TODOs in QLogMS

@@
 \def\thisDir{ch02-qlogms}
+\TODO{reshape figures}
+\TODO{rename labels}
+\TODO{import specific bib items}
 % \begin{abstract}
@@
 \section{Introduction} \label{sec:intro}
-  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades \cite{bragos2001characterisation,sanchez2011optimal,niedostatkiewicz2009,VanGheem2004}.
+  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades \citep{bragos2001characterisation,sanchez2011optimal,niedostatkiewicz2009,VanGheem2004}.
   Of course, we also want to attain a specified uncertainty level over the full frequency span.
 
-  Any LTI system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\cite{Oppenheim1983}.
+  Any LTI system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
   Therefore the performance of the proposed method is assessed on a prototype system of second order.
@@
   Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
-  This problem was already discussed in \cite{GeerardynIMTC2012}.
+  This problem was already discussed in \citet{GeerardynIMTC2012}.
 
@@
   When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in
-  the amplitude of the transfer function \cite{Oppenheim1983}:
+  the amplitude of the transfer function \citep{Oppenheim1983}:
   \begin{align}
@@
 
+  \TODO{put block diagram here}
+
 \subsection{Multisine Excitations}
-  To excite the system under test we will use multisine excitations \cite{Pintelon2001} with $F$ commensurate frequency components:
+  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ commensurate frequency components:
   \begin{equation}
@@
 
+  \TODO{put MATLAB code for each type of signal}
+
 \subsection{Equidistant (Linear) Grid Multisine}
-  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \cite{OppenheimDT,Mandal2007}.
+  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \citep{OppenheimDT,Mandal2007}.
 It allows to analyze periodic signals on an equidistant frequency grid very efficiently.
@@
   \end{equation}
-  Such a grid is called a quasi-logarithmic (quasi-log) grid \cite{Pintelon2001}.
+  Such a grid is called a quasi-logarithmic (quasi-log) grid \citep{Pintelon2001}.
 
@@
   \subsection{Pink Quasi-Logarithmic Multisine}
-  In \cite{Rojas2007} it is suggested that band-limited $1/f$ noise is a reasonable, albeit not optimal, robust excitation signal.
+  In \citep{Rojas2007} it is suggested that band-limited $1/f$ noise is a reasonable, albeit not optimal, robust excitation signal.
 
@@
 
-  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \cite{Pintelon2001, Gallager2008, matrixcookbook} to be approximately equal to
+\TODO{zin loopt niet goed}
+  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2001, Gallager2008, matrixcookbook} to be approximately equal to
   \begin{align}
@@
                               {\jac{\excited}}
-                              {\C_{X}}
+                              {\C_{X}^{-1}}
           }
@@
   \end{equation}
-  the Fisher information matrix \cite{Pintelon2001}.
+  the Fisher information matrix \citep{Pintelon2001}.
 
@@
   Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
-  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \cite{Pintelon2001}:
+  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2001}:
   \begin{equation}
@@
 
+  \TODO{formulate as lemmas, show steps}
   It is easy to show that for $m = \alpha^N$ the following relation holds:
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform \cite{Oppenheim1983} to the continuous time system \eqref{eq:secondOrderSystemCT}.
+  This form can also be obtained by applying Tustin's method or bilinear transform \citep{Oppenheim1983} to the continuous time system \eqref{eq:secondOrderSystemCT}.
 
@@
 
-  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT \cite{FDIDENT} for \matlab.
+  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT \citep{FDIDENT} for \matlab.
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
@@
     The BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
-    According to its manual \cite{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
-    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \cite{Zverev1967} for which the poles have a damping that is larger than $0.09$.
+    According to its manual \citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
+    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
     Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
@@
     \end{equation}
-    was estimated using \texttt{elis} \cite{FDIDENT}.
-    The initial estimate was a third-order band-pass type I Chebyshev filter \cite{Zverev1967} that conformed to the information given in the datasheet \cite{datasheet_bk1613}.
+    was estimated using \texttt{elis} \citep{FDIDENT}.
+    The initial estimate was a third-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613}.
 

### 2015-10-27 ch02-qlogms/logMS_IMTC.tex
Use tikz external

@@
   Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
-  This problem was already discussed in \citet{GeerardynIMTC2012}.
+  This problem was already discussed in \citet{Geerardyn2012IMTC}.
 
@@
 
+  \TODO{link naar log meas mode DSA (e.g.
+HP3562A) leggen.
+Bij HP 3562A, is $F/\mathrm{decade} = 80$, oftewel $\alpha = \sqrt[80]{10} \approx 1.029$ vast ingesteld.
+Dit beperkt bruikbaarheid van zo'n toestel.}
+
   Each decade within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains the same number of frequency components such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
@@
     \input{\thisDir/figs/freqGrid.tikz}
-    \caption{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
+    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
     \label{fig:freqGrids}
   \end{figure}
+
+  \TODO{plot: $\alpha $ (evt. $\cdot A_k^2$) i.f.v. $\omega$ voor verschillende signalen.}
+  \TODO{plot: $\Delta f $ i.f.v. $\omega$ voor verschillende signalen} 
+  \TODO{plot: $\# \omega / \mathrm{decade}$ i.f.v. $\omega$ voor verschillende signalen}
 
@@
   This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
-  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the bandwidth is approximately $2\damping\wn$.
+  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
   Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:normAlpha} can safely be neglected.
@@
     \input{\thisDir/figs/betaWC.tikz}
-    \caption{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
+    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
              The full lines depict the variance for a coarsely spaced signal.
@@
     \input{\thisDir/figs/alphaWC.tikz}
-    \caption{Worst case variance of the peak in the transfer function for logarithmic
+    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
              grid multisines and systems with different peak amplitudes.
@@
     \input{\thisDir/figs/SignalAndSystem.tikz}
-    \caption{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$.
+    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$.
 The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
@@
     \input{\thisDir/figs/Sys02-4.tikz}
-    \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
-             along with the corresponding variance and bias.}%
+    \caption[Simulated FRF and its variance for different excitation signals.]{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
+             along with the corresponding variance.}%
     \label{fig:FRF1}
@@
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption{FRFs for different second order systems with constant damping
+    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{FRFs for different second order systems with constant damping
              $\damping=0.2$ but different resonance frequencies. Comparison of the
@@
     \input{\thisDir/figs/damping005-cmp.tikz}
-    \caption{FRFs for different second order systems with constant damping
+    \caption[Simulated FRFs and their variances of systems with $\damping=0.05$ for different excitation signals.]{FRFs for different second order systems with constant damping
              $\damping=0.05$ but different resonance frequencies. Comparison of the
@@
     \input{\thisDir/figs/qlog_a050mall.tikz}
-    \caption{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
+    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
       \label{fig:measurements}
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+
+\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}

### 2015-10-27 ch02-qlogms/logMS_IMTC.tex
emove old bib defs

@@
-\def\thisDir{ch02-qlogms}
 \TODO{reshape figures}
@@
 \section{Introduction} \label{sec:intro}
-  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades \citep{bragos2001characterisation,sanchez2011optimal,niedostatkiewicz2009,VanGheem2004}.
+  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
   Of course, we also want to attain a specified uncertainty level over the full frequency span.

### 2015-10-28 front-and-back-matter/titlepages.tex
Add title page, some bib changes

%\promotortitle{Promotor/Promotors}
\promotor{
  \jurymember{prof. dr. ir.}{Johan Schoukens}{Vrije Universiteit Brussel}
  \jurymember{dr. ir.}{Tom Oomen}{Eindhoven University of Technology}
}

\title{Development of User-friendly\\System Identification Techniques}

\author{ir. Egon Geerardyn}

\jury{
  \jurymember{prof. dr. ir.}{Keith R. Godfrey}{Warwick University}
  \jurymember{prof. dr. ir.}{Tomas McKelvey}{Chalmers}
  \jurymember{dr. ir.}{Bart Peeters}{LMS}
  \jurymember[president]{prof. dr. ir.}{Johan Deconinck}{Vrije Universiteit Brussel}
  \jurymember[secretary]{dr. ir.}{Koen Tiels}{Vrije Universiteit Brussel}
}

\date{\today~~{\color{gray}(\texttt{\VCRevision})}}

\maketitlepage

### 2015-10-28 ch03-lrm/nonparametric.tex
Use make for figures, config compartments

\chapter{Non-parametric modeling}

\TODO{import LRM paper}
\TODO{import Mikaya LPMTrunc paper}

### 2015-10-28 ch05-initvals/InitialValuesPaper.tex
Include initial values
Also quite a bit of pgfplots external trickery/hackery
to make sure the file compiles.

% % BEGIN OF TIKZ ONLY
% \usepackage{tikz,pgfplots}
% \usepackage{pgfplotstable}
% \pgfplotsset{compat=newest}
% \usetikzlibrary{external}
% %\tikzset{external/optimize=false}
% \tikzset{external/mode=list and make}
% \tikzexternalize[prefix=tikz/]
% \tikzsetfigurename{figure}
% \input{\thisDir/styles.inc.tex}
% % END OF TIKZ ONLY
% \newcommand{\legref}[2][1]{(\ref{#2})}

%  \newlength\figureheight
%  \newlength\figurewidth
%  \setlength\figureheight{7cm}
%  \setlength\figurewidth{10cm}

%  \newlength\onecolumnwidth
%\title{Improved Initial Estimates Via FRF Smoothing Techniques for Parametric Identification of LTI Systems}

% \begin{abstract}
% Good initial values are crucial to obtain solutions of non-convex optimization problems. When estimating the transfer function of physical systems from measured noisy data, obtaining good initial parameter estimates is therefore a primordial step.
% In this paper, it is shown that smoothing the measured frequency response function (FRF) of a linear time-invariant system enhances the construction of initial estimates significantly, resulting in the optimization schemes to converge to a better optimum. 
% This is achieved with minimal user interaction.

% Two smoothing techniques, the time-truncated local polynomial method (LPM) and the regularized finite impulse response (RFIR), are compared with the existing generalized total least squares (GTLS) and the bootstrapped total least squares (BTLS) initial estimates. 
% The improvement attributable to smoothing is demonstrated by a simulation and by measurements of an electrical filter. 
% The results ultimately show that the parametric models obtained using the proposed starting values are much more likely to give a good description of the measured system and hence lead to more useful models.
% \end{abstract}

\setlength\onecolumnwidth{0.75\columnwidth}

%\comment{JL: 
%Focus of the article (this is what the article must reflect):

%\begin{itemize}
%\item demonstrate that a smoothed FRF, obtained as described in \cite{Lumori2014}, used as an initial estimate increases the success rate of a parametric LTI TF identification
%\item
%\comment{JL:  emphasize the importance of extending the SNR range for which the success rate is acceptable, yielding a reliable parametric estimator to be used with as little user interaction as possible.
%\end{itemize}
%}

\tikzset{external/export=false}
\section{Introduction}\label{se:introd}

The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723}.
Application of these methods to real devices and systems is well-known in published literature, including \cite{Lim2010,Robinson1990,Behjat2010}.

Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\cite{FDidentEd2Pintelon,Ljung1999,schoukens1999,pintGuil1998}. 
 Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
 However, in a noisy environment, the maximum likelihood estimator (MLE) engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
 Such local optima have a detrimental effect on the quality of the estimated model.

 In the perspective of developing identification tools that require as little user interaction as possible, it is important to increase the probability of the optimization algorithm to produce good estimates, or preferably even the global optimum.
 However, when noisy input-output measurements are to be processed, the presence of noise obstructs a clear view of the actual system behavior, especially for poor signal-to-noise ratios (SNRs).
 In non-parametric identification, the presence of noise is typically mitigated by averaging multiple measurements or using smoothing techniques.

The main aim and contribution of this article is to demonstrate that smoothing a measured FRF helps to avoid local optima during the parametric estimation of the MLE of a transfer function, using deterministic optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\cite{Lumori2014} and the regularized finite-impulse response (RFIR)~\cite{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).

The rest of the paper is structured as follows. Section~\ref{se:ProbForm} covers the problem formulation. Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the MLE. 
This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
In Section~\ref{se:Generality} the generality of the results is discussed briefly.
Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.

% !TEX root =  InitialValuesPaper.tex

\section{Problem formulation}\label{se:ProbForm}
%\begin{itemize}
%\item
%Block schematic of the output error framework

%\JL{In this section, the assumptions on the system and the noise are given, and the associated Maximum Likelihood estimator, formulated in the frequency domain. The latter turns out to be a non-convex function in the parameters, requiring initial estimates. The obtention of those is discussed in the subsequent section.}

In this section, the assumptions on the system and the noise are presented, together with the associated MLE (formulated in the frequency domain), which turns out to be a non-convex function in the parameters, requiring initial estimates. The procedure for obtaining the initial estimates is discussed in the subsequent sections.

\subsection{System Setup Framework and Model}
\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input. The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well. The full mathematical model of the system is
\begin{equation}\label{lpmtd1}
y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
\end{equation}
%\comment{We don't have any results with colored noise yet!}
where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics, 
%\comment{JL: note that $H_0 = 1$ in this paper, so only white noise is considered, i.e. $e(t) = v(t)$.}, 
$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
For white noise, $H_0 = 1$ and $e(t) = v(t)$.
Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this paper.
However, the generalization to continuous time is straightforward~\cite[Chapter 6]{FDidentEd2Pintelon} and has been demonstrated in Section~\ref{se:ExpMeas}.

\begin{figure}[tbh] %top bottom here
\centering
\input{\thisDir/fig/oesetup.tikz}
\caption{SISO LTI discrete-time system in an output error setup.}
\label{fig:oesetup}
\end{figure}

Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.

The output signal is disturbed by white random noise, resulting in noisy error-prone data. It is also possible to apply the estimation procedure in this paper to a system that is disturbed by colored noise, as will be demonstrated in Section~\ref{se:ExpMeas}.

\subsection{Parametric System Model}

With reference to equation (\ref{lpmtd1}), the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
\begin{equation}
    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t)
\label{ABpolys}
\end{equation}
where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation (\ref{lpmtd1}) that
\begin{equation}
    G_0(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
    \text{.}
\end{equation}

From~\cite[Section 6.3.2.]{FDidentEd2Pintelon}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
\begin{align}
A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
\label{DFTspectra}
\end{align}
with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions. 
In this paper, it is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.

\subsection{Parametric Identification Algorithm}\label{se:paramIdentAlgo}

The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
\begin{equation}
  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
\end{equation}
Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\cite[Section 9.11]{FDidentEd2Pintelon}:
\begin{equation}\label{eq:MLEcf}
V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
\end{equation}
for $N$ measurements and when $\varepsilon$ denotes the error in equation (\ref{DFTspectra}),  \emph{viz}.:
\begin{align}
\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
\end{align}
The variance of the error is of the form:
\begin{equation}\label{eq:sigmaEps}
\begin{split}
\sigma_\varepsilon^2(k,\theta) 
  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
   +  |B(k,\theta)|^2\sigma_U^2(k) \\
  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
\end{split}
\end{equation}
where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known? where do you use that? how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$. Isn't it the same thing?},
%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
Here, $\overline{B}$ denotes the complex conjugate of $B$.
%\comment{use $\sigma^2_U$ instead}

Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
The Levenberg-Marquardt~\cite{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this paper.

\begin{algorithm}
\caption{Levenberg-Marquardt~\cite{Marquardt1963}, \cite[Sec. 9.L.4]{FDidentEd2Pintelon}}\label{LMalgo}
\begin{algorithmic}[1]
  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \snorm{\atIter[i-1]{\theta} + \delta\theta} $
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \State \textbf{if} $\snorm{\delta\theta}/\snorm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
   \EndFor
%\EndFunction
\end{algorithmic}
\end{algorithm}

\begin{remark}
Alternatively, stochastic optimization algorithms~\cite{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
Stochastic optimization is not discussed in the remainder of this paper.
\end{remark}

\section{Methodology}\label{se:MethodEg}
In this section, the considered methods for obtaining the initial estimates of $\theta$ are briefly explained. Then their influence on the success rate of the maximum likelihood estimator is described.
%}

\subsection{Initial Estimates Procedure}\label{se:initEstProcs} %{Obtaining initial estimates}

%\begin{itemize}
%\item
%Obtain a good estimate of the FRF of the system by using the LPM: short description + reference

\begin{figure}
  \centering
  \includegraphics
  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
  \caption{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
  The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
\end{figure}

The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the MLE optimization process in the parametric identification of each system. 
The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:

\begin{enumerate}
\item
\emph{Using the true model ($G_0$) as initial estimate}

The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the MLE.

\item
\emph{Quadratic approximations of the ML}

%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}. These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$. These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$). Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}

The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior is suitable for improvement by the FRF smoothing tools, described below.

\item
\emph{Local polynomial method (LPM) with truncation}

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \cite{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact FRF $G_0$ and the transient term
%the leakage 
$T$ 
%from transients 
allow for an optimal application of the LPM, leading to a smooth FRF estimate with the transient suppressed.
%the elimination of both the leakage and interpolation errors.

  With reference to a detailed discussion in~\cite{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

  The LPM estimate of the FRF at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

%The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.

\emph{Impulse response truncation}. 
%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\cite{Lumori2014}.
%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.

The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
    0                    & t \geq \tau_{\mathrm{trunc}}
  \end{cases}
  \text{.}
\end{equation}
To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this paper for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\cite{Lumori2014}.

\item
\emph{Regularized finite impulse response (RFIR)}

%\ML: {This is included for comparison purposes .....}
The regularized finite impulse response (RFIR) method is a special case of the regularized autoregressive exogenous (RARX) method. 
%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.

%\JL{
The RFIR estimator is formulated in the time domain. It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
In this paper, the Diagonal Correlated (DC) kernel is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the log marginal likelihood (LML) of the measured output signal:
\begin{align}
\text{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \texttt{fmincon} in \MATLAB.

An implementation of the RFIR estimator is available as the \texttt{arx} function in the System Identification Toolbox since \MATLAB 2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \texttt{arxoptions}. 
The hyperparameters can be determined via \texttt{arxregul}.
More information about the RFIR estimator can be found in
~\cite{Pillonetto201081,Chen20121525}. 
The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

%\JL{
%{remark}
%\label{rem:FRFasSpectrum}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the FRF. A corresponding parametric estimate is obtained as follows. A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be 1 at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero. It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data. This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
%\end{remark}
%}

%\comment{JL: one could remove the subsection below (why? see my comments below), and mention that the the above initial estimates are then fed to the MLE, with the raw data, to obtain the final estimates.}

%\subsection{Genesis of the Initial Estimates} 
%\comment{JL: why `genesis'? This section is actually where you use the initial estimates, not their origin.}
%{Deploying the initial estimates}

%\comment{ML: Fig. \ref{fig:flowgraph} should include an additional path for RFIR/RARX, and the accompanying text (below) is to be modified accordingly.}
%Fig. \ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart? It has actually been explained in further details in \sectref{se:initEstProcs}.}
%\begin{enumerate}
%\item (Left (first) path of the flowchart): The true model $G_0$ as initial values,
%\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
%\item (Third path from the left of the flowchart): The LPM-truncated initial values with BTLS and GTLS, and  
%%\item (Right (fourth) path of the flowchart): The RFIR initial values with BTLS and GTLS.  
%\end{enumerate}

%\JL{
%The main contribution of this paper is to demonstrate that $\hat G_\mathrm{trunc}$ (third path) yields an improvement over $\hat G_\mathrm{exist}$ (second path). \comment{JL: these symbols haven't been introduced yet. I'm getting quite confident that this subsection can be removed.}The quantification of this improvement is formally introduced in the next section.
%}

%The latter 2 ....schematic is configured to include connections of the initial values and the input to the LPM block and/or to the MLE block(s) for estimation purposes.
%\end{itemize}
%\section{Example}\label{se:Example}

\subsection{Success Rates of the Initial Estimates}

The initial estimates described above are then fed to the MLE together with the raw data to obtain the final estimates.

Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
\begin{itemize}
\item 
$\model{0}$ via the true model $G_0$ as an initial estimate,
\item
$\model{exist}$ is obtained via GTLS and BTLS,
\item
$\model{trunc}$ via use of the LPM with truncation as an initial estimate,
\item
$\model{RFIR}$, initialized by means of the RFIR method. 
\end{itemize}

A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.

\begin{conjecture}\label{conj1}
In this paper it is assumed that use of the true model as an initial estimate for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) is the best possible initial estimate and will allow the optimization to converge to the \emph{best local optimum}, i.e. $\model{0}$.
%\JL{The associated model is denoted $\hat G_0$.}
\end{conjecture}
From this conjecture, use of the true system as an initial estimate would engender the best final estimate or hopefully even the global optimum.
Since the true system is not really known in practice, the work in this paper compares the capability of different possible initial estimates to emulate the result that would be obtained by using the true model as an initial estimate.

The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used. %using the selected initial estimate.

%$\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{BTLS}$ are discussed later on.

The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
%\JL{in agreement with assumption \ref{assumption_G0hat_is_global_optimum}} \emph{viz}:
\begin{align}
\eta=\Prob{\hat G_\bullet=\hat G_0}
\end{align}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
\begin{align}\label{eq:successrateTol}
\eta=\Prob{ \norm{\hat G_\bullet-\hat G_0} < tol}
\end{align}
with $tol$ a numerical tolerance that will be specified later.

% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered. Note that it is not obvious to determine a tolerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate. On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
%\comment{\EG{it is implemented that way now}}
% }

%\begin{align}
%p(\hat G_x=\hat G_\circ) %G_0(q)= B(q)/A(q)
%\end{align}

The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
\begin{align}
\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \texttt{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

% !TEX root =  InitialValuesPaper.tex

\section{Demonstration}\label{se:Demo}

\subsection{The System Under Consideration}

Two systems are considered. The first, with a quality factor $Q = 6\unit{dB}$, has the transfer function
  \begin{equation}
     G_0(z) \Big|_{Q=6\unit{dB}}
    = 1.74 \cdot 10^{-3}
    \frac{ z^2 + 2 z + 1 }
         { z^2 - 1.93 z + 0.94}
    \label{eq:systemundertest}
    \text{.}
  \end{equation}
The second system, with a quality factor $Q = 20\unit{dB}$, has the transfer function
  \begin{equation}
    G_0(z) \Big|_{Q=20\unit{dB}}
    = 309 \cdot 10^{-6}
            \frac{z^2 + 2 z + 1}
                 {z^2 - 1.98 z + 0.989}
    \label{eq:systundertest-20dB}
    \text{.}
  \end{equation}

Both systems are low-pass Chebyshev filters shown in \figref{fig:exampleFRF}. Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed signal-to-noise ratio (SNR) defined as
\begin{equation}
  \mathrm{SNR} 
    = \frac{\sigma_v}
           {\rms{y_0}}
    \approx \frac{\sigma_{v}}
                 {\left\| G_0 \right\|_2 \rms{u_0}}
    =  \frac{\sigma_{v}}
            {\left\| G_0 \right\|_2}
  \label{eq:SNR-definition}
  \text{.}
\end{equation}
is attained.
$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
%}%}

%\JL{
%\subsection{Successful VS failed estimation}
\subsection{Comparison of Successful and Failed Estimates}

%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $G_0$, $\hat G_0$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
%}
%\EG{
 \figref{fig:exampleFRF} depicts the Bode plot of the actual system $G_0$, in black
%\comment{JL: in what color? (EG) black},
 and different estimates $\model{exist}$
 %\comment{JL: does it matter whether it is $\hat G_\mathrm{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
 that may or may not approximate $\hat{G}_{0}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
 The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, discussed later.

 It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
that their distances from the true system, given by $\|\hat G_\mathrm{\bullet} - G_0\|_2^2$, have small values. On the other hand, the `failed' estimates are inaccurate descriptions of the true system. It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.
   %Given the 2-norm \eqref{eq:successrateTol} employed 
   %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t. the relative error, except when $\abs{G_0(\omega)}$ is small.
 %Practically, 
 %In practice, this means that a successful estimate provides reasonable estimates of the pass-band of the system, but may perform poorly in the stop-band. \comment{Further discussion required: what about the absolute error? Isn't it more or less white over the complete frequency band?} \ML{To be discussed}

 Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $G_0(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}. 
 %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $G_0(\omega)$ over the broad frequency ranges.
 %Consequently, such estimates are practically worthless as an approximation of $G_0$.
 Consequently, such estimates are practically worthless approximations of $G_0$.
 %}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

%\subsection{Computing the success rates}
\subsection{Computation of  the Success Rates}\label{se:CompuSR}

\subsubsection{Simulation}
A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
\begin{itemize}
\item of SNR: 
              $-20   \unit{dB}$, 
              $-16.7 \unit{dB}$, 
              $-13.3 \unit{dB}$, 
              $-10   \unit{dB}$, 
              $- 7.8 \unit{dB}$, 
              $- 5.6 \unit{dB}$, 
              $- 3.3 \unit{dB}$, 
              $- 1.1 \unit{dB}$, 
              $  1.1 \unit{dB}$, 
              $  3.3 \unit{dB}$, 
              $  5.6 \unit{dB}$, 
              $  7.8 \unit{dB}$, 
              $ 10   \unit{dB}$, 
              $ 13.3 \unit{dB}$, 
              $ 16.7 \unit{dB}$ and
              $ 20   \unit{dB}$
\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
\end{itemize}
One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
For each value-pair (SNR, $N_{3\mathrm{dB}}$), 200 simulations and estimations were performed, for each of which the success (binary result) was determined. The success rate $\eta$ in equation \eqref{eq:successrateTol} was then estimated as the proportion of the successes from the 200 runs.%}

%\ML{
\subsubsection{Illustrative Example}
In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\snorm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
This effectively shows an empirical cumulative distribution function of the distance measure $\snorm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}

%\JL{One observes:}
\subsubsection{Pertinent Observations}
With reference to \figref{fig:single-sim}, the following observations are worth noting: 
%\EG{
\begin{itemize}
\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\hat{G}_{0}$.
Two major classifications can be made:
\begin{enumerate}
  \item `good' estimates which have $\|\model{\bullet} - \hat{G}_{0} \|_2 < tol \approx 6 \cdot 10^{-5}$,
  \item `poor' estimates which are much farther from $\hat{G}_{0}$.  This is caused by the local optima.
\end{enumerate}
\item
The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
This indicates $74\%$ success for the existing methods, $95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
\end{itemize}
%}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
  \label{fig:single-sim}
\end{figure}

%\subsection{Improvement w.r.t. existing techniques}%
\subsection{Improvement Over Existing Techniques}

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\cite{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\cite{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

By aggregating the results for the different simulations and retaining the success rate $\eta$ only, a clearer view of the performance of the different methods is obtained.

The success rates of $\hat G_\mathrm{exist}$, $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{RFIR}$ are depicted in  \figref{fig:successRateVS_SNR36N3dB} for two different numbers of sample points within the $3\unit{dB}$ bandwidth, and for a range of SNR values. A close scrutiny of  \figref{fig:successRateVS_SNR36N3dB} reveals the following observations: \begin{itemize}
\item The success rates increase with increasing SNR values, as expected.
\item For very low SNR values (below $0\unit{dB}$), $\hat G_\mathrm{exist}$ and $\hat G_\mathrm{trunc}$ are unreliable, whereas $\hat G_\mathrm{RFIR}$ is reliably successful. 
\item For relatively high SNR ($20\unit{dB}$), all three estimators perform equally well.
\item For moderate SNR values, the success rate of $\hat G_\mathrm{trunc}$ lies above that of $\hat G_\mathrm{exist}$.
\item The RFIR-based estimate exhibits a success rate of, at least, $97\%$ for all studied conditions. 
This clearly indicates that regularization makes it possible to obtain far more reliable initial estimates than both the LPM-Truncation-based ones and the existing ones. 
This is an important conclusion.
\end{itemize}
%}

%\JL{An important conclusion can be drawn from the last observation, in the range of the SNR where the success rate almost reaches 100\%. Namely, it tells us to what extent the estimator $\hat G_\mathrm{trunc}$ allows the SNR to be decreased before the estimator gets a too high fail rate. In other words, it shows that $\hat G_\mathrm{trunc}$ is more reliable at lower SNRs than $\hat G_\mathrm{existing}$.}
%\JL{
As far as $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{exist}$ are concerned, the observations on \figref{fig:successRateVS_SNR36N3dB} clearly reveal the extent to which the estimator $\hat G_\mathrm{trunc}$ allows for the SNR to be decreased before the estimator attains too high a fail rate. 
In other words, it shows that, at low SNR values $\hat G_\mathrm{trunc}$ is more reliable than $\hat G_\mathrm{exist}$.

%\comment{JL: do we have the numerical results to add a remark like: At an SNR of xdB, the respective success rates of $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{existing}$ are $90\%$ and $95\%$. This means that, for that SNR, chances of failure have been reduced by a factor of 2!
%}
%\ML{Yea, shown below!}
%\EG{
  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ SNR, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
However, by using the truncated LPM's initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
Moreover, the RFIR initial values lead to poor estimates in less than $2\%$ ($>$ $98\%$ success rate) of the cases, since none were observed in the Monte Carlo simulation.

\paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
A close scrutiny of \figref{fig:successRateVS_SNR36N3dB} reveals that the SNR range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$. The range of improvement is approximately 5 dB where the success rate is above $90\%$. This result is very useful for a user working with noisy data.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/successRates.tikz}
 \caption{The success rate $\eta$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of SNRs, number of samples and for both test systems. The $95\%$ confidence intervals are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption{The accordance between the observed RMSE of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
 In the bottom plot, the difference $\Delta$ between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\hat{G}_0$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

\paragraph*{Remark about the model quality}
In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\hat{G}_{0}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\hat{G}_{0}$ itself might be ill-suited.
A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
In~\cite{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
In this context this heuristic boils down to: 
\begin{equation}
    \RMSE(\hat{G}_{0}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{G_0}}{\SNR} 
    \label{eq:heur-RMSE}
\end{equation}
where $n_{\theta}=5$ is the number of estimated parameters in this paper.
In \figref{fig:RMSE}, the empirical $\RMSE(\hat{G}_{0})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
When the RMSE is then divided by $\norm{G_0}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.

\section{Experimental Results}
\label{se:ExpMeas}
Measurements were performed on an electrical filter to assess the performance of the initial value generating methods in a physical setting.

\subsection{Experimental Setup}
The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\cite{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.

\begin{figure}
  \centering
  \includegraphics[width=0.8\onecolumnwidth]{\thisDir/fig/measurement.pdf}
  \caption{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \texttt{AO} and \texttt{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the inverse DFT.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
%  \input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
  \caption{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

\subsection{Identification Procedure}
The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
The mean signal from the input $u$ is of the form:
\begin{equation}
  \tilde{u}(t) = \frac{1}{N_R} \sum_{r=1}^{N_R} u^{[r]}(t)
\end{equation}
Thus, the reduced noise influence and the approximate noise co-variances are, respectively:
\begin{align}
  \hat\sigma_{u}^2(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( u^{[r]}(t) - \tilde{u}(t) \right)^2 \\
%and the noise co-variances are approximately
  \hat\sigma_{yu}(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( y^{[r]}(t) - \tilde{y}(t) \right)
                    \overline{\left( u^{[r]}(t) - \tilde{u}(t) \right)}
  \label{eq:variancePeriodic}            
\end{align}

Similar calculations apply to $y(t)$ and as such, $\hat\sigma_u(t)$, $\hat\sigma_y(t)$ and $\hat\sigma_{yu}(t)$ can be estimated.
Their frequency domain counterparts $\tilde{U}(\omega)$ and $\tilde{Y}(\omega)$ are obtained by using the DFT.
The resulting empirical transfer function estimate $Y^{[r]}(\omega)/U^{[r]}(\omega)$ and its periodic average $\tilde{Y}/\tilde{U}$ are shown in \figref{fig:bk1613}.
The noise covariances $\hat\sigma^2_{U}(\omega)$, $\hat\sigma^2_{Y}(\omega)$ and  $\hat\sigma_{YU}(\omega)$ are calculated as the sample covariance, akin to equation \eqref{eq:variancePeriodic}, and their values are shown in \figref{fig:SpectraMeasurement}.
Note that the SNR at the output $\mathrm{SNR}_{y} \approx 14 \unit{dB}$ is much smaller than at the input $\mathrm{SNR}_{u} \approx 50 \unit{dB}$.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  \caption{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

For each measurement repetition, the signals $u^{[r]}(t)$, $y^{[r]}(t)$ and the variances $\sigma_U^2(\omega)$, $\sigma_Y^2(\omega)$ are used in the maximum likelihood cost function given by equation \eqref{eq:MLEcf}.
The model chosen for the cost function comprises a numerator of third order, a denominator of sixth order and transient contribution of a fifth degree. This results in a transfer function of the form:
\begin{equation}
  \model{\bullet}(s,\theta) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
\end{equation}
which is typical of a sixth-order band-pass filter.
By processing the different repetitions, a parametric fit per initialization method corresponding to the appropriate branch in \figref{fig:flowgraph}, and per repetition can be obtained.

The following equation is constructed from the final estimates for each experiment; it gives an insight into the combined contribution to the `best' estimate from all the different initialization strategies, \emph{viz}:

\begin{equation}\label{eq:selectBest}
  \model{best} = 
    \Arg_{\hat{G}} 
    \min 
    \left\{ 
      V(\model{exist}),
      V(\model{trunc}),
      V(\model{RFIR})
    \right\}
\end{equation}
where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
This is also the approach followed in~\cite{FDIDENT} to combine different initial estimates.

\subsection{Reference Model Measurements}

%\JL{
Since the true model $G_0$ is not known for real-life systems, a practically viable reference model is needed.
Additional measurements were performed using a VXI measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\mathrm{VXI}$, and used as a reference model. 
The VXI measurement setup is summarized as follows.
\begin{itemize}
  \item Signal Generator card: VXI HP E1445A.
  \item Acquisition cards: VXI HP E1430A.
  \item Sampling frequency: $f_\mathrm{s} = 156\,250 \unit{Hz}$.
  \item A total of $558$ frequency bins were used for the estimation, in the excited frequency band $[0.1,20] \unit{kHz}$, with a frequency resolution of $35.7\unit{Hz}$, giving a measurement time of $28\unit{ms}$. The excitation signal was band-limited periodic noise with an RMS of $100\unit{mV}$.
  \item The input and output signals were buffered and anti-alias filtered.
\end{itemize}
This yielded the model $G_\mathrm{VXI}$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.  Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\mathrm{VXI}}$ as an initial estimate. Furthermore, $G_\mathrm{VXI}$ was used to play the role of $G_0$ from the previous section.

\subsection{Model Estimation}
  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
  The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
  The truncation method provides better estimates in many cases, but still suffers from a high variability.
  On the other hand, the RFIR-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
  Obviously, $\model{best}$ has the lowest cost function values of all methods.
  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the RFIR provides the best estimate in most of the cases.
  This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.

\begin{remark}
  In the simulations (e.g. \figref{fig:single-sim}), a $60\unit{dB}$ difference between `good' and `bad' estimates was observed.
  Such a large gap is not observed in the measurements (\figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}).
  Hence, defining a success rate based on a threshold tolerance would be very sensitive to the specific value of the threshold and hence unreliable.
  Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
  Practically, the median is used as a measure of location and the inter-quartile range (IQR) is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
  These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
  On the other hand, the IQR ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
\end{remark}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

\begin{table}
  \centering
  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
\input{\thisDir/table1.tex}
% \pgfplotstabletypeset[precision=0,outfile=table1.tex]{
% method            P000     P025     P050      P075       P100   
% \model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
% \model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
% \model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
% \model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
% \model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
% }
  \label{tbl:costMeasurements}
\end{table}

\subsection{Model Validation}
\subsubsection{Cost function limitations}
In the previous section, the cost function was studied to determine the effectiveness of the starting values.
However, inspecting the cost function $V(\theta)$ only accounts for how well an estimated model fits the measured data, which may be misleading.
For an example, overfitting a model may result in the absorption of both the systematic behavior and the noise into the model. 
Consequently, an arbitrarily small cost function may ensue although the estimated model may be virtually useless to predict the system behavior.

\subsubsection{Validation criterion}
To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
To this end, the model is validated using the 2-norm (or distance) on the model error:
\begin{equation}
  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
  \text{.}
  \label{eq:measurementCriterion}
\end{equation} 
This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the VXI.

\subsubsection{Validation performance}
The observed median and IQR of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
The existing methods provide good estimates in only $25\%$ of the cases.
The truncation method provides a considerable improvement but still suffers from $25\%$ poor estimates.
Compared to the existing BTLS and GTLS techniques, the RFIR and hence also $\model{best}$ entail an overall reduction in the observed distance by a factor $8$, in most cases. 
On the other hand, the reference $\model{VXI}$ shows the best global performance. 
This indicates that the proposed methods do no converge to the same local optimum.
Nevertheless, the proposed methods improve the model quality by almost an order of magnitude.

As the criterion in equation~\eqref{eq:measurementCriterion} no longer depends on the cost function, the initial estimates can also be investigated.
The difference between the distance of $\model[init]{\bullet}$ and $\model{\bullet}$ indicates how much the final ML estimate from the raw data, in each respective branch of \figref{fig:flowgraph}, improves over the initial estimate.
Remarkably, on average, the final ML estimation provides only a marginal improvement for the RFIR. 
However, this final step reduces the spread and hence yields a more reliable estimate.
E.g. note in \tabref{tbl:validationMeasurements} that this step reduces the worst-case distance from $18.21$ to $4.55$.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
\input{\thisDir/table2.tex}

% \pgfplotstabletypeset[precision=2,zerofill=true,outfile=table2.tex]{
% method              P000      P025      P050        P075     P100   
% \model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
% \model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
% \model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
% \model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
% \model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
% \model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
% \model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
% }
\label{tbl:validationMeasurements}
\end{table}

\section{Remark on Generality}
\label{se:Generality}
In the previous sections, the usefulness of smoothing techniques to obtain initial values has been illustrated on example systems.
Other systems, e.g. discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} commands in \MATLAB{} have also been tried.

No cases were observed where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.

The usefulness of particular initial estimates, e.g. $\model[init]{RFIR}$ is obviously linked to the appropriateness of the non-parametric smoother in the experimental conditions at hand.
However, it is beyond the scope of this paper to determine which particular smoother is optimal in some specific circumstance.

\section{Conclusion}\label{se:Conclusion}
The simulations have demonstrated that use of a smoothed non-parametric estimate of the FRF can improve the success rate of minimizing the ML cost function for the estimation of the transfer functions of linear time-invariant (LTI) systems, subjected to noisy signals. Specifically, two smoothing methods were used and compared: 1) the truncated LPM method, and 2) the RFIR method. The simulation results clearly show that the RFIR method is superior to the truncated LPM method and the existing BTLS/GTLS methods.

The usefulness of the initial values obtained via the proposed smoothing techniques was confirmed on a measurement of a band-pass filter in a noisy environment.
In most cases, the proposed initial values in the example made it possible to reduce the cost function by a factor two compared to existing methods.
Moreover, the obtained models were validated against a high-quality measurement where the RMS error on the transfer function could be reduced by a factor of eight for most cases, due to the improved initial values.

Thus, the work in this paper has demonstrated the effectiveness of the studied FRF smoothing techniques in enhancing the initial values.
Consequently, the ease-of-use of parametric model fitting is increased considerably by making it possible to obtain good parametric models without requiring any user interaction.

% \bibliographystyle{IEEEtran}
% \bibliography{InitEstBib}
% \end{document}

### 2015-10-28 ch05-initvals/styles.inc.tex
Include initial values
Also quite a bit of pgfplots external trickery/hackery
to make sure the file compiles.

\pgfplotsset{compat=newest}
\pgfplotsset{tick style={black!30},grid style={black!10}}
\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
\pgfplotsset{every axis label/.append style={font=\footnotesize}}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}
\pgfplotsset{every axis title/.append style={font=\footnotesize}}
\pgfplotsset{every axis post/.style={unbounded coords=jump}}
\pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}

\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
\definecolor{RFIR}{named}{TangoScarletRed3}
\definecolor{RFIRInit}{named}{TangoScarletRed1}
\definecolor{existing}{named}{TangoChameleon3}
\definecolor{G0Hat}{named}{TangoOrange2}
\definecolor{GVXI}{named}{G0Hat}
\definecolor{reference}{named}{black}

\definecolor{heuristic}{named}{TangoPlum2}
\definecolor{observed}{named}{TangoOrange3}

\definecolor{best}{named}{TangoAluminium6}

\definecolor{G0HatFill}{named}{TangoOrange1}
\definecolor{GVXIFill}{named}{G0HatFill}
\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
\definecolor{RFIRFill}{named}{TangoScarletRed1}
\definecolor{existingFill}{named}{TangoChameleon1}
\definecolor{bestFill}{named}{TangoAluminium3}

\definecolor{FRFMean}{named}{TangoPlum3}
\definecolor{FRFSingle}{named}{TangoPlum1}
\definecolor{FRFNoise}{named}{TangoChocolate1}

\pgfplotsset{FRFMean/.style={color=FRFMean,mark=*,mark options={solid},only marks,medsmallmarkers}}
\pgfplotsset{FRFSingle/.style={color=FRFSingle,mark=square*,mark options={solid},only marks,smallmarkers}}
\pgfplotsset{FRFNoise/.style={color=FRFNoise,mark=x,mark options={solid},only marks,smallmarkers}}

\pgfset{number format/1000 sep={\,}}

\pgfplotsset{bandwidth/.style={area style,fill=TangoButter1,draw=TangoButter2,fill opacity=0.5}}
\pgfplotsset{goodestimate/.style={color=TangoChameleon2,line join=round}}
\pgfplotsset{badestimate/.style={color=TangoScarletRed2,solid,line join=round}}
\pgfplotsset{exact/.style={color=black,dashed,line width=0.75pt,line join=round}}

\pgfplotsset{LPMTruncmark/.append style={mark=*,mark options={solid}}}
\pgfplotsset{RFIRmark/.append style={mark=square*,mark options={solid}}}
\pgfplotsset{existingmark/.append style={mark=triangle*,mark options={solid}}}
\pgfplotsset{existingInitmark/.append style={mark=triangle,mark options={solid}}}
\pgfplotsset{LPMTruncInitmark/.append style={mark=o,mark options={solid}}}
\pgfplotsset{RFIRInitmark/.append style={mark=square,mark options={solid}}}
\pgfplotsset{bestmark/.append style={mark=diamond*,mark options={solid}}}
\pgfplotsset{G0Hatmark/.append style={mark=asterisk,mark options={solid}}}

\pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
\pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
\pgfplotsset{existing/.style={color=existing}}
\pgfplotsset{LPMTruncInit/.style={color=LPMTruncInit,densely dashed}}
\pgfplotsset{LPMTrunc/.style={color=LPMTrunc}}
\pgfplotsset{RFIRInit/.style={color=RFIRInit,densely dashed}}
\pgfplotsset{RFIR/.style={color=RFIR}}
\pgfplotsset{best/.style={color=best}}

\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}

\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}

### 2015-10-28 config/styles.inc.tex
Include initial values
Also quite a bit of pgfplots external trickery/hackery
to make sure the file compiles.

--- 2015-10-25 ch02-qlogms/grids.inc.tex
@@
+\pgfplotsset{compat=newest}
+
+\def\thisDir{.}
+
+\pgfplotsset{tick style={black!30},grid style={black!10}}
+\pgfplotsset{every axis legend/.append style={font=\footnotesize}}
+\pgfplotsset{every axis label/.append style={font=\footnotesize}}
+\pgfplotsset{every tick label/.append style={font=\footnotesize}}
+\pgfplotsset{every axis title/.append style={font=\footnotesize}}
+\pgfplotsset{every axis post/.style={unbounded coords=jump}}
+\pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}
+
 %% Colors
@@
 \pgfplotsset{linrect/.style={fill=linms,draw=linms,line width=1pt}}
+
+\definecolor{model}{named}{blue}
+\definecolor{truesys}{named}{TangoAluminium5}
+
+\definecolor{linms}{named}{TangoScarletRed3}
+\definecolor{logms}{named}{TangoChameleon2}
+\definecolor{qlogms}{named}{TangoPlum3}
+\definecolor{clogms}{named}{TangoSkyBlue3}
+\definecolor{plogms}{named}{black}
+
+\definecolor{sigmalinms}{named}{linms}
+\definecolor{sigmaqlogms}{named}{qlogms}
+\definecolor{sigmaclogms}{named}{clogms}
+
+\definecolor{biaslinms}{named}{TangoScarletRed1}
+\definecolor{biasqlogms}{named}{TangoPlum1}
+\definecolor{biasclogms}{named}{TangoSkyBlue1}
+
+\definecolor{dbacolor}{named}{TangoScarletRed2}
+\definecolor{dbbcolor}{named}{TangoSkyBlue2}
+\definecolor{dbccolor}{named}{TangoChameleon2}
+\definecolor{dbdcolor}{named}{TangoOrange2}
+
+\pgfplotsset{linmsgrid/.style={ycomb,color=linms,solid,line width=0.7pt,mark size=1pt,mark=square*,mark options={solid}}}
+\pgfplotsset{logmsgrid/.style={ycomb,color=logms,solid,line width=0.7pt,mark size=1pt,mark=*,mark options={solid}}}
+\pgfplotsset{clogmsgrid/.style={ycomb,color=clogms,solid,line width=0.7pt,mark size=2pt,mark=x,mark options={solid}}}
+\pgfplotsset{plogmsgrid/.style={ycomb,color=plogms,solid,line width=0.7pt,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}
+
+\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
+\pgfplotsset{truesys/.style={color=truesys,line width=1.0pt}}
+
+\newcommand{\linmsmarker}{mark=square,mark options={solid}}
+\newcommand{\qlogmsmarker}{mark=triangle,mark options={solid}}
+\newcommand{\clogmsmarker}{mark=x,mark size=10pt,mark options={solid}}
+
+\newcommand{\dbamarker}{mark=x       ,mark options={solid}}
+\newcommand{\dbbmarker}{mark=o       ,mark options={solid}}
+\newcommand{\dbcmarker}{mark=square  ,mark options={solid}}
+\newcommand{\dbdmarker}{mark=triangle,mark options={solid}}
+
+\pgfplotsset{sigmalinms/.append style={color=sigmalinms,solid,line width=0.8pt}}
+\pgfplotsset{sigmaqlogms/.append style={color=sigmaqlogms,solid,line width=0.8pt}}
+\pgfplotsset{sigmaclogms/.append style={color=sigmaclogms,solid,line width=0.8pt}}
+
+\pgfplotsset{biaslinms/.style={color=biaslinms,only marks,mark=x,mark options={solid}}}
+\pgfplotsset{biasqlogms/.style={color=biasqlogms,only marks,mark=triangle,mark options={solid,rotate=180}}}
+\pgfplotsset{biasclogms/.style={color=biasclogms,only marks,mark=o,mark options={solid}}}
+
+\pgfplotsset{linms/.style={color=linms,solid,line width=0.5pt}}
+\pgfplotsset{qlogms/.style={color=qlogms,solid,line width=0.5pt}}
+\pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}
+
+\pgfplotsset{linmsconnect/.style={color=linms,%
+                                  solid,
+                                  line width=1pt,
+                                  mark=square*,
+                                  mark size=1pt,
+                                  mark options={solid}}}
+\pgfplotsset{qlogmsconnect/.style={color=qlogms,%
+                                  solid,
+                                  line width=1pt,%
+                                  mark=*,%
+                                  mark size=1pt,
+                                  mark options={solid}}}
+\pgfplotsset{clogmsconnect/.style={color=clogms,%
+                                   solid,
+                                   line width=1pt,%
+                                   mark=x,%
+                                   mark size=1pt,
+                                   mark options={solid}}}
+
+\pgfplotsset{dbavar/.style={color=dbacolor,solid,line width=1.0pt}}
+\pgfplotsset{dbbvar/.style={color=dbbcolor,solid,line width=1.0pt}}
+\pgfplotsset{dbcvar/.style={color=dbccolor,solid,line width=1.0pt}}
+\pgfplotsset{dbdvar/.style={color=dbdcolor,solid,line width=1.0pt}}
+
+\pgfplotsset{dbamin/.style={color=dbacolor,dashed,line width=1.0pt}}
+\pgfplotsset{dbbmin/.style={color=dbbcolor,dashed,line width=1.0pt}}
+\pgfplotsset{dbcmin/.style={color=dbccolor,dashed,line width=1.0pt}}
+\pgfplotsset{dbdmin/.style={color=dbdcolor,dashed,line width=1.0pt}}
+
+\pgfplotsset{dbamax/.style={color=dbacolor,solid,line width=1.0pt,mark=x ,mark options={solid}}}
+\pgfplotsset{dbbmax/.style={color=dbbcolor,solid,line width=1.0pt,mark=o ,mark options={solid}}}
+\pgfplotsset{dbcmax/.style={color=dbccolor,solid,line width=1.0pt,mark=square  ,mark options={solid}}}
+\pgfplotsset{dbdmax/.style={color=dbdcolor,solid,line width=1.0pt,mark=triangle,mark options={solid}}}
+
+\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
+\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
+\definecolor{RFIR}{named}{TangoScarletRed3}
+\definecolor{RFIRInit}{named}{TangoScarletRed1}
+\definecolor{existing}{named}{TangoChameleon3}
+\definecolor{G0Hat}{named}{TangoOrange2}
+\definecolor{GVXI}{named}{G0Hat}
+\definecolor{reference}{named}{black}
+
+\definecolor{heuristic}{named}{TangoPlum2}
+\definecolor{observed}{named}{TangoOrange3}
+
+\definecolor{best}{named}{TangoAluminium6}
+
+\definecolor{G0HatFill}{named}{TangoOrange1}
+\definecolor{GVXIFill}{named}{G0HatFill}
+\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
+\definecolor{RFIRFill}{named}{TangoScarletRed1}
+\definecolor{existingFill}{named}{TangoChameleon1}
+\definecolor{bestFill}{named}{TangoAluminium3}
+
+\definecolor{FRFMean}{named}{TangoPlum3}
+\definecolor{FRFSingle}{named}{TangoPlum1}
+\definecolor{FRFNoise}{named}{TangoChocolate1}
+
+\pgfplotsset{FRFMean/.style={color=FRFMean,mark=*,mark options={solid},only marks,medsmallmarkers}}
+\pgfplotsset{FRFSingle/.style={color=FRFSingle,mark=square*,mark options={solid},only marks,smallmarkers}}
+\pgfplotsset{FRFNoise/.style={color=FRFNoise,mark=x,mark options={solid},only marks,smallmarkers}}
+
+\pgfset{number format/1000 sep={\,}}
+
+\pgfplotsset{bandwidth/.style={area style,fill=TangoButter1,draw=TangoButter2,fill opacity=0.5}}
+\pgfplotsset{goodestimate/.style={color=TangoChameleon2,line join=round}}
+\pgfplotsset{badestimate/.style={color=TangoScarletRed2,solid,line join=round}}
+\pgfplotsset{exact/.style={color=black,dashed,line width=0.75pt,line join=round}}
+
+\pgfplotsset{LPMTruncmark/.append style={mark=*,mark options={solid}}}
+\pgfplotsset{RFIRmark/.append style={mark=square*,mark options={solid}}}
+\pgfplotsset{existingmark/.append style={mark=triangle*,mark options={solid}}}
+\pgfplotsset{existingInitmark/.append style={mark=triangle,mark options={solid}}}
+\pgfplotsset{LPMTruncInitmark/.append style={mark=o,mark options={solid}}}
+\pgfplotsset{RFIRInitmark/.append style={mark=square,mark options={solid}}}
+\pgfplotsset{bestmark/.append style={mark=diamond*,mark options={solid}}}
+\pgfplotsset{G0Hatmark/.append style={mark=asterisk,mark options={solid}}}
+
+\pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
+\pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
+\pgfplotsset{existing/.style={color=existing}}
+\pgfplotsset{LPMTruncInit/.style={color=LPMTruncInit,densely dashed}}
+\pgfplotsset{LPMTrunc/.style={color=LPMTrunc}}
+\pgfplotsset{RFIRInit/.style={color=RFIRInit,densely dashed}}
+\pgfplotsset{RFIR/.style={color=RFIR}}
+\pgfplotsset{best/.style={color=best}}
+
+\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
+\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
+\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
+\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}
+
+\tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}
+
+%% TABLE STYLES
+
+\pgfplotstableset{
+	%zerofill=true,
+	after row=[3pt],
+	assign column name/.code={%
+        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
+    },
+	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
+	columns/contribution/.style={column name={\textsc{Contribution}}},
+	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
+	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
+	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
+	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
+	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
+	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
+	postproc cell content/.append code={
+            %\ifnum1=\pgfplotstablepartno
+                \pgfkeysalso{@cell content/.add={}{\%}}%
+            %\fi
+        },
+	},
+	every head row/.style={before row=\toprule, after row={\\\midrule}},
+    every last row/.style={after row=\bottomrule}
+}

### 2015-10-28 ch05-initvals/InitialValuesPaper.tex
More outline added

@@
 
+\TODO{import references into main bibliography}
 %\comment{JL: 
@@
 %\begin{itemize}
-%\item demonstrate that a smoothed FRF, obtained as described in \cite{Lumori2014}, used as an initial estimate increases the success rate of a parametric LTI TF identification
+%\item demonstrate that a smoothed FRF, obtained as described in \citep{Lumori2014}, used as an initial estimate increases the success rate of a parametric LTI TF identification
 %\item
@@
 The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
-Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723}.
-Application of these methods to real devices and systems is well-known in published literature, including \cite{Lim2010,Robinson1990,Behjat2010}.
+Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,Guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni20071723}.
+Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.
 
-Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\cite{FDidentEd2Pintelon,Ljung1999,schoukens1999,pintGuil1998}.
+Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,schoukens1999,pintGuil1998}.
  Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
@@
 
-In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\cite{Lumori2014} and the regularized finite-impulse response (RFIR)~\cite{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
+In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\citep{Lumori2014} and the regularized finite-impulse response (RFIR)~\citep{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
 These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
@@
 Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this paper.
-However, the generalization to continuous time is straightforward~\cite[Chapter 6]{FDidentEd2Pintelon} and has been demonstrated in Section~\ref{se:ExpMeas}.
+However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
 
@@
 \input{\thisDir/fig/oesetup.tikz}
-\caption{SISO LTI discrete-time system in an output error setup.}
+\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
 \label{fig:oesetup}
@@
 
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
+Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
 
@@
 
-From~\cite[Section 6.3.2.]{FDidentEd2Pintelon}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
+From~\citep[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
 \begin{align}
@@
 \end{equation}
-Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\cite[Section 9.11]{FDidentEd2Pintelon}:
+Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
 \begin{equation}\label{eq:MLEcf}
@@
 Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
-The Levenberg-Marquardt~\cite{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
+The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
 Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this paper.
@@
 \begin{algorithm}
-\caption{Levenberg-Marquardt~\cite{Marquardt1963}, \cite[Sec. 9.L.4]{FDidentEd2Pintelon}}\label{LMalgo}
+\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
 \begin{algorithmic}[1]
@@
 \begin{remark}
-Alternatively, stochastic optimization algorithms~\cite{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
+Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
 This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
@@
   [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
-  \caption{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
   The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
@@
 
-%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}.
+%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
 These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$.
@@
 
-The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}.
+The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
 These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
@@
 
-A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \cite{Lumori2014}.
+A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \citep{Lumori2014}.
 Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
@@
 
-  With reference to a detailed discussion in~\cite{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+  With reference to a detailed discussion in~\citep{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
 \begin{subequations}\label{lpmImplQuadG}
@@
 %\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
-The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\cite{Lumori2014}.
+The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014}.
 %\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.
@@
 By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
-This can lead to a significant improvement over the classical LPM~\cite{Lumori2014}.
+This can lead to a significant improvement over the classical LPM~\citep{Lumori2014}.
 
@@
 More information about the RFIR estimator can be found in
-~\cite{Pillonetto201081,Chen20121525}. 
+~\citep{Pillonetto201081,Chen20121525}. 
 The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
@@
  % \caption{Results of an example of Monte Carlo simulation.}
- \caption{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
+ \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
  Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
@@
   \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
- \caption{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
+ \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
  The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
@@
 In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-The confidence intervals are calculated via the Clopper-Pearson method~\cite{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
-This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\cite{Ross2003}.
+The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
+This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
 Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.
@@
   \input{\thisDir/fig/successRates.tikz}
- \caption{The success rate $\eta$  obtained using the smoothers, i.e.
+ \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\eta$  obtained using the smoothers, i.e.
 $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of SNRs, number of samples and for both test systems.
@@
   \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption{The accordance between the observed RMSE of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
+ \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed RMSE of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
  In the bottom plot, the difference $\Delta$ between both is shown.
@@
 A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
-In~\cite{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
+In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
 In this context this heuristic boils down to: 
@@
 \subsection{Experimental Setup}
-The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\cite{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.
+The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\citep{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.
 
@@
   \includegraphics[width=0.8\onecolumnwidth]{\thisDir/fig/measurement.pdf}
-  \caption{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
+  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
 The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized.
@@
 %  \input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
-  \caption{Transfer function of the considered \BK{} 1613 filter.
+  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
   The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
@@
   \input{\thisDir/fig/elvis-spectra.tikz}
-  \caption{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
+  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
   \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
@@
 where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
-This is also the approach followed in~\cite{FDIDENT} to combine different initial estimates.
+This is also the approach followed in~\citep{FDIDENT} to combine different initial estimates.
 
@@
   \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
-  \caption{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
+  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
   The bottom plot shows a zoom of the top plot.
@@
   \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
-\input{\thisDir/table1.tex}
-% \pgfplotstabletypeset[precision=0,outfile=table1.tex]{
-% method            P000     P025     P050      P075       P100   
-% \model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
-% \model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
-% \model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
-% \model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
-% \model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
-% }
+% \input{\thisDir/table1.tex}
+\pgfplotstabletypeset[precision=0]{
+method            P000     P025     P050      P075       P100   
+\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
+\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
+\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
+\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
+\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
+}
   \label{tbl:costMeasurements}
@@
   \input{\thisDir/fig/meas-validation.tikz}
-  \caption{Validation of the measured models. 
+  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
   For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
@@
   \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
-\input{\thisDir/table2.tex}
+% \input{\thisDir/table2.tex}
 
-% \pgfplotstabletypeset[precision=2,zerofill=true,outfile=table2.tex]{
-% method              P000      P025      P050        P075     P100   
-% \model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
-% \model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
-% \model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
-% \model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
-% \model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
-% \model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
-% \model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
-% }
+\pgfplotstabletypeset[precision=2,zerofill=true]{
+method              P000      P025      P050        P075     P100   
+\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
+\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
+\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
+\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
+\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
+\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
+\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
+}
 \label{tbl:validationMeasurements}

### 2015-10-29 ch02-qlogms/logMS_IMTC.tex
More outline added
Set up glossaries

@@
 \section{Introduction} \label{sec:intro}
-  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
+  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
   Of course, we also want to attain a specified uncertainty level over the full frequency span.
@@
   \end{figure}
+
+  \begin{table}
+  \centering
+   \caption{Summary of the different frequency grids.}
+    \begin{tabular}{lccc} 
+    Grid & Linear & Logarithmic & Quasi-logarithmic \\
+
+    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
+    Parameters & $f_0, \Delta f$ & $f_0, \alpha$ & $f_0, \Delta f, \alpha$ \\
+    $f_{k+1} \isdef$ & $f_{k} + \Delta f$ & $f_{k} \cdot \alpha$ & \ldots \\
+
+    \end{tabular}
+    \TODO{afmaken, booktabs}
+  \end{table}
 

### 2015-10-29 config/glossaries.inc.tex
Set up glossaries

\usepackage[sanitize={symbol=false},toc,acronym,section=section,nonumberlist,xindy]{glossaries}

\renewcommand*{\acronymname}{List of Abbreviations}
\renewcommand*{\glssymbolsgroupname}{List of Symbols}

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#3\protect\footnote{#3: #4}},
plural={#3\glspluralsuffix},
firstplural={#3\glspluralsuffix\protect\footnote{#3: #4}},
#1}}

\newglossary[slg]{symbols}{sls}{slo}{\glssymbolsgroupname}
%\newglossary{symbols}{sym}{sbl}{List of Symbols}
\newcommand{\newsymbolglos}[3]{\newglossaryentry{#1}{type=symbols,%
                                 name={\ensuremath{#2}},sort={#1}%
                               symbol={\ensuremath{#2}},description={#3}}}
\newcommand{\sym}[1]{\glssymbol{#1}}

%% TERMS

%% SYMBOLS
\newsymbolglos{approx}{\approx}{Approximately equal}
\newsymbolglos{bydef}{\isdef}{Equal by definition}
\newsymbolglos{imagunit}{j}{The imaginary unit $j = \sqrt{-1}$}
\newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
\newsymbolglos{SetC}{\mathbb{C}}{Set of the complex numbers}
\newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\text{rad}/\text{s}$}
\newsymbolglos{f}{f}{Frequency in $\text{Hz}$}

%% ACRONYMS
\newacronym{vub}{VUB}{Vrije Universiteit Brussel}

\newacronym{siso}{SISO}{Single Input Single Output}
\newacronym{mimo}{MIMO}{Multiple Input Multiple Output}
\newacronym{bla}{BLA}{Best Linear Approximation}
\newacronym{frf}{FRF}{Frequency Response Function}
\newacronym{dut}{DUT}{Device Under Test}

\newacronym{FRF}{FRF}{frequency response function}
\newacronym{LTI}{LTI}{Linear time-invariant}

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LRIC}{LRIC}{Local Rational Method with Iterative Costfunction}

\newacronym{dft}{DFT}{Discrete Fourier Transform}
\newacronym{fft}{FFT}{Fast Fourier Transform}

\makeglossaries

### 2015-10-29 front-and-back-matter/frontmatter.tex
Include VC bundle for git/unix
Some formatting
Some small changes
Some TODOs in QLogMS
Use tikz external
Add title page, some bib changes
Set up glossaries

@@
-\maketitle
+\input{front-and-back-matter/summary.inc.tex}
+\input{front-and-back-matter/acknowledgements.inc.tex}
 
+\cleardoublepage
+\addcontentsline{toc}{chapter}{Contents}
 \tableofcontents
-%TODO: make sure all these appear in TOC
-%TODO: \listoffigures
-%TODO: \listoftables
-%TODO: list of symbols
-%TODO: list of acronyms
+\clearpage
+
+\KOMAoption{listof}{leveldown,totoc}
+
+\listoffigures
+\listoftables
+% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this
+
+\printglossary[type=\acronymtype,style=long,toctitle={Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
+\glsaddall[types=symbols]
+\printglossary[type=symbols,style=altlong4col,toctitle={List of Symbols}]
+
 \newpage

### 2015-10-29 config/glossaries.inc.tex
Update glossary a bit

@@
 \newsymbolglos{bydef}{\isdef}{Equal by definition}
-\newsymbolglos{imagunit}{j}{The imaginary unit $j = \sqrt{-1}$}
+\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
 \newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
@@
 \newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
-\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\text{rad}/\text{s}$}
-\newsymbolglos{f}{f}{Frequency in $\text{Hz}$}
+\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\unit{rad/s}$}
+\newsymbolglos{f}{f}{Frequency in $\unit{Hz}$}
 
 %% ACRONYMS
-\newacronym{vub}{VUB}{Vrije Universiteit Brussel}
+\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
 
-\newacronym{siso}{SISO}{Single Input Single Output}
-\newacronym{mimo}{MIMO}{Multiple Input Multiple Output}
-\newacronym{bla}{BLA}{Best Linear Approximation}
-\newacronym{frf}{FRF}{Frequency Response Function}
-\newacronym{dut}{DUT}{Device Under Test}
+\newacronym{iid}{i.i.d.}{independent and identically distributed}
+\newacronym{SISO}{SISO}{Single Input Single Output}
+\newacronym{MIMO}{MIMO}{Multiple Input Multiple Output}
+\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
+\newacronym{MISO}{MISO}{Multiple Input Single Output}
+\newacronym{BLA}{BLA}{Best Linear Approximation}
+\newacronym{DUT}{DUT}{Device Under Test}
 
@@
 \newacronym{LTI}{LTI}{Linear time-invariant}
+\newacronym{ETFE}{ETFE}{Empirical Transfer Function Estimate}
 
@@
 \newacronym{LRM}{LRM}{Local Rational Method}
-\newacronym{LRIC}{LRIC}{Local Rational Method with Iterative Costfunction}
+\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
 
-\newacronym{dft}{DFT}{Discrete Fourier Transform}
-\newacronym{fft}{FFT}{Fast Fourier Transform}
+\newacronym{DFT}{DFT}{Discrete Fourier Transform}
+\newacronym{FFT}{FFT}{Fast Fourier Transform}
 

### 2015-11-01 ch02-qlogms/logMS_IMTC.tex
Import SYSID2012 paper

@@
 \TODO{rename labels}
-\TODO{import specific bib items}
 % \begin{abstract}
@@
   \end{equation}
+\TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
+\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter.
+This will be well-approximated by considering only the second order system of the paper.}
+
   The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
@@
 \subsection{Multisine Excitations}
-  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ commensurate frequency components:
+  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ frequency components:
   \begin{equation}
@@
   For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
+  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.
+
+  Consequently, the complete multisine has a period of
+  \begin{equation}
+    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
+      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
+    \text{,}
+  \end{equation}
+  where the least common (integer) multiple of the real values $T_k$ is defined as
+  \begin{equation}
+    \lcm \set{T_1, \ldots, T_F} \isdef
+      \min \set{T \given{\forall i \in \set{1,\ldots,F}, \exists n_i \in \NaturalNumbers: n_i T_i = T }}
+      \text{.}
+   \end{equation}
+  Note that this minimum doesn't always exist (e.g. when $f_1 = 1 \unit{Hz}$ and $f_F = \pi \unit{Hz}$), in such cases the multisine is aperiodic.
 
@@
 
-  Each decade within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains the same number of frequency components such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+  Each decade that is completely  within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains
+   \begin{equation}
+     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
+         = \floor{\log_{\alpha} 10}
+   \end{equation}
+   excited frequency lines. 
+   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).
 
-  To return to the FRF, in Section \ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
+  To return to the FRF, in Section~\ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
   As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
-  bandwidth, one expects an equal variance for each system, as will be shown in Section \ref{sec:bestFrequencyResolution}.
+  bandwidth, one expects an equal variance for each system, as will be shown in Section~\ref{sec:bestFrequencyResolution}.
 
@@
   Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
+  \TODO{show $\alpha$ and $\beta$ graphically (cfr. poster)}
   We choose the resonance frequency of the systems such that
@@
 
+  \TODO{simulations from Larsson2012}
+
 \section{Measurements} \label{sec:measurement}

### 2015-11-01 ch02-qlogms/sysid.tex
Import SYSID2012 paper

\section{Introduction}\label{sec:intro}
Input design deals with the task of choosing an excitation signal in a way so that the information obtained from the experiment is maximized. This is a problem which has a long history in statistics. In system identification, the focus has mostly been on input design for dynamic systems. A common approach is to design the input spectrum and thereby maximizing the information matrix of the estimates, see e.g. \cite{Fedorov1972,Goodwin1977}.

A complicating issue in identification of dynamic system is the fact that the information matrix often depends on the true parameter values. Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design. There are two main solutions to this discussed in the engineering literature:
\begin{enumerate}
\item Iterative input design where the design updated as more information about the system is available, see e.g. \cite{Hjalmarsson2005,Gevers2005}.
\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007a} and references therein. 
\end{enumerate}

In this paper we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified. We will consider input design when it is known that the system has resonances, possibly spanning a large frequency band. It is however not necessary to know how many resonances are in the system. The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.

The following parts of the paper are structured as follows. Section~\ref{sec:inputDesign} briefly presents the necessary input design theory. Section~\ref{sec:logarithmic} deals with the situation when limit information is available. The idea is illustrated in a series of simulation examples in Section~\ref{sec:sim}. Finally, conclusions are drawn in Section~\ref{sec:conclusions}.

\section{Input design}\label{sec:inputDesign}
For the theoretical analysis, we consider SISO output error systems, i.e.
\begin{align}
y_t &=G(s,\theta)u_t  + e_t,
\end{align}
where $\{u_t\}$ is a known input sequence, $\{y_t\}$ the output sequence and
$\{e_t\}$ is zero mean Gaussian white noise.
$G$ is a rational, time invariant transfer function in continuous time. For notational simplicity, $s$ is used both as a complex variable and the differentiation operator, it should be clear from the context which is used. The transfer function is parameterized by the vector $\theta$. These parameters are unknown and therefore need to be estimated.

The goal of input design is to find an input that under the given experimental conditions, gives as much information as possible about the system. This can be done by considering the Fisher information matrix and optimizing the input power spectrum.

In open loop experiments, the scaled average information matrix is given by
\begin{align}
\IF & = \lim_{N\rightarrow\infty}
          \frac{1}{N}
            \sum_{t=1}^{N}
              {\left(\frac{\partial\hat{y}_t}{\partial\theta}\right)
               \left(\frac{\partial\hat{y}_t}{\partial\theta}\right)^{\T}},\\
\frac{\partial\hat{y}_t}{\partial\theta}
    & =\frac{\partial G(s,\theta)}{\partial \theta}u_t.
\end{align}
By Parseval's theorem, \IF can be expressed as
\begin{align}
\IF &= \frac{1}{\pi}
         \int\limits_0^\infty \mathrm{Re}
           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
           \right\}
           \phi_u(j\omega)
           \dd{\omega} \text{.}
\label{eq:IF}
\end{align}
The information matrix is a function of the input power spectrum, which is the only entity that can be used to improve the quality of the estimates. A common optimality criterion is D-optimality where $\det{\IF}$ is maximized \citep{Goodwin1977}.

The information matrix tells us how good the individual parameter estimates are. However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance. It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2001}. This gives
\begin{align}
\var{\hat{G}(j\omega)} &= \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
\label{eq:varG}
\end{align}

Typically, the input design formulation depends on the true system parameters. This means that the optimal input depends on the \emph{unknown} system that one wants to identify. Furthermore, classical input designs, such as the D-optimal, typically give signals with sparse spectra. This means that only a few frequencies are excited. A sparse spectrum is bad from a robustness point of view; there is very limited information about what happens at the unexcited frequencies. Therefore, a signal design to be optimal for one system may result in very bad estimates if applied to another system. To increase the robustness of the design, one could take a fraction, say $\alpha$, from the optimal power and redistribute over the whole frequency band of interest. From \eqref{eq:IF} and \eqref{eq:varG} we see that scaling the input power by $1-\alpha$, gives the transfer function variance
\begin{align}
\var{\hat{G}(j\omega)}\frac{1}{1-\alpha}.
\end{align}
This is a small loss while the increase in robustness can be significant if the added signal is robust. Such a robust signal is studied in the following parts of the paper.

%Such a signal is discussed in the next section.

%\subsection{Using prior system information}
%Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
% say $\hat{\theta}_0 \in \mathbb{R}^n$ exists. A D-optimal design can then be
% found based $\hat{\theta}_0$. The resulting determinant is
%\begin{align}
%  \left[\det\IF^\star\right]^{-1}
%    &= \min_{\phi_u(\omega)}
%             \left[\det\IF\right]^{-1}
%\end{align}
%
%The optimal input can be realized as sum of $n$ sinusoids.
%Such an input is typically not robust to the initial guess since \TODO{\ldots}.
%As a solution to this, the optimal input is modified so that a fraction of the
%power in the optimal design is taken away and redistributed over all frequencies.
%This ensures that some excitation power is available also at other frequencies.
%
%If $\lambda_i$ is the fraction of the input power at frequency $\omega_i$,
%then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
%\begin{align}
%  \det\IF^\star &= \prod_{i = 1}^{n}
%                      \lambda_i^2
%                      \alpha(\omega_i).
%\end{align}
%The optimal input spectrum is
%\begin{align}
%  \phi_u^\star(\omega) &= \sum_{i=1}^{n}
%                            \lambda_i^2
%                            \delta(\omega,\omega_i)
%\end{align}
%If a fraction, say $\eta$, of the power is taken from each frequency and used
%at other frequencies, the input spectrum can be written as
%\begin{align}
%  \phi_u(\omega) &= (1-\eta)
%                      \sum_{i=1}^{n}
%                        \lambda_i^2 
%                        \delta(\omega,\omega_i)
%                    + \phi_u^{\robust}(\omega),\\
%                 &= (1-\eta) \phi_u^\star    (\omega)
%                    +        \phi_u^{\robust}(\omega).
%\end{align}
%The term $ \phi_u^{\robust}$ is the part that introduces robustness and
%must be such that
%\begin{align}
%  \int_0^{\pi} \phi_u^{\robust}(\omega) \dd{\omega} &= n \eta.
%\end{align}
%The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
%a discrete spectrum, e.g. from a multi-sine signal, or as
%a continuous spectrum. The resulting information matrix for the robust input is hence
%\begin{align}
%  \IF &= (1-\eta)\IF^\star + \IF^\robust
%\end{align}
%The determinant is therefore
%\begin{multline}
%\det\left[(1-\eta)\IF^\star + \IF^\robust\right]
%  \geq \det\left[(1-\eta)\IF^\star\right] + \det\left[\IF^\robust\right] \\
%  =  (1-\eta)^n\det\left[\IF^\star\right] + \det\left[\IF^\robust\right]
%  \text{.}
%\end{multline}
%The inequality holds since the information matrix is a positive, semi-definite
%matrix. Hence the largest possible loss in the determinant due to the robustness
% is given by the factor $(1-\eta)^n$.
%\TODO{This bound is often very low, maybe better one should be found!}

\section{Logarithmic power distributions}\label{sec:logarithmic}
When no information about the system is known, it is desirable that
the excitation signal is such that regardless of the true system characteristics,
the resulting estimates have equally good statistical properties.
This can be ensured by a suitable choice of the input power spectrum.

 \subsection{A second order system}
Consider the second order system
\begin{align}
y_t &= G(s,\theta)=\frac{1}{\frac{s^2}{\omega_0^2} + 2\frac{\damping}{\omega_0}s + 1}u_t,
\label{eq:2ndOrderSys}
\end{align}
with parameters $\theta=[\omega_0\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\omega_0$
and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wR$.
Since information is local in the frequency domain, the input signal power inside $\wdB$, contributes significantly to the information matrix while input power outside $\wdB$ has a smaller contribution. This can be seen by considering the optimal design for a second order system. From \citep{Goodwin1977} we have that the D-optimal design for \eqref{eq:2ndOrderSys} is a single sinusoid at frequency
\begin{align}
\omega^\star =\frac{\omega_0\left(\left(1-2\damping^2\right)+\left(\left(1-2\damping^2\right)^2+15\right)^{1/2}\right)^{1/2}}{\sqrt{5}}.
\label{eq:optFreq}
\end{align}
For systems with low damping, i.e $\damping\ll1$ , $\omega^\star\approx\omega_0$, which is inside the bandwidth of the system. From \eqref{eq:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. Input design can be based on a guess of $\omega_0$, however if this guess is wrong, the resulting estimates may be unacceptable \citep{Rojas2007}.

When no information about the system is available, we propose using an input power spectrum with a logarithmic power distribution. This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2001}. We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\omega_0k_{min}\; \omega_0k_{max}]$, where the resolution is $k_0=1/T_{meas}$ and $T_{meas}$ is the measurement time. Hence, a finite measurement time limits the frequency resolution and therefore we have to put a lower limit on the frequency band of interest. Moreover, we can only impose the logarithmic distribution sufficiently well if $k_{min}$ is large enough.

First, we look at the bandlimited $1/f$ power spectrum given by
\begin{align*}
\label{eq:pink}
\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\omega_0k_{min}\; \omega_0k_{max}]$,}\\
                        0           &\text{otherwise}.
            \end{cases}
\end{align*}
With this input spectrum, the power inside $\wdB$ is
\begin{align}
  \frac{1}{2\pi}
    \int\limits_{(1-\damping)\wR}^{(1+\damping)\wR}
     \frac{1}{\omega} \dd{\omega}
  = \frac{1}{2\pi}
    \ln{\frac{1+\damping}{1-\damping}},
\end{align}
which is independent of $\omega_0$. The robustness of the $1/f$ input has been noted previously in e.g. \cite{Rojas2007}

Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2001}] given by
\begin{align}
  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\omega_k)},
\end{align}
where $\omega_{k}/\omega_{k+1} \approx \alpha_{f} = e^{\Delta}$.
Hence, the number of spectral lines inside \wdB is 
\begin{align}
\left\lfloor\ln{\left[\frac{1+\damping}{1-\damping}\right]}\Delta^{-1}\right\rfloor,
\end{align}
where $\lfloor\cdot\rfloor$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\omega_0$.

More generally, a multisine can be defined as:
\begin{equation}
 u \left[ n\right] = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
  \label{eq:MS}
\end{equation}
where $A_k$ and $\psi_k$ are its amplitude and phase spectrum; $f_s$ is the
sampling frequency and $f_0 = \frac{f_s}{N}$ the base frequency with $N$ the 
number of points in a period.

To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha_f$.

The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\omega_0$. 
This is illustrated in Section~\ref{sec:sim}.

\subsection{Sums of second order systems}
This section extends the previous section to more general systems than second order.
Consider a system
\begin{align}
G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
             =\sum_{i=1}^{K}  \frac{1}
                                   {   \frac{s^2}{\omega_i^2}
                                    + 2\frac{\damping_i}{\omega_i}s
                                    + 1},\\
\theta_i&=[\omega_i\;\damping_i]^{\T}.
\label{eq:sumSys}
\end{align}
The systems  $G_i$ will be called the \emph{sub-systems} of $G$. With loss of generality, we assume that $\omega_1 < \omega_2 < \cdots < \omega_K$. To properly identify the system $G$, excitation is required such that all
subsystems are properly excited, regardless of their individual resonance frequencies.

The information matrix for systems of the type \eqref{eq:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
\begin{align}
\IF &= \frac{1}{\pi}
\begin{bmatrix}
  \partial G_{1,1}        &\partial G_{1,2}       &\cdots         &\partial G_{1,K}\\
  \partial G_{2,1}        &\partial G_{2,2}       &\cdots         &\partial G_{2,K}\\
  \vdots                  &\vdots                 &\ddots         &\vdots          \\
  \partial G_{K,1}        &\partial G_{K,2}       &\cdots         &\partial G_{K,K}
\end{bmatrix},\\
\partial G_{i,j} &= \int_0^\infty
                      \mathrm{Re}\left\{
                          \frac{\partial G_i}
                               {\partial \theta_i}
                          \frac{\partial G_j^{\HT}}
                               {\partial \theta_j}
                                \right\}
                      \phi_u(\omega)\dd\omega.
\end{align}

Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
To illustrate this we look at a system with $K=2$, i.e. the sum of two second order systems.
The conclusions from the example are easily extended to systems consisting of more than two sub-systems.

\subsubsection{Example: Sum of two second order systems}
Consider the system
\begin{align}
G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
%&=\frac{1}{\frac{s^2}{\omega_1^2} + 2\frac{\damping_1}{\omega_1}s + 1} + \frac{1}{\frac{s^2}{\omega_2^2} + 2\frac{\damping_2}{\omega_2}s + 1},
\end{align}
with $\theta_1=[\omega_1\;\damping_1]^{\T}$ and $\theta_2=[\omega_2\;\damping_2]^{\T}$.
The information matrix for this system is
\begin{align}
\IF &=
       \begin{bmatrix}
         \partial G_{1,1}  & \partial G_{1,2}\\
         \partial G_{2,1}  & \partial G_{2,2}
       \end{bmatrix}.
\label{eq:infoEx}
\end{align}
To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:infoEx}, when the input spectrum \eqref{eq:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.

Direct calculations for $\damping < 1$ give
\begin{align}
\label{eq:auto}
\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_1^{\HT}}{\partial \omega_1}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\omega_1^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
\end{align}
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
% \begin{align}
% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
% &\int_0^\infty\left|\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
% \end{align}
\begin{gather}
\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:cross1} \\
\leq
\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \omega_1} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\omega_1\damping}\right]}{\omega_1^2\left[1+2\frac{\damping j\omega}{\omega_1} + \left(\frac{j\omega}{\omega_1}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\omega_1\right\}$. Hence $\left|\frac{\partial G_1}{\partial \omega_1} \right|$ has asymptotical slope 20\unit{\frac{dB}{dec.}} for low frequencies, at $j\omega=\damping\omega_1$ the slope increases to 40\unit{\frac{dB}{dec.}}. There are four poles which give a $-40$\unit{\frac{dB}{dec.}} roll-off after the peak. The shape of $\frac{\partial G_1}{\partial \omega_1} $ is illustrated in Fig.~\ref{fig:dG}.

A crude, albeit useful, bound on the integrand in \eqref{eq:cross} is
\begin{align}
&f\left(\omega,\theta_1,\theta_2\right)=
  \begin{cases}
   \frac{\omega^2}{\omega_1^2}
   \frac{1}{\omega}
   \partial G_1^\infty
                                       & \text{if $\omega \leq \omega_1$,}\\
   \phantom{\frac{\omega^2}{\omega^2}}
   \frac{1}{\omega}
   \partial G_1^\infty
                                       & \text{if $\omega_1 < \omega < \omega_2$,}\\
   \frac{\omega_2^2}{\omega^2}
   \frac{1}{\omega}
   \partial G_1^\infty
                                       & \text{if $\omega \geq \omega_2$,}
  \end{cases}
\end{align}
where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \omega_1}\right\|_\infty$. Again, direct calculations give
\begin{align}
\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\omega_1\left(2-\ln{\frac{\omega_1^2}{\omega_2^2}}\right)}{\omega_2^2}\damping^{-2} + \mathcal{O}(1).
\end{align}
Hence \eqref{eq:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
\begin{itemize}
\item the integral \eqref{eq:cross1} decreases as $\omega_2-\omega_1$ increases, and
\item lower damping further decreases the integral \eqref{eq:cross1} in comparison to \eqref{eq:auto}.
\end{itemize}

\begin{figure}
\centering
\input{\thisDir/figs/rolloff.tikz}
\caption{The shape of $\frac{\partial G_1}{\partial \omega_1}$. The roll-off around the peak is significant and depends on the damping of the system.}
\label{fig:dG}
\end{figure}

To further illustrate the decoupling of the two systems, we calculate \eqref{eq:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\omega_1$ and $\omega_2$. If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\omega_1-\omega_2$ and not on the actual frequencies. The resulting information matrix is then normalized so that the largest element is $1$.

In Fig.~\ref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling. The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1. In this example, the $\damping$ is set to be the same in both sub-systems. Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.

Based on the above arguments, we make the following approximation of the information matrix for systems with low damping,
\begin{align}
\IF&\approx \begin{bmatrix}\partial G_{1,1} &0\\
                        0&\partial G_{2,2}\end{bmatrix}.
\end{align}
Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
\begin{align}
\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &0\\
                        0&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
\end{align}

This results extends mutatis mutandis to systems consisting of more sub-systems.

\begin{figure}
\centering
\input{\thisDir/figs/coupling.tikz}
\caption{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
         The arrow indicates the direction of increasing separation.}
\label{fig:coupling}
\end{figure}

\section{Simulations}\label{sec:sim}
We considered a linear second order system that is to be identified, with the
only prior knowledge that its resonance frequency $\fR$ lies in a known
frequency band that may span several decades. 
Our goal is to identify such a system by means of a single excitation signal, 
such that the frequency response function (FRF) of the second order systems that are
equally damped are identified with the same uncertainty near their resonance.

\subsection{Excitation}
To excite the system under test, we used quasi-logarithmic (quasi-log) random-phase multisines. 
Their phase spectrum $\psi_{k}$ is the result of a uniform random process over $[0,2\pi[$.
A logarithmic spacing of the frequency components causes each decade within the band of interest to contain the same number of frequency components.

The quasi-log multisines were sampled at $f_s = 65\,536 \unit{Hz}$
and consisted of $N= 65\,536$ points such that the frequency spacing was $f_0 = 1\unit{Hz}$ for the linear grid.
This allowed the signal to cover four decades in the frequency domain,
from which we did not use the first decade.
Only frequencies between $1\unit{Hz}$ and $16\,384\unit{Hz}$ are excited, such that aliasing was avoided.

For the quasi-log excitation, a frequency ratio of $\alpha_f = 1.05$ was chosen
and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
amplitude was normalized such that the root mean square (RMS) value of $u[n]$
was equal to $1$.

The desired frequency ratio $\alpha_f$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
This causes a less dense coverage of the lowest frequency bands.

\subsection{System under test}
The systems we studied are low-pass second order systems with a given damping
$\damping$, resonance frequency $\fR$ and a DC gain of $0 \unit{dB}$. Such systems
can be represented in the discrete frequency domain by a transfer
function of the form:
\begin{equation}
  G \left( z \right) = \frac{         b_2  z^{2} + b_1 z + b_0}%
                            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:tf}
\end{equation}

These discrete-time systems were constructed using the \matlab\ function \texttt{cheby1}.

An output error (OE) model was used to describe the system under test with the
input $u[n]$, the system output $y_0[n]$, the white noise source $e[n]$
and the measured output $y[n] = y_0[n] + e[n]$.

\subsection{Simulation setup}
First, we considered a system with damping $\damping=0.05$ and resonant
frequency $\fR = 40 \unit{Hz}$.

The output noise $e[n]$ was white Gaussian noise with a standard deviation
$\sigma_e = 0.1123$ which was approximately $10$ times smaller than the
root mean square (RMS) value $y_0[n]$.

The simulations were repeated $R=1000$ times for each system with different realizations of the multisines $u[n]$ and the noise $e[n]$.
In order to avoid that all simulations started with zero initial conditions, $N + N_{\mathrm{trans}}$ data points were generated, from which the first $N_{\mathrm{trans}}$ points of each simulation were discarded.

For each of these simulations, the system was identified by means of the \texttt{oe}
function in the \matlab\ System Identification Toolbox\Cite{TDIDENT}.
To prevent convergence issues, we used the true model parameters
$\left\{ a_0, a_1, b_0, b_1, b_2 \right\}$ and model structure
as mentioned in \eqref{eq:tf} as starting values.
This increases the probability of the search converging to the global minimum, which
allowed to focus on the real quantity of interest: the variance of the FRF.

\subsection{Results for a single system}
The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).

These graphs show that the bias is more than $20 \unit{dB}$ less than the variance.
This means that the mean square error (MSE) of the estimated FRFs is mainly caused by the variance $\sigma_{\hat{G}}^2$ and not by a large bias.

\begin{figure}[hpt]
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sys005log0-1.tikz}
  \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.05$ 
           along with its variance and bias.}%
  \label{fig:FRF1}
\end{figure}

\subsection{Simulations on a range of second order systems}
The simulation carried out above was repeated for a more general set of systems.
We studied systems with both a damping of $\damping=0.05$ (as above) and $\damping=0.2$.
For these different damping values, systems with resonant frequencies
$\fR \in \{ 40  \unit{Hz}\!,$
          $ 80  \unit{Hz}\!,$
          $200  \unit{Hz}\!,$
          $400  \unit{Hz}\!,$
          $800  \unit{Hz}\!,$
          $  2 \unit{kHz}\!,$
          $  4 \unit{kHz}\!\}$ were considered.
The parameters pertaining to sampling and the excitation signal were left unchanged
from the previous simulations. For the systems with a damping of $0.2$, $\sigma_e$
was put at $0.0678$, which is approximately $10\%$ of the RMS value of $y_0[n]$.
To allow an easy comparison with a multisine with an equidistant (linear) frequency grid, we also evaluated the variance for such an excitation signal (which had all other parameters determined similarly to the quasi-log multisines).

In \figref{fig:damping005} and \figref{fig:damping02} the results from these
simulations are presented in a condensed form. 
They show the mean estimated FRFs ($\hat{G}$), the true FRFs ($G_0$) and the corresponding standard deviations ($\sigma_{\hat{G}}$) near the resonance frequency of the simulated systems.
The bias was at least $20\unit{dB}$ smaller than the standard deviation as well, but is omitted from the figures for clarity.

We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.

For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
we observe that the variance is nearly constant over the frequency range as well.
The standard deviation lies at around $-49.3 \unit{dB} \pm 2.2\unit{dB}$.
Systems that have a lower resonance frequency, exhibit a slightly higher variance 
on their estimated FRF (near the resonance).

The logarithmically-spaced excitation provides a much more constant dependency of resonance frequency to the variance than a linearly-spaced multisine, where the variance varies over respectively $35$ and $25 \unit{dB}$.

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/damping005-cmp.tikz}
  \caption{Comparison of the FRF and corresponding variances for
           different second order systems with constant damping
           $\damping=0.05$ but different resonance frequencies around
           their respective resonance frequencies, for both a quasi-log 
           and a linear multisine excitation.}%
  \label{fig:damping005}
\end{figure}

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/damping02-cmp.tikz}
  \caption{Comparison of the FRF and corresponding variances for
           different second order systems with constant damping
           $\damping=0.2$ but different resonance frequencies around
           their respective resonance frequencies, for both a quasi-log 
           and a linear multisine excitation.}%
  \label{fig:damping02}
\end{figure}

\subsection{Simulation example on higher order systems}
To show that the suggested method also works on more general systems,
we considered a system that consists of two second order systems \eqref{eq:tf} in 
parallel. This is equivalent to adding their respective transfer functions,
therefore, the resulting transfer function is of the form:
\begin{equation}
  G \left( z \right) 
  = \frac{         b_4 z^{4} + b_3 z^{3} + b_2 z^{2} + b_1 z + b_0}%
         {\phantom{a_4}z^{4} + a_3 z^{3} + a_2 z^{2} + a_1 z + a_0}
  \text{.}
\label{eq:tfO4}
\end{equation}

For example, a system composed of two second order systems with $\damping = 0.2$
and $\fR = 400 \unit{Hz}$ for the first system and $\fR=4 \unit{kHz}$ for the second
system was simulated similarly to the previous examples. The standard deviation
of the noise $\sigma_e$ was put at $0.0678$. The corresponding results are 
shown in \figref{fig:sumSys}.

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
  \label{fig:sumSys}
\end{figure}

We observe that the amplitude of the FRF is $9.8\unit{dB}$ and $8.1\unit{dB}$ at the resonant frequencies.
The standard deviation on the FRF lies respectively $59.7 \unit{dB}$ and $59.6 \unit{dB}$ lower than the FRF at these frequencies. 
This shows that both resonances are captured with a practically identical error.

\subsection{Conclusion}
The variance on the FRF near resonances with identical damping is nearly independent of the resonance frequency when a quasi-log multisine is used as excitation signal. 
This result was obtained for second order sections and illustrated on a more general system.

%%Conclusion
\section{Conclusions}\label{sec:conclusions}
In this paper we recalled that the design of an optimal excitation signal may require prior system knowledge that is insufficiently accurate or even unavailable. 
When only the limited prior knowledge that the system resonances lie in a certain (possibly wide) frequency band, we can create a suitable class of excitation signals. 
These signals are required to yield estimates having a variance that is independent of the resonance frequencies of the system. 
We showed that such a signal should have a power spectrum that is distributed in $1/f$.
In this paper (quasi-)logarithmic multisines were considered to serve this purpose.

By means of simulations for different second order sub-systems, it is confirmed that for a given damping, the variance of the estimated is almost independent of the actual resonance frequencies of the system within the frequency band of interest.
The same results were found for higher order systems and illustrated for an example. 
A theoretical motivation for these results is provided.

The proposed excitation signals therefore offer an easy and efficient way to identify systems in a wide frequency range such that an accuracy level that is independent of the resonance frequencies can be attained for the complete frequency span.

### 2015-11-01 config/glossaries.inc.tex
Import SYSID2012 paper

@@
 %% SYMBOLS
-\newsymbolglos{approx}{\approx}{Approximately equal}
-\newsymbolglos{bydef}{\isdef}{Equal by definition}
+\newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}
+
+\newsymbolglos{E-approx}{\approx}{Approximately equal}
+\newsymbolglos{E-bydef}{\isdef}{Equal by definition}
+\newsymbolglos{E-propto}{\propto}{Proportional to}
+
+\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
+\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
+\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
+
 \newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
-\newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
-\newsymbolglos{SetC}{\mathbb{C}}{Set of the complex numbers}
-\newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
-\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\unit{rad/s}$}
-\newsymbolglos{f}{f}{Frequency in $\unit{Hz}$}
+\newsymbolglos{lcm}{\lcm}{Least common multiple}
+\newsymbolglos{cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
+\newsymbolglos{SetR}{\RealNumbers}{Set of the real numbers}
+\newsymbolglos{SetZ}{\IntegerNumbers}{Set of integer numbers}
+\newsymbolglos{SetC}{\ComplexNumbers}{Set of the complex numbers}
+\newsymbolglos{SetN}{\NaturalNumbers}{Set of the natural numbers}
+\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}
+
+\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
+\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
+\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}
+
+\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
+\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}
+
+\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
+\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
+\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
+\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
 
@@
 \newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
+\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}
+
+\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}
 

### 2015-11-01 front-and-back-matter/frontmatter.tex
Import SYSID2012 paper

@@
 
-\printglossary[type=\acronymtype,style=long,toctitle={Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
+\printglossary[type=\acronymtype,style=long,toctitle={List of Acronyms}, title={List of Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
 \glsaddall[types=symbols]
-\printglossary[type=symbols,style=altlong4col,toctitle={List of Symbols}]
+\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]
 

### 2015-11-05 ch02-qlogms/logMS_IMTC.tex
Clean up experiment design a bit

@@
 \subsection{Multisine Excitations}
-  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ frequency components:
+  To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
+  \begin{definition}[Generalized multisine] \label{def:generalized-MS}
+  A generalized multisine $u(t)$ is a signal consisting of $F$ sine waves with a different frequencies $f_k$, amplitudes $A_k$ and phase shifts $\phi_k$:
   \begin{equation}
@@
   \end{equation}
-  In this expression, $f_k$ represents the $k^{\text{th}}$ excited frequency component.
-  $A_k$ is the amplitude and $\phi_k$ the phase of the $k^{\text{th}}$ spectral line.
+  For simplicity, one can stipulate that the frequency grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
+  \end{definition}
+
   We limit ourselves, without loss of generality, to random phase multisines.
@@
     the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
-  For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
   Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.
@@
       = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
-    \text{,}
+    \text{.}
   \end{equation}
-  where the least common (integer) multiple of the real values $T_k$ is defined as
+  \begin{definition}[Least common (integer) multiple] \label{def:lcm-real}
+  The least common multiple of the set of values $T_k \in \RealNumbers$ for $k \in \set{1, \ldots, F}$ is  
   \begin{equation}
     \lcm \set{T_1, \ldots, T_F} \isdef
-      \min \set{T \given{\forall i \in \set{1,\ldots,F}, \exists n_i \in \NaturalNumbers: n_i T_i = T }}
-      \text{.}
+      \min \set{T \given{\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }}
    \end{equation}
-  Note that this minimum doesn't always exist (e.g. when $f_1 = 1 \unit{Hz}$ and $f_F = \pi \unit{Hz}$), in such cases the multisine is aperiodic.
+   if such a minimum exists.
+   \end{definition}
+  \begin{example}
+   Consider a generalized multisine where $f_1 = 1 \unit{Hz}$ and $f_2 = \tfrac{2}{3} \unit{Hz}$.
+   The corresponding periods are $T_1 = f_1^{-1} = 1 \unit{s}$ and $T_2 = f_2^{-1} = 1.5 \unit{s}$.
+   The overall period of the multisine is $T = n_1 T_1 = n_2 T_2 = 3 \unit{s}$, i.e. $n_1 = 3$ and $n_2=2$.
+  \end{example}
+
+  \begin{example}
+   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
+   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
+   Consequently, such a `multisine' is not periodic.
+  \end{example}
+
+  This last example illustrates that a least common multiple of real numbers does not always exist.
+  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
 
@@
   \end{equation}
-  Such a grid is called a quasi-logarithmic (quasi-log) grid \citep{Pintelon2001}.
+  Such a grid is called a quasi-logarithmic (quasi-log) grid \citep{Pintelon2012}.
 
@@
 \TODO{zin loopt niet goed}
-  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2001, Gallager2008, matrixcookbook} to be approximately equal to
+  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
   \begin{align}
@@
   \end{equation}
-  the Fisher information matrix \citep{Pintelon2001}.
+  the Fisher information matrix \citep{Pintelon2012}.
 
@@
   Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
-  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2001}:
+  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
   \begin{equation}

### 2015-11-05 config/glossaries.inc.tex
Clean up experiment design a bit

@@
 text={#3},
-first={#3\protect\footnote{#3: #4}},
+first={#4~(#3)},
 plural={#3\glspluralsuffix},
-firstplural={#3\glspluralsuffix\protect\footnote{#3: #4}},
+firstplural={#4~(#3\glspluralsuffix)},
 #1}}
@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{SISO}{SISO}{Single Input Single Output}
-\newacronym{MIMO}{MIMO}{Multiple Input Multiple Output}
+\newacronym{SISO}{SISO}{single-input single-output}
+\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
 \newacronym{SIMO}{SIMO}{Single Input Multiple Output}
 \newacronym{MISO}{MISO}{Multiple Input Single Output}
-\newacronym{BLA}{BLA}{Best Linear Approximation}
-\newacronym{DUT}{DUT}{Device Under Test}
+\newacronym{BLA}{BLA}{best linear approximation}
+\newacronym{DUT}{DUT}{device under test}
 
 \newacronym{FRF}{FRF}{frequency response function}
-\newacronym{LTI}{LTI}{Linear time-invariant}
-\newacronym{ETFE}{ETFE}{Empirical Transfer Function Estimate}
+\newacronym{LTI}{LTI}{linear time-invariant}
+\newacronym{ETFE}{ETFE}{empirical transfer function estimate}
 

### 2015-11-08 ch02-qlogms/logMS_IMTC.tex
Add misalignmet figure to qlogms
Add some operators

@@
 
-  Each decade that is completely  within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains
+  \begin{property}
+    Each decade that is completely  within the range of excited frequencies $\set{f_1, \ldots, f_F}$ contains
    \begin{equation}
+     F_{\decade} \isdef
      \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
@@
    I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+  \end{property}
+
    Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).
@@
 
-  \subsection{Setup for selecting $\alpha$}
+  \subsection{Selection of the frequency grid spacing $\alpha$}
   When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
@@
   Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
-  \TODO{show $\alpha$ and $\beta$ graphically (cfr. poster)}
+
+  \begin{figure}
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/misalign.tikz}
+    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
+    The }
+    \label{fig:misalignment-logms}
+  \end{figure}
+
   We choose the resonance frequency of the systems such that
@@
   \end{equation}
-  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $[0,1]$.
+  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
   This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.

### 2015-11-08 config/glossaries.inc.tex
Add some operators

@@
 %% SYMBOLS
-\newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}
+% \newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}
 
@@
 
+\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identify matrix }
+
 \newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
@@
 \newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
+\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
+\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
+\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}
 

### 2015-11-08 ch02-qlogms/logMS_IMTC.tex
Figure ID cycle + some intro exp design

@@
   \subsection{The system under consideration}
-  We consider the transfer function models of generic linear time-invariant systems of arbitrary but finite orders $n_a\times n_b$:
+  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_a\times n_b$:
   \begin{align}
@@
                 }
+    \label{eq:logms:F}
     \end{equation}
@@
   \begin{property}
-    Each decade that is completely  within the range of excited frequencies $\set{f_1, \ldots, f_F}$ contains
+   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
    \begin{equation}
-     F_{\decade} \isdef
-     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
-         = \floor{\log_{\alpha} 10}
+     F_{B}(f) \isdef
+     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
+         = \floor{\log_{\alpha} \kappa}
+         \text{.}
    \end{equation}
-   excited frequency lines.
+   \end{property}
+  \begin{example}
+    For the frequency decade band $\decade(f) = \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
+  \end{example}
+
+   Obviously, the same argument can be held for any set of frequency bands with constant relative bandwidth (e.g. octave $\kappa = 2$).
    I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
-  \end{property}
-
-   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).
 

### 2015-11-08 config/glossaries.inc.tex
Figure ID cycle + some intro exp design

@@
 
+\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
+\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
+\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
+\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
+\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
+
+\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
+\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}
+
 \newsymbolglos{E-approx}{\approx}{Approximately equal}
@@
 
-\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
+\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
+
+\newsymbolglos{lcm}{\lcm}{Least common multiple}
+
+\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identity matrix}
+
 \newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
 \newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
+\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
 
-\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
-\newsymbolglos{lcm}{\lcm}{Least common multiple}
-\newsymbolglos{cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
-\newsymbolglos{SetR}{\RealNumbers}{Set of the real numbers}
-\newsymbolglos{SetZ}{\IntegerNumbers}{Set of integer numbers}
-\newsymbolglos{SetC}{\ComplexNumbers}{Set of the complex numbers}
-\newsymbolglos{SetN}{\NaturalNumbers}{Set of the natural numbers}
-\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}
+\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
+\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
+\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
+\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
+\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
+\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
+\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
+\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
+\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
+\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}
 
+\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
 \newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
-\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
 \newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}
 
-\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
-\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}
-
-\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identify matrix }
-
-\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
-\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
-\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
-\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
-\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
-\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
-\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}
+\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}
 

### 2015-11-12 ch02-qlogms/excitation-design.tex
Import QLogMS TIM paper
Some TODOs in QLogMS
emove old bib defs
Import SYSID2012 paper
Figure ID cycle + some intro exp design
Gebrol in intro/conclusie qLogMS

@@
 \chapter{Design of excitation signals}
+\def\thisDir{ch02-qlogms}
 \researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}
+
+\section{Introduction}
+\label{sec:excitation:intro}
+Experiment design is the first step in the system identification loop, as illustrated in \figref{fig:intro:identification-cycle}.
+Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
+In many cases
+
+\subsection{Generic excitation signals}
+\label{sec:excitation:intro:generic}
+
+\subsection{Optimal excitation signals}
+\label{sec:excitation:intro:optimal}
+Since generic excitation signals are not specifically geared towards the particular system under test, such signals tend to waste signal power.
+
+, such signals essentially don't use all the available signal power to reduce the uncertainty in the estimate.
+
+\subsection{Robust excitation signals}
+\label{sec:excitation:intro:robust}
+As illustrated above, optimal experiment design places the user in a catch-22 situation.
+
+\subsection{Approach in this chapter}
+\label{sec:excitation:intro:approach}
+In this chapter, the goal is to construct excitation signals that bridge the properties of generic and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
+In particular, a generic excitation signal will be used but its properties are tuned in such a way that it
+
+\input{ch02-qlogms/logMS_IMTC.tex}
+
+\input{ch02-qlogms/sysid.tex}
 
@@
 \subsection{\TODO{qLog design rules}}
+
+\section{Conclusion}
+\label{sec:excitation:conclusion}
+In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.
+
+The suggested amplitude compensation methods allow the user to measure a parametric LTI model for systems in a wide frequency band with a constant uncertainty.
+The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
+In practical applications, this slight increase is likely to be negligible.
+The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.
+
+We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equidamped set of systems.
+The presented method allows to select a maximal value for the frequency ratio $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.
+In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+
+\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}
+
+\begin{subappendices}
+  \section{Justification for considering only poles}
+
+\end{subappendices}

### 2015-11-12 ch02-qlogms/logMS_IMTC.tex
Gebrol in intro/conclusie qLogMS

@@
 \TODO{rename labels}
-% \begin{abstract}
-% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
-% Periodic signals are very popular in many advanced dynamic signal analyzers.
-% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
-% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
-% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
-% \end{abstract}
 
@@
   Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
+
   To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
@@
 
-  Consequently, the complete multisine has a period of
+  Consequently, the complete multisine has a period $T_{u(t)}$ that is the common multiple of the period of all its components:
   \begin{equation}
@@
   \begin{example}
-    For the frequency decade band $\decade(f) = \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
+    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
   \end{example}
@@
   We can again approximate such a signal by means of a quasi-logarithmic grid multisine.
-  To do so, we excite a quasi-logarithmic frequency grid $\set{f_1,\ldots,f_k,\ldots,f_F}$ and determine the corresponding amplitude spectrum $A_k$ such that each excited line carries the same power as the corresponding frequency band does for pink noise.
+  To do so, we construct a quasi-logarithmic frequency grid $\set{f_1,\ldots,f_k,\ldots,f_F}$ and determine the corresponding amplitude spectrum $A_k$ such that each excited line carries the same power as the corresponding frequency band does for pink noise.
 
@@
 \TODO{zin loopt niet goed}
-  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
+  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
   \begin{align}
@@
 
-  Let's select a logarithmic frequency grid with an infinite number of grid lines
+  Consider a logarithmic frequency grid with an infinite number of grid lines
   \begin{equation}
@@
   \end{equation}
+
   Consider a second grid, defined as a multiple of this grid, $m\vec{\omega} = \set{m \cdot \alpha^k \omega_0 \given{k \in \ZN}}$; both grids share the same frequency ratio $\alpha$.
@@
     However, if the system under test would have a lower resonance frequency, a quasi-log multisine with power compensation would perform better as was seen in the simulations.
-
-\section{Conclusion} \label{sec:conclusion}
-The suggested compensation method allows the user to measure a parametric LTI model for systems in a wide frequency band with a constant uncertainty.
-The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
-In practical applications, this slight increase is likely to be negligible.
-The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.
-
-We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equidamped set of systems.
-The presented method allows to select a maximal value for the frequency factor $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.
-In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
-
-\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}

### 2015-11-12 ch02-qlogms/excitation-design.tex
Beunen in excitation design

@@
 
-\input{ch02-qlogms/sysid.tex}
+\TODO{reshape figures}
+\TODO{rename labels}
 
-\section{\TODO{Robust vs optimal}}
-\section{\TODO{Robust QLog MS}}
-\subsection{\TODO{Constraints: time and power}}
-\subsection{\TODO{Informativity of experiment}}
-\subsection{\TODO{Normalized design w.r.t. damping}}
-\subsection{\TODO{Grid misalignment effects}}
-\subsection{\TODO{qLog design rules}}
+\section{Introduction} \label{sec:intro}
+  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
+  Of course, we also want to attain a specified uncertainty level over the full frequency span.
+
+  Any LTI system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
+  Therefore the performance of the proposed method is assessed on a prototype system of second order.
+  This does not limit the generality of the approach as we can add several of such systems to construct a general LTI system.
+
+  To ensure that any second order system with its resonance frequency in the specified frequency range is measured with an equal accuracy, the system output should contain a comparable power level irrespective of its resonance frequency.
+  For a system with a sufficiently low damping, one can intuitively understand that most of the information is contained within the $3 \unit{dB}$ bandwidth of the system.
+  Remember that an LTI system is naturally described in a logarithmic frequency axis (the slopes of such a system are specified in $\unit{dB}/\text{decade}$).
+  Hence, an excitation with a flat power spectrum and a linearly spaced frequency grid will over-excite the high end of the band at the cost of the low frequencies.
+  To restore equal excitation signal levels over the complete range of frequencies, we will need to distribute the power in $1/\omega$ over the frequency band.
+  In a noise excitation context, this results in pink noise.
+  In a periodic setting, this results in a multisine whose frequency components are spaced equidistantly on a logarithmic axis.
+
+  The main problem is that network and dynamic signal analyzers typically
+  rely on an equidistant frequency grid that comes with the Discrete Fourier Transform (DFT).
+  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
+  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
+  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
+  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
+  This problem was already discussed in \citet{Geerardyn2012IMTC}.
+
+  We will also present a simple method to determine a suitable density of a logarithmically spaced signal for a predefined minimal damping of the system to be tested.
+
+  In the first section of this paper, we start from a generic transfer function model and discuss a decomposition thereof in second order subsystems and their properties.
+  We provide a comparison between several possible implementations of the frequency grids.
+  We discuss their applicability to multisine signals.
+  We also introduce a compensation method for the problems of the quasi-logarithmic grid and propose a novel $1/f$ `pink' quasi-logarithmic multisine.
+  The second section describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant quality (signal to noise ratio (SNR)) is obtained.
+
+  In the third section, the presented techniques are illustrated on a simulation example.
+  Finally, we verify our results experimentally on the measurements of a band-pass filter.
+
+\section{Methodology} \label{sec:method}
+
+  \subsection{The system under consideration}
+  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_a\times n_b$:
+  \begin{align}
+    G\left( \Omega, \theta \right) = \frac{B\left( \Omega,\theta \right)}
+                                          {A\left( \Omega,\theta \right)}
+                                   = \frac{\sum\limits_{i=0}^{n_b-1} b_i \Omega^i}
+                                          {\sum\limits_{i=0}^{n_a-1} a_i \Omega^i}
+    \text{.} \label{eq:model}
+  \end{align}
+
+  The model is parametrized in the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
+  For a continuous time model $\Omega = s$, while for the discrete time case $\Omega = z$.
+
+  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
+
+  To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
+  In continuous time such a system can be described by a transfer function of the form
+  \begin{equation}
+    G\left(s \right) = \frac{\dc}
+                            {             \frac{s^2}
+                                               {\wn^2} 
+                             + 2 \damping \frac{s}
+                                               {\wn}
+                             + 1
+                            }
+  \text{.}
+  \label{eq:secondOrderSystemCT}
+  \end{equation}
+\TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
+\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter.
+This will be well-approximated by considering only the second order system of the paper.}
+
+  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
+  The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
+  The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.
+
+  When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in
+  the amplitude of the transfer function \citep{Oppenheim1983}:
+  \begin{align}
+   \left| G\left(\wM \right) \right| & \isdef
+          \max_{\omega} \left| G\left( \omega \right)  \right|
+        = \frac{\dc}
+               {2 \damping \sqrt{1-\damping^2}}
+               \label{eq:peakAmplitude}\\
+   \wM &
+        = \sqrt{1-2\damping^2} \wn
+        \label{eq:peakFrequency}
+    \text{.}
+  \end{align}
+
+\subsection{System and noise model}
+  In this paper, an output error (OE) system setup is used.
+  Denote
+    $U  \left(\omega\right)$ as the excitation signal,
+    $Y_0\left(\omega\right)$ the exact, unperturbed system output,
+    $E  \left(\omega\right)$ for the output noise source,
+    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal.
+
+  The output noise is assumed to be zero-mean and white with a
+  standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
+
+  \TODO{put block diagram here}
+
+\subsection{Multisine Excitations}
+  To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
+  \begin{definition}[Generalized multisine] \label{def:generalized-MS}
+  A generalized multisine $u(t)$ is a signal consisting of $F$ sine waves with a different frequencies $f_k$, amplitudes $A_k$ and phase shifts $\phi_k$:
+  \begin{equation}
+    u \left( t\right) = \frac{1}{\sqrt{F}}
+   \sum_{k=1}^{F} 
+     A_k 
+     \sin 
+       \left(2\pi f_k t + \phi_k \right)
+  \text{.}
+  \label{eq:MultisineCT}
+  \end{equation}
+  For simplicity, one can stipulate that the frequency grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
+  \end{definition}
+
+  We limit ourselves, without loss of generality, to random phase multisines.
+  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
+  This leaves two sets of free parameters to create a signal that suits our needs:
+    the amplitude of the spectral lines $A_k$ and
+    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
+  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.
+
+  Consequently, the complete multisine has a period $T_{u(t)}$ that is the common multiple of the period of all its components:
+  \begin{equation}
+    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
+      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
+    \text{.}
+  \end{equation}
+  \begin{definition}[Least common (integer) multiple] \label{def:lcm-real}
+  The least common multiple of the set of values $T_k \in \RealNumbers$ for $k \in \set{1, \ldots, F}$ is  
+  \begin{equation}
+    \lcm \set{T_1, \ldots, T_F} \isdef
+      \min \set{T \given{\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }}
+   \end{equation}
+   if such a minimum exists.
+   \end{definition}
+  \begin{example}
+   Consider a generalized multisine where $f_1 = 1 \unit{Hz}$ and $f_2 = \tfrac{2}{3} \unit{Hz}$.
+   The corresponding periods are $T_1 = f_1^{-1} = 1 \unit{s}$ and $T_2 = f_2^{-1} = 1.5 \unit{s}$.
+   The overall period of the multisine is $T = n_1 T_1 = n_2 T_2 = 3 \unit{s}$, i.e. $n_1 = 3$ and $n_2=2$.
+  \end{example}
+
+  \begin{example}
+   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
+   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
+   Consequently, such a `multisine' is not periodic.
+  \end{example}
+
+  This last example illustrates that a least common multiple of real numbers does not always exist.
+  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
+
+  \TODO{put MATLAB code for each type of signal}
+
+\subsection{Equidistant (Linear) Grid Multisine}
+  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \citep{OppenheimDT,Mandal2007}.
+It allows to analyze periodic signals on an equidistant frequency grid very efficiently.
+
+  An equidistant frequency grid $\set{f_1, \ldots, f_F}$ with spacing $\Delta f$
+  consisting of $F$ lines conforms to the following relation:
+  \begin{equation}
+    f_k = k \Delta f + k_0 \Delta f
+    \emspace \forall k \in \set{1,\ldots,F},
+    \emspace k_0 \in \NN
+    \text{.}
+  \label{eq:linGrid}
+  \end{equation}
+
+  Using such linear grid, we can easily construct a representation of a multisine
+  in discrete time that is suited for use with the DFT by sampling at a given sampling rate $f_s$:
+  \begin{equation}
+     u \left[ n\right] = \frac{1}{\sqrt{F}}
+     \sum_{k=1}^{F} 
+       A_k 
+       \sin 
+         \left(\frac{2\pi n \left( k + k_0 \right) \Delta f}{f_s} + \phi_k \right)
+    \label{eq:MultiSineDT}
+  \end{equation}
+
+  Such an equidistant grid is a very common choice.
+  Note that it has more frequency lines per decade (or octave) at higher frequencies.
+  Therefore, the excitation power per octave is larger at higher frequencies
+  when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+  For a constant amplitude spectrum, this means the dynamics that are present at lower frequencies are plagued by a higher uncertainty than the ones located at higher frequencies.
+
+  Therefore a signal with an equidistant frequency grid is undesirable for
+  our situation as it wastes signal power at high frequencies at the cost of an increased variance in the lower side of the band.
+
+\subsection{(Ideal) Logarithmic Grid Multisine}
+  For a logarithmic frequency grid $\set{f_1, \ldots, f_F}$ of $F$ lines,
+  the following relation holds between excited frequencies:
+  \begin{equation}
+    f_k = \alpha \cdot f_{k-1}
+    \emspace \forall k \in \set{1,\ldots,F}
+  \label{eq:logGrid}
+  \end{equation}
+  for a given lowest frequency $f_0$ and frequency ratio $\alpha > 1$.
+
+  When designing an excitation signal, it is common only to specify a (large) frequency band
+  by its boundary frequencies $f_{\min}$ and $f_{\max}$.
+  For a given $\alpha$ it is easy to determine the number of excited lines
+  within the frequency range of interest:
+    \begin{equation}
+      F = \floor{
+                  \frac{\log{f_{\max}} - \log{f_{\min}}}
+                       {\log{\alpha}}
+                }
+    \label{eq:logms:F}
+    \end{equation}
+  where $\floor{\bullet}$ denotes rounding towards zero.
+  In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.
+
+  \TODO{link naar log meas mode DSA (e.g.
+HP3562A) leggen.
+Bij HP 3562A, is $F/\mathrm{decade} = 80$, oftewel $\alpha = \sqrt[80]{10} \approx 1.029$ vast ingesteld.
+Dit beperkt bruikbaarheid van zo'n toestel.}
+
+  \begin{property}
+   Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
+   \begin{equation}
+     F_{B}(f) \isdef
+     \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
+         = \floor{\log_{\alpha} \kappa}
+         \text{.}
+   \end{equation}
+   \end{property}
+  \begin{example}
+    For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
+  \end{example}
+
+   Obviously, the same argument can be held for any set of frequency bands with constant relative bandwidth (e.g. octave $\kappa = 2$).
+   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+
+  To return to the FRF, in Section~\ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
+  As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
+  bandwidth, one expects an equal variance for each system, as will be shown in Section~\ref{sec:bestFrequencyResolution}.
+
+  For that reason, a log multisine is a good candidate for our purposes.
+  However, it is more involved both to generate and to analyze such a signal, as the excited frequencies don't lie on a commensurate frequency grid.
+  Especially for periodic measurements, this is a major downside since the period of such signal does not always exist (i.e. this leads to infinite measurement times).
+  It is therefore not practical to use a perfectly logarithmically spaced frequency grid as the \gls{DFT} or \gls{CZT}~\citep{Rabiner2004} explicitly rely on a commensurate frequency grid.
+
+\subsection{Quasi-Logarithmic Grid Multisine}
+  Since most measurement equipment and analysis methods rely on signals with an equidistant frequency grid, we create a frequency grid
+  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:logGrid} is approximately  valid but with the strict constraint that the frequencies must be a subset  of an equidistant frequency grid. 
+  This yields the following relation for  subsequent frequency lines:
+  \begin{equation}
+    f_k \approx \alpha \cdot f_{k-1}
+    \emspace \forall k \in \set{1,\ldots,F}
+  \label{eq:qlogGrid}
+  \end{equation}
+  under the constraint that
+  \begin{equation}
+    f_k = N \cdot \Delta f,\; N \in \NN
+    \text{.}
+    \label{eq:constraintLinGrid}
+  \end{equation}
+  Such a grid is called a quasi-logarithmic (quasi-log) grid~\citep{Pintelon2012}.
+
+  \begin{remark}
+  When $\alpha \not\in \NaturalNumbers$, it is possible that at the low end of the frequency band, $\Delta f > \left(\alpha -1 \right) f_{k-1}$ for some integer values of $k$.
+  In such cases, the commensurate frequency grid is not dense enough to realize a frequency ratio $\alpha$.
+  Consequently, the power spectrum at these low frequencies will be less than the one of an ideal logarithmic frequency grid.
+  \end{remark}
+
+  \begin{definition}
+  The effective frequency ratio $\alpha_k$ of a frequency grid is
+  \begin{equation}
+    \alpha_k \isdef  \frac{f_k}{f_k-1}
+    \text{.}
+  \end{equation}
+  \end{definition}
+
+  \begin{remark}
+  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality  \label{eq:qlogGrid} does not define the grid unambiguously.
+  The quasi-logarithmic grids constructed in this chapter are constructed using the relationship
+  \begin{equation}
+    f_k = \alpha_k f_{k-1} 
+    \text{ with } 
+      \alpha_k \isdef 
+          \round{   \frac{\alpha f_{k-1}}{\Delta f}}    
+           \frac{\Delta f}{f_{k-1}}
+      \approx \alpha 
+      \emspace 
+          \forall k \in \set{1,\ldots,F}
+     \text{.}
+     \label{eq:excitation:qlog:round}
+  \end{equation}
+  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer as in the \MATLAB function \code{round}.
+  This satisfies the approximate definition.
+  \end{remark}
+
+  \begin{remark}
+  The use of different rounding strategies in \eqref{eq:excitation:qlog:round}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
+  By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
+  \begin{equation}
+  \alpha_k^{\floor{}} \leq \alpha \leq  \alpha_k^{\ceil{}}
+  \qquad \text{and} \qquad
+  \alpha_k^{\floor{}} \leq \alpha_k^{\round{}} \leq  \alpha_k^{\ceil{}}
+  \qquad
+  \forall k \in \set{1,\ldots,F}
+  \text{.}
+  \end{equation}
+  \end{remark}
+
+  As this signal approximates a logarithmically spaced signal,  we expect that it will exhibit comparable properties.
+  On the other hand, by imposing \eqref{eq:constraintLinGrid}, it remains
+  possible to use signal techniques which rely on a commensurate frequency grid.
+
+\subsection{Compensated Quasi-Logarithmic Grid Multisine}
+  The power density of the quasi-log multisine at the low frequencies is reduced in comparison to that of the logarithmic grid multisine.
+  This is due to the limited available frequency resolution.
+  To compensate for this loss in power spectral density (PSD), we can increase the amplitude spectrum $A_k$ at these lines.
+  Note that we are not able to restore the frequency resolution, only the power in a certain band is made equal to the power in the logarithmic multisine in the same band.
+
+  First of all, we need to determine the factor $A_k$ needed to correct the power spectrum to match that of a log grid multisine.
+  To this end, one first constructs a log frequency grid $\LOGGRID = \set{\f_1, \ldots, \f_{F'}}$ for a given factor $\alpha$ and the corresponding quasi-log grid $\QLOGGRID = \set{f_1, \ldots, f_F}$ for a resolution $\Delta f$.
+  For each frequency $f_k$ in the quasi-log grid, we define $n\left(f_k\right)$
+  as the number of frequencies in the log grid that are nearer to $f_k$
+  than to any other grid line in the quasi-log grid:
+
+  \begin{equation}
+    n\left(f_k\right) = \numberOf \mathrm{nearestLines}_{f_k}
+    \label{eq:nfk}
+  \end{equation}
+  \begin{equation}
+    \mathrm{nearestLines}_{f_k} =
+      \left\{ 
+        \f_l \given{\begin{aligned} 
+                       \f_l \in \LOGGRID, \\
+                       \norm{\f_l - f_k} < \norm{\f_l - f_{k'}},\\
+                       \forall k' \neq k: f_k, f_{k'} \in \QLOGGRID
+                    \end{aligned}}
+      \right\}
+    \label{eq:nearestLines}
+  \end{equation}
+
+  When approximating a log multisine with constant amplitude spectrum $A_{\mathrm{in}}$, we choose the amplitude spectrum of the compensated quasi-log multisine as follows
+  \begin{equation}
+    A_k = A_{\mathrm{in}} \cdot \sqrt{n\left(f_k\right)}\emspace \forall k \in \set{1,\ldots,F}
+  \text{.}
+  \label{eq:compensationAk}
+  \end{equation}
+  This effectively concentrates the total power of the $n\left( f_k \right)$ surrounding lines in the log grid multisine at the frequency $f_k$ in the compensated quasi-log multisine.
+
+  The power spectrum of this compensated signal approximates the one of the log grid multisine better than an uncompensated quasi-log grid.
+  As the power spectrum approximates the power spectrum of the log grid multisine, the uncertainty of the frequency response function will be approximately independent of the frequency within the measured frequency band.
+
+  \subsection{Pink Quasi-Logarithmic Multisine}
+  In \citep{Rojas2007} it is suggested that band-limited $1/f$ noise is a reasonable, albeit not optimal, robust excitation signal.
+
+  For $1/f$ noise (`pink noise'), the power spectral density $S(f)$ is proportional to $1/f$.
+  We can again approximate such a signal by means of a quasi-logarithmic grid multisine.
+  To do so, we construct a quasi-logarithmic frequency grid $\set{f_1,\ldots,f_k,\ldots,f_F}$ and determine the corresponding amplitude spectrum $A_k$ such that each excited line carries the same power as the corresponding frequency band does for pink noise.
+
+  This allows to define the amplitude spectrum $A_k$ as
+  \begin{equation}
+    A_k = A_{\mathrm{in}}
+                 \sqrt{\int_{\fMin{k}}
+                     ^{\fMax{k}}
+                     \limits
+                     \frac{1}
+                          {f}
+                     \,\dd{f}}
+          = A_{\mathrm{in}}
+                \cdot
+                \sqrt{
+                \ln \frac{\;\fMax{k}\;}{\fMin{k}}
+                }
+  \end{equation}
+  where $\left[ \fMin{k}, \fMax{k} \right] $ denote the frequency range over which PSD of the pink noise is to be approximated by the power at frequency line $f_k$.
+
+  To reduce the complexity of the expressions for $\fMin{k}$ and $\fMax{k}$, we extend the frequency grid by one component to the left and to the right by means of the grid relation (equations \eqref{eq:qlogGrid} and \eqref{eq:constraintLinGrid}) to obtain the grid $\set{f_0, f_1, \ldots, f_F, f_{F+1}}$.
+
+  Using this extension, the frequency range covered by $f_k$ can then be calculated as
+    \begin{align}
+      \fMin{k} &= \mean{f_{k-1}}{f_k}\\
+      \fMax{k} &= \mean{f_{k+1}}{f_k}
+    \label{eq:fRange}
+    \text{.}
+    \end{align}
+  This range can be seen as the power spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
+  Note that instead of the geometric mean, the arithmetic mean can be used in \eqref{eq:fRange} to calculate almost identical boundaries.
+
+  \subsection{Comparison of the frequency grids}
+  To gain some insight into these different grids, \figref{fig:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
+  For this example, a frequency spacing $\Delta f = 1\unit{Hz}$ and frequency ratio $\alpha = 1.05$ are used.
+
+  \begin{figure}[ht]
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/freqGrid.tikz}
+    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
+    \label{fig:freqGrids}
+  \end{figure}
+
+  \begin{table}
+  \centering
+   \caption{Summary of the different frequency grids.}
+    \begin{tabular}{lccc} 
+    Grid & Linear & Logarithmic & Quasi-logarithmic \\
+
+    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
+    Parameters & $f_0, \Delta f$ & $f_0, \alpha$ & $f_0, \Delta f, \alpha$ \\
+    $f_{k+1} \isdef$ & $f_{k} + \Delta f$ & $f_{k} \cdot \alpha$ & \ldots \\
+
+    \end{tabular}
+    \TODO{afmaken, booktabs}
+  \end{table}
+
+  \TODO{plot: $\alpha $ (evt. $\cdot A_k^2$) i.f.v. $\omega$ voor verschillende signalen.}
+  \TODO{plot: $\Delta f $ i.f.v. $\omega$ voor verschillende signalen} 
+  \TODO{plot: $\# \omega / \mathrm{decade}$ i.f.v. $\omega$ voor verschillende signalen}
+
+  At the lowest frequencies the quasi-log grid and the linear grid frequencies do coincide and each line in the quasi-log grid is surrounded by many lines of the log grid.
+  The amplitudes of the compensated and pink quasi-log lines show that the compensation only has effect at the lower frequencies since the uncompensated counterpart has an amplitude spectrum close to $1$.
+  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
+
+\section{Optimization of the frequency spacing} \label{sec:optimAlpha}
+  \subsection{Calculation of the model uncertainty}
+  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing factor $\alpha$, has not been designed for.
+  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
+  Doing so will allow to determine a suitable value for the frequency spacing $\alpha$.
+
+\TODO{zin loopt niet goed}
+  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
+  \begin{align}
+    \C_{G\left( \omega_{\interest}\right) } \approx
+      \InnerQuadraticForm[\HT]
+                         {\jac{\interest}}
+                         {\FisherInformation_{\theta}^{-1}}
+     \label{eq:varPeak}
+  \end{align}
+  with 
+  \begin{equation}
+    \FisherInformation_{\theta} =
+    2
+    \real{
+          \InnerQuadraticForm[\HT]
+                              {\jac{\excited}}
+                              {\C_{X}^{-1}}
+          }
+    \label{eq:FisherInfo}
+  \end{equation}
+  the Fisher information matrix \citep{Pintelon2012}.
+
+  In these expressions, the Jacobian $\jac{\interest}$ matrix of the transfer function evaluated at the frequency of interest $\omega_{\interest}$ with respect to the model parameters $\theta$ is defined as
+  \begin{equation}
+    \jac{\interest} \isdef
+         \PartialDerivative{G\left( \omega_{\interest}, \theta \right) }
+                           {\theta}
+    \text{.}
+  \end{equation}
+  Similarly, $\jac{\excited}$ is the Jacobian calculated at the excited frequency lines $\omega_{\excited} = \set{\omega_1, \ldots, \omega_F}$.
+
+  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
+  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
+  \begin{equation}
+    \C_{X} =
+               \left[ \left.
+               \begin{matrix}
+                 \frac{\sigma^2_E\left(\omega_1 \right) }
+                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
+                 0 & \ddots & 0 \\
+                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
+                              {\abs{U\left(\omega_F \right)}^2 }
+               \end{matrix}
+               \right.^{\vphantom{x}}\right]
+    \text{.}
+  \end{equation}
+
+  In this paper, we select a single frequency of interest $\omega_{\interest}$
+  to obtain a scalar performance measure.
+  This is allowed as the matrix $\C_{X}$ is diagonal.
+
+  \subsection{Relation between the frequency grid and the system resonance} \label{sec:relationLogGridSystem}
+  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated FRFs of a set of prototype second-order systems excited by logarithmically spaced excitation signals.
+
+  Define $G_{1}$ for a second-order system with resonance frequency $\wn$, damping $\damping$ and DC gain $\dc$.
+  Denote $G_m$ a second-order system with the same $\damping$ and $\dc$ but a resonance frequency of $m\wn$.
+  If one calculates their FRFs by evaluating \eqref{eq:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
+  Both FRFs share the same `shape', but are `located' at different frequencies.
+
+  Consider a logarithmic frequency grid with an infinite number of grid lines
+  \begin{equation}
+    \vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}
+    \label{eq:freqGridLog}
+    \text{.}
+  \end{equation}
+
+  Consider a second grid, defined as a multiple of this grid, $m\vec{\omega} = \set{m \cdot \alpha^k \omega_0 \given{k \in \ZN}}$; both grids share the same frequency ratio $\alpha$.
+
+  \TODO{formulate as lemmas, show steps}
+  It is easy to show that for $m = \alpha^N$ the following relation holds:
+  \begin{equation}
+    G_1\left( \vec{\omega} \right)
+    \stackrel{(a)}{=} G_{\alpha^N} \left( \alpha^N \vec{\omega} \right)
+    \stackrel{(b)}{=} G_{\alpha^N} \left( \vec{\omega} \right)
+    \label{eq:gridPeriodicity}
+  \end{equation}
+  since
+  \begin{itemize}
+   \item[(a)] the numerical values of the FRFs $G_1(\vec{\omega})$ and $G_m(m\vec{\omega})$ are equal and,
+   \item[(b)] the grids $\alpha^N \vec{\omega} = \set{\alpha^{k+N} \omega_0 \given{k \in \ZN}}$ and $\vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}$ coincide for integer values of $N$.
+  \end{itemize}
+
+  This shows that systems with equal $\damping$ and $\dc$ but resonance frequencies that differ by a factor $\alpha^N$, will share an identical `shape` of their response at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
+
+  Taking this into account allows to limit the study of second order systems to a small set of systems that should be considered in the search for a suitable grid spacing $\alpha$.
+  We can limit the evaluation of the theoretical uncertainty \eqref{eq:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
+  \begin{equation}
+    \wn \alpha^{N+\gamma}\qquad \text{ with } 0 \leq \gamma < 1\text{.}
+    \label{eq:theoreticalBestVariationOmega}
+  \end{equation}
+  The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
+  The value $N$ will not influence the `shape` (and uncertainty) of the FRF.
+
+  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test can be considered within the `bulk' of the frequency grid with finite support.
+  I.e. there should be a few excited frequency lines that are logarithmically spaced, outside of the resonance peak of the actual system.
+  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.
+
+  \subsection{Selection of the frequency grid spacing $\alpha$}
+  When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
+  Note that $\dc$ is a scaling factor for the FRF.
+  Hence the results for different values of $\dc$ only differ by a scaling factor.
+  So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.
+
+  The choice of the damping is more important.
+  Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:peakAmplitude} to study the effect of differently damped systems.
+
+  Since the damping influences the $3\unit{dB}$ bandwidths, it will become important when one has to determine the grid spacing $\alpha$.
+  To deal with this, we introduce the normalized frequency ratio
+  \begin{equation}
+    \tilde{\alpha} = \frac{\alpha - 1}
+                          {\damping}
+                   \propto \frac{\omega_{k+1} - \omega_k}
+                                {\wdB}
+                           \cdot
+                           \frac{\wn}{\omega_k}
+    \text{.}
+    \label{eq:normAlpha} 
+  \end{equation}
+  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
+  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
+  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:normAlpha} can safely be neglected.
+
+  To determine a suitable value of the frequency spacing ratio $\alpha$ for the logarithmic and (compensated) quasi-logarithmic grid, we construct a logarithmic multisine signal in the frequency domain for a given frequency band (in this example, $\left[ 0.01 \unit{rad/s}, 100 \unit{rad/s}\right]$ was used).
+  In the previous section we saw that systems with equal damping and DC gain, will behave very similarly when excited by a log signal with spacing $\alpha$.
+
+  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
+
+  \begin{figure}
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/misalign.tikz}
+    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
+    The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
+    \label{fig:misalignment-logms}
+  \end{figure}
+
+  We choose the resonance frequency of the systems such that
+  \begin{equation}
+   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
+   \text{ with } 0 \leq \beta < 1
+   \label{eq:chosenVariationOmega}
+  \end{equation}
+  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
+  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
+  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
+  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
+  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
+  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.
+
+  We normalize the root mean square (RMS) value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
+  The noise level is kept constant, which causes the signal-to-noise ratio (SNR) per excited line to drop for more finely spaced excitation signals.
+  % SNR correct: Pnoise ~ sE^2
+  %              Psignal ~F*U^2 = 1 ==> U^2 = 1/F
+  %              SNR = Psignal / Pnoise = 1/(sE^2 * F)
+  %          ==> SNR decreases as F increases
+
+  We then calculate the theoretical variance on the magnitude of the peak in the FRF ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:varPeak} for a coarse grid.
+  A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
+  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked by such an FRF.
+
+  For each set of second order systems, we determine for which value of the misalignment coefficient $\beta$ the maximum variance on the FRF is obtained.
+
+  For these worst cases, we study how the frequency spacing $\alpha$ influences the uncertainty by decreasing $\alpha$ until no further improvement can be obtained.
+
+  \subsection{Discussion} \label{sec:bestFrequencyResolution}
+  As stated above, we start by evaluating the variance $\sigma_G\left( \wM\right)$ for a coarse frequency spacing $\tilde{\alpha} = 10$ for each of the prototype systems.
+  This is shown by the solid lines in \figref{fig:worstCaseBeta}.
+  One immediately notices that the variance depends strongly on the misalignment $\beta$ of the system and the frequency grid.
+
+  \begin{figure}
+    \centering
+      \setlength\figureheight{5cm}
+      \setlength\figurewidth{0.65\columnwidth}
+    \input{\thisDir/figs/betaWC.tikz}
+    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
+             The full lines depict the variance for a coarsely spaced signal.
+             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:optimAlpha}).}
+    \label{fig:worstCaseBeta}
+  \end{figure}
+
+  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will entail a large increase in the uncertainty of estimate.
+
+  For a large peak amplitude of the FRF (low damping), the worst case increase (marked with a cross) is approximately centered around $\beta = 0.5$ (i.e. midway between the nearest excited lines).
+  In systems with a higher damping, this symmetry is lost.
+  This can be explained intuitively as the $3\unit{dB}$ bandwidth is less symmetric for highly damped systems than in lightly damped systems with a very narrow resonance peak.
+  Also note that the value of $\sigma_G\left(\wM \right)$ is practically identical for $\beta=0$ and $\beta=1$.
+  This is in accordance with the claim that in the bulk of the grid, a shift over an integer number of lines will only marginally influence the uncertainty.
+
+  We explore the systems which have the worst uncertainty (as marked by a cross in \figref{fig:worstCaseBeta}).
+  For the corresponding values of the misalignment $\beta$, we evaluate the uncertainty when the frequency ratio $\alpha$ of the signal is decreased, while the total signal power is kept identical.
+  The results are displayed in \figref{fig:worstCaseAlpha}, where the marked points correspond to the marked points in \figref{fig:worstCaseBeta}.
+
+  \begin{figure}[ht]
+    \centering
+      \setlength\figureheight{5cm}
+      \setlength\figurewidth{0.65\columnwidth}
+    \input{\thisDir/figs/alphaWC.tikz}
+    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
+             grid multisines and systems with different peak amplitudes.
+             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
+    \label{fig:worstCaseAlpha}
+  \end{figure}
+
+  We notice that for sufficiently low $\tilde{\alpha}$, the variance on $G\left( \omega_M \right)$ is roughly independent of $\alpha$.
+  We will choose the optimal grid spacing
+  \begin{equation}
+    \alpha^{\star} = 1 + \damping
+    \label{eq:optimAlpha}
+  \end{equation}
+  such that it represents the coarsest frequency spacing for which the variance is approximately equal to that constant value.
+  This choice is indicated by the dashed line in \figref{fig:worstCaseAlpha}.
+
+  Choosing a finer grid will not improve the estimated $G\left( \wM \right)$ significantly.
+  But, on the other hand, a coarser grid will significantly decrease the quality of the measurement.
+  A grid that is too coarse will overlook the resonance peak.
+  Hence little information can be extracted from such a measurement (i.e. the variance on the estimate will be large).
+
+  If we determine the effect of the misalignment factor $\beta$ for a grid with frequency ratio $\alpha^{\star}$, we see that misalignment has a negligible effect on the uncertainty as shown by the dashed lines in \figref{fig:worstCaseBeta} for each of the prototype systems.
+  Note that these values do indeed coincide with the limiting values found in \figref{fig:worstCaseAlpha}.
+
+  Now we can interpret \figref{fig:worstCaseBeta} in more detail.
+  We see that for $\beta \in \set{0,1}$ (i.e. perfect alignment), the variance of a course grid (full lines) is lower than it is for a fine grid (dashed lines).
+  This is to be expected as a coarse grid places more power at each individual line.
+  Thereby it yields a smaller variance at those lines.
+  It is better tailored to systems which are closely aligned to the excited frequency grid.
+  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance will increase significantly and very fast.
+  This effect is more important for lowly damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.
+
+  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the FRF of the system are visualized in \figref{fig:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
+  The $3\unit{dB}$ bandwidth of the system is highlighted in gray together with the excited frequency lines that lie within that bandwidth.
+
+  \begin{figure}%
+    \centering
+      \setlength\figureheight{4cm}
+      \setlength\figurewidth{0.7\columnwidth}
+    \input{\thisDir/figs/SignalAndSystem.tikz}
+    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$.
+The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
+    \label{fig:signalAndSystem}
+  \end{figure}
+
+  We see that to attain this, four frequency components are needed within this bandwidth in order to be almost completely independent of misalignment.
+
+  In this section, we have shown that signals with a logarithmic frequency spacing allow to identify systems with equal damping equally well, when the frequency spacing is dense enough.
+  Practically, four frequency lines in the $3\unit{dB}$ bandwidth of each second order subsystem suffice to suppress the effect of misalignment of such a subsystem and the frequency grid of the excitation signal.
+
+\section{Simulations} \label{sec:simulation}
+In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
+  \subsection{Setup}
+  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
+  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
+  These can be represented by a transfer function of the form:
+  \begin{equation}
+    G \left( z \right)\Big|_{\damping, \fR} =
+       \frac{         b_2  z^{2} + b_1 z + b_0}%
+            {\phantom{a_2} z^{2} + a_1 z + a_0}
+  \text{.}
+  \label{eq:secondOrderSystemDTidentifiable}
+  \end{equation}
+
+  This form can also be obtained by applying Tustin's method or bilinear transform \citep{Oppenheim1983} to the continuous time system \eqref{eq:secondOrderSystemCT}.
+
+  The input signal has an equidistant frequency grid with a resolution $\Delta f = 1\unit{Hz}$ between $1 \unit{Hz}$ and $16\,384\unit{Hz}$.
+  The sampling frequency $f_s$ is set to $65\,536\unit{Hz}$ to prevent aliasing.
+  For the quasi-log grid multisine, the compensated and pink quasi-log multisine, we chose a frequency ratio $\alpha = 1.05$.
+  According to \eqref{eq:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the FRF $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
+  Each of these signals is constructed to have an RMS value of $1$.
+  The amplitude spectra of these signals are displayed in \figref{fig:freqGrids} for identical signal power.
+
+  At the output of the systems, white Gaussian noise $e[n]$ is added such that its standard deviation is approximately $10\%$ of the RMS value of the output.
+
+  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT \citep{FDIDENT} for \matlab.
+  This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
+  To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
+
+  Such an experiment is repeated $R=1000$ times with a different random phase  spectrum $\phi_k$ and a different noise realization $e[n]$ for each experiment.
+
+  \subsection{Systems with a `high' damping}
+  To test the signals for systems with a high damping with respect to the frequency ratio in the excitation signal, systems with a damping $\damping = 0.2$ are used.
+  White Gaussian noise $e[n]$ with a standard deviation $\sigma_e \approx 0.0678$ added to the output.
+
+  The resulting frequency response function $\hat{G}$ for one such system is shown in \figref{fig:FRF1} together with the standard deviation $\sigma_{\hat{G}}$ of the estimated parametric model for each of the different excitation signals.
+  The bias is at least $20\unit{dB}$ smaller than the standard  deviation.
+  Therefore the mean squared error (MSE) will be determined mainly by the variance of the estimate instead of the bias.
+
+  \begin{figure}[th]
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/Sys02-4.tikz}
+    \caption[Simulated FRF and its variance for different excitation signals.]{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
+             along with the corresponding variance.}%
+    \label{fig:FRF1}
+  \end{figure}
+
+  \figref{fig:damping02} displays the estimated transfer functions and their uncertainty in the vicinity of their corresponding resonances for the whole set of considered systems.
+  Using this condensed representation and the displayed envelopes of the uncertainty, we can deduce the frequency-dependent behavior of the model variance obtained by the different excitation signals.
+
+  \begin{figure}%
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/damping02-cmp.tikz}
+    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{FRFs for different second order systems with constant damping
+             $\damping=0.2$ but different resonance frequencies. Comparison of the
+             variances around the respective resonance frequency for the different
+             excitation signals.}%
+    \label{fig:damping02}
+  \end{figure}
+
+  For the linear grid multisine, the uncertainty is strongly dependent on the frequency, and is proportional to $1/\fR$.
+  The uncertainty is generally higher than the uncertainty obtained with logarithmically spaced multisines, as the power has been divided over more excited lines.
+
+  The quasi-log multisine already shows a fairly flat uncertainty of about $-52 \unit{dB}$ at the higher frequency ranges.
+  Yet at the lowest frequencies, the $1/\fR$ dependence can be observed again.
+  This is caused by the linear distribution of excited frequencies in this range, as shown in \figref{fig:freqGrids}.
+
+  The compensated quasi-log multisine shows a more constant variance of about $-51 \unit{dB}$ even at these low frequencies.
+  As more power is placed at low frequencies, less power can be placed at the higher ones.
+  This causes a slightly increased variance compared to the regular quasi-log multisine.
+  At the studied system with the lowest resonance frequency, the compensation fails to completely compensate the effects of the reduced number of lines in the $3\unit{dB}$ bandwidth of that system.
+  Nevertheless an improvement of about $5\unit{dB}$ is obtained with respect to the regular quasi-log multisine.
+
+  \subsection{Systems with a lower damping}
+  Given the optimal frequency ratio \eqref{eq:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
+  In this set of simulations, we check this by repeating the previous set for such systems.
+  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the SNR of $20\unit{dB}$.
+  The corresponding results are shown in \figref{fig:damping005}.
+
+  \begin{figure}%
+    \centering
+    \setlength\figureheight{5cm}
+    \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/damping005-cmp.tikz}
+    \caption[Simulated FRFs and their variances of systems with $\damping=0.05$ for different excitation signals.]{FRFs for different second order systems with constant damping
+             $\damping=0.05$ but different resonance frequencies. Comparison of the
+             variances around the respective resonance frequency for the different
+             excitation signals.}%
+    \label{fig:damping005}
+  \end{figure}
+
+  At the higher frequency bands, an approximately constant quality is still obtained for the (compensated) quasi-logarithmic signals.
+  At lower frequencies, however, the logarithmically spaced signals perform only slightly better than the linearly spaced excitation signal.
+  This is due to the fact that as the damping $\damping$ decreases, the $3\unit{dB}$ bandwidth of the resonance decreases and therefore less points can be fitted in this bandwidth at the lower frequencies.
+  In our case, only $1$ line was excited in the $3 \unit{dB}$ bandwidth (respectively $0.4 \unit{Hz}$ and $0.8\unit{Hz}$ wide) of the systems with the lowest resonance frequencies.
+  It is clearly unfeasible to estimate the five parameters in
+  \eqref{eq:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
+  In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
+  We do see, however, that the variance in the vicinity of the resonance is lower than in the case of a linearly spaced excitation.
+
+  \subsection{Simulation example on higher order systems}
+To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:tf} in parallel.
+This is equivalent to adding their respective transfer functions, therefore, the resulting transfer function is of the form:
+\begin{equation}
+  G \left( z \right) 
+  = \frac{         b_4 z^{4} + b_3 z^{3} + b_2 z^{2} + b_1 z + b_0}%
+         {\phantom{a_4}z^{4} + a_3 z^{3} + a_2 z^{2} + a_1 z + a_0}
+  \text{.}
+\label{eq:tfO4}
+\end{equation}
+
+For example, a system composed of two second order systems with $\damping = 0.2$ and $\fR = 400 \unit{Hz}$ for the first system and $\fR=4 \unit{kHz}$ for the second system was simulated similarly to the previous examples.
+The standard deviation of the noise $\sigma_e$ was put at $0.0678$.
+The corresponding results are  shown in \figref{fig:sumSys}.
+
+\begin{figure}%
+  \centering
+  \setlength{\figurewidth}{0.8\columnwidth}
+  \setlength{\figureheight}{5cm}
+  \input{\thisDir/figs/Sum02log0-2.tikz}
+  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
+           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
+  \label{fig:sumSys}
+\end{figure}
+
+We observe that the amplitude of the transfer function is $9.8\unit{dB}$ and $8.1\unit{dB}$ at the resonant frequencies.
+The standard deviation on the \glspl{FRF} lies respectively $59.7 \unit{dB}$ and $59.6 \unit{dB}$ lower than the \gls{FRF} at these frequencies. 
+This shows that both resonances are captured with a practically identical relative error.
+
+\section{Measurements} \label{sec:measurement}
+  \subsection{Setup}
+    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.
+
+    The BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
+    According to its manual \citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
+    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
+    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
+    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.
+
+    As excitation signals, a linear grid multisine, an uncompensated quasi-log multisine and pink quasi-log multisine with excited frequencies between $1 \unit{Hz}$ and $64 \unit{kHz}$ were used.
+    These multisines were sampled at $\fs = 256\unit{kHz}$ and had a frequency resolution of $\Delta f = 1 \unit{Hz}$, a frequency spacing $\alpha = 1.05$ and identical RMS values of approximately $0.25 \unit{V}$.
+    This amplitude was chosen such that the peak amplitude $\max \abs{u(t)}$ was approximately $1 \unit{V}$.
+
+    $R=50$ periods of the multisine were measured, from which the first period was discarded to suppress transient effects.
+    For each of the remaining periods, the FRF of the filter is calculated and its average $G\left(\omega \right)$ over the periods is calculated.
+    We also calculate the corresponding standard deviation $\sigma_G\left( \omega \right)$ of the FRF and normalize it for a single period of the excitation signal.
+    We denote $G\left(\omega \right)$ the non-parametric FRF and $\sigma_G\left( \omega \right)$ its standard deviation, as these measures are determined completely nonparametrically from the measurements.
+
+    For the parametric model, on the other hand, a continuous time LTI model of the form
+    \begin{equation}
+      G(s) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
+    \end{equation}
+    was estimated using \texttt{elis} \citep{FDIDENT}.
+    The initial estimate was a third-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613}.
+
+    We summarize the behavior of these parametric models by their average $G\left(\theta,\omega \right)$ over the different periods and their standard deviation $\sigma_G\left(\theta,\omega \right)$.
+
+    \subsection{Results}
+    In \figref{fig:measurements} the nonparametric FRF and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.
+
+    \begin{figure}%
+    \centering
+      \setlength\figureheight{5cm}
+      \setlength\figurewidth{0.8\columnwidth}
+    \input{\thisDir/figs/qlog_a050mall.tikz}
+    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
+      \label{fig:measurements}
+    \end{figure}
+
+    The uncertainty $\sigma_G\left(\theta,\omega\right)$ on the parametric model in its pass-band is observed to be nearly constant for most of the filters when excited by the (pink) quasi-log multisine.
+    For the linear grid multisine excitation, $\sigma_G\left(\theta,\omega\right)$ in the pass-band is clearly decreasing proportional to $1 / f$ for the different octave filters.
+    One can see that the performance of both uncompensated quasi-log and pink quasi-log multisines is practically identical.
+    This can be explained by the fact that in this experiment, $f_0$ was chosen low enough to ensure that all the second-order subsystems had their $3\unit{dB}$ bandwidth within the bulk of logarithmic part of the excited grid.
+    This observation also shows that in this practical application, the increase in uncertainty between the uncompensated and compensated quasi-log multisines is negligible, as was observed earlier in the simulations.
+    However, if the system under test would have a lower resonance frequency, a quasi-log multisine with power compensation would perform better as was seen in the simulations.
 
@@
 \end{subappendices}
+
+\input{ch02-qlogms/sysid.tex}

### 2015-11-12 ch02-qlogms/sysid.tex
Include bib items from Larsson2012
Gebrol in intro/conclusie qLogMS
Beunen in excitation design

@@
 \item Iterative input design where the design updated as more information about the system is available, see e.g. \cite{Hjalmarsson2005,Gevers2005}.
-\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007a} and references therein. 
+\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007} and references therein. 
 \end{enumerate}
@@
 %
-%If $\lambda_i$ is the fraction of the input power at frequency $\omega_i$,
+%If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
 %then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
@@
 %                      \lambda_i^2
-%                      \alpha(\omega_i).
+%                      \alpha(\wn[i]).
 %\end{align}
@@
 %                            \lambda_i^2
-%                            \delta(\omega,\omega_i)
+%                            \delta(\omega,\wn[i])
 %\end{align}
@@
 %                        \lambda_i^2 
-%                        \delta(\omega,\omega_i)
+%                        \delta(\omega,\wn[i])
 %                    + \phi_u^{\robust}(\omega),\\
@@
 \begin{align}
-y_t &= G(s,\theta)=\frac{1}{\frac{s^2}{\omega_0^2} + 2\frac{\damping}{\omega_0}s + 1}u_t,
+y_t &= G(s,\theta)=\frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
 \label{eq:2ndOrderSys}
 \end{align}
-with parameters $\theta=[\omega_0\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\omega_0$
+with parameters $\theta=[\wn\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$
 and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wR$.
@@
 \begin{align}
-\omega^\star =\frac{\omega_0\left(\left(1-2\damping^2\right)+\left(\left(1-2\damping^2\right)^2+15\right)^{1/2}\right)^{1/2}}{\sqrt{5}}.
+\omega^\star =\frac%
+{\wn
+  \sqrt{
+    \left(1-2\damping^2\right)
+    +
+    \left(\left(1-2\damping^2\right)^2+15\right)^{1/2}
+    }
+  }
+{\sqrt{5}}.
 \label{eq:optFreq}
 \end{align}
-For systems with low damping, i.e $\damping\ll1$ , $\omega^\star\approx\omega_0$, which is inside the bandwidth of the system.
+For systems with low damping, i.e $\damping\ll1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
 From \eqref{eq:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
-Input design can be based on a guess of $\omega_0$, however if this guess is wrong, the resulting estimates may be unacceptable \citep{Rojas2007}.
+Input design can be based on a guess of $\wn$, however if this guess is wrong, the resulting estimates may be unacceptable~\citep{Rojas2007}.
 
@@
 This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2001}.
-We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\omega_0k_{min}\; \omega_0k_{max}]$, where the resolution is $k_0=1/T_{meas}$ and $T_{meas}$ is the measurement time.
+We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/T_{meas}$ and $T_{meas}$ is the measurement time.
 Hence, a finite measurement time limits the frequency resolution and therefore we have to put a lower limit on the frequency band of interest.
-Moreover, we can only impose the logarithmic distribution sufficiently well if $k_{min}$ is large enough.
+Moreover, we can only impose the logarithmic distribution sufficiently well if $\kMin$ is large enough.
 
@@
 \label{eq:pink}
-\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\omega_0k_{min}\; \omega_0k_{max}]$,}\\
+\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
                         0           &\text{otherwise}.
@@
   \frac{1}{2\pi}
-    \int\limits_{(1-\damping)\wR}^{(1+\damping)\wR}
+    \int\limits_{(1-\damping)\wn}^{(1+\damping)\wn}
      \frac{1}{\omega} \dd{\omega}
@@
 \end{align}
-which is independent of $\omega_0$. The robustness of the $1/f$ input has been noted previously in e.g. \cite{Rojas2007}
+which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously in e.g. \cite{Rojas2007}
 
@@
 \begin{align}
-  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\omega_k)},
+  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
 \end{align}
@@
 \end{align}
-where $\lfloor\cdot\rfloor$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\omega_0$.
+where $\lfloor\cdot\rfloor$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
 
@@
 
-The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\omega_0$. 
+The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
 This is illustrated in Section~\ref{sec:sim}.
@@
              =\sum_{i=1}^{K}  \frac{1}
-                                   {   \frac{s^2}{\omega_i^2}
-                                    + 2\frac{\damping_i}{\omega_i}s
+                                   {   \frac{s^2}{\wn[i]^2}
+                                    + 2\frac{\damping_i}{\wn[i]}s
                                     + 1},\\
-\theta_i&=[\omega_i\;\damping_i]^{\T}.
+\theta_i&=[\wn[i]\;\damping_i]^{\T}.
 \label{eq:sumSys}
@@
 The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
-With loss of generality, we assume that $\omega_1 < \omega_2 < \cdots < \omega_K$.
-To properly identify the system $G$, excitation is required such that all
-subsystems are properly excited, regardless of their individual resonance frequencies.
+Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
+To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
 
@@
 G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
-%&=\frac{1}{\frac{s^2}{\omega_1^2} + 2\frac{\damping_1}{\omega_1}s + 1} + \frac{1}{\frac{s^2}{\omega_2^2} + 2\frac{\damping_2}{\omega_2}s + 1},
+%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping_1}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping_2}{\wn[2]}s + 1},
 \end{align}
-with $\theta_1=[\omega_1\;\damping_1]^{\T}$ and $\theta_2=[\omega_2\;\damping_2]^{\T}$.
+with $\theta_1=[\wn[1]\;\damping_1]^{\T}$ and $\theta_2=[\wn[2]\;\damping_2]^{\T}$.
 The information matrix for this system is
@@
 \label{eq:auto}
-\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_1^{\HT}}{\partial \omega_1}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\omega_1^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
+\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
 \end{align}
@@
 % \begin{align}
-% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
-% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
-% &\int_0^\infty\left|\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
+% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
+% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
+% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
 % \end{align}
 \begin{gather}
-\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\frac{1}{\omega}\dd\omega\right|
+\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
 \qquad \qquad \qquad \qquad \qquad
@@
 \leq
-\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right\}\right|\frac{1}{\omega}\dd\omega
+\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
 \leq \\
 \qquad \qquad \qquad \qquad \qquad
-\int_0^\infty\left|\frac{\partial G_1}{\partial \omega_1}\frac{\partial G_2^{\HT}}{\partial \omega_2}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
+\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
 \end{gather}
@@
 \begin{align}
-\frac{\partial G_1}{\partial \omega_1} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\omega_1\damping}\right]}{\omega_1^2\left[1+2\frac{\damping j\omega}{\omega_1} + \left(\frac{j\omega}{\omega_1}\right)^2\right]^2},
+\frac{\partial G_1}{\partial \wn[1]} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}{\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
 \end{align}
-which has zeros in $j\omega=\left\{0, \damping\omega_1\right\}$.
-Hence $\left|\frac{\partial G_1}{\partial \omega_1} \right|$ has asymptotical slope 20\unit{\frac{dB}{dec.}} for low frequencies, at $j\omega=\damping\omega_1$ the slope increases to 40\unit{\frac{dB}{dec.}}.
-There are four poles which give a $-40$\unit{\frac{dB}{dec.}} roll-off after the peak.
-The shape of $\frac{\partial G_1}{\partial \omega_1} $ is illustrated in Fig.~\ref{fig:dG}.
+which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
+Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}.
+There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak.
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in Fig.~\ref{fig:dG}.
 
@@
   \begin{cases}
-   \frac{\omega^2}{\omega_1^2}
+   \frac{\omega^2}{\wn[1]^2}
    \frac{1}{\omega}
    \partial G_1^\infty
-                                       & \text{if $\omega \leq \omega_1$,}\\
+                                       & \text{if $\omega \leq \wn[1]$,}\\
    \phantom{\frac{\omega^2}{\omega^2}}
@@
    \partial G_1^\infty
-                                       & \text{if $\omega_1 < \omega < \omega_2$,}\\
-   \frac{\omega_2^2}{\omega^2}
+                                       & \text{if $\wn[1] < \omega < \wn[2]$,}\\
+   \frac{\wn[2]^2}{\omega^2}
    \frac{1}{\omega}
    \partial G_1^\infty
-                                       & \text{if $\omega \geq \omega_2$,}
+                                       & \text{if $\omega \geq \wn[2]$,}
   \end{cases}
 \end{align}
-where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \omega_1}\right\|_\infty$. Again, direct calculations give
+where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
+Again, direct calculations give
 \begin{align}
-\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\omega_1\left(2-\ln{\frac{\omega_1^2}{\omega_2^2}}\right)}{\omega_2^2}\damping^{-2} + \mathcal{O}(1).
+\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
 \end{align}
@@
 \begin{itemize}
-\item the integral \eqref{eq:cross1} decreases as $\omega_2-\omega_1$ increases, and
+\item the integral \eqref{eq:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
 \item lower damping further decreases the integral \eqref{eq:cross1} in comparison to \eqref{eq:auto}.
@@
 \input{\thisDir/figs/rolloff.tikz}
-\caption{The shape of $\frac{\partial G_1}{\partial \omega_1}$. The roll-off around the peak is significant and depends on the damping of the system.}
+\caption{The shape of $\frac{\partial G_1}{\partial \wn[1]}$. The roll-off around the peak is significant and depends on the damping of the system.}
 \label{fig:dG}
@@
 
-To further illustrate the decoupling of the two systems, we calculate \eqref{eq:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\omega_1$ and $\omega_2$.
-If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\omega_1-\omega_2$ and not on the actual frequencies.
+To further illustrate the decoupling of the two systems, we calculate \eqref{eq:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
+If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
 The resulting information matrix is then normalized so that the largest element is $1$.
@@
            along with its variance and bias.}%
+           \TODO{reproduce figure with ALL excitation signals}
   \label{fig:FRF1}
@@
 
-\subsection{Simulation example on higher order systems}
-To show that the suggested method also works on more general systems,
-we considered a system that consists of two second order systems \eqref{eq:tf} in 
-parallel. This is equivalent to adding their respective transfer functions,
-therefore, the resulting transfer function is of the form:
-\begin{equation}
-  G \left( z \right) 
-  = \frac{         b_4 z^{4} + b_3 z^{3} + b_2 z^{2} + b_1 z + b_0}%
-         {\phantom{a_4}z^{4} + a_3 z^{3} + a_2 z^{2} + a_1 z + a_0}
-  \text{.}
-\label{eq:tfO4}
-\end{equation}
-
-For example, a system composed of two second order systems with $\damping = 0.2$
-and $\fR = 400 \unit{Hz}$ for the first system and $\fR=4 \unit{kHz}$ for the second
-system was simulated similarly to the previous examples. The standard deviation
-of the noise $\sigma_e$ was put at $0.0678$. The corresponding results are 
-shown in \figref{fig:sumSys}.
-
-\begin{figure}%
-  \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
-  \setlength{\figureheight}{5cm}
-  \input{\thisDir/figs/Sum02log0-2.tikz}
-  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
-           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
-  \label{fig:sumSys}
-\end{figure}
-
-We observe that the amplitude of the FRF is $9.8\unit{dB}$ and $8.1\unit{dB}$ at the resonant frequencies.
-The standard deviation on the FRF lies respectively $59.7 \unit{dB}$ and $59.6 \unit{dB}$ lower than the FRF at these frequencies. 
-This shows that both resonances are captured with a practically identical error.
-
 \subsection{Conclusion}

### 2015-11-13 ch02-qlogms/excitation-design.tex
Finished table on MS excitation

@@
   \begin{equation}
-    \alpha_k \isdef  \frac{f_k}{f_k-1}
+    \alpha_k \isdef  \frac{f_k}{f_{k-1}}
     \text{.}
@@
 
-  \begin{remark}
-  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality  \label{eq:qlogGrid} does not define the grid unambiguously.
-  The quasi-logarithmic grids constructed in this chapter are constructed using the relationship
-  \begin{equation}
-    f_k = \alpha_k f_{k-1} 
-    \text{ with } 
-      \alpha_k \isdef 
-          \round{   \frac{\alpha f_{k-1}}{\Delta f}}    
+  \begin{definition}
+  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality \eqref{eq:qlogGrid} does not define the grid unambiguously.
+  The quasi-logarithmic grids depicted in this chapter are constructed using the relationship
+  \begin{align}
+       \label{eq:excitation:qlog:gridDef}
+    f_k & = \alpha_k(N_k) f_{k-1}  
+        \quad
+            \forall k \in \set{1,\ldots,F}
+\end{align}
+with
+\begin{align}
+     \label{eq:excitation:qlog:roundAlpha}
+      \alpha_k(N_k) & \isdef 
+          \round{   \frac{\alpha^{N_k} f_{k-1}}{\Delta f}}    
            \frac{\Delta f}{f_{k-1}}
-      \approx \alpha 
-      \emspace 
-          \forall k \in \set{1,\ldots,F}
+      \approx \alpha \text{, and}\\
+         \label{eq:excitation:qlog:alphaPowerDef}
+          N_k & \isdef 
+            \min 
+            \set{n | n \in \NaturalNumbers, \alpha_k(n) > 1}
      \text{.}
-     \label{eq:excitation:qlog:round}
-  \end{equation}
-  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer as in the \MATLAB function \code{round}.
+  \end{align}
+  \end{definition}
+  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer according to the \IEEEfloat standards and as implemented in the \MATLAB function \code{round}.
   This satisfies the approximate definition.
-  \end{remark}
 
   \begin{remark}
-  The use of different rounding strategies in \eqref{eq:excitation:qlog:round}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
+  The use of different rounding strategies in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
   By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
@@
   \centering
-   \caption{Summary of the different frequency grids.}
-    \begin{tabular}{lccc} 
+   \caption{Summary of  properties of the different frequency grids.}
+    \begin{tabular}{rccc} 
+    \toprule
     Grid & Linear & Logarithmic & Quasi-logarithmic \\
+    \midrule
+    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
+    Properties 
+       & $f_0, \Delta f$ 
+       & $f_0, \alpha$ 
+       & $f_0, \Delta f, \alpha$\\
+    \midrule
+    $f_{k+1} \isdef$ 
+       & $f_{k} + \Delta f$ 
+       & $\alpha f_{k}$ 
+       & $\round{\frac{\alpha f_k}{\Delta f}} \Delta f$\\[5pt]
+    $\Delta f_k \isdef f_{k+1} - f_k$ 
+       & $\Delta f$
+       & $(\alpha - 1) f_k$
+       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
+    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
+       & $1 + \frac{\Delta f}{f_k}$ 
+       & $\alpha$ 
+       & $\approx \alpha $ \\[5pt]
+    $F_{\ClosedInterval{a,b}}$
+       & $\floor{\frac{b - a}{\Delta f}}$
+       & $\floor{\log_{\alpha} \frac{b}{a}}$
+       & \ldots\\[5pt]
+    $F_{\ClosedInterval{f, \kappa f}}$
+      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
+      & $\floor{\log_{\alpha} \kappa}$
+      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
+    \bottomrule
+    \end{tabular}
 
-    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
-    Parameters & $f_0, \Delta f$ & $f_0, \alpha$ & $f_0, \Delta f, \alpha$ \\
-    $f_{k+1} \isdef$ & $f_{k} + \Delta f$ & $f_{k} \cdot \alpha$ & \ldots \\
-
-    \end{tabular}
-    \TODO{afmaken, booktabs}
+    \TODO{afmaken}
   \end{table}

### 2015-11-13 ch02-qlogms/excitation-design.tex
Quite some work on ch02

@@
        & $\alpha f_{k}$
-       & $\round{\frac{\alpha f_k}{\Delta f}} \Delta f$\\[5pt]
+       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
+       \\[5pt]
     $\Delta f_k \isdef f_{k+1} - f_k$ 
@@
        & $\floor{\log_{\alpha} \frac{b}{a}}$
-       & \ldots\\[5pt]
+       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
     $F_{\ClosedInterval{f, \kappa f}}$
@@
       & $\floor{\log_{\alpha} \kappa}$
-      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
+      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
     \bottomrule
     \end{tabular}
-
-    \TODO{afmaken}
   \end{table}
+  \TODO{tabel: verschillende signalen: power per BW}
 
@@
   \subsection{Calculation of the model uncertainty}
-  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing factor $\alpha$, has not been designed for.
+  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing $\alpha$, has not been designed.
+
   In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
-  Doing so will allow to determine a suitable value for the frequency spacing $\alpha$.
+  Doing so allows to determine a suitable value for the frequency spacing $\alpha$.
 

### 2015-11-13 ch02-qlogms/sysid.tex
Quite some work on ch02

@@
 There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak.
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in Fig.~\ref{fig:dG}.
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:dG}.
 
@@
 
-In Fig.~\ref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
+In \figref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
 It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling.

### 2015-11-16 ch02-qlogms/excitation-design.tex
Quite some changes to CH02

@@
 Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
-In many cases
 
@@
 \label{sec:excitation:intro:generic}
+%TODO
 
@@
 Since generic excitation signals are not specifically geared towards the particular system under test, such signals tend to waste signal power.
+
+%TODO
 
@@
 As illustrated above, optimal experiment design places the user in a catch-22 situation.
+In the recent years, this has sparked attention towards robust signal design~\citep{Rojas2007} to alleviate the drawbacks of (nominal) optimal experiment design.
+%TODO
 
@@
 In this chapter, the goal is to construct excitation signals that bridge the properties of generic and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
-In particular, a generic excitation signal will be used but its properties are tuned in such a way that it
+In particular, a generic excitation signal will be used but its properties are tuned in such a way that it attains some properties of robust excitation signals without the requirement of very specific prior information.
 
@@
   \subsection{The system under consideration}
-  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_a\times n_b$:
+  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_b / n_a$:
   \begin{align}
@@
   Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
+  \TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
+\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter.
+This will be well-approximated by considering only the second order system of the paper.}
+
+  Within these sub-systems, we can distinguish first-order subsystems and second-order subsystems, the latter of which describe resonant phenomena.
+  Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
+  Afterwards, it will become obvious that
 
@@
   \end{equation}
-\TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
-\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter.
-This will be well-approximated by considering only the second order system of the paper.}
 
@@
 \subsection{System and noise model}
-  In this paper, an output error (OE) system setup is used.
+  In this chapter, an output error (OE) system setup is used.
   Denote
@@
     $E  \left(\omega\right)$ for the output noise source,
-    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal.
+    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
+
+  \begin{figure}
+    \centering
+    \input{\thisDir/figs/oesetup.tikz}
+    \caption[Output-error]{Output-error set-up.}
+  \end{figure}
 
@@
     \lcm \set{T_1, \ldots, T_F} \isdef
-      \min \set{T \given{\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }}
+      \min \Set{T |\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }
    \end{equation}
@@
 
-  \TODO{link naar log meas mode DSA (e.g.
-HP3562A) leggen.
-Bij HP 3562A, is $F/\mathrm{decade} = 80$, oftewel $\alpha = \sqrt[80]{10} \approx 1.029$ vast ingesteld.
-Dit beperkt bruikbaarheid van zo'n toestel.}
+  \begin{remark}
+    In different contexts, e.g.
+electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
+  \end{remark}
 
@@
     For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
+  \end{example}
+  \begin{example}
+    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
+    This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
   \end{example}
@@
     \end{align}
-  This range can be seen as the power spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
+  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
+
   Note that instead of the geometric mean, the arithmetic mean can be used in \eqref{eq:fRange} to calculate almost identical boundaries.
@@
 
-  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT \citep{FDIDENT} for \matlab.
+  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT~\citep{FDIDENT} for \MATLAB.
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
+  \TODO{add formulas with cost function etc.}
   To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
@@
   Such an experiment is repeated $R=1000$ times with a different random phase  spectrum $\phi_k$ and a different noise realization $e[n]$ for each experiment.
+
+  \begin{remark}
+  All simulations  have been repeated fitted with the \MATLAB System Identification Toolbox by means of the \code{oe} function~\citep{TDIDENT}.
+  The observed results were identical and hence are not elaborated further in this text.
+  \end{remark}
 
@@
   The bias is at least $20\unit{dB}$ smaller than the standard  deviation.
-  Therefore the mean squared error (MSE) will be determined mainly by the variance of the estimate instead of the bias.
+  Therefore the \gls{MSE} will be determined mainly by the variance of the estimate instead of the bias.
 
@@
     \caption[Simulated FRF and its variance for different excitation signals.]{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
-             along with the corresponding variance.}%
+             along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
     \label{fig:FRF1}
@@
   \section{Justification for considering only poles}
-
+  \TODO{benadering van 1/2 systeem a.d.h.v.
+0/2 systeem wanneer $\omega_z << \wn$ (of $\omega_z >> \wn)$: rond de resonantie zijn beiden ongeveer gelijk.
+Afgeleide naar de nul zijn klein rond de resonantie.
+Informatiematrix is langs twee kanten gewogen met die afgeleide, dus die nul maakt weinig uit.}
 \end{subappendices}

### 2015-11-16 ch02-qlogms/sysid.tex
Quite some changes to CH02

@@
 However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance.
-It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2001}.
+It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}.
 This gives
@@
 \begin{align}
-y_t &= G(s,\theta)=\frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
+y_t &= G(s,\theta) u_t = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
 \label{eq:2ndOrderSys}
@@
 with parameters $\theta=[\wn\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$
-and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wR$.
+and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
 Since information is local in the frequency domain, the input signal power inside $\wdB$, contributes significantly to the information matrix while input power outside $\wdB$ has a smaller contribution.
 This can be seen by considering the optimal design for a second order system.
-From \citep{Goodwin1977} we have that the D-optimal design for \eqref{eq:2ndOrderSys} is a single sinusoid at frequency
+From \citep[Example 6.4.5]{Goodwin1977} we have that the D-optimal design for \eqref{eq:2ndOrderSys} is a single sinusoid at frequency
 \begin{align}
@@
     +
-    \left(\left(1-2\damping^2\right)^2+15\right)^{1/2}
+    \sqrt{\left(1-2\damping^2\right)^2+15}
     }
@@
 \end{align}
-For systems with low damping, i.e $\damping\ll1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
+For lightly-damped systems, i.e $\damping \ll 1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
 From \eqref{eq:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
@@
 When no information about the system is available, we propose using an input power spectrum with a logarithmic power distribution.
-This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2001}.
-We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/T_{meas}$ and $T_{meas}$ is the measurement time.
+This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2012}.
+We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/\Tm$ and $\Tm$ is the measurement time.
 Hence, a finite measurement time limits the frequency resolution and therefore we have to put a lower limit on the frequency band of interest.
@@
 
-Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2001}] given by
+Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
 \begin{align}
@@
 \end{align}
-where $\omega_{k}/\omega_{k+1} \approx \alpha_{f} = e^{\Delta}$.
+where $\omega_{k}/\omega_{k+1} \approx \alpha = e^{\Delta}$.
 Hence, the number of spectral lines inside \wdB is 
 \begin{align}
-\left\lfloor\ln{\left[\frac{1+\damping}{1-\damping}\right]}\Delta^{-1}\right\rfloor,
+  \floor{
+    \log_{\alpha} \frac{1+\damping}{1-\damping} 
+  }
+  \text{,}
 \end{align}
-where $\lfloor\cdot\rfloor$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
+where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
 
@@
 
-To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha_f$.
+To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha$.
 
@@
 
-For the quasi-log excitation, a frequency ratio of $\alpha_f = 1.05$ was chosen
+For the quasi-log excitation, a frequency ratio of $\alpha = 1.05$ was chosen
 and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
@@
 
-The desired frequency ratio $\alpha_f$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
+The desired frequency ratio $\alpha$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
 This causes a less dense coverage of the lowest frequency bands.

### 2015-11-16 ch02-qlogms/excitation-design.tex
Lemmaified ch02

@@
   This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
+  Consequently,
 
@@
 
-  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
+  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the \gls{CRLB}.
   Doing so allows to determine a suitable value for the frequency spacing $\alpha$.
@@
   \subsection{Relation between the frequency grid and the system resonance} \label{sec:relationLogGridSystem}
-  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated FRFs of a set of prototype second-order systems excited by logarithmically spaced excitation signals.
+  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated \glspl{FRF} of a set of prototype second-order systems excited by logarithmically spaced excitation signals.
 
-  Define $G_{1}$ for a second-order system with resonance frequency $\wn$, damping $\damping$ and DC gain $\dc$.
-  Denote $G_m$ a second-order system with the same $\damping$ and $\dc$ but a resonance frequency of $m\wn$.
+  \paragraph{Simplification}
+  Instead of studying the response of all possible second-order sub-systems for every possible logarithmically spaced multisine-- a five-dimensional problem with parameters $\omega_0, \alpha, \wn, \damping, \dc$-- we argue in favor for a simplification of the problem by considering infinite frequency grids.
+
+  Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
+  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order system that shares the damping and \gls{DC} gain of the previous system but has a natural frequency $m\wn$.
+
   If one calculates their FRFs by evaluating \eqref{eq:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
@@
 
-  Consider a logarithmic frequency grid with an infinite number of grid lines
+  Denote $\infgrid{\omega}$ to be a logarithmic frequency grid with an infinite number of grid lines
   \begin{equation}
-    \vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}
+    \infgrid{\omega} \isdef \Set{\alpha^k \omega_0 | k \in \ZN}
     \label{eq:freqGridLog}
+  \end{equation}
+  and consequently an infinite span.
+  We can define a second grid as the $m$-fold multiple (with $m \in \RealNumbersWithoutZero$) of this grid and denote it $m\infgrid{\omega}$:
+  \begin{equation}
+    m \infgrid{\omega} \isdef \Set{m \alpha^k \omega_0 | k \in \ZN}
     \text{.}
   \end{equation}
+  Both $\infgrid{\omega}$ and $m\infgrid{\omega}$ share the frequency ratio $\alpha$.
+  \begin{remark} \label{rem:exc:gridscaling}
+    For $N \in \ZN$ it is obvious that $\infgrid{\omega} = \alpha^{N} \infgrid{\omega}$, i.e. both grids coincide.
+  \end{remark}
 
-  Consider a second grid, defined as a multiple of this grid, $m\vec{\omega} = \set{m \cdot \alpha^k \omega_0 \given{k \in \ZN}}$; both grids share the same frequency ratio $\alpha$.
+  \begin{definition}
+  To evaluate a function $G$ over the grid $\infgrid{\omega}$ with infinite span, let us introduce the shorthand notation $G(\infgrid{\omega})$ to mean $\set{G(\omega) | \omega \in \infgrid{\omega}}$.
+  \end{definition}
 
-  \TODO{formulate as lemmas, show steps}
-  It is easy to show that for $m = \alpha^N$ the following relation holds:
+  \begin{lemma} \label{lem:exc:sysscaling}
+  Consider the second-order systems $G(\omega; \wn)$ and $G(\omega; m\wn)$ with $m \in \RealNumbersWithoutZero$. 
+  For a frequency grid $\infgrid{\omega}$ with infinite span, it can be shown that $G(\infgrid{\omega}; \wn) = G(m \infgrid{\omega}; m\wn)$.
+  \end{lemma}
+  \begin{proof}
+  Pick any $\omega_{\star} \in \infgrid{\omega}$. The frequency $m\omega_{\star}$ is then by definition an element of the grid $m\infgrid{\omega}$.
+  Substituting $\omega = \omega_{\star}$ and $\omega = m \omega_{\star}$  into  $G(\omega; \wn)$ and $G(m\omega; m\wn)$  respectively, directly yields
   \begin{equation}
-    G_1\left( \vec{\omega} \right)
-    \stackrel{(a)}{=} G_{\alpha^N} \left( \alpha^N \vec{\omega} \right)
-    \stackrel{(b)}{=} G_{\alpha^N} \left( \vec{\omega} \right)
-    \label{eq:gridPeriodicity}
+    \frac{\dc}{- \omega_{\star}^2 \wn^{-2} + 2j\damping \omega_{\star} \wn^{-1} + 1} = 
+    \frac{\dc}{- (m\omega_{\star})^2 (m\wn)^{-2} + 2j\damping (m\omega_{\star}) (m\wn)^{-1} + 1}
+    \text{.}
   \end{equation}
-  since
-  \begin{itemize}
-   \item[(a)] the numerical values of the FRFs $G_1(\vec{\omega})$ and $G_m(m\vec{\omega})$ are equal and,
-   \item[(b)] the grids $\alpha^N \vec{\omega} = \set{\alpha^{k+N} \omega_0 \given{k \in \ZN}}$ and $\vec{\omega} = \set{\alpha^k \omega_0 \given{k \in \ZN}}$ coincide for integer values of $N$.
-  \end{itemize}
+  Since all the factors ``$m$'' cancel in the equation above, this proves the stated.
+  \end{proof}
 
-  This shows that systems with equal $\damping$ and $\dc$ but resonance frequencies that differ by a factor $\alpha^N$, will share an identical `shape` of their response at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
+  \begin{theorem}
+    Second-order  systems with equal damping $\damping$ and \gls{DC} gain $\dc$ but resonance frequencies that differ by a factor $\alpha^N$ with $N \in \IntegerNumbers$, share an identical `shape` of their \gls{FRF} at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
+    Or, formally: $G(\infgrid{\omega};\wn) = G(\infgrid{\omega}; \alpha^{N}\wn) \forall N \in \NaturalNumbers$.
+  \end{theorem}
+  \begin{proof}
+    This is an immediate consequence from Lemma~\ref{lem:exc:sysscaling} for $m= \alpha^{N}$ and Remark~\ref{rem:exc:gridscaling}.
+  \end{proof}
 
@@
   The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
-  The value $N$ will not influence the `shape` (and uncertainty) of the FRF.
+  The value of $N$ will not influence the `shape` (and uncertainty) of the FRF.
 
   The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test can be considered within the `bulk' of the frequency grid with finite support.
+  \TODO{more rigorous explanation why this is the case}
   I.e. there should be a few excited frequency lines that are logarithmically spaced, outside of the resonance peak of the actual system.
@@
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
-  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked by such an FRF.
+  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked in such an FRF.
 

### 2015-11-16 ch02-qlogms/sysid.tex
Lemmaified ch02

@@
 
-For each of these simulations, the system was identified by means of the \texttt{oe}
-function in the \matlab\ System Identification Toolbox\Cite{TDIDENT}.
-To prevent convergence issues, we used the true model parameters
-$\left\{ a_0, a_1, b_0, b_1, b_2 \right\}$ and model structure
-as mentioned in \eqref{eq:tf} as starting values.
-This increases the probability of the search converging to the global minimum, which
-allowed to focus on the real quantity of interest: the variance of the FRF.
-
 \subsection{Results for a single system}

### 2015-11-16 ch02-qlogms/excitation-design.tex
Remove quite some duplicae sections

@@
 \label{sec:excitation:intro:generic}
-%TODO
+\TODO{\ldots}
 
@@
 \label{sec:excitation:intro:optimal}
-Since generic excitation signals are not specifically geared towards the particular system under test, such signals tend to waste signal power.
-
-%TODO
-
-, such signals essentially don't use all the available signal power to reduce the uncertainty in the estimate.
+Since generic excitation signals are not specifically geared towards the particular system under test, such signals use signal power in an inefficient way that does not reduce the variance of the model estimate significantly.
+\TODO{\ldots}
 
@@
   \end{table}
-  \TODO{tabel: verschillende signalen: power per BW}
 
@@
            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
+           \TODO{also with other excitation signals?}
   \label{fig:sumSys}

### 2015-11-16 ch02-qlogms/sysid.tex
Remove quite some duplicae sections

@@
 
-\section{Simulations}\label{sec:sim}
-We considered a linear second order system that is to be identified, with the
-only prior knowledge that its resonance frequency $\fR$ lies in a known
-frequency band that may span several decades. 
-Our goal is to identify such a system by means of a single excitation signal, 
-such that the frequency response function (FRF) of the second order systems that are
-equally damped are identified with the same uncertainty near their resonance.
+% \section{Simulations}\label{sec:sim}
+% We considered a linear second order system that is to be identified, with the
+% only prior knowledge that its resonance frequency $\fR$ lies in a known
+% frequency band that may span several decades. 
+% Our goal is to identify such a system by means of a single excitation signal, 
+% such that the frequency response function (FRF) of the second order systems that are
+% equally damped are identified with the same uncertainty near their resonance.
 
-\subsection{Excitation}
-To excite the system under test, we used quasi-logarithmic (quasi-log) random-phase multisines. 
-Their phase spectrum $\psi_{k}$ is the result of a uniform random process over $[0,2\pi[$.
-A logarithmic spacing of the frequency components causes each decade within the band of interest to contain the same number of frequency components.
+% \subsection{Excitation}
+% To excite the system under test, we used quasi-logarithmic (quasi-log) random-phase multisines. 
+% Their phase spectrum $\psi_{k}$ is the result of a uniform random process over $[0,2\pi[$.
+% A logarithmic spacing of the frequency components causes each decade within the band of interest to contain the same number of frequency components.
 
-The quasi-log multisines were sampled at $f_s = 65\,536 \unit{Hz}$
-and consisted of $N= 65\,536$ points such that the frequency spacing was $f_0 = 1\unit{Hz}$ for the linear grid.
-This allowed the signal to cover four decades in the frequency domain,
-from which we did not use the first decade.
-Only frequencies between $1\unit{Hz}$ and $16\,384\unit{Hz}$ are excited, such that aliasing was avoided.
+% The quasi-log multisines were sampled at $f_s = 65\,536 \unit{Hz}$
+% and consisted of $N= 65\,536$ points such that the frequency spacing was $f_0 = 1\unit{Hz}$ for the linear grid.
+% This allowed the signal to cover four decades in the frequency domain,
+% from which we did not use the first decade.
+% Only frequencies between $1\unit{Hz}$ and $16\,384\unit{Hz}$ are excited, such that aliasing was avoided.
 
-For the quasi-log excitation, a frequency ratio of $\alpha = 1.05$ was chosen
-and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
-amplitude was normalized such that the root mean square (RMS) value of $u[n]$
-was equal to $1$.
+% For the quasi-log excitation, a frequency ratio of $\alpha = 1.05$ was chosen
+% and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
+% amplitude was normalized such that the root mean square (RMS) value of $u[n]$
+% was equal to $1$.
 
-The desired frequency ratio $\alpha$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
-This causes a less dense coverage of the lowest frequency bands.
+% The desired frequency ratio $\alpha$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
+% This causes a less dense coverage of the lowest frequency bands.
 
-\subsection{System under test}
-The systems we studied are low-pass second order systems with a given damping
-$\damping$, resonance frequency $\fR$ and a DC gain of $0 \unit{dB}$. Such systems
-can be represented in the discrete frequency domain by a transfer
-function of the form:
-\begin{equation}
-  G \left( z \right) = \frac{         b_2  z^{2} + b_1 z + b_0}%
-                            {\phantom{a_2} z^{2} + a_1 z + a_0}
-  \text{.}
-  \label{eq:tf}
-\end{equation}
+% \subsection{System under test}
+% The systems we studied are low-pass second order systems with a given damping
+% $\damping$, resonance frequency $\fR$ and a DC gain of $0 \unit{dB}$. Such systems
+% can be represented in the discrete frequency domain by a transfer
+% function of the form:
+% \begin{equation}
+%   G \left( z \right) = \frac{         b_2  z^{2} + b_1 z + b_0}%
+%                             {\phantom{a_2} z^{2} + a_1 z + a_0}
+%   \text{.}
+%   \label{eq:tf}
+% \end{equation}
 
-These discrete-time systems were constructed using the \matlab\ function \texttt{cheby1}.
+% These discrete-time systems were constructed using the \matlab\ function \texttt{cheby1}.
 
-An output error (OE) model was used to describe the system under test with the
-input $u[n]$, the system output $y_0[n]$, the white noise source $e[n]$
-and the measured output $y[n] = y_0[n] + e[n]$.
+% An output error (OE) model was used to describe the system under test with the
+% input $u[n]$, the system output $y_0[n]$, the white noise source $e[n]$
+% and the measured output $y[n] = y_0[n] + e[n]$.
 
-\subsection{Simulation setup}
-First, we considered a system with damping $\damping=0.05$ and resonant
-frequency $\fR = 40 \unit{Hz}$.
+% \subsection{Simulation setup}
+% First, we considered a system with damping $\damping=0.05$ and resonant
+% frequency $\fR = 40 \unit{Hz}$.
 
-The output noise $e[n]$ was white Gaussian noise with a standard deviation
-$\sigma_e = 0.1123$ which was approximately $10$ times smaller than the
-root mean square (RMS) value $y_0[n]$.
+% The output noise $e[n]$ was white Gaussian noise with a standard deviation
+% $\sigma_e = 0.1123$ which was approximately $10$ times smaller than the
+% root mean square (RMS) value $y_0[n]$.
 
-The simulations were repeated $R=1000$ times for each system with different realizations of the multisines $u[n]$ and the noise $e[n]$.
-In order to avoid that all simulations started with zero initial conditions, $N + N_{\mathrm{trans}}$ data points were generated, from which the first $N_{\mathrm{trans}}$ points of each simulation were discarded.
+% The simulations were repeated $R=1000$ times for each system with different realizations of the multisines $u[n]$ and the noise $e[n]$.
+% In order to avoid that all simulations started with zero initial conditions, $N + N_{\mathrm{trans}}$ data points were generated, from which the first $N_{\mathrm{trans}}$ points of each simulation were discarded.
 
-\subsection{Results for a single system}
-The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
-These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).
+% \subsection{Results for a single system}
+% The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
+% These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).
 
-These graphs show that the bias is more than $20 \unit{dB}$ less than the variance.
-This means that the mean square error (MSE) of the estimated FRFs is mainly caused by the variance $\sigma_{\hat{G}}^2$ and not by a large bias.
+% These graphs show that the bias is more than $20 \unit{dB}$ less than the variance.
+% This means that the mean square error (MSE) of the estimated FRFs is mainly caused by the variance $\sigma_{\hat{G}}^2$ and not by a large bias.
 
-\begin{figure}[hpt]
-  \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
-  \setlength{\figureheight}{5cm}
-  \input{\thisDir/figs/Sys005log0-1.tikz}
-  \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.05$ 
-           along with its variance and bias.}%
-           \TODO{reproduce figure with ALL excitation signals}
-  \label{fig:FRF1}
-\end{figure}
+% \begin{figure}[hpt]
+%   \centering
+%   \setlength{\figurewidth}{0.8\columnwidth}
+%   \setlength{\figureheight}{5cm}
+%   \input{\thisDir/figs/Sys005log0-1.tikz}
+%   \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.05$ 
+%            along with its variance and bias.}%
+%            \TODO{reproduce figure with ALL excitation signals}
+%   \label{fig:FRF1}
+% \end{figure}
 
-\subsection{Simulations on a range of second order systems}
-The simulation carried out above was repeated for a more general set of systems.
-We studied systems with both a damping of $\damping=0.05$ (as above) and $\damping=0.2$.
-For these different damping values, systems with resonant frequencies
-$\fR \in \{ 40  \unit{Hz}\!,$
-          $ 80  \unit{Hz}\!,$
-          $200  \unit{Hz}\!,$
-          $400  \unit{Hz}\!,$
-          $800  \unit{Hz}\!,$
-          $  2 \unit{kHz}\!,$
-          $  4 \unit{kHz}\!\}$ were considered.
-The parameters pertaining to sampling and the excitation signal were left unchanged
-from the previous simulations. For the systems with a damping of $0.2$, $\sigma_e$
-was put at $0.0678$, which is approximately $10\%$ of the RMS value of $y_0[n]$.
-To allow an easy comparison with a multisine with an equidistant (linear) frequency grid, we also evaluated the variance for such an excitation signal (which had all other parameters determined similarly to the quasi-log multisines).
+% \subsection{Simulations on a range of second order systems}
+% The simulation carried out above was repeated for a more general set of systems.
+% We studied systems with both a damping of $\damping=0.05$ (as above) and $\damping=0.2$.
+% For these different damping values, systems with resonant frequencies
+% $\fR \in \{ 40  \unit{Hz}\!,$
+%           $ 80  \unit{Hz}\!,$
+%           $200  \unit{Hz}\!,$
+%           $400  \unit{Hz}\!,$
+%           $800  \unit{Hz}\!,$
+%           $  2 \unit{kHz}\!,$
+%           $  4 \unit{kHz}\!\}$ were considered.
+% The parameters pertaining to sampling and the excitation signal were left unchanged
+% from the previous simulations. For the systems with a damping of $0.2$, $\sigma_e$
+% was put at $0.0678$, which is approximately $10\%$ of the RMS value of $y_0[n]$.
+% To allow an easy comparison with a multisine with an equidistant (linear) frequency grid, we also evaluated the variance for such an excitation signal (which had all other parameters determined similarly to the quasi-log multisines).
 
-In \figref{fig:damping005} and \figref{fig:damping02} the results from these
-simulations are presented in a condensed form. 
-They show the mean estimated FRFs ($\hat{G}$), the true FRFs ($G_0$) and the corresponding standard deviations ($\sigma_{\hat{G}}$) near the resonance frequency of the simulated systems.
-The bias was at least $20\unit{dB}$ smaller than the standard deviation as well, but is omitted from the figures for clarity.
+% In \figref{fig:damping005} and \figref{fig:damping02} the results from these
+% simulations are presented in a condensed form. 
+% They show the mean estimated FRFs ($\hat{G}$), the true FRFs ($G_0$) and the corresponding standard deviations ($\sigma_{\hat{G}}$) near the resonance frequency of the simulated systems.
+% The bias was at least $20\unit{dB}$ smaller than the standard deviation as well, but is omitted from the figures for clarity.
 
-We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
-the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.
+% We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
+% the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.
 
-For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
-we observe that the variance is nearly constant over the frequency range as well.
-The standard deviation lies at around $-49.3 \unit{dB} \pm 2.2\unit{dB}$.
-Systems that have a lower resonance frequency, exhibit a slightly higher variance 
-on their estimated FRF (near the resonance).
+% For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
+% we observe that the variance is nearly constant over the frequency range as well.
+% The standard deviation lies at around $-49.3 \unit{dB} \pm 2.2\unit{dB}$.
+% Systems that have a lower resonance frequency, exhibit a slightly higher variance 
+% on their estimated FRF (near the resonance).
 
-The logarithmically-spaced excitation provides a much more constant dependency of resonance frequency to the variance than a linearly-spaced multisine, where the variance varies over respectively $35$ and $25 \unit{dB}$.
+% The logarithmically-spaced excitation provides a much more constant dependency of resonance frequency to the variance than a linearly-spaced multisine, where the variance varies over respectively $35$ and $25 \unit{dB}$.
 
-\begin{figure}%
-  \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
-  \setlength{\figureheight}{5cm}
-  \input{\thisDir/figs/damping005-cmp.tikz}
-  \caption{Comparison of the FRF and corresponding variances for
-           different second order systems with constant damping
-           $\damping=0.05$ but different resonance frequencies around
-           their respective resonance frequencies, for both a quasi-log 
-           and a linear multisine excitation.}%
-  \label{fig:damping005}
-\end{figure}
+% \begin{figure}%
+%   \centering
+%   \setlength{\figurewidth}{0.8\columnwidth}
+%   \setlength{\figureheight}{5cm}
+%   \input{\thisDir/figs/damping005-cmp.tikz}
+%   \caption{Comparison of the FRF and corresponding variances for
+%            different second order systems with constant damping
+%            $\damping=0.05$ but different resonance frequencies around
+%            their respective resonance frequencies, for both a quasi-log 
+%            and a linear multisine excitation.}%
+%   \label{fig:damping005}
+% \end{figure}
 
-\begin{figure}%
-  \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
-  \setlength{\figureheight}{5cm}
-  \input{\thisDir/figs/damping02-cmp.tikz}
-  \caption{Comparison of the FRF and corresponding variances for
-           different second order systems with constant damping
-           $\damping=0.2$ but different resonance frequencies around
-           their respective resonance frequencies, for both a quasi-log 
-           and a linear multisine excitation.}%
-  \label{fig:damping02}
-\end{figure}
+% \begin{figure}%
+%   \centering
+%   \setlength{\figurewidth}{0.8\columnwidth}
+%   \setlength{\figureheight}{5cm}
+%   \input{\thisDir/figs/damping02-cmp.tikz}
+%   \caption{Comparison of the FRF and corresponding variances for
+%            different second order systems with constant damping
+%            $\damping=0.2$ but different resonance frequencies around
+%            their respective resonance frequencies, for both a quasi-log 
+%            and a linear multisine excitation.}%
+%   \label{fig:damping02}
+% \end{figure}
 
-\subsection{Conclusion}
-The variance on the FRF near resonances with identical damping is nearly independent of the resonance frequency when a quasi-log multisine is used as excitation signal. 
-This result was obtained for second order sections and illustrated on a more general system.
+% \subsection{Conclusion}
+% The variance on the FRF near resonances with identical damping is nearly independent of the resonance frequency when a quasi-log multisine is used as excitation signal. 
+% This result was obtained for second order sections and illustrated on a more general system.
 

### 2015-11-18 ch02-qlogms/excitation-design.tex
Fixup OE diagram

@@
     $U  \left(\omega\right)$ as the excitation signal,
-    $Y_0\left(\omega\right)$ the exact, unperturbed system output,
+    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
     $E  \left(\omega\right)$ for the output noise source,
-    $Y  \left(\omega\right) = Y_0\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
+    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
 
@@
     \caption[Output-error]{Output-error set-up.}
+    \label{fig:excitation:OE}
   \end{figure}
@@
   standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
-
-  \TODO{put block diagram here}
 

### 2015-11-24 ch02-qlogms/excitation-design.tex
Some updates to CH02

@@
    \begin{equation}
-     F_{B}(f) \isdef
+     F_{B} \isdef
      \floor{\frac{\log (\kappa f) - \log( f )}{\log \alpha}}
@@
   \begin{remark}
-  The use of different rounding strategies in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
+  The use of different rounding strategies --- e.g.
+the \code{ceil} function $\ceil{}$  and \code{floor} function $\floor{}$ --- in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
   By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
@@
   \qquad
-  \forall k \in \set{1,\ldots,F}
+  \forall k \in \NaturalNumbersWithoutZero
   \text{.}
   \end{equation}
+  This means that rounding using the \code{floor} operator favors to strictly attain the specified frequency bin density at the cost of a few more excited lines (and hence less allottable power per line).
+  The \code{ceil} function produces a grid that has more power per line at the cost of a reduced bin density.
+  On the other hand, using \code{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
   \end{remark}
@@
   This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
-  Consequently,
+  Consequently, both signals can be expected to behave in approximately the same way.
 
@@
   Consider the second-order systems $G(\omega; \wn)$ and $G(\omega; m\wn)$ with $m \in \RealNumbersWithoutZero$. 
-  For a frequency grid $\infgrid{\omega}$ with infinite span, it can be shown that $G(\infgrid{\omega}; \wn) = G(m \infgrid{\omega}; m\wn)$.
+  For a frequency grid $\infgrid{\omega}$ with infinite span, $G(\infgrid{\omega}; \wn) = G(m \infgrid{\omega}; m\wn)$.
   \end{lemma}
   \begin{proof}
-  Pick any $\omega_{\star} \in \infgrid{\omega}$. The frequency $m\omega_{\star}$ is then by definition an element of the grid $m\infgrid{\omega}$.
+  Consider any $\omega_{\star} \in \infgrid{\omega}$. The frequency $m\omega_{\star}$ is then by definition an element of the grid $m\infgrid{\omega}$.
   Substituting $\omega = \omega_{\star}$ and $\omega = m \omega_{\star}$  into  $G(\omega; \wn)$ and $G(m\omega; m\wn)$  respectively, directly yields
@@
     Second-order  systems with equal damping $\damping$ and \gls{DC} gain $\dc$ but resonance frequencies that differ by a factor $\alpha^N$ with $N \in \IntegerNumbers$, share an identical `shape` of their \gls{FRF} at the lines of a logarithmically spaced frequency grid with infinite span and a frequency ratio $\alpha$.
-    Or, formally: $G(\infgrid{\omega};\wn) = G(\infgrid{\omega}; \alpha^{N}\wn) \forall N \in \NaturalNumbers$.
+    Or, formally: $\forall N \in \NaturalNumbers: G(\infgrid{\omega};\wn) = G(\infgrid{\omega}; \alpha^{N}\wn)$.
   \end{theorem}

### 2015-11-24 ch04-lrmhinf/lrmhinf.tex
Some future work stuffies + labels

\chapter{Non-parametric resonance modeling}
\label{sec:hinf}

### 2015-11-24 ch06-concl/conclusions.tex
More outline added
Some future work stuffies + labels

@@
 \chapter{Conclusions}
+
+\section{Conclusions of this research}
+
+  \subsection{Excitation design}
+  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
+  Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
+  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
+  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping_{\min}$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
+  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid should conform to
+  \begin{equation}
+    \alpha \leq 1 + \damping_{\min}
+  \end{equation}
+  to attain a reliable estimate of the resonances present in the system.
+  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework present in \chapref{sec:excitation}. 
+  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited as in many cases.
+
+  In practical terms of a layman user, this means that the design of a quasi-logarithmic multisines discussed in this thesis, requires only limited prior knowledge from the user:
+  \begin{itemize}
+    \item the allowable measurement time (or equivalently, the minimal relevant frequency),
+    \item the allowable total excitation power,
+    \item a broad frequency band of interest that could span multiple decades, and,
+    \item the minimal expected relative damping $\damping_{\min}$ in the system.
+  \end{itemize}
+  This last requirement is the only requirement that is often overlooked in initial excitation designs.
+  \subsection{Non-parametric estimation}
+  \subsection{Initialization of parametric estimation}
 
@@
   \subsection{Excitation design}
-  \TODO{MIMO}
+  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
+  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
+  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time:
+  \begin{itemize}
+    \item Zippered multisines, where the frequency grids of the different input channels are interspersed.
+This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
+    \item Orthogonal multisines, which are computationally more involved to process.
+  \end{itemize}
+  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer a very easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
+
+  Also, in the related chapter, it has been assumed that the system is an \gls{LTI} system.
+  For weakly nonlinear systems, the proposed approach is likely to
+
+  \TODO{MIMO extension}
+  \TODO{zippered vs. orthogonal}
+
+  \subsection{Non-parametric estimators}
+    \TODO{Order selection / BW selection}
+    \TODO{MIMO LRM}
+    \TODO{Slowly time-varying}
+    \TODO{Static LPV measurements}
+
+  \subsection{Non-parametric estimation and interpolation}
+  \TODO{Link between local models and weighting function design}
+
+  \subsection{Parametric initialization}
+  In \chapref{sec:initvals} it was already illustrated that smoother can provide improved initial estimates of a system. 
+  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the the dimensionality in the parameter space.
+  By no means smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.
+
+  On the other hand, the \gls{LRM} and its variants discussed in \chapref{sec:nonparametric} provide some local information regarding the shape of the \gls{FRF} and hence also the transfer function.
+  The usefulness has already been seen in \chapref{sec:hinf} in connection to the computation of the \Hinf norm of a system.
+  Intrinsically, these local rational methods approximate the transfer function by a local model, or, equivalently a set of local poles and zeros.
+  Especially for resonant poles, one can expect that these local poles are closely linked to the global (actual) poles of a system.
+  As such, those could provide a valuable initialization strategy if the redundant local pole/zero information of neighboring windows can be reduced to a single global pole/zero initial value.
+  \TODO{optimal smoother}

### 2015-11-25 ch02-qlogms/excitation-design.tex
Aperiodic illustration

@@
    Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
-   Consequently, such a `multisine' is not periodic.
+   Consequently, such a generalized `multisine' is not periodic.
+   \begin{figure}
+     \centering
+     \setlength{\figurewidth}{\columnwidth}
+     \setlength{\figureheight}{3cm}
+     \input{\thisDir/figs/aperiodic.tikz}
+     \caption{
+     The first periods of $\sin \left( 2\pi f_1 t\right)$ with $f_1 = 1\unit{Hz}$  together with $\sin \left( 2 \pi f_2 t\right)$ for $f_2 = \pi \unit{Hz}$ to illustrate that both do not share a common period.}
+     \label{fig:excitation:aperiodicmultisine}
+    \end{figure}
   \end{example}

### 2015-11-25 ch02-qlogms/excitation-design.tex
Figure aperiodic removed from text
And some structure work on CH02

--- 2015-11-24 ch02-qlogms/excitation-design.tex
@@
    Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
-   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
-   Consequently, such a `multisine' is not periodic.
+   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number (unlike $T_1$ and $T_2$).
+   Consequently, such a generalized `multisine' is not periodic.
   \end{example}
@@
 
-  \begin{remark}
-    In different contexts, e.g.
-electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
-  \end{remark}
-
   \begin{property}
@@
   \end{example}
+  \begin{remark}
+    In different contexts, e.g.
+electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
+    Obviously, such alternative specifications are equivalent.
+  \end{remark}
   \begin{example}

### 2015-11-26 ch02-qlogms/excitation-design.tex
Some intro on Input design

@@
 Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
+
+\begin{conjecture}
+To identify the transfer function of a system, one has to apply an excitation signal to its input.
+\end{conjecture}
+\begin{conjecture}
+To know which excitation signal is a good signal to excite the system with, one needs to know the system.
+\end{conjecture}
+
+The two conjectures above illustrate the catch-22 a practicing modeler finds himself in: if one wishes to identify a system, one needs to apply a signal; but to determine a good signal, one needs to know the system.
+This conundrum becomes especially worrisome if one not only wants to use a `good' excitation signal, but rather the `best' excitation signal.
+
+In this chapter, we will investigate how one can develop excitation signals that try to alleviate this paradox by imposing heuristic prior knowledge about the system that is more generic than in a typical (robust) optimal input design, but less wasteful than typical generic full multisine signals.
 
@@
 \label{sec:excitation:intro:robust}
-As illustrated above, optimal experiment design places the user in a catch-22 situation.
+As illustrated above, optimal experiment design places the user in a catch-22 situation\footnote{See the 1961 Joseph Heller novel `Catch-22'.}.
 In the recent years, this has sparked attention towards robust signal design~\citep{Rojas2007} to alleviate the drawbacks of (nominal) optimal experiment design.
@@
   Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
-  This problem was already discussed in \citet{Geerardyn2012IMTC}.
 
@@
    Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
-   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number (unlike $T_1$ and $T_2$).
+   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number of seconds (unlike $T_1$ and $T_2$).
    Consequently, such a generalized `multisine' is not periodic.
@@
   Doing so allows to determine a suitable value for the frequency spacing $\alpha$.
+
+\TODO{cov-matrix uitschrijven}
 

### 2015-11-26 ch01-intro/introduction.tex
Figure ID cycle + some intro exp design
Gebrol in intro/conclusie qLogMS
Publications in intro

@@
 \chapter{Introduction}
+\def\thisDir{ch01-intro}
 
   \section{System idenfication}
+
+\begin{figure}
+
+  \centering
+  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
+  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
+  \label{fig:intro:identification-cycle}
+\end{figure}
+
    \section{Contributions}
+
+   \section{Publications}
+   The lion's share of this thesis has been published either in peer-reviewed scientific journals and conferences or has been submitted to such venues at the time of writing.
+   This section links my different publications to the different sections in this thesis.
+   For an overview of publications grouped by type, please refer to \pageref{publicationList}.
+
+\begin{refsection}
+% http://tex.stackexchange.com/questions/38580/displaying-selected-bibliographic-items-in-the-body-of-the-text
+% http://tex.stackexchange.com/questions/126226/how-do-i-instruct-fullcite-to-use-maxbibnames-rather-than-maxcitenames
+
+\makeatletter
+\DeclareCiteCommand{\fullcite}
+  {\defcounter{maxnames}{\blx@maxbibnames}%
+    \usebibmacro{prenote}}
+  {\usedriver
+     {\DeclareNameAlias{sortname}{default}}
+     {\thefield{entrytype}}}
+  {\multicitedelim}
+  {\usebibmacro{postnote}}
+\DeclareCiteCommand{\footfullcite}[\mkbibfootnote]
+  {\defcounter{maxnames}{\blx@maxbibnames}%
+    \usebibmacro{prenote}}
+  {\usedriver
+     {\DeclareNameAlias{sortname}{default}}
+     {\thefield{entrytype}}}
+  {\multicitedelim}
+  {\usebibmacro{postnote}}
+\makeatother
+
+% http://tex.stackexchange.com/questions/18664/underline-my-name-in-the-bibliography
+\DeclareNameFormat{author}{%
+\ifthenelse{\equal{#1}{Geerardyn}}%
+    {\textbf{\ifblank{#3}{}{#3\space}#1}}%
+    {\ifblank{#3}{}{#3\space}\ifblank{#5}{}{#5\space}#1}%
+\ifthenelse{\value{listcount}<\value{liststop}}%
+    {\addcomma\space}
+    {}}
+
+The quasi-logarithmic multisines presented in \chapref{sec:excitation} are based on a journal article published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+\begin{itemize}
+  \item \fullcite{Geerardyn2013TIM}, 
+\end{itemize}
+preliminary results were also presented at the 2012 \gls{IFAC} symposium on System Identification (\textsc{SYSID}) and the \gls{IEEE} International Instrumentation and Measurement Conference (\textsc{I$^{\text{2}}$MTC}):
+\begin{itemize}
+  \item \fullcite{Geerardyn2012IMTC}, and
+  \item \fullcite{Larsson2012SYSID}.
+\end{itemize}
+This work has also been presented at the following local (non-refereed) conferences:
+\begin{itemize}
+  \item \fullcite{Geerardyn2012Benelux}, and
+  \item \fullcite{Geerardyn2012ERNSI}.
+\end{itemize}
+
+The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript:
+\begin{itemize}
+  \item \TODO{Geerardyn2016LRM}
+\end{itemize}
+and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+\begin{itemize}
+  \item \fullcite{Lumori2014TIM}.
+\end{itemize}
+Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
+\begin{itemize}
+    \item \fullcite{Verbeke2015Benelux}.
+\end{itemize}
+
+The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and
+\begin{itemize}
+  \item \fullcite{Geerardyn2014IFAC},
+  \item \fullcite{Geerardyn2014ISMA}.
+\end{itemize}
+Preliminary results have been presented at local (non-refereed) conferences:
+\begin{itemize}
+  \item \fullcite{Geerardyn2013Benelux},
+  \item \fullcite{Geerardyn2013ERNSI},
+  \item \fullcite{Geerardyn2014Benelux},
+  \item \fullcite{Geerardyn2014DYSCO}, and
+  \item \fullcite{Geerardyn2014ERNSI}.
+\end{itemize}
+The experimental work related to \chapref{sec:hinf} is also presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
+\begin{itemize}
+  \item \fullcite{Voorhoeve2015}
+  \item \fullcite{Voorhoeve2015ERNSI}
+\end{itemize}
+
+The study of different initialization strategies as depicted in \chapref{sec:initvals} has been published in the \gls{IEEE} Transactions on Instrumentation \& Measurement:
+\begin{itemize}
+  \item \fullcite{Geerardyn2015TIM},
+\end{itemize}
+and also at the local (non-refereed) 2015 Benelux Meeting on Systems and Control:
+\begin{itemize}
+    \item \fullcite{Geerardyn2015Benelux}.
+\end{itemize}
+
+In collaboration with fellow researchers, I have written a few other publications.
+However, these publications are not covered in this thesis.
+
+\begin{itemize}
+  \item \fullcite{vanBerkel2014Automatica}
+  \item \fullcite{Cooman2012SMACD}
+  \item \fullcite{Cooman2012DYSCO}
+  \item \fullcite{Cooman2012ERNSI}
+\end{itemize}
+
+\end{refsection}

### 2015-11-26 config/glossaries.inc.tex
Beunen in excitation design
Quite some changes to CH02
Lemmaified ch02
Some updates to CH02
Publications in intro

@@
 \newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
+\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
 \newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
@@
 %% ACRONYMS
-\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
+\newacronym{BLA}{BLA}{best linear approximation}
 
-\newacronym{iid}{i.i.d.}{independent and identically distributed}
-\newacronym{SISO}{SISO}{single-input single-output}
-\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
-\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
-\newacronym{MISO}{MISO}{Multiple Input Single Output}
-\newacronym{BLA}{BLA}{best linear approximation}
+\newacronym{CRLB}{CRLB}{Cramér-Rao Lower Bound}
+\newacronym{CZT}{CZT}{Chirp $Z$ Transform}
+
+\newacronym{DC}{DC}{direct current}
+\newacronym{DFT}{DFT}{Discrete Fourier Transform}
+\newacronym{DSA}{DSA}{dynamic signal analyzer}
 \newacronym{DUT}{DUT}{device under test}
 
-\newacronym{FRF}{FRF}{frequency response function}
-\newacronym{LTI}{LTI}{linear time-invariant}
 \newacronym{ETFE}{ETFE}{empirical transfer function estimate}
 
+\newacronym{FFT}{FFT}{Fast Fourier Transform}
+\newacronym{FRF}{FRF}{frequency response function}
+
+\newacronym{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
+\newacronym{IFAC}{IFAC}{International Federation of Automatic Control}
+\newacronym{iid}{i.i.d.}{independent and identically distributed}
+
 \newacronym{LPM}{LPM}{Local Polynomial Method}
+\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
 \newacronym{LRM}{LRM}{Local Rational Method}
-\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
-\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}
+\newacronym{LTI}{LTI}{linear time-invariant}
+
+\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
+\newacronym{MISO}{MISO}{Multiple Input Single Output}
+\newacronym{MSE}{MSE}{mean squared error}
+
+\newacronym{PSD}{PSD}{power spectral density}
 
@@
 
-\newacronym{DFT}{DFT}{Discrete Fourier Transform}
-\newacronym{FFT}{FFT}{Fast Fourier Transform}
+\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
+\newacronym{SISO}{SISO}{single-input single-output}
+\newacronym{SPICE}{SPICE}{Simulation Program with Integrated Circuit Emphasis}
+\newacronym{SNR}{SNR}{signal to noise ratio}
+
+\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}
+
+\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
 

### 2015-11-28 ch02-qlogms/excitation-design.tex
Patching up some references

@@
 \chapter{Design of excitation signals}
+\label{sec:excitation}
 \def\thisDir{ch02-qlogms}
@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction}
   It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
@@
 
-  Any LTI system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
+  Any \gls{LTI} system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
   Therefore the performance of the proposed method is assessed on a prototype system of second order.
-  This does not limit the generality of the approach as we can add several of such systems to construct a general LTI system.
+  This does not limit the generality of the approach as we can add several of such systems to construct a general \gls{LTI} system.
 
@@
   For a system with a sufficiently low damping, one can intuitively understand that most of the information is contained within the $3 \unit{dB}$ bandwidth of the system.
-  Remember that an LTI system is naturally described in a logarithmic frequency axis (the slopes of such a system are specified in $\unit{dB}/\text{decade}$).
+  Remember that an \gls{LTI} system is naturally described in a logarithmic frequency axis (the slopes of such a system are specified in $\unit{dB}/\text{decade}$).
   Hence, an excitation with a flat power spectrum and a linearly spaced frequency grid will over-excite the high end of the band at the cost of the low frequencies.
@@
 \subsection{System and noise model}
-  In this chapter, an output error (OE) system setup is used.
+  In this chapter, an \gls{OE} system setup is used.
   Denote
@@
   \text{.}
-  \label{eq:secondOrderSystemDTidentifiable}
+  \label{eq:excitation:secondOrderSystemDTidentifiable}
   \end{equation}
@@
 
-  The obtained FRF is then fitted to the transfer function model \eqref{eq:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT~\citep{FDIDENT} for \MATLAB.
+  The obtained FRF is then fitted to the transfer function model \eqref{eq:excitation:secondOrderSystemDTidentifiable} using the \texttt{elis} function of the \FDIDENT~\citep{FDIDENT} for \MATLAB.
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
@@
   It is clearly unfeasible to estimate the five parameters in
-  \eqref{eq:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
+  \eqref{eq:excitation:secondOrderSystemDTidentifiable} using this little information in the $3\unit{dB}$ bandwidth of the system.
   In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
@@
   \subsection{Simulation example on higher order systems}
-To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:tf} in parallel.
+To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:excitation:secondOrderSystemDTidentifiable} in parallel.
 This is equivalent to adding their respective transfer functions, therefore, the resulting transfer function is of the form:
@@
 
-    For the parametric model, on the other hand, a continuous time LTI model of the form
+    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
     \begin{equation}
@@
 
-The suggested amplitude compensation methods allow the user to measure a parametric LTI model for systems in a wide frequency band with a constant uncertainty.
+The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in a wide frequency band with a constant uncertainty.
 The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.

### 2015-11-28 ch02-qlogms/sysid.tex
Patching up some references

@@
-\section{Introduction}\label{sec:intro}
+\section{Introduction}\label{sec:excitation:intro}
 Input design deals with the task of choosing an excitation signal in a way so that the information obtained from the experiment is maximized.
@@
 The following parts of the paper are structured as follows.
-Section~\ref{sec:inputDesign} briefly presents the necessary input design theory.
-Section~\ref{sec:logarithmic} deals with the situation when limit information is available.
-The idea is illustrated in a series of simulation examples in Section~\ref{sec:sim}.
-Finally, conclusions are drawn in Section~\ref{sec:conclusions}.
+\secref{sec:excitation:inputDesign} briefly presents the necessary input design theory.
+\secref{sec:excitation:logarithmic} deals with the situation when limit information is available.
+Finally, conclusions are drawn in \secref{sec:excitation:conclusions}.
 
-\section{Input design}\label{sec:inputDesign}
+\section{Input design}\label{sec:excitation:inputDesign}
 For the theoretical analysis, we consider SISO output error systems, i.e.
@@
            \dd{\omega} \text{.}
-\label{eq:IF}
+\label{eq:excitation:IF}
 \end{align}
@@
 \var{\hat{G}(j\omega)} &= \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
-\label{eq:varG}
+\label{eq:excitation:varG}
 \end{align}
@@
 To increase the robustness of the design, one could take a fraction, say $\alpha$, from the optimal power and redistribute over the whole frequency band of interest.
-From \eqref{eq:IF} and \eqref{eq:varG} we see that scaling the input power by $1-\alpha$, gives the transfer function variance
+From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the input power by $1-\alpha$, gives the transfer function variance
 \begin{align}
@@
 
-\section{Logarithmic power distributions}\label{sec:logarithmic}
+\section{Logarithmic power distributions}\label{sec:excitation:logarithmic}
 When no information about the system is known, it is desirable that
@@
 y_t &= G(s,\theta) u_t = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
-\label{eq:2ndOrderSys}
+\label{eq:excitation:2ndOrderSys}
 \end{align}
@@
 This can be seen by considering the optimal design for a second order system.
-From \citep[Example 6.4.5]{Goodwin1977} we have that the D-optimal design for \eqref{eq:2ndOrderSys} is a single sinusoid at frequency
+From \citep[Example 6.4.5]{Goodwin1977} we have that the D-optimal design for \eqref{eq:excitation:2ndOrderSys} is a single sinusoid at frequency
 \begin{align}
@@
 {\sqrt{5}}.
-\label{eq:optFreq}
+\label{eq:excitation:optFreq}
 \end{align}
 For lightly-damped systems, i.e $\damping \ll 1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
-From \eqref{eq:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
+From \eqref{eq:excitation:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
 Input design can be based on a guess of $\wn$, however if this guess is wrong, the resulting estimates may be unacceptable~\citep{Rojas2007}.
@@
 \begin{align*}
-\label{eq:pink}
+\label{eq:excitation:pink}
 \phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
@@
        \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
-  \label{eq:MS}
+  \label{eq:excitation:MS}
 \end{equation}
@@
 The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
-This is illustrated in Section~\ref{sec:sim}.
+This is illustrated in Section~\ref{sec:excitation:sim}.
 
@@
 \theta_i&=[\wn[i]\;\damping_i]^{\T}.
-\label{eq:sumSys}
+\label{eq:excitation:sumSys}
 \end{align}
@@
 
-The information matrix for systems of the type \eqref{eq:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
+The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
 \begin{align}
@@
        \end{bmatrix}.
-\label{eq:infoEx}
+\label{eq:excitation:infoEx}
 \end{align}
-To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:infoEx}, when the input spectrum \eqref{eq:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
+To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
 
@@
 \begin{align}
-\label{eq:auto}
+\label{eq:excitation:auto}
 \int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
@@
 % \begin{align}
-% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
+% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:excitation:cross1} \\
 % &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
-% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
+% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:excitation:cross}
 % \end{align}
@@
 \qquad \qquad \qquad \qquad \qquad
-\label{eq:cross1} \\
+\label{eq:excitation:cross1} \\
 \leq
@@
 \qquad \qquad \qquad \qquad \qquad
-\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
+\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
 \end{gather}
@@
 There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak.
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:dG}.
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:dG}.
 
-A crude, albeit useful, bound on the integrand in \eqref{eq:cross} is
+A crude, albeit useful, bound on the integrand in \eqref{eq:excitation:cross} is
 \begin{align}
@@
 \end{align}
-Hence \eqref{eq:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
+Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
 \begin{itemize}
-\item the integral \eqref{eq:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
-\item lower damping further decreases the integral \eqref{eq:cross1} in comparison to \eqref{eq:auto}.
+\item the integral \eqref{eq:excitation:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
+\item lower damping further decreases the integral \eqref{eq:excitation:cross1} in comparison to \eqref{eq:excitation:auto}.
 \end{itemize}
@@
 \caption{The shape of $\frac{\partial G_1}{\partial \wn[1]}$. The roll-off around the peak is significant and depends on the damping of the system.}
-\label{fig:dG}
+\label{fig:excitation:dG}
 \end{figure}
 
-To further illustrate the decoupling of the two systems, we calculate \eqref{eq:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
+To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
 If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
@@
 
-In \figref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
+In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
 It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling.
@@
          The arrow indicates the direction of increasing separation.}
-\label{fig:coupling}
+\label{fig:excitation:coupling}
 \end{figure}
 
-% \section{Simulations}\label{sec:sim}
+% \section{Simulations}\label{sec:excitation:sim}
 % We considered a linear second order system that is to be identified, with the
@@
 %   \text{.}
-%   \label{eq:tf}
+%   \label{eq:excitation:tf}
 % \end{equation}
@@
 % \subsection{Results for a single system}
-% The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
+% The outcome of the simulation over these repetitions are displayed in \figref{fig:excitation:FRF1}.
 % These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).
@@
 %            \TODO{reproduce figure with ALL excitation signals}
-%   \label{fig:FRF1}
+%   \label{fig:excitation:FRF1}
 % \end{figure}
@@
 
-% In \figref{fig:damping005} and \figref{fig:damping02} the results from these
+% In \figref{fig:excitation:damping005} and \figref{fig:excitation:damping02} the results from these
 % simulations are presented in a condensed form. 
@@
 
-% We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
+% We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:excitation:damping005})
 % the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.
 
-% For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
+% For the systems that are damped more ($\damping=0.2$ in \figref{fig:excitation:damping02}),
 % we observe that the variance is nearly constant over the frequency range as well.
@@
 %            and a linear multisine excitation.}%
-%   \label{fig:damping005}
+%   \label{fig:excitation:damping005}
 % \end{figure}
@@
 %            and a linear multisine excitation.}%
-%   \label{fig:damping02}
+%   \label{fig:excitation:damping02}
 % \end{figure}
@@
 %%Conclusion
-\section{Conclusions}\label{sec:conclusions}
+\section{Conclusions}\label{sec:excitation:conclusions}
 In this paper we recalled that the design of an optimal excitation signal may require prior system knowledge that is insufficiently accurate or even unavailable. 

### 2015-11-28 config/glossaries.inc.tex
Patching up some references

@@
 
-\newacronym{CRLB}{CRLB}{Cramér-Rao Lower Bound}
-\newacronym{CZT}{CZT}{Chirp $Z$ Transform}
+\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
+\newacronym{CZT}{CZT}{chirp $Z$-transform}
 
 \newacronym{DC}{DC}{direct current}
-\newacronym{DFT}{DFT}{Discrete Fourier Transform}
+\newacronym{DFT}{DFT}{discrete Fourier transform}
 \newacronym{DSA}{DSA}{dynamic signal analyzer}
+\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
 \newacronym{DUT}{DUT}{device under test}
@@
 
-\newacronym{FFT}{FFT}{Fast Fourier Transform}
+\newacronym{FFT}{FFT}{fast Fourier transform}
 \newacronym{FRF}{FRF}{frequency response function}
@@
 
-\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
-\newacronym{MISO}{MISO}{Multiple Input Single Output}
+\newacronym{MIMO}{MIMO}{multiple-input multiple-output}
+\newacronym{MISO}{MISO}{multiple-input single-output}
 \newacronym{MSE}{MSE}{mean squared error}
+
+\newacronym{OE}{OE}{output-error}
 
@@
 
-\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
+\newacronym{SIMO}{SIMO}{single-input multiple-output}
 \newacronym{SISO}{SISO}{single-input single-output}

### 2015-11-28 front-and-back-matter/acknowledgements.inc.tex
Patching up some references

\chapter{Acknowledgements}
%TODO m2t team
%TODO ELEC
%TODO proffen, technici, secretaressen
%TODO anna/maarten
%TODO office mates
%TODO EIT people
%TODO jury
%TODO christian larsson, istvan, MST
%TODO mikaya
%TODO CST
%TODO Rick, Annemiek, Matthijs, Frank
%TODO Johan
%TODO Tom
%TODO family
%TODO family-in-law
%TODO alexandra
%TODO pixie

### 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Import LPMSmooth Paper from Mikaya

% \title{
% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}

% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
% $^2$J. Lataire, \emph{Member, IEEE}\\

% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
% }

% \begin{document}
% \maketitle

% \begin{abstract}
% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function. Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework. The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors. The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
% \end{abstract}

% \begin{IEEEkeywords}
% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
% \end{IEEEkeywords}

\subsection{Introduction}

The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others. Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems. This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.

This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense. The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e. no user interaction. Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}. Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}. Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.

The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM. This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction. The cutoff index (truncation point) is determined by a statistically sound method. It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.

Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A single-input-single-output (SISO) LTI system is considered. %, based on  \cite{schoukens2010nonparametric}. 
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in Fig. 1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
\begin{equation}\label{lpmtd1}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

\begin{figure}[tbh] %top bottom here
\centering
\includegraphics{\thisDir/figs/tikz0.pdf}
\caption{SISO LTI discrete-time system in an output error setup.}
\label{lpmtdrep}
\end{figure}

Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.

In this paper, however, a nonparametric technique is developed, %the identification problem is 
formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:

\begin{itemize}

\item

The work in this paper is for discrete-time systems. Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
\item

Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
\item

Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.

\end{itemize}

The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.

Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.

These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.

\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}

Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.

\subsubsection{Spectral Nonparametric Model and Assumptions}

Using convolution, the noiseless output signal in Fig. \ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{lpmleak}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}

\begin{equation}\label{eq:defDFT}
X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
\end{equation}

The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
\begin{assumption}
The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

\begin{assumption}

The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
\end{assumption}

In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.

\begin{assumption}
The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
\end{assumption}

\begin{assumption}
The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
\end{assumption}

\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.  In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency. 
Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.

The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM. As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.

\paragraph{Formulation of the Linear LS LPM}
The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}. Section 7.2.2 of \cite{FDidentEd2Pintelon} 
gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.

The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
\begin{equation}\label{lpm1spectra}
Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
\end{equation}
where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

The choice of the tunable parameters $n$ and $R$ is discussed later on.

Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
\begin{equation}\label{lpmGTMatrix}
Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
\end{equation}
where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
\begin{align}
K(k,r) = &\left[
\begin{matrix}
U_0(k+r) & U_0(k+r)r & \dots 
\end{matrix}
\right.
\\ 
&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
\end{align}

Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
\begin{equation}\label{lpmGTMatrixStack}
Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
\end{equation}
where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
\begin{align}\label{eq:LSsolutionLPM}
\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
\end{align}

The formulation of

 equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$. The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}. %(per JL)!

The values $R = 2$, and $n=R+1=3$ will be used in the LPM.

When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
 these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
\begin{align}\label{lpmImplQuadG}
G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
\end{align}

\noindent
($r\in\mathbb{W}_3$)
and the vector of parameters:

\begin{equation}\label{lpmThetaEst}
\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
\end{equation}
The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:

\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
\end{equation}

The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering

   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
   \includegraphics{\thisDir/figs/LPMfigOmegak} 
   \caption{Illustration of the LPM. Top figures: input spectrum (left) and output spectrum (right). A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all $\Omega_k$.}

   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e. the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries). This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.

\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}

The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions. After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.

\item
Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.

\item
An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.

\item
A truncation is effected at the point beyond which the data record (impulse response) is buried in noise. % main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)

This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
\end{enumerate}

These procedures require that the following assumptions are satisfied.

\begin{assumption}
The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
\end{assumption}

This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value). It requires that the input signal excites the whole unit circle. This is satisfied, for instance, by using white noise as an excitation signal.

\begin{assumption}\label{ass:imprespdecay}
The impulse response decays exponentially with time.
\end{assumption}

\begin{assumption}\label{ass:decay90perctime}
Within $90\%$ of the measurement window, the impulse response decays

 to a level that is indistinguishable from the noise.

\end{assumption}

Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.

\subsubsection{Obtaining the Impulse Response Function}

The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:

\begin{align}\label{eq:impRespiDFT}
\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}

\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:

\begin{align}
\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}

\noindent 
(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
to ensure $\hat g_\mathrm{poly}(t)$ to be real.

Smoothing of the estimated FRF requires the correct estimate of the impulse response. Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e. DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. This anomaly is rectified by developing a simple estimator of the mean value, presented below.

\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}

The correct mean value of the impulse response accounts for (i.e. estimates) the DC value of the FRF. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response. The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
To this end, the following procedure is executed:

\begin{enumerate}
\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
\begin{align}
m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)
\end{align}

\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:

\begin{align}
\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}

\end{enumerate}

\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}

The FRF estimate is smoothed by truncating the estimated impulse response function. The truncation is applied at the time index beyond which the signal is indistinguishable from the noise. %The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise

This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.

% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
%
%
%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
%\label{se:expFitTheory}
%
%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
%%at which the estimated impulse response 
%gets below the noise floor.
%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
%This algorithm has been implemented as follows.

\begin{enumerate}
\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}. Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$. %In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:

%\JL{
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}

\noindent
This is valid, as per Assumption \ref{ass:decay90perctime}.
%}

%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.

\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise. Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
\begin{align}
\mathbb{T}_\mathrm{HSNR} = \left\{
t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
\right\}.
\end{align}

\noindent
(Subscript HSNR stands for High Signal-to-Noise Ratio.)

%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.

\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
\begin{align}\label{eq:TmaxDef}
\mathbb{T}_\mathrm{max} = \left\{
t: \left| \hat g(t)\right|>
\left|\hat g(t')\right|,
t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
\right\},
\end{align}

\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression

\begin{align}\label{eq:expFit}
\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
\end{align}

\noindent
for $\ln A$ and $a$ in a least squares sense. This is a quadratic problem in the parameters and, thus, solved in a single step. Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.

\item
Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:

\begin{align}\label{eq:truncTimeExpFit}
t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}

\noindent
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below. %(see the discussion below).
% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.

\item
 Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.

\end{enumerate}

\begin{figure}[tbh] %top bottom here
\centering

\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
\caption{Truncation of the impulse response via the fit of  an exponential. The light gray line is the noisy impulse response, and the dark gray one is its absolute value. Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. Black thick line: estimated exponential function \eqref{eq:expFit}.}
\label{FRF_truncate_expfitter}
\end{figure}

As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:

\begin{align}
%\input{theModelExpFit.tex}
y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
\\
&+0.592y_0(t-3) + u(t)
\end{align}

The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
The result is depicted in Figure \ref{FRF_truncate_expfitter}. An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line). The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e. $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).

%\JL{
\paragraph*{Considerations on the choice of $\gamma$}

\begin{itemize}
\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.

\item
The bias error is highest in the vicinity of (sharp) resonance peaks. If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used. %If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.

\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
\end{itemize}
%}

%\JL{
%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor?? Truncation reduces the variance of the estimate, but blows up the bias error. The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate. Can this trade off be computed experimentally? 
%}

\subsection{Simulation Results}\label{se:simResults}

Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.

\begin{figure}[tbh] %top bottom here
\centering

\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}

\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB. The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc). Dots: FRF estimates $\hat{G}$. Crosses: sample standard deviations $\hat{\sigma}$. Dashed lines: bias $\hat{b}$. White line: the true system $G_0$.}
\label{figLPMvsTrunc}
\end{figure}

In \figref{figLPMvsTrunc} one observes the following:
\begin{itemize}
\item
a decrease of the variance on the truncated estimate of about 10~dB,  i.e. a decrease of the black crosses, compared to the gray ones, is observed. %i.e. a decrease of the black crosses w.r.t.~the gray ones is observed.

\item 
the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.

\item
an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency. Still, this bias lies below the variance of the non-truncated estimate. As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked. % \JL{when performing the truncation}.

This bias depends on the time instant at which the truncation is performed, as discussed below.

\end{itemize}

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering

	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
 \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS). Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}

   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

In Fig. \ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated. Its minimum is indicated by a black dot, to the left of which a steep increase is observed. This is due to a bias error. To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.

A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error. However, it should be noted that this minimizer is unknown in practice, because it would require
the true FRF.

The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}. This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution. A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.

From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied. Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum. Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.

\subsection{Conclusion}\label{se:conclusion}

The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF. It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform. Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.

The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance. A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise. %A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.

% \bibliographystyle{IEEEtran}
% \bibliography{MikayaBibliography}
% \end{document}

### 2015-11-29 ch03-lrm/conclusion.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
+\section{Conclusion}\label{se:conclusion}
 
@@
 %A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/estimDC_TD.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
+% !TEX root =  LPMSmooth_ML_EG_JS_JL.tex
 
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
+\subsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
 
@@
 
+%\JL{
 \begin{align}
@@
 \end{align}
+%}
 
 \end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/introSmoothing.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
+% !TEX root =  LPMSmooth_ML_EG_JS_JL.tex
 
@@
 A truncation is effected at the point beyond which the data record (impulse response) is buried in noise. 
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
 This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
@@
 Within $90\%$ of the measurement window, the impulse response decays 
-
  to a level that is indistinguishable from the noise. 
-
 \end{assumption}
@@
 Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/introduction.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
+\section{Introduction}
 
@@
 \centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
+%\input{oesetup.tikz}
+\includegraphics{tikz0.pdf}
 \caption{SISO LTI discrete-time system in an output error setup.}
@@
 These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/obtainImpResp.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
+% !TEX root =  LPMSmooth_ML_EG_JS_JL.tex
 
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
+\subsection{Obtaining the Impulse Response Function}
 
@@
 
+%\JL{
 \noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
@@
 to ensure $\hat g_\mathrm{poly}(t)$ to be real.
+%}
 
@@
 This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/simResults.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
-
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
-
-\subsubsection{Spectral Nonparametric Model and Assumptions}
-
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
-\end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
-
-\begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
-
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
-\begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
-
-\begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$. 
-\end{assumption}
-
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
-
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
-
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
-
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
-
-\paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
-
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
-The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
-
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
-
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots 
-\end{matrix}
-\right.
-\\ 
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
-
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
-
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
-%(per JL)!
-
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
-
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
-\end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
-\begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
-
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
-
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
+\section{Simulation Results}\label{se:simResults}
 
@@
 
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
+\includegraphics[scale=0.9]{figLPMvsTruncWlegend}
 
@@
 
-In \figref{figLPMvsTrunc} one observes the following:
+In Figure \ref{figLPMvsTrunc} one observes the following:
 \begin{itemize}
@@
    \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
+    %\setlength\figureheight{0.45\columnwidth}
+    %\setlength\figurewidth{0.7\columnwidth}
+	%\input{pdfs.tikz}
+	\includegraphics{HistogramExpFitting.pdf}
  \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
@@
 Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-29 ch03-lrm/smoothingRMSdecrease.tex
Import LPMSmooth Paper from Mikaya

\subsubsection{Truncation Via a Statistical Test}\label{se:truncstattest}

\newcommand{\segm}[2]{\ensuremath{{#1}^{[#2]}}}
\newcommand{\RMS}{\ensuremath{\,\mathrm{rms}\,}}
\newcommand{\rms}[1]{\ensuremath{\RMS\left(#1\right)}}
\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}

To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated
%measured
 impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments. One can then gradually determine whether these segments are noise or the actual impulse response.

% 1) cut into NS segments of minimally NM samples
% 2) assume last segment == noise
%    start from back
% 3) F-test on Var, Var==RMS if dc == 0 (i.e. noise)
%    H0: s²(1) =  s²(2)
%    H1: s²(1) >  s²(2)
%    alpha >> ==> beta <<
% 4) if H1 and RMS(signal)/RMS(noise) > f
%    robustness, SNR
%    select segment i
% 5) refine until wanted resolution is obtained

\begin{enumerate}
  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By Assumption \ref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

  \item Iteration is then carried out from the last segment ($i = N_S$) towards the beginning of the impulse response. To determine whether the preceding segment $\segm{\hat{g}}{i-1}$ is completely dominated by noise,  both an $F$-test and an absolute criterion on the RMS are used.

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \cite{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances can be related to the RMS value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large RMS value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) = \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
           = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     H_0 :&\,\, s^2(i-1) = s^2(i)\\
     H_1 :&\,\, s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the RMS values of the two segments with a high confidence level of $\alpha=0.99$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  The high level of confidence ($\alpha=0.99$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \cite{Parsons1974}.
  In our case, such an error means that a part of the actual impulse response would falsely be regarded as noise, which could significantly increase the bias as information of the system is discarded.
  A Type~I error is less detrimental since, in that case, noise is falsely classified as a signal component and kept in the impulse response, thereby causing a sub-optimal value of the variance of the estimate.
  As the LPM samples are correlated over a short frequency span, the actual noise present in $\hat{g}$ may be slightly non-stationary.
  To cope with this, one can introduce other criteria which must be satisfied together with the outcome of the $F$-test.
  A criterion that shows good results is to check whether the segment $\segm{\hat{g}}{i-1}$ has an RMS value that is at least a factor $\kappa$ larger than the RMS of the noise.
  Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed. 
%  \JL{Q: doesn't this increase the probability of a Type II error?}
%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}

  \item This procedure is repeated until a segment $\segm{\hat{g}}{i-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute RMS value of the segment.
  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{i-1}$.
  One now has the choice to accept the last sample of $\segm{\hat{g}}{i-1}$ to be the last meaningful sample $t_{\mathrm{trunc}}$ for the impulse response.
  The accuracy of this estimate is limited by the length of the segment $L_S$.

  \item
  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{i-1}$ -- which may contain both the signal and noise -- yet again into smaller segments. The procedure described above is then repeated until a satisfactory, accurate $t_{\mathrm{trunc}}$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values. %rely on the RMS values to be accurate.
  To start this refinement, the last $\segm{\hat{g}}{i}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{i-1}$ cannot be asserted to be dominated by noise.

\end{enumerate}
%In Fig.~\ref{FRF_truncate_stat_EG}, this procedure is shown on the system depicted in \eqref{eq:systemSimulations}. 
This procedure is illustrated in Fig.~\ref{FRF_truncate_stat_EG} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $t_{\mathrm{trunc}} = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.  %after which all samples are fixed to a zero value for the smoothed estimate.

\begin{figure}[tbh] %top bottom here
\centering
 \setlength\figureheight{0.6\columnwidth}
 \setlength\figurewidth{0.8\columnwidth}
  \input{truncRMS.tikz}
\caption{Schematic of statistical determination of a smooth (improved) FRF. The different segments are separated by dotted lines.}
\label{FRF_truncate_stat_EG}
\end{figure}

### 2015-11-29 ch03-lrm/theory.tex
Import LPMSmooth Paper from Mikaya

--- 2015-11-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
-
-\subsection{Introduction}
-
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
-
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
-
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
-
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
-The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
-\end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
-
-In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
-
-\begin{itemize}
-
-\item
-
-The work in this paper is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
-
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency. 
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
-
-\end{itemize}
-
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup. 
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
-
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
-
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
+\section{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
 
@@
 
-\subsubsection{Spectral Nonparametric Model and Assumptions}
+\subsection{Spectral Nonparametric Model and Assumptions}
 
@@
 
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
-\paragraph{Windowing}
+\subsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
+\subsubsection{Windowing}
 The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
@@
 
-\paragraph{Formulation of the Linear LS LPM}
+\subsubsection{Formulation of the Linear LS LPM}
 The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
@@
 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak} 
-   \includegraphics{\thisDir/figs/LPMfigOmegak} 
+   \includegraphics[scale=0.92]{spectUOmegak} 
+   \includegraphics[scale=0.92]{spectYOmegak} 
+   \includegraphics{LPMfigOmegak} 
    \caption{Illustration of the LPM.
@@
 This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
-
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
-
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
-\begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
-
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
-
-\item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
-
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
-
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
-\end{enumerate}
-
-These procedures require that the following assumptions are satisfied.
-
-\begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
-\end{assumption}
-
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
-It requires that the input signal excites the whole unit circle.
-This is satisfied, for instance, by using white noise as an excitation signal.
-
-\begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
-\end{assumption}
-
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
-
- to a level that is indistinguishable from the noise.
-
-\end{assumption}
-
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
-
-\subsubsection{Obtaining the Impulse Response Function}
-
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
-\begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
-\end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
-\begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
-\end{align}
-
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
-Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
-
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
-
-The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
-A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
-%The first is a frequency-domain technique and the second is a time-domain technique.
-
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
-The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
-To this end, the following procedure is executed:
-
-\begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
-\begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)
-\end{align}
-
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
-
-\begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
-\end{align}
-
-\end{enumerate}
-
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
-
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
-
-This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
-
-\begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
-
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
-%\JL{
-\begin{align}
-\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
-\end{align}
-
-\noindent
-This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
-
-%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
-
-\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
-Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
-\begin{align}
-\mathbb{T}_\mathrm{HSNR} = \left\{
-t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
-\right\}.
-\end{align}
-
-\noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
-
-%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
-
-\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
-\begin{align}\label{eq:TmaxDef}
-\mathbb{T}_\mathrm{max} = \left\{
-t: \left| \hat g(t)\right|>
-\left|\hat g(t')\right|,
-t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
-\right\},
-\end{align}
-
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
-
-\begin{align}\label{eq:expFit}
-\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
-\end{align}
-
-\noindent
-for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, solved in a single step.
-Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
-
-\item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
-\begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
-\end{align}
-
-\noindent
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
-
-\item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
-
-\end{enumerate}
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
-\caption{Truncation of the impulse response via the fit of  an exponential.
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value.
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}.
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\label{FRF_truncate_expfitter}
-\end{figure}
-
-As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
-
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
-$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
-
-%\JL{
-\paragraph*{Considerations on the choice of $\gamma$}
-
-\begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
-
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
-If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
-
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
-\end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
-
-\subsection{Simulation Results}\label{se:simResults}
-
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
-\label{figLPMvsTrunc}
-\end{figure}
-
-In \figref{figLPMvsTrunc} one observes the following:
-\begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
-
-\item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
-
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
-Still, this bias lies below the variance of the non-truncated estimate.
-As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
-
-This bias depends on the time instant at which the truncation is performed, as discussed below.
-
-\end{itemize}
-
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
-   \label{fig:pdfAndRMSeVStruncTime}
-\end{figure}
-
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
-
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
-
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
-Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
-
-\subsection{Conclusion}\label{se:conclusion}
-
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
-Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
-
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
-A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2015-11-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
cleanup of LPMtrunc section

@@
 % \end{IEEEkeywords}
+\researchBasedOn[This section]{Lumori2014TIM}
 
@@
 
-The measurement of frequency response functions (FRFs) of dynamic systems is an important topic in the measurement society.  FRF measurement techniques are discussed, for instance, in 
+The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.  
+\gls{FRF} measurement techniques are discussed, for instance, in 
 \cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, FRFs have been shown to provide a quick insight into the dynamic properties of linear-time-invariant (LTI) systems.
+Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
 This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
 
-This paper uses nonparametric models in conjunction with the local polynomial method (LPM) \cite{pintelon2010lpm1} to estimate the complex frequency response function (FRF) in a linear-least-squares (LS) sense.
+This paper uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion. 
 The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
@@
 
-\subsection{Theory on the LPM and Windowing: OE Setup}\label{se:theoryLPMandWindowing}
+\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}\label{se:theoryLPMandWindowing}
 
@@
 The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
+\TODO{ordos are incorrect: notation-wise}
 \begin{align}\label{lpmGTaylorS}
@@
 
-The formulation of
-
- equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
+The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
 The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
@@
 
-The values $R = 2$, and $n=R+1=3$ will be used in the LPM.
+The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
 
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},
- these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
+When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
 \begin{align}\label{lpmImplQuadG}
@@
 \end{equation}
-The LPM estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-
+The \gls{LPM} estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
 \begin{equation}
@@
    \includegraphics{\thisDir/figs/LPMfigOmegak} 
-   \caption{Illustration of the LPM.
+   \caption{Illustration of the \gls{LPM}.
 Top figures: input spectrum (left) and output spectrum (right).
@@
 the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the LPM, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
+This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
 
-\section{Smoothing the FRF estimate}\label{se:smoothingFRFestimate}
+\section{Smoothing the \gls{FRF} estimate}\label{se:smoothingFRFestimate}
 
-The method for smoothing (improving) the LPM estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the LPM estimate of the FRF (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from Section \ref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
+The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions.
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from \secref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
 \begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the inverse discrete Fourier transform (IDFT) of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
+\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
 
@@
 \item
-An accurate estimate of the DC value of the FRF is computed by inspecting the average value of the tail of the estimated impulse response.
+An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response.
 
@@
 A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-% main part lies at the beginning, and one can assume that, from a certain time instant, only noise remains.)
 
-This action results in smoothing the LPM estimate of the FRF. An exponential fitting method is introduced to determine the truncation point.
+This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}. 
+An exponential fitting method is introduced to determine the truncation point.
 \end{enumerate}
@@
 
-This assumption ensures that the impulse response corresponding to the FRF can be computed (up to its mean value).
+This assumption ensures that the impulse response corresponding to the \gls{FRF} can be computed (up to its mean value).
 It requires that the input signal excites the whole unit circle.
@@
 \begin{assumption}\label{ass:imprespdecay}
-The impulse response decays exponentially with time.
+The impulse response $g(t)$ decays exponentially with time, i.e. $\exists A, a \in \PositiveRealNumbers, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
 \end{assumption}
@@
 Within $90\%$ of the measurement window, the impulse response decays 
-
  to a level that is indistinguishable from the noise.
@@
 The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the IDFT of the LPM-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the FRF in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
+}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
 
@@
 \end{align}
-
-\noindent where the estimated FRF in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
+where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
 
@@
 \end{align}
+(with $\conj{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$) to ensure $\hat g_\mathrm{poly}(t)$ to be real.
 
-\noindent 
-(with $\overline{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$)
-to ensure $\hat g_\mathrm{poly}(t)$ to be real.
-
-Smoothing of the estimated FRF requires the correct estimate of the impulse response.
-Unfortunately, the LPM presented in Section II and in \cite{schoukens2010nonparametric} does not estimate the FRF  at the frequency $\Omega_0$ (i.e.
-DC value of the FRF), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
+\TODO{fix reference Section II}
+Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response.
+Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \cite{schoukens2010nonparametric} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
+\gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
@@
 
-\subsubsection{Estimating the DC Value of the FRF}\label{se:DCvalueEst}
+\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}
 
 The correct mean value of the impulse response accounts for (i.e.
-estimates) the DC value of the FRF.
+estimates) the \gls{DC} value of the \gls{FRF}.
 A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
@@
 
-According to Assumption \ref{ass:imprespdecay}, the true impulse response tends   to zero asymptotically; and by Assumption \ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
+According to Assumption~\ref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by Assumption~\ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
 The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
@@
 \item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the LPM, as %$\hat g_\mathrm{poly}(t)$ as
+}}(t)$, estimated by the \gls{LPM}, as %$\hat g_\mathrm{poly}(t)$ as
 \begin{align}
@@
 
-The FRF estimate is smoothed by truncating the estimated impulse response function.
-The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
-%The truncation is applied at the time index after which the signal is expected not to be distinguishable from the noise
+The \gls{FRF} estimate is smoothed by truncating the estimated impulse response function. The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
 
 This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
-
-% !TEX root = LPMSmooth_ML_EG_JS_JL.tex
-%
-%
-%\subsubsection{Truncation by Fitting an Exponential on the Maxima}
-%\label{se:expFitTheory}
-%
-%An alternative truncation method is to determine the index at which the envelope of the estimated impulse response 
-%%at which the estimated impulse response 
-%gets below the noise floor.
-%%Another way of truncating is by determining from which index on the envelope of the estimated impulse response gets below the noise floor.
-%This algorithm has been implemented as follows.
 
@@
 
-%\JL{
 \begin{align}
@@
 \end{align}
-
-\noindent
 This is valid, as per Assumption \ref{ass:decay90perctime}.
-%}
 
@@
 \noindent
-(Subscript HSNR stands for High Signal-to-Noise Ratio.)
+(Subscript HSNR stands for High \gls{SNR}.)
 
@@
 \end{align}
-
-\noindent
 for $\ln A$ and $a$ in a least squares sense. 
-This is a quadratic problem in the parameters and, thus, solved in a single step.
+This is a quadratic problem in the parameters and, thus, amount to a convex optimization problem that can be solved directly.
 Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
@@
 
-\begin{align}
-%\input{theModelExpFit.tex}
-y_0(t) =& 2.583y_0(t - 1) -2.176y_0(t - 2)\dots \nonumber
-\\
-&+0.592y_0(t-3) + u(t)
-\end{align}
+\begin{equation}
+y_0(t) = 2.583y_0(t - 1) -2.176y_0(t - 2)+0.592y_0(t-3) + u(t)
+\end{equation}
 
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the Signal-to-Noise-Ratio (SNR) was 14.2~dB.
-The result is depicted in Figure \ref{FRF_truncate_expfitter}.
+The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
+The result is depicted in \figref{FRF_truncate_expfitter}.
 An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
@@
 
-%\JL{
 \paragraph*{Considerations on the choice of $\gamma$}
@@
 \begin{itemize}
-\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated FRF, but increases its bias, and vice versa.
+\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated \gls{FRF}, but increases its bias, and vice versa.
 
@@
 
-\item If one is interested in obtaining a smooth initial estimate of the FRF, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
+\item If one is interested in obtaining a smooth initial estimate of the \gls{FRF}, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
 \end{itemize}
-%}
-
-%\JL{
-%TO BE FURTHER ELABORATED: what is `significantly' below the noise floor??
-Truncation reduces the variance of the estimate, but blows up the bias error.
-The impulse response should be truncated at that index where the bias error becomes approximately equal to the standard deviation of the truncated estimate.
-Can this trade off be computed experimentally?
-%}
 
@@
 
-Figures \ref{figLPMvsTrunc} and \ref{fig:pdfAndRMSeVStruncTime} compare the LPM with and without truncation of the impulse response. They were obtained from simulations on 
-the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
+\figref{figLPMvsTrunc} and \figref{fig:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response. 
+They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{se:LPMFRFest}:
 \begin{subequations}
@@
 \end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 18.3~dB.
+where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.
 
@@
 
-\caption{Comparison of the LPM and Truncated LPM estimates of the FRF for an SNR of 18.3~dB.
-The gray plots pertain to the LPM estimate without truncation, the black ones to the LPM with truncation (trunc).
-Dots: FRF estimates $\hat{G}$.
+\caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$.
+The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc).
+Dots: \gls{FRF} estimates $\hat{G}$.
 Crosses: sample standard deviations $\hat{\sigma}$.
@@
 \item
-a decrease of the variance on the truncated estimate of about 10~dB,  i.e.
+a decrease of the variance on the truncated estimate of about $10 \unit{dB}$,  i.e.
 a decrease of the black crosses, compared to the gray ones, is observed.
@@
 \item 
-the error on the truncated LPM estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
+the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
 
@@
 As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
-% \JL{when performing the truncation}.
 
@@
 	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
- \caption{Black full line (left hand side y-axis (ordinate)): total RMS error as a function of the truncation time (the single black dot is the minimum of the RMS).
+ \caption{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}).
 Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
@@
 
-In Fig.
-\ref{fig:pdfAndRMSeVStruncTime}, the black graph is the RMS error of the estimated FRF (without the DC value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
+In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
 Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
 This is due to a bias error.
-To the right hand side of the minimum, the RMS error increases very gradually, due to an increase of the noise variance.
+To the right hand side of the minimum, the \gls{RMS} error increases very gradually, due to an increase of the noise variance.
 
-A good practice would be to truncate the impulse response at the minimizer (black dot) of the RMS error.
+A good practice would be to truncate the impulse response at the minimizer (black dot) of the \gls{RMS} error.
 However, it should be noted that this minimizer is unknown in practice, because it would require
-the true FRF.
+the true \gls{FRF}.
 
@@
 
-From the plot, we can conclude that the RMS error increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
+From the plot, we can conclude that the \gls{RMSE} increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
 On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
-The graph also shows that the RMS error of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the RMS error w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
+The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
+Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
 Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
@@
 
-The paper introduced a novel time domain method to smooth the LPM-estimate of an FRF.
-It consisted of, after obtaining the FRF from the LPM, computing the associated estimated impulse response via the inverse Discrete Fourier Transform.
+The paper introduced a novel time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}.
+It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.
 Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
 
-The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the FRF, resulting in a decreased variance.
+The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the \gls{FRF}, resulting in a decreased variance.
 A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-%A bias-variance trade-off is possible, by tuning the time at which one considers the impulse response to be indistinguishable from the noise.
 

### 2015-11-30 config/glossaries.inc.tex
cleanup of LPMtrunc section

@@
 
-\newsymbolglos{E-approx}{\approx}{Approximately equal}
-\newsymbolglos{E-bydef}{\isdef}{Equal by definition}
-\newsymbolglos{E-propto}{\propto}{Proportional to}
+\newsymbolglos{E-approx}{\approx}{Is approximately equal to \ldots}
+\newsymbolglos{E-bydef}{\isdef}{Is defined as \ldots}
+\newsymbolglos{E-propto}{\propto}{Is proportional to \ldots}
+\newsymbolglos{E-distributed}{\distributedAs}{Is distributed as \ldots}
 
@@
 \newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
+\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
 \newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
-\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
+\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
 \newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
@@
 
+\newacronym{IDFT}{IDFT}{inverse discrete Fourier transform}
 \newacronym{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
@@
 \newacronym{LRM}{LRM}{Local Rational Method}
+\newacronym{LS}{LS}{least-squares}
 \newacronym{LTI}{LTI}{linear time-invariant}
@@
 \newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}
+\newacronym{RMS}{RMS}{root-mean-square}
+\newacronym{RMSE}{RMSE}{root mean squared error}
 

### 2015-11-30 ch02-qlogms/excitation-design.tex
Some info on periodicity
Example: show period of quantized GMS

@@
   \begin{definition}[Least common (integer) multiple] \label{def:lcm-real}
-  The least common multiple of the set of values $T_k \in \RealNumbers$ for $k \in \set{1, \ldots, F}$ is  
+  The least common multiple of the set of values $T_k \in \mathbb{F}\without\set{0}$ for $k \in \mathbb{K} \isdef \set{1, \ldots, F}$ is  
   \begin{equation}
     \lcm \set{T_1, \ldots, T_F} \isdef
-      \min \Set{T |\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }
+      \min \Set{T |\forall k \in \mathbb{K}, \exists n_k \in \NaturalNumbersWithoutZero: n_k T_k = T }
    \end{equation}
    if such a minimum exists.
+   When $\mathbb{F} \in \Set{\NaturalNumbers, \Integers, \RationalNumbers}$, a minimum always exists.
+   For $\mathbb{F} = \RealNumbers$, a minimum is not guaranteed to exist (see below).
+   % more info: http://mathworld.wolfram.com/LeastCommonMultiple.html
    \end{definition}
@@
 
-  \begin{example}
+  \begin{example}\label{eg:excitation:non-periodic}
    Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
@@
   \end{example}
+  \begin{remark}
+  In practical applications each frequency will be represented as either a fixed-point or floating point number with a limited numerical precision $\delta$.
+  Hence, each frequency line $f_k$ will be approximated by a line at $\round{f_k \delta^{-1}} \delta \isdef m_k \delta$ where $m_k \in \Integers$.
+  The resulting multisine has a period 
+  \begin{equation}
+     T 
+     = \lcm \Set{T_k |  k \in \mathbb{K}} 
+     = \lcm \Set{m_k^{-1} \delta^{-1} |  k \in \mathbb{K}}
+     = \delta^{-1} \lcm \Set{m_k^{-1} |  k \in \mathbb{K}}
+     \text{.}
+  \end{equation}
+  The latter $\lcm$ always exists because $m_k^{-1}  \in \RationalNumbers$ as $m_k \in \Integers$.
+  The resulting period $T$ might, however, might be too long for practical use.
+  E.g.
+when $\delta \approx 2.2\cdot 10^{-16}$ (\code{double} precision), the period of a multisine with components as in Example~\ref{eg:excitation:non-periodic} is $T \approx 2.8 \cdot 10^{14} \unit{s} \approx 9 \cdot 10^{6} \unit{year}$.
+  \end{remark}
 

### 2015-11-30 config/glossaries.inc.tex
Some info on periodicity
Example: show period of quantized GMS

@@
 \newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
+\newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
 \newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
+\newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}
 \newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
+\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
 \newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
@@
 
-\newsymbolglos{E-approx}{\approx}{Is approximately equal to \ldots}
-\newsymbolglos{E-bydef}{\isdef}{Is defined as \ldots}
-\newsymbolglos{E-propto}{\propto}{Is proportional to \ldots}
-\newsymbolglos{E-distributed}{\distributedAs}{Is distributed as \ldots}
+\newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
+\newsymbolglos{E-bydef}{\isdef}{is defined as \ldots}
+\newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
+\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
 
@@
 \newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
-\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when B is omitted, the decimal logarithm is implied)}
+\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when $B$ is omitted, $B=10$ is implied)}
 \newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
@@
 \newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
-\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}
+\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
 

### 2015-11-30 ch02-qlogms/code/periodOfGMS.m

@@ -1,0 +1,22 @@
+close all;
+clear variables;
+clc;
+
+f = [1 3/2 pi];
+delta = eps(double(1));
+fBin        = round(f/delta);
+fQuantized  = fBin * delta;
+
+Tquant = 1./fQuantized;
+
+% lcm of rational numbers = lcm (numerators) / gcd (denominators)
+
+LCM = 1;
+GCD = gcd(fBin(1), gcd(fBin(2), fBin(3)));
+
+T = 1/delta * LCM / GCD;
+Tdy = T/24/3600;
+Tyr = Tdy/365.2425;
+
+fprintf('delta = %g\n',delta);
+fprintf('T = %g s = %g days =  %g yr\n', T, Tdy, Tyr);

### 2015-11-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
LPMtrunc: more references formatted

@@
 \gls{FRF} measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723,FDidentEd2Pintelon}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
+\cite{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007,Pintelon2012}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
 Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
-This capability is very useful for model validation and/or selection \cite{FDidentEd2Pintelon}.
+This capability is very useful for model validation and/or selection \cite{Pintelon2012}.
 
@@
 Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{pintelon2010lpm1,schoukens2010nonparametric}.
+Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{Pintelon2010LPM1,schoukens2010nonparametric}.
 Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
@@
 In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{FDidentEd2Pintelon,Mahata2006}. The following  choices are made:
+formulated in the frequency domain, consistent with \cite{Pintelon2012,Mahata2006}. The following  choices are made:
 
@@
 
-Ultimately, in Section \ref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
+Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
 
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in Section \ref{se:conclusion}.
+These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in \secref{se:conclusion}.
 
-\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}\label{se:theoryLPMandWindowing}
+\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}
+\label{se:theoryLPMandWindowing}
 
@@
 \ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{FDidentEd2Pintelon} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
+As shown in \cite{Pintelon2012} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
 \begin{equation}\label{lpmleak}
@@
 
-\subsubsection{The Hanning Window and the LPM}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
+\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
 \paragraph{Windowing}
@@
 %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{schoukens2006leakagereduction,Antoni20071723,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
+Pertinent details of the Hanning window are discussed in \cite{Schoukens2006LPM,Antoni2007FRF,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
 
 The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{FDidentEd2Pintelon}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
+As shown in \cite{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
 
 \paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length \emph{N} as outlined below \cite{schoukens2010nonparametric}.
-Section 7.2.2 of \cite{FDidentEd2Pintelon}
-gives the general formulation of the LPM for MIMO systems. The formulation in this paper is a summary for a SISO system.
+The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \cite{schoukens2010nonparametric}. 
+\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems. 
+The formulation in this paper is a summary for a \gls{SISO} system.
 
-The DFT spectra at the output of the SISO system in Fig. \ref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
+The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
 \begin{equation}\label{lpm1spectra}
@@
 
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
+The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
    \centering
-
    \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak} 
@@
 This procedure is repeated for all $\Omega_k$.}
-
    \label{LPM_Schematic_EG}
@@
 the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
-This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated FRF, $\hat{G}_\text{poly}(\Omega_k)$.
+This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.
 
 \section{Smoothing the \gls{FRF} estimate}\label{se:smoothingFRFestimate}
-
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions.
@@
 \begin{assumption}\label{ass:imprespdecay}
-The impulse response $g(t)$ decays exponentially with time, i.e. $\exists A, a \in \PositiveRealNumbers, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
+The impulse response $g(t)$ decays exponentially with time, i.e.
+$\exists A \in \PositiveRealNumbers, \exists a \in \NegativeRealNumbers \without \Set{0}, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
 \end{assumption}

### 2015-12-02 ch02-qlogms/excitation-design.tex
Example: numerical precision -> period

@@
   \begin{remark}
-  In practical applications each frequency will be represented as either a fixed-point or floating point number with a limited numerical precision $\delta$.
-  Hence, each frequency line $f_k$ will be approximated by a line at $\round{f_k \delta^{-1}} \delta \isdef m_k \delta$ where $m_k \in \Integers$.
+  In practical applications each frequency will be represented as either a fixed-point or floating point number with a limited numerical precision $\eps$.
+  Hence, each frequency line $f_k$ will be approximated by a line at $\round{f_k \eps^{-1}} \eps \isdef m_k \eps$ where $m_k \in \Integers$.
   The resulting multisine has a period 
@@
      = \lcm \Set{T_k |  k \in \mathbb{K}} 
-     = \lcm \Set{m_k^{-1} \delta^{-1} |  k \in \mathbb{K}}
-     = \delta^{-1} \lcm \Set{m_k^{-1} |  k \in \mathbb{K}}
+     = \lcm \Set{m_k^{-1} \eps^{-1} |  k \in \mathbb{K}}
+     = \eps^{-1} \lcm \Set{m_k^{-1} |  k \in \mathbb{K}}
      \text{.}
@@
   E.g.
-when $\delta \approx 2.2\cdot 10^{-16}$ (\code{double} precision), the period of a multisine with components as in Example~\ref{eg:excitation:non-periodic} is $T \approx 2.8 \cdot 10^{14} \unit{s} \approx 9 \cdot 10^{6} \unit{year}$.
+when $\eps \approx 1.2\cdot 10^{-7}$ (\code{single} precision), the period of a multisine with components as in Example~\ref{eg:excitation:non-periodic} is $T \approx 8.4 \cdot 10^{6} \unit{s} \approx 97 \unit{days}$.
+  For \code{double} precision, $\eps \approx 2.2 \cdot 10^{-16}$ and the period $T \approx 9 \cdot 10^{6} \unit{year}$.
   \end{remark}
@@
   \begin{example}
-    The~\citep{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
+    The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
     This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.

### 2015-12-02 ch02-qlogms/code/foldOver.m

@@ -1,0 +1,11 @@
+function val = foldOver(func, vals)
+    
+    if numel(vals) <= 1
+        val = vals;
+        return;
+    end
+    val = func(vals(1), vals(2));
+    for ii = 3:numel(vals)
+        val = func(val, vals(ii));
+    end
+end

### 2015-12-02 ch02-qlogms/code/periodOfGMS.m

@@ -3,20 +3,23 @@ clear variables;
 clc;
 
 f = [1 3/2 pi];
-delta = eps(double(1));
-fBin        = round(f/delta);
-fQuantized  = fBin * delta;
+
+float = 'single';
+
+epsilon = double(eps(float));
+mk      = (round(f/epsilon));
+fQuantized  = mk * epsilon;
 
 Tquant = 1./fQuantized;
 
 % lcm of rational numbers = lcm (numerators) / gcd (denominators)
-
+% http://math.stackexchange.com/questions/44836/rational-numbers-lcm-and-hcf
 LCM = 1;
-GCD = gcd(fBin(1), gcd(fBin(2), fBin(3)));
 
-T = 1/delta * LCM / GCD;
+T = 1/epsilon * LCM / vgcd(mk);
+
 Tdy = T/24/3600;
 Tyr = Tdy/365.2425;
 
-fprintf('delta = %g\n',delta);
+fprintf('epsilon = %g (%s)\n',epsilon, float);
 fprintf('T = %g s = %g days =  %g yr\n', T, Tdy, Tyr);

### 2015-12-02 ch02-qlogms/code/vgcd.m

@@ -1,0 +1,4 @@
+function val = vgcd(vals)
+    
+    val = foldOver(@gcd, vals);
+end

### 2015-12-02 ch02-qlogms/code/vlcm.m

@@ -1,0 +1,4 @@
+function val = vlcm(vals)
+    
+   val = foldOver(@lcm, vals);
+end

### 2015-12-02 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Fix some references in LPMSmooth

@@
 \gls{FRF} measurement techniques are discussed, for instance, in 
-\cite{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007,Pintelon2012}, and applied to real practical devices and systems \cite{Lim2010,Robinson1990,Behjat2010}, among others.
+\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others.
 Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
-This capability is very useful for model validation and/or selection \cite{Pintelon2012}.
+This capability is very useful for model validation and/or selection \citep{Pintelon2012}.
 
@@
 no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \cite{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \cite{Pintelon2010LPM1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \cite{fanGijbels1996LPM} with a specific focus on parametric tuning.
+Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{bendatPiersol1993,Oppenheim1983}.
+Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,schoukens2010nonparametric}.
+Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{fanGijbels1996LPM} with a specific focus on parametric tuning.
 
 The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \cite{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
+This is done by truncating the associated impulse response, as in \citep{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
 The cutoff index (truncation point) is determined by a statistically sound method.
@@
 
-Based on \cite{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
+Based on \citep{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
 A single-input-single-output (SISO) LTI system is considered.
-%, based on  \cite{schoukens2010nonparametric}.
+%, based on  \citep{schoukens2010nonparametric}.
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
@@
 
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.
+Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
 
 In this paper, however, a nonparametric technique is developed, %the identification problem is 
-formulated in the frequency domain, consistent with \cite{Pintelon2012,Mahata2006}. The following  choices are made:
+formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}. The following  choices are made:
 
@@
 
-These FRF estimates are also compared with the true LTI system ${G}_0(\Omega_k)$. Discussion of the simulation results is then followed by a conclusion in \secref{se:conclusion}.
+These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$. 
+Discussion of the simulation results is then followed by a conclusion in \secref{se:conclusion}.
 
@@
 
-Details of the theory pertaining to this section may be found in \cite{schoukens2010nonparametric}, basic aspects of which are presented below.
+Details of the theory pertaining to this section may be found in \citep{schoukens2010nonparametric}, basic aspects of which are presented below.
 
@@
 \ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \cite{Pintelon2012} and \cite{Pintelon1997} the DFT spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
+As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
 \begin{equation}\label{lpmleak}
@@
 \end{equation}
-where $U_0(k)$ is the DFT spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
-In this paper, the DFT of a signal $x(t)$ is defined explicitly as  \cite{Oppenheim1983}
+where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
+In this paper, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}
 
@@
 
-The following assumptions are consistent with \cite{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
+The following assumptions are consistent with \citep{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
 \begin{assumption}
@@
 %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \cite{Schoukens2006LPM,Antoni2007FRF,schoukens2010nonparametric,Wellstead198155} and \cite{harris1978}.
+Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,schoukens2010nonparametric,Wellstead198155} and \citep{harris1978}.
 
 The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \cite{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
+As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
 
 \paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \cite{schoukens2010nonparametric}. 
+The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{schoukens2010nonparametric}. 
 \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems. 
@@
 
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \cite{schoukens2010nonparametric}, \emph{viz}:
+The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{schoukens2010nonparametric}, \emph{viz}:
 \TODO{ordos are incorrect: notation-wise}
@@
 The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \cite{schoukens2010nonparametric}.
+The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{schoukens2010nonparametric}.
 %(per JL)!
@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response.
-Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \cite{schoukens2010nonparametric} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
+Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{schoukens2010nonparametric} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
 \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.

### 2015-12-03 ch05-initvals/InitialValuesPaper.tex
Fix pgfplots external + crossref nastiness
Set up glossaries
Improve initvals chapter: flowgraph font
Patching up some references
Some formatting (minor)

@@
 
-\setlength\onecolumnwidth{0.75\columnwidth}
+\setlength\onecolumnwidth{\columnwidth}
 
@@
 
-\tikzset{external/export=false}
 \section{Introduction}\label{se:introd}
@@
   [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
-  The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this paper (3, 4).
+  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
 \end{figure}
 
-The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the MLE optimization process in the parametric identification of each system. 
+The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the \gls{MLE} optimization process in the parametric identification of each system. 
 The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:
@@
 
-The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the MLE.
+The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the \gls{MLE}.
 
@@
 
-The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
+The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{pintGuil1998}.
 These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
@@
 These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
-Their finite sample behavior is suitable for improvement by the FRF smoothing tools, described below.
+Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.
 
@@
 
-A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \citep{Lumori2014}.
+A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014}.
 Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
-The smooth characteristics of both the exact FRF $G_0$ and the transient term
-%the leakage 
-$T$ 
-%from transients 
-allow for an optimal application of the LPM, leading to a smooth FRF estimate with the transient suppressed.
-%the elimination of both the leakage and interpolation errors.
+The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
 
-  With reference to a detailed discussion in~\citep{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+  With reference to a detailed discussion in~\citep{Lumori2014}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
 \begin{subequations}\label{lpmImplQuadG}
@@
 
-  The LPM estimate of the FRF at frequency index $k$ is the first estimated local parameter, \emph{viz}:
+  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
 \begin{equation}
@@
 
-\item
-\emph{Regularized finite impulse response (RFIR)}
+\item \emph{\Glsfirst{RFIR}}
 
-%\ML: {This is included for comparison purposes .....}
-The regularized finite impulse response (RFIR) method is a special case of the regularized autoregressive exogenous (RARX) method. 
+The \gls{RFIR} method is a special case of the \gls{RARX} method. 
 %This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.
@@
 %\JL{
-The RFIR estimator is formulated in the time domain. It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
+The \gls{RFIR} estimator is formulated in the time domain. 
+It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
 \begin{align}\label{eq:hRFIRdef}
@@
 The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
-In this paper, the Diagonal Correlated (DC) kernel is used. 
+Here, the \gls{DCkernel} is used. 
 Specifically, the element at $t_1,t_2$ of $P$ is given by
@@
  for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
- The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the log marginal likelihood (LML) of the measured output signal:
+ The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
 \begin{align}
-\text{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
+\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
 \end{align}
 where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
-This problem is solved using \texttt{fmincon} in \MATLAB.
+This problem is solved using \code{fmincon} in \MATLAB.
 
-An implementation of the RFIR estimator is available as the \texttt{arx} function in the System Identification Toolbox since \MATLAB 2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \texttt{arxoptions}.
-The hyperparameters can be determined via \texttt{arxregul}.
-More information about the RFIR estimator can be found in
+An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}.
+The hyperparameters can be determined via \code{arxregul}.
+More information about the \gls{RFIR} estimator can be found in
 ~\citep{Pillonetto201081,Chen20121525}. 
-The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
+The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
 %\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
@@
 
-%\JL{
-%{remark}
-%\label{rem:FRFasSpectrum}
-Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the FRF.
+\begin{remark}
+Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
 A corresponding parametric estimate is obtained as follows. 
-A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be 1 at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero.
+A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero.
 It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data.
 This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
-%\end{remark}
+\end{remark}
 %}
@@
 \end{align}
- which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \texttt{integral}.
+ which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
 %\comment{EG: The exact implementation is in the L2Norm function.
@@
 In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
+The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
@@
 To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
-The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \texttt{AO} and \texttt{AI} pins on the breadboard, which were wired to BNC connectors.
+The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
 Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-%  \input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
+  %\input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
   \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/elvis-spectra.tikz}
+  %\input{\thisDir/fig/elvis-spectra.tikz}
+  %TODO: simplify figure
   \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
@@
 Other systems, e.g.
-discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} commands in \MATLAB{} have also been tried.
+discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \code{cheby1}, \code{cheby2}, \code{ellip} and \code{butter} commands in \MATLAB{} have also been tried.
 
@@
 However, it is beyond the scope of this paper to determine which particular smoother is optimal in some specific circumstance.
+
+\TODO{figures from review letter}
 

### 2015-12-03 config/glossaries.inc.tex
Example: numerical precision -> period
Some formatting (minor)

@@
 
+\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
+\newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}
+
 \newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
@@
 \newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
-
-\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
 
@@
 \newacronym{BLA}{BLA}{best linear approximation}
+\newacronym{BTLS}{BTLS}{bootstrapped total least squares}
 
@@
 \newacronym{DC}{DC}{direct current}
+\newacronym{DCkernel}{DC kernel}{Diagonal Correlated (DC) kernel}
 \newacronym{DFT}{DFT}{discrete Fourier transform}
@@
 
+\newacronym{GTLS}{GTLS}{generalized total least squares}
+
 \newacronym{IDFT}{IDFT}{inverse discrete Fourier transform}
@@
 
+\newacronym{LML}{LML}{log marginal likelihood}
 \newacronym{LPM}{LPM}{Local Polynomial Method}
@@
 \newacronym{MISO}{MISO}{multiple-input single-output}
+\newacronym{MLE}{MLE}{maximum-likelihood estimator}
 \newacronym{MSE}{MSE}{mean squared error}
@@
 
-\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}
+\newacronym{RARX}{RARX}{regularized auto-regressive exogenous}
+\newacronym{RFIR}{RFIR}{regularized finite impulse response}
 \newacronym{RMS}{RMS}{root-mean-square}

### 2015-12-05 ch05-initvals/InitialValuesPaper.tex
Small changes initvals

@@
       \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
-      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \snorm{\atIter[i-1]{\theta} + \delta\theta} $
+      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \norm{\atIter[i-1]{\theta} + \delta\theta} $
       \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
@@
       \EndIf
-      \State \textbf{if} $\snorm{\delta\theta}/\snorm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
+      \State \textbf{if} $\norm{\delta\theta}/\norm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
    \EndFor
@@
 In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
-This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\snorm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
-This effectively shows an empirical cumulative distribution function of the distance measure $\snorm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}
+This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
+This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}
 
@@
 %\EG{
-  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ SNR, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
-However, by using the truncated LPM's initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
-Moreover, the RFIR initial values lead to poor estimates in less than $2\%$ ($>$ $98\%$ success rate) of the cases, since none were observed in the Monte Carlo simulation.
+  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ \gls{SNR}, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
+However, by using the truncated \gls{LPM}'s initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
+Moreover, the \gls{RFIR} initial values lead to poor estimates in less than $2\%$ ($>$ $98\%$ success rate) of the cases, since none were observed in the Monte Carlo simulation.
 
 \paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
-A close scrutiny of \figref{fig:successRateVS_SNR36N3dB} reveals that the SNR range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
+A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
 The range of improvement is approximately 5 dB where the success rate is above $90\%$.
@@
   \input{\thisDir/fig/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\eta$  obtained using the smoothers, i.e.
-$\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of SNRs, number of samples and for both test systems.
+ \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\eta$  obtained using the smoothers, i.e.
+$\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
 The $95\%$ confidence intervals are indicated by bars.}
@@
   \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed RMSE of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
- In the bottom plot, the difference $\Delta$ between both is shown.
+ \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
+ In the bottom plot, the difference between both is shown.
  Consequently, it makes sense to examine the behavior of the models in terms of $\hat{G}_0$ as long as this RMSE meets the user's requirements.}
@@
 Since the true model $G_0$ is not known for real-life systems, a practically viable reference model is needed.
-Additional measurements were performed using a VXI measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
+Additional measurements were performed using a \gls{VXI} measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
 Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\mathrm{VXI}$, and used as a reference model. 
-The VXI measurement setup is summarized as follows.
+The \gls{VXI} measurement setup is summarized as follows.
 \begin{itemize}
-  \item Signal Generator card: VXI HP E1445A.
-  \item Acquisition cards: VXI HP E1430A.
+  \item Signal Generator card: \gls{VXI} HP E1445A.
+  \item Acquisition cards: \gls{VXI} HP E1430A.
   \item Sampling frequency: $f_\mathrm{s} = 156\,250 \unit{Hz}$.
   \item A total of $558$ frequency bins were used for the estimation, in the excited frequency band $[0.1,20] \unit{kHz}$, with a frequency resolution of $35.7\unit{Hz}$, giving a measurement time of $28\unit{ms}$.
-The excitation signal was band-limited periodic noise with an RMS of $100\unit{mV}$.
+The excitation signal was band-limited periodic noise with an \gls{RMS} of $100\unit{mV}$.
   \item The input and output signals were buffered and anti-alias filtered.
@@
   The truncation method provides better estimates in many cases, but still suffers from a high variability.
-  On the other hand, the RFIR-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
+  On the other hand, the \gls{RFIR}-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
   Obviously, $\model{best}$ has the lowest cost function values of all methods.
-  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the RFIR provides the best estimate in most of the cases.
+  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the \gls{RFIR} provides the best estimate in most of the cases.
   This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.
@@
   Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
-  Practically, the median is used as a measure of location and the inter-quartile range (IQR) is used to inspect the spread as these are far more robust to outliers than e.g.
-the sample mean and variance.
+  Practically, the median is used as a measure of location and the \gls{IQR} is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
   These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
-  On the other hand, the IQR ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
+  On the other hand, the \gls{IQR} ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
 \end{remark}
@@
 \section{Conclusion}\label{se:Conclusion}
-The simulations have demonstrated that use of a smoothed non-parametric estimate of the FRF can improve the success rate of minimizing the ML cost function for the estimation of the transfer functions of linear time-invariant (LTI) systems, subjected to noisy signals.
-Specifically, two smoothing methods were used and compared: 1) the truncated LPM method, and 2) the RFIR method.
-The simulation results clearly show that the RFIR method is superior to the truncated LPM method and the existing BTLS/GTLS methods.
+The simulations have demonstrated that use of a smoothed non-parametric estimate of the \gls{FRF} can improve the success rate of minimizing the \gls{ML} cost function for the estimation of the transfer functions of \gls{LTI} systems, subjected to noisy signals.
+Specifically, two smoothing methods were used and compared: 1) the truncated \gls{LPM} method, and 2) the \gls{RFIR} method.
+The simulation results clearly show that the \gls{RFIR} method is superior to the truncated \gls{LPM} method and the existing \gls{BTLS} and \gls{GTLS} methods.
 
@@
 In most cases, the proposed initial values in the example made it possible to reduce the cost function by a factor two compared to existing methods.
-Moreover, the obtained models were validated against a high-quality measurement where the RMS error on the transfer function could be reduced by a factor of eight for most cases, due to the improved initial values.
+Moreover, the obtained models were validated against a high-quality measurement where the \gls{RMS} error on the transfer function could be reduced by a factor of eight for most cases, due to the improved initial values.
 
-Thus, the work in this paper has demonstrated the effectiveness of the studied FRF smoothing techniques in enhancing the initial values.
+Thus, the work in this paper has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
 Consequently, the ease-of-use of parametric model fitting is increased considerably by making it possible to obtain good parametric models without requiring any user interaction.

### 2015-12-07 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Fix bibliography

@@
 \gls{FRF} measurement techniques are discussed, for instance, in 
-\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others.
+\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others.
 Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
@@
 no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{bendatPiersol1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,schoukens2010nonparametric}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{fanGijbels1996LPM} with a specific focus on parametric tuning.
+Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}.
+Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}.
+Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
 
@@
 
-Based on \citep{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
+Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
 A single-input-single-output (SISO) LTI system is considered.
-%, based on  \citep{schoukens2010nonparametric}.
+%, based on  \citep{Schoukens2009LPM}.
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
@@
 
-Details of the theory pertaining to this section may be found in \citep{schoukens2010nonparametric}, basic aspects of which are presented below.
+Details of the theory pertaining to this section may be found in \citep{Schoukens2009LPM}, basic aspects of which are presented below.
 
@@
 
-The following assumptions are consistent with \citep{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
+The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (Fig. \ref{lpmtdrep}):
 \begin{assumption}
@@
 %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
-Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,schoukens2010nonparametric,Wellstead198155} and \citep{harris1978}.
+Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
 
@@
 \paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{schoukens2010nonparametric}. 
+The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}. 
 \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems. 
@@
 
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{schoukens2010nonparametric}, \emph{viz}:
+The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
 \TODO{ordos are incorrect: notation-wise}
@@
 The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{schoukens2010nonparametric}.
+The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.
 %(per JL)!
@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response.
-Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{schoukens2010nonparametric} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
+Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
 \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.

### 2015-12-07 ch05-initvals/InitialValuesPaper.tex
Fix bibliography

@@
 The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
-Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,Guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni20071723}.
+Typical measurement techniques and identification strategies of transfer functions (TFs) or \glspl{FRF} are discussed in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
 Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.
 
-Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,schoukens1999,pintGuil1998}.
+Parametric identification of \gls{LTI} systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}. 
  Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
- However, in a noisy environment, the maximum likelihood estimator (MLE) engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
+ However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
  Such local optima have a detrimental effect on the quality of the estimated model.
@@
 
-The main aim and contribution of this article is to demonstrate that smoothing a measured FRF helps to avoid local optima during the parametric estimation of the MLE of a transfer function, using deterministic optimization algorithms.
+The main aim and contribution of this article is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
 Hence, such techniques make it possible to increase the ``success rate'' (i.e.
@@
 
-In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\citep{Lumori2014} and the regularized finite-impulse response (RFIR)~\citep{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
-These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
+In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
+These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
 %The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).
@@
 Section~\ref{se:ProbForm} covers the problem formulation.
-Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the MLE.
+Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}.
 This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
@@
 
-The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{pintGuil1998}.
+The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}.
 These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
@@
 
-A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014}.
+A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014TIM}.
 Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
@@
 
-  With reference to a detailed discussion in~\citep{Lumori2014}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
 \begin{subequations}\label{lpmImplQuadG}
@@
 %\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
-The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014}.
+The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM}.
 %\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.
@@
 By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
-This can lead to a significant improvement over the classical LPM~\citep{Lumori2014}.
+This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
 
@@
 More information about the \gls{RFIR} estimator can be found in
-~\citep{Pillonetto201081,Chen20121525}. 
+~\citep{Pillonetto2010,Chen2012}. 
 The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
@@
 The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
+\TODO{meer uitleg over Clopper-Pearson}
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

### 2015-12-07 ch02-qlogms/excitation-design.tex
Small changes
Fix bibliography
stress: periodicity

@@
   Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
-
-  \TODO{put MATLAB code for each type of signal}
+  In actual implementations with limited numerical precision, this gives rise to signals that are periodic but whose period can be too long to be practically viable for periodic measurements.
+  Consequently, it is undesirable to use generalized multisines that have an overly long period.
 
@@
   It allows to analyze periodic signals on an equidistant frequency grid very efficiently.
+  For such a frequency grid, it is guaranteed that the signal is periodic in the time domain, unlike for the generalized multisines of the previous section.
 
@@
        & $\floor{\log_{\alpha} \frac{b}{a}}$
-       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
+       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
     $F_{\ClosedInterval{f, \kappa f}}$
@@
       & $\floor{\log_{\alpha} \kappa}$
-      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
+      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
     \bottomrule
@@
 
-\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}
-
 \begin{subappendices}

### 2015-12-10 ch05-initvals/InitialValuesPaper.tex
Some small changes: abbrevs, initvals

@@
 For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
-For each value-pair (SNR, $N_{3\mathrm{dB}}$), 200 simulations and estimations were performed, for each of which the success (binary result) was determined.
-The success rate $\eta$ in equation \eqref{eq:successrateTol} was then estimated as the proportion of the successes from the 200 runs.%}
+For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
+Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
+This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $200$ runs.
 
@@
 The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
-This indicates $74\%$ success for the existing methods, $95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
+This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
 \end{itemize}
@@
 \end{remark}
+\TODO{define IQR mathmatically}
 

### 2015-12-10 config/glossaries.inc.tex
Small changes initvals
Some small changes: abbrevs, initvals

@@
 \newcommand{\sym}[1]{\glssymbol{#1}}
-
-%% TERMS
 
@@
 %% ACRONYMS
-\newacronym{BLA}{BLA}{best linear approximation}
-\newacronym{BTLS}{BTLS}{bootstrapped total least squares}
+\setulcolor{gray}
+%\newcommand{\abbrev}[1]{\ul{#1}}
+\newcommand{\abbrev}[1]{#1}
+
+\newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
+\newacronym{BK}{B\&K}{\bruelkjaer}
+\newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}
 
@@
 
-\newacronym{DC}{DC}{direct current}
-\newacronym{DCkernel}{DC kernel}{Diagonal Correlated (DC) kernel}
+\newacronym{DC}{DC}{direct current (also: mean value)}
+\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
 \newacronym{DFT}{DFT}{discrete Fourier transform}
@@
 
+\newacronym{HP}{HP}{Hewlett-Packard}
+
 \newacronym{IDFT}{IDFT}{inverse discrete Fourier transform}
@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
+\newacronym{IQR}{IQR}{inter-quartile range}
 
@@
 \newacronym{MISO}{MISO}{multiple-input single-output}
+\newacronym{ML}{ML}{maximum-likelihood}
 \newacronym{MLE}{MLE}{maximum-likelihood estimator}
@@
 
-\newacronym{RARX}{RARX}{regularized auto-regressive exogenous}
-\newacronym{RFIR}{RFIR}{regularized finite impulse response}
-\newacronym{RMS}{RMS}{root-mean-square}
-\newacronym{RMSE}{RMSE}{root mean squared error}
+\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
+\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
+\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
+\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}
 
@@
 
+\newacronym{VME}{VME}{Versa Module Eurocard (\glsentrytext{IEEE} 1014)}
 \newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
+\newacronym{VXI}{VXI}{\abbrev{V}ME e\abbrev{x}tensions for \abbrev{i}nstrumentation}
 

### 2015-12-14 ch05-initvals/InitialValuesPaper.tex
initval: meas figures/table on own pages

@@
 Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
-The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the inverse DFT.
+The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the \gls{IDFT}.
 
@@
 
-\begin{figure}
+\begin{figure}[p]
   \centering
@@
 
-\begin{table}
+\begin{table}[p]
   \centering
@@
 \end{figure}
-\begin{table}
+\begin{table}[p]
   \centering

### 2015-12-29 ch01-intro/introduction.tex
Patching up some references
Voorhoeve2015 in bibliograhy

@@
 \end{figure}
-
-   \section{Contributions}
 
@@
 \end{itemize}
-The experimental work related to \chapref{sec:hinf} is also presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
+The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
 \begin{itemize}
-  \item \fullcite{Voorhoeve2015}
+  \item \fullcite{Voorhoeve2015SYSID}
   \item \fullcite{Voorhoeve2015ERNSI}
@@
 \begin{itemize}
-  \item \fullcite{vanBerkel2014Automatica}
-  \item \fullcite{Cooman2012SMACD}
-  \item \fullcite{Cooman2012DYSCO}
-  \item \fullcite{Cooman2012ERNSI}
+  \item \fullcite{vanBerkel2014Automatica},
+  \item \fullcite{Cooman2012SMACD},
+  \item \fullcite{Cooman2012DYSCO},
+  \item \fullcite{Cooman2012ERNSI}.
 \end{itemize}
-
 \end{refsection}

### 2016-01-18 ch02-qlogms/excitation-design.tex
Small tweaks
Small changes

@@
   If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
-  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
+  Intuitively, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
   From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
@@
   It is better tailored to systems which are closely aligned to the excited frequency grid.
-  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance will increase significantly and very fast.
-  This effect is more important for lowly damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.
+  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance increases significantly.
+  This effect is more important for lightly-damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.
 

### 2016-01-20 ch06-concl/conclusions.tex
Small changes
Add epigraphs

@@
 \chapter{Conclusions}
+\myEpigraph{Life can only be understood backwards; but it must be lived forwards.}{Søren Kierkegaard}{}
 
@@
   to attain a reliable estimate of the resonances present in the system.
-  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework present in \chapref{sec:excitation}. 
+  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework presented in \chapref{sec:excitation}. 
   Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited as in many cases.
@@
 
-\section{Future research}
+\section{Future perspectives}
   \subsection{Excitation design}

### 2016-01-28 front-and-back-matter/summary.inc.tex
Add summary

\chapter{Summary}
To understand, simulate and control physical systems around us, good mathematical models of these systems are required. To obtain such models, system identification is a set of powerful tools that serve to extract mathematical models from measurements of the physical world given the assumptions one makes about this world. To this end, one has to carry out different steps:
\begin{enumerate}
 \item perform experiments to observe the world in a meaningful way,
 \item inspect the measured data and check whether they are of good quality,
 \item suppress unwanted effects and extract the features of interest from the measurements,
\item fit a mathematical model to the measurement data.
\end{enumerate}

Unfortunately, the effective use of system identification hinges strongly on the skill the user possesses for each of these steps. This doctorate focuses on providing easy-to-use system identification tools. This should allow both beginning users to obtain good models with little effort, and seasoned practitioners to obtain better models with more ease.

The first part of this work focuses on the design of a good experiment. Contrary to optimal design, this work related to robust experiment design, uses very little and relatively ``unstructured'' information about the system under test such that the obtained multisine signals can be used to measure a wide class of systems effectively. This design relies on a few assumptions such as a very rough idea of the frequency band of interest and the minimal damping one expects to observe from the system to obtain a polyvalent excitation design.

The second part of this thesis describes non-parametric estimators for the frequency response function (FRF) that can estimate and suppress leakage and noise effects in the measurements. Most importantly, in this work extensions of the Local Polynomial and Local Rational Method (LPM and LRM) are investigated. This family of local estimators rely on approximating the input-output measurements in local windows in the frequency domain by either polynomial or rational models.

Consequently, such local models can be used to great effect in areas where high-order models are commonly used, e.g. for the flexible dynamics of mechanical structures. In particular, these techniques have been used on an active vibration isolation system to estimate the resonance peaks without having to rely on high-order models and the tremendous model selection effort they require. Equally important, this has also shown that these local modeling methods allow a much more accurate view of the resonance to be extracted, than one can obtain from typical FRFs by exploiting the local models to interpolate in-between the frequency grid. Hence, compared to typical FRF measurements, this can reduce the measurement time significantly.

The final part of the thesis considers the use of non-parametric smoothers to obtain better initial values to fit (global) parametric models to the measurement data. In particular, the situation with low signal-to-noise is considered since many initialization procedures tend to produce poor models. In this research, it has been shown that a very considerable improvement can be obtained, either by using a modified LPM or by using regularization. This allows users to obtain more reliable models, even from poor measurement data.

### 2016-02-01 ch05-initvals/letter.inc.tex
Include initvals review letter (prelim!)
Include review letter from initial values paper
Most of the review letter should go in the future.
Anyhow, at least the figures are already there, so we can add them
to the text.

\newcommand{\reviewer}[1]{\paragraph{#1}}

\reviewer{Reviewer \#2 (Remarks for the Author):}
\begin{quote}
The authors propose two smoothing techniques, which improve the initial estimates for transfer function identification. Figure 2 and section VI are appreciated.

Comments:

1. Please treat carefully the optimization problems. Just presenting the cost functions is not enough.

3. Which are the optimization algorithms? Clear steps must be provided. 
\end{quote}
Note that the minimization of the cost function (5) in the paper has been extensively studied in the literature (e.g. \cite[Section 9.11]{Pintelon2001} which has been referenced in the manuscript).
We have used the well-known Levenberg-Marquardt optimization algorithm to perform the non-convex optimization.
This information has also been added to the paper.

\begin{quote}
2. Do your smoothing techniques guarantee and/or keep the minimum? 
\end{quote}
The cost function involving the smoothed estimate is different from the cost function with the raw data. 
Obviously, in that case the minimum is expected to be shifted.
However, the result from this cost function is used as an \emph{initial} estimate for the cost function with the raw data. 
In the end, only the cost function with the raw data is retained.
The initial estimate does \emph{not} change the minimum of a cost function.

\begin{quote}
4. The transparency of the paper is suffering because the authors do not present how the theoretical results from sections II and III are applied in section IV.

5. The same comment is also applied for section V, i.e., low transparency. 
\end{quote}

The theoretical considerations in sections II and III are applied in section IV.
In section III, the initial estimation procedures are enumerated, and a distinct notation for each of them is given:
\begin{itemize}
  \item use of the true parameters: $\model{0}$,
  \item use of existing techniques: $\model{exist}$,
  \item use of the LPM with truncation: $\model{trunc}$,
  \item use of the RFIR: $\model{RFIR}$.
\end{itemize}
Then, the results of the latter three initialization techniques are compared to the results with $\model{0}$ in Section IV (simulations) and Section V (measurements).

\begin{quote}
6. I am not sure if section IV is actually necessary. You may drop it out. 
\end{quote}

The presence of section IV is crucial for the article, and will not be skipped, for the following reason. 
The goal of the article is to demonstrate that the use of smoothing techniques increases the success rate the minimization of the ML cost function. 
While Sections II and III introduce the methods used, Section IV actually \emph{does} the demonstration of the improvement. 
It is important to include the simulation results, because these allow to make Monte Carlo simulations at various SNR values, to obtain statistically meaningful results. 
It would be much more difficult to apply a Monte Carlo method to the measurements, since a huge number of experiments must be performed, with different experimental conditions (SNR), on a variety of different systems.

\begin{quote}
2) It is unclear how generalizable the procedure introduced by Authors is, and what is its domain of applicability. Based on section IV Demonstration (simulated data), a reader may be convinced that RFIR is the absolute winner.

So, it comes as an unpleasant surprise in section V Experimental Results to learn that RFIR only wins in $50\%$ of cases (Table I). The natural question of ``why so different'' is never discussed. It seems that a lack of ground truth in a real experiment is correctly addressed by using a response from an almost noiseless system (60dB, p.18). Could it be that in simulation two low-pass filters were investigated (each with $n_{\theta} = 5$ parameters, p.13), while in experiment pass-band filter was tested with $n_{\theta} = 9$ adjustable parameters? Having the same system tested in simulations and in experiment could partially answer this question.

However, the results in Table I do not necessarily nullify a usefulness of the RFIR as a starting point. It may be that in the cases when $\model{RFIR}$ is not the best estimate, a difference between $\model{best}$ and $\model{RFIR}$ is acceptably small. If for cases when $\model{best} = \model{RFIR}$ is much better than the second best estimate $G_{2nd}$, then it makes sense to always use RFIR, as a penalty for wrong choice would be mild.

\end{quote}

The fact that ‘only’ $50\%$ of the RFIR estimates turn out to be the best estimates does not mean that the remaining $50\%$ from RFIR are bad estimates. 
It simply means that, for the remaining $50\%$, the other methods (trunc and exist) happened to give a slightly smaller cost function. 
Since Table I is misleading, we have decided to remove it from the paper.

In \figref{fig:overview} we can compare $\model{2nd}$ and $\model{best}$.
By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
In \figref{fig:histogram}, the different methods are compared in this respect by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
From that figure it can be seen that there is little performance to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method (as measured by the cost function $V$).
The outcome is a lot less favorable for the alternative methods.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  The same data as in Fig.~10 and Fig.~11 of the paper is presented.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in the paper.
  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e. there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
  }
  \label{fig:histogram}
\end{figure}

\begin{quote}

The use of a fixed method would greatly simplify an algorithm design in any standalone autonomous toolbox. The results in Table II do not help to uncover whether such a strategy is permissible. To solve this dilemma, two histograms of differences $\Delta = \model{best} - \model{2nd}$ need to be built and shown: one for $\model{best} = \model{FRIR}$ and the other for $\model{best} \neq \model{FRIR}$. 
\end{quote}

We agree that a single method would greatly simplify the implementation of a toolbox.
However, we think that using multiple initial value strategies is a valuable approach since this makes a toolbox more robust to different conditions (SNR, frequency resolution, system order, \ldots) as it reduces the likelihood that a local optimum is hit.
This can e.g. be seen in subplot 2 of \figref{fig:distancesStress} (which is discussed further on).
A similar approach w.r.t. to combine initial values is followed in some toolboxes, e.g. \cite{FDIDENT,TDIDENT}.

Many nature-inspired optimization algorithms (such as Particle Swarm Optimization (PSO)) and stochastic optimization algorithms even use hundreds or thousands of randomized initial values, in part to avoid local optima.
But, obviously, using many initial values comes at a (considerable) increase in computational cost.

While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.

\begin{quote}
The abstract promises a better starting point for a minimization of a non-convex cost function. However, no effort is undertaken in the paper to show that improvement is expected ``in most cases'' (or, under which conditions). The boundaries between different domains of starting points leading to different local minima may be very complicated. In fact, the higher the dimension of a search space is ($n_{\theta}$), the more likely it is that the boundaries are more complicated.

It is obvious that in some cases where subsets of starting points stretch over the boundaries, a particular strategy for selecting a starting point may lead to improvement. However, the paper doesn't explain why this should happen ``in most cases''. A reader would gain more confidence in a robustness of the introduced method if its boundary of applicability were clearly spelled out (for example: the method applicable to filters of order less than ... based on extensive testing). 
\end{quote}

We agree that the complicated boundaries between attraction regions of the different local optima of a cost function makes this a hard problem.
Moreover, the intricate relationship between the actual pole locations, signal SNR, choice of excitation signal, \ldots and shape of the cost function makes that determining clear boundaries on the usability of a starting value seems intractable to us.

On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g. heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.

For the parametric estimates, we ran some additional simulations to verify the usability of the proposed initial values.
In particular, we used
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
Note: the band-pass and band-stop filters actually have a model order of 20.

The input excitation and the disturbing output noise were both white and Gaussian.
The results of a Monte Carlo simulation consisting of $100$ runs (as described above) have been summarized qualitatively in the paper (due to limited space) and are discussed below in more detail.

\TODO{add table with different transfer functions, generation code, etc. for stress test}

\begin{figure}[p]
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \centering
  %\ref{legBodes}
  \input{\thisDir/fig/bodeplots.tikz}
  \caption{Bode plots of the tested filters~\legref{leg:bode:true}. Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  Left to right: low-pass, band-pass, high-pass and band-stop.
  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
  }
  \label{fig:bodeplots}
\end{figure}

\begin{figure}[p]
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \centering
  \input{\thisDir/fig/distances.tikz}
  \caption{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.

Our general conclusion from these simulations is that RFIR performs as well (or a lot better) than the existing techniques when good models are observed.

{\footnotesize
A few additional remarks are appropriate with respect to these results:
\begin{itemize}
  \item In many of the tested situations (subplots 1,3,13-16), all methods yield a good model quality.
  \item In some situations (subplots 8, 10, 12), the model quality is generally poor. 
  The fact that for subplots 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
  \item In subplot 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
  \item The RFIR performs (significantly) better than the existing methods in various cases (subplot 4-7, 9, 11).
  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g. in subplots 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
  Particularly, subplot 2 implies that \model{best} contains initial estimates of all different techniques.
  \item For all of the tested systems (except perhaps subplot 2), the truncated LPM is not advisable over the existing methods.
\end{itemize}
}

### 2016-02-01 ch05-initvals/InitialValuesPaper.tex
Include initvals review letter (prelim!)
Include review letter from initial values paper
Most of the review letter should go in the future.
Anyhow, at least the figures are already there, so we can add them
to the text.
Table with different stress test cases

@@
 where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
-This is also the approach followed in~\citep{FDIDENT} to combine different initial estimates.
+This is similar to the approach followed in~\citep{FDIDENT} to combine different initial estimates.
 
@@
 \end{remark}
-\TODO{define IQR mathmatically}
 
@@
 \begin{equation}
+  \validationDistance{\bullet} 
+  \isdef 
   \norm{\model{\bullet} - G_{\mathrm{VXI}}}
@@
 \label{se:Generality}
-In the previous sections, the usefulness of smoothing techniques to obtain initial values has been illustrated on example systems.
-Other systems, e.g.
-discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \code{cheby1}, \code{cheby2}, \code{ellip} and \code{butter} commands in \MATLAB{} have also been tried.
+In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
+In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
+However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.
 
-No cases were observed where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
+\subsection{Limitations of the smoothers}
+On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g.
+heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
+However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.
+
+In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
+For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
+
+\subsection{Stress test of the smoothers}
+To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
+In particular, we used
+\begin{itemize}
+  \item low-pass, high-pass, band-pass and band-stop 
+  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
+\end{itemize}
+discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
+The band-pass and band-stop filters actually have a model order of 20.
+
+\TODO{add table with different transfer functions, generation code, etc. for stress test}
+
+The input excitation and the disturbing output noise were both white and Gaussian.
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:init:stress:bodes}
+  \input{\thisDir/fig/bodeplots.tikz}
+  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
+  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
+  Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
+  Left to right: low-pass, band-pass, high-pass and band-stop.
+  }
+  \label{fig:bodeplots}
+\end{figure}
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:distances}
+  \input{\thisDir/fig/distances.tikz}
+  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
+  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
+  }
+  \label{fig:distancesStress}
+\end{figure}
+
+\begin{table}[p]
+  \centering
+% \input{\thisDir/table2.tex}
+  \caption{Overview of the test cases for the initialization stress test.}
+\begin{tabular}{crlrrrr}
+\toprule
+\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta}$  &  $\eta_{\mathrm{exist}}$   &  $\eta_{\mathrm{RFIR}}$  &  $\eta_{\mathrm{best}}$ \\
+\midrule
+1  &  {Chebyshev I}  &  low-pass   &  0  &  0  &  0  &  0\\
+2  &  {Chebyshev I}  &  band-pass   &  0  &  0  &  0  &  0\\
+3  &  {Chebyshev I}  &  high-pass   &  0  &  0  &  0  &  0\\
+4  &  {Chebyshev I}  &  band-stop   &  0  &  0  &  0  &  0\\
+5  &  {Chebyshev II}   &  low-pass   &  0  &  0  &  0  &  0\\
+6  &  {Chebyshev II}   &  band-pass   &  0  &  0  &  0  &  0\\
+7  &  {Chebyshev II}   &  high-pass   &  0  &  0  &  0  &  0\\
+8  &  {Chebyshev II}   &  band-stop   &  0  &  0  &  0  &  0\\
+9  &  Elliptical   &  low-pass   &  0  &  0  &  0  &  0\\
+10   &  Elliptical   &  band-pass   &  0  &  0  &  0  &  0\\
+11   &  Elliptical   &  high-pass   &  0  &  0  &  0  &  0\\
+12   &  Elliptical   &  band-stop   &  0  &  0  &  0  &  0\\
+13   &  Butterworth  &  low-pass   &  0  &  0  &  0  &  0\\
+14   &  Butterworth  &  band-pass   &  0  &  0  &  0  &  0\\
+15   &  Butterworth  &  high-pass   &  0  &  0  &  0  &  0\\
+16   &  Butterworth  &  band-stop   &  0  &  0  &  0  &  0\\
+\bottomrule
+\end{tabular}
+\label{tbl:init:stresstest}
+\end{table}
+
+\subsection{Observations}
+The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
+
+A few remarks regarding these results are appropriate.
+\begin{itemize}
+  \item In many of the tested situations (cases 1,3,13-16), all methods yield a good model quality.
+  \item In some situations (cases 8, 10, 12), the model quality is generally poor. 
+  The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
+  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
+  \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
+  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
+  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
+  \item The RFIR performs (significantly) better than the existing methods in various cases (4-7, 9, 11).
+  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.
+in cases 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
+  Particularly, case 2 implies that \model{best} contains initial estimates of all different techniques.
+  \item For all of the tested systems (except possibly for case 2), the truncated LPM is not advisable over the existing methods.
+\end{itemize}
+
+In general, one can see from these simulations that \gls{RFIR} either performs as well as (or even better than) the existing techniques when a good estimate is obtained.
+There are no cases where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
 On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.
-
-The usefulness of particular initial estimates, e.g. $\model[init]{RFIR}$ is obviously linked to the appropriateness of the non-parametric smoother in the experimental conditions at hand.
-However, it is beyond the scope of this paper to determine which particular smoother is optimal in some specific circumstance.
-
-\TODO{figures from review letter}
 
@@
 Consequently, the ease-of-use of parametric model fitting is increased considerably by making it possible to obtain good parametric models without requiring any user interaction.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{InitEstBib}
-% \end{document}

### 2016-02-01 ch05-initvals/letter.inc.tex
Table with different stress test cases

@@
 \newcommand{\reviewer}[1]{\paragraph{#1}}
-
-\reviewer{Reviewer \#2 (Remarks for the Author):}
-\begin{quote}
-The authors propose two smoothing techniques, which improve the initial estimates for transfer function identification. Figure 2 and section VI are appreciated.
-
-Comments:
-
-1. Please treat carefully the optimization problems. Just presenting the cost functions is not enough.
-
-3. Which are the optimization algorithms? Clear steps must be provided. 
-\end{quote}
-Note that the minimization of the cost function (5) in the paper has been extensively studied in the literature (e.g. \cite[Section 9.11]{Pintelon2001} which has been referenced in the manuscript).
-We have used the well-known Levenberg-Marquardt optimization algorithm to perform the non-convex optimization.
-This information has also been added to the paper.
-
-\begin{quote}
-2. Do your smoothing techniques guarantee and/or keep the minimum? 
-\end{quote}
-The cost function involving the smoothed estimate is different from the cost function with the raw data. 
-Obviously, in that case the minimum is expected to be shifted.
-However, the result from this cost function is used as an \emph{initial} estimate for the cost function with the raw data. 
-In the end, only the cost function with the raw data is retained.
-The initial estimate does \emph{not} change the minimum of a cost function.
-
-\begin{quote}
-4. The transparency of the paper is suffering because the authors do not present how the theoretical results from sections II and III are applied in section IV.
-
-5. The same comment is also applied for section V, i.e., low transparency. 
-\end{quote}
-
-The theoretical considerations in sections II and III are applied in section IV.
-In section III, the initial estimation procedures are enumerated, and a distinct notation for each of them is given:
-\begin{itemize}
-  \item use of the true parameters: $\model{0}$,
-  \item use of existing techniques: $\model{exist}$,
-  \item use of the LPM with truncation: $\model{trunc}$,
-  \item use of the RFIR: $\model{RFIR}$.
-\end{itemize}
-Then, the results of the latter three initialization techniques are compared to the results with $\model{0}$ in Section IV (simulations) and Section V (measurements).
-
-\begin{quote}
-6. I am not sure if section IV is actually necessary. You may drop it out. 
-\end{quote}
-
-The presence of section IV is crucial for the article, and will not be skipped, for the following reason. 
-The goal of the article is to demonstrate that the use of smoothing techniques increases the success rate the minimization of the ML cost function. 
-While Sections II and III introduce the methods used, Section IV actually \emph{does} the demonstration of the improvement. 
-It is important to include the simulation results, because these allow to make Monte Carlo simulations at various SNR values, to obtain statistically meaningful results. 
-It would be much more difficult to apply a Monte Carlo method to the measurements, since a huge number of experiments must be performed, with different experimental conditions (SNR), on a variety of different systems.
-
-\begin{quote}
-2) It is unclear how generalizable the procedure introduced by Authors is, and what is its domain of applicability.
-Based on section IV Demonstration (simulated data), a reader may be convinced that RFIR is the absolute winner.
-
-So, it comes as an unpleasant surprise in section V Experimental Results to learn that RFIR only wins in $50\%$ of cases (Table I).
-The natural question of ``why so different'' is never discussed.
-It seems that a lack of ground truth in a real experiment is correctly addressed by using a response from an almost noiseless system (60dB, p.18).
-Could it be that in simulation two low-pass filters were investigated (each with $n_{\theta} = 5$ parameters, p.13), while in experiment pass-band filter was tested with $n_{\theta} = 9$ adjustable parameters?
-Having the same system tested in simulations and in experiment could partially answer this question.
-
-However, the results in Table I do not necessarily nullify a usefulness of the RFIR as a starting point.
-It may be that in the cases when $\model{RFIR}$ is not the best estimate, a difference between $\model{best}$ and $\model{RFIR}$ is acceptably small.
-If for cases when $\model{best} = \model{RFIR}$ is much better than the second best estimate $G_{2nd}$, then it makes sense to always use RFIR, as a penalty for wrong choice would be mild.
-
-\end{quote}
-
-The fact that ‘only’ $50\%$ of the RFIR estimates turn out to be the best estimates does not mean that the remaining $50\%$ from RFIR are bad estimates. 
-It simply means that, for the remaining $50\%$, the other methods (trunc and exist) happened to give a slightly smaller cost function. 
-Since Table I is misleading, we have decided to remove it from the paper.
 
@@
   \input{\thisDir/fig/overview-cost-val.tikz}
-  \caption{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
-  The same data as in Fig.~10 and Fig.~11 of the paper is presented.
+  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
   Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
@@
   \input{\thisDir/fig/special-histogram.tikz}
-  \caption{
+  \caption[Performance degradation/enhancement for selecting the second best model.]{
   Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in the paper.
@@
 While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.
-
-\begin{quote}
-The abstract promises a better starting point for a minimization of a non-convex cost function.
-However, no effort is undertaken in the paper to show that improvement is expected ``in most cases'' (or, under which conditions).
-The boundaries between different domains of starting points leading to different local minima may be very complicated.
-In fact, the higher the dimension of a search space is ($n_{\theta}$), the more likely it is that the boundaries are more complicated.
-
-It is obvious that in some cases where subsets of starting points stretch over the boundaries, a particular strategy for selecting a starting point may lead to improvement.
-However, the paper doesn't explain why this should happen ``in most cases''.
-A reader would gain more confidence in a robustness of the introduced method if its boundary of applicability were clearly spelled out (for example: the method applicable to filters of order less than ...
-based on extensive testing).
-\end{quote}
-
-We agree that the complicated boundaries between attraction regions of the different local optima of a cost function makes this a hard problem.
-Moreover, the intricate relationship between the actual pole locations, signal SNR, choice of excitation signal, \ldots and shape of the cost function makes that determining clear boundaries on the usability of a starting value seems intractable to us.
-
-On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g.
-heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
-In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
-For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
-
-For the parametric estimates, we ran some additional simulations to verify the usability of the proposed initial values.
-In particular, we used
-\begin{itemize}
-  \item low-pass, high-pass, band-pass and band-stop 
-  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
-\end{itemize}
-discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
-Note: the band-pass and band-stop filters actually have a model order of 20.
-
-The input excitation and the disturbing output noise were both white and Gaussian.
-The results of a Monte Carlo simulation consisting of $100$ runs (as described above) have been summarized qualitatively in the paper (due to limited space) and are discussed below in more detail.
-
-\TODO{add table with different transfer functions, generation code, etc. for stress test}
-
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.75\columnwidth}
-  \setlength{\figureheight}{0.6\figurewidth}
-  \centering
-  %\ref{legBodes}
-  \input{\thisDir/fig/bodeplots.tikz}
-  \caption{Bode plots of the tested filters~\legref{leg:bode:true}. Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
-  Left to right: low-pass, band-pass, high-pass and band-stop.
-  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
-  }
-  \label{fig:bodeplots}
-\end{figure}
-
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.75\columnwidth}
-  \setlength{\figureheight}{0.6\figurewidth}
-  \centering
-  \input{\thisDir/fig/distances.tikz}
-  \caption{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
-  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
-  }
-  \label{fig:distancesStress}
-\end{figure}
-
-The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
-
-Our general conclusion from these simulations is that RFIR performs as well (or a lot better) than the existing techniques when good models are observed.
-
-{\footnotesize
-A few additional remarks are appropriate with respect to these results:
-\begin{itemize}
-  \item In many of the tested situations (subplots 1,3,13-16), all methods yield a good model quality.
-  \item In some situations (subplots 8, 10, 12), the model quality is generally poor. 
-  The fact that for subplots 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
-  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
-  \item In subplot 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
-  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
-  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
-  \item The RFIR performs (significantly) better than the existing methods in various cases (subplot 4-7, 9, 11).
-  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.
-in subplots 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
-  Particularly, subplot 2 implies that \model{best} contains initial estimates of all different techniques.
-  \item For all of the tested systems (except perhaps subplot 2), the truncated LPM is not advisable over the existing methods.
-\end{itemize}
-}

### 2016-02-01 ch05-initvals/InitialValuesPaper.tex
Table with success rates for stress test
Using tolerance 0.02.

@@
 To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
-In particular, we used
+In particular, all combinations of
 \begin{itemize}
@@
 \end{itemize}
-discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
-The band-pass and band-stop filters actually have a model order of 20.
-
-\TODO{add table with different transfer functions, generation code, etc. for stress test}
+discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
+All filters $G$ have been normalized in such a way that $\norm[2]{G} = 1$.
+The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
+The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
+Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
 
@@
   \caption{Overview of the test cases for the initialization stress test.}
-\begin{tabular}{crlrrrr}
+\begin{tabular}{crlrrrrr}
 \toprule
-\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta}$  &  $\eta_{\mathrm{exist}}$   &  $\eta_{\mathrm{RFIR}}$  &  $\eta_{\mathrm{best}}$ \\
+\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta} [\%]$  &  $\eta_{\mathrm{exist}} [\%]$ &  $\eta_{\mathrm{trunc}} [\%]$   &  $\eta_{\mathrm{RFIR}} [\%]$  &  $\eta_{\mathrm{best}} [\%]$ \\
 \midrule
-1  &  {Chebyshev I}  &  low-pass   &  0  &  0  &  0  &  0\\
-2  &  {Chebyshev I}  &  band-pass   &  0  &  0  &  0  &  0\\
-3  &  {Chebyshev I}  &  high-pass   &  0  &  0  &  0  &  0\\
-4  &  {Chebyshev I}  &  band-stop   &  0  &  0  &  0  &  0\\
-5  &  {Chebyshev II}   &  low-pass   &  0  &  0  &  0  &  0\\
-6  &  {Chebyshev II}   &  band-pass   &  0  &  0  &  0  &  0\\
-7  &  {Chebyshev II}   &  high-pass   &  0  &  0  &  0  &  0\\
-8  &  {Chebyshev II}   &  band-stop   &  0  &  0  &  0  &  0\\
-9  &  Elliptical   &  low-pass   &  0  &  0  &  0  &  0\\
-10   &  Elliptical   &  band-pass   &  0  &  0  &  0  &  0\\
-11   &  Elliptical   &  high-pass   &  0  &  0  &  0  &  0\\
-12   &  Elliptical   &  band-stop   &  0  &  0  &  0  &  0\\
-13   &  Butterworth  &  low-pass   &  0  &  0  &  0  &  0\\
-14   &  Butterworth  &  band-pass   &  0  &  0  &  0  &  0\\
-15   &  Butterworth  &  high-pass   &  0  &  0  &  0  &  0\\
-16   &  Butterworth  &  band-stop   &  0  &  0  &  0  &  0\\
+1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
+2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
+3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
+4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
+5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
+6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
+7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
+8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
+9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
+10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
+11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
+12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
+13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
+14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
+15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
+16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
 \bottomrule
@@
 The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
+In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used.
 

### 2016-02-02 config/styles.inc.tex
Clean up special histogram figure

@@
 
+\pgfplotsset{degradationBox/.style={area legend,solid,draw=none,fill=TangoOrange1,opacity=0.7}}
+\pgfplotsset{degradationMedian/.style={color=TangoOrange3,solid,line width=2.0pt,opacity=0.7}}
+\pgfplotsset{degradationMarks/.style={color=TangoScarletRed2,only marks,mark=triangle*,mark options={solid,fill=TangoScarletRed1,rotate=180},opacity=0.7}}
+
+\pgfplotsset{enhancementBox/.style={area legend,solid,draw=none,fill=TangoSkyBlue1!80!white,opacity=0.7}}
+\pgfplotsset{enhancementMedian/.style={color=TangoSkyBlue2,solid,line width=2.0pt,opacity=0.7}}
+\pgfplotsset{enhancementMarks/.style={color=TangoChameleon3,only marks,mark=triangle*,mark options={solid,fill=TangoChameleon2},opacity=0.7}}
+
+\pgfplotsset{percentileLines/.style={black,dashed}}
+
 \tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}

### 2016-02-07 ch05-initvals/InitialValuesPaper.tex
initvals almost finished

@@
 
-\TODO{import references into main bibliography}
 %\comment{JL: 
@@
 
-The rest of the paper is structured as follows.
+The rest of the chapter is structured as follows.
 Section~\ref{se:ProbForm} covers the problem formulation.
@@
 where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
-%\comment{JL: note that $H_0 = 1$ in this paper, so only white noise is considered, i.e. $e(t) = v(t)$.}, 
 $e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
 For white noise, $H_0 = 1$ and $e(t) = v(t)$.
-Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this paper.
+Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
 However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
@@
 The output signal is disturbed by white random noise, resulting in noisy error-prone data.
-It is also possible to apply the estimation procedure in this paper to a system that is disturbed by colored noise, as will be demonstrated in Section~\ref{se:ExpMeas}.
+It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in Section~\ref{se:ExpMeas}.
 
@@
 with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions.
-In this paper, it is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
+\begin{assumption}
+It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
+\end{assumption}
+
+\begin{remark}
+The knowledge of the true model orders makes the analysis of the smoothers easier to carry out as we thus avoid extra calculation time required to perform model selection.
+However, these smoothers can be used in conjunction with model order selection procedures.
+\end{remark}
 
@@
 The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
-Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this paper.
+Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this chapter.
 
@@
 This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
-Stochastic optimization is not discussed in the remainder of this paper.
+Stochastic optimization is not discussed in the remainder of this chapter.
 \end{remark}
@@
   [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this paper (3, 4).
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (3, 4).
   The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
@@
 \end{subequations}
-where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.
+where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
+In this instance, $n=3$.
 
@@
 \end{equation}
-where $\gamma=1$ was used in this paper for simplicity.
+where $\gamma=1$ was used in this chapter for simplicity.
 By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
@@
 \item 
-$\model{0}$ via the true model $G_0$ as an initial estimate,
+$\model{0}$ via the true model $\true{G}$ as an initial estimate,
 \item
@@
 \item
-$\model{trunc}$ via use of the LPM with truncation as an initial estimate,
+$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
 \item
@@
 \begin{conjecture}\label{conj1}
-In this paper it is assumed that use of the true model as an initial estimate for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) is the best possible initial estimate and will allow the optimization to converge to the \emph{best local optimum}, i.e.
+The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
 $\model{0}$.
-%\JL{The associated model is denoted $\hat G_0$.}
 \end{conjecture}
+
 From this conjecture, use of the true system as an initial estimate would engender the best final estimate or hopefully even the global optimum.
-Since the true system is not really known in practice, the work in this paper compares the capability of different possible initial estimates to emulate the result that would be obtained by using the true model as an initial estimate.
+Since the true system is not really known in practice, this chapter compares the capability of different possible initial estimates to emulate the result that would be obtained by using the true model as an initial estimate.
 
@@
 Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
-This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $200$ runs.
+This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
 
@@
 
-In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
-\TODO{meer uitleg over Clopper-Pearson}
+In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
+Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
+The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
+The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
+A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
+In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
+\begin{equation}
+\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
+\end{equation}
+with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e.
+$z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
+which requires inversion of the \gls{CDF} of a normal distribution.
+However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e.
+when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta 1$~\citep{Ross2003}.
+An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
+In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
+In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
+\begin{equation}
+ \mathrm{CI}_{\mathrm{ClopperPearson}} \isdef
+ \left[
+  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)
+  \;,\;
+  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
+ \right]
+\end{equation}
+where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution that is closely related to the Binomial distribution.
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
+
 Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.
+However, since there is often a clear separation between the different techniques, no efforts have been made to try out confidence interval estimators that offer more conservative results.
 
@@
 \end{equation}
-where $n_{\theta}=5$ is the number of estimated parameters in this paper.
+where $n_{\theta}=5$ is the number of estimated parameters in this case.
 In \figref{fig:RMSE}, the empirical $\RMSE(\hat{G}_{0})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
@@
 This is similar to the approach followed in~\citep{FDIDENT} to combine different initial estimates.
+
+Alternatively, one can define the best model ($\model{best}$) and the second best model ($\model{2nd}$) as the models that comply to the inequalty
+$
+  \costFunc{}\left(\model{best}\right) < 
+  \costFunc{}\left( \model{2nd} \right) < 
+  \ldots
+$
+where $\model{best} \neq \model{2nd}$.
 
@@
 
+\section{Consequences of selecting the `best` model}
+To determine how important it is to select the 
+\TODO{justify these experiments}
+
+In \figref{fig:overview} we can compare $\model{2nd}$ and $\model{best}$.
+By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
+In \figref{fig:init:histogramEnhancement}, the different methods are compared in this respect by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
+From that figure it can be seen that there is little performance to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method (as measured by the cost function $V$).
+The outcome is a lot less favorable for the alternative methods.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/overview-cost-val.tikz}
+  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
+  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
+  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
+  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
+  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
+  \label{fig:overview}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \ref{leg:init:secondBest}
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.60\figurewidth}
+  \input{\thisDir/fig/special-histogram.tikz}
+  \caption[Performance degradation/enhancement for selecting the second best model.]{
+  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
+  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
+  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
+  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
+  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
+  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
+  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e.
+there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
+  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
+  }
+  \label{fig:init:histogramEnhancement}
+\end{figure}
+
 \section{Remark on Generality}
@@
 
-In particular for RFIR, a simulation study in~\cite{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
+In particular for RFIR, a simulation study in~\citep{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
 For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
@@
 
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \centering
-  \ref{leg:init:stress:bodes}
-  \input{\thisDir/fig/bodeplots.tikz}
-  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
-  For each filter, two of the parametric estimates $\model{\bullet}$ are shown per method.
-  Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
-  Left to right: low-pass, band-pass, high-pass and band-stop.
-  }
-  \label{fig:bodeplots}
-\end{figure}
-
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \centering
-  \ref{leg:distances}
-  \input{\thisDir/fig/distances.tikz}
-  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
-  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
-  }
-  \label{fig:distancesStress}
-\end{figure}
-
-\begin{table}[p]
-  \centering
-% \input{\thisDir/table2.tex}
+\begin{table}
+  \centering
   \caption{Overview of the test cases for the initialization stress test.}
@@
 The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
-In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used.
+In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm{\model{\bullet} - \true{G}} < tol$.
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:init:stress:bodes}
+  \input{\thisDir/fig/bodeplots.tikz}
+  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
+  For each filter, two (randomly selected) instanced of the parametric estimates $\model{\bullet}$ are shown per method.
+  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
+  % Left to right: low-pass, band-pass, high-pass and band-stop.
+  }
+  \label{fig:bodeplots}
+\end{figure}
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:distances}
+  \input{\thisDir/fig/distances.tikz}
+  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
+  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
+  }
+  \label{fig:distancesStress}
+\end{figure}
 
@@
 
-Thus, the work in this paper has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
-Consequently, the ease-of-use of parametric model fitting is increased considerably by making it possible to obtain good parametric models without requiring any user interaction.
+Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
+Consequently, the ease-of-use of parametric model fitting can be increased considerably by making it possible to obtain good parametric models without requiring any additional user interaction.

### 2016-02-07 ch05-initvals/letter.inc.tex
Clean up special histogram figure
initvals almost finished

@@
 \newcommand{\reviewer}[1]{\paragraph{#1}}
-
-In \figref{fig:overview} we can compare $\model{2nd}$ and $\model{best}$.
-By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
-In \figref{fig:histogram}, the different methods are compared in this respect by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
-From that figure it can be seen that there is little performance to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method (as measured by the cost function $V$).
-The outcome is a lot less favorable for the alternative methods.
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/overview-cost-val.tikz}
-  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
-  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
-  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
-  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
-  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
-  \label{fig:overview}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.75\columnwidth}
-  \setlength{\figureheight}{0.60\figurewidth}
-  \input{\thisDir/fig/special-histogram.tikz}
-  \caption[Performance degradation/enhancement for selecting the second best model.]{
-  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in the paper.
-  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
-  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
-  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
-  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
-  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
-  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e.
-there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
-  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
-  }
-  \label{fig:histogram}
-\end{figure}
 

### 2016-02-07 ch06-concl/conclusions.tex
initvals almost finished

@@
   On the other hand, the \gls{LRM} and its variants discussed in \chapref{sec:nonparametric} provide some local information regarding the shape of the \gls{FRF} and hence also the transfer function.
-  The usefulness has already been seen in \chapref{sec:hinf} in connection to the computation of the \Hinf norm of a system.
+  The usefulness has already been illustrated in \chapref{sec:hinf} in connection to the computation of the \Hinf norm of a system.
   Intrinsically, these local rational methods approximate the transfer function by a local model, or, equivalently a set of local poles and zeros.
-  Especially for resonant poles, one can expect that these local poles are closely linked to the global (actual) poles of a system.
+  Especially for resonant poles, one can expect that these local poles are closely linked to the global (physical) poles of a system.
   As such, those could provide a valuable initialization strategy if the redundant local pole/zero information of neighboring windows can be reduced to a single global pole/zero initial value.
+  Probably techniques in model order reduction could provide a good starting point to calculate such initial values.
   \TODO{optimal smoother}

### 2016-02-07 ch05-initvals/InitialValuesPaper.tex
Some changes to initval

@@
 In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
-\begin{equation}
- \mathrm{CI}_{\mathrm{ClopperPearson}} \isdef
- \left[
-  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)
-  \;,\;
+\begin{align}
+ \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
+ \underline{\eta} &\isdef 
+  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
+  \overline{\eta} &\isdef
   \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
- \right]
-\end{equation}
+\end{align}
 where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution that is closely related to the Binomial distribution.
@@
   \centering
-  \includegraphics[width=0.8\onecolumnwidth]{\thisDir/fig/measurement.pdf}
+  \includegraphics[width=0.6\onecolumnwidth]{\thisDir/fig/measurement.pdf}
   \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  %\input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
+  \input{\thisDir/fig/bode-bk1613.tikz}
   \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
   The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
+  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
   \label{fig:bk1613}

### 2016-02-07 ch05-initvals/InitialValuesPaper.tex
More plot, more info on CIE, 2nd order effects

@@
 However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e.
-when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta 1$~\citep{Ross2003}.
-An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
+when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta \leq 1$~\citep{Ross2003}.
+An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
 In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
@@
  \underline{\eta} &\isdef 
-  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
+  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
   \overline{\eta} &\isdef
@@
 \end{align}
-where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution that is closely related to the Binomial distribution.
+where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution.
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
 
-Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.
-However, since there is often a clear separation between the different techniques, no efforts have been made to try out confidence interval estimators that offer more conservative results.
+In this chapter, the Clopper-Pearson method--as implemented in \MATLAB's \code{binofit}-- is used whenever confidence bounds are shown.
+Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.
+However, since there is often a clear separation between the different techniques, no efforts have been made to use confidence interval estimators that offer less conservative results.
 
@@
 \section{Consequences of selecting the `best` model}
-To determine how important it is to select the 
-\TODO{justify these experiments}
+To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
+To do so, we inspect the performance by means of the cost function (used during estimation) and by means of the validation distance.
+The datasets used in this analysis are those from the measurements, but similar results can be obtained from the other data sets.
 
@@
 By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
-In \figref{fig:init:histogramEnhancement}, the different methods are compared in this respect by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
-From that figure it can be seen that there is little performance to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method (as measured by the cost function $V$).
-The outcome is a lot less favorable for the alternative methods.
+In \figref{fig:init:histogramEnhancement}, the different methods are compared by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
+As such, each column in the figure indicates the performance of this method when it is not the `best'.
+Obviously, when we consider the cost function used during estimation (left subfigure), we can only degrade the performance by construction of $\model{best}$.
+For the validation data, however, this is no longer guaranteed as can be seen in the right subplot.
+On average, there is very little performance that can be gained from not using $\model{best}$, however, for two or three data points, there is a considerable improvement.
+From that figure it can also be seen that there is little performance to lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method.
+The outcome is less favorable for the alternative methods.
+For $\model{exist}$ it can be seen that selecting those instead of $\model{best}$  degrades the validation performance by $10$ or even more in $75\%$ of the cases.
+The situation is already less severe for $\model{trunc}$ (in $75\%$ of the cases, the degradation is larger than $0.5$).
 

### 2016-02-08 ch05-initvals/InitialValuesPaper.tex
Some work on init-vals

@@
   \setlength{\figureheight}{0.68\figurewidth}
-  %\input{\thisDir/fig/elvis-spectra.tikz}
+  \input{\thisDir/fig/elvis-spectra.tikz}
   %TODO: simplify figure
@@
   Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
-  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is negligible.}
+  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
   \label{fig:overview}
@@
   The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
-  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the data shows when method $\bullet$ is \emph{not} selected as the `best' method.
+  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the plot shows when method $\bullet$ is \emph{not} selected as the `best' method.
   The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
@@
 \end{itemize}
-discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
-All filters $G$ have been normalized in such a way that $\norm[2]{G} = 1$.
+discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
+Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
 The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
@@
 
-The input excitation and the disturbing output noise were both white and Gaussian.
+The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
+Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
 
@@
 Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
-Consequently, the ease-of-use of parametric model fitting can be increased considerably by making it possible to obtain good parametric models without requiring any additional user interaction.
+Consequently, the quality of parametric estimates can be increased considerably by using non-parametric \gls{FRF} models to initialize the non-convex optimization problem of fitting a rational transfer function model.
+Hence, the ease-of-use of parametric model fitting can be increased significantly by having high-quality non-parametric \gls{FRF} models.
+This comes at a limited cost for the end-user: in principle these smoothers can be tried without any additional intervention by the user.
+The only disadvantage is the additional computational effort required and hence also the increase in wall clock time to obtain a parametric estimate.
+However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest.

### 2016-02-08 ch05-initvals/InitialValuesPaper.tex
Init-vals: more or less ready

@@
 
-The main aim and contribution of this article is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
+The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
 Hence, such techniques make it possible to increase the ``success rate'' (i.e.
@@
 
-In this chapter, the Clopper-Pearson method--as implemented in \MATLAB's \code{binofit}-- is used whenever confidence bounds are shown.
+In this chapter, the Clopper-Pearson method---as implemented in \MATLAB's \code{binofit}---is used whenever confidence bounds are shown.
 Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.

### 2016-02-08 ch05-initvals/letter.inc.tex
Init-vals: more or less ready

@@
-\newcommand{\reviewer}[1]{\paragraph{#1}}
+% \begin{quote}
 
-\begin{quote}
-
-The use of a fixed method would greatly simplify an algorithm design in any standalone autonomous toolbox.
+% The use of a fixed method would greatly simplify an algorithm design in any standalone autonomous toolbox.
 The results in Table II do not help to uncover whether such a strategy is permissible.
 To solve this dilemma, two histograms of differences $\Delta = \model{best} - \model{2nd}$ need to be built and shown: one for $\model{best} = \model{FRIR}$ and the other for $\model{best} \neq \model{FRIR}$.
-\end{quote}
+% \end{quote}
 
-We agree that a single method would greatly simplify the implementation of a toolbox.
-However, we think that using multiple initial value strategies is a valuable approach since this makes a toolbox more robust to different conditions (SNR, frequency resolution, system order, \ldots) as it reduces the likelihood that a local optimum is hit.
-This can e.g. be seen in subplot 2 of \figref{fig:distancesStress} (which is discussed further on).
-A similar approach w.r.t. to combine initial values is followed in some toolboxes, e.g. \cite{FDIDENT,TDIDENT}.
+% We agree that a single method would greatly simplify the implementation of a toolbox.
+% However, we think that using multiple initial value strategies is a valuable approach since this makes a toolbox more robust to different conditions (SNR, frequency resolution, system order, \ldots) as it reduces the likelihood that a local optimum is hit.
+% This can e.g. be seen in subplot 2 of \figref{fig:distancesStress} (which is discussed further on).
+% A similar approach w.r.t. to combine initial values is followed in some toolboxes, e.g. \cite{FDIDENT,TDIDENT}.
 
-Many nature-inspired optimization algorithms (such as Particle Swarm Optimization (PSO)) and stochastic optimization algorithms even use hundreds or thousands of randomized initial values, in part to avoid local optima.
-But, obviously, using many initial values comes at a (considerable) increase in computational cost.
+% Many nature-inspired optimization algorithms (such as Particle Swarm Optimization (PSO)) and stochastic optimization algorithms even use hundreds or thousands of randomized initial values, in part to avoid local optima.
+% But, obviously, using many initial values comes at a (considerable) increase in computational cost.
 
-While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.
+% While this discussion and this inherent trade-off is very interesting, we think this is outside of the scope of the paper where we only wish to demonstrate that smoothing techniques such as RFIR are a worthwhile source of initial values, but not necessarily the only one.

### 2016-02-11 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some minor things
Some minor fixes in captions etc.

@@
 The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in \citep{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
+This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
 The cutoff index (truncation point) is determined by a statistically sound method.
@@
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in Fig.
-1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
+This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
 \begin{equation}\label{lpmtd1}
@@
 
-Using convolution, the noiseless output signal in Fig.
-\ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
+Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
 As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
@@
 
-The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (Fig. \ref{lpmtdrep}):
+The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (\figref{lpmtdrep}):
 \begin{assumption}
@@
 \begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
+G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
+\bigO{\left(\frac{r}{N}\right)^{(R+1)}},
 \\
 \label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
+T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
+\bigO{  \left(\frac{r}{N}\right)^{(R+1)}  }
+,
 \\
@@
 \begin{assumption}\label{ass:imprespdecay}
-The impulse response $g(t)$ decays exponentially with time, i.e.
+The impulse response $g(t)$ decays exponentially over time, i.e.
 $\exists A \in \PositiveRealNumbers, \exists a \in \NegativeRealNumbers \without \Set{0}, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
@@
  to a level that is indistinguishable from the noise.
-
 \end{assumption}
@@
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct.
-This anomaly is rectified by developing a simple estimator of the mean value, presented below.
+This limitation is lifted by developing a simple estimator of the mean value, presented below.
 
 \subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}
-
 The correct mean value of the impulse response accounts for (i.e.
@@
 The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
-This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
+This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
 Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.

### 2016-02-11 ch05-initvals/InitialValuesPaper.tex
Some minor fixes in captions etc.

@@
 \end{itemize}
-discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
+discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
 Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
@@
 Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
+See \tabref{tbl:init:stresstest} for an overview of the filters and  \figref{fig:bodeplots} for the corresponding bode plots.
 

### 2016-02-11 ch05-initvals/InitialValuesPaper.tex
Corrections Johan: ch05 (part 1) + compu complex

@@
 Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}.
-This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
+This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
 In Section~\ref{se:Generality} the generality of the results is discussed briefly.
@@
 
-The output signal is disturbed by white random noise, resulting in noisy error-prone data.
-It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in Section~\ref{se:ExpMeas}.
+In this chapter we assume that the output signal is disturbed by random noise, resulting in noisy error-prone data.
+For the simulations, white noise is used.
+It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{se:ExpMeas}.
 
@@
 
-With reference to equation (\ref{lpmtd1}), the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
-\begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t)
+With reference to equation \eqref{lpmtd1}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
+\begin{equation}
+    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in \left( - \infty, + \infty \right)
 \label{ABpolys}
 \end{equation}
-where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation (\ref{lpmtd1}) that
+where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation \eqref{lpmtd1} that
 \begin{equation}
@@
 with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions.
+\TODO{explain init/end conditions in this context}
 \begin{assumption}
@@
 \item
-\emph{Using the true model ($G_0$) as initial estimate}
+\emph{Using the true model ($\true{G}$) as initial estimate}
 
@@
 
+\section{Computational effort}\label{sec:initvals:computation}
+While improved initial values yield better models of an improved quality, their generation does require some computational effort.
+Although the amount of available computing power has been steadily increasing over the last decades, it remains important to keep an eye on the computing effort required to estimate a model or, in this case, to generate the starting values required to estimate a model.
+E.g.
+in embedded applications where computing power and physical power consumption are  restrained and which have been attracting a lot of attention in data science during the recent years\TODO{cite arduino, rasbpi}, it remains an important factor to account for.
+
+Here, we will discuss two aspects of the computational effort very briefly.
+On the one hand, the computation time, as measured on a physical computer with a practical implementation of the algorithms, gives a rough idea of how these methods may perform in practice.
+On the other hand, the asymptotic complexity of the different smoothers is investigated. 
+While such asymptotics give little insight in practical running times, they are valuable tools to see how well (or poor) such methods scale up towards larger datasets.
+
+\subsection{Practical runtime}
+In practical measurements of the computation time for any piece of software, one typically distinguishes between different kinds of `time'.
+\begin{itemize}
+  \item The wall-clock time $\wallclocktime$, sometimes called `real time`, is the time difference between the start and end of the program under test.
+  \item The \glsentryshort{CPU} time $\cputime$, is the amount of time that the \glspl{CPU} actually spends executing the program under test.
+\end{itemize}
+This distinction is necessary for multi-tasking environments (such as computer), since during the execution of the program under test, the \gls{CPU} may spend a while to execute other programs in the background.
+The latter obviously requires a small amount of wall-clock time, but it does not increase the \gls{CPU} time of the program:
+\begin{equation}
+  \wallclocktime = \cputime + t_{\mathrm{other\;processes}}
+\end{equation}
+for a single-core \gls{CPU}.
+
+In summary, the $\cputime$ is an indication of the computational effort required to execute the algorithm, whereas $\wallclocktime$ indicates the amount of time a user has to wait for the program.
+In this case $\cputime$ is hence the most relevant of both, since $\wallclocktime$ is also determined by what other programs the user is running at the same time.
+
+Unfortunately, \MATLAB, like many other interpreted languages, does not provide any feature to measure $\cputime$ of a segment of code.
+Instead, the typical \code{tic} and \code{toc} functions measure the wall-clock time.
+To reduce the effect of other running programs and one-time actions (e.g.
+just-in-time compilation, caching, \ldots), it is a common practice~\citep{McKeeman2008} to repeatedly measure $\wallclocktime$ and retain the minimum (as an approximation for $\cputime$) and/or the median (to reduce the effect of other programs claiming the \gls{CPU} for extended amounts of time).
+
+In this case, the \MATLAB function \code{timeit}~\citep{matlab:timeit} has been used to measure the timing of the different functions.
+This function  reports the median wall-clock time and chooses the number of repetitions automatically.
+The timings have been measured on an Early 2013 MacBook Pro Retina 15-inch with $2.7\unit{GHz}$ Intel Core i7 \gls{CPU} and $16 \unit{GB}$ \gls{RAM} running Mac OS X 10.11.3 and \MATLAB R2015b.
+The recommendations from the white paper by \citet{McKeeman2008} have been followed during these measurements.
+
+\TODO{describe settings for the experiment: $N$, etc.}
+
+The observed timings are shown in \TODO{tableref}.
+\TODO{discuss timings}
+
+\TODO{table summary}
+
+\subsection{Asymptotic runtime}
+For the asymptotic runtime, we are mainly interested in how each of the smoothers scale with the size of the dataset, i.e. the number of samples $N$.
+
+% See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation
+
+The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear system requires $\bigO{n^3}$ operations in general~\citep{Golub1996}.
+The truncation of the impulse response relies on linear regression which takes $\bigO{n_{\theta}^2 N}$ operations.
+Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N}$ since both $n_{\theta}$ and $N_W$ are typically small.
+
+Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
+Using general methods, this is an operations that requires $\bigO{N^3}$ time.
+% However, due to the Toeplitz structure~\citep{Heinig2011} of the regression matrix, this can be solved in $\bigO{N^2}$.
+
+It can be seen that the local modeling methods scale more favorably than e.g. \gls{RFIR}.
+
+\subsection{Implementation aspects}
+\TODO{hint towards parallization}
+\TODO{most costly: iteration}
+
 \section{Conclusion}\label{se:Conclusion}

### 2016-02-11 ch05-initvals/InitialValuesPaper.tex
Add TODOs for most of Johan's comments

--- 2016-02-08 ch05-initvals/InitialValuesPaper.tex
@@
 %}
-
-\section{Introduction}\label{se:introd}
-
-The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
-Typical measurement techniques and identification strategies of transfer functions (TFs) or \glspl{FRF} are discussed in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
-Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.
-
-Parametric identification of \gls{LTI} systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}. 
- Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
- However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
- Such local optima have a detrimental effect on the quality of the estimated model.
-
- In the perspective of developing identification tools that require as little user interaction as possible, it is important to increase the probability of the optimization algorithm to produce good estimates, or preferably even the global optimum.
- However, when noisy input-output measurements are to be processed, the presence of noise obstructs a clear view of the actual system behavior, especially for poor signal-to-noise ratios (SNRs).
- In non-parametric identification, the presence of noise is typically mitigated by averaging multiple measurements or using smoothing techniques.
-
-The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
-Hence, such techniques make it possible to increase the ``success rate'' (i.e.
-the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
-%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
-
-In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
-These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
-%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).
-
-The rest of the chapter is structured as follows.
-Section~\ref{se:ProbForm} covers the problem formulation.
-Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}.
-This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
-In Section~\ref{se:Generality} the generality of the results is discussed briefly.
-Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.
-
-% !TEX root =  InitialValuesPaper.tex
-
-\section{Problem formulation}\label{se:ProbForm}
-%\begin{itemize}
-%\item
-%Block schematic of the output error framework
-
-%\JL{In this section, the assumptions on the system and the noise are given, and the associated Maximum Likelihood estimator, formulated in the frequency domain.
-The latter turns out to be a non-convex function in the parameters, requiring initial estimates.
-The obtention of those is discussed in the subsequent section.}
-
-In this section, the assumptions on the system and the noise are presented, together with the associated MLE (formulated in the frequency domain), which turns out to be a non-convex function in the parameters, requiring initial estimates.
-The procedure for obtaining the initial estimates is discussed in the subsequent sections.
-
-\subsection{System Setup Framework and Model}
-\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input.
-The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well.
-The full mathematical model of the system is
-\begin{equation}\label{lpmtd1}
-y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
-\end{equation}
-%\comment{We don't have any results with colored noise yet!}
-where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
-$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
-For white noise, $H_0 = 1$ and $e(t) = v(t)$.
-Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
-However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
-
-\begin{figure}[tbh] %top bottom here
-\centering
-\input{\thisDir/fig/oesetup.tikz}
-\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
-\label{fig:oesetup}
-\end{figure}
-
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
-
-The output signal is disturbed by white random noise, resulting in noisy error-prone data.
-It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in Section~\ref{se:ExpMeas}.
-
-\subsection{Parametric System Model}
-
-With reference to equation (\ref{lpmtd1}), the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
-\begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t)
-\label{ABpolys}
-\end{equation}
-where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation (\ref{lpmtd1}) that
-\begin{equation}
-    G_0(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
-    \text{.}
-\end{equation}
-
-From~\citep[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
-\begin{align}
-A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
-\label{DFTspectra}
-\end{align}
-with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions.
-\begin{assumption}
-It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
-\end{assumption}
-
-\begin{remark}
-The knowledge of the true model orders makes the analysis of the smoothers easier to carry out as we thus avoid extra calculation time required to perform model selection.
-However, these smoothers can be used in conjunction with model order selection procedures.
-\end{remark}
-
-\subsection{Parametric Identification Algorithm}\label{se:paramIdentAlgo}
-
-The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
-\begin{equation}
-  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
-\end{equation}
-Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
-\begin{equation}\label{eq:MLEcf}
-V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
-\end{equation}
-for $N$ measurements and when $\varepsilon$ denotes the error in equation (\ref{DFTspectra}),  \emph{viz}.:
-\begin{align}
-\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
-\end{align}
-The variance of the error is of the form:
-\begin{equation}\label{eq:sigmaEps}
-\begin{split}
-\sigma_\varepsilon^2(k,\theta) 
-  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
-   +  |B(k,\theta)|^2\sigma_U^2(k) \\
-  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
-\end{split}
-\end{equation}
-where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known?
-where do you use that?
-how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$.
-Isn't it the same thing?},
-%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
-and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
-Here, $\overline{B}$ denotes the complex conjugate of $B$.
-%\comment{use $\sigma^2_U$ instead}
-
-Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
-The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
-Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this chapter.
-
-\begin{algorithm}
-\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
-\begin{algorithmic}[1]
-  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
-  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
-%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
-   \For{$i$ \textbf{in} $1 \to \infty$}
-      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
-      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
-      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
-      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
-      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \norm{\atIter[i-1]{\theta} + \delta\theta} $
-      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
-          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
-      \Else
-          \State $\lambda \gets 0.4 \lambda$
-      \EndIf
-      \State \textbf{if} $\norm{\delta\theta}/\norm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
-   \EndFor
-%\EndFunction
-\end{algorithmic}
-\end{algorithm}
-
-\begin{remark}
-Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
-This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
-Stochastic optimization is not discussed in the remainder of this chapter.
-\end{remark}
-
-\section{Methodology}\label{se:MethodEg}
-In this section, the considered methods for obtaining the initial estimates of $\theta$ are briefly explained.
-Then their influence on the success rate of the maximum likelihood estimator is described.
-%}
-
-\subsection{Initial Estimates Procedure}\label{se:initEstProcs} %{Obtaining initial estimates}
-
-%\begin{itemize}
-%\item
-%Obtain a good estimate of the FRF of the system by using the LPM: short description + reference
-
-\begin{figure}
-  \centering
-  \includegraphics
-  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (3, 4).
-  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
-\end{figure}
-
-The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the \gls{MLE} optimization process in the parametric identification of each system. 
-The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:
-
-\begin{enumerate}
-\item
-\emph{Using the true model ($G_0$) as initial estimate}
-
-The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the \gls{MLE}.
-
-\item
-\emph{Quadratic approximations of the ML}
-
-%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
-These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$.
-These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$).
-Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}
-
-The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}.
-These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
-$\theta$.
-These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
-Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.
-
-\item
-\emph{Local polynomial method (LPM) with truncation}
-
-A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014TIM}.
-Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
-The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
-
-  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
-\begin{subequations}\label{lpmImplQuadG}
-\begin{align}
-G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
-\\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
-\end{align}
-\end{subequations}
-where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
-In this instance, $n=3$.
-
-  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
-\begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
-\text{.}
-\end{equation}
-This procedure is repeated for all $k$ in the frequency band of interest.
-
-%The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.
-
-\emph{Impulse response truncation}. 
-%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
-The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM}.
-%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.
-
-The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
-\begin{equation}
-  g_{\mathrm{trunc}}(t) = 
-  \begin{cases}
-    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
-    0                    & t \geq \tau_{\mathrm{trunc}}
-  \end{cases}
-  \text{.}
-\end{equation}
-To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
-Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
-\begin{equation}
-  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
-  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
-  \text{,}
-\end{equation}
-where $\gamma=1$ was used in this chapter for simplicity.
-By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
-This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
-
-\item \emph{\Glsfirst{RFIR}}
-
-The \gls{RFIR} method is a special case of the \gls{RARX} method. 
-%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.
-
-%\JL{
-The \gls{RFIR} estimator is formulated in the time domain. 
-It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
-\begin{align}\label{eq:hRFIRdef}
-\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
-\end{align}
-where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
-Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
-Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
-The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
-Here, the \gls{DCkernel} is used. 
-Specifically, the element at $t_1,t_2$ of $P$ is given by
-\begin{equation}
-P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
-\end{equation}
- for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
- The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
-\begin{align}
-\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
-\end{align}
-where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
-This problem is solved using \code{fmincon} in \MATLAB.
-
-An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}.
-The hyperparameters can be determined via \code{arxregul}.
-More information about the \gls{RFIR} estimator can be found in
-~\citep{Pillonetto2010,Chen2012}. 
-The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
-%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
-\end{enumerate}
-
-\begin{remark}
-Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
-A corresponding parametric estimate is obtained as follows. 
-A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero.
-It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data.
-This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
-\end{remark}
-%}
-
-%\comment{JL: one could remove the subsection below (why?
-see my comments below), and mention that the the above initial estimates are then fed to the MLE, with the raw data, to obtain the final estimates.}
-
-%\subsection{Genesis of the Initial Estimates} 
-%\comment{JL: why `genesis'? This section is actually where you use the initial estimates, not their origin.}
-%{Deploying the initial estimates}
-
-%\comment{ML: Fig. \ref{fig:flowgraph} should include an additional path for RFIR/RARX, and the accompanying text (below) is to be modified accordingly.}
-%Fig.
-\ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart?
-It has actually been explained in further details in \sectref{se:initEstProcs}.}
-%\begin{enumerate}
-%\item (Left (first) path of the flowchart): The true model $G_0$ as initial values,
-%\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
-%\item (Third path from the left of the flowchart): The LPM-truncated initial values with BTLS and GTLS, and  
-%%\item (Right (fourth) path of the flowchart): The RFIR initial values with BTLS and GTLS.  
-%\end{enumerate}
-
-%\JL{
-%The main contribution of this paper is to demonstrate that $\hat G_\mathrm{trunc}$ (third path) yields an improvement over $\hat G_\mathrm{exist}$ (second path).
-\comment{JL: these symbols haven't been introduced yet.
-I'm getting quite confident that this subsection can be removed.}The quantification of this improvement is formally introduced in the next section.
-%}
-
-%The latter 2 ....schematic is configured to include connections of the initial values and the input to the LPM block and/or to the MLE block(s) for estimation purposes.
-%\end{itemize}
-%\section{Example}\label{se:Example}
-
-\subsection{Success Rates of the Initial Estimates}
-
-The initial estimates described above are then fed to the MLE together with the raw data to obtain the final estimates.
-
-Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
-%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
-\begin{itemize}
-\item 
-$\model{0}$ via the true model $\true{G}$ as an initial estimate,
-\item
-$\model{exist}$ is obtained via GTLS and BTLS,
-\item
-$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
-\item
-$\model{RFIR}$, initialized by means of the RFIR method. 
-\end{itemize}
-
-A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
-
-\begin{conjecture}\label{conj1}
-The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
-$\model{0}$.
-\end{conjecture}
-
-From this conjecture, use of the true system as an initial estimate would engender the best final estimate or hopefully even the global optimum.
-Since the true system is not really known in practice, this chapter compares the capability of different possible initial estimates to emulate the result that would be obtained by using the true model as an initial estimate.
-
-The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used.
-%using the selected initial estimate.
-
-%$\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{BTLS}$ are discussed later on.
-
-The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
-%\JL{in agreement with assumption \ref{assumption_G0hat_is_global_optimum}} \emph{viz}:
-\begin{align}
-\eta=\Prob{\hat G_\bullet=\hat G_0}
-\end{align}
-In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
-\begin{align}\label{eq:successrateTol}
-\eta=\Prob{ \norm{\hat G_\bullet-\hat G_0} < tol}
-\end{align}
-with $tol$ a numerical tolerance that will be specified later.
-
-% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered.
-Note that it is not obvious to determine a tolerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate.
-On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
-%\comment{\EG{it is implemented that way now}}
-% }
-
-%\begin{align}
-%p(\hat G_x=\hat G_\circ) %G_0(q)= B(q)/A(q)
-%\end{align}
-
-The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
-\begin{align}
-\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
-\end{align}
- which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
-%\comment{EG: The exact implementation is in the L2Norm function.
-Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr.
-testDistance).
-I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
-%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
-The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.
-
-% !TEX root =  InitialValuesPaper.tex
-
-\section{Demonstration}\label{se:Demo}
-
-\subsection{The System Under Consideration}
-
-Two systems are considered. The first, with a quality factor $Q = 6\unit{dB}$, has the transfer function
-  \begin{equation}
-     G_0(z) \Big|_{Q=6\unit{dB}}
-    = 1.74 \cdot 10^{-3}
-    \frac{ z^2 + 2 z + 1 }
-         { z^2 - 1.93 z + 0.94}
-    \label{eq:systemundertest}
-    \text{.}
-  \end{equation}
-The second system, with a quality factor $Q = 20\unit{dB}$, has the transfer function
-  \begin{equation}
-    G_0(z) \Big|_{Q=20\unit{dB}}
-    = 309 \cdot 10^{-6}
-            \frac{z^2 + 2 z + 1}
-                 {z^2 - 1.98 z + 0.989}
-    \label{eq:systundertest-20dB}
-    \text{.}
-  \end{equation}
-
-Both systems are low-pass Chebyshev filters shown in \figref{fig:exampleFRF}.
-Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed signal-to-noise ratio (SNR) defined as
-\begin{equation}
-  \mathrm{SNR} 
-    = \frac{\sigma_v}
-           {\rms{y_0}}
-    \approx \frac{\sigma_{v}}
-                 {\left\| G_0 \right\|_2 \rms{u_0}}
-    =  \frac{\sigma_{v}}
-            {\left\| G_0 \right\|_2}
-  \label{eq:SNR-definition}
-  \text{.}
-\end{equation}
-is attained.
-$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
-%}%}
-
-%\JL{
-%\subsection{Successful VS failed estimation}
-\subsection{Comparison of Successful and Failed Estimates}
-
-%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $G_0$, $\hat G_0$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
-%}
-%\EG{
- \figref{fig:exampleFRF} depicts the Bode plot of the actual system $G_0$, in black
-%\comment{JL: in what color? (EG) black},
- and different estimates $\model{exist}$
- %\comment{JL: does it matter whether it is $\hat G_\mathrm{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
- that may or may not approximate $\hat{G}_{0}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
- The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, discussed later.
-
- It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
-that their distances from the true system, given by $\|\hat G_\mathrm{\bullet} - G_0\|_2^2$, have small values.
-On the other hand, the `failed' estimates are inaccurate descriptions of the true system.
-It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.
-   %Given the 2-norm \eqref{eq:successrateTol} employed 
-   %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t.
-the relative error, except when $\abs{G_0(\omega)}$ is small.
- %Practically, 
- %In practice, this means that a successful estimate provides reasonable estimates of the pass-band of the system, but may perform poorly in the stop-band.
-\comment{Further discussion required: what about the absolute error?
-Isn't it more or less white over the complete frequency band?} \ML{To be discussed}
-
- Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $G_0(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}.
- %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $G_0(\omega)$ over the broad frequency ranges.
- %Consequently, such estimates are practically worthless as an approximation of $G_0$.
- Consequently, such estimates are practically worthless approximations of $G_0$.
- %}
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.8\onecolumnwidth}
-  \setlength{\figureheight}{0.6\figurewidth}
-  \input{\thisDir/fig/exampleSystems.tikz}
- % \caption{Results of an example of Monte Carlo simulation.}
- \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
- Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
-\label{fig:exampleFRF}
-\end{figure}
-
-%\subsection{Computing the success rates}
-\subsection{Computation of  the Success Rates}\label{se:CompuSR}
-
-\subsubsection{Simulation}
-A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
-\begin{itemize}
-\item of SNR: 
-              $-20   \unit{dB}$, 
-              $-16.7 \unit{dB}$, 
-              $-13.3 \unit{dB}$, 
-              $-10   \unit{dB}$, 
-              $- 7.8 \unit{dB}$, 
-              $- 5.6 \unit{dB}$, 
-              $- 3.3 \unit{dB}$, 
-              $- 1.1 \unit{dB}$, 
-              $  1.1 \unit{dB}$, 
-              $  3.3 \unit{dB}$, 
-              $  5.6 \unit{dB}$, 
-              $  7.8 \unit{dB}$, 
-              $ 10   \unit{dB}$, 
-              $ 13.3 \unit{dB}$, 
-              $ 16.7 \unit{dB}$ and
-              $ 20   \unit{dB}$
-\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
-\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
-\end{itemize}
-One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
-The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
-For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
-For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
-Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
-This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
-
-%\ML{
-\subsubsection{Illustrative Example}
-In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
-This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
-This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}
-
-%\JL{One observes:}
-\subsubsection{Pertinent Observations}
-With reference to \figref{fig:single-sim}, the following observations are worth noting: 
-%\EG{
-\begin{itemize}
-\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\hat{G}_{0}$.
-Two major classifications can be made:
-\begin{enumerate}
-  \item `good' estimates which have $\|\model{\bullet} - \hat{G}_{0} \|_2 < tol \approx 6 \cdot 10^{-5}$,
-  \item `poor' estimates which are much farther from $\hat{G}_{0}$.  This is caused by the local optima.
-\end{enumerate}
-\item
-The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
-The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
-This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
-\end{itemize}
-%}
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.8\onecolumnwidth}
-  \setlength{\figureheight}{0.6\figurewidth}
-  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
- \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
- The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
- $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
-  \label{fig:single-sim}
-\end{figure}
-
-%\subsection{Improvement w.r.t. existing techniques}%
-\subsection{Improvement Over Existing Techniques}
-
-In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
-The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
-The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
-A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
-In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
-\begin{equation}
-\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
-\end{equation}
-with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e.
-$z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
-which requires inversion of the \gls{CDF} of a normal distribution.
-However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e.
-when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta \leq 1$~\citep{Ross2003}.
-An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
-In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
-In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
-\begin{align}
- \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
- \underline{\eta} &\isdef 
-  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
-  \overline{\eta} &\isdef
-  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
-\end{align}
-where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution.
-This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
-
-In this chapter, the Clopper-Pearson method---as implemented in \MATLAB's \code{binofit}---is used whenever confidence bounds are shown.
-Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.
-However, since there is often a clear separation between the different techniques, no efforts have been made to use confidence interval estimators that offer less conservative results.
-
-By aggregating the results for the different simulations and retaining the success rate $\eta$ only, a clearer view of the performance of the different methods is obtained.
-
-The success rates of $\hat G_\mathrm{exist}$, $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{RFIR}$ are depicted in  \figref{fig:successRateVS_SNR36N3dB} for two different numbers of sample points within the $3\unit{dB}$ bandwidth, and for a range of SNR values.
-A close scrutiny of  \figref{fig:successRateVS_SNR36N3dB} reveals the following observations: \begin{itemize}
-\item The success rates increase with increasing SNR values, as expected.
-\item For very low SNR values (below $0\unit{dB}$), $\hat G_\mathrm{exist}$ and $\hat G_\mathrm{trunc}$ are unreliable, whereas $\hat G_\mathrm{RFIR}$ is reliably successful. 
-\item For relatively high SNR ($20\unit{dB}$), all three estimators perform equally well.
-\item For moderate SNR values, the success rate of $\hat G_\mathrm{trunc}$ lies above that of $\hat G_\mathrm{exist}$.
-\item The RFIR-based estimate exhibits a success rate of, at least, $97\%$ for all studied conditions. 
-This clearly indicates that regularization makes it possible to obtain far more reliable initial estimates than both the LPM-Truncation-based ones and the existing ones. 
-This is an important conclusion.
-\end{itemize}
-%}
-
-%\JL{An important conclusion can be drawn from the last observation, in the range of the SNR where the success rate almost reaches 100\%.
-Namely, it tells us to what extent the estimator $\hat G_\mathrm{trunc}$ allows the SNR to be decreased before the estimator gets a too high fail rate.
-In other words, it shows that $\hat G_\mathrm{trunc}$ is more reliable at lower SNRs than $\hat G_\mathrm{existing}$.}
-%\JL{
-As far as $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{exist}$ are concerned, the observations on \figref{fig:successRateVS_SNR36N3dB} clearly reveal the extent to which the estimator $\hat G_\mathrm{trunc}$ allows for the SNR to be decreased before the estimator attains too high a fail rate.
-In other words, it shows that, at low SNR values $\hat G_\mathrm{trunc}$ is more reliable than $\hat G_\mathrm{exist}$.
-
-%\comment{JL: do we have the numerical results to add a remark like: At an SNR of xdB, the respective success rates of $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{existing}$ are $90\%$ and $95\%$.
-This means that, for that SNR, chances of failure have been reduced by a factor of 2!
-%}
-%\ML{Yea, shown below!}
-%\EG{
-  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ \gls{SNR}, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
-However, by using the truncated \gls{LPM}'s initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
-Moreover, the \gls{RFIR} initial values lead to poor estimates in less than $2\%$ ($>$ $98\%$ success rate) of the cases, since none were observed in the Monte Carlo simulation.
-
-\paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
-A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
-The range of improvement is approximately 5 dB where the success rate is above $90\%$.
-This result is very useful for a user working with noisy data.
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\eta$  obtained using the smoothers, i.e.
-$\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
-The $95\%$ confidence intervals are indicated by bars.}
-  \label{fig:successRateVS_SNR36N3dB}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.66\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
- In the bottom plot, the difference between both is shown.
- Consequently, it makes sense to examine the behavior of the models in terms of $\hat{G}_0$ as long as this RMSE meets the user's requirements.}
-  \label{fig:RMSE}
-\end{figure}
-
-\paragraph*{Remark about the model quality}
-In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\hat{G}_{0}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\hat{G}_{0}$ itself might be ill-suited.
-A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
-In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
-In this context this heuristic boils down to: 
-\begin{equation}
-    \RMSE(\hat{G}_{0}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{G_0}}{\SNR} 
-    \label{eq:heur-RMSE}
-\end{equation}
-where $n_{\theta}=5$ is the number of estimated parameters in this case.
-In \figref{fig:RMSE}, the empirical $\RMSE(\hat{G}_{0})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
-It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
-When the RMSE is then divided by $\norm{G_0}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
-
-\section{Experimental Results}
-\label{se:ExpMeas}
-Measurements were performed on an electrical filter to assess the performance of the initial value generating methods in a physical setting.
-
-\subsection{Experimental Setup}
-The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\citep{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\onecolumnwidth]{\thisDir/fig/measurement.pdf}
-  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
-The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized.
-  Blue arrows indicate coax cables. 
-  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
-  \label{fig:measurementSetup}
-\end{figure}
-
-To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
-The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
-The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
-The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
-To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
-The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
-Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
-The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the \gls{IDFT}.
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.75\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/bode-bk1613.tikz}
-  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
-  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
-  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
-  \label{fig:bk1613}
-\end{figure}
-
-\subsection{Identification Procedure}
-The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
-The mean signal from the input $u$ is of the form:
-\begin{equation}
-  \tilde{u}(t) = \frac{1}{N_R} \sum_{r=1}^{N_R} u^{[r]}(t)
-\end{equation}
-Thus, the reduced noise influence and the approximate noise co-variances are, respectively:
-\begin{align}
-  \hat\sigma_{u}^2(t) &= \frac{1}{N_R - 1} 
-                    \sum_{r=1}^{N_R} 
-                    \left( u^{[r]}(t) - \tilde{u}(t) \right)^2 \\
-%and the noise co-variances are approximately
-  \hat\sigma_{yu}(t) &= \frac{1}{N_R - 1} 
-                    \sum_{r=1}^{N_R} 
-                    \left( y^{[r]}(t) - \tilde{y}(t) \right)
-                    \overline{\left( u^{[r]}(t) - \tilde{u}(t) \right)}
-  \label{eq:variancePeriodic}            
-\end{align}
-
-Similar calculations apply to $y(t)$ and as such, $\hat\sigma_u(t)$, $\hat\sigma_y(t)$ and $\hat\sigma_{yu}(t)$ can be estimated.
-Their frequency domain counterparts $\tilde{U}(\omega)$ and $\tilde{Y}(\omega)$ are obtained by using the DFT.
-The resulting empirical transfer function estimate $Y^{[r]}(\omega)/U^{[r]}(\omega)$ and its periodic average $\tilde{Y}/\tilde{U}$ are shown in \figref{fig:bk1613}.
-The noise covariances $\hat\sigma^2_{U}(\omega)$, $\hat\sigma^2_{Y}(\omega)$ and  $\hat\sigma_{YU}(\omega)$ are calculated as the sample covariance, akin to equation \eqref{eq:variancePeriodic}, and their values are shown in \figref{fig:SpectraMeasurement}.
-Note that the SNR at the output $\mathrm{SNR}_{y} \approx 14 \unit{dB}$ is much smaller than at the input $\mathrm{SNR}_{u} \approx 50 \unit{dB}$.
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.75\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/elvis-spectra.tikz}
-  %TODO: simplify figure
-  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
-  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
-  \label{fig:SpectraMeasurement}
-\end{figure}
-
-For each measurement repetition, the signals $u^{[r]}(t)$, $y^{[r]}(t)$ and the variances $\sigma_U^2(\omega)$, $\sigma_Y^2(\omega)$ are used in the maximum likelihood cost function given by equation \eqref{eq:MLEcf}.
-The model chosen for the cost function comprises a numerator of third order, a denominator of sixth order and transient contribution of a fifth degree. This results in a transfer function of the form:
-\begin{equation}
-  \model{\bullet}(s,\theta) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
-\end{equation}
-which is typical of a sixth-order band-pass filter.
-By processing the different repetitions, a parametric fit per initialization method corresponding to the appropriate branch in \figref{fig:flowgraph}, and per repetition can be obtained.
-
-The following equation is constructed from the final estimates for each experiment; it gives an insight into the combined contribution to the `best' estimate from all the different initialization strategies, \emph{viz}:
-
-\begin{equation}\label{eq:selectBest}
-  \model{best} = 
-    \Arg_{\hat{G}} 
-    \min 
-    \left\{ 
-      V(\model{exist}),
-      V(\model{trunc}),
-      V(\model{RFIR})
-    \right\}
-\end{equation}
-where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
-This is similar to the approach followed in~\citep{FDIDENT} to combine different initial estimates.
-
-Alternatively, one can define the best model ($\model{best}$) and the second best model ($\model{2nd}$) as the models that comply to the inequalty
-$
-  \costFunc{}\left(\model{best}\right) < 
-  \costFunc{}\left( \model{2nd} \right) < 
-  \ldots
-$
-where $\model{best} \neq \model{2nd}$.
-
-\subsection{Reference Model Measurements}
-
-%\JL{
-Since the true model $G_0$ is not known for real-life systems, a practically viable reference model is needed.
-Additional measurements were performed using a \gls{VXI} measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
-Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\mathrm{VXI}$, and used as a reference model. 
-The \gls{VXI} measurement setup is summarized as follows.
-\begin{itemize}
-  \item Signal Generator card: \gls{VXI} HP E1445A.
-  \item Acquisition cards: \gls{VXI} HP E1430A.
-  \item Sampling frequency: $f_\mathrm{s} = 156\,250 \unit{Hz}$.
-  \item A total of $558$ frequency bins were used for the estimation, in the excited frequency band $[0.1,20] \unit{kHz}$, with a frequency resolution of $35.7\unit{Hz}$, giving a measurement time of $28\unit{ms}$.
-The excitation signal was band-limited periodic noise with an \gls{RMS} of $100\unit{mV}$.
-  \item The input and output signals were buffered and anti-alias filtered.
-\end{itemize}
-This yielded the model $G_\mathrm{VXI}$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.
-Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\mathrm{VXI}}$ as an initial estimate.
-Furthermore, $G_\mathrm{VXI}$ was used to play the role of $G_0$ from the previous section.
-
-\subsection{Model Estimation}
-  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
-  The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
-  The truncation method provides better estimates in many cases, but still suffers from a high variability.
-  On the other hand, the \gls{RFIR}-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
-  Obviously, $\model{best}$ has the lowest cost function values of all methods.
-  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the \gls{RFIR} provides the best estimate in most of the cases.
-  This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.
-
-\begin{remark}
-  In the simulations (e.g. \figref{fig:single-sim}), a $60\unit{dB}$ difference between `good' and `bad' estimates was observed.
-  Such a large gap is not observed in the measurements (\figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}).
-  Hence, defining a success rate based on a threshold tolerance would be very sensitive to the specific value of the threshold and hence unreliable.
-  Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
-  Practically, the median is used as a measure of location and the \gls{IQR} is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
-  These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
-  On the other hand, the \gls{IQR} ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
-\end{remark}
-
-\begin{figure}[p]
-  \centering
-  \setlength{\figurewidth}{0.85\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \setlength{\figurewidth}{0.75\onecolumnwidth}
-  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
-  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
-  The bottom plot shows a zoom of the top plot.
-  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
-  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
-  \label{fig:costMeasurements}
-\end{figure}
-
-\begin{table}[p]
-  \centering
-  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
-% \input{\thisDir/table1.tex}
-\pgfplotstabletypeset[precision=0]{
-method            P000     P025     P050      P075       P100   
-\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
-\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
-\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
-\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
-\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
-}
-  \label{tbl:costMeasurements}
-\end{table}
-
-\subsection{Model Validation}
-\subsubsection{Cost function limitations}
-In the previous section, the cost function was studied to determine the effectiveness of the starting values.
-However, inspecting the cost function $V(\theta)$ only accounts for how well an estimated model fits the measured data, which may be misleading.
-For an example, overfitting a model may result in the absorption of both the systematic behavior and the noise into the model. 
-Consequently, an arbitrarily small cost function may ensue although the estimated model may be virtually useless to predict the system behavior.
-
-\subsubsection{Validation criterion}
-To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
-To this end, the model is validated using the 2-norm (or distance) on the model error:
-\begin{equation}
-  \validationDistance{\bullet} 
-  \isdef 
-  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
-  \text{.}
-  \label{eq:measurementCriterion}
-\end{equation} 
-This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the VXI.
-
-\subsubsection{Validation performance}
-The observed median and IQR of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
-The existing methods provide good estimates in only $25\%$ of the cases.
-The truncation method provides a considerable improvement but still suffers from $25\%$ poor estimates.
-Compared to the existing BTLS and GTLS techniques, the RFIR and hence also $\model{best}$ entail an overall reduction in the observed distance by a factor $8$, in most cases. 
-On the other hand, the reference $\model{VXI}$ shows the best global performance. 
-This indicates that the proposed methods do no converge to the same local optimum.
-Nevertheless, the proposed methods improve the model quality by almost an order of magnitude.
-
-As the criterion in equation~\eqref{eq:measurementCriterion} no longer depends on the cost function, the initial estimates can also be investigated.
-The difference between the distance of $\model[init]{\bullet}$ and $\model{\bullet}$ indicates how much the final ML estimate from the raw data, in each respective branch of \figref{fig:flowgraph}, improves over the initial estimate.
-Remarkably, on average, the final ML estimation provides only a marginal improvement for the RFIR. 
-However, this final step reduces the spread and hence yields a more reliable estimate.
-E.g. note in \tabref{tbl:validationMeasurements} that this step reduces the worst-case distance from $18.21$ to $4.55$.
-
-\begin{figure}[p]
-  \centering
-  \setlength{\figurewidth}{0.85\onecolumnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \setlength{\figurewidth}{0.75\onecolumnwidth}
-  \input{\thisDir/fig/meas-validation.tikz}
-  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
-  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
-  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
-  The bottom plot shows a zoom of the top plot.
-  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
-  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
-  \label{fig:validationMeasurements}
-\end{figure}
-\begin{table}[p]
-  \centering
-  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
-% \input{\thisDir/table2.tex}
-
-\pgfplotstabletypeset[precision=2,zerofill=true]{
-method              P000      P025      P050        P075     P100   
-\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
-\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
-\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
-\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
-\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
-\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
-\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
-}
-\label{tbl:validationMeasurements}
-\end{table}
-
-\section{Consequences of selecting the `best` model}
-To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
-To do so, we inspect the performance by means of the cost function (used during estimation) and by means of the validation distance.
-The datasets used in this analysis are those from the measurements, but similar results can be obtained from the other data sets.
-
-In \figref{fig:overview} we can compare $\model{2nd}$ and $\model{best}$.
-By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
-In \figref{fig:init:histogramEnhancement}, the different methods are compared by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
-As such, each column in the figure indicates the performance of this method when it is not the `best'.
-Obviously, when we consider the cost function used during estimation (left subfigure), we can only degrade the performance by construction of $\model{best}$.
-For the validation data, however, this is no longer guaranteed as can be seen in the right subplot.
-On average, there is very little performance that can be gained from not using $\model{best}$, however, for two or three data points, there is a considerable improvement.
-From that figure it can also be seen that there is little performance to lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method.
-The outcome is less favorable for the alternative methods.
-For $\model{exist}$ it can be seen that selecting those instead of $\model{best}$  degrades the validation performance by $10$ or even more in $75\%$ of the cases.
-The situation is already less severe for $\model{trunc}$ (in $75\%$ of the cases, the degradation is larger than $0.5$).
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/overview-cost-val.tikz}
-  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
-  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
-  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
-  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
-  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
-  \label{fig:overview}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \ref{leg:init:secondBest}
-  \setlength{\figurewidth}{0.75\columnwidth}
-  \setlength{\figureheight}{0.60\figurewidth}
-  \input{\thisDir/fig/special-histogram.tikz}
-  \caption[Performance degradation/enhancement for selecting the second best model.]{
-  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
-  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
-  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
-  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the plot shows when method $\bullet$ is \emph{not} selected as the `best' method.
-  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
-  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
-  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e.
-there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
-  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
-  }
-  \label{fig:init:histogramEnhancement}
-\end{figure}
-
-\section{Remark on Generality}
-\label{se:Generality}
-In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
-In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
-However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.
-
-\subsection{Limitations of the smoothers}
-On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g.
-heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
-However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.
-
-In particular for RFIR, a simulation study in~\citep{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
-For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
-
-\subsection{Stress test of the smoothers}
-To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
-In particular, all combinations of
-\begin{itemize}
-  \item low-pass, high-pass, band-pass and band-stop 
-  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
-\end{itemize}
-discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
-Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
-The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
-The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
-Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
-
-The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
-Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
-
-\begin{table}
-  \centering
-  \caption{Overview of the test cases for the initialization stress test.}
-\begin{tabular}{crlrrrrr}
-\toprule
-\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta} [\%]$  &  $\eta_{\mathrm{exist}} [\%]$ &  $\eta_{\mathrm{trunc}} [\%]$   &  $\eta_{\mathrm{RFIR}} [\%]$  &  $\eta_{\mathrm{best}} [\%]$ \\
-\midrule
-1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
-2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
-3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
-4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
-5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
-6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
-7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
-8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
-9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
-10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
-11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
-12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
-13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
-14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
-15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
-16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
-\bottomrule
-\end{tabular}
-\label{tbl:init:stresstest}
-\end{table}
-
-\subsection{Observations}
-The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
-In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm{\model{\bullet} - \true{G}} < tol$.
-
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \centering
-  \ref{leg:init:stress:bodes}
-  \input{\thisDir/fig/bodeplots.tikz}
-  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
-  For each filter, two (randomly selected) instanced of the parametric estimates $\model{\bullet}$ are shown per method.
-  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
-  % Left to right: low-pass, band-pass, high-pass and band-stop.
-  }
-  \label{fig:bodeplots}
-\end{figure}
-
-\begin{figure}[p]
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.68\figurewidth}
-  \centering
-  \ref{leg:distances}
-  \input{\thisDir/fig/distances.tikz}
-  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
-  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
-  }
-  \label{fig:distancesStress}
-\end{figure}
-
-A few remarks regarding these results are appropriate.
-\begin{itemize}
-  \item In many of the tested situations (cases 1,3,13-16), all methods yield a good model quality.
-  \item In some situations (cases 8, 10, 12), the model quality is generally poor. 
-  The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
-  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
-  \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
-  This is a underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
-  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
-  \item The RFIR performs (significantly) better than the existing methods in various cases (4-7, 9, 11).
-  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.
-in cases 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
-  Particularly, case 2 implies that \model{best} contains initial estimates of all different techniques.
-  \item For all of the tested systems (except possibly for case 2), the truncated LPM is not advisable over the existing methods.
-\end{itemize}
-
-In general, one can see from these simulations that \gls{RFIR} either performs as well as (or even better than) the existing techniques when a good estimate is obtained.
-There are no cases where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
-On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.
-
-\section{Conclusion}\label{se:Conclusion}
-The simulations have demonstrated that use of a smoothed non-parametric estimate of the \gls{FRF} can improve the success rate of minimizing the \gls{ML} cost function for the estimation of the transfer functions of \gls{LTI} systems, subjected to noisy signals.
-Specifically, two smoothing methods were used and compared: 1) the truncated \gls{LPM} method, and 2) the \gls{RFIR} method.
-The simulation results clearly show that the \gls{RFIR} method is superior to the truncated \gls{LPM} method and the existing \gls{BTLS} and \gls{GTLS} methods.
-
-The usefulness of the initial values obtained via the proposed smoothing techniques was confirmed on a measurement of a band-pass filter in a noisy environment.
-In most cases, the proposed initial values in the example made it possible to reduce the cost function by a factor two compared to existing methods.
-Moreover, the obtained models were validated against a high-quality measurement where the \gls{RMS} error on the transfer function could be reduced by a factor of eight for most cases, due to the improved initial values.
-
-Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
-Consequently, the quality of parametric estimates can be increased considerably by using non-parametric \gls{FRF} models to initialize the non-convex optimization problem of fitting a rational transfer function model.
-Hence, the ease-of-use of parametric model fitting can be increased significantly by having high-quality non-parametric \gls{FRF} models.
-This comes at a limited cost for the end-user: in principle these smoothers can be tried without any additional intervention by the user.
-The only disadvantage is the additional computational effort required and hence also the increase in wall clock time to obtain a parametric estimate.
-However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest.

### 2016-02-11 ch05-initvals/initial-values.tex
Use make for figures, config compartments
Include initial values
Also quite a bit of pgfplots external trickery/hackery
to make sure the file compiles.
Some future work stuffies + labels
Add epigraphs
Include initvals review letter (prelim!)
Include review letter from initial values paper
Most of the review letter should go in the future.
Anyhow, at least the figures are already there, so we can add them
to the text.
Init-vals: more or less ready
Add TODOs for most of Johan's comments

@@
 \chapter{Initialization of parametric estimators}
+\label{sec:initvals}
+\myEpigraph{Everything starts somewhere, though many physicists disagree.
+But people have always been dimly aware of the problem with the start of things.
+They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
+\gdef\thisDir{ch05-initvals}
+
+\section{Introduction}\label{se:introd}
+
+The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
+Typical measurement techniques and identification strategies of transfer functions (TFs) or \glspl{FRF} are discussed in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
+Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.
+
+Parametric identification of \gls{LTI} systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}. 
+ Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
+ However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
+ Such local optima have a detrimental effect on the quality of the estimated model.
+
+ In the perspective of developing identification tools that require as little user interaction as possible, it is important to increase the probability of the optimization algorithm to produce good estimates, or preferably even the global optimum.
+ However, when noisy input-output measurements are to be processed, the presence of noise obstructs a clear view of the actual system behavior, especially for poor signal-to-noise ratios (SNRs).
+ In non-parametric identification, the presence of noise is typically mitigated by averaging multiple measurements or using smoothing techniques.
+
+The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
+Hence, such techniques make it possible to increase the ``success rate'' (i.e.
+the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
+%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
+
+In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
+These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
+%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).
+
+The rest of the chapter is structured as follows.
+Section~\ref{se:ProbForm} covers the problem formulation.
+Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}.
+This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
+In Section~\ref{se:Generality} the generality of the results is discussed briefly.
+Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.
+
+% !TEX root =  InitialValuesPaper.tex
+
+\section{Problem formulation}\label{se:ProbForm}
+%\begin{itemize}
+%\item
+%Block schematic of the output error framework
+
+%\JL{In this section, the assumptions on the system and the noise are given, and the associated Maximum Likelihood estimator, formulated in the frequency domain.
+The latter turns out to be a non-convex function in the parameters, requiring initial estimates.
+The obtention of those is discussed in the subsequent section.}
+
+In this section, the assumptions on the system and the noise are presented, together with the associated MLE (formulated in the frequency domain), which turns out to be a non-convex function in the parameters, requiring initial estimates.
+The procedure for obtaining the initial estimates is discussed in the subsequent sections.
+
+\subsection{System Setup Framework and Model}
+\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input.
+The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well.
+The full mathematical model of the system is
+\begin{equation}\label{lpmtd1}
+y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
+\end{equation}
+%\comment{We don't have any results with colored noise yet!}
+where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
+$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
+For white noise, $H_0 = 1$ and $e(t) = v(t)$.
+Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
+However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
+
+\begin{figure}[tbh] %top bottom here
+\centering
+\input{\thisDir/fig/oesetup.tikz}
+\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
+\label{fig:oesetup}
+\end{figure}
+
+Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
+
+In this chapter we assume that the output signal is disturbed by random noise, resulting in noisy error-prone data.
+For the simulations, white noise is used.
+It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{se:ExpMeas}.
+
+\subsection{Parametric System Model}
+
+With reference to equation \eqref{lpmtd1}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
+\begin{equation}
+    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in \left( - \infty, + \infty \right)
+\label{ABpolys}
+\end{equation}
+where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation \eqref{lpmtd1} that
+\begin{equation}
+    G_0(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
+    \text{.}
+\end{equation}
+
+From~\citep[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
+\begin{align}
+A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
+\label{DFTspectra}
+\end{align}
+with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions.
+\TODO{explain init/end conditions in this context}
+\begin{assumption}
+It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
+\end{assumption}
+
+\begin{remark}
+The knowledge of the true model orders makes the analysis of the smoothers easier to carry out as we thus avoid extra calculation time required to perform model selection.
+However, these smoothers can be used in conjunction with model order selection procedures.
+\end{remark}
+
+\subsection{Parametric Identification Algorithm}\label{se:paramIdentAlgo}
+
+The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
+\begin{equation}
+  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
+\end{equation}
+Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
+\begin{equation}\label{eq:MLEcf}
+V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
+\end{equation}
+for $N$ measurements and when $\varepsilon$ denotes the error in equation \eqref{DFTspectra},  \emph{viz}.:
+\begin{align}
+\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
+\end{align}
+The variance of the error is of the form:
+\begin{equation}\label{eq:sigmaEps}
+\begin{split}
+\sigma_\varepsilon^2(k,\theta) 
+  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
+   +  |B(k,\theta)|^2\sigma_U^2(k) \\
+  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
+\end{split}
+\end{equation}
+where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known?
+where do you use that?
+how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$.
+Isn't it the same thing?},
+%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
+and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
+Here, $\overline{B}$ denotes the complex conjugate of $B$.
+%\comment{use $\sigma^2_U$ instead}
+
+Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
+The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
+Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this chapter.
+
+\begin{algorithm}
+\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
+\begin{algorithmic}[1]
+  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
+  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
+%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
+   \For{$i$ \textbf{in} $1 \to \infty$}
+      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
+      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
+      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
+      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
+      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \norm{\atIter[i-1]{\theta} + \delta\theta} $
+      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
+          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
+      \Else
+          \State $\lambda \gets 0.4 \lambda$
+      \EndIf
+      \State \textbf{if} $\norm{\delta\theta}/\norm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
+   \EndFor
+%\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
+\begin{remark}
+Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
+This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
+Stochastic optimization is not discussed in the remainder of this chapter.
+\end{remark}
+
+\section{Methodology}\label{se:MethodEg}
+In this section, the considered methods for obtaining the initial estimates of $\theta$ are briefly explained.
+Then their influence on the success rate of the maximum likelihood estimator is described.
+%}
+
+\subsection{Initial Estimates Procedure}\label{se:initEstProcs} %{Obtaining initial estimates}
+
+%\begin{itemize}
+%\item
+%Obtain a good estimate of the FRF of the system by using the LPM: short description + reference
+
+\begin{figure}
+  \centering
+  \includegraphics
+  [width=0.95\columnwidth]{\thisDir/fig/flowgraph}
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (3, 4).
+  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
+\end{figure}
+
+The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the \gls{MLE} optimization process in the parametric identification of each system. 
+The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:
+
+\begin{enumerate}
+\item
+\emph{Using the true model ($\true{G}$) as initial estimate}
+
+The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the \gls{MLE}.
+
+\item
+\emph{Quadratic approximations of the ML}
+
+%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
+These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$.
+These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$).
+Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}
+
+The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}.
+These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
+$\theta$.
+These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
+Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.
+
+\item
+\emph{Local polynomial method (LPM) with truncation}
+
+A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014TIM}.
+Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
+The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
+
+  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+\begin{subequations}\label{lpmImplQuadG}
+\begin{align}
+G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
+\\
+T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
+\end{align}
+\end{subequations}
+where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
+In this instance, $n=3$.
+
+  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
+\begin{equation}
+\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
+\text{.}
+\end{equation}
+This procedure is repeated for all $k$ in the frequency band of interest.
+
+%The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.
+
+\emph{Impulse response truncation}. 
+%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
+The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM}.
+%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.
+
+The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
+\begin{equation}
+  g_{\mathrm{trunc}}(t) = 
+  \begin{cases}
+    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
+    0                    & t \geq \tau_{\mathrm{trunc}}
+  \end{cases}
+  \text{.}
+\end{equation}
+To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
+Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
+\begin{equation}
+  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
+  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
+  \text{,}
+\end{equation}
+where $\gamma=1$ was used in this chapter for simplicity.
+By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
+This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
+
+\item \emph{\Glsfirst{RFIR}}
+
+The \gls{RFIR} method is a special case of the \gls{RARX} method. 
+%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.
+
+%\JL{
+The \gls{RFIR} estimator is formulated in the time domain. 
+It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
+\begin{align}\label{eq:hRFIRdef}
+\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
+\end{align}
+where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
+Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
+Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
+The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
+Here, the \gls{DCkernel} is used. 
+Specifically, the element at $t_1,t_2$ of $P$ is given by
+\begin{equation}
+P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
+\end{equation}
+ for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
+ The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
+\begin{align}
+\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
+\end{align}
+where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
+This problem is solved using \code{fmincon} in \MATLAB.
+
+An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}.
+The hyperparameters can be determined via \code{arxregul}.
+More information about the \gls{RFIR} estimator can be found in
+~\citep{Pillonetto2010,Chen2012}. 
+The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
+%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
+\end{enumerate}
+
+\begin{remark}
+Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
+A corresponding parametric estimate is obtained as follows. 
+A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero.
+It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data.
+This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
+\TODO{spectra als formule geven}
+\end{remark}
+%}
+
+%\comment{JL: one could remove the subsection below (why?
+see my comments below), and mention that the the above initial estimates are then fed to the MLE, with the raw data, to obtain the final estimates.}
+
+%\subsection{Genesis of the Initial Estimates} 
+%\comment{JL: why `genesis'? This section is actually where you use the initial estimates, not their origin.}
+%{Deploying the initial estimates}
+
+%\comment{ML: Fig. \ref{fig:flowgraph} should include an additional path for RFIR/RARX, and the accompanying text (below) is to be modified accordingly.}
+%Fig.
+\ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart?
+It has actually been explained in further details in \sectref{se:initEstProcs}.}
+%\begin{enumerate}
+%\item (Left (first) path of the flowchart): The true model $G_0$ as initial values,
+%\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
+%\item (Third path from the left of the flowchart): The LPM-truncated initial values with BTLS and GTLS, and  
+%%\item (Right (fourth) path of the flowchart): The RFIR initial values with BTLS and GTLS.  
+%\end{enumerate}
+
+%\JL{
+%The main contribution of this paper is to demonstrate that $\hat G_\mathrm{trunc}$ (third path) yields an improvement over $\hat G_\mathrm{exist}$ (second path).
+\comment{JL: these symbols haven't been introduced yet.
+I'm getting quite confident that this subsection can be removed.}The quantification of this improvement is formally introduced in the next section.
+%}
+
+%The latter 2 ....schematic is configured to include connections of the initial values and the input to the LPM block and/or to the MLE block(s) for estimation purposes.
+%\end{itemize}
+%\section{Example}\label{se:Example}
+
+\subsection{Success Rates of the Initial Estimates}
+
+The initial estimates described above are then fed to the MLE together with the raw data to obtain the final estimates.
+
+Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
+%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
+\begin{itemize}
+\item 
+$\model{0}$ via the true model $\true{G}$ as an initial estimate,
+\item
+$\model{exist}$ is obtained via GTLS and BTLS,
+\item
+$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
+\item
+$\model{RFIR}$, initialized by means of the RFIR method. 
+\end{itemize}
+
+A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
+
+\begin{conjecture}\label{conj1}
+The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
+$\model{0}$.
+\end{conjecture}
+\TODO{Johan: merk op dat dit niet zo hoeft te zijn! zelfs vanuit $\true{G}$ kan het misgaan}
+
+From this conjecture, use of the true system as an initial estimate would engender the best final estimate or hopefully even the global optimum.
+Since the true system is not really known in practice, this chapter compares the capability of different possible initial estimates to emulate the result that would be obtained by using the true model as an initial estimate.
+
+The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used.
+%using the selected initial estimate.
+
+%$\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{BTLS}$ are discussed later on.
+
+The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
+%\JL{in agreement with assumption \ref{assumption_G0hat_is_global_optimum}} \emph{viz}:
+\begin{align}
+\eta=\Prob{\hat G_\bullet=\hat G_0}
+\end{align}
+In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
+\begin{align}\label{eq:successrateTol}
+\eta=\Prob{ \norm{\hat G_\bullet-\hat G_0} < tol}
+\end{align}
+with $tol$ a numerical tolerance that will be specified later on.
+\TODO{Johan: beter een relatief criterium gebruiken (delen door $\norm{\true{G}}$)}
+
+% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered.
+Note that it is not obvious to determine a tolerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate.
+On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
+%\comment{\EG{it is implemented that way now}}
+% }
+
+%\begin{align}
+%p(\hat G_x=\hat G_\circ) %G_0(q)= B(q)/A(q)
+%\end{align}
+
+The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
+\begin{align}
+\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
+\end{align}
+ which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
+%\comment{EG: The exact implementation is in the L2Norm function.
+Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr.
+testDistance).
+I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
+%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
+The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.
+
+% !TEX root =  InitialValuesPaper.tex
+
+\section{Demonstration}\label{se:Demo}
+
+\subsection{The System Under Consideration}
+
+Two systems are considered. The first, with a quality factor $Q = 6\unit{dB}$, has the transfer function
+  \begin{equation}
+     G_0(z) \Big|_{Q=6\unit{dB}}
+    = 1.74 \cdot 10^{-3}
+    \frac{ z^2 + 2 z + 1 }
+         { z^2 - 1.93 z + 0.94}
+    \label{eq:systemundertest}
+    \text{.}
+  \end{equation}
+The second system, with a quality factor $Q = 20\unit{dB}$, has the transfer function
+  \begin{equation}
+    G_0(z) \Big|_{Q=20\unit{dB}}
+    = 309 \cdot 10^{-6}
+            \frac{z^2 + 2 z + 1}
+                 {z^2 - 1.98 z + 0.989}
+    \label{eq:systundertest-20dB}
+    \text{.}
+  \end{equation}
+
+Both systems are low-pass Chebyshev filters shown in \figref{fig:exampleFRF}. 
+Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
+\begin{equation}
+  \mathrm{SNR} 
+    = \frac{\sigma_v}
+           {\rms{y_0}}
+    \approx \frac{\sigma_{v}}
+                 {\left\| G_0 \right\|_2 \rms{u_0}}
+    =  \frac{\sigma_{v}}
+            {\left\| G_0 \right\|_2}
+  \label{eq:SNR-definition}
+  \text{.}
+\end{equation}
+is attained.
+$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
+%}%}
+
+%\JL{
+%\subsection{Successful VS failed estimation}
+\subsection{Comparison of Successful and Failed Estimates}
+
+%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $G_0$, $\hat G_0$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
+%}
+%\EG{
+ \figref{fig:exampleFRF} depicts the Bode plot of the actual system $G_0$, in black
+%\comment{JL: in what color? (EG) black},
+ and different estimates $\model{exist}$
+ %\comment{JL: does it matter whether it is $\hat G_\mathrm{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
+ that may or may not approximate $\hat{G}_{0}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
+ The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, discussed later.
+
+ It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
+that their distances from the true system, given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
+On the other hand, the `failed' estimates are inaccurate descriptions of the true system.
+It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.
+   %Given the 2-norm \eqref{eq:successrateTol} employed 
+   %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t.
+the relative error, except when $\abs{G_0(\omega)}$ is small.
+ %Practically, 
+ %In practice, this means that a successful estimate provides reasonable estimates of the pass-band of the system, but may perform poorly in the stop-band.
+\comment{Further discussion required: what about the absolute error?
+Isn't it more or less white over the complete frequency band?} \ML{To be discussed}
+
+ Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $G_0(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}.
+ %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $G_0(\omega)$ over the broad frequency ranges.
+ %Consequently, such estimates are practically worthless as an approximation of $G_0$.
+ Consequently, such estimates are practically worthless approximations of $G_0$.
+ %}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.8\columnwidth}
+  \setlength{\figureheight}{0.6\figurewidth}
+  \input{\thisDir/fig/exampleSystems.tikz}
+ % \caption{Results of an example of Monte Carlo simulation.}
+ \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
+ Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
+\label{fig:exampleFRF}
+\end{figure}
+
+%\subsection{Computing the success rates}
+\subsection{Computation of  the Success Rates}\label{se:CompuSR}
+
+\subsubsection{Simulation}
+A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
+\begin{itemize}
+\item of SNR: 
+              $-20   \unit{dB}$, 
+              $-16.7 \unit{dB}$, 
+              $-13.3 \unit{dB}$, 
+              $-10   \unit{dB}$, 
+              $- 7.8 \unit{dB}$, 
+              $- 5.6 \unit{dB}$, 
+              $- 3.3 \unit{dB}$, 
+              $- 1.1 \unit{dB}$, 
+              $  1.1 \unit{dB}$, 
+              $  3.3 \unit{dB}$, 
+              $  5.6 \unit{dB}$, 
+              $  7.8 \unit{dB}$, 
+              $ 10   \unit{dB}$, 
+              $ 13.3 \unit{dB}$, 
+              $ 16.7 \unit{dB}$ and
+              $ 20   \unit{dB}$
+\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
+\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
+\end{itemize}
+\TODO{johan: tijdsconstantes geven}
+One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
+The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
+For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
+For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
+Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
+This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
+
+%\ML{
+\subsubsection{Illustrative Example}
+In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
+This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
+This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}
+
+%\JL{One observes:}
+\subsubsection{Pertinent Observations}
+With reference to \figref{fig:single-sim}, the following observations are worth noting: 
+%\EG{
+\begin{itemize}
+\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\hat{G}_{0}$.
+Two major classifications can be made:
+\begin{enumerate}
+  \item `good' estimates which have $\|\model{\bullet} - \hat{G}_{0} \|_2 < tol \approx 6 \cdot 10^{-5}$,
+  \item `poor' estimates which are much farther from $\hat{G}_{0}$.  This is caused by the local optima.
+\end{enumerate}
+\item
+The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
+The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
+This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
+\end{itemize}
+%}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.8\columnwidth}
+  \setlength{\figureheight}{0.6\figurewidth}
+  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
+ \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
+ The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
+ $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
+  \label{fig:single-sim}
+\end{figure}
+
+%\subsection{Improvement w.r.t. existing techniques}%
+\subsection{Improvement Over Existing Techniques}
+
+In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
+Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
+The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
+The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
+A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
+In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
+\begin{equation}
+\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
+\end{equation}
+with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e.
+$z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
+which requires inversion of the \gls{CDF} of a normal distribution.
+However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e.
+when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta \leq 1$~\citep{Ross2003}.
+An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
+In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
+In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
+\begin{align}
+ \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
+ \underline{\eta} &\isdef 
+  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
+  \overline{\eta} &\isdef
+  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
+\end{align}
+where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution.
+This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
+
+In this chapter, the Clopper-Pearson method---as implemented in \MATLAB's \code{binofit}---is used whenever confidence bounds are shown.
+Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly due to the conservatism in these bounds.
+However, since there is often a clear separation between the different techniques, no efforts have been made to use confidence interval estimators that offer less conservative results.
+
+By aggregating the results for the different simulations and retaining the success rate $\eta$ only, a clearer view of the performance of the different methods is obtained.
+
+The success rates of $\hat G_\mathrm{exist}$, $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{RFIR}$ are depicted in  \figref{fig:successRateVS_SNR36N3dB} for two different numbers of sample points within the $3\unit{dB}$ bandwidth, and for a range of SNR values.
+A close scrutiny of  \figref{fig:successRateVS_SNR36N3dB} reveals the following observations: \begin{itemize}
+\item The success rates increase with increasing SNR values, as expected.
+\item For very low SNR values (below $0\unit{dB}$), $\hat G_\mathrm{exist}$ and $\hat G_\mathrm{trunc}$ are unreliable, whereas $\hat G_\mathrm{RFIR}$ is reliably successful. 
+\item For relatively high SNR ($20\unit{dB}$), all three estimators perform equally well.
+\item For moderate SNR values, the success rate of $\hat G_\mathrm{trunc}$ lies above that of $\hat G_\mathrm{exist}$.
+\item The RFIR-based estimate exhibits a success rate of, at least, $97\%$ for all studied conditions. 
+This clearly indicates that regularization makes it possible to obtain far more reliable initial estimates than both the LPM-Truncation-based ones and the existing ones. 
+This is an important conclusion.
+\end{itemize}
+%}
+
+%\JL{An important conclusion can be drawn from the last observation, in the range of the SNR where the success rate almost reaches 100\%.
+Namely, it tells us to what extent the estimator $\hat G_\mathrm{trunc}$ allows the SNR to be decreased before the estimator gets a too high fail rate.
+In other words, it shows that $\hat G_\mathrm{trunc}$ is more reliable at lower SNRs than $\hat G_\mathrm{existing}$.}
+%\JL{
+As far as $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{exist}$ are concerned, the observations on \figref{fig:successRateVS_SNR36N3dB} clearly reveal the extent to which the estimator $\hat G_\mathrm{trunc}$ allows for the SNR to be decreased before the estimator attains too high a fail rate.
+In other words, it shows that, at low SNR values $\hat G_\mathrm{trunc}$ is more reliable than $\hat G_\mathrm{exist}$.
+
+%\comment{JL: do we have the numerical results to add a remark like: At an SNR of xdB, the respective success rates of $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{existing}$ are $90\%$ and $95\%$.
+This means that, for that SNR, chances of failure have been reduced by a factor of 2!
+%}
+%\ML{Yea, shown below!}
+%\EG{
+  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ \gls{SNR}, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
+However, by using the truncated \gls{LPM}'s initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
+Moreover, the \gls{RFIR} initial values lead to poor estimates in less than $2\%$ ($>$ $98\%$ success rate) of the cases, since none were observed in the Monte Carlo simulation.
+
+\paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
+A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
+The range of improvement is approximately 5 dB where the success rate is above $90\%$.
+This result is very useful for a user working with noisy data.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/successRates.tikz}
+ \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\eta$  obtained using the smoothers, i.e.
+$\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
+The $95\%$ confidence intervals are indicated by bars.}
+  \label{fig:successRateVS_SNR36N3dB}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.66\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
+ \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
+ In the bottom plot, the difference between both is shown.
+ Consequently, it makes sense to examine the behavior of the models in terms of $\hat{G}_0$ as long as this RMSE meets the user's requirements.}
+  \label{fig:RMSE}
+\end{figure}
+
+\paragraph*{Remark about the model quality}
+In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\hat{G}_{0}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\hat{G}_{0}$ itself might be ill-suited.
+A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
+In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
+In this context this heuristic boils down to: 
+\begin{equation}
+    \RMSE(\hat{G}_{0}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{G_0}}{\SNR} 
+    \label{eq:heur-RMSE}
+\end{equation}
+where $n_{\theta}=5$ is the number of estimated parameters in this case.
+In \figref{fig:RMSE}, the empirical $\RMSE(\hat{G}_{0})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
+It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
+When the RMSE is then divided by $\norm{G_0}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
+
+\section{Experimental Results}
+\label{se:ExpMeas}
+Measurements were performed on an electrical filter to assess the performance of the initial value generating methods in a physical setting.
+
+\subsection{Experimental Setup}
+The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\citep{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\columnwidth]{\thisDir/fig/measurement.pdf}
+  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
+The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized.
+  Blue arrows indicate coax cables. 
+  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
+  \label{fig:measurementSetup}
+\end{figure}
+
+To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
+The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
+The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
+The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
+To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
+The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
+Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
+The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the \gls{IDFT}.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/bode-bk1613.tikz}
+  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
+  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
+  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
+  \label{fig:bk1613}
+\end{figure}
+
+\subsection{Identification Procedure}
+The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
+The mean signal from the input $u$ is of the form:
+\begin{equation}
+  \tilde{u}(t) = \frac{1}{N_R} \sum_{r=1}^{N_R} u^{[r]}(t)
+\end{equation}
+Thus, the reduced noise influence and the approximate noise co-variances are, respectively:
+\begin{align}
+  \hat\sigma_{u}^2(t) &= \frac{1}{N_R - 1} 
+                    \sum_{r=1}^{N_R} 
+                    \left( u^{[r]}(t) - \tilde{u}(t) \right)^2 \\
+%and the noise co-variances are approximately
+  \hat\sigma_{yu}(t) &= \frac{1}{N_R - 1} 
+                    \sum_{r=1}^{N_R} 
+                    \left( y^{[r]}(t) - \tilde{y}(t) \right)
+                    \overline{\left( u^{[r]}(t) - \tilde{u}(t) \right)}
+  \label{eq:variancePeriodic}            
+\end{align}
+
+Similar calculations apply to $y(t)$ and as such, $\hat\sigma_u(t)$, $\hat\sigma_y(t)$ and $\hat\sigma_{yu}(t)$ can be estimated.
+Their frequency domain counterparts $\tilde{U}(\omega)$ and $\tilde{Y}(\omega)$ are obtained by using the DFT.
+The resulting empirical transfer function estimate $Y^{[r]}(\omega)/U^{[r]}(\omega)$ and its periodic average $\tilde{Y}/\tilde{U}$ are shown in \figref{fig:bk1613}.
+The noise covariances $\hat\sigma^2_{U}(\omega)$, $\hat\sigma^2_{Y}(\omega)$ and  $\hat\sigma_{YU}(\omega)$ are calculated as the sample covariance, akin to equation \eqref{eq:variancePeriodic}, and their values are shown in \figref{fig:SpectraMeasurement}.
+Note that the SNR at the output $\mathrm{SNR}_{y} \approx 14 \unit{dB}$ is much smaller than at the input $\mathrm{SNR}_{u} \approx 50 \unit{dB}$.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/elvis-spectra.tikz}
+  %TODO: simplify figure
+  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
+  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
+  \label{fig:SpectraMeasurement}
+\end{figure}
+
+For each measurement repetition, the signals $u^{[r]}(t)$, $y^{[r]}(t)$ and the variances $\sigma_U^2(\omega)$, $\sigma_Y^2(\omega)$ are used in the maximum likelihood cost function given by equation \eqref{eq:MLEcf}.
+The model chosen for the cost function comprises a numerator of third order, a denominator of sixth order and transient contribution of a fifth degree. This results in a transfer function of the form:
+\begin{equation}
+  \model{\bullet}(s,\theta) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
+\end{equation}
+which is typical of a sixth-order band-pass filter.
+By processing the different repetitions, a parametric fit per initialization method corresponding to the appropriate branch in \figref{fig:flowgraph}, and per repetition can be obtained.
+
+The following equation is constructed from the final estimates for each experiment; it gives an insight into the combined contribution to the `best' estimate from all the different initialization strategies, \emph{viz}:
+
+\begin{equation}\label{eq:selectBest}
+  \model{best} = 
+    \Arg_{\hat{G}} 
+    \min 
+    \left\{ 
+      V(\model{exist}),
+      V(\model{trunc}),
+      V(\model{RFIR})
+    \right\}
+\end{equation}
+where $V(\hat{G})$ corresponds to the cost function in equation \eqref{eq:MLEcf} in the parametric estimates of $\hat{G}$.
+This is similar to the approach followed in~\citep{FDIDENT} to combine different initial estimates.
+
+Alternatively, one can define the best model ($\model{best}$) and the second best model ($\model{2nd}$) as the models that comply to the inequalty
+$
+  \costFunc{}\left(\model{best}\right) < 
+  \costFunc{}\left( \model{2nd} \right) < 
+  \ldots
+$
+where $\model{best} \neq \model{2nd}$.
+
+\subsection{Reference Model Measurements}
+
+%\JL{
+Since the true model $\true{G}$ is not known for real-life systems, a practically viable reference model is needed.
+Additional measurements were performed using a \gls{VXI} measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
+Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\mathrm{VXI}$, and used as a reference model. 
+The \gls{VXI} measurement setup is summarized as follows.
+\begin{itemize}
+  \item Signal Generator card: \gls{VXI} HP E1445A.
+  \item Acquisition cards: \gls{VXI} HP E1430A.
+  \item Sampling frequency: $f_\mathrm{s} = 156\,250 \unit{Hz}$.
+  \item A total of $558$ frequency bins were used for the estimation, in the excited frequency band $[0.1,20] \unit{kHz}$, with a frequency resolution of $35.7\unit{Hz}$, giving a measurement time of $28\unit{ms}$.
+The excitation signal was band-limited periodic noise with an \gls{RMS} of $100\unit{mV}$.
+  \item The input and output signals were buffered and anti-alias filtered.
+\end{itemize}
+This yielded the model $G_\mathrm{VXI}$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.
+Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\mathrm{VXI}}$ as an initial estimate.
+Furthermore, $G_\mathrm{VXI}$ was used to play the role of $G_0$ from the previous section.
+
+\subsection{Model Estimation}
+  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
+  The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
+  The truncation method provides better estimates in many cases, but still suffers from a high variability.
+  On the other hand, the \gls{RFIR}-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
+  Obviously, $\model{best}$ has the lowest cost function values of all methods.
+  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the \gls{RFIR} provides the best estimate in most of the cases.
+  This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.
+
+\begin{remark}
+  In the simulations (e.g. \figref{fig:single-sim}), a $60\unit{dB}$ difference between `good' and `bad' estimates was observed.
+  Such a large gap is not observed in the measurements (\figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}).
+  Hence, defining a success rate based on a threshold tolerance would be very sensitive to the specific value of the threshold and hence unreliable.
+  Instead, the statistical location and dispersion are inspected to assess the relative performance of each method.
+  Practically, the median is used as a measure of location and the \gls{IQR} is used to inspect the spread as these are far more robust to outliers than e.g. the sample mean and variance.
+  These measures also have an easy interpretation: the median ($50\%$ percentile) indicates the cost function value that $50\%$ of the repetitions attain.
+  On the other hand, the \gls{IQR} ($25\%$ through $75\%$ percentile) contains  exactly half of the observations.
+\end{remark}
+
+\begin{figure}[p]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
+  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
+  The bottom plot shows a zoom of the top plot.
+  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
+  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
+  \label{fig:costMeasurements}
+\end{figure}
+
+\begin{table}[p]
+  \centering
+  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
+% \input{\thisDir/table1.tex}
+\pgfplotstabletypeset[precision=0]{
+method            P000     P025     P050      P075       P100   
+\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
+\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
+\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
+\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
+\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
+}
+  \label{tbl:costMeasurements}
+\end{table}
+
+\subsection{Model Validation}
+\subsubsection{Cost function limitations}
+In the previous section, the cost function was studied to determine the effectiveness of the starting values.
+However, inspecting the cost function $V(\theta)$ only accounts for how well an estimated model fits the measured data, which may be misleading.
+For an example, overfitting a model may result in the absorption of both the systematic behavior and the noise into the model. 
+Consequently, an arbitrarily small cost function may ensue although the estimated model may be virtually useless to predict the system behavior.
+
+\subsubsection{Validation criterion}
+To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
+To this end, the model is validated using the 2-norm (or distance) on the model error:
+\begin{equation}
+  \validationDistance{\bullet} 
+  \isdef 
+  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
+  \text{.}
+  \label{eq:measurementCriterion}
+\end{equation} 
+This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the \gls{VXI}.
+
+\subsubsection{Validation performance}
+The observed median and \gls{IQR} of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
+The existing methods provide good estimates in only $25\%$ of the cases.
+The truncation method provides a considerable improvement but still suffers from $25\%$ poor estimates.
+Compared to the existing \gls{BTLS} and \gls{GTLS} techniques, the \gls{RFIR} and hence also $\model{best}$ entail an overall reduction in the observed distance by a factor $8$, in most cases. 
+On the other hand, the reference $\model{VXI}$ shows the best global performance. 
+This indicates that the proposed methods do no converge to the same local optimum.
+Nevertheless, the proposed methods improve the model quality by almost an order of magnitude.
+
+As the criterion in equation~\eqref{eq:measurementCriterion} no longer depends on the cost function, the initial estimates can also be investigated.
+The difference between the distance of $\model[init]{\bullet}$ and $\model{\bullet}$ indicates how much the final ML estimate from the raw data, in each respective branch of \figref{fig:flowgraph}, improves over the initial estimate.
+Remarkably, on average, the final ML estimation provides only a marginal improvement for the \gls{RFIR}. 
+However, this final step reduces the spread and hence yields a more reliable estimate.
+E.g. note in \tabref{tbl:validationMeasurements} that this step reduces the worst-case distance from $18.21$ to $4.55$.
+
+\begin{figure}[p]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \input{\thisDir/fig/meas-validation.tikz}
+  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
+  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
+  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
+  The bottom plot shows a zoom of the top plot.
+  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
+  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
+  \label{fig:validationMeasurements}
+\end{figure}
+\begin{table}[p]
+  \centering
+  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
+% \input{\thisDir/table2.tex}
+
+\pgfplotstabletypeset[precision=2,zerofill=true]{
+method              P000      P025      P050        P075     P100   
+\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
+\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
+\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
+\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
+\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
+\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
+\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
+}
+\label{tbl:validationMeasurements}
+\end{table}
+
+\section{Consequences of selecting the `best` model}
+To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
+To do so, we inspect the performance by means of the cost function (used during estimation) and by means of the validation distance.
+The datasets used in this analysis are those from the measurements, but similar results can be obtained from the other data sets.
+
+In \figref{fig:overview} we can compare $\model{2nd}$ and $\model{best}$.
+By inspecting the different estimates for  each of the repeated experiments (\figref{fig:overview}), it can easily be seen that choosing $\model{RFIR}$ while it is not $\model{best}$ only leads to a very modest performance degradation.
+In \figref{fig:init:histogramEnhancement}, the different methods are compared by subtracting the performance of the $\model{best}$ from the performance of the respective methods.
+As such, each column in the figure indicates the performance of this method when it is not the `best'.
+Obviously, when we consider the cost function used during estimation (left subfigure), we can only degrade the performance by construction of $\model{best}$.
+For the validation data, however, this is no longer guaranteed as can be seen in the right subplot.
+On average, there is very little performance that can be gained from not using $\model{best}$, however, for two or three data points, there is a considerable improvement.
+From that figure it can also be seen that there is little performance to lose from choosing $\model{RFIR}$ over $\model{best}$ when RFIR is not the `best' method.
+The outcome is less favorable for the alternative methods.
+For $\model{exist}$ it can be seen that selecting those instead of $\model{best}$  degrades the validation performance by $10$ or even more in $75\%$ of the cases.
+The situation is already less severe for $\model{trunc}$ (in $75\%$ of the cases, the degradation is larger than $0.5$).
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/fig/overview-cost-val.tikz}
+  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
+  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
+  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
+  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
+  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
+  \label{fig:overview}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \ref{leg:init:secondBest}
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.60\figurewidth}
+  \input{\thisDir/fig/special-histogram.tikz}
+  \caption[Performance degradation/enhancement for selecting the second best model.]{
+  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
+  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
+  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
+  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the plot shows when method $\bullet$ is \emph{not} selected as the `best' method.
+  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
+  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
+  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e.
+there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
+  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
+  }
+  \label{fig:init:histogramEnhancement}
+\end{figure}
+
+\section{Remark on Generality}
+\label{se:Generality}
+In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
+In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
+However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.
+
+\subsection{Limitations of the smoothers}
+On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g.
+heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
+However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.
+
+In particular for RFIR, a simulation study in~\citep{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
+For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
+
+\subsection{Stress test of the smoothers}
+To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
+In particular, all combinations of
+\begin{itemize}
+  \item low-pass, high-pass, band-pass and band-stop 
+  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
+\end{itemize}
+discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
+Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
+The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
+The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
+Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
+See \tabref{tbl:init:stresstest} for an overview of the filters and  \figref{fig:bodeplots} for the corresponding bode plots.
+
+The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
+Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
+
+\begin{table}
+  \centering
+  \caption{Overview of the test cases for the initialization stress test.}
+\begin{tabular}{crlrrrrr}
+\toprule
+\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta} [\%]$  &  $\eta_{\mathrm{exist}} [\%]$ &  $\eta_{\mathrm{trunc}} [\%]$   &  $\eta_{\mathrm{RFIR}} [\%]$  &  $\eta_{\mathrm{best}} [\%]$ \\
+\midrule
+1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
+2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
+3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
+4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
+5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
+6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
+7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
+8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
+9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
+10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
+11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
+12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
+13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
+14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
+15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
+16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
+\bottomrule
+\end{tabular}
+\label{tbl:init:stresstest}
+\end{table}
+
+\subsection{Observations}
+The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
+In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm{\model{\bullet} - \true{G}} < tol$.
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:init:stress:bodes}
+  \input{\thisDir/fig/bodeplots.tikz}
+  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
+  For each filter, two (randomly selected) instanced of the parametric estimates $\model{\bullet}$ are shown per method.
+  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
+  % Left to right: low-pass, band-pass, high-pass and band-stop.
+  }
+  \label{fig:bodeplots}
+\end{figure}
+
+\begin{figure}[p]
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \centering
+  \ref{leg:distances}
+  \input{\thisDir/fig/distances.tikz}
+  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
+  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
+  }
+  \label{fig:distancesStress}
+\end{figure}
+
+A few remarks regarding these results are appropriate.
+\begin{itemize}
+  \item In many of the tested situations (cases 1,3,13-16), all methods yield a good model quality.
+  \item In some situations (cases 8, 10, 12), the model quality is generally poor. 
+  The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
+  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
+  \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
+  This is an underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
+  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
+  \item The RFIR performs (significantly) better than the existing methods in various cases (4-7, 9, 11).
+  \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.
+in cases 2, 4 and 6, this illustrates that combining initialization schemes improves the model quality.
+  Particularly, case 2 implies that \model{best} contains initial estimates of all different techniques.
+  \item For all of the tested systems (except possibly for case 2), the truncated LPM is not advisable over the existing methods.
+\end{itemize}
+
+In general, one can see from these simulations that \gls{RFIR} either performs as well as (or even better than) the existing techniques when a good estimate is obtained.
+There are no cases where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
+On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.
+
+\section{Computational effort}\label{sec:initvals:computation}
+While improved initial values yield better models of an improved quality, their generation does require some computational effort.
+Although the amount of available computing power has been steadily increasing over the last decades, it remains important to keep an eye on the computing effort required to estimate a model or, in this case, to generate the starting values required to estimate a model.
+E.g.
+in embedded applications where computing power and physical power consumption are  restrained and which have been attracting a lot of attention in data science during the recent years\TODO{cite arduino, rasbpi}, it remains an important factor to account for.
+
+Here, we will discuss two aspects of the computational effort very briefly.
+On the one hand, the computation time, as measured on a physical computer with a practical implementation of the algorithms, gives a rough idea of how these methods may perform in practice.
+On the other hand, the asymptotic complexity of the different smoothers is investigated. 
+While such asymptotics give little insight in practical running times, they are valuable tools to see how well (or poor) such methods scale up towards larger datasets.
+
+\subsection{Practical runtime}
+In practical measurements of the computation time for any piece of software, one typically distinguishes between different kinds of `time'.
+\begin{itemize}
+  \item The wall-clock time $\wallclocktime$, sometimes called `real time`, is the time difference between the start and end of the program under test.
+  \item The \glsentryshort{CPU} time $\cputime$, is the amount of time that the \glspl{CPU} actually spends executing the program under test.
+\end{itemize}
+This distinction is necessary for multi-tasking environments (such as computer), since during the execution of the program under test, the \gls{CPU} may spend a while to execute other programs in the background.
+The latter obviously requires a small amount of wall-clock time, but it does not increase the \gls{CPU} time of the program:
+\begin{equation}
+  \wallclocktime = \cputime + t_{\mathrm{other\;processes}}
+\end{equation}
+for a single-core \gls{CPU}.
+
+In summary, the $\cputime$ is an indication of the computational effort required to execute the algorithm, whereas $\wallclocktime$ indicates the amount of time a user has to wait for the program.
+In this case $\cputime$ is hence the most relevant of both, since $\wallclocktime$ is also determined by what other programs the user is running at the same time.
+
+Unfortunately, \MATLAB, like many other interpreted languages, does not provide any feature to measure $\cputime$ of a segment of code.
+Instead, the typical \code{tic} and \code{toc} functions measure the wall-clock time.
+To reduce the effect of other running programs and one-time actions (e.g.
+just-in-time compilation, caching, \ldots), it is a common practice~\citep{McKeeman2008} to repeatedly measure $\wallclocktime$ and retain the minimum (as an approximation for $\cputime$) and/or the median (to reduce the effect of other programs claiming the \gls{CPU} for extended amounts of time).
+
+In this case, the \MATLAB function \code{timeit}~\citep{matlab:timeit} has been used to measure the timing of the different functions.
+This function  reports the median wall-clock time and chooses the number of repetitions automatically.
+The timings have been measured on an Early 2013 MacBook Pro Retina 15-inch with $2.7\unit{GHz}$ Intel Core i7 \gls{CPU} and $16 \unit{GB}$ \gls{RAM} running Mac OS X 10.11.3 and \MATLAB R2015b.
+The recommendations from the white paper by \citet{McKeeman2008} have been followed during these measurements.
+
+\TODO{describe settings for the experiment: $N$, etc.}
+
+The observed timings are shown in \TODO{tableref}.
+\TODO{discuss timings}
+
+\TODO{table summary}
+
+\subsection{Asymptotic runtime}
+For the asymptotic runtime, we are mainly interested in how each of the smoothers scale with the size of the dataset, i.e. the number of samples $N$.
+
+% See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation
+
+The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear system requires $\bigO{n^3}$ operations in general~\citep{Golub1996}.
+The truncation of the impulse response relies on linear regression which takes $\bigO{n_{\theta}^2 N}$ operations.
+Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N}$ since both $n_{\theta}$ and $N_W$ are typically small.
+
+Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
+Using general methods, this is an operations that requires $\bigO{N^3}$ time.
+% However, due to the Toeplitz structure~\citep{Heinig2011} of the regression matrix, this can be solved in $\bigO{N^2}$.
+
+It can be seen that the local modeling methods scale more favorably than e.g. \gls{RFIR}.
+
+\subsection{Implementation aspects}
+\TODO{hint towards parallization}
+\TODO{most costly: iteration}
+
+\section{Conclusion}\label{se:Conclusion}
+The simulations have demonstrated that use of a smoothed non-parametric estimate of the \gls{FRF} can improve the success rate of minimizing the \gls{ML} cost function for the estimation of the transfer functions of \gls{LTI} systems, subjected to noisy signals.
+Specifically, two smoothing methods were used and compared: 1) the truncated \gls{LPM} method, and 2) the \gls{RFIR} method.
+The simulation results clearly show that the \gls{RFIR} method is superior to the truncated \gls{LPM} method and the existing \gls{BTLS} and \gls{GTLS} methods.
+
+The usefulness of the initial values obtained via the proposed smoothing techniques was confirmed on a measurement of a band-pass filter in a noisy environment.
+In most cases, the proposed initial values in the example made it possible to reduce the cost function by a factor two compared to existing methods.
+Moreover, the obtained models were validated against a high-quality measurement where the \gls{RMS} error on the transfer function could be reduced by a factor of eight for most cases, due to the improved initial values.
+
+Thus, the work in this chapter has demonstrated the effectiveness of the studied \gls{FRF} smoothing techniques in enhancing the initial values.
+Consequently, the quality of parametric estimates can be increased considerably by using non-parametric \gls{FRF} models to initialize the non-convex optimization problem of fitting a rational transfer function model.
+Hence, the ease-of-use of parametric model fitting can be increased significantly by having high-quality non-parametric \gls{FRF} models.
+This comes at a limited cost for the end-user: in principle these smoothers can be tried without any additional intervention by the user.
+The only disadvantage is the additional computational effort required and hence also the increase in wall clock time to obtain a parametric estimate.
+However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest.
+
+%\input{ch05-initvals/InitialValuesPaper.tex}
+
+%\input{ch05-initvals/letter.inc.tex}

### 2016-02-13 ch05-initvals/initial-values.tex
Some more comments of Johan addressed

@@
 \begin{remark}
+The \gls{LRM} has also been tried to generate better initial values.
+However, given the discussion in \chapref{sec:nonparametric}, it is clear that the \gls{LRM} performs poorly in low \gls{SNR} situations.
+The same was apparent from the quick trial we ran on \gls{LRM} starting values.
+As such, the use of \gls{LRM} over \gls{LPM} offers no advantage for generation initial estimates.
+\end{remark}
+
+\begin{remark}
 Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
@@
 \end{conjecture}
-\TODO{Johan: merk op dat dit niet zo hoeft te zijn! zelfs vanuit $\true{G}$ kan het misgaan}
+\begin{remark}
+The use of $\true{G}$ as an initial estimation not necessarily entails in converging to the global optimum since it is not guaranteed that $\true{G}$ lies within the attraction region of the global optimum.
+\end{remark}
 
@@
 \subsection{Asymptotic runtime}
-For the asymptotic runtime, we are mainly interested in how each of the smoothers scale with the size of the dataset, i.e. the number of samples $N$.
+For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$.
 
@@
 Using general methods, this is an operations that requires $\bigO{N^3}$ time.
-% However, due to the Toeplitz structure~\citep{Heinig2011} of the regression matrix, this can be solved in $\bigO{N^2}$.
 
@@
 \subsection{Implementation aspects}
-\TODO{hint towards parallization}
-\TODO{most costly: iteration}
+This section discusses some implications and recommendations for the implementation of  a system identification toolbox.
+
+Whereas \gls{RFIR} is shown to provide reliable starting values, it remains advisable to have multiple initialization strategies available to improve the likelihood of attaining a good starting value.
+This is also the approach that toolboxes such as \citep{FDIDENT} and \citep{TDIDENT} employ.
+Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e. one can easily try out a different strategy in parallel without incurring a lot of overhead.
+As such, computing multiple starting values can happen without a significant increase in wall-clock time and consequently a sluggish user-experience.
 

### 2016-02-13 ch05-initvals/initial-values.tex
Improve caption of 2nd order fx of initvals

@@
   Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
-  In red/orange the positive values ($X_{\bullet} > X_{\mathrm{best}}$), the performance degradation for using $\model{\bullet}$ over $\model{best}$ is shown.
-  The negative values ($X_{\bullet} < X_{\mathrm{best}}$), i.e. the performance enhancement (for using $\model{\bullet}$ instead of $\model{best}$) is shown in green/blue.
-  Zero values (i.e. $X_{\bullet} = X_{\mathrm{best}}$) are not shown, hence the plot shows when method $\bullet$ is \emph{not} selected as the `best' method.
+  The markers show individual observations and the boxes show the \gls{IQR}.
   The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
-  The performance degradation of choosing $\model{RFIR}$ instead of $\model{best}$ is smaller than the corresponding performance degradation for the other methods.
-  The performance enhancement from choosing $\model{RFIR}$ over $\model{best}$, is almost on par with the corresponding performance degradation (i.e.
-there is little to gain \emph{or} lose from choosing $\model{RFIR}$ over $\model{best}$).
-  For $\model{trunc}$ and $\model{exist}$, there is much less performance to gain from picking those over $\model{best}$ and there is a lot more to lose.
+  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
+  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
   }

### 2016-02-15 front-and-back-matter/summary.inc.tex
Shorten summary

@@
 \chapter{Summary}
-To understand, simulate and control physical systems around us, good mathematical models of these systems are required.
-To obtain such models, system identification is a set of powerful tools that serve to extract mathematical models from measurements of the physical world given the assumptions one makes about this world.
-To this end, one has to carry out different steps:
+To understand, simulate and control physical systems, good mathematical models are required. 
+System identification is a set of powerful tools that distill mathematical models from measurements of the physical world. 
+To this end, one has to:
 \begin{enumerate}
- \item perform experiments to observe the world in a meaningful way,
- \item inspect the measured data and check whether they are of good quality,
+\item perform experiments to observe the system in a meaningful way,
 \item suppress unwanted effects and extract the features of interest from the measurements,
-\item fit a mathematical model to the measurement data.
+\item fit a model to the measurements.
 \end{enumerate}
 
-Unfortunately, the effective use of system identification hinges strongly on the skill the user possesses for each of these steps.
-This doctorate focuses on providing easy-to-use system identification tools.
-This should allow both beginning users to obtain good models with little effort, and seasoned practitioners to obtain better models with more ease.
+Unfortunately, the effective use of system identification hinges strongly on the skill of the user. This doctorate focuses on easy-to-use system identification tools. 
+These should allow both beginners to obtain good models, and seasoned practitioners to obtain better models with ease.
 
-The first part of this work focuses on the design of a good experiment.
-Contrary to optimal design, this work related to robust experiment design, uses very little and relatively ``unstructured'' information about the system under test such that the obtained multisine signals can be used to measure a wide class of systems effectively.
-This design relies on a few assumptions such as a very rough idea of the frequency band of interest and the minimal damping one expects to observe from the system to obtain a polyvalent excitation design.
+The first part of this work focuses on the design of a robust experiment. 
+In contrast to optimal designs, only a few assumptions about the system, e.g. the minimal damping and the frequency bands of interest, are made. 
+Therefore, such a constructed multisine signal can be used to measure many different systems efficiently.
 
-The second part of this thesis describes non-parametric estimators for the frequency response function (FRF) that can estimate and suppress leakage and noise effects in the measurements.
-Most importantly, in this work extensions of the Local Polynomial and Local Rational Method (LPM and LRM) are investigated.
-This family of local estimators rely on approximating the input-output measurements in local windows in the frequency domain by either polynomial or rational models.
+The second part of this thesis describes non-parametric estimators for the frequency response function (FRF) that estimate and suppress leakage and noise effects. 
+Extensions of the Local Polynomial and Local Rational Method (LPM and LRM) are investigated.
+These approximate the input-output measurements in local frequency domain windows by either polynomial or rational models.
 
-Consequently, such local models can be used to great effect in areas where high-order models are commonly used, e.g.
-for the flexible dynamics of mechanical structures.
-In particular, these techniques have been used on an active vibration isolation system to estimate the resonance peaks without having to rely on high-order models and the tremendous model selection effort they require.
-Equally important, this has also shown that these local modeling methods allow a much more accurate view of the resonance to be extracted, than one can obtain from typical FRFs by exploiting the local models to interpolate in-between the frequency grid.
-Hence, compared to typical FRF measurements, this can reduce the measurement time significantly.
+Such local models can be used to great effect e.g. for the flexible dynamics of mechanical structures.
+ These local models have been used to obtain a more detailed view of the many resonance peaks of an active vibration isolation system than typical FRFs provide and unlike high-order models, they don’t incur laborious model-order selection.
+Consequently, the measurement time and modeling effort can be reduced significantly.
 
-The final part of the thesis considers the use of non-parametric smoothers to obtain better initial values to fit (global) parametric models to the measurement data.
-In particular, the situation with low signal-to-noise is considered since many initialization procedures tend to produce poor models.
-In this research, it has been shown that a very considerable improvement can be obtained, either by using a modified LPM or by using regularization.
-This allows users to obtain more reliable models, even from poor measurement data.
+The final part of the thesis considers the use of FRF smoothers to obtain better initial values to fit parametric models to the measurement data. 
+In particular for low signal-to-noise ratios, local modeling or regularization provide a considerable improvements. 
+This allows users to obtain better models, even from poor measurements.

### 2016-02-16 front-and-back-matter/titlepages.tex
Update VUB title page
Update title page + summary

@@
 \promotor{
-  \jurymember{prof. dr. ir.}{Johan Schoukens}{Vrije Universiteit Brussel}
+  \jurymember{prof. dr. ir.}{Johan Schoukens}{Vrije Universiteit Brussel (VUB)}
   \jurymember{dr. ir.}{Tom Oomen}{Eindhoven University of Technology}
@@
 
-\title{Development of User-friendly\\System Identification Techniques}
+\title{Development of User-Friendly\\System Identification Techniques}
 
@@
 \jury{
-  \jurymember{prof. dr. ir.}{Keith R. Godfrey}{Warwick University}
-  \jurymember{prof. dr. ir.}{Tomas McKelvey}{Chalmers}
-  \jurymember{dr. ir.}{Bart Peeters}{LMS}
-  \jurymember[president]{prof. dr. ir.}{Johan Deconinck}{Vrije Universiteit Brussel}
-  \jurymember[secretary]{dr. ir.}{Koen Tiels}{Vrije Universiteit Brussel}
+  \jurymember[president]{prof. dr. ir.}{Johan Deconinck}{VUB -- ETEC}
+  \jurymember[vice-president]{prof. dr. ir.}{Patrick Guillaume}{VUB -- MECH}
+  \jurymember[secretary]{dr. ir.}{Koen Tiels}{VUB -- ELEC}
+  \jurymember{prof. dr. ir.}{Keith R. Godfrey}{University of Warwick}
+  \jurymember{prof. dr. ir.}{Tomas McKelvey}{Chalmers University of Technology}
+  \jurymember{dr. ir.}{Bart Peeters}{Siemens Industry Software -- LMS}
 }

### 2016-02-16 ch05-initvals/initial-values.tex
LM algo rewritten
Timing of initvals completed

@@
 \begin{algorithmic}[1]
-  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
-  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
-%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
+  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon(\theta)^{\TT} \epsilon(\theta)$. 
+\Function{LevenbergMarquardt}{$\epsilon(\theta),  \theta^{\mathrm{init}}$}
+   \State $\atIter[0]{\theta} \gets \theta^{\mathrm{init}}$
+   \Comment{$\atIter[i]{X}$ denotes $X$ at iteration $i$.}
    \For{$i$ \textbf{in} $1 \to \infty$}
-      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
+      \State $U \, \Sigma \, W^{\TT} \gets \code{svd}\left( \frac{\partial \epsilon(\atIter[i-1]{\theta})}{\partial \theta}\right)$ 
+        \Comment{Singular value decomposition of Jacobian}
+      % \State $
+      %                  \text{Denote }\Sigma \equiv 
+      %                  \left[ \begin{matrix} 
+      %                  \sigma_1         & \deemph{0} & \deemph{\cdots} &           & \deemph{0}      \\
+      %                  \deemph{0}      & \sigma_2    &                   &           &                   \\
+      %                  \deemph{\vdots} &              & \ddots            &           & \deemph{\vdots} \\
+      %                                    &              &                   & \sigma_n &                   \\
+      %                   \deemph{0}      &              & \deemph{\cdots} &           & \deemph{0}      
+      %                   \end{matrix}\right]
+      %                $
       % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
-      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
-      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
-      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \norm{\atIter[i-1]{\theta} + \delta\theta} $
-      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
-          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
+      \If{$\lambda$ is undefined}
+        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{nn}})/100$
+      \EndIf
+      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, n}$
+      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon(\atIter[i-1]{\theta})$
+      \State $\atIter[i]{\theta} \gets \frac{(\atIter[i-1]{\theta} + \delta\theta) }{ \norm[2]{\atIter[i-1]{\theta} + \delta\theta} }$
+      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$} \Comment{Current step is a deterioration}
+         \State $\atIter[i]{\theta} \gets \atIter[i-1]{\theta}$ \Comment{Restart loop from previous estimate}
+          \State $\lambda \gets 10 \lambda$ 
       \Else
@@
       \EndIf
-      \State \textbf{if} $\norm{\delta\theta}/\norm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
+      \If {$\norm[2]{\delta\theta} < n_{\theta}  \cdot 10^{-6} \norm[2]{\atIter[i]{\theta}}$}
+          \State \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
+      \EndIf
    \EndFor
-%\EndFunction
+\EndFunction
 \end{algorithmic}
@@
  for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
- The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
+ The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
 \begin{align}
@@
 \end{align}
-where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
+where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
 This problem is solved using \code{fmincon} in \MATLAB.
@@
 \item 
-$\model{0}$ via the true model $\true{G}$ as an initial estimate,
+$\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
 \item
@@
 \begin{conjecture}\label{conj1}
-The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
-$\model{0}$.
+The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear optimization algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
+$\model{\trueSymbol}$.
 \end{conjecture}
@@
 
-%$\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{BTLS}$ are discussed later on.
-
 The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
-%\JL{in agreement with assumption \ref{assumption_G0hat_is_global_optimum}} \emph{viz}:
-\begin{align}
-\eta=\Prob{\hat G_\bullet=\hat G_0}
-\end{align}
+\begin{equation}
+\eta_{\bullet}=\Prob{\model{\bullet}=\model{\trueSymbol}}
+\end{equation}
 In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
-\begin{align}\label{eq:successrateTol}
-\eta=\Prob{ \norm{\hat G_\bullet-\hat G_0} < tol}
-\end{align}
+\begin{equation}\label{eq:successrateTol}
+\eta_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < tol}
+\end{equation}
 with $tol$ a numerical tolerance that will be specified later on.
-\TODO{Johan: beter een relatief criterium gebruiken (delen door $\norm{\true{G}}$)}
+\begin{remark}
+For an automated approach, it is better to define the success rate in terms of relative errors on the transfer function, i.e.
+\begin{equation}
+\eta_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < rel.tol  \norm[2]{\true{G}}}
+\text{.}
+\end{equation}
+\end{remark}
+\begin{remark}
+In this chapter, the absolute criterion is used.
+However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\eta$ is only mildly sensitive towards the tolerance $tol$ (or $rel.tol$) when the tolerance is chosen with care.
+Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $tol = rel.tol \norm[2]{\true{G}}$.
+\end{remark}
 
@@
 
-%\begin{align}
-%p(\hat G_x=\hat G_\circ) %G_0(q)= B(q)/A(q)
-%\end{align}
-
-The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
+The distance measure used in equation \eqref{eq:successrateTol} is defined as
 \begin{align}
-\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
+\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
+\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
 \end{align}
@@
 
-The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
-Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
+The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
+Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
 
@@
 The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
-In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm{\model{\bullet} - \true{G}} < tol$.
+In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}} < tol$.
+This is equivalent to the relative criterion of success since $\norm[2]{\true{G}} = 1$ for all systems.
 
@@
 
-\TODO{describe settings for the experiment: $N$, etc.}
-
-The observed timings are shown in \TODO{tableref}.
-\TODO{discuss timings}
-
-\TODO{table summary}
+To measure the timing of the different methods, essentially the same settings were used as in \secref{se:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $N_{3\unit{dB}} \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
+For each of the branches in \figref{fig:flowgraph}, three different timings are recorded (when applicable):
+\begin{itemize}
+  \item $t_{\mathrm{smooth}}$ is the time it takes to perform the smoothing (all blocks before \gls{GTLS}/\gls{BTLS}),
+  \item $t_{\mathrm{init}}$ is the time it takes to fit $\model[init]{\bullet}$, and
+  \item $t_{\mathrm{final}}$ is the time it takes to fit $\model{\bullet}$.
+\end{itemize}
+The median timings as returned by \code{timeit} are reported in \tabref{tbl:init:timing}.
+
+\begin{table}
+  \centering
+  \centering
+  \caption{Observed timing of the different estimation steps.}
+% \input{\thisDir/table2.tex}
+\pgfplotstabletypeset[precision=2,zerofill=true]{
+Q  NBW  method  tsmooth    tinit  tfinal
+ 6  36  \model{true}    nan     nan     0.197034 
+ 6  36  \model{exist}   nan     nan     0.159937 
+ 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
+ 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
+ 6  48  \model{true}    nan     nan     0.209216 
+ 6  48  \model{exist}   nan     nan     0.206823 
+ 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
+ 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
+20  36  \model{true}    nan     nan     0.445936 
+20  36  \model{exist}   nan     nan     0.429752 
+20  36  \model{trunc}   4.83667     0.225876    0.454757 
+20  36  \model{RFIR}    6.92575     0.253981    0.482431 
+20  48  \model{true}    nan     nan     0.467081 
+20  48  \model{exist}   nan     nan     0.457577 
+20  48  \model{trunc}   6.59726     0.312937    0.461114 
+20  48  \model{RFIR}    8.05168     0.312297    0.468905 
+}
+\label{tbl:init:timing}
+
+\TODO{fix pgfplotstable formatting}
+\end{table}
+
+From the timings in \tabref{tbl:init:timing}, it can be seen that the smoothers require a considerable amount of time that overshadows the fitting time.
+However, it should be noted that all these implementations rely on code that has not been optimized for performance.
+As such it is not possible to draw conclusions about the performance one may expect from performance-optimized implementations one would use in a commercial toolbox.
+In particular the \gls{RFIR} smoother takes an exorbitant amount of time.
+The fact that for small problem sizes (top of the table) the runtime is only slightly shorter than for the larger problems (bottom of the table), suggests that there is a considerable fixed overhead in the implementation we used.
+Particularly, the construction of the \gls{DCkernel} matrix happens to be the culprit for these long execution times.
+The truncated \gls{LPM}, on the other hand, requires a more reasonable amount of time for the short data lengths.
+For longer datasets, it appears that the \code{kron} function is one of the major culprits for the long runtimes of the \gls{LPM}.
 
 \subsection{Asymptotic runtime}
-For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$.
+For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e.
+the number of samples $N$, and the model complexity $n_{\theta}$ of the smoother.
 
@@
 
-The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear system requires $\bigO{n^3}$ operations in general~\citep{Golub1996}.
-The truncation of the impulse response relies on linear regression which takes $\bigO{n_{\theta}^2 N}$ operations.
-Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N}$ since both $n_{\theta}$ and $N_W$ are typically small.
-
-Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
-Using general methods, this is an operations that requires $\bigO{N^3}$ time.
-
-It can be seen that the local modeling methods scale more favorably than e.g. \gls{RFIR}.
+The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e.
+$n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear regression problem with $C$ parameters and $D$ datapoints takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation}.
+The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
+Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$
+
+The \gls{RFIR} relies on fitting a \gls{FIR} filter with $n_{\theta} = n_g$ taps to $N$ datapoints.
+Using the same logic as above, this requires $\bigO{N n_{g}^2 + n_g^3}$ operations.
+
+The computational complexity  of both methods scales linearly in the length of the dataset.
+However, since the required length $n_g$ of a \gls{FIR} filter is typically a lot more (e.g.
+$200$ in this chapter) than the number of local parameters (or bandwidth) of the \gls{LPM} (e.g.
+$N_W = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
+Intuitively, the local modeling methods benefit from their locality since that enables them to be flexible without a huge amount of parameters.
 

### 2016-02-16 ch05-initvals/styles.inc.tex
Table with different stress test cases
Clean up special histogram figure
Timing of initvals completed

@@
 
-\pgfplotstableset{
+\pgfplotstableset{%
 	%zerofill=true,
 	after row=[3pt],
+                  clear infinite,
 	assign column name/.code={%
@@
 	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
+                  columns/Q/.style={column type=r,column name={\shortstack[r]{\textsc{$Q$.}\\{$\unit{dB}$}}}},
+                  columns/NBW/.style={column type=r,column name={\shortstack[r]{\textsc{$N_{\mathrm{3dB}}$.}\\{}}}},
+                  columns/tsmooth/.style={column type=r,column name={X}},
+                  columns/tinit/.style={column type=r,column name={\shortstack[r]{\textsc{$t_{\mathrm{init}}$.}\\{$\unit{s}$}}}},
+                  columns/tfinal/.style={column type=r,column name={\shortstack[r]{\textsc{$t_{\mathrm{final}}$.}\\{$\unit{s}$}}}},
 	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},

### 2016-02-16 ch05-initvals/initial-values.tex
Clean up timing table

@@
 % \input{\thisDir/table2.tex}
-\pgfplotstabletypeset[precision=2,zerofill=true]{
+\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0, %round to 1 ms
+    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
+    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
+    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
+    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
+    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
+    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
+]{%
 Q  NBW  method  tsmooth    tinit  tfinal
- 6  36  \model{true}    nan     nan     0.197034 
+ 6  36  \model{\trueSymbol}    nan     nan     0.197034 
  6  36  \model{exist}   nan     nan     0.159937 
@@
  6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
- 6  48  \model{true}    nan     nan     0.209216 
+ 6  48  \model{\trueSymbol}    nan     nan     0.209216 
  6  48  \model{exist}   nan     nan     0.206823 
@@
  6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
-20  36  \model{true}    nan     nan     0.445936 
+20  36  \model{\trueSymbol}    nan     nan     0.445936 
 20  36  \model{exist}   nan     nan     0.429752 
@@
 20  36  \model{RFIR}    6.92575     0.253981    0.482431 
-20  48  \model{true}    nan     nan     0.467081 
+20  48  \model{\trueSymbol}    nan     nan     0.467081 
 20  48  \model{exist}   nan     nan     0.457577 
@@
 \label{tbl:init:timing}
-
-\TODO{fix pgfplotstable formatting}
 \end{table}
@@
 The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e.
-$n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear regression problem with $C$ parameters and $D$ datapoints takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation}.
+$n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
 The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.

### 2016-02-16 ch05-initvals/styles.inc.tex
Clean up timing table

--- 2015-10-28 ch05-initvals/styles.inc.tex
@@
 
-\pgfplotstableset{
-	%zerofill=true,
+\pgfplotstableset{%
+	zerofill=true,
 	after row=[3pt],
+                  every head row/.style={before row=\toprule, after row={\\\midrule}},
+                  every last row/.style={after row=\bottomrule}
 	assign column name/.code={%
@@
 	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}},
-	columns/contribution/.style={column name={\textsc{Contribution}}},
 	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
@@
 	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
-	postproc cell content/.append code={
-            %\ifnum1=\pgfplotstablepartno
-                \pgfkeysalso{@cell content/.add={}{\%}}%
-            %\fi
-        },
-	},
-	every head row/.style={before row=\toprule, after row={\\\midrule}},
-    every last row/.style={after row=\bottomrule}
+                    	postproc cell content/.append code={\pgfkeysalso{@cell content/.add={}{\%}}},
 	}
+}

### 2016-02-17 ch01-intro/introduction.tex
Add epigraphs
Fix timing table in initvals better

@@
 \def\thisDir{ch01-intro}
-
+\myEpigraph{It's a dangerous business, Frodo, going out your door.
+You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}
   \section{System idenfication}
@@
 In collaboration with fellow researchers, I have written a few other publications.
-However, these publications are not covered in this thesis.
+However, these publications are not covered in this dissertation.
 

### 2016-02-17 ch05-initvals/initial-values.tex
Fix timing table in initvals better

@@
 % \input{\thisDir/table2.tex}
-\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0, %round to 1 ms
+\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
     columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
@@
 Q  NBW  method  tsmooth    tinit  tfinal
- 6  36  \model{\trueSymbol}    nan     nan     0.197034 
- 6  36  \model{exist}   nan     nan     0.159937 
+ % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
+ % 6  36  \model{exist}   nan     nan     0.159937 
  6  36  \model{trunc}   0.745073    0.0623485   0.163107 
  6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
- 6  48  \model{\trueSymbol}    nan     nan     0.209216 
- 6  48  \model{exist}   nan     nan     0.206823 
+ % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
+ % 6  48  \model{exist}   nan     nan     0.206823 
  6  48  \model{trunc}   1.00383     0.0902347   0.208173 
  6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
-20  36  \model{\trueSymbol}    nan     nan     0.445936 
-20  36  \model{exist}   nan     nan     0.429752 
+% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
+% 20  36  \model{exist}   nan     nan     0.429752 
 20  36  \model{trunc}   4.83667     0.225876    0.454757 
 20  36  \model{RFIR}    6.92575     0.253981    0.482431 
-20  48  \model{\trueSymbol}    nan     nan     0.467081 
-20  48  \model{exist}   nan     nan     0.457577 
+% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
+% 20  48  \model{exist}   nan     nan     0.457577 
 20  48  \model{trunc}   6.59726     0.312937    0.461114 

### 2016-02-17 ch05-initvals/initial-values.tex
Uniformize formatting a bit

@@
 \begin{equation}\label{lpmtd1}
-y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
+y(t)=\true{G}(q^{-1})u_0(t)+H_0(q^{-1})e(t)
 \end{equation}
 %\comment{We don't have any results with colored noise yet!}
-where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
+where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
 $e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
@@
 \begin{equation}
-    G_0(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
+    \true{G}(q^{-1})= \frac{B(q^{-1})}{A(q^{-1})}
     \text{.}
@@
 \end{align}
-with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions.
-\TODO{explain init/end conditions in this context}
+with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the difference between the initial and end conditions of the filter $\true{G}$ during the measurement record.
 \begin{assumption}
@@
 
-\subsection{Initial Estimates Procedure}\label{se:initEstProcs} %{Obtaining initial estimates}
-
-%\begin{itemize}
-%\item
-%Obtain a good estimate of the FRF of the system by using the LPM: short description + reference
-
+\subsection{Initial Estimates Procedure}\label{sec:init:procedures}
 \begin{figure}
@@
   \includegraphics
-  [width=0.95\columnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (3, 4).
+  [width=\columnwidth]{\thisDir/fig/flowgraph}
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (\circledNum{3}, \circledNum{4}).
   The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
@@
 Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
-The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
-
-  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
+
+  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
 \begin{subequations}\label{lpmImplQuadG}
 \begin{align}
-G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
+\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
 \\
@@
 \ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart?
-It has actually been explained in further details in \sectref{se:initEstProcs}.}
+It has actually been explained in further details in \secref{sec:init:procedures}.}
 %\begin{enumerate}
-%\item (Left (first) path of the flowchart): The true model $G_0$ as initial values,
+%\item (Left (first) path of the flowchart): The true model $\true{G}$ as initial values,
 %\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
@@
 Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
-%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
 \begin{itemize}
-\item 
-$\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
-\item
-$\model{exist}$ is obtained via GTLS and BTLS,
-\item
-$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
-\item
-$\model{RFIR}$, initialized by means of the RFIR method. 
+    \item $\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
+    \item $\model{exist}$ is obtained via GTLS and BTLS,
+    \item $\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
+    \item $\model{RFIR}$, initialized by means of the RFIR method. 
 \end{itemize}
@@
   \begin{equation}
-     G_0(z) \Big|_{Q=6\unit{dB}}
+     \true{G}(z) \Big|_{Q=6\unit{dB}}
     = 1.74 \cdot 10^{-3}
@@
   \begin{equation}
-    G_0(z) \Big|_{Q=20\unit{dB}}
+    \true{G}(z) \Big|_{Q=20\unit{dB}}
     = 309 \cdot 10^{-6}
@@
     \approx \frac{\sigma_{v}}
-                 {\left\| G_0 \right\|_2 \rms{u_0}}
+                 {\left\| \true{G} \right\|_2 \rms{u_0}}
     =  \frac{\sigma_{v}}
-            {\left\| G_0 \right\|_2}
+            {\left\| \true{G} \right\|_2}
   \label{eq:SNR-definition}
@@
 
-%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $G_0$, $\hat G_0$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
+%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $\true{G}$, $\hat \true{G}$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
 %}
 %\EG{
- \figref{fig:exampleFRF} depicts the Bode plot of the actual system $G_0$, in black
+ \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black
 %\comment{JL: in what color? (EG) black},
@@
  %\comment{JL: does it matter whether it is $\hat G_\mathrm{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
- that may or may not approximate $\hat{G}_{0}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
+ that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
  The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, discussed later.
@@
    %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t.
-the relative error, except when $\abs{G_0(\omega)}$ is small.
+the relative error, except when $\abs{\true{G}(\omega)}$ is small.
  %Practically, 
@@
 
- Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $G_0(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}.
- %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $G_0(\omega)$ over the broad frequency ranges.
- %Consequently, such estimates are practically worthless as an approximation of $G_0$.
- Consequently, such estimates are practically worthless approximations of $G_0$.
+ Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $\true{G}(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}.
+ %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $\true{G}(\omega)$ over the broad frequency ranges.
+ %Consequently, such estimates are practically worthless as an approximation of $\true{G}$.
+ Consequently, such estimates are practically worthless approximations of $\true{G}$.
  %}
@@
  % \caption{Results of an example of Monte Carlo simulation.}
- \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
+ \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
  Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
@@
 In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
-This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \hat{G}_{0}}$ are shown for the different strategies, and sorted by an ascending norm.
-This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \hat{G}_{0}}$ as sampled by the Monte Carlo algorithm.%}
+This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
+This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}
 
@@
 \begin{itemize}
-\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\hat{G}_{0}$.
+\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\model{\trueSymbol}$.
 Two major classifications can be made:
 \begin{enumerate}
-  \item `good' estimates which have $\|\model{\bullet} - \hat{G}_{0} \|_2 < tol \approx 6 \cdot 10^{-5}$,
-  \item `poor' estimates which are much farther from $\hat{G}_{0}$.  This is caused by the local optima.
+  \item `good' estimates which have $\|\model{\bullet} - \model{\trueSymbol} \|_2 < tol \approx 6 \cdot 10^{-5}$,
+  \item `poor' estimates which are much farther from $\model{\trueSymbol}$.  This is caused by the local optima.
 \end{enumerate}
@@
   \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\hat{G}_0$ approximates the true system $G_0$.
+ \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
  In the bottom plot, the difference between both is shown.
- Consequently, it makes sense to examine the behavior of the models in terms of $\hat{G}_0$ as long as this RMSE meets the user's requirements.}
+ Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
   \label{fig:RMSE}
@@
 \paragraph*{Remark about the model quality}
-In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\hat{G}_{0}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\hat{G}_{0}$ itself might be ill-suited.
+In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\trueSymbol}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\trueSymbol}$ itself might be ill-suited.
 A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
@@
 \begin{equation}
-    \RMSE(\hat{G}_{0}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{G_0}}{\SNR} 
+    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{\true{G}}}{\SNR} 
     \label{eq:heur-RMSE}
@@
 where $n_{\theta}=5$ is the number of estimated parameters in this case.
-In \figref{fig:RMSE}, the empirical $\RMSE(\hat{G}_{0})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
+In \figref{fig:RMSE}, the empirical $\RMSE(\model{\trueSymbol})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
 It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
-When the RMSE is then divided by $\norm{G_0}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
+When the RMSE is then divided by $\norm{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
 
@@
 Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\mathrm{VXI}}$ as an initial estimate.
-Furthermore, $G_\mathrm{VXI}$ was used to play the role of $G_0$ from the previous section.
+Furthermore, $G_\mathrm{VXI}$ was used to play the role of $\true{G}$ from the previous section.
 
@@
   \input{\thisDir/fig/distances.tikz}
-  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - G_0}$ for the different tested systems (different numbered plots) and the different initial values (colors).
-  Note that since $\norm{G_0}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
+  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
+  Note that since $\norm{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
   }

### 2016-02-18 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Uniformized a lot of figures, styles, ...

@@
 
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
-\TODO{ordos are incorrect: notation-wise}
+The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
 \begin{align}\label{lpmGTaylorS}
 G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
-\bigO{\left(\frac{r}{N}\right)^{(R+1)}},
+\bigO{\left(\frac{r}{N}\right)^{R+1}},
 \\
@@
 T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
-\bigO{  \left(\frac{r}{N}\right)^{(R+1)}  }
+\bigO{  \left(\frac{r}{N}\right)^{R+1}  }
 ,

### 2016-02-18 ch05-initvals/initial-values.tex
Uniformized a lot of figures, styles, ...

@@
 ~\citep{Pillonetto2010,Chen2012}. 
-The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
-%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
+The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the \gls{FRF}.
 \end{enumerate}
@@
 A corresponding parametric estimate is obtained as follows. 
-A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero.
-It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data.
-This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
-\TODO{spectra als formule geven}
+A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $I$ set to zero:
+\begin{equation}
+  U_{\mathrm{FRF}}(\omega_k) \isdef 1 
+  \qquad \text{and} \qquad
+  Y_{\mathrm{FRF}}(\omega_k)  \isdef G_{\bullet}(\omega_k)
+  \text{.}
+\end{equation}
+It is important to note that invoking the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the \glspl{FRF} from methods 3) and 4) will yield a different result from applying the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the raw data.
+This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance.
 \end{remark}
@@
 % \input{\thisDir/table2.tex}
-
-\pgfplotstabletypeset[precision=2,zerofill=true]{
+\pgfplotstabletypeset[zerofill=true,precision=2]{
 method              P000      P025      P050        P075     P100   

### 2016-02-18 config/styles.inc.tex
Uniformize formatting a bit
Uniformized a lot of figures, styles, ...

@@
 
-\def\thisDir{.}
+% \def\thisDir{.}
 
@@
 \pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
-\pgfplotsset{bw/.style={fill=bwfill,draw=bwline}}
+\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
 \pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}
@@
 \pgfplotsset{percentileLines/.style={black,dashed}}
-
 \tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}
@@
 %% TABLE STYLES
+% http://tex.stackexchange.com/questions/83487/pgfplotstable-converting-zeros-to-in-a-knitr-inline-table
 
@@
 	after row=[3pt],
+         every head row/.style={before row=\toprule, after row={\\\midrule}},
+         every last row/.style={after row=\bottomrule},
 	assign column name/.code={%
@@
         },
-	},
-	every head row/.style={before row=\toprule, after row={\\\midrule}},
-    every last row/.style={after row=\bottomrule}
 	}
+}

### 2016-02-18 ch02-qlogms/sysid.tex
Some consistency fixes

@@
-\section{Introduction}\label{sec:excitation:intro}
+\section{Introduction}\label{sec:excitation:sysid2012:intro}
 Input design deals with the task of choosing an excitation signal in a way so that the information obtained from the experiment is maximized.
@@
 
-The following parts of the paper are structured as follows.
+% The following parts of the paper are structured as follows.
 \secref{sec:excitation:inputDesign} briefly presents the necessary input design theory.
@@
 \end{align}
-which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously in e.g. \cite{Rojas2007}
+which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \cite{Rojas2007}
 
@@
 The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
-This is illustrated in Section~\ref{sec:excitation:sim}.
+This is illustrated in \secref{sec:excitation:sim}.
 

### 2016-02-18 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some consistency fixes

@@
 
+\TODO{paper $\to$ section}
+
+\TODO{use gls commands in this part}
+
+\TODO{remove duplicate labels (global)}
+
 \subsection{Introduction}
@@
 This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
-\begin{equation}\label{lpmtd1}
+\begin{equation}\label{eq:lpm:TD}
 y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
@@
 
-The rest of the paper is structured as follows. Section \ref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup.
-Section \ref{se:smoothingFRFestimate} discusses the novel smoothing method.
+The rest of the paper is structured as follows. \secref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup.
+\secref{se:smoothingFRFestimate} discusses the novel smoothing method.
 
@@
 In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
+%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:lpm:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
 Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
@@
 
-The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{lpmtd1} and \eqref{lpmleak}, \emph{viz}:
+The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:lpm:TD} and \eqref{lpmleak}, \emph{viz}:
 \begin{equation}\label{lpm1spectra}
@@
 When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}\label{lpmImplQuadG}
-G_0(\Omega_{k+r})&\approx G_0(\Omega_k)+g_1r+g_2r^2
+\begin{align}
+G_0(\Omega_{k+r})
+  &\approx 
+  G_0(\Omega_k)+g_1r+g_2r^2
+  \label{eq:lpm:expansionG:quadratic}
 \\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_1r+t_2r^2\label{lpmImplQuadT}
+  T(\Omega_{k+r})
+    &\approx 
+    T(\Omega_k)+t_1r+t_2r^2
+    \label{eq:lpm:expansionT:quadratic}
 \end{align}
-
-\noindent
-($r\in\mathbb{W}_3$)
-and the vector of parameters:
-
+with ($r\in\mathbb{W}_3$) and the vector of parameters:
 \begin{equation}\label{lpmThetaEst}
@@
 \begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in Section \ref{se:DCvalueEst}.
+\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in \secref{se:DCvalueEst}.
 Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
@@
 
-The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}.
+The truncation time is determined from the data as described in \secref{se:truncImpulseResp}.
 This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.

### 2016-02-18 ch05-initvals/initial-values.tex
Some small changes all over the place

@@
   %TODO: simplify figure
-  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
-  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
+  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
   \label{fig:SpectraMeasurement}

### 2016-02-18 ch02-qlogms/excitation-design.tex
Add epigraphs
Some small changes all over the place
Ch02: merge conclusion

@@
 \def\thisDir{ch02-qlogms}
+\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
 \researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}
@@
     \toprule
-    Grid & Linear & Logarithmic & Quasi-logarithmic \\
+     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
     \midrule
@@
        & $\alpha f_{k}$
-       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
+       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
        \\[5pt]
@@
 
-\section{Simulations} \label{sec:simulation}
+\section{Simulations} \label{sec:excitation:simulation}
 In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
@@
 \label{sec:excitation:conclusion}
+In this chapter, we recalled that the design of optimal excitation signals may require prior knowledge that is either not sufficiently accurate or even unavailable.
+When only the limited prior knowledge that the system resonances lie in a certain (possibly very wide) frequency band, a suitable class of excitation signals can be constructed such that the relative uncertainty of the estimated resonance is independent of the resonance frequency.
+We showed that such a signal should have a power spectrum that is distributed in $1/f$.
+
 In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.
-
-The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in a wide frequency band with a constant uncertainty.
+The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in an even wider frequency band with a constant uncertainty.
 The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
-In practical applications, this slight increase is likely to be negligible.
+In practice, this slight increase is likely to be negligible.
 The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.

### 2016-02-18 ch02-qlogms/sysid.tex
Some small changes all over the place
Ch02: merge conclusion

@@
 \end{align}
-where $\omega_{k}/\omega_{k+1} \approx \alpha = e^{\Delta}$.
+where $\omega_{k}/\omega_{k+1} \approx \alpha$.
 Hence, the number of spectral lines inside \wdB is 
@@
 The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
-This is illustrated in \secref{sec:excitation:sim}.
+This is illustrated in \secref{sec:excitation:simulation}.
 
@@
 % This result was obtained for second order sections and illustrated on a more general system.
-
-%%Conclusion
-\section{Conclusions}\label{sec:excitation:conclusions}
-In this paper we recalled that the design of an optimal excitation signal may require prior system knowledge that is insufficiently accurate or even unavailable. 
-When only the limited prior knowledge that the system resonances lie in a certain (possibly wide) frequency band, we can create a suitable class of excitation signals. 
-These signals are required to yield estimates having a variance that is independent of the resonance frequencies of the system. 
-We showed that such a signal should have a power spectrum that is distributed in $1/f$.
-In this paper (quasi-)logarithmic multisines were considered to serve this purpose.
-
-By means of simulations for different second order sub-systems, it is confirmed that for a given damping, the variance of the estimated is almost independent of the actual resonance frequencies of the system within the frequency band of interest.
-The same results were found for higher order systems and illustrated for an example. 
-A theoretical motivation for these results is provided.
-
-The proposed excitation signals therefore offer an easy and efficient way to identify systems in a wide frequency range such that an accuracy level that is independent of the resonance frequencies can be attained for the complete frequency span.

### 2016-02-18 ch02-qlogms/excitation-design.tex
Clean up figures from CH02

@@
     \centering
-    \setlength\figureheight{5cm}
       \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figureheight{0.5\figurewidth}
     \input{\thisDir/figs/freqGrid.tikz}
@@
     \centering
-    \setlength\figureheight{5cm}
       \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figureheight{0.5\figurewidth}
     \input{\thisDir/figs/misalign.tikz}
@@
     \centering
-      \setlength\figureheight{5cm}
-      \setlength\figurewidth{0.65\columnwidth}
+      \setlength\figurewidth{0.68\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/betaWC.tikz}
@@
 
-  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will entail a large increase in the uncertainty of estimate.
+  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will lead to a large increase in the uncertainty of estimate.
 
@@
     \centering
-      \setlength\figureheight{5cm}
-      \setlength\figurewidth{0.65\columnwidth}
+      \setlength\figurewidth{0.68\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/alphaWC.tikz}
@@
     \centering
-      \setlength\figureheight{4cm}
-      \setlength\figurewidth{0.7\columnwidth}
+      \setlength\figurewidth{0.5\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/SignalAndSystem.tikz}
@@
     \centering
-    \setlength\figureheight{5cm}
-    \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figurewidth{0.68\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/Sys02-4.tikz}
-    \caption[Simulated FRF and its variance for different excitation signals.]{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
-             along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
+    \caption[Simulated FRF and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
     \label{fig:FRF1}
@@
     \centering
-    \setlength\figureheight{5cm}
-    \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figurewidth{0.68\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{FRFs for different second order systems with constant damping
+    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{\glspl{FRF} for different second order systems with constant damping
              $\damping=0.2$ but different resonance frequencies. Comparison of the
@@
     \centering
-    \setlength\figureheight{5cm}
-    \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figurewidth{0.68\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/damping005-cmp.tikz}
@@
   \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
-  \setlength{\figureheight}{5cm}
+  \setlength\figurewidth{0.68\columnwidth}
+  \setlength\figureheight{0.68\figurewidth}
   \input{\thisDir/figs/Sum02log0-2.tikz}
@@
     \centering
-      \setlength\figureheight{5cm}
       \setlength\figurewidth{0.8\columnwidth}
+      \setlength\figureheight{0.68\figurewidth}
     \input{\thisDir/figs/qlog_a050mall.tikz}

### 2016-02-18 ch03-lrm/nonparametric.tex
More outline added
Some future work stuffies + labels
Add Milgram quote

@@
 \chapter{Non-parametric modeling}
+\def\thisDir{ch03-lrm}
+\label{sec:nonparametric}
 
+\myEpigraph{The essence in obedience consists in the fact that a person comes to view himself as an instrument for carrying out another person's wishes and he therefore no longer regards himself as responsible for his actions.}{Stanley Milgram}{Obedience to Authority}
+
+\section{\TODO{LPM}}
+\section{\TODO{LRM}}
 \TODO{import LRM paper}
-\TODO{import Mikaya LPMTrunc paper}
+\section{\TODO{LPM with impulse response truncation}}
+\input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}
+
+\section{\TODO{Bias-variance trade-off }}
+\TODO{import LRM paper}
+
+\subsection{\TODO{Tuning rules}}
+\subsubsection{\TODO{Tuning using an Oracle}}
+\subsubsection{\TODO{Cross-validation}}
+
+\subsection{\TODO{Application}}
+
+\subsubsection{\TODO{AVIS}}
+\subsubsection{\TODO{F16}}

### 2016-02-20 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Clean up chapter 3

@@
-% \title{
-% Smoothing the LPM-Estimate of the Frequency Response Function Via an Impulse Response Truncation Technique}
-
-% \author{$^1$M.L.D. Lumori, \emph{Senior Member, IEEE}, $^2$E. Geerardyn, \emph{Student Member, IEEE}, \\ $^2$J. Schoukens, \emph{Fellow, IEEE}, and
-% $^2$J. Lataire, \emph{Member, IEEE}\\
-
-% \thanks{$^1$University of San Diego, Department of Electrical Engineering, 5998 Alcal\'a Park, San Diego, CA 92110, USA {\tt\small mlumori@sandiego.edu}}
-% \thanks{$^2$Vrije Universiteit Brussel, Dept. ELEC, Fundamental Electricity and Instrumentation, Pleinlaan 2, 1050 Brussels, Belgium}
-% \thanks{This work was supported in part by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem Fund, METH1), and by the Belgian Federal Government (IAP VII DYSCO).}
-% }
-
-% \begin{document}
-% \maketitle
-
 % \begin{abstract}
@@
 The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this paper makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
+The truncation method introduced in this section makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
 % \end{abstract}
 
-% \begin{IEEEkeywords}
-% Smoothing methods, Estimation, Least squares methods, Frequency response, Frequency domain analysis
-% \end{IEEEkeywords}
 \researchBasedOn[This section]{Lumori2014TIM}
@@
 \TODO{use gls commands in this part}
-
-\TODO{remove duplicate labels (global)}
 
@@
 
-This paper uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
+This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
 The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
 no user interaction.
-Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}.
-Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}.
-Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
+Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}.
+Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}.
+Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
 
-The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM.
-This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction.
+The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the LPM.
+This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
 The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
+It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
 
 Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A single-input-single-output (SISO) LTI system is considered.
+A \gls{SISO} \gls{LTI} system is considered.
 %, based on  \citep{Schoukens2009LPM}.
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
+This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
 \begin{equation}\label{eq:lpm:TD}
@@
 
-In this paper, however, a nonparametric technique is developed, %the identification problem is
+In this section, however, a nonparametric technique is developed, %the identification problem is
 formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}. The following  choices are made:
@@
 
-The work in this paper is for discrete-time systems.
+The work in this section is for discrete-time systems.
 Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
@@
 
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric FRF counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
+Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
 \item
@@
 
-The rest of the paper is structured as follows. \secref{se:theoryLPMandWindowing} covers the theory on the LPM and windowing for an OE setup.
+The rest of the section is structured as follows. \secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
 \secref{se:smoothingFRFestimate} discusses the novel smoothing method.
 
-Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth LPM estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the LPM estimate $\hat{G}_\text{poly}(\Omega_k)$.
+Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.
 
@@
 where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
-In this paper, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}
+In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}
 
@@
 \begin{assumption}
-The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
+The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
 \end{assumption}
@@
 The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$.
+\TODO{assumption is not complete! some expectation is missing!}
 \end{assumption}
@@
 
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the LPM.
-As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the LPM.
+The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}.
+As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the \gls{LPM}.
 
 \paragraph{Formulation of the Linear LS LPM}
-The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
+The \gls{LPM} is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
 \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
-The formulation in this paper is a summary for a \gls{SISO} system.
+The formulation in this section is a summary for a \gls{SISO} system.
 
@@
 The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.
-%(per JL)!
 
@@
 \end{equation}
-The \gls{LPM} estimate of the FRF is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
+The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
 \begin{equation}
@@
 
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
+The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
@@
 \end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \{1,\dots,N/2\}$ (i.e.
-the entire frequency band, including Nyquist, but excluding DC, and regularizing at the boundaries).
+This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e.
+the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries).
 This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.
@@
 
-The \gls{FRF} estimate is smoothed by truncating the estimated impulse response function. The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
+The \gls{FRF} estimate is smoothed by truncating the estimated impulse response function. 
+The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
 
@@
 \begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the LPM, corrected for its DC value as discussed in \secref{se:DCvalueEst}.
+\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{se:DCvalueEst}.
 Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
@@
 \end{align}
-
-\noindent
 (Subscript HSNR stands for High \gls{SNR}.)
@@
 
-\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. This is done by solving the following expression
+\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. 
+This is done by solving the following expression
 
@@
 Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
-
 \begin{align}\label{eq:truncTimeExpFit}
@@
 \end{align}
-
-\noindent
 where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
@@
 
-The paper introduced a novel time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}.
+The section introduced a novel time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}.
 It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.
@@
 A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-
-% \bibliographystyle{IEEEtran}
-% \bibliography{MikayaBibliography}
-% \end{document}

### 2016-02-20 ch02-qlogms/excitation-design.tex
Clean up chapter 2: show derivatives of G

@@
 \myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
-\researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}
+\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }
+\TODO{rename labels}
 
@@
 \label{sec:excitation:intro}
+Input design deals with the task of choosing an excitation signal in a way so that the information obtained from the experiment is maximized. 
+This is a problem which has a long history in statistics. 
+In system identification, the focus has mostly been on input design for dynamic systems.
+A common approach is to design the input spectrum and thereby maximizing the information matrix of the estimates, see e.g. \cite{Fedorov1972,Goodwin1977}.
+
+A complicating issue in identification of dynamic system is the fact that the information matrix often depends on the true parameter values. 
+Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design. 
+There are two main solutions to this discussed in the engineering literature:
+\begin{enumerate}
+\item Iterative input design where the design updated as more information about the system is available, see e.g. \cite{Hjalmarsson2005,Gevers2005}.
+\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007} and references therein. 
+\end{enumerate}
+
+In this chapter we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified. 
+We will consider input design when it is known that the system has resonances, possibly spanning a large frequency band. 
+It is however not necessary to know how many resonances are in the system. 
+The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.
+
 Experiment design is the first step in the system identification loop, as illustrated in \figref{fig:intro:identification-cycle}.
 Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
-
-\begin{conjecture}
-To identify the transfer function of a system, one has to apply an excitation signal to its input.
-\end{conjecture}
-\begin{conjecture}
-To know which excitation signal is a good signal to excite the system with, one needs to know the system.
-\end{conjecture}
-
-The two conjectures above illustrate the catch-22 a practicing modeler finds himself in: if one wishes to identify a system, one needs to apply a signal; but to determine a good signal, one needs to know the system.
-This conundrum becomes especially worrisome if one not only wants to use a `good' excitation signal, but rather the `best' excitation signal.
-
-In this chapter, we will investigate how one can develop excitation signals that try to alleviate this paradox by imposing heuristic prior knowledge about the system that is more generic than in a typical (robust) optimal input design, but less wasteful than typical generic full multisine signals.
-
-\subsection{Generic excitation signals}
-\label{sec:excitation:intro:generic}
-\TODO{\ldots}
-
-\subsection{Optimal excitation signals}
-\label{sec:excitation:intro:optimal}
-Since generic excitation signals are not specifically geared towards the particular system under test, such signals use signal power in an inefficient way that does not reduce the variance of the model estimate significantly.
-\TODO{\ldots}
-
-\subsection{Robust excitation signals}
-\label{sec:excitation:intro:robust}
-As illustrated above, optimal experiment design places the user in a catch-22 situation\footnote{See the 1961 Joseph Heller novel `Catch-22'.}.
-In the recent years, this has sparked attention towards robust signal design~\citep{Rojas2007} to alleviate the drawbacks of (nominal) optimal experiment design.
-%TODO
 
@@
 \input{ch02-qlogms/logMS_IMTC.tex}
-
-\TODO{reshape figures}
-\TODO{rename labels}
 
@@
 
-  In the first section of this paper, we start from a generic transfer function model and discuss a decomposition thereof in second order subsystems and their properties.
+  In the first section of this chapter, we start from a generic transfer function model and discuss a decomposition thereof in second order subsystems and their properties.
   We provide a comparison between several possible implementations of the frequency grids.
@@
   Finally, we verify our results experimentally on the measurements of a band-pass filter.
+
+\section{Input design}\label{sec:excitation:inputDesign}
+For the theoretical analysis, we consider SISO output error systems, i.e.
+\begin{align}
+y(t) &=G(s,\theta)u(t)  + e(t),
+\end{align}
+where $u(t)$ is a known input sequence, $y(t)$ the output sequence and $e(t)$ is zero mean Gaussian white noise.
+$G$ is a rational, time invariant transfer function in continuous time. 
+For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
+The transfer function is parameterized by the vector $\theta$.
+These parameters are unknown and therefore need to be estimated.
+
+The goal of input design is to find an input that under the given experimental conditions, gives as much information as possible about the system.
+This can be done by optimizing the input power spectrum such that  a scalar criterion involving the Fisher information matrix is minimized.
+
+In open loop experiments, the scaled average information matrix is given by
+\begin{align}
+\IF & = \lim_{N\rightarrow\infty}
+          \frac{1}{N}
+            \sum_{t=1}^{N}
+              {\left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)
+               \left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)^{\T}},\\
+\frac{\partial\hat{y}(t)}{\partial\theta}
+    & =\frac{\partial G(s,\theta)}{\partial \theta}u(t).
+\end{align}
+By Parseval's theorem, $\IF$ can be expressed as
+\begin{align}
+\IF &= \frac{1}{\pi}
+         \int\limits_0^\infty \mathrm{Re}
+           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
+                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
+           \right\}
+           \powerspec{u}(j\omega)
+           \dd{\omega} \text{.}
+\label{eq:excitation:IF}
+\end{align}
+The information matrix is a function of the input power spectrum $\powerspec{u}$, which is the only entity that can be used to improve the quality of the estimates.
+A common optimality criterion is D-optimality where $\det{\IF}$ is maximized \citep{Goodwin1977}.
+
+The information matrix tells us how good the individual parameter estimates are.
+However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance.
+It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}.
+This gives
+\begin{align}
+\var{\hat{G}(j\omega)} &= \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
+\label{eq:excitation:varG}
+\end{align}
+
+Typically, the input design formulation depends on the true system parameters.
+This means that the optimal input depends on the \emph{unknown} system that one wants to identify.
+Furthermore, classical input designs, such as the D-optimal, typically give signals with sparse spectra.
+This means that only a few frequencies are excited.
+A sparse spectrum is bad from a robustness point of view; there is very limited information about what happens at the unexcited frequencies.
+Therefore, a signal design to be optimal for one system may result in very bad estimates if applied to another system.
+To increase the robustness of the design, one could take a small fraction $\delta$, from the optimal power and redistribute this power over the whole frequency band of interest.
+From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the input power by $1-\delta$, gives the transfer function variance
+\begin{align}
+\var{\hat{G}(j\omega)}\frac{1}{1-\delta}.
+\end{align}
+This is a small loss while the increase in robustness can be significant if the added signal is robust. Such a robust signal is studied in the following parts of the chapter.
+
+%Such a signal is discussed in the next section.
+
+%\subsection{Using prior system information}
+%Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
+% say $\hat{\theta}_0 \in \mathbb{R}^n$ exists. A D-optimal design can then be
+% found based $\hat{\theta}_0$. The resulting determinant is
+%\begin{align}
+%  \left[\det\IF^\star\right]^{-1}
+%    &= \min_{\phi_u(\omega)}
+%             \left[\det\IF\right]^{-1}
+%\end{align}
+%
+%The optimal input can be realized as sum of $n$ sinusoids.
+%Such an input is typically not robust to the initial guess since \TODO{\ldots}.
+%As a solution to this, the optimal input is modified so that a fraction of the
+%power in the optimal design is taken away and redistributed over all frequencies.
+%This ensures that some excitation power is available also at other frequencies.
+%
+%If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
+%then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
+%\begin{align}
+%  \det\IF^\star &= \prod_{i = 1}^{n}
+%                      \lambda_i^2
+%                      \alpha(\wn[i]).
+%\end{align}
+%The optimal input spectrum is
+%\begin{align}
+%  \phi_u^\star(\omega) &= \sum_{i=1}^{n}
+%                            \lambda_i^2
+%                            \delta(\omega,\wn[i])
+%\end{align}
+%If a fraction, say $\eta$, of the power is taken from each frequency and used
+%at other frequencies, the input spectrum can be written as
+%\begin{align}
+%  \phi_u(\omega) &= (1-\eta)
+%                      \sum_{i=1}^{n}
+%                        \lambda_i^2 
+%                        \delta(\omega,\wn[i])
+%                    + \phi_u^{\robust}(\omega),\\
+%                 &= (1-\eta) \phi_u^\star    (\omega)
+%                    +        \phi_u^{\robust}(\omega).
+%\end{align}
+%The term $ \phi_u^{\robust}$ is the part that introduces robustness and
+%must be such that
+%\begin{align}
+%  \int_0^{\pi} \phi_u^{\robust}(\omega) \dd{\omega} &= n \eta.
+%\end{align}
+%The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
+%a discrete spectrum, e.g. from a multi-sine signal, or as
+%a continuous spectrum. The resulting information matrix for the robust input is hence
+%\begin{align}
+%  \IF &= (1-\eta)\IF^\star + \IF^\robust
+%\end{align}
+%The determinant is therefore
+%\begin{multline}
+%\det\left[(1-\eta)\IF^\star + \IF^\robust\right]
+%  \geq \det\left[(1-\eta)\IF^\star\right] + \det\left[\IF^\robust\right] \\
+%  =  (1-\eta)^n\det\left[\IF^\star\right] + \det\left[\IF^\robust\right]
+%  \text{.}
+%\end{multline}
+%The inequality holds since the information matrix is a positive, semi-definite
+%matrix. Hence the largest possible loss in the determinant due to the robustness
+% is given by the factor $(1-\eta)^n$.
+%\TODO{This bound is often very low, maybe better one should be found!}
+
+\section{Logarithmic power distributions}\label{sec:excitation:logarithmic}
+When no information about the system is known, it is desirable that
+the excitation signal is such that regardless of the true system characteristics,
+the resulting estimates have equally good statistical properties.
+This can be ensured by a suitable choice of the input power spectrum.
+
+ \subsection{A second order system}
+Consider the second order system
+\begin{align}
+y_t &= G(s,\theta) u_t = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
+\label{eq:excitation:2ndOrderSys}
+\end{align}
+with parameters $\theta=[\wn\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$
+and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
+Since information is local in the frequency domain, the input signal power inside $\wdB$, contributes significantly to the information matrix while input power outside $\wdB$ has a smaller contribution.
+This can be seen by considering the optimal design for a second order system.
+From \citep[Example 6.4.5]{Goodwin1977} we have that the D-optimal design for \eqref{eq:excitation:2ndOrderSys} is a single sinusoid at frequency
+\begin{align}
+\omega^\star =\frac%
+{\wn
+  \sqrt{
+    \left(1-2\damping^2\right)
+    +
+    \sqrt{\left(1-2\damping^2\right)^2+15}
+    }
+  }
+{\sqrt{5}}.
+\label{eq:excitation:optFreq}
+\end{align}
+For lightly-damped systems, i.e $\damping \ll 1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
+From \eqref{eq:excitation:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
+Input design can be based on a guess of $\wn$, however if this guess is wrong, the resulting estimates may be unacceptable~\citep{Rojas2007}.
+
+When no information about the system is available, we propose using an input power spectrum with a logarithmic power distribution.
+This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2012}.
+We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/\Tm$ and $\Tm$ is the measurement time.
+Hence, a finite measurement time limits the frequency resolution and therefore we have to put a lower limit on the frequency band of interest.
+Moreover, we can only impose the logarithmic distribution sufficiently well if $\kMin$ is large enough.
+
+First, we look at the bandlimited $1/f$ power spectrum given by
+\begin{align*}
+\label{eq:excitation:pink}
+\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
+                        0           &\text{otherwise}.
+            \end{cases}
+\end{align*}
+With this input spectrum, the power inside $\wdB$ is
+\begin{align}
+  \frac{1}{2\pi}
+    \int\limits_{(1-\damping)\wn}^{(1+\damping)\wn}
+     \frac{1}{\omega} \dd{\omega}
+  = \frac{1}{2\pi}
+    \ln{\frac{1+\damping}{1-\damping}},
+\end{align}
+which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \cite{Rojas2007}
+
+Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
+\begin{align}
+  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
+\end{align}
+where $\omega_{k}/\omega_{k+1} \approx \alpha$.
+Hence, the number of spectral lines inside \wdB is 
+\begin{align}
+  \floor{
+    \log_{\alpha} \frac{1+\damping}{1-\damping} 
+  }
+  \text{,}
+\end{align}
+where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
+
+More generally, a multisine can be defined as:
+\begin{equation}
+ u \left[ n\right] = \frac{1}{\sqrt{F}}
+   \sum_{k=1}^{F} 
+     A_k 
+     \sin 
+       \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
+  \label{eq:excitation:MS}
+\end{equation}
+where $A_k$ and $\psi_k$ are its amplitude and phase spectrum; $f_s$ is the
+sampling frequency and $f_0 = \frac{f_s}{N}$ the base frequency with $N$ the 
+number of points in a period.
+
+To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha$.
+
+The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
+This is illustrated in \secref{sec:excitation:simulation}.
+
+\subsection{Sums of second order systems}
+This section extends the previous section to more general systems than second order.
+Consider a system
+\begin{align}
+G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
+             =\sum_{i=1}^{K}  \frac{1}
+                                   {   \frac{s^2}{\wn[i]^2}
+                                    + 2\frac{\damping_i}{\wn[i]}s
+                                    + 1},\\
+\theta_i&=[\wn[i]\;\damping_i]^{\T}.
+\label{eq:excitation:sumSys}
+\end{align}
+The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
+Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
+To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
+
+The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
+\begin{align}
+\IF &= \frac{1}{\pi}
+\begin{bmatrix}
+  \partial G_{1,1}        &\partial G_{1,2}       &\deemph{\cdots}         &\partial G_{1,K}\\
+  \partial G_{2,1}        &\partial G_{2,2}       &\deemph{\cdots}         &\partial G_{2,K}\\
+  \deemph{\vdots}                  &\deemph{\vdots}                 &\deemph{\ddots}         &\deemph{\vdots}          \\
+  \partial G_{K,1}        &\partial G_{K,2}       &\deemph{\cdots}         &\partial G_{K,K}
+\end{bmatrix},\\
+\partial G_{i,j} &= \int_0^\infty
+                      \mathrm{Re}\left\{
+                          \frac{\partial G_i}
+                               {\partial \theta_i}
+                          \frac{\partial G_j^{\HT}}
+                               {\partial \theta_j}
+                                \right\}
+                      \phi_u(\omega)\dd\omega.
+\end{align}
+
+Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
+The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
+To illustrate this we look at a system with $K=2$, i.e. the sum of two second order systems.
+The conclusions from the example are easily extended to systems consisting of more than two sub-systems.
+
+\subsubsection{Example: Sum of two second order systems}
+Consider the system
+\begin{align}
+G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
+%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping_1}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping_2}{\wn[2]}s + 1},
+\end{align}
+with $\theta_1=[\wn[1]\;\damping_1]^{\T}$ and $\theta_2=[\wn[2]\;\damping_2]^{\T}$.
+The information matrix for this system is
+\begin{align}
+\IF &=
+       \begin{bmatrix}
+         \partial G_{1,1}  & \partial G_{1,2}\\
+         \partial G_{2,1}  & \partial G_{2,2}
+       \end{bmatrix}.
+\label{eq:excitation:infoEx}
+\end{align}
+To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
+
+Direct calculations for $\damping < 1$ give
+\begin{align}
+\label{eq:excitation:auto}
+\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
+\end{align}
+For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
+% \begin{align}
+% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:excitation:cross1} \\
+% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
+% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:excitation:cross}
+% \end{align}
+\begin{gather}
+\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
+\qquad \qquad \qquad \qquad \qquad
+\label{eq:excitation:cross1} \\
+\leq
+\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
+\leq \\
+\qquad \qquad \qquad \qquad \qquad
+\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
+\end{gather}
+To proceed, consider
+\begin{align}
+\frac{\partial G_1}{\partial \wn[1]} 
+  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
+  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
+\end{align}
+which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
+Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
+There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:dG}.
+
+A crude, albeit useful, bound on the integrand in \eqref{eq:excitation:cross} is
+\begin{align}
+&f\left(\omega,\theta_1,\theta_2\right)=
+  \begin{cases}
+   \frac{\omega^2}{\wn[1]^2}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\omega \leq \wn[1]$,}\\
+   \phantom{\frac{\omega^2}{\omega^2}}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\wn[1] < \omega < \wn[2]$,}\\
+   \frac{\wn[2]^2}{\omega^2}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\omega \geq \wn[2]$,}
+  \end{cases}
+\end{align}
+where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
+Again, direct calculations give
+\begin{align}
+\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
+\end{align}
+Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
+\begin{itemize}
+\item the integral \eqref{eq:excitation:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
+\item lower damping further decreases the integral \eqref{eq:excitation:cross1} in comparison to \eqref{eq:excitation:auto}.
+\end{itemize}
+
+\begin{figure}
+\centering
+\setlength\figurewidth{0.68\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/rolloff.tikz}
+\caption{The shape of $\frac{\partial G_1}{\partial \wn[1]}$. The roll-off around the peak is significant and depends on the damping of the system.}
+\label{fig:excitation:dG}
+\end{figure}
+
+To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
+If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
+The resulting information matrix is then normalized so that the largest element is $1$.
+
+In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
+It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling.
+The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1.
+In this example, the $\damping$ is set to be the same in both sub-systems.
+Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
+
+Based on the above arguments, we approximate the information matrix for lightly-damped systems as a block-diagonal matrix:
+\begin{align}
+\IF&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
+                        \deemph{0}&\partial G_{2,2}\end{bmatrix}.
+\end{align}
+Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
+\begin{align}
+\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
+                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
+&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
+\end{align}
+
+This results extends mutatis mutandis to systems consisting of more sub-systems.
+
+\begin{figure}
+\centering
+\setlength\figurewidth{0.68\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/coupling.tikz}
+\caption{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
+         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
+         The arrow indicates the direction of increasing separation.}
+\label{fig:excitation:coupling}
+\end{figure}
 
@@
 
-  In this paper, we select a single frequency of interest $\omega_{\interest}$
+  In this chapter, we select a single frequency of interest $\omega_{\interest}$
   to obtain a scalar performance measure.
@@
   \paragraph{Simplification}
-  Instead of studying the response of all possible second-order sub-systems for every possible logarithmically spaced multisine-- a five-dimensional problem with parameters $\omega_0, \alpha, \wn, \damping, \dc$-- we argue in favor for a simplification of the problem by considering infinite frequency grids.
+  Instead of studying the response of all possible second-order sub-systems for every possible logarithmically spaced multisine-- a five-dimensional problem with parameters $(\omega_0, \alpha, \wn, \damping, \dc)$-- we argue in favor for a simplification of the problem by considering frequency grids with an infinite span.
 
@@
   \section{Justification for considering only poles}
+
+\TODO{explain the section}
+Remember that the rational transfer function of any \gls{LTI} system $G$ can be decomposed in its partial fraction form:
+\begin{equation}
+  G(s) = \sum_i \frac{K_i (s+\wz[i])}{} +  
+\end{equation}
+
+Consider the second-order subsystem
+\begin{equation}
+  G_2(s, \theta) = \frac{K \wn^2 \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)}
+\end{equation}
+parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
+To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
+\begin{align}
+  \PartialDerivative{G_2}{K} 
+    &= 
+  \frac{\wn^2}{\wz}
+  \frac{s + \wz}{s^2 + 2 \damping \wn s + \wn^2 }
+  \\
+  \PartialDerivative{G_2}{\wz} 
+    &= 
+    \frac{-K \wn^2}
+              {\wz} 
+    \frac{s}
+              {s^2 + 2 \damping \wn s + \wn^2} 
+  \\
+  \PartialDerivative{G_2}{\wn} 
+  &= 
+  \frac{2 K \wn}
+            {\wz} 
+  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
+            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^2}
+  \\
+  \PartialDerivative{G_2}{\damping}
+  &= 
+  \frac{-2 K \wn^3}
+            {\wz}
+  \frac{s \left( s + \wz \right)}
+             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^2}
+  \text{.}
+\end{align}
+
+The poles of these derivatives coincide with the system poles (possibly with doubled multiplicity).
+Conequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$.
+
   \TODO{benadering van 1/2 systeem a.d.h.v.
@@
 Informatiematrix is langs twee kanten gewogen met die afgeleide, dus die nul maakt weinig uit.}
+
+\begin{figure}
+  \centering
+  \remakeNextFigure
+  \setlength\figurewidth{0.9\columnwidth}
+  \setlength\figureheight{\figurewidth}
+  \input{\thisDir/figs/derivs.tikz}
+  \caption{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$.
+It can be seen that the derivatives are dominated by the resonance peak.
+This means that for a good input signal, it is critical to have power near the resonance peak.
+\TODO{indicate slopes?}}
+\end{figure}
+
 \end{subappendices}

### 2016-02-20 ch02-qlogms/sysid.tex
Clean up figures from CH02
Clean up chapter 2: show derivatives of G

@@
 \section{Introduction}\label{sec:excitation:sysid2012:intro}
-Input design deals with the task of choosing an excitation signal in a way so that the information obtained from the experiment is maximized.
-This is a problem which has a long history in statistics.
-In system identification, the focus has mostly been on input design for dynamic systems.
-A common approach is to design the input spectrum and thereby maximizing the information matrix of the estimates, see e.g.
-\cite{Fedorov1972,Goodwin1977}.
-
-A complicating issue in identification of dynamic system is the fact that the information matrix often depends on the true parameter values.
-Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design.
-There are two main solutions to this discussed in the engineering literature:
-\begin{enumerate}
-\item Iterative input design where the design updated as more information about the system is available, see e.g. \cite{Hjalmarsson2005,Gevers2005}.
-\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007} and references therein. 
-\end{enumerate}
-
-In this paper we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified.
-We will consider input design when it is known that the system has resonances, possibly spanning a large frequency band.
-It is however not necessary to know how many resonances are in the system.
-The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.
-
-% The following parts of the paper are structured as follows.
-\secref{sec:excitation:inputDesign} briefly presents the necessary input design theory.
-\secref{sec:excitation:logarithmic} deals with the situation when limit information is available.
-Finally, conclusions are drawn in \secref{sec:excitation:conclusions}.
-
-\section{Input design}\label{sec:excitation:inputDesign}
-For the theoretical analysis, we consider SISO output error systems, i.e.
-\begin{align}
-y_t &=G(s,\theta)u_t  + e_t,
-\end{align}
-where $\{u_t\}$ is a known input sequence, $\{y_t\}$ the output sequence and
-$\{e_t\}$ is zero mean Gaussian white noise.
-$G$ is a rational, time invariant transfer function in continuous time.
-For notational simplicity, $s$ is used both as a complex variable and the differentiation operator, it should be clear from the context which is used.
-The transfer function is parameterized by the vector $\theta$.
-These parameters are unknown and therefore need to be estimated.
-
-The goal of input design is to find an input that under the given experimental conditions, gives as much information as possible about the system.
-This can be done by considering the Fisher information matrix and optimizing the input power spectrum.
-
-In open loop experiments, the scaled average information matrix is given by
-\begin{align}
-\IF & = \lim_{N\rightarrow\infty}
-          \frac{1}{N}
-            \sum_{t=1}^{N}
-              {\left(\frac{\partial\hat{y}_t}{\partial\theta}\right)
-               \left(\frac{\partial\hat{y}_t}{\partial\theta}\right)^{\T}},\\
-\frac{\partial\hat{y}_t}{\partial\theta}
-    & =\frac{\partial G(s,\theta)}{\partial \theta}u_t.
-\end{align}
-By Parseval's theorem, \IF can be expressed as
-\begin{align}
-\IF &= \frac{1}{\pi}
-         \int\limits_0^\infty \mathrm{Re}
-           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
-                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
-           \right\}
-           \phi_u(j\omega)
-           \dd{\omega} \text{.}
-\label{eq:excitation:IF}
-\end{align}
-The information matrix is a function of the input power spectrum, which is the only entity that can be used to improve the quality of the estimates.
-A common optimality criterion is D-optimality where $\det{\IF}$ is maximized \citep{Goodwin1977}.
-
-The information matrix tells us how good the individual parameter estimates are.
-However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance.
-It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}.
-This gives
-\begin{align}
-\var{\hat{G}(j\omega)} &= \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
-\label{eq:excitation:varG}
-\end{align}
-
-Typically, the input design formulation depends on the true system parameters.
-This means that the optimal input depends on the \emph{unknown} system that one wants to identify.
-Furthermore, classical input designs, such as the D-optimal, typically give signals with sparse spectra.
-This means that only a few frequencies are excited.
-A sparse spectrum is bad from a robustness point of view; there is very limited information about what happens at the unexcited frequencies.
-Therefore, a signal design to be optimal for one system may result in very bad estimates if applied to another system.
-To increase the robustness of the design, one could take a fraction, say $\alpha$, from the optimal power and redistribute over the whole frequency band of interest.
-From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the input power by $1-\alpha$, gives the transfer function variance
-\begin{align}
-\var{\hat{G}(j\omega)}\frac{1}{1-\alpha}.
-\end{align}
-This is a small loss while the increase in robustness can be significant if the added signal is robust. Such a robust signal is studied in the following parts of the paper.
-
-%Such a signal is discussed in the next section.
-
-%\subsection{Using prior system information}
-%Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
-% say $\hat{\theta}_0 \in \mathbb{R}^n$ exists. A D-optimal design can then be
-% found based $\hat{\theta}_0$. The resulting determinant is
-%\begin{align}
-%  \left[\det\IF^\star\right]^{-1}
-%    &= \min_{\phi_u(\omega)}
-%             \left[\det\IF\right]^{-1}
-%\end{align}
-%
-%The optimal input can be realized as sum of $n$ sinusoids.
-%Such an input is typically not robust to the initial guess since \TODO{\ldots}.
-%As a solution to this, the optimal input is modified so that a fraction of the
-%power in the optimal design is taken away and redistributed over all frequencies.
-%This ensures that some excitation power is available also at other frequencies.
-%
-%If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
-%then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
-%\begin{align}
-%  \det\IF^\star &= \prod_{i = 1}^{n}
-%                      \lambda_i^2
-%                      \alpha(\wn[i]).
-%\end{align}
-%The optimal input spectrum is
-%\begin{align}
-%  \phi_u^\star(\omega) &= \sum_{i=1}^{n}
-%                            \lambda_i^2
-%                            \delta(\omega,\wn[i])
-%\end{align}
-%If a fraction, say $\eta$, of the power is taken from each frequency and used
-%at other frequencies, the input spectrum can be written as
-%\begin{align}
-%  \phi_u(\omega) &= (1-\eta)
-%                      \sum_{i=1}^{n}
-%                        \lambda_i^2 
-%                        \delta(\omega,\wn[i])
-%                    + \phi_u^{\robust}(\omega),\\
-%                 &= (1-\eta) \phi_u^\star    (\omega)
-%                    +        \phi_u^{\robust}(\omega).
-%\end{align}
-%The term $ \phi_u^{\robust}$ is the part that introduces robustness and
-%must be such that
-%\begin{align}
-%  \int_0^{\pi} \phi_u^{\robust}(\omega) \dd{\omega} &= n \eta.
-%\end{align}
-%The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
-%a discrete spectrum, e.g. from a multi-sine signal, or as
-%a continuous spectrum. The resulting information matrix for the robust input is hence
-%\begin{align}
-%  \IF &= (1-\eta)\IF^\star + \IF^\robust
-%\end{align}
-%The determinant is therefore
-%\begin{multline}
-%\det\left[(1-\eta)\IF^\star + \IF^\robust\right]
-%  \geq \det\left[(1-\eta)\IF^\star\right] + \det\left[\IF^\robust\right] \\
-%  =  (1-\eta)^n\det\left[\IF^\star\right] + \det\left[\IF^\robust\right]
-%  \text{.}
-%\end{multline}
-%The inequality holds since the information matrix is a positive, semi-definite
-%matrix. Hence the largest possible loss in the determinant due to the robustness
-% is given by the factor $(1-\eta)^n$.
-%\TODO{This bound is often very low, maybe better one should be found!}
-
-\section{Logarithmic power distributions}\label{sec:excitation:logarithmic}
-When no information about the system is known, it is desirable that
-the excitation signal is such that regardless of the true system characteristics,
-the resulting estimates have equally good statistical properties.
-This can be ensured by a suitable choice of the input power spectrum.
-
- \subsection{A second order system}
-Consider the second order system
-\begin{align}
-y_t &= G(s,\theta) u_t = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
-\label{eq:excitation:2ndOrderSys}
-\end{align}
-with parameters $\theta=[\wn\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$
-and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
-Since information is local in the frequency domain, the input signal power inside $\wdB$, contributes significantly to the information matrix while input power outside $\wdB$ has a smaller contribution.
-This can be seen by considering the optimal design for a second order system.
-From \citep[Example 6.4.5]{Goodwin1977} we have that the D-optimal design for \eqref{eq:excitation:2ndOrderSys} is a single sinusoid at frequency
-\begin{align}
-\omega^\star =\frac%
-{\wn
-  \sqrt{
-    \left(1-2\damping^2\right)
-    +
-    \sqrt{\left(1-2\damping^2\right)^2+15}
-    }
-  }
-{\sqrt{5}}.
-\label{eq:excitation:optFreq}
-\end{align}
-For lightly-damped systems, i.e $\damping \ll 1$ , $\omega^\star\approx \wn$, which is inside the bandwidth of the system. 
-From \eqref{eq:excitation:optFreq} it is clear that the optimal design depends on the resonance of the system to be identified. 
-Input design can be based on a guess of $\wn$, however if this guess is wrong, the resulting estimates may be unacceptable~\citep{Rojas2007}.
-
-When no information about the system is available, we propose using an input power spectrum with a logarithmic power distribution.
-This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2012}.
-We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/\Tm$ and $\Tm$ is the measurement time.
-Hence, a finite measurement time limits the frequency resolution and therefore we have to put a lower limit on the frequency band of interest.
-Moreover, we can only impose the logarithmic distribution sufficiently well if $\kMin$ is large enough.
-
-First, we look at the bandlimited $1/f$ power spectrum given by
-\begin{align*}
-\label{eq:excitation:pink}
-\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
-                        0           &\text{otherwise}.
-            \end{cases}
-\end{align*}
-With this input spectrum, the power inside $\wdB$ is
-\begin{align}
-  \frac{1}{2\pi}
-    \int\limits_{(1-\damping)\wn}^{(1+\damping)\wn}
-     \frac{1}{\omega} \dd{\omega}
-  = \frac{1}{2\pi}
-    \ln{\frac{1+\damping}{1-\damping}},
-\end{align}
-which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \cite{Rojas2007}
-
-Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
-\begin{align}
-  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
-\end{align}
-where $\omega_{k}/\omega_{k+1} \approx \alpha$.
-Hence, the number of spectral lines inside \wdB is 
-\begin{align}
-  \floor{
-    \log_{\alpha} \frac{1+\damping}{1-\damping} 
-  }
-  \text{,}
-\end{align}
-where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
-
-More generally, a multisine can be defined as:
-\begin{equation}
- u \left[ n\right] = \frac{1}{\sqrt{F}}
-   \sum_{k=1}^{F} 
-     A_k 
-     \sin 
-       \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
-  \label{eq:excitation:MS}
-\end{equation}
-where $A_k$ and $\psi_k$ are its amplitude and phase spectrum; $f_s$ is the
-sampling frequency and $f_0 = \frac{f_s}{N}$ the base frequency with $N$ the 
-number of points in a period.
-
-To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha$.
-
-The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
-This is illustrated in \secref{sec:excitation:simulation}.
-
-\subsection{Sums of second order systems}
-This section extends the previous section to more general systems than second order.
-Consider a system
-\begin{align}
-G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
-             =\sum_{i=1}^{K}  \frac{1}
-                                   {   \frac{s^2}{\wn[i]^2}
-                                    + 2\frac{\damping_i}{\wn[i]}s
-                                    + 1},\\
-\theta_i&=[\wn[i]\;\damping_i]^{\T}.
-\label{eq:excitation:sumSys}
-\end{align}
-The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
-Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
-To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
-
-The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
-\begin{align}
-\IF &= \frac{1}{\pi}
-\begin{bmatrix}
-  \partial G_{1,1}        &\partial G_{1,2}       &\cdots         &\partial G_{1,K}\\
-  \partial G_{2,1}        &\partial G_{2,2}       &\cdots         &\partial G_{2,K}\\
-  \vdots                  &\vdots                 &\ddots         &\vdots          \\
-  \partial G_{K,1}        &\partial G_{K,2}       &\cdots         &\partial G_{K,K}
-\end{bmatrix},\\
-\partial G_{i,j} &= \int_0^\infty
-                      \mathrm{Re}\left\{
-                          \frac{\partial G_i}
-                               {\partial \theta_i}
-                          \frac{\partial G_j^{\HT}}
-                               {\partial \theta_j}
-                                \right\}
-                      \phi_u(\omega)\dd\omega.
-\end{align}
-
-Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
-The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
-To illustrate this we look at a system with $K=2$, i.e. the sum of two second order systems.
-The conclusions from the example are easily extended to systems consisting of more than two sub-systems.
-
-\subsubsection{Example: Sum of two second order systems}
-Consider the system
-\begin{align}
-G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
-%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping_1}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping_2}{\wn[2]}s + 1},
-\end{align}
-with $\theta_1=[\wn[1]\;\damping_1]^{\T}$ and $\theta_2=[\wn[2]\;\damping_2]^{\T}$.
-The information matrix for this system is
-\begin{align}
-\IF &=
-       \begin{bmatrix}
-         \partial G_{1,1}  & \partial G_{1,2}\\
-         \partial G_{2,1}  & \partial G_{2,2}
-       \end{bmatrix}.
-\label{eq:excitation:infoEx}
-\end{align}
-To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
-
-Direct calculations for $\damping < 1$ give
-\begin{align}
-\label{eq:excitation:auto}
-\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
-\end{align}
-For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
-% \begin{align}
-% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:excitation:cross1} \\
-% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
-% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:excitation:cross}
-% \end{align}
-\begin{gather}
-\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
-\qquad \qquad \qquad \qquad \qquad
-\label{eq:excitation:cross1} \\
-\leq
-\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
-\leq \\
-\qquad \qquad \qquad \qquad \qquad
-\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
-\end{gather}
-To proceed, consider
-\begin{align}
-\frac{\partial G_1}{\partial \wn[1]} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}{\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
-\end{align}
-which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
-Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}.
-There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak.
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:dG}.
-
-A crude, albeit useful, bound on the integrand in \eqref{eq:excitation:cross} is
-\begin{align}
-&f\left(\omega,\theta_1,\theta_2\right)=
-  \begin{cases}
-   \frac{\omega^2}{\wn[1]^2}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\omega \leq \wn[1]$,}\\
-   \phantom{\frac{\omega^2}{\omega^2}}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\wn[1] < \omega < \wn[2]$,}\\
-   \frac{\wn[2]^2}{\omega^2}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\omega \geq \wn[2]$,}
-  \end{cases}
-\end{align}
-where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
-Again, direct calculations give
-\begin{align}
-\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
-\end{align}
-Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
-\begin{itemize}
-\item the integral \eqref{eq:excitation:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
-\item lower damping further decreases the integral \eqref{eq:excitation:cross1} in comparison to \eqref{eq:excitation:auto}.
-\end{itemize}
-
-\begin{figure}
-\centering
-\input{\thisDir/figs/rolloff.tikz}
-\caption{The shape of $\frac{\partial G_1}{\partial \wn[1]}$. The roll-off around the peak is significant and depends on the damping of the system.}
-\label{fig:excitation:dG}
-\end{figure}
-
-To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
-If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
-The resulting information matrix is then normalized so that the largest element is $1$.
-
-In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
-It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling.
-The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1.
-In this example, the $\damping$ is set to be the same in both sub-systems.
-Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
-
-Based on the above arguments, we make the following approximation of the information matrix for systems with low damping,
-\begin{align}
-\IF&\approx \begin{bmatrix}\partial G_{1,1} &0\\
-                        0&\partial G_{2,2}\end{bmatrix}.
-\end{align}
-Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
-\begin{align}
-\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &0\\
-                        0&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
-&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
-\end{align}
-
-This results extends mutatis mutandis to systems consisting of more sub-systems.
-
-\begin{figure}
-\centering
-\input{\thisDir/figs/coupling.tikz}
-\caption{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
-         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
-         The arrow indicates the direction of increasing separation.}
-\label{fig:excitation:coupling}
-\end{figure}
 

### 2016-02-21 ch02-qlogms/excitation-design.tex
Improve derivatives figure
More work on derivatives of O(2) sys

@@
   \section{Justification for considering only poles}
-
-\TODO{explain the section}
+\TODO{move into main text}
 Remember that the rational transfer function of any \gls{LTI} system $G$ can be decomposed in its partial fraction form:
@@
 The poles of these derivatives coincide with the system poles (possibly with doubled multiplicity).
-Conequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$.
-
-  \TODO{benadering van 1/2 systeem a.d.h.v.
-0/2 systeem wanneer $\omega_z << \wn$ (of $\omega_z >> \wn)$: rond de resonantie zijn beiden ongeveer gelijk.
-Afgeleide naar de nul zijn klein rond de resonantie.
-Informatiematrix is langs twee kanten gewogen met die afgeleide, dus die nul maakt weinig uit.}
+Conequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
+The roll-off near the resonance is determined by the damping $\damping$.
+As such, the Fisher information matrix is pre-dominantly determined by the input power spectrum near $\wn$.
+Note that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ have the steepest roll-off near the resonance.
+As such, those parameters are the most important for the experiment design.
 
@@
   \centering
-  \remakeNextFigure
   \setlength\figurewidth{0.9\columnwidth}
@@
   \input{\thisDir/figs/derivs.tikz}
-  \caption{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$.
+  \caption[Derivatives of a second-order system for each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
+  % The numbers indicate the (asymptotic) slope as a multiple of $20 \unit{dB/\decade}$.
+  The roll-off near $\wn$ is significant and depends strongly on $\damping$.
   It can be seen that the derivatives are dominated by the resonance peak. 
   This means that for a good input signal, it is critical to have power near the resonance peak. 
-\TODO{indicate slopes?}}
+  Note also that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ exhibit a sharper peak and hence $\damping$ and $\wn$ are the most important parameters of the model.
+  In this example, $\damping = \varXi$, $K = \varK$, $\frac{\wz}{\wn} \in \Set{\varWzSmall, 1, \varWzBig}$ and $\wn = \varWn \unit{rad/s}$ were used.
+}
+\label{fig:excitation:derivatives}
 \end{figure}

### 2016-02-22 ch02-qlogms/excitation-design.tex
Extend derivatives to higher mult of sub-sys

@@
 \section{Logarithmic power distributions}\label{sec:excitation:logarithmic}
-When no information about the system is known, it is desirable that
-the excitation signal is such that regardless of the true system characteristics,
-the resulting estimates have equally good statistical properties.
+When no information about the system is known, it is desirable that the excitation signal is such that regardless of the true system characteristics, the resulting estimates have equally good statistical properties.
 This can be ensured by a suitable choice of the input power spectrum.
@@
 \begin{align}
-y_t &= G(s,\theta) u_t = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u_t,
+y(t) &= G(s,\theta) u(t) = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u(t),
 \label{eq:excitation:2ndOrderSys}
@@
 When no information about the system is available, we propose using an input power spectrum with a logarithmic power distribution.
-This can be achieved either with a continuous bandlimited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2012}.
+This can be achieved either with a continuous band-limited $1/f$ spectrum or a quasi-logarithmic multisine spectrum \citep{Pintelon2012}.
 We choose to work with an equidistant frequency grid with resolution $f_0$ and design the input in the frequency band $[\wn \kMin\; \wn \kMax]$, where the resolution is $k_0=1/\Tm$ and $\Tm$ is the measurement time.
@@
 
-First, we look at the bandlimited $1/f$ power spectrum given by
+First, we look at the band-limited $1/f$ power spectrum given by
 \begin{align*}
@@
                                    {   \frac{s^2}{\wn[i]^2}
-                                    + 2\frac{\damping_i}{\wn[i]}s
+                                    + 2\frac{\damping[i]}{\wn[i]}s
                                     + 1},\\
-\theta_i&=[\wn[i]\;\damping_i]^{\T}.
+\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
 \label{eq:excitation:sumSys}
@@
 G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
-%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping_1}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping_2}{\wn[2]}s + 1},
-\end{align}
-with $\theta_1=[\wn[1]\;\damping_1]^{\T}$ and $\theta_2=[\wn[2]\;\damping_2]^{\T}$.
+%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
+\end{align}
+with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
 The information matrix for this system is
@@
 \TODO{move into main text}
-Remember that the rational transfer function of any \gls{LTI} system $G$ can be decomposed in its partial fraction form:
-\begin{equation}
-  G(s) = \sum_i \frac{K_i (s+\wz[i])}{} +  
-\end{equation}
-
-Consider the second-order subsystem
-\begin{equation}
-  G_2(s, \theta) = \frac{K \wn^2 \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)}
+Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form:
+\begin{align}
+  G(s) &= 
+    \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\sum\limits_{i=0}^{\numel{A}} a_i s^i} 
+        =    
+   \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\prod\limits_{i=1}^{I_1} \left( s - \pole[i] \right)^{M_{1,i}} 
+               \prod\limits_{i=1}^{I_2} \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{M_{2,i}}}
+        \\
+        &  = 
+        \sum_{i=1}^{I_1} 
+          \sum_{\multiplicity=1}^{M_{1,i}} 
+            \frac{\dc[i]}
+                      { \left( s - \pole[i] \right)^{\multiplicity}}
+            + 
+        \sum_{i=1}^{I_2} 
+          \sum_{\multiplicity=1}^{M_{2,i}}
+           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
+                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
+        \label{eq:excitation:PFE}
+\end{align}
+where $I_1$ denotes the number of real-valued poles, $I_2$ denotes the number of complex conjugated pole pairs.
+$M_{1,i}$ and $M_{2,i}$ denotes the multiplicity of the corresponding poles, such that $\numel{A} = \sum_i^{I_1} M_{1,i} + 2 \sum_{i}^{I_2} M_{2,i}$.
+Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.
+
+Consider a second-order subsystem
+\begin{equation}
+  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
 \end{equation}
@@
     &= 
-  \frac{\wn^2}{\wz}
-  \frac{s + \wz}{s^2 + 2 \damping \wn s + \wn^2 }
+  \frac{\wn^{2\multiplicity}}{\wz}
+  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
   \\
@@
     &= 
-    \frac{-K \wn^2}
+    \frac{-K \wn^{2\multiplicity}}
               {\wz} 
     \frac{s}
-              {s^2 + 2 \damping \wn s + \wn^2} 
+              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
   \\
@@
   &= 
-  \frac{2 K \wn}
+  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
             {\wz} 
   \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
-            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^2}
+            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
   \\
@@
   &= 
-  \frac{-2 K \wn^3}
+  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
             {\wz}
   \frac{s \left( s + \wz \right)}
-             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^2}
-  \text{.}
-\end{align}
-
-The poles of these derivatives coincide with the system poles (possibly with doubled multiplicity).
-Conequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
-The roll-off near the resonance is determined by the damping $\damping$.
+             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
+  \text{.}
+\end{align}
+
+The poles of these derivatives coincide with the system poles (possibly with increased multiplicity).
+Consequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
+The roll-off near the resonance is determined mainly by the damping $\damping$ and the multiplicity $\multiplicity$ of the sub-system.
 As such, the Fisher information matrix is pre-dominantly determined by the input power spectrum near $\wn$.
@@
   \input{\thisDir/figs/derivs.tikz}
-  \caption[Derivatives of a second-order system for each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
+  \caption[Derivatives of a second-order sub-system towards each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
   % The numbers indicate the (asymptotic) slope as a multiple of $20 \unit{dB/\decade}$.
   The roll-off near $\wn$ is significant and depends strongly on $\damping$.
-  It can be seen that the derivatives are dominated by the resonance peak. 
+  It can be seen that the derivatives are dominated by the resonance peak, an effect that is even more prominent when $\multiplicity$ is large.
   This means that for a good input signal, it is critical to have power near the resonance peak. 
   Note also that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ exhibit a sharper peak and hence $\damping$ and $\wn$ are the most important parameters of the model.
-  In this example, $\damping = \varXi$, $K = \varK$, $\frac{\wz}{\wn} \in \Set{\varWzSmall, 1, \varWzBig}$ and $\wn = \varWn \unit{rad/s}$ were used.
+  In this example, $\damping = \varXi$, $K = \varK$, $\frac{\wz}{\wn} \in \Set{\varWzSmall, 1, \varWzBig}$, $\multiplicity=1$ and $\wn = \varWn \unit{rad/s}$ were used.
 }
@@
 
-\input{ch02-qlogms/sysid.tex}
+% \input{ch02-qlogms/sysid.tex}

### 2016-02-22 ch06-concl/conclusions.tex
Extend derivatives to higher mult of sub-sys

@@
   As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
-  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping_{\min}$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
+  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
   Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid should conform to
   \begin{equation}
-    \alpha \leq 1 + \damping_{\min}
+    \alpha \leq 1 + \damping[\min]
   \end{equation}
   to attain a reliable estimate of the resonances present in the system.
-  The choice to use the equality $\alpha = 1+ \damping_{\min}$ is the optimal choice within the framework presented in \chapref{sec:excitation}. 
-  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited as in many cases.
+  The choice to use the equality $\alpha = 1+ \damping[\min]$ is the optimal choice within the framework presented in \chapref{sec:excitation}. 
+  Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited.
 
@@
     \item the allowable total excitation power,
-    \item a broad frequency band of interest that could span multiple decades, and,
-    \item the minimal expected relative damping $\damping_{\min}$ in the system.
+    \item a broad frequency band of interest that could span multiple decades, and,\
+    \item the minimal expected relative damping $\damping[\min]$ in the system,
+    \item the assumption that the resonances are well-separated in the frequency domain.
   \end{itemize}
-  This last requirement is the only requirement that is often overlooked in initial excitation designs.
+
   \subsection{Non-parametric estimation}

### 2016-02-22 ch02-qlogms/code/derivativesSubsys.m

@@ -1,0 +1,32 @@
+clear all;
+close all;
+clc;
+
+syms K wz s wn xi
+syms m
+m = 5; % mupad refuses to check for equality when m is symbolic (prolly some restraint is needed)
+
+G = K*(s/wz+1)/(s^2/wn^2 + 2*xi*s/wn + 1)^m
+
+derivative = @(f, x) simplify(diff(f,x))
+
+dGdK  = derivative(G,K)
+dGdwz = derivative(G,wz)
+dGdwn = derivative(G,wn)
+dGdxi = derivative(G,xi)
+
+numer = K*wn^(2*m)/wz*(s+wz);
+D     = s^2 + 2*xi*wn*s+wn^2;
+denom = (D)^m;
+
+assert(logical(simplify(G == numer/denom)))
+
+dGdK_man  = G/K
+dGdwz_man = -K*wn^(2*m)*s/wz^2/D^m
+dGdwn_man =  2*m*K*wn^(2*m-1)/wz*(s+wz)*(s+xi*wn)*s/D^(m+1)
+dGdxi_man = -2*K*m*wn^(2*m+1)*s*(s+wz)/wz/D^(m+1)
+
+assert(logical(simplify(dGdK_man  == dGdK)) , 'dGdK is wrong')
+assert(logical(simplify(dGdwz_man == dGdwz)), 'dGdwz is wrong')
+assert(logical(simplify(dGdwn_man == dGdwn)), 'dGdwn is wrong')
+assert(logical(simplify(dGdxi_man == dGdxi)), 'dGdxi is wrong')

### 2016-02-22 ch02-qlogms/excitation-design.tex
Some comments from Tom + merge CH02

@@
 \begin{align}
-\var{\hat{G}(j\omega)} &= \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
+\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
 \label{eq:excitation:varG}
@@
 
-Typically, the input design formulation depends on the true system parameters.
-This means that the optimal input depends on the \emph{unknown} system that one wants to identify.
-Furthermore, classical input designs, such as the D-optimal, typically give signals with sparse spectra.
+Typically, the input design formulation depends on the true system parameters. This means that the optimal input depends on the \emph{unknown} system that one wants to identify. 
+Furthermore, classical input designs, such as the D-optimal design, typically give signals with sparse spectra. 
 This means that only a few frequencies are excited. 
@@
 
-%\subsection{Using prior system information}
-%Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
+% \TODO{begin}
+% \newcommand{\robust}{\mathrm{robust}\}
+% \subsection{Using prior system information}
+% Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
 % say $\hat{\theta}_0 \in \mathbb{R}^n$ exists. A D-optimal design can then be
 % found based $\hat{\theta}_0$. The resulting determinant is
-%\begin{align}
+% \begin{align}
 %  \left[\det\IF^\star\right]^{-1}
@@
 %             \left[\det\IF\right]^{-1}
-%\end{align}
-%
-%The optimal input can be realized as sum of $n$ sinusoids.
-%Such an input is typically not robust to the initial guess since \TODO{\ldots}.
-%As a solution to this, the optimal input is modified so that a fraction of the
-%power in the optimal design is taken away and redistributed over all frequencies.
-%This ensures that some excitation power is available also at other frequencies.
-%
-%If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
-%then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
-%\begin{align}
+% \end{align}
+
+% The optimal input can be realized as sum of $n$ sinusoids.
+% Such an input is typically not robust to the initial guess since \TODO{\ldots}.
+% As a solution to this, the optimal input is modified so that a fraction of the
+% power in the optimal design is taken away and redistributed over all frequencies.
+% This ensures that some excitation power is available also at other frequencies.
+
+% If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
+% then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
+% \begin{align}
 %  \det\IF^\star &= \prod_{i = 1}^{n}
@@
 %                      \alpha(\wn[i]).
-%\end{align}
-%The optimal input spectrum is
-%\begin{align}
+% \end{align}
+% The optimal input spectrum is
+% \begin{align}
 %  \phi_u^\star(\omega) &= \sum_{i=1}^{n}
@@
 %                            \delta(\omega,\wn[i])
-%\end{align}
-%If a fraction, say $\eta$, of the power is taken from each frequency and used
-%at other frequencies, the input spectrum can be written as
-%\begin{align}
+% \end{align}
+% If a fraction, say $\eta$, of the power is taken from each frequency and used
+% at other frequencies, the input spectrum can be written as
+% \begin{align}
 %  \phi_u(\omega) &= (1-\eta)
@@
 %                    +        \phi_u^{\robust}(\omega).
-%\end{align}
-%The term $ \phi_u^{\robust}$ is the part that introduces robustness and
-%must be such that
-%\begin{align}
+% \end{align}
+% The term $ \phi_u^{\robust}$ is the part that introduces robustness and
+% must be such that
+% \begin{align}
 %  \int_0^{\pi} \phi_u^{\robust}(\omega) \dd{\omega} &= n \eta.
-%\end{align}
-%The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
-%a discrete spectrum, e.g. from a multi-sine signal, or as
-%a continuous spectrum. The resulting information matrix for the robust input is hence
-%\begin{align}
+% \end{align}
+% The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
+% a discrete spectrum, e.g. from a multi-sine signal, or as
+% a continuous spectrum. The resulting information matrix for the robust input is hence
+% \begin{align}
 %  \IF &= (1-\eta)\IF^\star + \IF^\robust
-%\end{align}
-%The determinant is therefore
-%\begin{multline}
-%\det\left[(1-\eta)\IF^\star + \IF^\robust\right]
+% \end{align}
+% The determinant is therefore
+% \begin{multline}
+% \det\left[(1-\eta)\IF^\star + \IF^\robust\right]
 %  \geq \det\left[(1-\eta)\IF^\star\right] + \det\left[\IF^\robust\right] \\
@@
 %  \text{.}
-%\end{multline}
-%The inequality holds since the information matrix is a positive, semi-definite
-%matrix. Hence the largest possible loss in the determinant due to the robustness
+% \end{multline}
+% The inequality holds since the information matrix is a positive, semi-definite
+% matrix. Hence the largest possible loss in the determinant due to the robustness
 % is given by the factor $(1-\eta)^n$.
-%\TODO{This bound is often very low, maybe better one should be found!}
+% \TODO{This bound is often very low, maybe better one should be found!}
+% \TODO{end}
 
@@
 \begin{align}
-  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
-\end{align}
-where $\omega_{k}/\omega_{k+1} \approx \alpha$.
+  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\dirac{\omega - \omega_k}},
+\end{align}
+where $\omega_{k}/\omega_{k+1} \approx \alpha$ and $\dirac{\omega}$ denotes the Dirac distribution.
 Hence, the number of spectral lines inside \wdB is 
@@
 This is illustrated in \secref{sec:excitation:simulation}.
+
+\subsection{Generic system}
+%TODO: explain generic LTI system
+Consider a second-order subsystem
+\begin{equation}
+  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
+\end{equation}
+parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
+To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
+\begin{align}
+  \PartialDerivative{G_2}{K} 
+    &= 
+  \frac{\wn^{2\multiplicity}}{\wz}
+  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
+  \\
+  \PartialDerivative{G_2}{\wz} 
+    &= 
+    \frac{-K \wn^{2\multiplicity}}
+              {\wz} 
+    \frac{s}
+              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
+  \\
+  \PartialDerivative{G_2}{\wn} 
+  &= 
+  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
+            {\wz} 
+  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
+            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
+  \\
+  \PartialDerivative{G_2}{\damping}
+  &= 
+  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
+            {\wz}
+  \frac{s \left( s + \wz \right)}
+             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
+  \text{.}
+\end{align}
+
+The poles of these derivatives coincide with the system poles (possibly with increased multiplicity).
+Consequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
+The roll-off near the resonance is determined mainly by the damping $\damping$ and the multiplicity $\multiplicity$ of the sub-system.
+As such, the Fisher information matrix is pre-dominantly determined by the input power spectrum near $\wn$.
+Note that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ have the steepest roll-off near the resonance.
+As such, those parameters are the most important for the experiment design.
+
+\begin{figure}
+  \centering
+  \setlength\figurewidth{0.9\columnwidth}
+  \setlength\figureheight{\figurewidth}
+  \input{\thisDir/figs/derivs.tikz}
+  \caption[Derivatives of a second-order sub-system towards each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
+  % The numbers indicate the (asymptotic) slope as a multiple of $20 \unit{dB/\decade}$.
+  The roll-off near $\wn$ is significant and depends strongly on $\damping$.
+  It can be seen that the derivatives are dominated by the resonance peak, an effect that is even more prominent when $\multiplicity$ is large.
+  This means that for a good input signal, it is critical to have power near the resonance peak. 
+  Note also that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ exhibit a sharper peak and hence $\damping$ and $\wn$ are the most important parameters of the model.
+  In this example, $\damping = \varXi$, $K = \varK$, $\frac{\wz}{\wn} \in \Set{\varWzSmall, 1, \varWzBig}$, $\multiplicity=1$ and $\wn = \varWn \unit{rad/s}$ were used.
+}
+\label{fig:excitation:derivatives}
+\end{figure}
 
@@
 There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:dG}.
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.
 
@@
 
-\begin{figure}
-\centering
-\setlength\figurewidth{0.68\columnwidth}
-\setlength\figureheight{0.68\figurewidth}
-\input{\thisDir/figs/rolloff.tikz}
-\caption{The shape of $\frac{\partial G_1}{\partial \wn[1]}$. The roll-off around the peak is significant and depends on the damping of the system.}
-\label{fig:excitation:dG}
-\end{figure}
-
 To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
@@
 In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
-It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling.
-The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1.
+It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling.
+The diagonal blocks of the normalized $\IF$ in all cases have some elements close to $1$. 
 In this example, the $\damping$ is set to be the same in both sub-systems. 
@@
 
-  The model is parametrized in the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
+  The model is parametrized by the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
   For a continuous time model $\Omega = s$, while for the discrete time case $\Omega = z$.
 
-  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
-  \TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
-\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter.
-This will be well-approximated by considering only the second order system of the paper.}
-
+  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion:
+  \TODO{move into main text}
+Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form:
+\begin{align}
+  G(s) &= 
+    \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\sum\limits_{i=0}^{\numel{A}} a_i s^i} 
+        =    
+   \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\prod\limits_{i=1}^{I_1} \left( s - \pole[i] \right)^{M_{1,i}} 
+               \prod\limits_{i=1}^{I_2} \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{M_{2,i}}}
+        \\
+        &  = 
+        \sum_{i=1}^{I_1} 
+          \sum_{\multiplicity=1}^{M_{1,i}} 
+            \frac{\dc[i]}
+                      { \left( s - \pole[i] \right)^{\multiplicity}}
+            + 
+        \sum_{i=1}^{I_2} 
+          \sum_{\multiplicity=1}^{M_{2,i}}
+           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
+                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
+        \label{eq:excitation:PFE}
+\end{align}
+where $I_1$ denotes the number of real-valued poles, $I_2$ denotes the number of complex conjugated pole pairs.
+$M_{1,i}$ and $M_{2,i}$ denotes the multiplicity of the corresponding poles, such that $\numel{A} = \sum_i^{I_1} M_{1,i} + 2 \sum_{i}^{I_2} M_{2,i}$.
+Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.  
   Within these sub-systems, we can distinguish first-order subsystems and second-order subsystems, the latter of which describe resonant phenomena.
   Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
-  Afterwards, it will become obvious that
 
@@
 
-  This last example illustrates that a least common multiple of real numbers does not always exist.
+  This last example illustrates that a least common multiple of real numbers is not guaranteed to exist.
   Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
@@
     \end{equation}
-  where $\floor{\bullet}$ denotes rounding towards zero.
+  where $\floor{\bullet}$ denotes rounding towards the nearest smaller integer value.
   In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.
 
-  \begin{property}
+  \begin{property}\label{prop:excitation:log:relBW}
    Each frequency band $B = \ClosedInterval{f, \kappa f}$ with $\kappa \in \PositiveRealNumbers \without \set{0,1}$ that is completely within the range of the excited logarithmic grid of frequencies $\set{f_1, \ldots, f_F}$ contains a constant number of frequency lines
@@
     For the frequency decade band $\decade(f) \isdef \ClosedInterval{f, 10 f}$, a logarithmic frequency grid contains $F_{\decade} = \floor{\log_{\alpha} 10}$ excited lines.
+    Note that this is independent of the frequency $f$.
   \end{example}
@@
     In different contexts, e.g.
-electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} or the \code{logspace} function in \MATLAB it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$).
+electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} and programming languages, it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$) instead of the grid ratio $\alpha$.
     Obviously, such alternative specifications are equivalent.
@@
   \end{example}
-
-   Obviously, the same argument can be held for any set of frequency bands with constant relative bandwidth (e.g. octave $\kappa = 2$).
-   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
-
-  To return to the FRF, in Section~\ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
+  \begin{example}
+    The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
+    As such, the effective frequency ratio $\alpha = \sqrt[F]{\frac{f_{\max}}{f_{\min}}}$ in this vector.
+  \end{example}
+
+   From \propref{prop:excitation:log:relBW}, it can be seen that for any set of frequency bands with a constant relative bandwidth (e.g.
+decades~($\kappa=10$), octaves~($\kappa=2$),\ldots ), a logarithmic  frequency grid contains a constant number of lines per frequency band.
+   Consequently, the power in each relative bandwidth is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+
+  To return to the \gls{FRF}, in \secref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
   As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
-  bandwidth, one expects an equal variance for each system, as will be shown in Section~\ref{sec:bestFrequencyResolution}.
-
-  For that reason, a log multisine is a good candidate for our purposes.
+  bandwidth, one expects an equal variance for each system, as will be shown in \secref{sec:bestFrequencyResolution}.
+
+  For that reason, a logarithmic multisine is a good candidate for our purposes.
   However, it is more involved both to generate and to analyze such a signal, as the excited frequencies don't lie on a commensurate frequency grid.
@@
   \end{definition}
-  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer according to the \IEEEfloat standards and as implemented in the \MATLAB function \code{round}.
+  In the equation above, $\round{\placeholder}$ denotes rounding towards the nearest integer according to the \IEEEfloat standards and as implemented in the \MATLAB function \mcode{round}.
   This satisfies the approximate definition.
@@
   The use of different rounding strategies --- e.g.
-the \code{ceil} function $\ceil{}$  and \code{floor} function $\floor{}$ --- in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
+the \mcode{ceil} function $\ceil{}$  and \mcode{floor} function $\floor{}$ --- in \eqref{eq:excitation:qlog:roundAlpha}, allows for slightly different guarantees on the effective $\alpha_k$ attained by the grid.
   By denoting $\alpha_k^{\placeholder}$ as the effective frequency ratio for a rounding strategy $\placeholder$  in that equation, one can trivially see that the following relationships hold:
@@
   \end{equation}
-  This means that rounding using the \code{floor} operator favors to strictly attain the specified frequency bin density at the cost of a few more excited lines (and hence less allottable power per line).
-  The \code{ceil} function produces a grid that has more power per line at the cost of a reduced bin density.
-  On the other hand, using \code{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
+  This means that rounding using the \mcode{floor} operator favors to strictly attain the specified frequency bin density at the cost of a few more excited lines (and hence less allottable power per line).
+  The \mcode{ceil} function produces a grid that has more power per line at the cost of a reduced bin density.
+  On the other hand, using \mcode{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
   \end{remark}
@@
   The power density of the quasi-log multisine at the low frequencies is reduced in comparison to that of the logarithmic grid multisine.
-  This is due to the limited available frequency resolution.
-  To compensate for this loss in power spectral density (PSD), we can increase the amplitude spectrum $A_k$ at these lines.
+  This is due to the limited available frequency resolution if one sticks to the \gls{DFT} frequency grid.
+  To compensate for this loss in \gls{PSD}, we can increase the amplitude spectrum $A_k$ at these lines.
   Note that we are not able to restore the frequency resolution, only the power in a certain band is made equal to the power in the logarithmic multisine in the same band.
@@
 \TODO{zin loopt niet goed}
-  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
+  As in \citep{Pintelon2012, Gallager2008, matrixcookbook}, the covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown to be approximately equal to
   \begin{align}
@@
 
-  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test can be considered within the `bulk' of the frequency grid with finite support.
-  \TODO{more rigorous explanation why this is the case}
+  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies within the `bulk' of the frequency grid with finite support.
+  This can be understood intuitively by inspecting the derivatives that constitute the Fisher information matrix (see \figref{fig:excitation:derivatives}): those derivatives are significantly larger near the resonance frequency than at other frequencies.
+
   I.e. there should be a few excited frequency lines that are logarithmically spaced, outside of the resonance peak of the actual system.
@@
   \begin{remark}
-  All simulations  have been repeated fitted with the \MATLAB System Identification Toolbox by means of the \code{oe} function~\citep{TDIDENT}.
+  All simulations  have been repeated fitted with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
   The observed results were identical and hence are not elaborated further in this text.
@@
 
-\begin{subappendices}
-  \section{Justification for considering only poles}
-\TODO{move into main text}
-Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form:
-\begin{align}
-  G(s) &= 
-    \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
-              {\sum\limits_{i=0}^{\numel{A}} a_i s^i} 
-        =    
-   \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
-              {\prod\limits_{i=1}^{I_1} \left( s - \pole[i] \right)^{M_{1,i}} 
-               \prod\limits_{i=1}^{I_2} \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{M_{2,i}}}
-        \\
-        &  = 
-        \sum_{i=1}^{I_1} 
-          \sum_{\multiplicity=1}^{M_{1,i}} 
-            \frac{\dc[i]}
-                      { \left( s - \pole[i] \right)^{\multiplicity}}
-            + 
-        \sum_{i=1}^{I_2} 
-          \sum_{\multiplicity=1}^{M_{2,i}}
-           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
-                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
-        \label{eq:excitation:PFE}
-\end{align}
-where $I_1$ denotes the number of real-valued poles, $I_2$ denotes the number of complex conjugated pole pairs.
-$M_{1,i}$ and $M_{2,i}$ denotes the multiplicity of the corresponding poles, such that $\numel{A} = \sum_i^{I_1} M_{1,i} + 2 \sum_{i}^{I_2} M_{2,i}$.
-Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.
-
-Consider a second-order subsystem
-\begin{equation}
-  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
-\end{equation}
-parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
-To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
-\begin{align}
-  \PartialDerivative{G_2}{K} 
-    &= 
-  \frac{\wn^{2\multiplicity}}{\wz}
-  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
-  \\
-  \PartialDerivative{G_2}{\wz} 
-    &= 
-    \frac{-K \wn^{2\multiplicity}}
-              {\wz} 
-    \frac{s}
-              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
-  \\
-  \PartialDerivative{G_2}{\wn} 
-  &= 
-  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
-            {\wz} 
-  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
-            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
-  \\
-  \PartialDerivative{G_2}{\damping}
-  &= 
-  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
-            {\wz}
-  \frac{s \left( s + \wz \right)}
-             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
-  \text{.}
-\end{align}
-
-The poles of these derivatives coincide with the system poles (possibly with increased multiplicity).
-Consequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
-The roll-off near the resonance is determined mainly by the damping $\damping$ and the multiplicity $\multiplicity$ of the sub-system.
-As such, the Fisher information matrix is pre-dominantly determined by the input power spectrum near $\wn$.
-Note that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ have the steepest roll-off near the resonance.
-As such, those parameters are the most important for the experiment design.
-
-\begin{figure}
-  \centering
-  \setlength\figurewidth{0.9\columnwidth}
-  \setlength\figureheight{\figurewidth}
-  \input{\thisDir/figs/derivs.tikz}
-  \caption[Derivatives of a second-order sub-system towards each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
-  % The numbers indicate the (asymptotic) slope as a multiple of $20 \unit{dB/\decade}$.
-  The roll-off near $\wn$ is significant and depends strongly on $\damping$.
-  It can be seen that the derivatives are dominated by the resonance peak, an effect that is even more prominent when $\multiplicity$ is large.
-  This means that for a good input signal, it is critical to have power near the resonance peak. 
-  Note also that $\PartialDerivative{G_2}{\wn}$ and $\PartialDerivative{G_2}{\damping}$ exhibit a sharper peak and hence $\damping$ and $\wn$ are the most important parameters of the model.
-  In this example, $\damping = \varXi$, $K = \varK$, $\frac{\wz}{\wn} \in \Set{\varWzSmall, 1, \varWzBig}$, $\multiplicity=1$ and $\wn = \varWn \unit{rad/s}$ were used.
-}
-\label{fig:excitation:derivatives}
-\end{figure}
-
-\end{subappendices}
-
 % \input{ch02-qlogms/sysid.tex}

### 2016-02-22 ch02-qlogms/excitation-design.tex
Many small changes to CH02, CH05

@@
 In system identification, the focus has mostly been on input design for dynamic systems.
-A common approach is to design the input spectrum and thereby maximizing the information matrix of the estimates, see e.g. \cite{Fedorov1972,Goodwin1977}.
+A common approach is to design the input spectrum and thereby maximizing the information matrix of the estimates, see e.g. \citep{Fedorov1972,Goodwin1977}.
 
@@
 Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design.
-There are two main solutions to this discussed in the engineering literature:
+There are two main solutions to this in the engineering literature:
 \begin{enumerate}
-\item Iterative input design where the design updated as more information about the system is available, see e.g. \cite{Hjalmarsson2005,Gevers2005}.
-\item Robust input design one tries to make the input design robust to uncertainty in the a priori knowledge of the true parameter values, see e.g. \cite{Rojas2007} and references therein. 
+\item Iterative input design where the design updated as more information about the system is available, see e.g. \citep{Hjalmarsson2005,Gevers2005}.
+The disadvantage of this approach is that multiple experiments are required to converge to the optimal design.
+Moreover, since the signal is optimized for a specific system model, it is likely that changes in the dynamics might be hard to observe using such a signal.
+
+\item Robust input design one tries to make the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g. \citep{Rojas2007} and references therein. 
+While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought and experimentation than (nominal) optimal designs.
+E.g. the approach followed by \citet{Rojas2007} relies on both nominal parameter values and the distribution function of these parameters to design a robust (optimal) excitation signal.
 \end{enumerate}
-
-In this chapter we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified. 
-We will consider input design when it is known that the system has resonances, possibly spanning a large frequency band. 
-It is however not necessary to know how many resonances are in the system. 
-The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.
-
-Experiment design is the first step in the system identification loop, as illustrated in \figref{fig:intro:identification-cycle}.
-Consequently, the design that is chosen influences every further step in the identification process and limit the model quality that can be attained.
 
@@
 \label{sec:excitation:intro:approach}
+In this chapter, we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified. 
+We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
+It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics\TODO{citation}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)}.
+
+The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.
+
 In this chapter, the goal is to construct excitation signals that bridge the properties of generic and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
-In particular, a generic excitation signal will be used but its properties are tuned in such a way that it attains some properties of robust excitation signals without the requirement of very specific prior information.
-
-\input{ch02-qlogms/logMS_IMTC.tex}
+In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without the requirement of very specific prior information.
 
 \section{Introduction}
-  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
+  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~.
   Of course, we also want to attain a specified uncertainty level over the full frequency span.
@@
 
-\section{Input design}\label{sec:excitation:inputDesign}
-For the theoretical analysis, we consider SISO output error systems, i.e.
+\section{Input design}
+\label{sec:excitation:inputDesign}
+For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
 \begin{align}
@@
   \subsection{The system under consideration}
-  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $n_b / n_a$:
-  \begin{align}
-    G\left( \Omega, \theta \right) = \frac{B\left( \Omega,\theta \right)}
+  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $\order{B} / \order{A}$:
+  \begin{align}
+    G\left( \Omega, \theta \right) 
+    = \frac{B\left( \Omega,\theta \right)}
                   {A\left( \Omega,\theta \right)}
-                                   = \frac{\sum\limits_{i=0}^{n_b-1} b_i \Omega^i}
-                                          {\sum\limits_{i=0}^{n_a-1} a_i \Omega^i}
+    = \frac{\sum\limits_{i=0}^{\order{B}} b_i \Omega^i}
+                  {\sum\limits_{i=0}^{\order{A}} a_i \Omega^i}
     \text{.} \label{eq:model}
@@
   Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion:
-  \TODO{move into main text}
 Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form:
@@
   \end{equation}
-  For simplicity, one can stipulate that the frequency grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
+  Without loss of generality, one can stipulate that the frequency grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
   \end{definition}
 
-  We limit ourselves, without loss of generality, to random phase multisines.
+  For \gls{LTI} systems, it is well-known \TODO{refer to eqn. from Larsson} that the information matrix only depends upon the amplitude spectrum of the input and not upon its phase spectrum.
+  As such, in this chapter assume random-phase multisines since this is a reasonable choice for systems that are dominantly linear~\TODO{referentie}.
   Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
@@
     the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
-  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.
+  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.
 
@@
   when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
-  For a constant amplitude spectrum, this means the dynamics that are present at lower frequencies are plagued by a higher uncertainty than the ones located at higher frequencies.
+  This is a rather common choice in multisine excitations when no other constraints are taken into account.
+  For a constant amplitude spectrum, this means that a model of the low-frequency dynamics is typically plagued by a higher uncertainty than for models of high-frequency dynamics.
+  This is caused by the fact that the lower frequency bands receive less signal power than the high frequency bands.
 
@@
   For that reason, a logarithmic multisine is a good candidate for our purposes.
-  However, it is more involved both to generate and to analyze such a signal, as the excited frequencies don't lie on a commensurate frequency grid.
+  However, it is more involved both to generate and to analyze such a signal, as the excited frequencies do not lie on a commensurate frequency grid.
   Especially for periodic measurements, this is a major downside since the period of such signal does not always exist (i.e. this leads to infinite measurement times).

### 2016-02-22 ch05-initvals/initial-values.tex
Many small changes to CH02, CH05

@@
 where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
-This problem is solved using \code{fmincon} in \MATLAB.
-
-An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}.
-The hyperparameters can be determined via \code{arxregul}.
+This problem is solved using \mcode{fmincon} in \MATLAB.
+
+An implementation of the \gls{RFIR} estimator is available as the \mcode{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \mcode{arxoptions}.
+The hyperparameters can be determined via \mcode{arxregul}.
 More information about the \gls{RFIR} estimator can be found in
@@
 
-\subsection{Identification Procedure}
+\subsection{Identification procedure}
 The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
@@
 
-\subsection{Reference Model Measurements}
+\subsection{Reference model measurements}
 
@@
 
-\subsection{Model Estimation}
+\subsection{Model estimation}
   The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
@@
 
-\subsection{Model Validation}
+\subsection{Model validation}
 \subsubsection{Cost function limitations}
@@
 
-\section{Remark on Generality}
+\section{Remark on the generality}
 \label{se:Generality}
@@
 \end{itemize}
-discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
+discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \mcode{cheby1}, \mcode{cheby2}, \mcode{ellip} and \mcode{butter} are simulated.
 Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
@@
 Unfortunately, \MATLAB, like many other interpreted languages, does not provide any feature to measure $\cputime$ of a segment of code.
-Instead, the typical \code{tic} and \code{toc} functions measure the wall-clock time.
+Instead, the typical \mcode{tic} and \mcode{toc} functions measure the wall-clock time.
 To reduce the effect of other running programs and one-time actions (e.g.
@@
 
-In this case, the \MATLAB function \code{timeit}~\citep{matlab:timeit} has been used to measure the timing of the different functions.
+In this case, the \MATLAB function \mcode{timeit}~\citep{matlab:timeit} has been used to measure the timing of the different functions.
 This function  reports the median wall-clock time and chooses the number of repetitions automatically.
@@
 \end{itemize}
-The median timings as returned by \code{timeit} are reported in \tabref{tbl:init:timing}.
+The median timings as returned by \mcode{timeit} are reported in \tabref{tbl:init:timing}.
 
@@
 However, it should be noted that all these implementations rely on code that has not been optimized for performance.
-As such it is not possible to draw conclusions about the performance one may expect from performance-optimized implementations one would use in a commercial toolbox.
+As such it is not possible to draw conclusions about the performance one may expect from optimized implementations that one would use in a commercial toolbox.
+
 In particular the \gls{RFIR} smoother takes an exorbitant amount of time.
@@
 The truncated \gls{LPM}, on the other hand, requires a more reasonable amount of time for the short data lengths.
-For longer datasets, it appears that the \code{kron} function is one of the major culprits for the long runtimes of the \gls{LPM}.
+For longer datasets, it appears that the \mcode{kron} function is one of the major culprits for the long runtimes of the \gls{LPM}.
 
@@
 The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
-Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$
+Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
 
@@
 This is also the approach that toolboxes such as \citep{FDIDENT} and \citep{TDIDENT} employ.
-Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e. one can easily try out a different strategy in parallel without incurring a lot of overhead.
+Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e.
+one can easily try out a different strategy in parallel without incurring a lot of overhead in terms of wall-clock time.
 As such, computing multiple starting values can happen without a significant increase in wall-clock time and consequently a sluggish user-experience.
@@
 This comes at a limited cost for the end-user: in principle these smoothers can be tried without any additional intervention by the user.
-The only disadvantage is the additional computational effort required and hence also the increase in wall clock time to obtain a parametric estimate.
-However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest.
-
-%\input{ch05-initvals/InitialValuesPaper.tex}
-
-%\input{ch05-initvals/letter.inc.tex}
+The only disadvantage is the additional computational effort required and hence also the increase in wall-clock time to obtain a parametric estimate.
+However, thanks to the recent trend of parallel computing and the fact that this problem is embarrassingly parallel, we expect that increases in wall-clock time can be kept very modest if performance-tuned implementations are used.

### 2016-02-23 ch02-qlogms/excitation-design.tex
Remove some unneeded files

@@
 %TODO: explain generic LTI system
-Consider a second-order subsystem
+Consider the second-order subsystem with multiplicity $\multiplicity$:
 \begin{equation}
@@
   \begin{remark}
-  All simulations  have been repeated fitted with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
-  The observed results were identical and hence are not elaborated further in this text.
+  All simulations  have been repeated as well by fitting with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
+  The observed results were similar and hence are not elaborated further in this text.
+  For more information, please refer to \citep{Larsson2012SYSID}.
   \end{remark}
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
-
-% \input{ch02-qlogms/sysid.tex}

### 2016-02-23 ch02-qlogms/code/derivativesSubsys.m

@@ -2,31 +2,33 @@ clear all;
 close all;
 clc;
 
-syms K wz s wn xi
+syms K wz s wn xi wp 
 syms m
 m = 5; % mupad refuses to check for equality when m is symbolic (prolly some restraint is needed)
 
-G = K*(s/wz+1)/(s^2/wn^2 + 2*xi*s/wn + 1)^m
+G1 = K/(s+wp)
+G2 = K*(s/wz+1)/(s^2/wn^2 + 2*xi*s/wn + 1)^m
 
 derivative = @(f, x) simplify(diff(f,x))
 
-dGdK  = derivative(G,K)
-dGdwz = derivative(G,wz)
-dGdwn = derivative(G,wn)
-dGdxi = derivative(G,xi)
+dG2dK  = derivative(G2,K)
+dG2dwz = derivative(G2,wz)
+dG2dwn = derivative(G2,wn)
+dG2dxi = derivative(G2,xi)
+
 
 numer = K*wn^(2*m)/wz*(s+wz);
 D     = s^2 + 2*xi*wn*s+wn^2;
 denom = (D)^m;
 
-assert(logical(simplify(G == numer/denom)))
+assert(logical(simplify(G2 == numer/denom)))
 
-dGdK_man  = G/K
+dG2dK_man = G2/K
 dGdwz_man = -K*wn^(2*m)*s/wz^2/D^m
 dGdwn_man =  2*m*K*wn^(2*m-1)/wz*(s+wz)*(s+xi*wn)*s/D^(m+1)
 dGdxi_man = -2*K*m*wn^(2*m+1)*s*(s+wz)/wz/D^(m+1)
 
-assert(logical(simplify(dGdK_man  == dGdK)) , 'dGdK is wrong')
-assert(logical(simplify(dGdwz_man == dGdwz)), 'dGdwz is wrong')
-assert(logical(simplify(dGdwn_man == dGdwn)), 'dGdwn is wrong')
-assert(logical(simplify(dGdxi_man == dGdxi)), 'dGdxi is wrong')
+assert(logical(simplify(dGdK_man  == dG2dK)) , 'dGdK is wrong')
+assert(logical(simplify(dGdwz_man == dG2dwz)), 'dGdwz is wrong')
+assert(logical(simplify(dGdwn_man == dG2dwn)), 'dGdwn is wrong')
+assert(logical(simplify(dGdxi_man == dG2dxi)), 'dGdxi is wrong')

### 2016-02-23 ch02-qlogms/excitation-design.tex
Some work on CH02

@@
 \item Robust input design one tries to make the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g. \citep{Rojas2007} and references therein. 
-While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought and experimentation than (nominal) optimal designs.
-E.g. the approach followed by \citet{Rojas2007} relies on both nominal parameter values and the distribution function of these parameters to design a robust (optimal) excitation signal.
+While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
+E.g. the approach followed by \citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
+As such, this requires more advanced prior knowledge of the system to cope with the uncertainty of the prior knowledge.
 \end{enumerate}
@@
 \label{sec:excitation:intro:approach}
-In this chapter, we focus on robust excitation and we address the situation where there is very limited a priori information about the system to be identified. 
+In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
+In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
 We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
 It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
+
 Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics\TODO{citation}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)}.
 
-The advantage of the proposed input design is that regardless of where these resonances are located, the resulting transfer function variance will be the same, for a given damping in the system.
-
-In this chapter, the goal is to construct excitation signals that bridge the properties of generic and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
-In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without the requirement of very specific prior information.
-
-\section{Introduction}
-  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~.
-  Of course, we also want to attain a specified uncertainty level over the full frequency span.
-
-  Any \gls{LTI} system of finite order can be expanded into a  finite sum of systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
+  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
   Therefore the performance of the proposed method is assessed on a prototype system of second order.
@@
   The main problem is that network and dynamic signal analyzers typically
-  rely on an equidistant frequency grid that comes with the Discrete Fourier Transform (DFT).
+  rely on an equidistant frequency grid that comes with the \gls{DFT}.
   A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
@@
   We will also present a simple method to determine a suitable density of a logarithmically spaced signal for a predefined minimal damping of the system to be tested.
+
+  \paragraph{Contents}
+  In \secref{sec:excitation:inputDesign}, we first discuss (optimal) input design on an example second-order system.
+
+  \TODO{
+  \begin{itemize}
+    \item input design
+    \item system parametrization
+    \item $1/f$ power
+    \item frequency grid specification
+    \item optimization of frequency grid
+    \item simulations
+    \item measurements
+  \end{itemize}
+  }
+
+  \TODO{somewhere: mention D-optimal is indep of parametrization}
+  \TODO{somewhere: mention optimality criterion is of lesser importance for a ``good'' signal (optimal in X = good in Y in most cases)}
 
@@
   Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion:
-Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form:
+Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form\citep[Appendix]{Oppenheim1996}:
 \begin{align}
@@
   Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
+\begin{remark}
+  For non-proper systems, one can write the transfer function $G_{\mathrm{non-proper}}(s) = P(s) + G_{\mathrm{proper}}$ where $P(s)$ is a polynomial and $G_{\mathrm{proper}}(s)$ a proper rational function.
+  As such, the polynomial $P(s)$ should be added to equation \eqref{eq:excitation:PFE} for non-proper systems.
+\end{remark}
 

### 2016-02-23 ch05-initvals/initial-values.tex
Some changes from Tom

@@
 \gdef\thisDir{ch05-initvals}
-
-\section{Introduction}\label{se:introd}
-
+\researchBasedOn{Geerardyn2015TIM}
+
+\TODO{bedoeling duidelijker stellen }
+
+\section{Introduction}
+\label{se:introd}
 The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
-Typical measurement techniques and identification strategies of transfer functions (TFs) or \glspl{FRF} are discussed in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
-Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.
-
-Parametric identification of \gls{LTI} systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}. 
- Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
- However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
- Such local optima have a detrimental effect on the quality of the estimated model.
-
- In the perspective of developing identification tools that require as little user interaction as possible, it is important to increase the probability of the optimization algorithm to produce good estimates, or preferably even the global optimum.
- However, when noisy input-output measurements are to be processed, the presence of noise obstructs a clear view of the actual system behavior, especially for poor signal-to-noise ratios (SNRs).
- In non-parametric identification, the presence of noise is typically mitigated by averaging multiple measurements or using smoothing techniques.
+Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
+Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.
+
+Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}.
+ Maximizing the likelihood function of the parameters probably yields a common, consistent, and efficient estimator.
+ However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization.
+ As for many nonlinear optimization problems, this often involves an iterative algorithm to produce the optimal model.
+ The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima.
+ Hence, good initial estimates are essential to obtain a high quality model estimate.
+
+ In the perspective of developing identification tools that require minimal user interaction, it is important that good initial estimates are produced for a wide variety of systems and experimental settings; i.e.
+to increase the probability of the optimization algorithm to produce good estimates, or preferably even the global optimum.
+ However, when noisy input-output measurements are to be processed, the presence of noise obstructs a clear view of the actual system behavior, especially for poor \glspl{SNR}.
+ Such problems can be mitigated using non-parametric techniques: the presence of noise is typically reduced by averaging multiple measurements or by using more advanced smoothing techniques.
 
@@
 The rest of the chapter is structured as follows. 
-Section~\ref{se:ProbForm} covers the problem formulation.
-Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}.
-This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
-In Section~\ref{se:Generality} the generality of the results is discussed briefly.
-Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.
-
-% !TEX root =  InitialValuesPaper.tex
+\secref{se:ProbForm} covers the problem formulation. 
+\secref{se:MethodEg} presents the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
+This is followed by \secref{se:Demo} and \secref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
+In \secref{se:Generality} the generality of the results is investigated briefly.
+The computational effort and recommendations for practical implementations are given in \secref{sec:initvals:computation}.
+Ultimately, concluding remarks are presented in \secref{se:Conclusion}.
 
@@
 \subsection{System Setup Framework and Model}
-\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input.
-The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well.
-The full mathematical model of the system is
+\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic \gls{LTI} discrete-time \gls{SISO} system, subjected to a known white random noise input.
+The full model of the system is
 \begin{equation}\label{lpmtd1}
@@
 $e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
-For white noise, $H_0 = 1$ and $e(t) = v(t)$.
-Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
+We only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
 However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
 
-\begin{figure}[tbh] %top bottom here
+\begin{figure}[tbh]
 \centering
@@
 
+\TODO{paragraaf naar intro verplaatsen}
 Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
@@
 In this chapter we assume that the output signal is disturbed by random noise, resulting in noisy error-prone data.
-For the simulations, white noise is used.
+For the simulations, white noise is used ($H_0 = 1$ and $e(t) = v(t)$).
 It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{se:ExpMeas}.
@@
 \begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in \left( - \infty, + \infty \right)
+    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{} \IntegerNumbers
 \label{ABpolys}
@@
 
-From~\citep[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
+From~\citet[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the \glspl{DFT} of the windowed signals, equation \eqref{ABpolys} is of the form
 \begin{align}
@@
 \end{align}
-with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the difference between the initial and end conditions of the filter $\true{G}$ during the measurement record.
-\begin{assumption}
-It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
-\end{assumption}
+with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the \gls{DFT} frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the difference between the initial and end conditions of the filters $\true{G}$ and $\true{H}$ during the measurement record.
 
@@
 \end{remark}
+
+\begin{assumption}
+It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
+\end{assumption}
 
@@
   [width=\columnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this chapter (\circledNum{3}, \circledNum{4}).
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convext optimization problem.
   The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
@@
 
-The distance measure used in equation \eqref{eq:successrateTol} is defined as
+The norm used in equation \eqref{eq:successrateTol} is defined as
 \begin{align}
@@
   \item `good' estimates which have $\|\model{\bullet} - \model{\trueSymbol} \|_2 < tol \approx 6 \cdot 10^{-5}$,
-  \item `poor' estimates which are much farther from $\model{\trueSymbol}$.  This is caused by the local optima.
+  \item `poor' estimates which are much further from $\model{\trueSymbol}$.  This is caused by the local optima.
 \end{enumerate}
@@
 To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
-The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
-Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
-The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the \gls{IDFT}.
+The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
+Although acquisition and generation were synchronized, there is a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
+Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
+This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
+As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated, the time-domain counterpart $y(t)$ can be obtained using the \gls{IDFT}.
 
@@
 For each measurement repetition, the signals $u^{[r]}(t)$, $y^{[r]}(t)$ and the variances $\sigma_U^2(\omega)$, $\sigma_Y^2(\omega)$ are used in the maximum likelihood cost function given by equation \eqref{eq:MLEcf}.
-The model chosen for the cost function comprises a numerator of third order, a denominator of sixth order and transient contribution of a fifth degree. This results in a transfer function of the form:
-\begin{equation}
-  \model{\bullet}(s,\theta) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
+The model order was chosen according to the specifications of the sixth-order (Chebyshev) bandpass filter \citep{datasheet_bk1613}.
+Since such a bandpass filter is of sixth degree and requires a relative degree of 3 to produce a $60 \unit{dB/decade}$ slope at high frequencies, this means that the transfer function has a numerator of third order, a denominator of sixth order and transient contribution of a fifth degree (i.e.
+model order: $3/6+5$).
+This results in a transfer function of the form:
+\begin{equation}
+  \model{\bullet}(s,\theta) = 
+  \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
 \end{equation}
@@
 By processing the different repetitions, a parametric fit per initialization method corresponding to the appropriate branch in \figref{fig:flowgraph}, and per repetition can be obtained. 
+\begin{remark}
+Fitting the data with models of increased order (e.g. $4/6+5$) has also been attemped, but those models did not yield significant improvements.
+\end{remark}
 

### 2016-02-24 ch02-qlogms/excitation-design.tex
Improve CH02

@@
 \researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }
-\TODO{rename labels}
 
@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics\TODO{citation}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)}.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)} amongst others.
 
@@
   \paragraph{Contents}
-  In \secref{sec:excitation:inputDesign}, we first discuss (optimal) input design on an example second-order system.
-
-  \TODO{
-  \begin{itemize}
-    \item input design
-    \item system parametrization
-    \item $1/f$ power
-    \item frequency grid specification
-    \item optimization of frequency grid
-    \item simulations
-    \item measurements
-  \end{itemize}
-  }
-
-  \TODO{somewhere: mention D-optimal is indep of parametrization}
+  In \secref{sec:excitation:inputDesign}, we first consider (optimal) input design for an example second-order system.
+  Next in \secref{}, \gls{LTI} systems are parametrized to facilitate the input design.
+  This will lead to signals with a $1/f$ power spectrum as in \secref{sec:excitation:logarithmic}.
+  In \secref{sec:excitation:grids} a comparison of different discrete frequency grids is provided, this is afterwards related to the problem of generating a multisine signal with a $1/f$ power spectral density.
+  Next, \secref{sec:excitation:optimAlpha} describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant model quality is obtained.
+  The usefulness of the proposed signals is illustrated on simulations in \secref{sec:excitation:simulation} and validated on the measurement of a set of band-pass filters in \secref{sec:excitation:measurement}.
+  Conclusions are formulated in \secref{sec:excitation:conclusion}.
+
   \TODO{somewhere: mention optimality criterion is of lesser importance for a ``good'' signal (optimal in X = good in Y in most cases)}
-
-  In the first section of this chapter, we start from a generic transfer function model and discuss a decomposition thereof in second order subsystems and their properties.
-  We provide a comparison between several possible implementations of the frequency grids.
-  We discuss their applicability to multisine signals.
-  We also introduce a compensation method for the problems of the quasi-logarithmic grid and propose a novel $1/f$ `pink' quasi-logarithmic multisine.
-  The second section describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant quality (signal to noise ratio (SNR)) is obtained.
-
-  In the third section, the presented techniques are illustrated on a simulation example.
-  Finally, we verify our results experimentally on the measurements of a band-pass filter.
 
@@
 The transfer function is parameterized by the vector $\theta$.
-These parameters are unknown and therefore need to be estimated.
+These parameters are unknown and hence we are interested in estimating their values.
 
@@
 The information matrix is a function of the input power spectrum $\powerspec{u}$, which is the only entity that can be used to improve the quality of the estimates. 
-A common optimality criterion is D-optimality where $\det{\IF}$ is maximized \citep{Goodwin1977}.
+A common optimality criterion is D-optimality where $\det{\IF}$ is maximized~\citep{Goodwin1977}.
+
+\begin{remark}
+D-optimal input designs are quite popular since this criterion minimizes the volume of  the probability density region of the parameters~\citep[Chapter 6]{Goodwin1977}.
+Moreover, the D-optimal input design is independent of the parametrization of the system (as long as the different parametrizations can be related by a bijective function).
+\end{remark}
 
@@
 
-%Such a signal is discussed in the next section.
-
-% \TODO{begin}
-% \newcommand{\robust}{\mathrm{robust}\}
-% \subsection{Using prior system information}
-% Consider a system $G(s,\theta)$ where some initial guess of the parameter vector,
-% say $\hat{\theta}_0 \in \mathbb{R}^n$ exists. A D-optimal design can then be
-% found based $\hat{\theta}_0$. The resulting determinant is
-% \begin{align}
-%  \left[\det\IF^\star\right]^{-1}
-%    &= \min_{\phi_u(\omega)}
-%             \left[\det\IF\right]^{-1}
-% \end{align}
-
-% The optimal input can be realized as sum of $n$ sinusoids.
-% Such an input is typically not robust to the initial guess since \TODO{\ldots}.
-% As a solution to this, the optimal input is modified so that a fraction of the
-% power in the optimal design is taken away and redistributed over all frequencies.
-% This ensures that some excitation power is available also at other frequencies.
-
-% If $\lambda_i$ is the fraction of the input power at frequency $\wn[i]$,
-% then the determinant of $\IF^\star$ can be expressed as \Cite{Goodwin}
-% \begin{align}
-%  \det\IF^\star &= \prod_{i = 1}^{n}
-%                      \lambda_i^2
-%                      \alpha(\wn[i]).
-% \end{align}
-% The optimal input spectrum is
-% \begin{align}
-%  \phi_u^\star(\omega) &= \sum_{i=1}^{n}
-%                            \lambda_i^2
-%                            \delta(\omega,\wn[i])
-% \end{align}
-% If a fraction, say $\eta$, of the power is taken from each frequency and used
-% at other frequencies, the input spectrum can be written as
-% \begin{align}
-%  \phi_u(\omega) &= (1-\eta)
-%                      \sum_{i=1}^{n}
-%                        \lambda_i^2 
-%                        \delta(\omega,\wn[i])
-%                    + \phi_u^{\robust}(\omega),\\
-%                 &= (1-\eta) \phi_u^\star    (\omega)
-%                    +        \phi_u^{\robust}(\omega).
-% \end{align}
-% The term $ \phi_u^{\robust}$ is the part that introduces robustness and
-% must be such that
-% \begin{align}
-%  \int_0^{\pi} \phi_u^{\robust}(\omega) \dd{\omega} &= n \eta.
-% \end{align}
-% The spectrum $\phi_u^{\robust}(\omega)$ can for example be chosen as
-% a discrete spectrum, e.g. from a multi-sine signal, or as
-% a continuous spectrum. The resulting information matrix for the robust input is hence
-% \begin{align}
-%  \IF &= (1-\eta)\IF^\star + \IF^\robust
-% \end{align}
-% The determinant is therefore
-% \begin{multline}
-% \det\left[(1-\eta)\IF^\star + \IF^\robust\right]
-%  \geq \det\left[(1-\eta)\IF^\star\right] + \det\left[\IF^\robust\right] \\
-%  =  (1-\eta)^n\det\left[\IF^\star\right] + \det\left[\IF^\robust\right]
-%  \text{.}
-% \end{multline}
-% The inequality holds since the information matrix is a positive, semi-definite
-% matrix. Hence the largest possible loss in the determinant due to the robustness
-% is given by the factor $(1-\eta)^n$.
-% \TODO{This bound is often very low, maybe better one should be found!}
-% \TODO{end}
-
-\section{Logarithmic power distributions}\label{sec:excitation:logarithmic}
+\section{Logarithmic power distributions}
+\label{sec:excitation:logarithmic}
 When no information about the system is known, it is desirable that the excitation signal is such that regardless of the true system characteristics, the resulting estimates have equally good statistical properties.
@@
 For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
-% \begin{align}
-% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:excitation:cross1} \\
-% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
-% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:excitation:cross}
-% \end{align}
 \begin{gather}
@@
 
-\section{Methodology} \label{sec:method}
+\section{Methodology} 
+\label{sec:excitation:method}
 
@@
                   {\sum\limits_{i=0}^{\order{A}} a_i \Omega^i}
-    \text{.} \label{eq:model}
+    \text{.} 
+    \label{eq:excitation:model}
   \end{align}
@@
   \text{.}
-  \label{eq:secondOrderSystemCT}
-  \end{equation}
-
-  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
+  \label{eq:excitation:secondOrderSystemCT}
+  \end{equation}
+
+  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:excitation:model}.
   The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
@@
                {2 \damping \sqrt{1-\damping^2}}
-               \label{eq:peakAmplitude}\\
+               \label{eq:excitation:peakAmplitude}\\
    \wM &
         = \sqrt{1-2\damping^2} \wn
-        \label{eq:peakFrequency}
+        \label{eq:excitation:peakFrequency}
     \text{.}
@@
   To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
-  \begin{definition}[Generalized multisine] \label{def:generalized-MS}
+  \begin{definition}[Generalized multisine] \label{def:excitation:generalized-MS}
   A generalized multisine $u(t)$ is a signal consisting of $F$ sine waves with a different frequencies $f_k$, amplitudes $A_k$ and phase shifts $\phi_k$:
@@
   \text{.}
-  \label{eq:MultisineCT}
+  \label{eq:excitation:MultisineCT}
   \end{equation}
@@
     the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
-  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.
+  Note that the $k^{\text{th}}$ term in \eqref{eq:excitation:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.
 
@@
   \end{equation}
-  \begin{definition}[Least common (integer) multiple] \label{def:lcm-real}
+  \begin{definition}[Least common (integer) multiple] \label{def:excitation:lcm-real}
   The least common multiple of the set of values $T_k \in \mathbb{F}\without\set{0}$ for $k \in \mathbb{K} \isdef \set{1, \ldots, F}$ is  
@@
   This last example illustrates that a least common multiple of real numbers is not guaranteed to exist.
-  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
+  Consequently, the generalized multisine of \defref{def:excitation:generalized-MS} is not guaranteed to be periodic.
   In actual implementations with limited numerical precision, this gives rise to signals that are periodic but whose period can be too long to be practically viable for periodic measurements.
@@
     \text{.}
-  \label{eq:linGrid}
+  \label{eq:excitation:linGrid}
   \end{equation}
@@
          \left(\frac{2\pi n \left( k + k_0 \right) \Delta f}{f_s} + \phi_k \right)
-    \label{eq:MultiSineDT}
+    \label{eq:excitation:MultiSineDT}
   \end{equation}
@@
     \emspace \forall k \in \set{1,\ldots,F}
-  \label{eq:logGrid}
+  \label{eq:excitation:logGrid}
   \end{equation}
@@
                 }
-    \label{eq:logms:F}
+    \label{eq:excitation:logms:F}
     \end{equation}
   where $\floor{\bullet}$ denotes rounding towards the nearest smaller integer value.
-  In the Section \ref{sec:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.
+  In the Section \ref{sec:excitation:optimAlpha}, the choice of a suitable $\alpha$ is elaborated.
 
@@
 
-  To return to the \gls{FRF}, in \secref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
+  To return to the \gls{FRF}, in \secref{sec:excitation:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
   As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
-  bandwidth, one expects an equal variance for each system, as will be shown in \secref{sec:bestFrequencyResolution}.
+  bandwidth, one expects an equal variance for each system, as will be shown in \secref{sec:excitation:bestFrequencyResolution}.
 
@@
   Since most measurement equipment and analysis methods rely on signals with an equidistant frequency grid, we create a frequency grid
-  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:logGrid} is approximately valid but with the strict constraint that the frequencies must be a subset  of an equidistant frequency grid. 
+  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:excitation:logGrid} is approximately valid but with the strict constraint that the frequencies must be a subset  of an equidistant frequency grid.
   This yields the following relation for  subsequent frequency lines:
@@
     \emspace \forall k \in \set{1,\ldots,F}
-  \label{eq:qlogGrid}
+  \label{eq:excitation:qlogGrid}
   \end{equation}
@@
     \text{.}
-    \label{eq:constraintLinGrid}
+    \label{eq:excitation:constraintLinGrid}
   \end{equation}
@@
   \begin{definition}
-  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality \eqref{eq:qlogGrid} does not define the grid unambiguously.
+  For the implementation of a quasi-logarithmic frequency grid,  the approximate equality \eqref{eq:excitation:qlogGrid} does not define the grid unambiguously.
   The quasi-logarithmic grids depicted in this chapter are constructed using the relationship
@@
   As this signal approximates a logarithmically spaced signal,  we expect that it will exhibit comparable properties.
-  On the other hand, by imposing \eqref{eq:constraintLinGrid}, it remains
+  On the other hand, by imposing \eqref{eq:excitation:constraintLinGrid}, it remains
   possible to use signal techniques which rely on a commensurate frequency grid.
@@
     n\left(f_k\right) = \numberOf \mathrm{nearestLines}_{f_k}
-    \label{eq:nfk}
+    \label{eq:excitation:nfk}
   \end{equation}
@@
       \right\}
-    \label{eq:nearestLines}
+    \label{eq:excitation:nearestLines}
   \end{equation}
@@
   \text{.}
-  \label{eq:compensationAk}
+  \label{eq:excitation:compensationAk}
   \end{equation}
@@
 
-  To reduce the complexity of the expressions for $\fMin{k}$ and $\fMax{k}$, we extend the frequency grid by one component to the left and to the right by means of the grid relation (equations \eqref{eq:qlogGrid} and \eqref{eq:constraintLinGrid}) to obtain the grid $\set{f_0, f_1, \ldots, f_F, f_{F+1}}$.
+  To reduce the complexity of the expressions for $\fMin{k}$ and $\fMax{k}$, we extend the frequency grid by one component to the left and to the right by means of the grid relation (equations \eqref{eq:excitation:qlogGrid} and \eqref{eq:excitation:constraintLinGrid}) to obtain the grid $\set{f_0, f_1, \ldots, f_F, f_{F+1}}$.
 
@@
       \fMax{k} &= \mean{f_{k+1}}{f_k}
-    \label{eq:fRange}
-    \text{.}
-    \end{align}
-  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:nearestLines}.
+    \label{eq:excitation:fRange}
+    \text{.}
+    \end{align}
+  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:excitation:nearestLines}.
   Consequently, both signals can be expected to behave in approximately the same way.
 
-  Note that instead of the geometric mean, the arithmetic mean can be used in \eqref{eq:fRange} to calculate almost identical boundaries.
+  Note that instead of the geometric mean, the arithmetic mean can be used in \eqref{eq:excitation:fRange} to calculate almost identical boundaries.
 
   \subsection{Comparison of the frequency grids}
-  To gain some insight into these different grids, \figref{fig:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
+  To gain some insight into these different grids, \figref{fig:excitation:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
   For this example, a frequency spacing $\Delta f = 1\unit{Hz}$ and frequency ratio $\alpha = 1.05$ are used.
@@
     \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
-    \label{fig:freqGrids}
+    \label{fig:excitation:freqGrids}
   \end{figure}
@@
 
-\section{Optimization of the frequency spacing} \label{sec:optimAlpha}
+\section{Optimization of the frequency spacing} 
+\label{sec:excitation:optimAlpha}
   \subsection{Calculation of the model uncertainty}
@@
                          {\FisherInformation_{\theta}^{-1}}
-     \label{eq:varPeak}
+     \label{eq:excitation:varPeak}
   \end{align}
@@
           }
-    \label{eq:FisherInfo}
+    \label{eq:excitation:FisherInfo}
   \end{equation}
@@
   In this chapter, we select a single frequency of interest $\omega_{\interest}$
-  to obtain a scalar performance measure.
+  to obtain a scalar performance criterion.
   This is allowed as the matrix $\C_{X}$ is diagonal.
 
-  \subsection{Relation between the frequency grid and the system resonance} \label{sec:relationLogGridSystem}
+\begin{remark}
+\citet{Goodwin1977} note that for optimal input designs:
+\begin{quote}
+The choice of criteria is often not critical since it is usually the case that a good experiment according to one criterion will be deemed good by other criteria. 
+Naturally this will only be true for sensibly chosen criteria.
+\end{quote}
+Also for the design of robust excitation signals, this is worthwhile observation.
+\end{remark}
+
+  \subsection{Relation between the frequency grid and the system resonance} \label{sec:excitation:relationLogGridSystem}
   To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated \glspl{FRF} of a set of prototype second-order systems excited by logarithmically spaced excitation signals.
@@
 
-  Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
+  Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:excitation:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
   Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order system that shares the damping and \gls{DC} gain of the previous system but has a natural frequency $m\wn$.
 
-  If one calculates their FRFs by evaluating \eqref{eq:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
+  If one calculates their FRFs by evaluating \eqref{eq:excitation:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
   Both FRFs share the same `shape', but are `located' at different frequencies.
@@
     \infgrid{\omega} \isdef \Set{\alpha^k \omega_0 | k \in \ZN}
-    \label{eq:freqGridLog}
+    \label{eq:excitation:freqGridLog}
   \end{equation}
@@
   Both $\infgrid{\omega}$ and $m\infgrid{\omega}$ share the frequency ratio $\alpha$.
-  \begin{remark} \label{rem:exc:gridscaling}
+  \begin{remark} \label{rem:excitation:exc:gridscaling}
     For $N \in \ZN$ it is obvious that $\infgrid{\omega} = \alpha^{N} \infgrid{\omega}$, i.e. both grids coincide.
@@
 
-  \begin{lemma} \label{lem:exc:sysscaling}
+  \begin{lemma} \label{lem:excitation:exc:sysscaling}
   Consider the second-order systems $G(\omega; \wn)$ and $G(\omega; m\wn)$ with $m \in \RealNumbersWithoutZero$. 
@@
   \begin{proof}
-    This is an immediate consequence from Lemma~\ref{lem:exc:sysscaling} for $m= \alpha^{N}$ and Remark~\ref{rem:exc:gridscaling}.
+    This is an immediate consequence from Lemma~\ref{lem:excitation:exc:sysscaling} for $m= \alpha^{N}$ and Remark~\ref{rem:excitation:exc:gridscaling}.
   \end{proof}
@@
   Taking this into account allows to limit the study of second order systems to a small set of systems that should be considered in the search for a suitable grid spacing $\alpha$.
-  We can limit the evaluation of the theoretical uncertainty \eqref{eq:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
+  We can limit the evaluation of the theoretical uncertainty \eqref{eq:excitation:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
   \begin{equation}
     \wn \alpha^{N+\gamma}\qquad \text{ with } 0 \leq \gamma < 1\text{.}
-    \label{eq:theoreticalBestVariationOmega}
+    \label{eq:excitation:theoreticalBestVariationOmega}
   \end{equation}
@@
   \subsection{Selection of the frequency grid spacing $\alpha$}
-  When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
+  When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
   Note that $\dc$ is a scaling factor for the FRF.
@@
   The choice of the damping is more important.
-  Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:peakAmplitude} to study the effect of differently damped systems.
+  Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:excitation:peakAmplitude} to study the effect of differently damped systems.
 
@@
     \text{.}
-    \label{eq:normAlpha} 
+    \label{eq:excitation:normAlpha} 
   \end{equation}
@@
   The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
-  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:normAlpha} can safely be neglected.
+  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:excitation:normAlpha} can safely be neglected.
 
@@
 
-  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
+  Instead of using \eqref{eq:excitation:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
 
@@
     The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
-    \label{fig:misalignment-logms}
+    \label{fig:excitation:misalignment-logms}
   \end{figure}
@@
    \text{ with } 0 \leq \beta < 1
-   \label{eq:chosenVariationOmega}
-  \end{equation}
-  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
-  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
+   \label{eq:excitation:chosenVariationOmega}
+  \end{equation}
+  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:excitation:misalignment-logms}
+  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
   If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
@@
 
-  We then calculate the theoretical variance on the magnitude of the peak in the FRF ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:varPeak} for a coarse grid.
+  We then calculate the theoretical variance on the magnitude of the peak in the FRF ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
@@
 
-  \subsection{Discussion} \label{sec:bestFrequencyResolution}
+  \subsection{Discussion} \label{sec:excitation:bestFrequencyResolution}
   As stated above, we start by evaluating the variance $\sigma_G\left( \wM\right)$ for a coarse frequency spacing $\tilde{\alpha} = 10$ for each of the prototype systems.
-  This is shown by the solid lines in \figref{fig:worstCaseBeta}.
+  This is shown by the solid lines in \figref{fig:excitation:worstCaseBeta}.
   One immediately notices that the variance depends strongly on the misalignment $\beta$ of the system and the frequency grid.
@@
              The full lines depict the variance for a coarsely spaced signal.
-             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:optimAlpha}).}
-    \label{fig:worstCaseBeta}
+             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:excitation:optimAlpha}).}
+    \label{fig:excitation:worstCaseBeta}
   \end{figure}
@@
 
-  We explore the systems which have the worst uncertainty (as marked by a cross in \figref{fig:worstCaseBeta}).
+  We explore the systems which have the worst uncertainty (as marked by a cross in \figref{fig:excitation:worstCaseBeta}).
   For the corresponding values of the misalignment $\beta$, we evaluate the uncertainty when the frequency ratio $\alpha$ of the signal is decreased, while the total signal power is kept identical.
-  The results are displayed in \figref{fig:worstCaseAlpha}, where the marked points correspond to the marked points in \figref{fig:worstCaseBeta}.
+  The results are displayed in \figref{fig:excitation:worstCaseAlpha}, where the marked points correspond to the marked points in \figref{fig:excitation:worstCaseBeta}.
 
@@
              The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
-    \label{fig:worstCaseAlpha}
+    \label{fig:excitation:worstCaseAlpha}
   \end{figure}
@@
     \alpha^{\star} = 1 + \damping
-    \label{eq:optimAlpha}
+    \label{eq:excitation:optimAlpha}
   \end{equation}
   such that it represents the coarsest frequency spacing for which the variance is approximately equal to that constant value.
-  This choice is indicated by the dashed line in \figref{fig:worstCaseAlpha}.
+  This choice is indicated by the dashed line in \figref{fig:excitation:worstCaseAlpha}.
 
@@
 
-  If we determine the effect of the misalignment factor $\beta$ for a grid with frequency ratio $\alpha^{\star}$, we see that misalignment has a negligible effect on the uncertainty as shown by the dashed lines in \figref{fig:worstCaseBeta} for each of the prototype systems.
-  Note that these values do indeed coincide with the limiting values found in \figref{fig:worstCaseAlpha}.
-
-  Now we can interpret \figref{fig:worstCaseBeta} in more detail.
+  If we determine the effect of the misalignment factor $\beta$ for a grid with frequency ratio $\alpha^{\star}$, we see that misalignment has a negligible effect on the uncertainty as shown by the dashed lines in \figref{fig:excitation:worstCaseBeta} for each of the prototype systems.
+  Note that these values do indeed coincide with the limiting values found in \figref{fig:excitation:worstCaseAlpha}.
+
+  Now we can interpret \figref{fig:excitation:worstCaseBeta} in more detail.
   We see that for $\beta \in \set{0,1}$ (i.e. perfect alignment), the variance of a course grid (full lines) is lower than it is for a fine grid (dashed lines).
@@
 
-  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the FRF of the system are visualized in \figref{fig:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
+  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the FRF of the system are visualized in \figref{fig:excitation:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
   The $3\unit{dB}$ bandwidth of the system is highlighted in gray together with the excited frequency lines that lie within that bandwidth.
@@
 The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
-    \label{fig:signalAndSystem}
+    \label{fig:excitation:signalAndSystem}
   \end{figure}
@@
 \section{Simulations} \label{sec:excitation:simulation}
-In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
+In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:method}.
   \subsection{Setup}
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform \citep{Oppenheim1983} to the continuous time system \eqref{eq:secondOrderSystemCT}.
+  This form can also be obtained by applying Tustin's method or bilinear transform \citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSystemCT}.
 
@@
   For the quasi-log grid multisine, the compensated and pink quasi-log multisine, we chose a frequency ratio $\alpha = 1.05$.
-  According to \eqref{eq:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the FRF $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
+  According to \eqref{eq:excitation:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the FRF $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
   Each of these signals is constructed to have an RMS value of $1$.
-  The amplitude spectra of these signals are displayed in \figref{fig:freqGrids} for identical signal power.
+  The amplitude spectra of these signals are displayed in \figref{fig:excitation:freqGrids} for identical signal power.
 
@@
 
-  The resulting frequency response function $\hat{G}$ for one such system is shown in \figref{fig:FRF1} together with the standard deviation $\sigma_{\hat{G}}$ of the estimated parametric model for each of the different excitation signals.
+  The resulting frequency response function $\hat{G}$ for one such system is shown in \figref{fig:excitation:FRF1} together with the standard deviation $\sigma_{\hat{G}}$ of the estimated parametric model for each of the different excitation signals.
   The bias is at least $20\unit{dB}$ smaller than the standard  deviation.
@@
     \caption[Simulated FRF and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
-    \label{fig:FRF1}
+    \label{fig:excitation:FRF1}
   \end{figure}
 
-  \figref{fig:damping02} displays the estimated transfer functions and their uncertainty in the vicinity of their corresponding resonances for the whole set of considered systems.
+  \figref{fig:excitation:damping02} displays the estimated transfer functions and their uncertainty in the vicinity of their corresponding resonances for the whole set of considered systems.
   Using this condensed representation and the displayed envelopes of the uncertainty, we can deduce the frequency-dependent behavior of the model variance obtained by the different excitation signals.
@@
              excitation signals.}%
-    \label{fig:damping02}
+    \label{fig:excitation:damping02}
   \end{figure}
@@
   Yet at the lowest frequencies, the $1/\fR$ dependence can be observed again.
-  This is caused by the linear distribution of excited frequencies in this range, as shown in \figref{fig:freqGrids}.
+  This is caused by the linear distribution of excited frequencies in this range, as shown in \figref{fig:excitation:freqGrids}.
 
@@
   \subsection{Systems with a lower damping}
-  Given the optimal frequency ratio \eqref{eq:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
+  Given the optimal frequency ratio \eqref{eq:excitation:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
   In this set of simulations, we check this by repeating the previous set for such systems.
   In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the SNR of $20\unit{dB}$.
-  The corresponding results are shown in \figref{fig:damping005}.
+  The corresponding results are shown in \figref{fig:excitation:damping005}.
 
@@
              excitation signals.}%
-    \label{fig:damping005}
+    \label{fig:excitation:damping005}
   \end{figure}
@@
   \text{.}
-\label{eq:tfO4}
+\label{eq:excitation:tfO4}
 \end{equation}
@@
 The standard deviation of the noise $\sigma_e$ was put at $0.0678$.
-The corresponding results are  shown in \figref{fig:sumSys}.
+The corresponding results are  shown in \figref{fig:excitation:sumSys}.
 
@@
            \TODO{also with other excitation signals?}
-  \label{fig:sumSys}
+  \label{fig:excitation:sumSys}
 \end{figure}
@@
 
-\section{Measurements} \label{sec:measurement}
+\section{Measurements} 
+\label{sec:excitation:measurement}
   \subsection{Setup}
+    \label{sec:excitation:measurement:setup}
     To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.
 
-    The BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
+    The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
     According to its manual \citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
@@
     As excitation signals, a linear grid multisine, an uncompensated quasi-log multisine and pink quasi-log multisine with excited frequencies between $1 \unit{Hz}$ and $64 \unit{kHz}$ were used.
-    These multisines were sampled at $\fs = 256\unit{kHz}$ and had a frequency resolution of $\Delta f = 1 \unit{Hz}$, a frequency spacing $\alpha = 1.05$ and identical RMS values of approximately $0.25 \unit{V}$.
+    These multisines were sampled at $\fs = 256\unit{kHz}$ and had a frequency resolution of $\Delta f = 1 \unit{Hz}$, a frequency spacing $\alpha = 1.05$ and identical \gls{RMS} values of approximately $0.25 \unit{V}$.
     This amplitude was chosen such that the peak amplitude $\max \abs{u(t)}$ was approximately $1 \unit{V}$.
@@
     \begin{equation}
-      G(s) = \frac{\sum_{i=0}^3 b_i s^i}{\sum_{i=0}^6 a_i s^i}
+      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
     \end{equation}
     was estimated using \texttt{elis} \citep{FDIDENT}.
-    The initial estimate was a third-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613}.
+    The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.
 
@@
     \subsection{Results}
-    In \figref{fig:measurements} the nonparametric FRF and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.
+    In \figref{fig:excitation:measurements} the nonparametric FRF and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.
 
@@
     \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
-      \label{fig:measurements}
+      \label{fig:excitation:measurements}
     \end{figure}

### 2016-02-24 ch02-qlogms/excitation-design.tex
Lots of work on CH02

@@
   This will lead to signals with a $1/f$ power spectrum as in \secref{sec:excitation:logarithmic}.
-  In \secref{sec:excitation:grids} a comparison of different discrete frequency grids is provided, this is afterwards related to the problem of generating a multisine signal with a $1/f$ power spectral density.
+  In \secref{sec:excitation:multisine} a comparison of different discrete frequency grids is provided, this is afterwards related to the problem of generating a multisine signal with a $1/f$ power spectral density.
   Next, \secref{sec:excitation:optimAlpha} describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant model quality is obtained.
@@
 
-  \TODO{somewhere: mention optimality criterion is of lesser importance for a ``good'' signal (optimal in X = good in Y in most cases)}
-
 \section{Input design}
@@
 \end{align}
-where $u(t)$ is a known input sequence, $y(t)$ the output sequence and $e(t)$ is zero mean Gaussian white noise.
+where $u(t)$ is a known input sequence, $y(t)$ the output sequence and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
 $G$ is a rational, time invariant transfer function in continuous time.
@@
 \begin{remark}
-D-optimal input designs are quite popular since this criterion minimizes the volume of  the probability density region of the parameters~\citep[Chapter 6]{Goodwin1977}.
-Moreover, the D-optimal input design is independent of the parametrization of the system (as long as the different parametrizations can be related by a bijective function).
+D-optimal input designs are quite popular since this criterion minimizes the volume of uncertainty ellipsoid of the parameters.
+Moreover, the D-optimal input design is independent of the parametrization of the system (as long as the different parametrizations can be related by a bijective function)~\citep[Chapter 6]{Goodwin1977}.
 \end{remark}
@@
 However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance.
-It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}.
-This gives
+It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}. This gives
 \begin{align}
@@
 \end{align}
-with parameters $\theta=[\wn\;\damping]^{\T}$. The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$
-and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
+with parameters $\theta=[\wn\;\damping]^{\T}$. 
+The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$ and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
+The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.
+
+When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in the amplitude of the transfer function~\citep{Oppenheim1983}:
+  \begin{align}
+   \left| G\left(\wM \right) \right| & \isdef
+          \max_{\omega} \left| G\left( \omega \right)  \right|
+        = \frac{\dc}
+               {2 \damping \sqrt{1-\damping^2}}
+               \label{eq:excitation:peakAmplitude}\\
+   \wM &
+        = \sqrt{1-2\damping^2} \wn
+        \label{eq:excitation:peakFrequency}
+    \text{.}
+  \end{align}
+
 Since information is local in the frequency domain, the input signal power inside $\wdB$, contributes significantly to the information matrix while input power outside $\wdB$ has a smaller contribution.
@@
 
-Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
-\begin{align}
-  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\dirac{\omega - \omega_k}},
-\end{align}
-where $\omega_{k}/\omega_{k+1} \approx \alpha$ and $\dirac{\omega}$ denotes the Dirac distribution.
-Hence, the number of spectral lines inside \wdB is 
-\begin{align}
-  \floor{
-    \log_{\alpha} \frac{1+\damping}{1-\damping} 
-  }
-  \text{,}
-\end{align}
-where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.
-
-More generally, a multisine can be defined as:
-\begin{equation}
- u \left[ n\right] = \frac{1}{\sqrt{F}}
-   \sum_{k=1}^{F} 
-     A_k 
-     \sin 
-       \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
-  \label{eq:excitation:MS}
-\end{equation}
-where $A_k$ and $\psi_k$ are its amplitude and phase spectrum; $f_s$ is the
-sampling frequency and $f_0 = \frac{f_s}{N}$ the base frequency with $N$ the 
-number of points in a period.
-
-To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha$.
+Alternatively, one could also construct a signal with power spectrum concentrated at discrete frequency lines.
+Such signals are elaborated in \secref{sec:excitation:method}.
+
+% Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
+% \begin{align}
+%   \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\dirac{\omega - \omega_k}},
+% \end{align}
+% where $\omega_{k}/\omega_{k+1} \approx \alpha$ and $\dirac{\omega}$ denotes the Dirac distribution.
+% Hence, the number of spectral lines inside \wdB is 
+% \begin{align}
+%   \floor{
+%     \log_{\alpha} \frac{1+\damping}{1-\damping} 
+%   }
+%   \text{,}
+% \end{align}
+% where $\floor{\placeholder}$ is the nearest integer rounded downwards. 
+% The number of spectral lines is independent of $\wn$.
+
+% More generally, a multisine can be defined as:
+% \begin{equation}
+%  u \left[ n\right] = \frac{1}{\sqrt{F}}
+%    \sum_{k=1}^{F} 
+%      A_k 
+%      \sin 
+%        \left(\frac{2\pi n k f_0}{f_s} + \psi_k \right)
+%   \label{eq:excitation:MS}
+% \end{equation}
+% where $A_k$ and $\psi_k$ are its amplitude and phase spectrum; $f_s$ is the
+% sampling frequency and $f_0 = \frac{f_s}{N}$ the base frequency with $N$ the 
+% number of points in a period.
+
+% To construct a quasi-logarithmic multisine, only frequency lines $f_j$ within the set of available sine components $\left\{f_0, 2 f_0, \ldots, F f_0  \right\}$ are excited for which the ratio of two consecutive frequencies $f_j$ and $f_{j-1}$ is approximately constant: $\frac{f_{j-1}}{f_j} \approx \alpha$.
 
@@
 
-\subsection{Generic system}
-%TODO: explain generic LTI system
+\subsection{Sums of second order systems}
+This section extends the previous section to more general systems than second order.
+Consider a system
+\begin{align}
+G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
+             =\sum_{i=1}^{K}  \frac{1}
+                                   {   \frac{s^2}{\wn[i]^2}
+                                    + 2\frac{\damping[i]}{\wn[i]}s
+                                    + 1},\\
+\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
+\label{eq:excitation:sumSys}
+\end{align}
+The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
+Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
+To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
+
+The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
+\begin{align}
+\IF &= \frac{1}{\pi}
+\begin{bmatrix}
+  \partial G_{1,1}        &\partial G_{1,2}       &\deemph{\cdots}         &\partial G_{1,K}\\
+  \partial G_{2,1}        &\partial G_{2,2}       &\deemph{\cdots}         &\partial G_{2,K}\\
+  \deemph{\vdots}                  &\deemph{\vdots}                 &\deemph{\ddots}         &\deemph{\vdots}          \\
+  \partial G_{K,1}        &\partial G_{K,2}       &\deemph{\cdots}         &\partial G_{K,K}
+\end{bmatrix},\\
+\partial G_{i,j} &= \int_0^\infty
+                      \mathrm{Re}\left\{
+                          \frac{\partial G_i}
+                               {\partial \theta_i}
+                          \frac{\partial G_j^{\HT}}
+                               {\partial \theta_j}
+                                \right\}
+                      \phi_u(\omega)\dd\omega.
+\end{align}
+
+Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
+The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
+To illustrate this we look at a system with $K=2$, i.e. the sum of two second order systems.
+The conclusions from the example are easily extended to systems consisting of more than two sub-systems.
+
+\subsubsection{Example: Sum of two second-order systems}
+\label{sec:excitation:ex:sumOfSecondOrderSipmle}
+Consider the system
+\begin{align}
+G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
+%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
+\end{align}
+with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
+The information matrix for this system is
+\begin{align}
+\IF &=
+       \begin{bmatrix}
+         \partial G_{1,1}  & \partial G_{1,2}\\
+         \partial G_{2,1}  & \partial G_{2,2}
+       \end{bmatrix}.
+\label{eq:excitation:infoEx}
+\end{align}
+To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
+
+Direct calculations for $\damping < 1$ give
+\begin{align}
+\label{eq:excitation:auto}
+\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
+\end{align}
+For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
+\begin{gather}
+\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
+\qquad \qquad \qquad \qquad \qquad
+\label{eq:excitation:cross1} \\
+\leq
+\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
+\leq \\
+\qquad \qquad \qquad \qquad \qquad
+\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
+\end{gather}
+To proceed, consider
+\begin{align}
+\frac{\partial G_1}{\partial \wn[1]} 
+  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
+  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
+\end{align}
+which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
+Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
+There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
+The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.
+
+A crude, albeit useful, bound on the integrand in \eqref{eq:excitation:cross} is
+\begin{align}
+&f\left(\omega,\theta_1,\theta_2\right)=
+  \begin{cases}
+   \frac{\omega^2}{\wn[1]^2}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\omega \leq \wn[1]$,}\\
+   \phantom{\frac{\omega^2}{\omega^2}}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\wn[1] < \omega < \wn[2]$,}\\
+   \frac{\wn[2]^2}{\omega^2}
+   \frac{1}{\omega}
+   \partial G_1^\infty
+                                       & \text{if $\omega \geq \wn[2]$,}
+  \end{cases}
+\end{align}
+where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
+Again, direct calculations give
+\begin{align}
+\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
+\end{align}
+Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
+\begin{itemize}
+\item the integral \eqref{eq:excitation:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
+\item lower damping further decreases the integral \eqref{eq:excitation:cross1} in comparison to \eqref{eq:excitation:auto}.
+\end{itemize}
+
+To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
+If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
+The resulting information matrix is then normalized so that the largest element is $1$.
+
+In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
+It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling.
+The diagonal blocks of the normalized $\IF$ in all cases have some elements close to $1$. 
+In this example, the $\damping$ is set to be the same in both sub-systems. 
+Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
+
+Based on the above arguments, we approximate the information matrix for lightly-damped systems as a block-diagonal matrix:
+\begin{align}
+\IF&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
+                        \deemph{0}&\partial G_{2,2}\end{bmatrix}.
+\end{align}
+Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
+\begin{align}
+\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
+                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
+&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
+\end{align}
+
+This results extends mutatis mutandis to systems consisting of more sub-systems.
+
+\begin{figure}
+\centering
+\setlength\figurewidth{0.68\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/coupling.tikz}
+\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
+         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
+         The arrow indicates the direction of increasing separation.}
+\label{fig:excitation:coupling}
+\end{figure}
+
+\section{System parametrization} 
+\label{sec:excitation:parametrization}
+
+  We consider the transfer function models of proper \gls{LTI} systems of arbitrary but finite orders $\order{B} / \order{A}$:
+  \begin{align}
+    G\left( \Omega, \theta \right) 
+    = \frac{B\left( \Omega,\theta \right)}
+                  {A\left( \Omega,\theta \right)}
+    = \frac{\sum\limits_{i=0}^{\order{B}} b_i \Omega^i}
+                  {\sum\limits_{i=0}^{\order{A}} a_i \Omega^i}
+    \text{.} 
+    \label{eq:excitation:model}
+  \end{align}
+
+The model is parametrized by the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
+For a continuous time model $\Omega = s$, while for the discrete time case $\Omega = z$.
+For the sake of notational simplicity, $\Omega = s$ will be used further on, but the results are similar for $\Omega=z$.
+Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form~\citep[Appendix]{Oppenheim1996}:
+\begin{align}
+  G(s) &= 
+    \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\sum\limits_{i=0}^{\numel{A}} a_i s^i} 
+        =    
+   \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
+              {\prod\limits_{i=1}^{I_1} \left( s - \pole[i] \right)^{M_{1,i}} 
+               \prod\limits_{i=1}^{I_2} \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{M_{2,i}}}
+        \\
+        &  = 
+        \sum_{i=1}^{I_1} 
+          \sum_{\multiplicity=1}^{M_{1,i}} 
+            \frac{\dc[i]}
+                      { \left( s - \pole[i] \right)^{\multiplicity}}
+            + 
+        \sum_{i=1}^{I_2} 
+          \sum_{\multiplicity=1}^{M_{2,i}}
+           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
+                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
+        \label{eq:excitation:PFE}
+\end{align}
+where $I_1$ denotes the number of real-valued poles, $I_2$ denotes the number of complex conjugated pole pairs.
+$M_{1,i}$ and $M_{2,i}$ denotes the multiplicity of the corresponding poles, such that $\numel{A} = \sum_i^{I_1} M_{1,i} + 2 \sum_{i}^{I_2} M_{2,i}$.
+Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.
+  Within these sub-systems, we can distinguish first-order subsystems and second-order subsystems, the latter of which describe resonant phenomena.
+  Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
+\begin{remark}
+  For non-proper systems, one can write the transfer function $G_{\mathrm{non-proper}}(s) = P(s) + G_{\mathrm{proper}}$ where $P(s)$ is a polynomial and $G_{\mathrm{proper}}(s)$ a proper rational function.
+  As such, the polynomial $P(s)$ should be added to equation \eqref{eq:excitation:PFE} for non-proper systems.
+\end{remark}
+
 Consider the second-order subsystem with multiplicity $\multiplicity$:
@@
 The poles of these derivatives coincide with the system poles (possibly with increased multiplicity).
-Consequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives will exhibit a sharp resonance peak just as the actual sub-system $G_2$ as illustrated in \figref{fig:excitation:derivatives}.
+Consequently, this means that for lightly-damped systems ($\damping \ll \sqrt{2}$), these derivatives exhibit a sharp resonance peak at the same frequency as the actual sub-system $G_2$, see also \figref{fig:excitation:derivatives}.
 The roll-off near the resonance is determined mainly by the damping $\damping$ and the multiplicity $\multiplicity$ of the sub-system.
@@
 
-\subsection{Sums of second order systems}
-This section extends the previous section to more general systems than second order.
-Consider a system
-\begin{align}
-G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
-             =\sum_{i=1}^{K}  \frac{1}
-                                   {   \frac{s^2}{\wn[i]^2}
-                                    + 2\frac{\damping[i]}{\wn[i]}s
-                                    + 1},\\
-\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
-\label{eq:excitation:sumSys}
-\end{align}
-The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
-Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
-To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
-
-The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
-\begin{align}
-\IF &= \frac{1}{\pi}
-\begin{bmatrix}
-  \partial G_{1,1}        &\partial G_{1,2}       &\deemph{\cdots}         &\partial G_{1,K}\\
-  \partial G_{2,1}        &\partial G_{2,2}       &\deemph{\cdots}         &\partial G_{2,K}\\
-  \deemph{\vdots}                  &\deemph{\vdots}                 &\deemph{\ddots}         &\deemph{\vdots}          \\
-  \partial G_{K,1}        &\partial G_{K,2}       &\deemph{\cdots}         &\partial G_{K,K}
-\end{bmatrix},\\
-\partial G_{i,j} &= \int_0^\infty
-                      \mathrm{Re}\left\{
-                          \frac{\partial G_i}
-                               {\partial \theta_i}
-                          \frac{\partial G_j^{\HT}}
-                               {\partial \theta_j}
-                                \right\}
-                      \phi_u(\omega)\dd\omega.
-\end{align}
-
-Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
-The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
-To illustrate this we look at a system with $K=2$, i.e. the sum of two second order systems.
-The conclusions from the example are easily extended to systems consisting of more than two sub-systems.
-
-\subsubsection{Example: Sum of two second order systems}
-Consider the system
-\begin{align}
-G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
-%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
-\end{align}
-with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
-The information matrix for this system is
-\begin{align}
-\IF &=
-       \begin{bmatrix}
-         \partial G_{1,1}  & \partial G_{1,2}\\
-         \partial G_{2,1}  & \partial G_{2,2}
-       \end{bmatrix}.
-\label{eq:excitation:infoEx}
-\end{align}
-To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
-
-Direct calculations for $\damping < 1$ give
-\begin{align}
-\label{eq:excitation:auto}
-\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
-\end{align}
-For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
-\begin{gather}
-\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
-\qquad \qquad \qquad \qquad \qquad
-\label{eq:excitation:cross1} \\
-\leq
-\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
-\leq \\
-\qquad \qquad \qquad \qquad \qquad
-\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
-\end{gather}
-To proceed, consider
-\begin{align}
-\frac{\partial G_1}{\partial \wn[1]} 
-  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
-  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
-\end{align}
-which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
-Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
-There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.
-
-A crude, albeit useful, bound on the integrand in \eqref{eq:excitation:cross} is
-\begin{align}
-&f\left(\omega,\theta_1,\theta_2\right)=
-  \begin{cases}
-   \frac{\omega^2}{\wn[1]^2}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\omega \leq \wn[1]$,}\\
-   \phantom{\frac{\omega^2}{\omega^2}}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\wn[1] < \omega < \wn[2]$,}\\
-   \frac{\wn[2]^2}{\omega^2}
-   \frac{1}{\omega}
-   \partial G_1^\infty
-                                       & \text{if $\omega \geq \wn[2]$,}
-  \end{cases}
-\end{align}
-where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
-Again, direct calculations give
-\begin{align}
-\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
-\end{align}
-Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
-\begin{itemize}
-\item the integral \eqref{eq:excitation:cross1} decreases as $\wn[2]-\wn[1]$ increases, and
-\item lower damping further decreases the integral \eqref{eq:excitation:cross1} in comparison to \eqref{eq:excitation:auto}.
-\end{itemize}
-
-To further illustrate the decoupling of the two systems, we calculate \eqref{eq:excitation:infoEx} for different values of the damping $\damping$ and separations of the two resonances $\wn[1]$ and $\wn[2]$.
-If the separation is taken in terms of $\wdB$-units for the lower resonance, the result only depends on the difference $\wn[1]-\wn[2]$ and not on the actual frequencies.
-The resulting information matrix is then normalized so that the largest element is $1$.
-
-In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations.
-It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling.
-The diagonal blocks of the normalized $\IF$ in all cases have some elements close to $1$. 
-In this example, the $\damping$ is set to be the same in both sub-systems. 
-Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
-
-Based on the above arguments, we approximate the information matrix for lightly-damped systems as a block-diagonal matrix:
-\begin{align}
-\IF&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
-                        \deemph{0}&\partial G_{2,2}\end{bmatrix}.
-\end{align}
-Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
-\begin{align}
-\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
-                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
-&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
-\end{align}
-
-This results extends mutatis mutandis to systems consisting of more sub-systems.
-
-\begin{figure}
-\centering
-\setlength\figurewidth{0.68\columnwidth}
-\setlength\figureheight{0.68\figurewidth}
-\input{\thisDir/figs/coupling.tikz}
-\caption{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
-         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
-         The arrow indicates the direction of increasing separation.}
-\label{fig:excitation:coupling}
-\end{figure}
-
-\section{Methodology} 
-\label{sec:excitation:method}
-
-  \subsection{The system under consideration}
-  We consider the transfer function models of generic \gls{LTI} systems of arbitrary but finite orders $\order{B} / \order{A}$:
-  \begin{align}
-    G\left( \Omega, \theta \right) 
-    = \frac{B\left( \Omega,\theta \right)}
-                  {A\left( \Omega,\theta \right)}
-    = \frac{\sum\limits_{i=0}^{\order{B}} b_i \Omega^i}
-                  {\sum\limits_{i=0}^{\order{A}} a_i \Omega^i}
-    \text{.} 
-    \label{eq:excitation:model}
-  \end{align}
-
-  The model is parametrized by the vector $\theta = \left[b_0 \,\cdots\, b_{n_b-1} \; a_0 \,\cdots\, a_{n_a-1} \right]^{\T}$ and  is evaluated at different frequencies $\Omega$ in the complex plane.
-  For a continuous time model $\Omega = s$, while for the discrete time case $\Omega = z$.
-
-  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion:
-Remember that the rational transfer function of any strictly proper \gls{LTI} system $G$ can be decomposed in its partial fraction form\citep[Appendix]{Oppenheim1996}:
-\begin{align}
-  G(s) &= 
-    \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
-              {\sum\limits_{i=0}^{\numel{A}} a_i s^i} 
-        =    
-   \frac{\sum\limits_{i=0}^{\numel{B}} b_i s^i}
-              {\prod\limits_{i=1}^{I_1} \left( s - \pole[i] \right)^{M_{1,i}} 
-               \prod\limits_{i=1}^{I_2} \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{M_{2,i}}}
-        \\
-        &  = 
-        \sum_{i=1}^{I_1} 
-          \sum_{\multiplicity=1}^{M_{1,i}} 
-            \frac{\dc[i]}
-                      { \left( s - \pole[i] \right)^{\multiplicity}}
-            + 
-        \sum_{i=1}^{I_2} 
-          \sum_{\multiplicity=1}^{M_{2,i}}
-           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
-                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
-        \label{eq:excitation:PFE}
-\end{align}
-where $I_1$ denotes the number of real-valued poles, $I_2$ denotes the number of complex conjugated pole pairs.
-$M_{1,i}$ and $M_{2,i}$ denotes the multiplicity of the corresponding poles, such that $\numel{A} = \sum_i^{I_1} M_{1,i} + 2 \sum_{i}^{I_2} M_{2,i}$.
-Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.
-  Within these sub-systems, we can distinguish first-order subsystems and second-order subsystems, the latter of which describe resonant phenomena.
-  Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
-\begin{remark}
-  For non-proper systems, one can write the transfer function $G_{\mathrm{non-proper}}(s) = P(s) + G_{\mathrm{proper}}$ where $P(s)$ is a polynomial and $G_{\mathrm{proper}}(s)$ a proper rational function.
-  As such, the polynomial $P(s)$ should be added to equation \eqref{eq:excitation:PFE} for non-proper systems.
-\end{remark}
-
-  To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
-  In continuous time such a system can be described by a transfer function of the form
-  \begin{equation}
-    G\left(s \right) = \frac{\dc}
-                            {             \frac{s^2}
-                                               {\wn^2} 
-                             + 2 \damping \frac{s}
-                                               {\wn}
-                             + 1
-                            }
-  \text{.}
-  \label{eq:excitation:secondOrderSystemCT}
-  \end{equation}
-
-  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:excitation:model}.
-  The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
-  The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.
-
-  When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in
-  the amplitude of the transfer function \citep{Oppenheim1983}:
-  \begin{align}
-   \left| G\left(\wM \right) \right| & \isdef
-          \max_{\omega} \left| G\left( \omega \right)  \right|
-        = \frac{\dc}
-               {2 \damping \sqrt{1-\damping^2}}
-               \label{eq:excitation:peakAmplitude}\\
-   \wM &
-        = \sqrt{1-2\damping^2} \wn
-        \label{eq:excitation:peakFrequency}
-    \text{.}
-  \end{align}
-
-\subsection{System and noise model}
-  In this chapter, an \gls{OE} system setup is used.
+Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e.
+equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
+
+\paragraph{System and noise model}
+  In the remainder of this chapter, an \gls{OE} setting is used.
   Denote
@@
     $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
-
-  \begin{figure}
+    The output noise is assumed to be zero-mean and white with a standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
+
+  \begin{figure}[h]
     \centering
@@
 
-  The output noise is assumed to be zero-mean and white with a
-  standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
-
-\subsection{Multisine Excitations}
+\section{Multisine Excitations}
+\label{sec:excitation:multisine}
+In contrast to signal with a continuous $1/f$ \gls{PSD} presented in \secref{sec:excitation:logarithmic}, similar results can be obtained by using signals that have a discrete frequency grid.
+Such signals are presented in this section.
+
   To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
@@
 
-  For \gls{LTI} systems, it is well-known \TODO{refer to eqn. from Larsson} that the information matrix only depends upon the amplitude spectrum of the input and not upon its phase spectrum.
-  As such, in this chapter assume random-phase multisines since this is a reasonable choice for systems that are dominantly linear~\TODO{referentie}.
+  For \gls{LTI} systems, it is well-known that the information matrix only depends upon the amplitude spectrum of the input and not upon its phase spectrum as indicated in \eqref{eq:excitation:IF}.
+  As such, the results presented in this chapter also do not depend on the particular choice of the phase spectrum.
+  This means a user is free to make an appropriate choice for their application.
+
+  In this chapter, random-phase multisines are used since this is a reasonable choice for systems that are dominantly linear~\TODO{ref: BLA}.
   Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
   This leaves two sets of free parameters to create a signal that suits our needs:
-    the amplitude of the spectral lines $A_k$ and
-    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
+  \begin{itemize}
+    \item the amplitude of the spectral lines $A_k$, and
+    \item the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
+  \end{itemize}
   Note that the $k^{\text{th}}$ term in \eqref{eq:excitation:MultisineCT} is periodic with period $T_k \isdef f_k^{-1}$.
@@
 
-\TODO{cov-matrix uitschrijven}
-
-\TODO{zin loopt niet goed}
-  As in \citep{Pintelon2012, Gallager2008, matrixcookbook}, the covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown to be approximately equal to
+  As in \citep{Pintelon2012, Gallager2008, matrixcookbook}, and equivalently to the derivation in \secref{sec:excitation:inputDesign}, the covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown to be approximately equal to
   \begin{align}
@@
 
-  In this chapter, we select a single frequency of interest $\omega_{\interest}$
-  to obtain a scalar performance criterion.
+  In this chapter, we select a single frequency of interest $\omega_{\interest}$ to obtain a scalar performance criterion.
   This is allowed as the matrix $\C_{X}$ is diagonal.
@@
 
-  \subsection{Relation between the frequency grid and the system resonance} \label{sec:excitation:relationLogGridSystem}
+  \subsection{Relation between the frequency grid and the system resonance} 
+  \label{sec:excitation:relationLogGridSystem}
   To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated \glspl{FRF} of a set of prototype second-order systems excited by logarithmically spaced excitation signals.
 
-  \paragraph{Simplification}
-  Instead of studying the response of all possible second-order sub-systems for every possible logarithmically spaced multisine-- a five-dimensional problem with parameters $(\omega_0, \alpha, \wn, \damping, \dc)$-- we argue in favor for a simplification of the problem by considering frequency grids with an infinite span.
-
+  Instead of studying the response of all possible second-order sub-systems for every possible logarithmically spaced multisine-- a six-dimensional problem with parameters $(\omega_0, \alpha)$ for the grid, and $(\wz, \wn, \damping, \dc)$ for the sub-system-- we argue to simplify the problem in such a way that the results are still valid for the more complicated setting.
+
+  \subsubsection{Exploiting the grid misalignment between the system and the grid}
   Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:excitation:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
@@
 
-  If one calculates their FRFs by evaluating \eqref{eq:excitation:secondOrderSystemCT}, one sees that $G_1(\omega)$ and $G_m(m\omega)$ yield the same numerical values for any value of the pulsation $\omega$.
+  If one calculates their FRFs by evaluating \eqref{eq:excitation:secondOrderSystemCT}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
   Both FRFs share the same `shape', but are `located' at different frequencies.
@@
 
-  \subsection{Selection of the frequency grid spacing $\alpha$}
-  When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
-  Note that $\dc$ is a scaling factor for the FRF.
-  Hence the results for different values of $\dc$ only differ by a scaling factor.
-  So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.
+  \subsection{Exploiting the shape of the derivatives}
+   In particular, from \figref{fig:excitation:derivatives}, it can be seen that the derivatives with respect to $(\wn, \damping)$ exhibit a sharper resonance and hence $(\wn, \damping)$ will prove the hardest to identify.
+   This means that if one would design a signal to identify just $(\wn, \damping)$, such a signal would also be well-suited to identify the other parameters since their corresponding weight in the Fisher information matrix is very similar (especially in the vicinity of the resonance, where their amplitude is most significant).
+
+   As such, the free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$.
+
+  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
+  % Note that $\dc$ is a scaling factor for the FRF.
+  % Hence the results for different values of $\dc$ only differ by a scaling factor.
+  % So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.
 
@@
   Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:excitation:peakAmplitude} to study the effect of differently damped systems.
-
-  Since the damping influences the $3\unit{dB}$ bandwidths, it will become important when one has to determine the grid spacing $\alpha$.
+  However, do remember that $\abs{G(\wM)} = (2\damping\sqrt{1-\damping^2})^{-1}$ for the simplifications introduced above as in \eqref{eq:excitation:peakAmplitude}.
+
+  \subsection{Selection of the frequency grid spacing $\alpha$}
+  Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
   To deal with this, we introduce the normalized frequency ratio
@@
 
-  Instead of using \eqref{eq:excitation:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
+  Instead of using \eqref{eq:excitation:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we follow an equivalent approach that is more intuitive to interpret.
 
@@
   We normalize the root mean square (RMS) value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
-  The noise level is kept constant, which causes the signal-to-noise ratio (SNR) per excited line to drop for more finely spaced excitation signals.
+  The noise level is kept constant, which causes the \gls{SNR} per excited line to drop for more finely spaced excitation signals.
   % SNR correct: Pnoise ~ sE^2
@@
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
-  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked in such an FRF.
+  It is obvious that such an excitation signal will not perform well in most cases, as the resonance peak is very likely to be overlooked in such an \gls{FRF}.
 
@@
 
-  \subsection{Discussion} \label{sec:excitation:bestFrequencyResolution}
+  \subsection{Discussion} 
+  \label{sec:excitation:bestFrequencyResolution}
   As stated above, we start by evaluating the variance $\sigma_G\left( \wM\right)$ for a coarse frequency spacing $\tilde{\alpha} = 10$ for each of the prototype systems.
@@
 
-  Choosing a finer grid will not improve the estimated $G\left( \wM \right)$ significantly.
-  But, on the other hand, a coarser grid will significantly decrease the quality of the measurement.
-  A grid that is too coarse will overlook the resonance peak.
+  Choosing a finer grid will not improve the estimated $G\left( \wM \right)$ significantly, but will rather produce an \gls{FRF} where the \gls{SNR} per bin is decreased.
+  On the other hand, a coarser grid will significantly decrease the quality of the measurement as it overlooks the resonance peak.
   Hence little information can be extracted from such a measurement (i.e. the variance on the estimate will be large).
@@
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
-  \TODO{add formulas with cost function etc.}
+  % \TODO{add formulas with cost function etc.}
   To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
@@
   \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
-           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
-           \TODO{also with other excitation signals?}
+           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a logarithmic multisine.}%
   \label{fig:excitation:sumSys}

### 2016-02-24 ch02-qlogms/excitation-design.tex
Small changes to CH02

@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)} amongst others.
-
-  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.
+
+  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion~\citep{Oppenheim1983}.
   Therefore the performance of the proposed method is assessed on a prototype system of second order.
@@
     \end{equation}
-    was estimated using \texttt{elis} \citep{FDIDENT}.
+    was estimated using \texttt{elis}~\citep{FDIDENT}.
     The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.

### 2016-02-25 config/glossaries.inc.tex
Table with different stress test cases
Some work on init-vals
Corrections Johan: ch05 (part 1) + compu complex
Some changes from Tom
Improve CH02
Fix glspl on first use

@@
 plural={#3\glspluralsuffix},
-firstplural={#4~(#3\glspluralsuffix)},
+firstplural={#4\glspluralsuffix~(#3\glspluralsuffix)},
 #1}}
@@
 
+\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
+\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
+\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
+\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
 \newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
-\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
 \newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
+\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
 \newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
 \newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}
-\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
-\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
-\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
-\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
 
@@
 \newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
+\newsymbolglos{E-ll}{\ll}{is much smaller than \ldots}
+\newsymbolglos{E-gg}{\gg}{is much greater than \ldots}
 
@@
 
+\newacronym{ADC}{ADC}{analog-to-digital converter}
+
 \newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
 \newacronym{BK}{B\&K}{\bruelkjaer}
+\newacronym{BNC}{BNC}{Bayonet Neill-Concelman (connector)}
 \newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}
 
+\newacronym{CDF}{CDF}{cumulative distribution function}
+\newacronym{CPU}{CPU}{central processing unit}
 \newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
@@
 
+\newacronym{DAC}{DAC}{digital-to-analog converter}
 \newacronym{DC}{DC}{direct current (also: mean value)}
@@
 \newacronym{FFT}{FFT}{fast Fourier transform}
+\newacronym{FIR}{FIR}{finite impulse response}
 \newacronym{FRF}{FRF}{frequency response function}
@@
 
+\newacronym{NI}{NI}{National Instruments}
+
 \newacronym{OE}{OE}{output-error}
 
+\newacronym{PDF}{PDF}{probability distribution function}
 \newacronym{PSD}{PSD}{power spectral density}
 
+\newacronym{RAM}{RAM}{random-access memory}
 \newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
@@
 
+\newacronym{TF}{TF}{transfer function}
 \newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}

### 2016-02-25 ch02-qlogms/excitation-design.tex
Some minor changes to CH02

@@
 
-\item Robust input design one tries to make the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g. \citep{Rojas2007} and references therein. 
+\item Robust input design one tries to make the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007} and references therein. 
 While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
-E.g. the approach followed by \citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
+E.g. the approach followed by~\citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
 As such, this requires more advanced prior knowledge of the system to cope with the uncertainty of the prior knowledge.
@@
   In \secref{sec:excitation:inputDesign}, we first consider (optimal) input design for an example second-order system.
-  Next in \secref{}, \gls{LTI} systems are parametrized to facilitate the input design.
-  This will lead to signals with a $1/f$ power spectrum as in \secref{sec:excitation:logarithmic}.
-  In \secref{sec:excitation:multisine} a comparison of different discrete frequency grids is provided, this is afterwards related to the problem of generating a multisine signal with a $1/f$ power spectral density.
+  \secref{sec:excitation:logarithmic} expounds the use of a signal with $1/f$  power spectrum on some basic sub-systems.
+  Next, in \secref{sec:excitation:parametrization} \gls{LTI} systems are parametrized to facilitate a robust input design based on the observations of the preceding section.
+  In \secref{sec:excitation:multisine} a comparison of different discrete frequency grids is provided, this is related to the problem of generating a multisine signal with a $1/f$ power spectral density.
   Next, \secref{sec:excitation:optimAlpha} describes the selection of a suitable frequency ratio $\alpha$ for a logarithmically spaced grid such that constant model quality is obtained.
@@
 Alternatively, one could also construct a signal with power spectrum concentrated at discrete frequency lines.
-Such signals are elaborated in \secref{sec:excitation:method}.
+Such signals are elaborated in \secref{sec:excitation:multisine}.
 
@@
 equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
+\begin{assumption}
+
+\end{assumption}
 
@@
 \subsection{Equidistant (Linear) Grid Multisine}
-  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \citep{OppenheimDT,Mandal2007}. 
+  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical \gls{DFT} analysis \citep{OppenheimDT,Mandal2007}. 
   It allows to analyze periodic signals on an equidistant frequency grid very efficiently.
@@
   Using such linear grid, we can easily construct a representation of a multisine
-  in discrete time that is suited for use with the DFT by sampling at a given sampling rate $f_s$:
+  in discrete time that is suited for use with the \gls{DFT} by sampling at a given sampling rate $f_s$:
   \begin{equation}
@@
   \begin{example}
+    The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
+    As such, the effective frequency ratio $\alpha = \sqrt[F]{\frac{f_{\max}}{f_{\min}}}$ in this vector.
+  \end{example}
+  \begin{example}
     The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
@@
   \end{example}
-  \begin{example}
-    The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
-    As such, the effective frequency ratio $\alpha = \sqrt[F]{\frac{f_{\max}}{f_{\min}}}$ in this vector.
-  \end{example}
 
@@
   Especially for periodic measurements, this is a major downside since the period of such signal does not always exist (i.e. this leads to infinite measurement times).
-  It is therefore not practical to use a perfectly logarithmically spaced frequency grid as the \gls{DFT} or \gls{CZT}~\citep{Rabiner2004} explicitly rely on a commensurate frequency grid.
+  It is therefore not practical to use a perfectly logarithmically spaced frequency grid as the \gls{DFT} or \gls{CZT}~\citep{Rabiner2004} explicitly rely on an equidistantly-spaced frequency grid.
 
@@
   \end{equation}
-  where $\left[ \fMin{k}, \fMax{k} \right] $ denote the frequency range over which PSD of the pink noise is to be approximated by the power at frequency line $f_k$.
+  where $\left[ \fMin{k}, \fMax{k} \right] $ denote the frequency range over which \gls{PSD} of the pink noise is to be approximated by the power at frequency line $f_k$.
 
@@
   To determine a suitable value of the frequency spacing ratio $\alpha$ for the logarithmic and (compensated) quasi-logarithmic grid, we construct a logarithmic multisine signal in the frequency domain for a given frequency band (in this example, $\left[ 0.01 \unit{rad/s}, 100 \unit{rad/s}\right]$ was used).
-  In the previous section we saw that systems with equal damping and DC gain, will behave very similarly when excited by a log signal with spacing $\alpha$.
+  In the previous section we saw that systems with equal damping and \gls{DC} gain, will behave very similarly when excited by a log signal with spacing $\alpha$.
 
@@
   This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
-  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
+  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the \gls{FRF} at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
   Intuitively, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
@@
 
-  We normalize the root mean square (RMS) value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
+  We normalize the\gls{RMS} value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
   The noise level is kept constant, which causes the \gls{SNR} per excited line to drop for more finely spaced excitation signals.
@@
 
-  We then calculate the theoretical variance on the magnitude of the peak in the FRF ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
+  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
@@
              The full lines depict the variance for a coarsely spaced signal.
-             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:excitation:optimAlpha}).}
+             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
     \label{fig:excitation:worstCaseBeta}
@@
 
-  For a large peak amplitude of the FRF (low damping), the worst case increase (marked with a cross) is approximately centered around $\beta = 0.5$ (i.e. midway between the nearest excited lines).
+  For a large peak amplitude of the \gls{FRF} (low damping), the worst case increase (marked with a cross) is approximately centered around $\beta = 0.5$ (i.e.
+midway between the nearest excited lines).
   In systems with a higher damping, this symmetry is lost.
@@
 
-  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the FRF of the system are visualized in \figref{fig:excitation:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
+  To give a more intuitive feeling how the frequency spacing $\alpha$ and the system under test react, both the input spectrum and the \gls{FRF} of the system are visualized in \figref{fig:excitation:signalAndSystem} for the worst value of $\beta$ and the optimal frequency spacing $\alpha^{\star}$.
   The $3\unit{dB}$ bandwidth of the system is highlighted in gray together with the excited frequency lines that lie within that bandwidth.
@@
 \section{Simulations} \label{sec:excitation:simulation}
-In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:method}.
+In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
   \subsection{Setup}
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform \citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSystemCT}.
+  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSystemCT}.
 
@@
   For the quasi-log grid multisine, the compensated and pink quasi-log multisine, we chose a frequency ratio $\alpha = 1.05$.
-  According to \eqref{eq:excitation:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the FRF $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
-  Each of these signals is constructed to have an RMS value of $1$.
+  According to \eqref{eq:excitation:optimAlpha}, this frequency ratio is suited for second-order systems with a damping $\damping \geq 0.05$, or a peak amplitude of the \gls{FRF} $\abs{G(\wM)}$ less than approximately $20\unit{dB}$.
+  Each of these signals is constructed to have an \gls{RMS} value of $1$.
   The amplitude spectra of these signals are displayed in \figref{fig:excitation:freqGrids} for identical signal power.
@@
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
-  % \TODO{add formulas with cost function etc.}
+  %TODO: add formulas with cost function etc.
   To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
@@
     \input{\thisDir/figs/Sys02-4.tikz}
-    \caption[Simulated FRF and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
+    \caption[Simulated \gls{FRF} and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
     \label{fig:excitation:FRF1}
@@
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{\glspl{FRF} for different second order systems with constant damping
-             $\damping=0.2$ but different resonance frequencies. Comparison of the
-             variances around the respective resonance frequency for the different
-             excitation signals.}%
+    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.2$ for different excitation signals.]{%
+       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
+       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
     \label{fig:excitation:damping02}
@@
   In this set of simulations, we check this by repeating the previous set for such systems.
-  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the SNR of $20\unit{dB}$.
+  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the \gls{SNR} of $20\unit{dB}$.
   The corresponding results are shown in \figref{fig:excitation:damping005}.
@@
     \input{\thisDir/figs/damping005-cmp.tikz}
-    \caption[Simulated FRFs and their variances of systems with $\damping=0.05$ for different excitation signals.]{FRFs for different second order systems with constant damping
-             $\damping=0.05$ but different resonance frequencies. Comparison of the
-             variances around the respective resonance frequency for the different
-             excitation signals.}%
+    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
+    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
     \label{fig:excitation:damping005}
@@
     $R=50$ periods of the multisine were measured, from which the first period was discarded to suppress transient effects.
-    For each of the remaining periods, the FRF of the filter is calculated and its average $G\left(\omega \right)$ over the periods is calculated.
-    We also calculate the corresponding standard deviation $\sigma_G\left( \omega \right)$ of the FRF and normalize it for a single period of the excitation signal.
+    For each of the remaining periods, the \gls{FRF} of the filter is calculated and its average $G\left(\omega \right)$ over the periods is calculated.
+    We also calculate the corresponding standard deviation $\sigma_G\left( \omega \right)$ of the \gls{FRF} and normalize it for a single period of the excitation signal.
     We denote $G\left(\omega \right)$ the non-parametric FRF and $\sigma_G\left( \omega \right)$ its standard deviation, as these measures are determined completely nonparametrically from the measurements.
@@
     \subsection{Results}
-    In \figref{fig:excitation:measurements} the nonparametric FRF and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.
+    In \figref{fig:excitation:measurements} the nonparametric \gls{FRF} and the standard deviation of the corresponding parametric estimates are shown in a similar way as for the simulations in the previous section.
 
@@
 
-We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equidamped set of systems.
+We have also shown an effective way to choose the frequency spacing of a (quasi)-logarithmically spaced multisine for an equi-damped set of systems.
 The presented method allows to select a maximal value for the frequency ratio $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.

### 2016-02-25 config/styles.inc.tex
Clean up chapter 3
More work on derivatives of O(2) sys
Some small changes to graphics in CH02

@@
 \pgfplotsset{compat=newest}
+%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots
 
@@
 \pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}
+
+\pgfplotsset{legendAbovePlot/.style={legend style={at={(0.5,1.025)},anchor={south},nodes=right,legend columns=-1,font=\footnotesize,draw=none,/tikz/every even column/.append style={column sep=1em}}}}
 
@@
 
+\pgfplotsset{myDerivs/.style={color=black,solid,line width=1.0pt}}
+
 \pgfplotsset{degradationBox/.style={area legend,solid,draw=none,fill=TangoOrange1,opacity=0.7}}
@@
 \pgfplotsset{percentileLines/.style={black,dashed}}
+%NOTE: we need tikzset here, these styles are used on NODE (\in TikZ) instead of Pgfplots stuff
 \tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}
+
+\tikzset{numSlope/.style={anchor=center,align=center,font=\scriptsize}}
 

### 2016-02-25 ch02-qlogms/excitation-design.tex
Some changse to CH02

@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.
 
@@
 \begin{align}
-y(t) &= G(s,\theta) u(t) = \frac{1}{\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}u(t),
+y(t) 
+  &= 
+  G(s,\theta) u(t) 
+  = \frac{1}
+                {\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}
+      u(t),
 \label{eq:excitation:2ndOrderSys}
@@
 with parameters $\theta=[\wn\;\damping]^{\T}$. 
-The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$ and the $3\unit{dB}$ bandwidth of the system is $\wdB \isdef 2\damping\wn$.
-The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.
+The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$.
 
@@
           \max_{\omega} \left| G\left( \omega \right)  \right|
-        = \frac{\dc}
+        = \frac{1}
                {2 \damping \sqrt{1-\damping^2}}
@@
   \end{align}
+  The $3\unit{dB}$ bandwidth around this resonance peak is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.
 
@@
   G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
+\label{eq:excitation:secondOrderSubsystem}
 \end{equation}
@@
 \begin{assumption}
-
+\TODO{assume separation in freq}
 \end{assumption}
+
+\begin{assumption}
+\TODO{small damping}
+\end{assumption}
+
+\begin{remark}
+\TODO{leads to block-diagonal information matrix such that the variance of the FRF is decoupled near the resonances}
+\end{remark}
 
@@
 
-  In this chapter, random-phase multisines are used since this is a reasonable choice for systems that are dominantly linear~\TODO{ref: BLA}.
+  In this chapter, random-phase multisines are used since this is a reasonable choice for systems that are dominantly linear~\citep{Schoukens2004}.
   Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
@@
   \subsubsection{Exploiting the grid misalignment between the system and the grid}
-  Denote $G(\omega; \wn)$ a second-order system as in \eqref{eq:excitation:secondOrderSystemCT} with natural frequency $\wn$, damping ratio $\damping$ and \gls{DC} gain $\dc$.
-  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order system that shares the damping and \gls{DC} gain of the previous system but has a natural frequency $m\wn$.
-
-  If one calculates their FRFs by evaluating \eqref{eq:excitation:secondOrderSystemCT}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
-  Both FRFs share the same `shape', but are `located' at different frequencies.
+  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
+  Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order sub-system that shares the same parameters, except its natural frequency which is situated at $m\wn$.
+
+  If one calculates their \glspl{FRF} by evaluating \eqref{eq:excitation:secondOrderSubsystem}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
+  Both \glspl{FRF} share the same `shape', but are `located' at different frequencies.
 
@@
 
-  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
+  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSubsystem}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
   % Note that $\dc$ is a scaling factor for the FRF.
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSystemCT}.
+  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSubsystem}.
 

### 2016-02-25 ch02-qlogms/excitation-design.tex
Repeat assumption in system part

@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, vibration analysis and acoustics testing amongst others.
+%TODO{ meer referenties? }
 
@@
   To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
-  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.
+  Their frequency spacing is approximately logarithmic but nevertheless conforms to the linear frequency grid of the \gls{DFT}.
 
@@
 Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e.
-equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
+equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems under the assumptions given below.
+
 \begin{assumption}
-\TODO{assume separation in freq}
+The sub-systems in \eqref{eq:excitation:PFE} all are either lightly damped ($\damping \ll \sqrt{1/2}$) or are not of interest to the user.
 \end{assumption}
@@
 \begin{assumption}
-\TODO{small damping}
+The resonance frequencies $\wn[i]$ and $\wn[j]$ of all the different sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain.
 \end{assumption}
 
-\begin{remark}
-\TODO{leads to block-diagonal information matrix such that the variance of the FRF is decoupled near the resonances}
-\end{remark}
+Under these assumptions, the Fisher information matrix will be approximately a diagonal block matrix, where the $i^{\text{th}}$ block corresponds to the parameters $\left[\wn[i], \wz[i], \damping[i], \dc[i,1], \ldots, \dc[i,M_{2,i}] \right]$ of a particular sub-system.
+Using the same logic as in \secref{sec:excitation:ex:sumOfSecondOrderSipmle}, this means that the variance of the complete system is approximately equal to the variance obtained for each sub-system, due to the decoupling of the Fisher information matrix.
 

### 2016-02-25 ch05-initvals/initial-values.tex
small changes init-vals
ARduino/RasbPi removed

@@
 \begin{align}
-\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
+\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta,\sigma)^{-1}y - \log |\Sigma(\alpha,\beta,\sigma)| \text{,}
 \end{align}
@@
 The same was apparent from the quick trial we ran on \gls{LRM} starting values.
-As such, the use of \gls{LRM} over \gls{LPM} offers no advantage for generation initial estimates.
+As such, the use of \gls{LRM} over \gls{LPM} offers no advantage for generating initial estimates in the settings used in this chapter.
 \end{remark}
@@
 E.g.
-in embedded applications where computing power and physical power consumption are  restrained and which have been attracting a lot of attention in data science during the recent years\TODO{cite arduino, rasbpi}, it remains an important factor to account for.
+in the field of embedded processors, which has been attracting a lot of attention over the last few years leading to ``Internet of Things'', it remains an important factor since computing power and physical power consumption are still relatively scarce.
 

### 2016-02-28 ch04-lrmhinf/conference.tex
Import LRM Hinf files

% arara: pdflatex: { shell : yes }
% arara: bibtex
% arara: makeglossaries
% arara: pdflatex: { shell : yes, synctex : yes}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xspace}
smart
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{tangocolors}
\usepackage{tikz}
\usetikzlibrary{spy}
\usepackage{pgfplots}

\usepackage{color}
\newcommand{\EDIT}{\textcolor{red}{EDIT}}

\newlength\figureheight 
\newlength\figurewidth

%\usepackage{hyperref}

\input{definitions.inc.tex}
\input{blockdiag.inc.tex}
\input{styles.inc.tex}

\usepackage{graphicx}
\graphicspath{{./figures/}{.}{./tikz/}}

\newcommand{\TODO}[1]{ {\color{red} #1} }

\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

\begin{document}

\begin{frontmatter}

\title{Enhancing \Hinf{} Norm Estimation using Local LPM/LRM  Modeling: Applied to an AVIS\thanksref{thx}}

\thanks[thx]{This work is supported by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem), and by the Belgian Government through the Interuniversity Poles of Attraction (IAP VII-Dysco) Program, the Innovational Research Incentives Scheme under the VENI grant ``Precision Motion: Beyond the Nanometer'' (no. 13073) awarded by NWO (Netherlands Organization for Scientific Research) and STW (Dutch Science Foundation).}

\author[VUB]{Egon Geerardyn} 
\author[TUE]{Tom Oomen} 
\author[VUB]{Johan Schoukens}

\address[VUB]{ELEC Department, Vrije Universiteit Brussel, Brussels, Belgium. \\ (e-mails: \href{mailto:egon.geerardyn@vub.ac.be}{egon.geerardyn}, \href{mailto:johan.schoukens@vub.ac.be}{johan.schoukens} @vub.ac.be)}
\address[TUE]{Control System Technology Group, Mechanical Engineering Department, Technische Universiteit Eindhoven, Eindhoven, the Netherlands. (e-mail: \href{mailto:t.a.e.oomen@tue.nl}{t.a.e.oomen@tue.nl})}

\begin{keyword}
Frequency-response;
Uncertainty;
Norms;
Estimation;
Polynomials;
Signal Processing;
System Identification;
Robust Control.
\end{keyword}

\begin{abstract}~
Accurate uncertainty modeling is of key importance in high performance robust control design. 
The aim of this paper is to develop a new uncertainty modeling procedure that leads to enhanced accuracy for the $\mathcal{H}_\infty$ norm. 
A frequency response based approach is adopted. 
The key novelty of this paper is a new method to address the intergrid error using local parametric modeling methods. 
These local polynomial and rational models enhance the estimates at the discrete frequency grid.
Moreover, the presented methods are shown to enhance the intergrid error estimate.
This is illustrated using simulations and experiments on an industrial active vibration isolation system.
Compared to the local polynomial models, local rational models are able to handle lightly-damped resonances using far fewer data points, which means that measurement time can be kept short.
\end{abstract}

\end{frontmatter}

\section{Introduction}
\label{sec:Intro}

Robustness is of critical importance in feedback controlled systems, since feedback control can lead to performance degradation or even closed-loop instability. 
An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
The underlying feedback control principle is skyhook damping \citep{Karnopp1995}. However, the performance of skyhook damping is limited by high-frequent parasitic resonance phenomena. 
Such model uncertainties can be taken account explicitly in a robust control design, see, e.g., \citet{Zhang2005HybridAvis} and \citet{Chida2008} for approaches based on \Hinf{} optimization. 
However, the uncertainty estimation in these references is based on rough prior assumptions and hence inaccurate. 
On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
On the other hand, this can also lead to potentially conservative results, since if the estimated uncertainty is too large, the resulting controller is robust for an overly large class of candidate systems.

Several approaches have been developed in the literature to determine accurate bounds on the model uncertainty. First, model validation techniques have been developed, see \cite{Poolla1994} for time domain results and \cite{Smith1992} for frequency domain results. 
However, these results are typically overly optimistic, as is shown in \cite{Oomen2009UncEstim}. 
Second, model-error-modeling approaches based on parametric system identification with explicit characterization of bias and variance errors has been proposed in \cite{Ljung1999MEM}. 
An important aspect in these methods is that these require a significant user intervention in the model parameterization step and rely on assumptions that are asymptotic in the data length. 
Third, non-parametric identification approaches have been adopted, e.g., as in \Citet{vandeWal2002}, \Citet{deVries1994}. 
In \Citet{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. In \Citet{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case approach. 
However, such worst-case methods are well-known to be overly conservative \cite[Section 9.5.2]{Vinnicombe2001}. Fourth, recently a data-driven \Hinf{} norm estimation has been developed in \cite{Wahlberg2010} and \cite{Oomen2014ILH}. 
This method relies on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking intergrid errors into account.
Recent application of this method in \cite{Oomen2014ILH} has revealed that these iterative methods lead to much higher \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the intergrid error.

Although recently developed data-driven algorithms provide an accurate estimation of the \Hinf{} norm, these methods require a sequence of dedicated iterative experiments. 
In addition, the required number of experiments inflates in the multivariable case, see \cite{Oomen2014ILH}. 
The aim in this paper is to develop a method that provides accurate estimates of the \Hinf{} norm using data from a single experiment.

The main contribution of this paper is a new method for \Hinf{} norm estimation by exploiting recently developed \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} identification approaches.
These frequency-local models constitute a golden mean between simple non-parametric techniques (third approach) and a full parametric model (second approach). 
In particular, these methods lead to an improved frequency response estimation at the standard \gls{DFT} grid and provide an accurate estimation of the intergrid behavior.

\subsubsection{Contents}
\label{par:toc}
In \secref{sec:Problem}, the problem is formulated and illustrated on an example.
In \secref{sec:LocalModels}, the local modeling methods -- \gls{LPM} and \gls{LRM} are introduced, including the relevant notation.
The main contribution of this paper, which is a new approach for estimating \norm{\Delta} employing these local methods, is presented in \secref{sec:LPMHinf}. The example in \secref{sec:example} is revisited in \secref{sec:simulation}.
Afterwards, the technique is illustrated on measurement data of an \gls{AVIS} in \secref{sec:measurement}.
Finally, the obtained results and some challenges are discussed in \secref{sec:conclusion}.

\glsresetall % reset the usage of all abbreviations s.t. intro and body get the explanation at first use

\section{Problem Formulation}
\label{sec:Problem}
Robust control based on \Hinf{} optimization requires a nominal parametric model $\hat P$ and a bound on the model error $\Delta$. 
After the model $\hat P$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$. 
The \Hinf{} norm of the model error $\Delta$, i.e.
\begin{equation}
  \gamma = \infnorm{\Delta} \isdef \sup_{\omega} \abs{\Delta(\omega)}
  \label{eq:HinfNormSISO}
\end{equation}
for a \gls{SISO} system, or its weighted form $\infnorm{W \Delta V}$, is a measure that serves an important purpose in many robust control design methodologies that specifies the `size' of the model class for which a controller is to be designed \citep{Skogestad2005,Oomen2012SIRP}.
In this paper, the non-weighted \Hinf{} norm is considered to facilitate the presentation. 
The proposed approach can be adapted straightforwardly to incorporate the weighting filters $W$ and $V$.

In this paper, a frequency response-based approach is pursued. 
When only a limited amount of data is measured, the frequency resolution of the \gls{FRF} is limited and this can cause unreliable estimates of $\hinfnorm{\Delta}$ when resonances are present. 
The goal of this paper is to obtain an accurate estimate of $\hinfnorm{\Delta}$ using a finite amount of input-output data of a single (generic) experiment carried out on the set-up explained below.

\subsection{Set-up}
Consider the \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ that is shown in \figref{fig:DeltaOpenLoop}. 
The system is excited by input signal $u_{\Delta}(n)$ and the output $y_{\Delta}(n) = y_{\Delta0}(n) + v(n)$ where $v(n)$ is colored additive noise (i.e. $v(n) = H(q)e(n)$).
We measure $N$ samples of the input $u_{\Delta}$ and output $y_{\Delta}$ and try to determine both the \gls{FRF} of $\Delta$ and $\infnorm{\Delta}$ from this data.

It is emphasized that the presented results in this paper directly extend to closed-loop systems, as is explained in detail in \secref{sec:control}. 
\begin{figure}
  \centering
  \input{figures/deltaopenloop.tikz}
  \caption{Model-error system $\Delta$ in open loop.}
  \label{fig:DeltaOpenLoop}
\end{figure}

\subsection{Motivating Example}
\label{sec:example}
Consider the discrete time (model-error) system $\Delta$ (as in \figref{fig:DeltaOpenLoop}) as unmodeled dynamics:
\begin{equation}
  \Delta(z) = \frac{0.412 z + 0.405}{z^2 - 1.137 z + 0.954}
  \label{eq:O2sysDT}
  \text{,}
\end{equation}
with  sampling time $\Ts=\TsValue$, which is the zero-order-hold transformed second-order continuous time system.
The input $u_{\Delta}$ is white Guassian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_u}{\sigma_v}
  \label{eq:SNR}
\end{equation}
of $0\unit{dB}$ at the output is obtained.

Using classical \gls{SA} techniques -- i.e. splitting the signals into $N_S$ segments, applying a window before using the \gls{DFT} and averaging the \glspl{FRF} over the segments -- an \gls{FRF} of $\Delta$ can be obtained.
In \figref{fig:exampleFRF}, the ensuing \gls{FRF} for a Hann window and $N_S=1$ (no averaging) is shown together with those obtained using the local modeling methods introduced in this paper.
% persoon: Von Hann. Het venster wordt vaak gewoon Hann genoemd (of zelfs Hanning, maar die vind ik te verwarrend t.o.v. Hamming (naam & venster))

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.9\columnwidth}
  \setlength{\figureheight}{0.8\figurewidth}
  \input{figures/example-LRM-SNR1.tikz}
  \caption{Simulation example revealing that \glsfirst{SA} leads to an underestimate $\infnorm{\Delta}$. The proposed approach using \gls{LRM} significantly enhances the intergrid estimate as well as the at-grid estimate. For comparison, it is shown that \gls{LPM} does not perform well in this situation. The interpolated \gls{LRM} and true $\Delta$ almost coincide.}
  \label{fig:exampleFRF}
\end{figure}

From \figref{fig:exampleFRF} it shows that the \gls{SA} approach is not advisable to estimate $\infnorm{\Delta}$, since the frequency resolution is not dense enough to properly capture the actual resonance peak.
Increasing $N_S$ will reduce the variability of this estimate, at the cost of a decreased frequency resolution, so it is even more likely to `overlook' a resonance that is detectable from the data.

\subsection{Proposed approach}
The proposed in this paper is to use local parametric modeling methods, including \gls{LPM} and \gls{LRM} to
\begin{itemize}
\item enhance the \gls{FRF} estimate of $\Delta$ at the \gls{DFT} grid; and
\item exploit the local parametric models for accurate intergrid error estimation.
\end{itemize}
A key aspect herein is that the proposed approach does not require a global parametric model of the error system.

\section{Local Modeling Methods}
\label{sec:LocalModels}
In the following section the \gls{LPM} and \gls{LRM} are introduced and some practical consideration are given.
We first start from the global system equations and introduce the approximations made by the local modeling methods.

The system in \figref{fig:DeltaOpenLoop} can be described, for an infinitely long data record, by
\begin{equation}
  y_{\Delta}(n) = \Delta(q)u(n) + v(n) = \Delta(q)u(n) + H(q)e(n)
  \label{eq:sysDeltaInfData}
\end{equation}
where $n = \frac{t}{\Ts}$ is the time instant normalized by the sampling time $\Ts$, $q^{-1}$ is the lag operator and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For the practical situation where the data length is limited ($n \in \set{0,\ldots,N-1}$), \eqref{eq:sysDeltaInfData} has to include the influence of the system transient $t_{\Delta'}(n)$ and the noise transient $t_{H}(n)$:
\begin{equation}
    y_{\Delta}(n) = \Delta(q)u(n) + H(q)e(n) + \overbrace{t_{\Delta'}(n) + t_{H}(n)}^{t_{\Delta}(n)}
    \label{eq:sysDeltaFiniteData}
\end{equation}
where both transient contributions can be combined into a single transient term $t_{\Delta}(n)$.

By applying the \gls{DFT}
\begin{equation}
  X(k) = \frac{1}{\sqrt{N}} \sum_{n=0}^{N-1} x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
  \label{eq:DFT}
\end{equation} 
to both sides of \eqref{eq:sysDeltaFiniteData}, its frequency domain equivalent is obtained:
\begin{equation}
  Y_{\Delta}(k) = \Delta(\omega_k) U_{\Delta}(k) + T_{\Delta}(\omega_k) + V(k)
  \label{eq:sysDeltaFiniteDataFD}
\end{equation}
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$.

\subsection{The \glsentrydesc{LPM}}
\label{sec:LPM}
The \gls{LPM} revolves around the observation that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$ are smooth over the frequency, and as such can be approximated well by a Taylor series \citep{Schoukens2009LPM}.

In the \gls{LPM} these Taylor series are estimated by considering a local window ($r = -N_{W}, \ldots, N_{W}$) of $2N_{W} + 1$ lines around each frequency bin $k$:
\begin{align}
  \Delta(\omega_{k+r})     &\approx \delta_{0}(k) + \sum_{i=1}^{N_{B}} \delta_{i}(k) r^{i} &\isdef \ctr\Delta_{k}(r)\label{eq:LPMTaylorSystem} \\
  T_{\Delta}(\omega_{k+r}) &\approx t_{0}(k)      + \sum_{i=1}^{N_{T}} t_{i}(k)      r^{i} &\isdef \ctr{T}_{k}(r)\label{eq:LPMTaylorTransient}
\end{align}
where $\delta_{i}(k)$ and $t_{i}(k)$ are the (complex-valued) coefficients of the local polynomials $\ctr{\Delta}_{k}$ and $\ctr{T}_{k}$.
We denote these parameters associated with the \gls{LPM} as $\lpm{N_W,N_B,N_T}$.
Around each frequency bin $k$, $\delta_{i}(k)$ and $t_{i}(k)$ are obtained by fitting \eqref{eq:sysDeltaFiniteDataFD}  in least-squares sense with \eqref{eq:LPMTaylorSystem} and \eqref{eq:LPMTaylorTransient} substituted.
Thereby minimizing the local (linear least-squares) cost function 
\begin{equation}
  \sum_{r=-N_W}^{N_W} \left| Y_{\Delta}(k+r) - \ctr{\Delta}_{k}(r) U_{\Delta}(k+r) - \ctr{T}_{k}(r) \right|^2 \text{.}
  \label{eq:costLxM}
\end{equation}

At the edges  of the frequency grid (where $k \leq N_{W}$ or $k \geq \frac{N}{2} - N_{W}$), the local window index $r$ becomes degenerate.
This can be tackled by using e.g. an asymmetric window around $k$ as is done in \citep{Pintelon2010LPM1} or by exploiting the periodicity of the \gls{DFT} over the frequency \citep{McKelvey2012LRM}.
In this paper, we limit the notation to the `bulk' of the frequency grid to enhance the presentation of the formulas, and tacitly use the former approach in the actual computation.

Several remarks are appropriate.
\begin{itemize}
\item In typical applications of the \gls{LPM}, mainly the parameters $\delta_0(k)$ and $t_0(k)$ are of interest, as they are an improved estimate of the \gls{FRF} $\Delta(\omega_k)$ and the spectrum of the leakage $T_{\Delta}(\omega_k)$. 
In contrast, in the proposed approach in this paper, all $\delta$ parameters are of interest to interpolate the \gls{FRF} in-between the frequency grid.
\item The $\lpm{N_W,N_B,N_T}$ is used such that the local fit retains some degrees of freedoms: i.e. $2 N_W + 1  - (N_B + N_T + 2) > 0$.
\item The separation between $\Delta$ and $T_{\Delta}$ in \eqref{eq:sysDeltaFiniteDataFD} imposes requirements on the input signal. 
These requirements essentially imply that this is only possible if the input spectrum $\mat{U(\omega_{{k-N_{W}}}) & \cdots & U(\omega_{{k+N_{W}}})}$ is sufficiently `rough' over all frequencies. 
Importantly, this is the case for random noise and random phase multisines \citep{Schoukens2009LPM}.
\item Although the \gls{LPM} is illustrated for the \gls{SISO} generalized \gls{OE} case, it can be extended to work for \gls{MIMO} systems, with feedback and within the \gls{EIV} framework as is done in \citep{Pintelon2010LPM1,Pintelon2010LPM2}.
For a more detailed exposition of the \gls{LPM}, we also refer to \citep{Schoukens2006LPM, Schoukens2009LPM, Gevers2011LPM}.

\end{itemize}

\subsection{The \glsentrydesc{LRM}}
The \gls{LRM} builds upon the same basic idea of the \gls{LPM}, namely that the transfer function and transient contribution in \eqref{eq:sysDeltaFiniteDataFD} are `structured' over frequency.
Instead of using polynomials to capture the local structure, rational models are used as an approximation \citep{McKelvey2012LRM}.

In equation \eqref{eq:sysDeltaFiniteDataFD} that is fitted locally, the different factors $\Delta(\omega_k)$ and $T_{\Delta}(\omega_k)$ are expanded into rational functions instead of polynomials:
\begin{align}
  \Delta(\omega_{k+r})     &\approx \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} = \frac{B_k(r)}{A_k(r)} &\isdef \ctr\Delta_{k}(r)\label{eq:LRMTaylorSystem} \\
  T_{\Delta}(\omega_{k+r}) &\approx \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  =  \frac{T_k(r)}{A_k(r)}&\isdef \ctr{T}_{k}(r)\label{eq:LRMTaylorTransient}
  \text{.}
\end{align}

We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders and bandwidth defined above.
Similarly to the \gls{LPM}, these equation can be written in a matrix formulation for every frequency.
The resulting linear least-squares problem is closely related to the approach of \cite{Levy1959}.

\section{Local Models for \Hinf{} norm estimation}
\label{sec:LPMHinf}
In the previous section, the \gls{LPM} and \gls{LRM} have been shown to offer a way to estimate the error-system transfer function $\Delta$ with a reduced influence of the transient term $T_{\Delta}$. Essentially, this is achieved by approximating $\Delta$ and $T_{\Delta}$ around frequency bin $k$ by the low-order local models $\ctr{\Delta}_{k}$ and $\ctr{T}_{k}$, being either polynomial or rational functions.
In this section the use of the LPM and LRM is extended towards an approach that exploits these estimated local models to obtain a more fine-grained view of the error-system $\Delta$ specifically geared towards determining $\norm[\infty]{\Delta}$.

Remember that evaluating the local model $\ctr\Delta_{k}(r)$ corresponds to the value of $\Delta$'s \gls{FRF} in the frequency $\omega_{k+r}$ as captured by the local model around $\omega_{k}$.
To ease the notation, denote
\begin{equation}
  \Delta_{k}(\omega_{k+r}) \isdef \ctr{\Delta}_{k}(r) \text{.}
\end{equation}

As only a discrete grid of $\omega_k$s is available, the \Hinf{} norm \eqref{eq:HinfNormSISO} based on those measurements is
\begin{equation}
  \gamma_{\mathrm{FRF}} 
    \isdef \max_{\omega_k} \abs{\Delta\left( \omega_k \right)}  
    < \infnorm{\Delta} = \gamma
  \label{eq:gammaFRF}
\end{equation}
where the discrete grid entails in an underestimate of $\gamma$ due to the intergrid error, see also \figref{fig:exampleFRF}.

This raises the question what $\left|\Delta(\omega)\right|$ should be for any value $\omega$ not on the grid.
Using the \gls{LPM}/\gls{LRM}, we notice that for every $\omega$ within the excited frequency grid, two local models that are adjacent to $\omega$ can be found.
We denote those adjacent local models as $\Delta_{k_L(\omega)}$ and $\Delta_{k_R(\omega)}$.
Note that these models are based on the input/output spectra in the vicinity of $\omega$, hence due to their local validity additional information can be extracted regarding the value of $\Delta(\omega)$.
Since they are expressed in a parametric formulation (\eqref{eq:LPMTaylorSystem} for \gls{LPM}, \eqref{eq:LRMTaylorSystem} for \gls{LRM}), these can be evaluated locally for a continuous frequency range $\omega$.

With respect to estimating $\abs{\Delta}$ in the \Hinf{} norm \eqref{eq:HinfNormSISO}, this means that we have two candidate values that carry information: $\abs{\Delta_{k_L(\omega)}(\omega)}$ and $\abs{\Delta_{k_R(\omega)}(\omega)}$. In view of the worst-case nature of the \Hinf{} norm, a suitable solution is to use the largest value: $\max \set{\abs{\Delta_{k_L(\omega)}(\omega)}, \abs{\Delta_{k_R(\omega)}(\omega)}}$.

This leads to the following expression for estimating $\infnorm{\Delta}$ based on the local models:
\begin{equation}
  \widehat{\norm[]{\Delta_{\mathrm{LxM}}}}_{\infty} \isdef \max_{\omega} \max \set{\abs{\Delta_{k_L(\omega)}(\omega)}, \abs{\Delta_{k_R(\omega)}(\omega)}}
  \label{eq:gammaInterpolOptim}
  \text{.}
\end{equation}

Instead of formally optimizing \eqref{eq:gammaInterpolOptim} over the frequency $\omega$, this expression can be approximated arbitrarily well by evaluating the expression on a sufficiently dense frequency grid.
This is the approach we use in the implementation.

\section{Simulation Example Revisited}
\label{sec:simulation}
In order to get a clear idea of the performance of this method, we illustrate it applied to a simple discrete-time resonant second-order system.
This corresponds to the example given in Section~\ref{sec:example}, as depicted graphically in \figref{fig:DeltaOpenLoop}.

If we now take a closer look at the results for $\lrm{5,2,2,2}$ and $\lpm{3,2,2}$ for this example as shown in \figref{fig:exampleFRF}, we can see that the \gls{LPM} is not well-suited to operate in this setting.
Since there are very little points near the resonance, and a local polynomial model has a hard time capturing the resonant pole, the obtained \gls{FRF} estimate is unreliable. 
Consequently, the estimated \Hinf{} norm based on the interpolated local parametric model also is unreliable.
These observations are corroborated by the results in \citep{Schoukens2013LPMerror}, where it is shown that the \gls{LPM} requires seven points within the $3 \unit{dB}$ bandwidth of the resonance for a reliable estimate.

In sharp constrast, it can be observed in \figref{fig:exampleFRF} that the \gls{LRM} is able to model the resonance well and yields a great estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 25.68 \unit{dB}$ in the simulation, where the theoretical value is $\infnorm{\Delta} = 25.69 \unit{dB}$.
This can be attributed to the fact that the \gls{LRM} uses a rational model to locally approximate the actual $\Delta$, which means that the (resonant) pole is estimated and used to obtain a local estimate of $\hinfnorm{\Delta}$. These results confirm the advantages of the proposed method in uncertainty modeling for robust control design purposes.

\section{Application to an \glsentryname{AVIS}}
\label{sec:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
Moreover, the \gls{AVIS} is equipped with six geophones measuring the velocity and eight linear motors allow to actively compensate for vibration of the platform.

\begin{figure}
  \centering
  \includegraphics[width=0.85\columnwidth]{avis}
  \caption{\Glsfirst{AVIS}.}
  \label{fig:avis}
\end{figure}

To facilitate the presentation, only the vertical translation is considered, i.e., a \gls{SISO} error system is considered.

\subsection{Control Framework}
\label{sec:control}
The \gls{AVIS} should be in closed-loop for experimentation, see \figref{fig:tpc}. 
To implement the approach in this paper, a suitable uncertainty structure is employed that addresses the closed-loop operation of the system. 
In particular, the so-called dual-Youla framework is adopted \citep{Hansen1989,Anderson1998}.

\begin{figure}
 \centering
 \input{figures/tpcrobust.tikz}
 \caption{The considered feedback configuration $T(\ModelSet[],C)$ with controller $C$ and plant model set $\ModelSet[]$.}
 \label{fig:tpc}
\end{figure}

In particular, an experimental controller $C = C^{\mathrm{exp}} $ decomposed into a \gls{RCF}: $C = N_c D_c^{-1} $ is assumed available.
The plant model set $\mathcal{P}$ consists of a nominal model $\hat{P} = \hat{N} \hat{D}^{-1}$, also decomposed into an \gls{RCF}, and the model error $\Delta$ which has the focus in this paper.

This leads to a model set $\ModelSet[]$ (as shown in \figref{fig:dualYoula}) that is described by
\begin{equation}
  \ModelSet[] \isdef \set{\left. \frac{\hat{N} + D_c \Delta}{\hat{D} - N_c \Delta} \right| \hinfnorm{\Delta} \leq \gamma_{\ModelSet[]}  }
  \label{eq:dualYoulaModelSet}
  \text{,}
\end{equation}
where $\gamma_{\ModelSet[]}$ is the \Hinf{} norm that is to be estimated.
To do so, the signals $u_{\Delta}$ and $y_{\Delta}$ in \figref{fig:dualYoula} are required.
For the dual-Youla structure, it can be shown that $u_{\Delta}$ can be determined noiselessly and $y_{\Delta}$ is also accessible, but is disturbed by noise \citep{Anderson1998}.
This means that $\Delta$ in \figref{fig:dualYoula} can be estimated in an open-loop setting equivalent to \figref{fig:DeltaOpenLoop} in the problem formulation.

\begin{figure}
 \centering
 \input{figures/dualYoula.tikz}
 \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $C$, plant model set $\mathcal{P}$ and nominal plant model $\hat{P}$.}
 \label{fig:dualYoula}
\end{figure}

\subsubsection{Remark}
If we consider the robust control criterion
\begin{equation}
  J(P,C) \isdef \infnorm{W T(P,C) V}
  \label{eq:controlCrit}
\end{equation}
with weighting filters $W$ and $V$, well-chosen \glspl{RCF} of $\hat{P}$ and $C$ allows to connect the identification of $\hat{P}$ and the control performance \eqref{eq:controlCrit} as in \citep{Oomen2012SIRP}.
This is the approach we follow to construct $\hat{P}$ and all relevant \glspl{RCF}.

In that setting, it can be shown that when a robust controller $C^{\mathrm{R}}$ is designed given $\ModelSet[]$, both the plant identification and control design step aim to optimize the control criterion \eqref{eq:controlCrit}.
An interesting result is that the control performance of the actual plant $P_0$ can be upper-bounded:
\begin{equation}
  J(P_0,C^{\mathrm{R}}) \leq J(\hat{P}, C^{\mathrm{exp}}) + \gamma
  \text{,}
\end{equation}
which shows that in this setting the knowledge of $\gamma = \infnorm{\Delta}$ gives valuable control performance guarantees for the actual plant $P_0$.
This also shows that even for a weighted control criterion \eqref{eq:controlCrit}, there is no need to consider a weighted $\infnorm{W' \Delta V'}$ in the control design, when a suitable model structure is chosen.

\subsection{Results}
\label{sec:resultsAvis}
We determine a (global) control-relevant parametric model $\hat{P}$ directly in the coprime factorization described in the previous section. 
We measure the \gls{FRF} using a random phase quasi-logarithmic multisine \citep{Geerardyn2013TIM} applied to the $r_1$ input of the closed-loop system (keeping the set-point $r_2 =0$).
The experimental controller $C^{\mathrm{exp}}$ was designed using classical PID rules.
In this experiment five periods of the $65\,536$ points long multisine are measured at a sampling frequency of $1\unit{kHz}$.
Only $1550$ bins are excited in such a way that $\omega_k \approx 1.001 \omega_{k-1}$.
An eigth-order parametric model $\hat{P}$ (\figref{fig:avis-frf}) is fitted using the coprime factor identification described by \cite{Oomen2012SIRP}, which optimizes a criterion alike \eqref{eq:controlCrit}.
This $\Hinf$ criterion accentuates high gains in the misfit of the coprime factors, which explains the seemingly bad fit around $100 \unit{Hz}$ in \figref{fig:avis-frf}.
The chosen model provides a reasonable description of the plant, while  some unmodeled dynamics end up in $\Delta$.
Next, $\Delta$ is identified non-parametrically by applying the multisine and calculating the $u_{\Delta}$ and $y_{\Delta}$ given the estimated $\hat{P}$ and known $C^{\mathrm{exp}}$.

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.9\columnwidth}
    \setlength{\figureheight}{0.8\figurewidth}
    \input{figures/avis-frf.tikz}
 \caption{Measured \gls{FRF} (\ref{m2t:plantFRF}) and fitted model $\hat{P}$ (\ref{m2t:plantModel}) of the \gls{AVIS}.}
 \label{fig:avis-frf}
\end{figure}

To test the methods on a low-resolution frequency grid, we use only one out of four excited bins to estimate the $\lrm{6,2,2,2}$ of $\Delta$ and apply the proposed interpolation \eqref{eq:gammaInterpolOptim}.
The \gls{LRM} applied to the full frequency resolution data is used as validation for the method.
The results are shown in \figref{fig:avisMeas} for the whole frequency band and \figref{fig:avisMeasZoom} for a frequency range where two resonances are observed and where the results of $\lpm{4,2,2}$ are shown for the sparse frequency grid.
With the proposed method in mind, it is more informative to observe how the peak values of the different parasitic resonances in $\Delta$ are handled, as these affect $\hinfnorm{\Delta}$, instead of focusing on the global value of $\hinfnorm{\Delta}$ as sole criterion.

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.9\columnwidth}
    \setlength{\figureheight}{0.8\figurewidth}
    \input{figures/avis-delta-full.tikz}
 \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
 \label{fig:avisMeas}
\end{figure}

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.9\columnwidth}
    \setlength{\figureheight}{0.8\figurewidth}
   \input{figures/avis4.tikz}
 \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. Clearly, the \gls{LRM} leads to a higher peak value, especially at $328\unit{Hz}$. The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid, which reveals excellent interpolation properties. }
 \label{fig:avisMeasZoom}
\end{figure}

There are two important aspects that we examine for the studied methods.
First, it should be asserted how the interpolation compares with the validation data.
Secondly, the estimated peak values of the individual resonances are of interest to determine whether an improved $\hinfnorm{\Delta}$ could be obtained by inspecting the intergrid behavior.

\subsubsection{Interpolation performance}
In \figref{fig:avisMeas} we can see that the estimation and validation data for \gls{LRM} are generally in agreement.
By having a look at \figref{fig:avisMeasZoom}, we can see that around both resonances the \gls{LRM} interpolation method agrees really well with the validation data.
In that frequency range, the relative difference between the interpolated data and the validation data is about $2\%$.
For the \gls{LPM} data points on the other hand, it can be seen that the \gls{LPM} estimates are validated in the `flat' regions of the \gls{FRF}.
Near the resonances the \gls{LPM} performs unreliably as a zero-only model (i.e. a polynomial) is not flexible enough to describe a lightly-damped pole well in the local bandwidth.
This drawback can be mitigated by increasing the frequency resolution \citep{Schoukens2013LPMerror}, thereby increasing the measurement time considerably.
Interpolation using the \gls{LRM} approximates the actual $\Delta$ very well and might also provide a better estimate of the peak values.

\subsubsection{Estimate of the peak value}
We examine both resonances in \figref{fig:avisMeasZoom} to inspect the peak values in more detail.
For the resonance near $296\unit{Hz}$ (in the left call-out), only a modest increase of $1.4\unit{dB}$ of the peak value to $-14.0 \unit{dB}$ is obtained using the interpolation.
This can be attributed to the nearest on-grid data point where $\abs{\Delta} = -15.3 \unit{dB}$, which is also observed in the validation data.

The other resonance at $328\unit{Hz}$ in the right call-out, however, shows a more substantial improvement.
There, it can be observed that peak is estimated at $-2.5\unit{dB}$ using the \gls{LRM} with interpolation.
In the validation data, the nearest point shows an amplitude of $-3.2\unit{dB}$ (about $8\%$ difference), which shows that the estimated peak agrees well with the validation data.
Moreover, if we compare the estimated peak value in that resonance with the nearest data point in the estimation data, we get an idea of the improvement that is obtained by interpolation.
The nearest on-grid data point has an amplitude of $-9.9 \unit{dB}$; so this amounts to an improvement of $7.4\unit{dB}$ for the peak value by means of interpolation of exactly the same data record.

This suggests that the local rational models with interpolation are a very reasonable approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.

\section{Conclusion and further research}
\label{sec:conclusion}
High performance, non-conservative robust control design requires an accurate estimate of the \Hinf\ norm of the model error $\Delta$.
In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\norm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models. 
In addition, it is illustrated that the \gls{LPM} is not flexible enough to handle sharp resonances using very few data points.
The \gls{LRM} on the other hand is better suited for that case and is therefore the advisable solution to obtain a better estimate.
The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation was able to retrieve the true $\Hinf{}$ norm.
Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$.
Furthermore, the results are validated by a detailed validation measurement. 
Ongoing research focuses on extending the technique to \gls{MIMO} systems and the study of its stochastic properties.

%TODO: acknowledgments reviewers

\bibliography{biblio/references,biblio/ownWork} 
%\bibliographystyle{ifacconf}

\end{document}

### 2016-02-28 ch04-lrmhinf/paper.tex
Import LRM Hinf files

% \renewcommand{\glsgroupskip}{}
% \glsdisablehyper

\input{\thisDir/styles.inc.tex}

\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

% \section{Introduction}
% \label{sec:Intro}

% Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability. 
% An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
% The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
% However, the performance of skyhook damping is limited by high-frequent parasitic resonance phenomena. 
% Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
% However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
% On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
% On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.

% Several approaches have been developed to determine bounds on the model uncertainty. First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
% However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
% Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
% Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
% In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
% In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
% However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
% Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
% These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
% A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
% Unfortunately, these methods require a sequence of dedicated iterative experiments.
% This increases the measurement time significantly, especially for \gls{MIMO} plants.
% When measurement time is expensive, this is a severe impediment.

% Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
% The aim of the present paper is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
% The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} as introduced in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
% In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the peak value, as is required for the $\Hinf{}$ norm. 
% The performance of these local parametric models with respect to robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.

% \vspace{-1em}
% \paragraph*{Outline}
% \label{par:toc}
% The problem is formulated in \secref{sec:Problem}.
% In \secref{sec:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
% In \secref{sec:simulation} the method is illustrated on simulations, and the required measurement time is determined.
% The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:measurement}.
% Finally, the results and some challenges are discussed in \secref{sec:conclusion}.

% \glsresetall % reset the usage of all abbreviations s.t. intro and body get the explanation at first use

% \section{Problem Formulation}
% \label{sec:Problem}
% Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
% After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
% The \Hinf{} norm of the error system $\Delta$, i.e.
% \begin{equation}
%   \gamma 
%      = 
%        \infnorm{\Delta} 
%     \isdef 
%        \sup_{\omega} 
%          \abs{\Delta(\omega)}
%   \label{eq:HinfNormSISO}
% \end{equation}
% for a stable \gls{SISO} system, or its weighted form $\infnorm{W \Delta V}$, is a measure that serves an important purpose in many robust control design methodologies that specifies the `size' of the model class for which a controller is to be designed~\citep{Skogestad2005}.

% To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
% $ \omega_{\star} 
%      \isdef 
%        \arg
%          \sup_{\omega} 
%            \abs{\Delta(\omega)}
%   \text{.}
%   \label{eq:omega-star}
% $
% However, in a finite measurement time, non-parametric approaches only allow access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
% As such, \eqref{eq:HinfNormSISO} can be rewritten as
% \begin{equation}
%   \gamma \isdef \sup_{\omega} \abs{\Delta(\omega)}
%          = \sup 
%              \set{
%                 \ezbrace{\sup_{\omega \in \DFTGrid  } \abs{\Delta(\omega)}}{\gamma_{\mathrm{FRF}}}
%                 \;,\;
%                 \ezbrace{
%                 \sup_{\omega \in \InterGrid} \abs{\Delta(\omega)}}{\gamma_{\mathrm{IG}}}}
%   \label{eq:gamma-split-grid}
% \end{equation}
% where $\Omega \isdef \openInterval{0}{\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
% Two cases can be distinguished:
% \begin{enumerate}
%   \item $\omega_{\star} \in \DFTGrid$ such that $\abs{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
%   \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\abs{\Delta(\omega_{\star})}  = \gamma = \gamma_{\mathrm{IG}}$ is determined by the inter-grid behavior.
% \end{enumerate}
% The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
% Its expected value over different realizations of the input signal $\expectedValue{\gamma_{\mathrm{FRF}}} \leq \gamma$ due to the limited frequency resolution.
% Such an underestimate may lead to overly optimistic controller designs.

% The main contribution of this paper is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
% Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.

% \subsection{Set-up}
% \TODO{overgang $\Delta(q)$ naar output-error}

% Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
% For an infinitely long data record, this can be described in the time-domain as
% \begin{equation}
%   y_{\Delta}(n) 
%     = 
%       y_{\Delta0}
%       + v(n) 
%     = 
%       \Delta(q)u_{\Delta}(n) 
%       + H(q)e(n)
%   \label{eq:sysDeltaInfData}
% \end{equation}
% where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
% For a limited data record ($n \in \set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
% \begin{equation}
%     y_{\Delta}(n) 
%       = 
%         \Delta(q)u(n) 
%         + H(q)e(n) 
%         + t_{\Delta}(n)
%     \text{.}
%     \label{eq:sysDeltaFiniteData}
% \end{equation}
% By applying the \gls{DFT}
% \begin{equation}
%   X(k) 
%        = 
%          \frac{1}
%               {\sqrt{N}} 
%          \sum_{n=0}^{N-1} 
%             x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
%          \quad   
%          \forall k \in \mathbb{Z}
%   \label{eq:DFT}
% \end{equation} 
% to both sides of~\eqref{eq:sysDeltaFiniteData}, one obtains:
% \begin{equation}
%   Y_{\Delta}(k) 
%                 = 
%                   \Delta(\omega_k) U_{\Delta}(k) 
%                   + T_{\Delta}(\omega_k) 
%                   + V(k) 
%   \text{.}
%   \label{eq:sysDeltaFiniteDataFD}
% \end{equation}
% The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

% The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:control}.
% The results in this paper are presented in discrete time, but the extension to the continuous time case is straightforward.

% \section{\Hinf{} Norm Estimation Procedure}
% \label{sec:LPMHinf}
% To estimate $\gamma_{\mathrm{IG}}$, we propose to identify local parametric models in the frequency domain.
% The frequency axis is partitioned into continuous segments $\Omega_k \isdef \openInterval{ \omega_{k-1} }{ \omega_{k+1} }$ in view of the local validity of the local models.
% In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
% \begin{equation}
%   \gamma_{\mathrm{IG}} = 
%     \sup \set{ \left. 
%                 \sup_{\omega \in \Omega_k} \abs{\LocalModel{\Delta}_k(\omega)}
%                 \right|
%                 k = 1,\ldots,N-1
%                 }
%    \label{eq:gamma-inter-grid}
% \end{equation}
% where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k$th) frequency $\omega_k$.
% An example of such local models is shown in \figref{fig:interpol-quantities}.
% Two alternative methods allow to evaluate~\eqref{eq:gamma-inter-grid} practically.

% \begin{figure}
%   \centering
%   \setlength{\figurewidth}{0.8\columnwidth}
%   \setlength{\figureheight}{0.68\figurewidth}
%   \input{\thisDir/figs/interpolation-show.tikz}
%   \caption{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
%   The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
% \label{fig:interpol-quantities}
% \end{figure}

% \vspace{-3em}
% \paragraph*{Direct method}
% % \subsubsection{Direct method}
% One can implement the definition~\eqref{eq:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
% Hence, it boils down to solving the optimization problems
% \begin{equation}
%   % \gamma_{\mathrm{IG}}(k) 
%   % = 
%       \max_{\omega \in \Omega_k} 
%       \abs{\LocalModel{\Delta}_k(\omega)}
%       \label{eq:gamma-direct}
% \end{equation}
% for $k \in \set{1,\ldots,N-1}$.
% These are tractable since $\omega$ is one-dimensional and restricted to the intervals $\Omega_k$.
% Unfortunately, this approach offers no insight in the behavior of $\abs{\Delta(\omega)}$, e.g. around the peak amplitude.

% \vspace{-2em}
% \paragraph*{Interpolation method}
% To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
% It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\abs{\omega_k-\omega}$ is small.
% To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
% \begin{align}
%   k_L(\omega) & 
%                 \isdef
%                   \max
%                   \set{k 
%                     \given{
%                       \omega_k \in \DFTGrid, 
%                       \omega_k \leq \omega}
%                   }\\
%   k_R(\omega) & 
%                 \isdef
%                   \min
%                   \set{k 
%                     \given{
%                       \omega_k \in \DFTGrid, 
%                       \omega_k \geq \omega}
%                   }
%   \text{.}
%   \label{eq:kL-kR-indexing-functions}
% \end{align}
% Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
% In view of obtaining the maximum amplitude, these are `interpolated' to obtain a single estimate:
% \begin{equation}
%   \abs{\Delta_{\mathrm{LRM}}(\omega)}
%     \isdef
%     \sup \set{
%        \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
%         \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
%     }
%     \label{eq:DeltaLRMInterpolation}
% \end{equation}
% by retaining the largest both.
% It follows that
% \begin{align}
%   \widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty} 
%     & \isdef
%     \sup_{\omega\in\Omega}
%     \abs{\Delta_{\mathrm{LRM}}(\omega)} \\
%    &  =
%       \sup_{\omega\in\Omega} \; 
%       \sup \set{
%                  \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
%                  \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
%   \label{eq:gammaInterpolOptim}
%   \text{.}
% \end{align}

% \vspace{-2em}
% \paragraph*{Remarks:}
% The optimization problems~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} can, e.g. be solved by griding the frequency $\omega$.
% The peak amplitudes obtained using~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
% $% \begin{equation}
%   \Omega_k = \set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
% $ % \end{equation}
% for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
% In \figref{fig:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.

% \subsection{The \glsentrydesc{LRM}}
% \label{sec:LRM}
% The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
% The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:sysDeltaFiniteDataFD} are smooth functions of the frequency.
% As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
% \begin{align}
%   \Delta(\omega_{k+r})     
%     &\approx 
%         \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
%       = 
%         \frac{B_k(r)}{A_k(r)} 
%       \isdef 
%         \LocalModel{\Delta}_{k}(\omega_{k+r})
%       \label{eq:LRMTaylorSystem} \\
%   T_{\Delta}(\omega_{k+r}) 
%     &\approx 
%         \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
%       = 
%         \frac{T_k'(r)}{A_k(r)} 
%       \isdef 
%         \LocalModel{T}_{k}(\omega_{k+r})
%   \label{eq:LRMTaylorTransient}
%   \text{.}
% \end{align}
% Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
% This yields
% \begin{equation}
%   Y_{\Delta}(k+r) 
%                  \approx
%                     \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
%                     + T_{\Delta}(\omega_{k+r}) 
%     \quad
%     \forall r \in \LocalWindow
%     \text{.}
%     \label{eq:LocalWindowSpectra}
% \end{equation}
% By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
% \begin{align}
%   Y_{\Delta}(k+r) 
%                   & \approx
%                     \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
%                     + \LocalModel{T}_k(\omega_{k+r}) 
%                     & \forall r \in \LocalWindow \\
%                   & = 
%                     \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
%                     + 
%                     \frac{T'_k(r)}{A_k(r)} 
%                     & \forall r \in \LocalWindow
%     \text{.}
%     \label{eq:LocalWindowSpectraLRM}
% \end{align}
% To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
% By doing so, the local linear-least-squares cost function
% \begin{equation}
%   \sum_{r=-N_W}^{N_W} 
%   \left| 
%     A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
%   \right|^2
%   \label{eq:localCostLRM}
% \end{equation}
%  around each bin $k$ can be constructed.
% We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
% For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.

% For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM}.

% \section{Simulation}
% \label{sec:simulation}
% To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
% The behavior of these simpler systems then allows to predict the behavior for these more complex systems.

% Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems.
% As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g. mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
% To estimate $\norm{\Delta}$ mainly the resonant sub-systems are of interest.
% Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
% This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
% By normalizing the conclusions for the time constant $\tau$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\xi$.
% Specifically, the system's $\tau \isdef (\xi\omega_{\mathrm{n}})^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\xi$ is the relative damping and $\omega_{\mathrm{n}}$ the undamped natural frequency.

% \subsection{A concrete simulation}
% Consider a discrete time system $\Delta$ (see \figref{fig:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
% \begin{equation}
%   \Delta(z) 
%     =  \frac{0.45373 z + 0.44752}
%             {z^2 - 1.0595 z + 0.96079}
%   \label{eq:O2sysDT}
%   \text{,}
% \end{equation}
% which has $\tau = 50 \unit{samples}$ (i.e. $\xi=0.02$ and $\omega_{\mathrm{n}} = 1 \unit{rad/S}$).
% The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
% \begin{equation}
%   \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
%               {\sqrt{\inv{N}\sum_n v^2(n) }}
%        = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
%        \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
%   \label{eq:SNR}
% \end{equation}
% of $10$ is obtained.

% Classical \gls{SA} techniques~\citep{Bendat1980} can estimate the \gls{FRF} of $\Delta$.
% This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
% By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
% In this paper a Hann window and $N_S=1$ are used.
% Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).

% \figref{fig:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
% The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to linear models ($N_B=1$). 
% Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.

% \begin{figure}
%   \centering
%   \setlength{\figurewidth}{0.75\columnwidth}
%   \setlength{\figureheight}{0.68\figurewidth}
%   \input{\thisDir/figs/example-both.tikz}
%   %\input{\thisDir/figs/example-LRM-SNR1.tikz}
%   \caption{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
%   Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
%   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
%   Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
%   \label{fig:exampleIntergrid}
% \end{figure}

% It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
% Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
% The \gls{LPM}, on the other hand, does not provide a reliable estimate.

% \subsection{Study of the experiment length}
% Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
% In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

% We simulate the system \eqref{eq:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
% To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:LPMHinf}.
% The values of $N \in \closedInterval{35}{16 000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
% These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
% The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:MC-run-length}.

% \begin{figure}
%   \centering
%   \setlength{\figurewidth}{0.75\columnwidth}
%   \setlength{\figureheight}{0.68\figurewidth}
%   \input{\thisDir/figs/MC-runlength.tikz}
%   %\input{figures/runLength.tikz}
%   \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\tau$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
%   However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \tau$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are mostly due to the noise.
%   }
% \label{fig:MC-run-length}
% \end{figure}

% It can be seen in \figref{fig:MC-run-length} that $N \geq 20\tau$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e. $\expectedValue{\gamma_{\mathrm{FRF}}} \approx \gamma$.
% Starting from about $N=4 \text{ to } 5\tau$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
% For long experiments $(N \to \infty)$, the true $\norm{\Delta}$ is recovered.
% Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.

% \section{Application to an \glsentryname{AVIS}}
% \label{sec:measurement}
% The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:avis}.
% The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
% Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
% To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.

% \subsection{Measurement \& control framework}
% \label{sec:control}
% The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:tpc}) with $r_2 = 0$.
% The controller $\Controller=\experimental\Controller$  stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
% The $r_1$ input consists of five periods of a random phase multisine~\citep{Geerardyn2013TIM} of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.

% \begin{figure}
%  \centering
%  \input{\thisDir/figs/tpcrobust.tikz}
%  \caption{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
%  \label{fig:tpc}
% \end{figure}

% \begin{figure}
%  \centering
%  \input{\thisDir/figs/dualYoula.tikz}
%  \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
% \label{fig:dualYoula}
% \end{figure}

% The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
% \begin{equation}
%   \ModelSet[] 
%     \isdef 
%       \set{
%           \left. 
%             \frac{\hat{N} + D_c \Delta}
%                  {\hat{D} - N_c \Delta} 
%           \right| 
%             \hinfnorm{\Delta} \leq \gamma
%         }
%   \label{eq:dualYoulaModelSet}
%   \text{,}
% \end{equation}
% where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:dualYoula}).
% To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:dualYoula} are required.
% These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
% In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:LPMHinf} applies.

% The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
% In view of the robust control criterion
% \begin{equation}
%   \Crit(\Plant,\Controller) 
%     \isdef 
%       \infnorm{W \ClosedLoop{\Plant,\Controller} V}
%   \label{eq:controlCrit}
%   \text{,}
% \end{equation}
% the \glspl{RCF} are constructed such that
% $
%   \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
%   \leq
%   \Crit \left( \estimated\Plant, \experimental\Controller \right)
%   + \gamma
% $
% where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
% % Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
% I.e. even for a weighted control criterion \eqref{eq:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
% In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:avis-frf}) is estimated.
% Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:avisMeas}).

% \begin{figure}
%  \centering
%     \setlength{\figurewidth}{0.75\columnwidth}
%     \setlength{\figureheight}{0.68\figurewidth}
%     \input{\thisDir/figs/avis-frf.tikz}
%  \caption{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
%  \label{fig:avis-frf}
%  \label{fig:avis}
% \end{figure}

% \subsection{Results}
% \label{sec:resultsAvis}
% To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
% The full dataset that includes bins not used in the estimation is used to validate the interpolation results.

% The measured $\Delta$ is shown in \figref{fig:avisMeas} for the whole frequency band and \figref{fig:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
% Two aspects of the proposed method are examined.
% First, the interpolation results for a continuous frequency range are validated.
% Second, the peak amplitudes of $\Delta(\omega)$ are inspected as these are  indicators for $\infnorm{\Delta}$.

% \begin{figure}
%  \centering
%     \setlength{\figurewidth}{0.75\columnwidth}
%     \setlength{\figureheight}{0.68\figurewidth}
%     \input{\thisDir/figs/avis-delta-full.tikz}
%  \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
% \label{fig:avisMeas}
% \end{figure}

% \begin{figure}
%  \centering
%     \setlength{\figurewidth}{0.75\columnwidth}
%     \setlength{\figureheight}{0.68\figurewidth}
%    \input{\thisDir/figs/avis4.tikz}
%  \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation. Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$. The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
% \label{fig:avisMeasZoom}
% \end{figure}

% \vspace{-2em}
% \paragraph*{Interpolation performance}
% \label{sec:avis-interpol}
% \figref{fig:avisMeas} and \figref{fig:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
% In the frequency range shown in \figref{fig:avisMeasZoom}, the relative difference between both is at most $2\%$.

% \vspace{-2em}
% \paragraph*{Peak value estimates}
% \label{sec:avis-peak-value}
% Near $296\unit{Hz}$, a modest improvement of the peak estimate from $-15.3 \unit{dB}$ (at-grid) to $-14.0 \unit{dB}$ is obtained by the interpolation.
% The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
% The proposed method \eqref{eq:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
% $\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
% This peak agrees well with the validation data, where the nearest (at-grid) value has an amplitude of $-3.2\unit{dB}$ (i.e. $8\%$ difference).

% This suggests that the local rational models with interpolation are a very good approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.

% \section{Conclusion and Further Research}
% \label{sec:conclusion}
% A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
% In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\norm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
% It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\norm{\Delta}$.
% The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
% It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
% Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
% Furthermore, the results are validated by a detailed validation measurement.
% Ongoing research focuses on extending the technique to \gls{MIMO} systems and the study of its stochastic properties.

### 2016-02-28 ch04-lrmhinf/styles.inc.tex
Import LRM Hinf files

\definecolor{LRM}{named}{TangoScarletRed3}
\definecolor{LPM}{named}{TangoSkyBlue2}
\definecolor{SA}{named}{TangoChameleon2}
\definecolor{truesys}{named}{TangoAluminium4}
\definecolor{validation}{named}{TangoChameleon2}

\definecolor{LPMshade}{named}{TangoSkyBlue1}
\definecolor{LRMshade}{named}{TangoScarletRed1}
\definecolor{refColor}{named}{TangoAluminium6}

\definecolor{frf}{named}{TangoButter3}
\definecolor{param}{named}{TangoScarletRed2}

\pgfplotsset{egon/.style={line join=round}}

\pgfplotsset{truesys/.style={egon,color=truesys,densely dotted,line width=1.5pt}}

\pgfplotsset{hinfnorm/.style={egon,dashed}}
\pgfplotsset{interpol/.style={egon,sharp plot,solid,mark options={solid}}}

\pgfplotsset{LRMgrid/.style={color=LRM,mark size=1.5pt,only marks,mark=square*,mark options={solid}}}
\pgfplotsset{LPMgrid/.style={color=LPM,mark size=1.5pt,only marks,mark=*,mark options={solid}}}
\pgfplotsset{SAgrid/.style={color=SA,densely dotted,solid,mark=triangle*,mark size=1.5pt,mark options={solid}}}

\pgfplotsset{smallmarkers/.append style={mark size=0.5pt}} %TODO: replace smallmarkers -> medsmallmarkers

\pgfplotsset{frf/.style={line join=round,color=frf,solid,mark options={solid},mark size=0.2pt}} %TODO: replace

\pgfplotsset{paramPhat/.style={egon,color=param,solid,line width=1.2pt}}

\pgfplotsset{validation/.style={color=validation,densely dotted,mark=diamond*,mark size=1pt,mark options={solid}}}

\pgfplotsset{shaded/.style={opacity=0.5,area legend,solid}}

\pgfplotsset{LPMshade/.style={shaded,fill=LPMshade,draw=LPM}}
\pgfplotsset{LRMshade/.style={shaded,fill=LRMshade,draw=LRM}}

\pgfplotsset{reference/.append style={color=refColor,densely dotted,line width=0.75pt}}
\pgfplotsset{gammafrf/.style={color=black,mark=pentagon,mark options={solid}}}

### 2016-02-28 config/styles.inc.tex
Import LRM Hinf files

@@
 \pgfplotsset{every tick label/.append style={font=\footnotesize}}
-\pgfplotsset{every axis title/.append style={font=\footnotesize}}
+\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
 \pgfplotsset{every axis post/.style={unbounded coords=jump}}
-\pgfplotsset{every axis title/.append style={at={(0.5,0.95)}}}
 
@@
 
+\definecolor{model}{named}{blue}
+\definecolor{truesys}{named}{TangoAluminium5}
+
+\definecolor{linms}{named}{TangoScarletRed3}
+\definecolor{logms}{named}{TangoChameleon2}
+\definecolor{qlogms}{named}{TangoPlum3}
+\definecolor{clogms}{named}{TangoSkyBlue3}
+\definecolor{plogms}{named}{black}
+
+\definecolor{sigmalinms}{named}{linms}
+\definecolor{sigmaqlogms}{named}{qlogms}
+\definecolor{sigmaclogms}{named}{clogms}
+
+\definecolor{biaslinms}{named}{TangoScarletRed1}
+\definecolor{biasqlogms}{named}{TangoPlum1}
+\definecolor{biasclogms}{named}{TangoSkyBlue1}
+
+\definecolor{dbacolor}{named}{TangoScarletRed2}
+\definecolor{dbbcolor}{named}{TangoSkyBlue2}
+\definecolor{dbccolor}{named}{TangoChameleon2}
+\definecolor{dbdcolor}{named}{TangoOrange2}
+
 \definecolor{linms}{named}{TangoScarletRed3}
@@
   \definecolor{dbdcolor}{named}{TangoOrange2}
+
+\definecolor{first}{named}{TangoScarletRed2}
+\definecolor{second}{named}{TangoOrange2}
+\definecolor{third}{named}{TangoChameleon3}
+\definecolor{fourth}{named}{TangoSkyBlue3}
+\definecolor{fifth}{named}{TangoPlum1}
+\definecolor{sixth}{named}{TangoChocolate2}
 
@@
 \pgfplotsset{linrect/.style={fill=linms,draw=linms,line width=1pt}}
-
-\definecolor{model}{named}{blue}
-\definecolor{truesys}{named}{TangoAluminium5}
-
-\definecolor{linms}{named}{TangoScarletRed3}
-\definecolor{logms}{named}{TangoChameleon2}
-\definecolor{qlogms}{named}{TangoPlum3}
-\definecolor{clogms}{named}{TangoSkyBlue3}
-\definecolor{plogms}{named}{black}
-
-\definecolor{sigmalinms}{named}{linms}
-\definecolor{sigmaqlogms}{named}{qlogms}
-\definecolor{sigmaclogms}{named}{clogms}
-
-\definecolor{biaslinms}{named}{TangoScarletRed1}
-\definecolor{biasqlogms}{named}{TangoPlum1}
-\definecolor{biasclogms}{named}{TangoSkyBlue1}
-
-\definecolor{dbacolor}{named}{TangoScarletRed2}
-\definecolor{dbbcolor}{named}{TangoSkyBlue2}
-\definecolor{dbccolor}{named}{TangoChameleon2}
-\definecolor{dbdcolor}{named}{TangoOrange2}
 
@@
 
+\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
 \pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
@@
 \tikzset{numSlope/.style={anchor=center,align=center,font=\scriptsize}}
+
+%% interpolation figure
+
+\pgfplotsset{continuous/.style={line width=0.75pt,mark options={solid},mark size=3pt}}
+\pgfplotsset{first/.style={color=first,continuous}}
+\pgfplotsset{second/.style={color=second,continuous}}
+\pgfplotsset{third/.style={color=third,continuous}}
+\pgfplotsset{fourth/.style={color=fourth,continuous}}
+\pgfplotsset{fifth/.style={color=fifth,continuous}}
+\pgfplotsset{sixth/.style={color=sixth,continuous}}
+
+\pgfplotsset{range/.style={line width=0.75pt,mark options={solid},mark=|,mark size=2pt}}
+
+\pgfplotsset{atGrid/.style={mark=*,mark size=1.5pt,only marks,mark options={solid}}}
+\pgfplotsset{firstgrid/.style={atGrid,color=first}}
+\pgfplotsset{secondgrid/.style={atGrid,color=second}}
+\pgfplotsset{thirdgrid/.style={atGrid,color=third}}
+\pgfplotsset{fourthgrid/.style={atGrid,color=fourth}}
+\pgfplotsset{fifthgrid/.style={atGrid,color=fifth}}
+\pgfplotsset{sixthgrid/.style={atGrid,color=sixth}}
+
+%%
 

### 2016-02-28 ch04-lrmhinf/paper.tex
Atually include figures + text from CH04

@@
 
-% \section{Introduction}
-% \label{sec:Intro}
+\section{Introduction}
+\label{sec:Intro}
 
-% Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability. 
-% An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
-% The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
-% However, the performance of skyhook damping is limited by high-frequent parasitic resonance phenomena. 
-% Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
-% However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
-% On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
-% On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.
+Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability. 
+An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
+The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
+However, the performance of skyhook damping is limited by high-frequent parasitic resonance phenomena. 
+Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
+However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
+On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
+On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.
 
-% Several approaches have been developed to determine bounds on the model uncertainty. First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
-% However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
-% Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
-% Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
-% In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
-% In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
-% However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
-% Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
-% These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
-% A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
-% Unfortunately, these methods require a sequence of dedicated iterative experiments.
-% This increases the measurement time significantly, especially for \gls{MIMO} plants.
-% When measurement time is expensive, this is a severe impediment.
+Several approaches have been developed to determine bounds on the model uncertainty. First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
+However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
+Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
+Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
+In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
+In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
+However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
+Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
+These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
+A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
+Unfortunately, these methods require a sequence of dedicated iterative experiments.
+This increases the measurement time significantly, especially for \gls{MIMO} plants.
+When measurement time is expensive, this is a severe impediment.
 
-% Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
-% The aim of the present paper is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
-% The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} as introduced in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
-% Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
-% In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the peak value, as is required for the $\Hinf{}$ norm. 
-% The performance of these local parametric models with respect to robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
-% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
-% The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
+Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
+The aim of the present paper is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
+The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} as introduced in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
+In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the peak value, as is required for the $\Hinf{}$ norm. 
+The performance of these local parametric models with respect to robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
+Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
 
-% \vspace{-1em}
-% \paragraph*{Outline}
-% \label{par:toc}
-% The problem is formulated in \secref{sec:Problem}.
-% In \secref{sec:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
-% In \secref{sec:simulation} the method is illustrated on simulations, and the required measurement time is determined.
-% The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:measurement}.
-% Finally, the results and some challenges are discussed in \secref{sec:conclusion}.
+\vspace{-1em}
+\paragraph*{Outline}
+\label{par:toc}
+The problem is formulated in \secref{sec:Problem}.
+In \secref{sec:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
+In \secref{sec:simulation} the method is illustrated on simulations, and the required measurement time is determined.
+The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:measurement}.
+Finally, the results and some challenges are discussed in \secref{sec:conclusion}.
 
-% \glsresetall % reset the usage of all abbreviations s.t. intro and body get the explanation at first use
+\glsresetall % reset the usage of all abbreviations s.t. intro and body get the explanation at first use
 
-% \section{Problem Formulation}
-% \label{sec:Problem}
-% Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
-% After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
-% The \Hinf{} norm of the error system $\Delta$, i.e.
-% \begin{equation}
-%   \gamma 
+\section{Problem Formulation}
+\label{sec:Problem}
+Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
+After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
+The \Hinf{} norm of the error system $\Delta$, i.e.
+\begin{equation}
+  \gamma 
+     = 
+       \infnorm{\Delta} 
+    \isdef 
+       \sup_{\omega} 
+         \abs{\Delta(\omega)}
+  \label{eq:HinfNormSISO}
+\end{equation}
+for a stable \gls{SISO} system, or its weighted form $\infnorm{W \Delta V}$, is a measure that serves an important purpose in many robust control design methodologies that specifies the `size' of the model class for which a controller is to be designed~\citep{Skogestad2005}.
+
+To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
+$ \omega_{\star} 
+     \isdef 
+       \arg
+         \sup_{\omega} 
+           \abs{\Delta(\omega)}
+  \text{.}
+  \label{eq:omega-star}
+$
+However, in a finite measurement time, non-parametric approaches only allow access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
+As such, \eqref{eq:HinfNormSISO} can be rewritten as
+\begin{equation}
+  \gamma \isdef \sup_{\omega} \abs{\Delta(\omega)}
+         = \sup 
+             \set{
+                \ezbrace{\sup_{\omega \in \DFTGrid  } \abs{\Delta(\omega)}}{\gamma_{\mathrm{FRF}}}
+                \;,\;
+                \ezbrace{
+                \sup_{\omega \in \InterGrid} \abs{\Delta(\omega)}}{\gamma_{\mathrm{IG}}}}
+  \label{eq:gamma-split-grid}
+\end{equation}
+where $\Omega \isdef \OpenInterval{0}{\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
+Two cases can be distinguished:
+\begin{enumerate}
+  \item $\omega_{\star} \in \DFTGrid$ such that $\abs{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
+  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\abs{\Delta(\omega_{\star})}  = \gamma = \gamma_{\mathrm{IG}}$ is determined by the inter-grid behavior.
+\end{enumerate}
+The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
+Its expected value over different realizations of the input signal $\expectedValue{\gamma_{\mathrm{FRF}}} \leq \gamma$ due to the limited frequency resolution.
+Such an underestimate may lead to overly optimistic controller designs.
+
+The main contribution of this paper is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
+Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
+
+\subsection{Set-up}
+\TODO{overgang $\Delta(q)$ naar output-error}
+
+Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
+For an infinitely long data record, this can be described in the time-domain as
+\begin{equation}
+  y_{\Delta}(n) 
+    = 
+      y_{\Delta0}
+      + v(n) 
+    = 
+      \Delta(q)u_{\Delta}(n) 
+      + H(q)e(n)
+  \label{eq:sysDeltaInfData}
+\end{equation}
+where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
+For a limited data record ($n \in \set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
+\begin{equation}
+    y_{\Delta}(n) 
+      = 
+        \Delta(q)u(n) 
+        + H(q)e(n) 
+        + t_{\Delta}(n)
+    \text{.}
+    \label{eq:sysDeltaFiniteData}
+\end{equation}
+By applying the \gls{DFT}
+\begin{equation}
+  X(k) 
+       = 
+         \frac{1}
+              {\sqrt{N}} 
+         \sum_{n=0}^{N-1} 
+            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
+         \quad   
+         \forall k \in \mathbb{Z}
+  \label{eq:DFT}
+\end{equation} 
+to both sides of~\eqref{eq:sysDeltaFiniteData}, one obtains:
+\begin{equation}
+  Y_{\Delta}(k) 
+                = 
+                  \Delta(\omega_k) U_{\Delta}(k) 
+                  + T_{\Delta}(\omega_k) 
+                  + V(k) 
+  \text{.}
+  \label{eq:sysDeltaFiniteDataFD}
+\end{equation}
+The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
+
+The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:control}.
+The results in this paper are presented in discrete time, but the extension to the continuous time case is straightforward.
+
+\section{\Hinf{} Norm Estimation Procedure}
+\label{sec:LPMHinf}
+To estimate $\gamma_{\mathrm{IG}}$, we propose to identify local parametric models in the frequency domain.
+The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} }{ \omega_{k+1} }$ in view of the local validity of the local models.
+In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
+\begin{equation}
+  \gamma_{\mathrm{IG}} = 
+    \sup \set{ \left. 
+                \sup_{\omega \in \Omega_k} \abs{\LocalModel{\Delta}_k(\omega)}
+                \right|
+                k = 1,\ldots,N-1
+                }
+   \label{eq:gamma-inter-grid}
+\end{equation}
+where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k$th) frequency $\omega_k$.
+An example of such local models is shown in \figref{fig:interpol-quantities}.
+Two alternative methods allow to evaluate~\eqref{eq:gamma-inter-grid} practically.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.8\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/interpolation-show.tikz}
+  \caption{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
+  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
+\label{fig:interpol-quantities}
+\end{figure}
+
+\vspace{-3em}
+\paragraph*{Direct method}
+% \subsubsection{Direct method}
+One can implement the definition~\eqref{eq:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
+Hence, it boils down to solving the optimization problems
+\begin{equation}
+  % \gamma_{\mathrm{IG}}(k) 
   % = 
-%        \infnorm{\Delta} 
-%     \isdef 
-%        \sup_{\omega} 
-%          \abs{\Delta(\omega)}
-%   \label{eq:HinfNormSISO}
-% \end{equation}
-% for a stable \gls{SISO} system, or its weighted form $\infnorm{W \Delta V}$, is a measure that serves an important purpose in many robust control design methodologies that specifies the `size' of the model class for which a controller is to be designed~\citep{Skogestad2005}.
+      \max_{\omega \in \Omega_k} 
+      \abs{\LocalModel{\Delta}_k(\omega)}
+      \label{eq:gamma-direct}
+\end{equation}
+for $k \in \set{1,\ldots,N-1}$.
+These are tractable since $\omega$ is one-dimensional and restricted to the intervals $\Omega_k$.
+Unfortunately, this approach offers no insight in the behavior of $\abs{\Delta(\omega)}$, e.g. around the peak amplitude.
 
-% To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
-% $ \omega_{\star} 
-%      \isdef 
-%        \arg
-%          \sup_{\omega} 
-%            \abs{\Delta(\omega)}
-%   \text{.}
-%   \label{eq:omega-star}
-% $
-% However, in a finite measurement time, non-parametric approaches only allow access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
-% As such, \eqref{eq:HinfNormSISO} can be rewritten as
-% \begin{equation}
-%   \gamma \isdef \sup_{\omega} \abs{\Delta(\omega)}
-%          = \sup 
-%              \set{
-%                 \ezbrace{\sup_{\omega \in \DFTGrid  } \abs{\Delta(\omega)}}{\gamma_{\mathrm{FRF}}}
-%                 \;,\;
-%                 \ezbrace{
-%                 \sup_{\omega \in \InterGrid} \abs{\Delta(\omega)}}{\gamma_{\mathrm{IG}}}}
-%   \label{eq:gamma-split-grid}
-% \end{equation}
-% where $\Omega \isdef \openInterval{0}{\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
-% Two cases can be distinguished:
-% \begin{enumerate}
-%   \item $\omega_{\star} \in \DFTGrid$ such that $\abs{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
-%   \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\abs{\Delta(\omega_{\star})}  = \gamma = \gamma_{\mathrm{IG}}$ is determined by the inter-grid behavior.
-% \end{enumerate}
-% The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
-% Its expected value over different realizations of the input signal $\expectedValue{\gamma_{\mathrm{FRF}}} \leq \gamma$ due to the limited frequency resolution.
-% Such an underestimate may lead to overly optimistic controller designs.
+\vspace{-2em}
+\paragraph*{Interpolation method}
+To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
+It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\abs{\omega_k-\omega}$ is small.
+To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
+\begin{align}
+  k_L(\omega) & 
+                \isdef
+                  \max
+                  \set{k 
+                    \given{
+                      \omega_k \in \DFTGrid, 
+                      \omega_k \leq \omega}
+                  }\\
+  k_R(\omega) & 
+                \isdef
+                  \min
+                  \set{k 
+                    \given{
+                      \omega_k \in \DFTGrid, 
+                      \omega_k \geq \omega}
+                  }
+  \text{.}
+  \label{eq:kL-kR-indexing-functions}
+\end{align}
+Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
+In view of obtaining the maximum amplitude, these are `interpolated' to obtain a single estimate:
+\begin{equation}
+  \abs{\Delta_{\mathrm{LRM}}(\omega)}
+    \isdef
+    \sup \set{
+       \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
+        \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+    }
+    \label{eq:DeltaLRMInterpolation}
+\end{equation}
+by retaining the largest both.
+It follows that
+\begin{align}
+  \widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty} 
+    & \isdef
+    \sup_{\omega\in\Omega}
+    \abs{\Delta_{\mathrm{LRM}}(\omega)} \\
+   &  =
+      \sup_{\omega\in\Omega} \; 
+      \sup \set{
+                 \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
+                 \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
+  \label{eq:gammaInterpolOptim}
+  \text{.}
+\end{align}
 
-% The main contribution of this paper is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
-% Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
+\vspace{-2em}
+\paragraph*{Remarks:}
+The optimization problems~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} can, e.g. be solved by griding the frequency $\omega$.
+The peak amplitudes obtained using~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
+$% \begin{equation}
+  \Omega_k = \set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
+$ % \end{equation}
+for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
+In \figref{fig:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
 
-% \subsection{Set-up}
-% \TODO{overgang $\Delta(q)$ naar output-error}
+\subsection{The \glsentrydesc{LRM}}
+\label{sec:LRM}
+The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
+The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:sysDeltaFiniteDataFD} are smooth functions of the frequency.
+As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
+\begin{align}
+  \Delta(\omega_{k+r})     
+    &\approx 
+        \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
+      = 
+        \frac{B_k(r)}{A_k(r)} 
+      \isdef 
+        \LocalModel{\Delta}_{k}(\omega_{k+r})
+      \label{eq:LRMTaylorSystem} \\
+  T_{\Delta}(\omega_{k+r}) 
+    &\approx 
+        \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
+      = 
+        \frac{T_k'(r)}{A_k(r)} 
+      \isdef 
+        \LocalModel{T}_{k}(\omega_{k+r})
+  \label{eq:LRMTaylorTransient}
+  \text{.}
+\end{align}
+Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
+This yields
+\begin{equation}
+  Y_{\Delta}(k+r) 
+                 \approx
+                    \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
+                    + T_{\Delta}(\omega_{k+r}) 
+    \quad
+    \forall r \in \LocalWindow
+    \text{.}
+    \label{eq:LocalWindowSpectra}
+\end{equation}
+By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
+\begin{align}
+  Y_{\Delta}(k+r) 
+                  & \approx
+                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
+                    + \LocalModel{T}_k(\omega_{k+r}) 
+                    & \forall r \in \LocalWindow \\
+                  & = 
+                    \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
+                    + 
+                    \frac{T'_k(r)}{A_k(r)} 
+                    & \forall r \in \LocalWindow
+    \text{.}
+    \label{eq:LocalWindowSpectraLRM}
+\end{align}
+To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
+By doing so, the local linear-least-squares cost function
+\begin{equation}
+  \sum_{r=-N_W}^{N_W} 
+  \left| 
+    A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
+  \right|^2
+  \label{eq:localCostLRM}
+\end{equation}
+ around each bin $k$ can be constructed.
+We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
+For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.
 
-% Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
-% For an infinitely long data record, this can be described in the time-domain as
-% \begin{equation}
-%   y_{\Delta}(n) 
-%     = 
-%       y_{\Delta0}
-%       + v(n) 
-%     = 
-%       \Delta(q)u_{\Delta}(n) 
-%       + H(q)e(n)
-%   \label{eq:sysDeltaInfData}
-% \end{equation}
-% where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
-% For a limited data record ($n \in \set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
-% \begin{equation}
-%     y_{\Delta}(n) 
-%       = 
-%         \Delta(q)u(n) 
-%         + H(q)e(n) 
-%         + t_{\Delta}(n)
-%     \text{.}
-%     \label{eq:sysDeltaFiniteData}
-% \end{equation}
-% By applying the \gls{DFT}
-% \begin{equation}
-%   X(k) 
-%        = 
-%          \frac{1}
-%               {\sqrt{N}} 
-%          \sum_{n=0}^{N-1} 
-%             x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
-%          \quad   
-%          \forall k \in \mathbb{Z}
-%   \label{eq:DFT}
-% \end{equation} 
-% to both sides of~\eqref{eq:sysDeltaFiniteData}, one obtains:
-% \begin{equation}
-%   Y_{\Delta}(k) 
-%                 = 
-%                   \Delta(\omega_k) U_{\Delta}(k) 
-%                   + T_{\Delta}(\omega_k) 
-%                   + V(k) 
-%   \text{.}
-%   \label{eq:sysDeltaFiniteDataFD}
-% \end{equation}
-% The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
+For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM}.
 
-% The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:control}.
-% The results in this paper are presented in discrete time, but the extension to the continuous time case is straightforward.
+\section{Simulation}
+\label{sec:simulation}
+To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
+The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
 
-% \section{\Hinf{} Norm Estimation Procedure}
-% \label{sec:LPMHinf}
-% To estimate $\gamma_{\mathrm{IG}}$, we propose to identify local parametric models in the frequency domain.
-% The frequency axis is partitioned into continuous segments $\Omega_k \isdef \openInterval{ \omega_{k-1} }{ \omega_{k+1} }$ in view of the local validity of the local models.
-% In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
-% \begin{equation}
-%   \gamma_{\mathrm{IG}} = 
-%     \sup \set{ \left. 
-%                 \sup_{\omega \in \Omega_k} \abs{\LocalModel{\Delta}_k(\omega)}
-%                 \right|
-%                 k = 1,\ldots,N-1
-%                 }
-%    \label{eq:gamma-inter-grid}
-% \end{equation}
-% where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k$th) frequency $\omega_k$.
-% An example of such local models is shown in \figref{fig:interpol-quantities}.
-% Two alternative methods allow to evaluate~\eqref{eq:gamma-inter-grid} practically.
+Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems.
+As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
+mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
+To estimate $\norm{\Delta}$ mainly the resonant sub-systems are of interest.
+Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
+This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
+By normalizing the conclusions for the time constant $\tau$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\xi$.
+Specifically, the system's $\tau \isdef (\xi\omega_{\mathrm{n}})^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\xi$ is the relative damping and $\omega_{\mathrm{n}}$ the undamped natural frequency.
 
-% \begin{figure}
-%   \centering
-%   \setlength{\figurewidth}{0.8\columnwidth}
-%   \setlength{\figureheight}{0.68\figurewidth}
-%   \input{\thisDir/figs/interpolation-show.tikz}
-%   \caption{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
-%   The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
-% \label{fig:interpol-quantities}
-% \end{figure}
+\subsection{A concrete simulation}
+Consider a discrete time system $\Delta$ (see \figref{fig:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
+\begin{equation}
+  \Delta(z) 
+    =  \frac{0.45373 z + 0.44752}
+            {z^2 - 1.0595 z + 0.96079}
+  \label{eq:O2sysDT}
+  \text{,}
+\end{equation}
+which has $\tau = 50 \unit{samples}$ (i.e. $\xi=0.02$ and $\omega_{\mathrm{n}} = 1 \unit{rad/S}$).
+The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
+\begin{equation}
+  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
+              {\sqrt{\inv{N}\sum_n v^2(n) }}
+       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
+       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
+  \label{eq:SNR}
+\end{equation}
+of $10$ is obtained.
 
-% \vspace{-3em}
-% \paragraph*{Direct method}
-% % \subsubsection{Direct method}
-% One can implement the definition~\eqref{eq:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
-% Hence, it boils down to solving the optimization problems
-% \begin{equation}
-%   % \gamma_{\mathrm{IG}}(k) 
-%   % = 
-%       \max_{\omega \in \Omega_k} 
-%       \abs{\LocalModel{\Delta}_k(\omega)}
-%       \label{eq:gamma-direct}
-% \end{equation}
-% for $k \in \set{1,\ldots,N-1}$.
-% These are tractable since $\omega$ is one-dimensional and restricted to the intervals $\Omega_k$.
-% Unfortunately, this approach offers no insight in the behavior of $\abs{\Delta(\omega)}$, e.g. around the peak amplitude.
+Classical \gls{SA} techniques~\citep{Bendat1980} can estimate the \gls{FRF} of $\Delta$.
+This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
+By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
+In this paper a Hann window and $N_S=1$ are used.
+Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
 
-% \vspace{-2em}
-% \paragraph*{Interpolation method}
-% To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
-% It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\abs{\omega_k-\omega}$ is small.
-% To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
-% \begin{align}
-%   k_L(\omega) & 
-%                 \isdef
-%                   \max
-%                   \set{k 
-%                     \given{
-%                       \omega_k \in \DFTGrid, 
-%                       \omega_k \leq \omega}
-%                   }\\
-%   k_R(\omega) & 
-%                 \isdef
-%                   \min
-%                   \set{k 
-%                     \given{
-%                       \omega_k \in \DFTGrid, 
-%                       \omega_k \geq \omega}
-%                   }
-%   \text{.}
-%   \label{eq:kL-kR-indexing-functions}
-% \end{align}
-% Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
-% In view of obtaining the maximum amplitude, these are `interpolated' to obtain a single estimate:
-% \begin{equation}
-%   \abs{\Delta_{\mathrm{LRM}}(\omega)}
-%     \isdef
-%     \sup \set{
-%        \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
-%         \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
-%     }
-%     \label{eq:DeltaLRMInterpolation}
-% \end{equation}
-% by retaining the largest both.
-% It follows that
-% \begin{align}
-%   \widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty} 
-%     & \isdef
-%     \sup_{\omega\in\Omega}
-%     \abs{\Delta_{\mathrm{LRM}}(\omega)} \\
-%    &  =
-%       \sup_{\omega\in\Omega} \; 
-%       \sup \set{
-%                  \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
-%                  \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
-%   \label{eq:gammaInterpolOptim}
-%   \text{.}
-% \end{align}
+\figref{fig:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
+The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to linear models ($N_B=1$). 
+Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.
 
-% \vspace{-2em}
-% \paragraph*{Remarks:}
-% The optimization problems~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} can, e.g. be solved by griding the frequency $\omega$.
-% The peak amplitudes obtained using~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
-% $% \begin{equation}
-%   \Omega_k = \set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
-% $ % \end{equation}
-% for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
-% In \figref{fig:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/example-both.tikz}
+  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
+  \caption{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
+  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
+  Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
+  \label{fig:exampleIntergrid}
+\end{figure}
 
-% \subsection{The \glsentrydesc{LRM}}
-% \label{sec:LRM}
-% The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
-% The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:sysDeltaFiniteDataFD} are smooth functions of the frequency.
-% As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
-% \begin{align}
-%   \Delta(\omega_{k+r})     
-%     &\approx 
-%         \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
-%       = 
-%         \frac{B_k(r)}{A_k(r)} 
-%       \isdef 
-%         \LocalModel{\Delta}_{k}(\omega_{k+r})
-%       \label{eq:LRMTaylorSystem} \\
-%   T_{\Delta}(\omega_{k+r}) 
-%     &\approx 
-%         \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
-%       = 
-%         \frac{T_k'(r)}{A_k(r)} 
-%       \isdef 
-%         \LocalModel{T}_{k}(\omega_{k+r})
-%   \label{eq:LRMTaylorTransient}
-%   \text{.}
-% \end{align}
-% Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
-% This yields
-% \begin{equation}
-%   Y_{\Delta}(k+r) 
-%                  \approx
-%                     \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
-%                     + T_{\Delta}(\omega_{k+r}) 
-%     \quad
-%     \forall r \in \LocalWindow
-%     \text{.}
-%     \label{eq:LocalWindowSpectra}
-% \end{equation}
-% By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
-% \begin{align}
-%   Y_{\Delta}(k+r) 
-%                   & \approx
-%                     \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
-%                     + \LocalModel{T}_k(\omega_{k+r}) 
-%                     & \forall r \in \LocalWindow \\
-%                   & = 
-%                     \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
-%                     + 
-%                     \frac{T'_k(r)}{A_k(r)} 
-%                     & \forall r \in \LocalWindow
-%     \text{.}
-%     \label{eq:LocalWindowSpectraLRM}
-% \end{align}
-% To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
-% By doing so, the local linear-least-squares cost function
-% \begin{equation}
-%   \sum_{r=-N_W}^{N_W} 
-%   \left| 
-%     A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
-%   \right|^2
-%   \label{eq:localCostLRM}
-% \end{equation}
-%  around each bin $k$ can be constructed.
-% We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
-% For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.
+It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
+Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
+The \gls{LPM}, on the other hand, does not provide a reliable estimate.
 
-% For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM}.
+\subsection{Study of the experiment length}
+Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
+In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.
 
-% \section{Simulation}
-% \label{sec:simulation}
-% To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
-% The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
+We simulate the system \eqref{eq:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
+To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:LPMHinf}.
+The values of $N \in \ClosedInterval{35}{16 000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
+These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
+The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:MC-run-length}.
 
-% Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems.
-% As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
-mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
-% To estimate $\norm{\Delta}$ mainly the resonant sub-systems are of interest.
-% Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
-% This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
-% By normalizing the conclusions for the time constant $\tau$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\xi$.
-% Specifically, the system's $\tau \isdef (\xi\omega_{\mathrm{n}})^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\xi$ is the relative damping and $\omega_{\mathrm{n}}$ the undamped natural frequency.
-
-% \subsection{A concrete simulation}
-% Consider a discrete time system $\Delta$ (see \figref{fig:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
-% \begin{equation}
-%   \Delta(z) 
-%     =  \frac{0.45373 z + 0.44752}
-%             {z^2 - 1.0595 z + 0.96079}
-%   \label{eq:O2sysDT}
-%   \text{,}
-% \end{equation}
-% which has $\tau = 50 \unit{samples}$ (i.e. $\xi=0.02$ and $\omega_{\mathrm{n}} = 1 \unit{rad/S}$).
-% The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
-% \begin{equation}
-%   \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
-%               {\sqrt{\inv{N}\sum_n v^2(n) }}
-%        = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
-%        \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
-%   \label{eq:SNR}
-% \end{equation}
-% of $10$ is obtained.
-
-% Classical \gls{SA} techniques~\citep{Bendat1980} can estimate the \gls{FRF} of $\Delta$.
-% This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
-% By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
-% In this paper a Hann window and $N_S=1$ are used.
-% Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
-
-% \figref{fig:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
-% The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to linear models ($N_B=1$). 
-% Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.
-
-% \begin{figure}
-%   \centering
-%   \setlength{\figurewidth}{0.75\columnwidth}
-%   \setlength{\figureheight}{0.68\figurewidth}
-%   \input{\thisDir/figs/example-both.tikz}
-%   %\input{\thisDir/figs/example-LRM-SNR1.tikz}
-%   \caption{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
-%   Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
-%   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
-%   Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
-%   \label{fig:exampleIntergrid}
-% \end{figure}
-
-% It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
-% Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
-% The \gls{LPM}, on the other hand, does not provide a reliable estimate.
-
-% \subsection{Study of the experiment length}
-% Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
-% In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.
-
-% We simulate the system \eqref{eq:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
-% To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:LPMHinf}.
-% The values of $N \in \closedInterval{35}{16 000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
-% These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
-% The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:MC-run-length}.
-
-% \begin{figure}
-%   \centering
-%   \setlength{\figurewidth}{0.75\columnwidth}
-%   \setlength{\figureheight}{0.68\figurewidth}
-%   \input{\thisDir/figs/MC-runlength.tikz}
-%   %\input{figures/runLength.tikz}
-%   \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\tau$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
-%   However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \tau$).
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/MC-runlength.tikz}
+  %\input{figures/runLength.tikz}
+  \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\tau$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \tau$).
 A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}.
 The shaded areas show the $\pm \sigma$ intervals which are mostly due to the noise.
-%   }
-% \label{fig:MC-run-length}
-% \end{figure}
+  }
+\label{fig:MC-run-length}
+\end{figure}
 
-% It can be seen in \figref{fig:MC-run-length} that $N \geq 20\tau$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
+It can be seen in \figref{fig:MC-run-length} that $N \geq 20\tau$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
 $\expectedValue{\gamma_{\mathrm{FRF}}} \approx \gamma$.
-% Starting from about $N=4 \text{ to } 5\tau$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
-% For long experiments $(N \to \infty)$, the true $\norm{\Delta}$ is recovered.
-% Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.
+Starting from about $N=4 \text{ to } 5\tau$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
+For long experiments $(N \to \infty)$, the true $\norm{\Delta}$ is recovered.
+Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.
 
-% \section{Application to an \glsentryname{AVIS}}
-% \label{sec:measurement}
-% The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:avis}.
-% The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
-% Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
-% To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
+\section{Application to an \glsentryname{AVIS}}
+\label{sec:measurement}
+The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:avis}.
+The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
+Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
+To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
 
-% \subsection{Measurement \& control framework}
-% \label{sec:control}
-% The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:tpc}) with $r_2 = 0$.
-% The controller $\Controller=\experimental\Controller$  stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
-% The $r_1$ input consists of five periods of a random phase multisine~\citep{Geerardyn2013TIM} of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
+\subsection{Measurement \& control framework}
+\label{sec:control}
+The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:tpc}) with $r_2 = 0$.
+The controller $\Controller=\experimental\Controller$  stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
+The $r_1$ input consists of five periods of a random phase multisine~\citep{Geerardyn2013TIM} of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
 
-% \begin{figure}
-%  \centering
-%  \input{\thisDir/figs/tpcrobust.tikz}
-%  \caption{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
-%  \label{fig:tpc}
-% \end{figure}
+\begin{figure}
+ \centering
+ \input{\thisDir/figs/tpcrobust.tikz}
+ \caption{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
+ \label{fig:tpc}
+\end{figure}
 
-% \begin{figure}
-%  \centering
-%  \input{\thisDir/figs/dualYoula.tikz}
-%  \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
-% \label{fig:dualYoula}
-% \end{figure}
+\begin{figure}
+ \centering
+ \input{\thisDir/figs/dualYoula.tikz}
+ \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
+\label{fig:dualYoula}
+\end{figure}
 
-% The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
-% \begin{equation}
-%   \ModelSet[] 
-%     \isdef 
-%       \set{
-%           \left. 
-%             \frac{\hat{N} + D_c \Delta}
-%                  {\hat{D} - N_c \Delta} 
-%           \right| 
-%             \hinfnorm{\Delta} \leq \gamma
-%         }
-%   \label{eq:dualYoulaModelSet}
-%   \text{,}
-% \end{equation}
-% where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:dualYoula}).
-% To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:dualYoula} are required.
-% These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
-% In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:LPMHinf} applies.
+The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
+\begin{equation}
+  \ModelSet[] 
+    \isdef 
+      \set{
+          \left. 
+            \frac{\hat{N} + D_c \Delta}
+                 {\hat{D} - N_c \Delta} 
+          \right| 
+            \hinfnorm{\Delta} \leq \gamma
+        }
+  \label{eq:dualYoulaModelSet}
+  \text{,}
+\end{equation}
+where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:dualYoula}).
+To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:dualYoula} are required.
+These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
+In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:LPMHinf} applies.
 
-% The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
-% In view of the robust control criterion
-% \begin{equation}
-%   \Crit(\Plant,\Controller) 
-%     \isdef 
-%       \infnorm{W \ClosedLoop{\Plant,\Controller} V}
-%   \label{eq:controlCrit}
-%   \text{,}
-% \end{equation}
-% the \glspl{RCF} are constructed such that
-% $
-%   \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
-%   \leq
-%   \Crit \left( \estimated\Plant, \experimental\Controller \right)
-%   + \gamma
-% $
-% where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
-% % Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
-% I.e. even for a weighted control criterion \eqref{eq:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
-% In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:avis-frf}) is estimated.
-% Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:avisMeas}).
+The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
+In view of the robust control criterion
+\begin{equation}
+  \Crit(\Plant,\Controller) 
+    \isdef 
+      \infnorm{W \ClosedLoop{\Plant,\Controller} V}
+  \label{eq:controlCrit}
+  \text{,}
+\end{equation}
+the \glspl{RCF} are constructed such that
+$
+  \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
+  \leq
+  \Crit \left( \estimated\Plant, \experimental\Controller \right)
+  + \gamma
+$
+where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
+% Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
+I.e. even for a weighted control criterion \eqref{eq:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
+In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:avis-frf}) is estimated.
+Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:avisMeas}).
 
-% \begin{figure}
-%  \centering
-%     \setlength{\figurewidth}{0.75\columnwidth}
-%     \setlength{\figureheight}{0.68\figurewidth}
-%     \input{\thisDir/figs/avis-frf.tikz}
-%  \caption{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
-%  \label{fig:avis-frf}
-%  \label{fig:avis}
-% \end{figure}
+\begin{figure}
+ \centering
+    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
+    \input{\thisDir/figs/avis-frf.tikz}
+ \caption{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
+ \label{fig:avis-frf}
+ \label{fig:avis}
+\end{figure}
 
-% \subsection{Results}
-% \label{sec:resultsAvis}
-% To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
-% The full dataset that includes bins not used in the estimation is used to validate the interpolation results.
+\subsection{Results}
+\label{sec:resultsAvis}
+To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
+The full dataset that includes bins not used in the estimation is used to validate the interpolation results.
 
-% The measured $\Delta$ is shown in \figref{fig:avisMeas} for the whole frequency band and \figref{fig:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
-% Two aspects of the proposed method are examined.
-% First, the interpolation results for a continuous frequency range are validated.
-% Second, the peak amplitudes of $\Delta(\omega)$ are inspected as these are  indicators for $\infnorm{\Delta}$.
+The measured $\Delta$ is shown in \figref{fig:avisMeas} for the whole frequency band and \figref{fig:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
+Two aspects of the proposed method are examined.
+First, the interpolation results for a continuous frequency range are validated.
+Second, the peak amplitudes of $\Delta(\omega)$ are inspected as these are  indicators for $\infnorm{\Delta}$.
 
-% \begin{figure}
-%  \centering
-%     \setlength{\figurewidth}{0.75\columnwidth}
-%     \setlength{\figureheight}{0.68\figurewidth}
+\begin{figure}
+ \centering
+    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
     % \input{\thisDir/figs/avis-delta-full.tikz}
-%  \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
-% \label{fig:avisMeas}
-% \end{figure}
+    \TODOfig{split plots}
+ \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
+\label{fig:avisMeas}
+\end{figure}
 
-% \begin{figure}
-%  \centering
-%     \setlength{\figurewidth}{0.75\columnwidth}
-%     \setlength{\figureheight}{0.68\figurewidth}
-%    \input{\thisDir/figs/avis4.tikz}
-%  \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
+\begin{figure}
+ \centering
+    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
+   \input{\thisDir/figs/avis4.tikz}
+ \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
 Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
 The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
-% \label{fig:avisMeasZoom}
-% \end{figure}
+\label{fig:avisMeasZoom}
+\end{figure}
 
-% \vspace{-2em}
-% \paragraph*{Interpolation performance}
-% \label{sec:avis-interpol}
-% \figref{fig:avisMeas} and \figref{fig:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
-% In the frequency range shown in \figref{fig:avisMeasZoom}, the relative difference between both is at most $2\%$.
+\vspace{-2em}
+\paragraph*{Interpolation performance}
+\label{sec:avis-interpol}
+\figref{fig:avisMeas} and \figref{fig:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
+In the frequency range shown in \figref{fig:avisMeasZoom}, the relative difference between both is at most $2\%$.
 
-% \vspace{-2em}
-% \paragraph*{Peak value estimates}
-% \label{sec:avis-peak-value}
-% Near $296\unit{Hz}$, a modest improvement of the peak estimate from $-15.3 \unit{dB}$ (at-grid) to $-14.0 \unit{dB}$ is obtained by the interpolation.
-% The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
-% The proposed method \eqref{eq:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
-% $\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
-% This peak agrees well with the validation data, where the nearest (at-grid) value has an amplitude of $-3.2\unit{dB}$ (i.e. $8\%$ difference).
+\vspace{-2em}
+\paragraph*{Peak value estimates}
+\label{sec:avis-peak-value}
+Near $296\unit{Hz}$, a modest improvement of the peak estimate from $-15.3 \unit{dB}$ (at-grid) to $-14.0 \unit{dB}$ is obtained by the interpolation.
+The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
+The proposed method \eqref{eq:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
+$\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
+This peak agrees well with the validation data, where the nearest (at-grid) value has an amplitude of $-3.2\unit{dB}$ (i.e. $8\%$ difference).
 
-% This suggests that the local rational models with interpolation are a very good approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
+This suggests that the local rational models with interpolation are a very good approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
 
-% \section{Conclusion and Further Research}
-% \label{sec:conclusion}
-% A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
-% In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\norm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
-% It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\norm{\Delta}$.
-% The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
-% It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
-% Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
-% Furthermore, the results are validated by a detailed validation measurement.
-% Ongoing research focuses on extending the technique to \gls{MIMO} systems and the study of its stochastic properties.
+\section{Conclusion and Further Research}
+\label{sec:conclusion}
+A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
+In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\norm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
+It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\norm{\Delta}$.
+The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
+It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
+Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
+Furthermore, the results are validated by a detailed validation measurement.
+Ongoing research focuses on extending the technique to \gls{MIMO} systems and the study of its stochastic properties.

### 2016-02-28 config/styles.inc.tex
Atually include figures + text from CH04

@@
 \pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
-\pgfplotsset{every axis post/.style={unbounded coords=jump}}
+\pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}
 
@@
 \definecolor{truesys}{named}{TangoAluminium5}
+% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper
 
@@
 
-  \definecolor{dbacolor}{named}{TangoScarletRed2}
-  \definecolor{dbbcolor}{named}{TangoSkyBlue2}
-  \definecolor{dbccolor}{named}{TangoChameleon2}
-  \definecolor{dbdcolor}{named}{TangoOrange2}
-
 \definecolor{first}{named}{TangoScarletRed2}
@@
 \definecolor{sixth}{named}{TangoChocolate2}
+
+\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
+\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
+\definecolor{RFIR}{named}{TangoScarletRed3}
+\definecolor{RFIRInit}{named}{TangoScarletRed1}
+\definecolor{existing}{named}{TangoChameleon3}
+\definecolor{G0Hat}{named}{TangoOrange2}
+\definecolor{GVXI}{named}{G0Hat}
+\definecolor{reference}{named}{black}
+
+\definecolor{heuristic}{named}{TangoPlum2}
+\definecolor{observed}{named}{TangoOrange3}
+
+\definecolor{best}{named}{TangoAluminium6}
+
+\definecolor{G0HatFill}{named}{TangoOrange1}
+\definecolor{GVXIFill}{named}{G0HatFill}
+\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
+\definecolor{RFIRFill}{named}{TangoScarletRed1}
+\definecolor{existingFill}{named}{TangoChameleon1}
+\definecolor{bestFill}{named}{TangoAluminium3}
+
+\definecolor{FRFMean}{named}{TangoPlum3}
+\definecolor{FRFSingle}{named}{TangoPlum1}
+\definecolor{FRFNoise}{named}{TangoChocolate1}
+
+\definecolor{LRM}{named}{TangoScarletRed3}
+\definecolor{LPM}{named}{TangoSkyBlue2}
+\definecolor{SA}{named}{TangoChameleon2}
+
+\definecolor{validation}{named}{TangoChameleon2}
+
+\definecolor{LPMshade}{named}{TangoSkyBlue1}
+\definecolor{LRMshade}{named}{TangoScarletRed1}
+\definecolor{refColor}{named}{TangoAluminium6}
+
+\definecolor{frf}{named}{TangoButter3} %TODO: replace
+\definecolor{param}{named}{TangoScarletRed2}
 
@@
 
-\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
-\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
-\definecolor{RFIR}{named}{TangoScarletRed3}
-\definecolor{RFIRInit}{named}{TangoScarletRed1}
-\definecolor{existing}{named}{TangoChameleon3}
-\definecolor{G0Hat}{named}{TangoOrange2}
-\definecolor{GVXI}{named}{G0Hat}
-\definecolor{reference}{named}{black}
-
-\definecolor{heuristic}{named}{TangoPlum2}
-\definecolor{observed}{named}{TangoOrange3}
-
-\definecolor{best}{named}{TangoAluminium6}
-
-\definecolor{G0HatFill}{named}{TangoOrange1}
-\definecolor{GVXIFill}{named}{G0HatFill}
-\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
-\definecolor{RFIRFill}{named}{TangoScarletRed1}
-\definecolor{existingFill}{named}{TangoChameleon1}
-\definecolor{bestFill}{named}{TangoAluminium3}
-
-\definecolor{FRFMean}{named}{TangoPlum3}
-\definecolor{FRFSingle}{named}{TangoPlum1}
-\definecolor{FRFNoise}{named}{TangoChocolate1}
+%% Initial values
 
@@
 
+%% LRM chapters
+
+\pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}
+
+\pgfplotsset{hinfnorm/.style={dashed}}
+\pgfplotsset{interpol/.style={sharp plot,solid,mark options={solid}}}
+
+\pgfplotsset{LRMgrid/.style={color=LRM,mark size=1.5pt,only marks,mark=square*,mark options={solid}}}
+\pgfplotsset{LPMgrid/.style={color=LPM,mark size=1.5pt,only marks,mark=*,mark options={solid}}}
+\pgfplotsset{SAgrid/.style={color=SA,densely dotted,solid,mark=triangle*,mark size=1.5pt,mark options={solid}}}
+
+\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}} %TODO: replace
+
+\pgfplotsset{paramPhat/.style={color=param,solid,line width=1.2pt}}
+
+\pgfplotsset{validation/.style={color=validation,densely dotted,mark=diamond*,mark size=1pt,mark options={solid}}}
+
+\pgfplotsset{shaded/.style={opacity=0.5,area legend,solid}}
+
+\pgfplotsset{LPMshade/.style={shaded,fill=LPMshade,draw=LPM}}
+\pgfplotsset{LRMshade/.style={shaded,fill=LRMshade,draw=LRM}}
+
+\pgfplotsset{reference/.append style={color=refColor,densely dotted,line width=0.75pt}}
+\pgfplotsset{gammafrf/.style={color=black,mark=pentagon,mark options={solid}}}
+
 %% interpolation figure
-
 \pgfplotsset{continuous/.style={line width=0.75pt,mark options={solid},mark size=3pt}}

### 2016-02-28 config/blockdiag.inc.tex

\usetikzlibrary{positioning}  % positioning
\usetikzlibrary{decorations.pathmorphing}  % snake lines
\usetikzlibrary{matrix}                    % block alignment
\usetikzlibrary{arrows}                    % arrow heads
\usetikzlibrary{calc}                      % manipulation of coordinates
\usetikzlibrary{fit}

\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

%% Block diagram settings
\definecolor{weight}{named}{TangoButter3}
\definecolor{plant}{named}{TangoScarletRed2}
\definecolor{plantset}{named}{TangoOrange2}
\definecolor{modelset}{named}{plantset}
\definecolor{delta}{named}{black}
\definecolor{controller}{named}{TangoPlum2}

\definecolor{TPC}{named}{TangoAluminium4}

\tikzstyle{line}      = [thick]
\tikzstyle{block}     = [draw,rectangle,line,minimum height=2em,minimum width=2em]
\tikzstyle{weight}    = [block,color=weight]
\tikzstyle{controller}= [block,color=controller]
\tikzstyle{plant}     = [block,color=plant]
\tikzstyle{sum}       = [draw,circle,inner sep=0mm,minimum size=2mm]
\tikzstyle{connector} = [->,line]
\tikzstyle{branch}    = [circle,inner sep=0pt,minimum size=0.75mm,fill=black,draw=black]
\tikzset{groupbox/.style={draw,rectangle,line, fill opacity=0.2,fill=#1,color=#1}}
\tikzset{groupbox/.default=red}
\tikzstyle{weightbox} = [groupbox=weight]
\tikzstyle{none}      = [inner sep=0,outer sep=-0,fill=#1,#1]
\tikzset{none/.default=black}

\tikzset{groupcirc/.style={rectangle,fill opacity=0.2,fill=#1,color=#1}}
\tikzset{groupcirc/.default=red}

### 2016-02-29 ch02-qlogms/excitation-design.tex
Add some TODOs
Fix styles + some comments of Johan CH02

@@
 
-\subsection{Approach in this chapter}
+\subsection{General purpose robust excitation signals}
 \label{sec:excitation:intro:approach}
@@
                  \frac{\sigma^2_E\left(\omega_1 \right) }
-                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
-                 0 & \ddots & 0 \\
-                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
+                      {\abs{ U\left(\omega_1 \right)}^2 } & \deemph{0} & \deemph{0}\\
+                 \deemph{0} & \ddots & \deemph{0} \\
+                 \deemph{0} & \deemph{0} & \frac{\sigma^2_E\left(\omega_F \right) }
                               {\abs{U\left(\omega_F \right)}^2 }
@@
   %TODO: add formulas with cost function etc.
-  To aid convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
+  To improve convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
 
@@
   The observed results were similar and hence are not elaborated further in this text.
-  For more information, please refer to \citep{Larsson2012SYSID}.
+  For more information, please refer to~\citep{Larsson2012SYSID}.
   \end{remark}
@@
   \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
-           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a logarithmic multisine.}%
+           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
   \label{fig:excitation:sumSys}
@@
     The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
-    According to its manual \citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
-    A first guess to realize such a filter is a third-order Chebyshev band-pass filter of Type I \citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
+    According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
+    A first guess to realize such a filter is a sixth-order Chebyshev band-pass filter of Type I~\citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
+    %TODO: datasheet FRF?, pzmap with \damping shown, evt. tabel: per pool-paar: \wn ifv \wc, \damping
     Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
@@
     was estimated using \texttt{elis}~\citep{FDIDENT}.
-    The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.
+    The initial estimate was a sixth-order band-pass type I Chebyshev filter~\citep{Zverev1967} that conformed to the information given in the datasheet~\citep{datasheet_bk1613} to aid convergence to a good optimum.
 
@@
     \input{\thisDir/figs/qlog_a050mall.tikz}
-    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
+    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
+    \TODO{use styles from above}
       \label{fig:excitation:measurements}

### 2016-02-29 config/styles.inc.tex
Add some TODOs
Fix styles + some comments of Johan CH02

@@
 \pgfplotsset{compat=newest}
-%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots
-
-% \def\thisDir{.}
 
@@
 \pgfplotsset{every tick label/.append style={font=\footnotesize}}
-\pgfplotsset{every axis title/.append style={font=\footnotesize, at={(0.5,0.95)}}}
+\pgfplotsset{every axis title/.append style={at={(0.5,1.025)}}}
 \pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}
 
+%http://tex.stackexchange.com/questions/18152/how-can-i-adjust-the-horizontal-spacing-between-legend-entries-in-pgfplots
 \pgfplotsset{legendAbovePlot/.style={legend style={at={(0.5,1.025)},anchor={south},nodes=right,legend columns=-1,font=\footnotesize,draw=none,/tikz/every even column/.append style={column sep=1em}}}}
+
+%TODO: avoid duplicated styles !!
+
+%% Number formatting
+\pgfset{number format/1000 sep={\,}}
 
@@
 
-\definecolor{model}{named}{blue}
+\definecolor{model}{named}{black}
 \definecolor{truesys}{named}{TangoAluminium5}
@@
 
+  \definecolor{bwfill}{named}{TangoAluminium1}
+  \definecolor{bwline}{named}{TangoAluminium5}
+
+  \definecolor{safezone}{named}{bwfill}
+
+%% Marker sizes
+\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
+\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
+\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
+\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
+\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}
+
 %% TikZ styles
@@
 %% marker styles
-  \definecolor{bwfill}{named}{TangoAluminium1}
-  \definecolor{bwline}{named}{TangoAluminium5}
-
-  \definecolor{safezone}{named}{bwfill}
 
@@
 \pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
-\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=0.75pt}}
+\pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
+
+\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
+\pgfplotsset{truesys/.style={color=tangogrey,line width=1pt}}
+\pgfplotsset{mainsys/.style={color=black,line width=1pt}}
+\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
+
+\pgfplotsset{meas/.style={color=meas,only marks,mark=*,mark options={solid},mark size=1pt}}
 
@@
 
-\pgfplotsset{linmsgrid/.style={color=linms,gridline,mark=square*,mark options={solid}}}
-\pgfplotsset{logmsgrid/.style={color=logms,gridline,mark=*,mark options={solid}}}
-\pgfplotsset{clogmsgrid/.style={color=clogms,gridline,mark size=2pt,mark=x,mark options={solid}}}
-\pgfplotsset{plogmsgrid/.style={color=plogms,gridline,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}
-
-\pgfplotsset{linms/.style={color=linms}}
-\pgfplotsset{clogms/.style={color=clogms}}
-\pgfplotsset{rlogms/.style={color=rlogms}}
-\pgfplotsset{qlogms/.style={color=qlogms}}
-\pgfplotsset{plogms/.style={color=plogms}}
-
-\pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
-\pgfplotsset{truesys/.style={color=tangogrey,line width=0.9pt}}
-
-\pgfplotsset{meas/.style={color=meas,only marks,mark=*,mark options={solid},mark size=1pt}}
+\pgfplotsset{linmsgrid/.style={color=linms,gridline,linmsmarker}}
+\pgfplotsset{logmsgrid/.style={color=logms,gridline,logmsmarker}}
+\pgfplotsset{clogmsgrid/.style={color=clogms,gridline,clogmsmarker}}
+\pgfplotsset{plogmsgrid/.style={color=plogms,gridline,plogmsmarker}}
 
@@
 
+%TODO: change these styles?
 \pgfplotsset{linmsmeas/.style={color=linms,densely dashed,line width=0.7pt}}
@@
 
-\pgfplotsset{sigmalinms/.style={linms,connectline}}
-\pgfplotsset{sigmaqlogms/.style={qlogms,connectline}}
-\pgfplotsset{sigmaclogms/.style={clogms,connectline}}
-\pgfplotsset{sigmaplogms/.style={plogms,connectline}}
+\pgfplotsset{sigmaline/.style={solid,line width=0.8pt}}
+\pgfplotsset{sigmalinms/.append style={linms,sigmaline}}
+\pgfplotsset{sigmaqlogms/.append style={qlogms,sigmaline}}
+\pgfplotsset{sigmaclogms/.append style={clogms,sigmaline}}
+\pgfplotsset{sigmaplogms/.append style={plogms,sigmaline}}
+
+\pgfplotsset{biasline/.style={densely dotted}}
+\pgfplotsset{biaslinms/.style={color=biaslinms,linmsmarker,biasline}}
+\pgfplotsset{biasqlogms/.style={color=biasqlogms,qlogmsmarker,biasline}}
+\pgfplotsset{biasclogms/.style={color=biasclogms,clogmsmarker,biasline}}
 
 \pgfplotsset{linrect/.style={fill=linms,draw=linms,line width=1pt}}
-
-\pgfplotsset{linmsgrid/.style={ycomb,color=linms,solid,line width=0.7pt,mark size=1pt,mark=square*,mark options={solid}}}
-\pgfplotsset{logmsgrid/.style={ycomb,color=logms,solid,line width=0.7pt,mark size=1pt,mark=*,mark options={solid}}}
-\pgfplotsset{clogmsgrid/.style={ycomb,color=clogms,solid,line width=0.7pt,mark size=2pt,mark=x,mark options={solid}}}
-\pgfplotsset{plogmsgrid/.style={ycomb,color=plogms,solid,line width=0.7pt,mark size=2pt,mark=triangle,mark options={solid,line width=0.7pt}}}
-
-\pgfplotsset{model/.style={color=model,dashed,line width=1.0pt}}
-\pgfplotsset{truesys/.style={color=truesys,line width=1.0pt}}
-
-\newcommand{\linmsmarker}{mark=square,mark options={solid}}
-\newcommand{\qlogmsmarker}{mark=triangle,mark options={solid}}
-\newcommand{\clogmsmarker}{mark=x,mark size=10pt,mark options={solid}}
 
@@
 \newcommand{\dbdmarker}{mark=triangle,mark options={solid}}
-
-\pgfplotsset{sigmalinms/.append style={color=sigmalinms,solid,line width=0.8pt}}
-\pgfplotsset{sigmaqlogms/.append style={color=sigmaqlogms,solid,line width=0.8pt}}
-\pgfplotsset{sigmaclogms/.append style={color=sigmaclogms,solid,line width=0.8pt}}
-
-\pgfplotsset{biaslinms/.style={color=biaslinms,only marks,mark=x,mark options={solid}}}
-\pgfplotsset{biasqlogms/.style={color=biasqlogms,only marks,mark=triangle,mark options={solid,rotate=180}}}
-\pgfplotsset{biasclogms/.style={color=biasclogms,only marks,mark=o,mark options={solid}}}
 
@@
 
-\pgfplotsset{dbavar/.style={color=dbacolor,solid,line width=1.0pt}}
-\pgfplotsset{dbbvar/.style={color=dbbcolor,solid,line width=1.0pt}}
-\pgfplotsset{dbcvar/.style={color=dbccolor,solid,line width=1.0pt}}
-\pgfplotsset{dbdvar/.style={color=dbdcolor,solid,line width=1.0pt}}
-
-\pgfplotsset{dbamin/.style={color=dbacolor,dashed,line width=1.0pt}}
-\pgfplotsset{dbbmin/.style={color=dbbcolor,dashed,line width=1.0pt}}
-\pgfplotsset{dbcmin/.style={color=dbccolor,dashed,line width=1.0pt}}
-\pgfplotsset{dbdmin/.style={color=dbdcolor,dashed,line width=1.0pt}}
-
-\pgfplotsset{dbamax/.style={color=dbacolor,solid,line width=1.0pt,mark=x ,mark options={solid}}}
-\pgfplotsset{dbbmax/.style={color=dbbcolor,solid,line width=1.0pt,mark=o ,mark options={solid}}}
-\pgfplotsset{dbcmax/.style={color=dbccolor,solid,line width=1.0pt,mark=square  ,mark options={solid}}}
-\pgfplotsset{dbdmax/.style={color=dbdcolor,solid,line width=1.0pt,mark=triangle,mark options={solid}}}
-
 %% Initial values
@@
 \pgfplotsset{FRFNoise/.style={color=FRFNoise,mark=x,mark options={solid},only marks,smallmarkers}}
-
-\pgfset{number format/1000 sep={\,}}
 
@@
 
-\pgfplotsset{mediummarkers/.append style={mark size=1pt}}
-\pgfplotsset{smallmarkers/.append style={mark size=0.75pt}}
-\pgfplotsset{medsmallmarkers/.append style={mark size=0.5pt}}
-\pgfplotsset{tinymarkers/.append style={mark size=0.25pt}}
-\pgfplotsset{extremelytinymarkers/.append style={mark size=0.05pt}}
-
 \pgfplotsset{myDerivs/.style={color=black,solid,line width=1.0pt}}
@@
 
-\pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}
+%TODO: redefine this thingie for LRM chapters
+% \pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}
 
@@
 
-%%
-
 %% TABLE STYLES

### 2016-02-29 ch02-qlogms/excitation-design.tex
fix figure + small stuff
Meeste comments Johan CH02

@@
 
-\item Robust input design one tries to make the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007} and references therein. 
+\item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007} and references therein. 
 While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, vibration analysis and acoustics testing amongst others.
-%TODO{ meer referenties? }
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustics testing amongst others.
+%TODO reference acoustics (ISMA?)
 
@@
   To restore equal excitation signal levels over the complete range of frequencies, we will need to distribute the power in $1/\omega$ over the frequency band.
+  \TODO{cite SYSID2006 papers: Rojas2006, Goodman2006, ...}
   In a noise excitation context, this results in pink noise.
@@
 \end{align}
-where $u(t)$ is a known input sequence, $y(t)$ the output sequence and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
+where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
 $G$ is a rational, time invariant transfer function in continuous time.
@@
 \begin{equation}
-  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
+  G_2(s, \theta) = \frac{\dc \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
 \label{eq:excitation:secondOrderSubsystem}
@@
 \begin{align}
-  \PartialDerivative{G_2}{K} 
+  \PartialDerivative{G_2}{\dc} 
     &= 
+    \frac{G_2}{\dc}
+    =
   \frac{\wn^{2\multiplicity}}{\wz}
@@
     &= 
-    \frac{-K \wn^{2\multiplicity}}
+    \frac{-\dc \wn^{2\multiplicity}}
               {\wz} 
@@
   &= 
-  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
+  \frac{2 \dc \wn^{2\multiplicity-1} \multiplicity}
             {\wz} 
@@
   &= 
-  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
+  \frac{-2 \dc \wn^{2\multiplicity + 1} \multiplicity}
             {\wz}
@@
 The roll-off near the resonance is determined mainly by the damping $\damping$ and the multiplicity $\multiplicity$ of the sub-system.
+The relationship between the frequency of the zero $\wz$ and the resonance frequency $\wn$ alters the shape of these derivatives, but has little impact in the vicinity of the resonance peak.
 As such, the Fisher information matrix is pre-dominantly determined by the input power spectrum near $\wn$.
@@
 \paragraph{System and noise model}
+%TODO: move this paragraph forward (before Fi matrix)
   In the remainder of this chapter, an \gls{OE} setting is used.
@@
 \label{sec:excitation:multisine}
-In contrast to signal with a continuous $1/f$ \gls{PSD} presented in \secref{sec:excitation:logarithmic}, similar results can be obtained by using signals that have a discrete frequency grid.
+In contrast to signals with a continuous $1/f$ \gls{PSD} presented in \secref{sec:excitation:logarithmic}, similar results can be obtained by using signals that have a discrete frequency grid.
 Such signals are presented in this section.
@@
   \end{equation}
+  %TODO: johan: te ingewikkeld (tot 2.5.1 wegdoen)
+  %T
   \begin{definition}[Least common (integer) multiple] \label{def:excitation:lcm-real}
@@
   \begin{equation}
-    f_k = N \cdot \Delta f,\; N \in \NN
+    f_k = N_k \cdot \Delta f,\; N_k \in \NN
     \text{.}
@@
   On the other hand, using \mcode{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
+  For this reason, the grid constructed using $\alpha_k^{\round{}}$, i.e. by using the normal \mcode{round} function, has been used in the remaind of this chapter.
   \end{remark}
@@
   We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
+  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
+  %TODO: mention crest factor? (here compensation/pink hurts)
 
@@
 
-  We normalize the\gls{RMS} value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
+  We normalize the \gls{RMS} value of the excitation signal to $1$ and choose $\sigma_E\left( \omega \right) = 0.1$ for all evaluations.
   The noise level is kept constant, which causes the \gls{SNR} per excited line to drop for more finely spaced excitation signals.

### 2016-02-29 ch02-qlogms/excitation-design.tex
Most comments of Johan addressed

@@
 
-  Consequently, the complete multisine has a period $T_{u(t)}$ that is the common multiple of the period of all its components:
+  Consequently, the complete multisine has a period $T_{u(t)}$ that is the (least) common multiple of the period of its components:
   \begin{equation}
@@
   \end{equation}
-  %TODO: johan: te ingewikkeld (tot 2.5.1 wegdoen)
-  %T
-  \begin{definition}[Least common (integer) multiple] \label{def:excitation:lcm-real}
-  The least common multiple of the set of values $T_k \in \mathbb{F}\without\set{0}$ for $k \in \mathbb{K} \isdef \set{1, \ldots, F}$ is  
-  \begin{equation}
-    \lcm \set{T_1, \ldots, T_F} \isdef
-      \min \Set{T |\forall k \in \mathbb{K}, \exists n_k \in \NaturalNumbersWithoutZero: n_k T_k = T }
-   \end{equation}
-   if such a minimum exists.
-   When $\mathbb{F} \in \Set{\NaturalNumbers, \Integers, \RationalNumbers}$, a minimum always exists.
-   For $\mathbb{F} = \RealNumbers$, a minimum is not guaranteed to exist (see below).
-   % more info: http://mathworld.wolfram.com/LeastCommonMultiple.html
-   \end{definition}
+
   \begin{example}
@@
    The corresponding periods are $T_1 = f_1^{-1} = 1 \unit{s}$ and $T_2 = f_2^{-1} = 1.5 \unit{s}$.
-   The overall period of the multisine is $T = n_1 T_1 = n_2 T_2 = 3 \unit{s}$, i.e. $n_1 = 3$ and $n_2=2$.
+   The overall period of the multisine is $T_{u(t)} = n_1 T_1 = n_2 T_2 = 3 \unit{s}$, i.e. $n_1 = 3$ and $n_2=2$.
   \end{example}
@@
   \begin{example}\label{eg:excitation:non-periodic}
-   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
-   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$ since $T_3$ is an irrational number of seconds (unlike $T_1$ and $T_2$).
-   Consequently, such a generalized `multisine' is not periodic.
+   Consider the generalized multisine with $f_1 = 1 \unit{Hz}$, $f_2 = \pi \unit{Hz}$, and $f_3 = \pi^2 \unit{Hz}$.
+   The corresponding periods are then $T_1 = 1 \unit{s}$, $T_2 = \pi^{-1} \unit{s}$, and $T_3 = \pi^{-2} \unit{s}$.
+   However, a common multiple of those periods cannot be found since there exist no positive integers $n_1$, $n_2$, and $n_3$ that ensure that $T_{u(t)} = n_1 T_1 = n_2 T_2 = n_3 T_3$.
+   As such, this generalized `multisine' is not periodic.
   \end{example}
-  \begin{remark}
-  In practical applications each frequency will be represented as either a fixed-point or floating point number with a limited numerical precision $\eps$.
-  Hence, each frequency line $f_k$ will be approximated by a line at $\round{f_k \eps^{-1}} \eps \isdef m_k \eps$ where $m_k \in \Integers$.
-  The resulting multisine has a period 
-  \begin{equation}
-     T 
-     = \lcm \Set{T_k |  k \in \mathbb{K}} 
-     = \lcm \Set{m_k^{-1} \eps^{-1} |  k \in \mathbb{K}}
-     = \eps^{-1} \lcm \Set{m_k^{-1} |  k \in \mathbb{K}}
-     \text{.}
-  \end{equation}
-  The latter $\lcm$ always exists because $m_k^{-1}  \in \RationalNumbers$ as $m_k \in \Integers$.
-  The resulting period $T$ might, however, might be too long for practical use.
-  E.g.
-when $\eps \approx 1.2\cdot 10^{-7}$ (\code{single} precision), the period of a multisine with components as in Example~\ref{eg:excitation:non-periodic} is $T \approx 8.4 \cdot 10^{6} \unit{s} \approx 97 \unit{days}$.
-  For \code{double} precision, $\eps \approx 2.2 \cdot 10^{-16}$ and the period $T \approx 9 \cdot 10^{6} \unit{year}$.
-  \end{remark}
 
@@
   Consequently, the generalized multisine of \defref{def:excitation:generalized-MS} is not guaranteed to be periodic.
-  In actual implementations with limited numerical precision, this gives rise to signals that are periodic but whose period can be too long to be practically viable for periodic measurements.
-  Consequently, it is undesirable to use generalized multisines that have an overly long period.
 
@@
   For such a frequency grid, it is guaranteed that the signal is periodic in the time domain, unlike for the generalized multisines of the previous section.
+  Moreover, such a signal can be created easily using a waveform generator that has a constant sampling frequency $f_s$.
 
@@
 \subsection{(Ideal) Logarithmic Grid Multisine}
-  For a logarithmic frequency grid $\set{f_1, \ldots, f_F}$ of $F$ lines,
-  the following relation holds between excited frequencies:
+  For a logarithmic frequency grid $\set{f_1, \ldots, f_F}$ of $F$ lines, the following relation holds between excited frequencies:
   \begin{equation}
@@
   for a given lowest frequency $f_0$ and frequency ratio $\alpha > 1$.
-
-  When designing an excitation signal, it is common only to specify a (large) frequency band
-  by its boundary frequencies $f_{\min}$ and $f_{\max}$.
-  For a given $\alpha$ it is easy to determine the number of excited lines
-  within the frequency range of interest:
+  Note that for $\alpha \in \NaturalNumbers$, such a frequency grid is a subset of a linear frequency grid and hence the multisine is periodic.
+  However, when $\alpha \not\in \NaturalNumbers$, the signal is not guaranteed to be periodic (see \egref{eg:excitation:non-periodic}).
+
+  When designing an excitation signal, it is common only to specify a (large) frequency band by its boundary frequencies $f_{\min}$ and $f_{\max}$.
+  For a given $\alpha$ it is easy to determine the number of excited lines within the frequency range of interest:
     \begin{equation}
@@
   First of all, we need to determine the factor $A_k$ needed to correct the power spectrum to match that of a log grid multisine.
-  To this end, one first constructs a log frequency grid $\LOGGRID = \set{\f_1, \ldots, \f_{F'}}$ for a given factor $\alpha$ and the corresponding quasi-log grid $\QLOGGRID = \set{f_1, \ldots, f_F}$ for a resolution $\Delta f$.
-  For each frequency $f_k$ in the quasi-log grid, we define $n\left(f_k\right)$
-  as the number of frequencies in the log grid that are nearer to $f_k$
-  than to any other grid line in the quasi-log grid:
+  To this end, one first constructs a logarithmic frequency grid $\LOGGRID = \set{\f_1, \ldots, \f_{F'}}$ for a given factor $\alpha$ and the corresponding quasi-log grid $\QLOGGRID = \set{f_1, \ldots, f_F}$ for a resolution $\Delta f$.
+  For each frequency $f_k$ in the quasi-log grid, we define $n\left(f_k\right)$ as the number of frequencies in the logarithmic grid that are nearer to $f_k$ than to any other grid line in the quasi-log grid:
 
@@
     \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
+    \TODO{use same color conventions here}
     \label{fig:excitation:freqGrids}
@@
   The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies within the `bulk' of the frequency grid with finite support.
+  \TODO{rule of thumb: when is it bulk or not? $f(\alpha,f_0,\Delta f, \wn, \damping)$}
   This can be understood intuitively by inspecting the derivatives that constitute the Fisher information matrix (see \figref{fig:excitation:derivatives}): those derivatives are significantly larger near the resonance frequency than at other frequencies.
@@
   We do see, however, that the variance in the vicinity of the resonance is lower than in the case of a linearly spaced excitation.
+  \TODO{determine rule-of-thumb: resonance peak $\tuple{\wn,\damping}$ in bulk of grid $\tuple{\alpha,\omega_0,\Delta f}$}
 

### 2016-02-29 ch05-initvals/initial-values.tex
Add some TODOs
Fix flowgraph

@@
 \subsection{Initial Estimates Procedure}\label{sec:init:procedures}
-\begin{figure}
-  \centering
-  \includegraphics
-  [width=\columnwidth]{\thisDir/fig/flowgraph}
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
   \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convext optimization problem.
-  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
+  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 
+  \label{fig:flowgraph}
 \end{figure}
@@
 \begin{enumerate}
-\item
-\emph{Using the true model ($\true{G}$) as initial estimate}
+\item \emph{Using the true model ($\true{G}$) as initial estimate}
 
@@
 
-\item
-\emph{Quadratic approximations of the ML}
+\item \emph{Quadratic approximations of the ML}
 
@@
 
-\item
-\emph{Local polynomial method (LPM) with truncation}
+\item \emph{Local polynomial method (LPM) with truncation}
 
@@
   \input{\thisDir/fig/special-histogram.tikz}
+  %TODO: put legend inside figure (note: subplot magic!!)
   \caption[Performance degradation/enhancement for selecting the second best model.]{
@@
   \input{\thisDir/fig/bodeplots.tikz}
+  %TODO: put legend inside figure (note: subplot magic!!)
   \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
@@
   }
+  %TODO: put legend inside figure (note: subplot magic!!)
   \label{fig:distancesStress}

### 2016-02-29 ch05-initvals/initial-values.tex
Update flowgraph

@@
   \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
-  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convext optimization problem.
+  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convex optimization problem.
   The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 

### 2016-03-01 ch02-qlogms/excitation-design.tex
Vuistregels etc.

@@
   \end{remark}
-  \begin{example}
+  \begin{example} \label{eg:excitation:logarithmicGrid:matlab}
     The \MATLAB code \mcode[mathescape]{f = logspace(log10($f_{\min}$), log10($f_{\max}$), $F$)} produces a logarithmically spaced frequency vector \mcode{f} with $F$ elements in the range $\left[ f_{\min}, f_{\max} \right]$.
@@
 
+  \begin{definition} \label{def:excitation:bulk}
+  We denote the `\term{bulk}' of the quasi-logarithmic frequency grid as the frequency region where $\frac{f_k}{f_{k-1}} \approx \alpha$ can be attained.
+  A necessary condition for $f_k$ to be part of the bulk is that $\Delta f \leq \left(\alpha -1 \right) f_{k-1}$.
+  Equivalently, the bulk can be seen as the frequency interval $\RightOpenInterval{\frac{\Delta f}{\alpha - 1} , +\infty}$.
+  \end{definition}
+
   \begin{definition}
@@
        \label{eq:excitation:qlog:gridDef}
-    f_k & = \alpha_k(N_k) f_{k-1}  
+    f_k & = \alpha_k(n_k) f_{k-1}  
         \quad
@@
       \alpha_k(N_k) & \isdef 
-          \round{   \frac{\alpha^{N_k} f_{k-1}}{\Delta f}}    
+          \round{   \frac{\alpha^{n_k} f_{k-1}}{\Delta f}}    
            \frac{\Delta f}{f_{k-1}}
@@
          \label{eq:excitation:qlog:alphaPowerDef}
-          N_k & \isdef 
+          n_k & \isdef 
             \min 
@@
   On the other hand, using \mcode{round} as in \eqref{eq:excitation:qlog:roundAlpha}, provides a grid that is somewhere in-between both extremes.
-  For this reason, the grid constructed using $\alpha_k^{\round{}}$, i.e. by using the normal \mcode{round} function, has been used in the remaind of this chapter.
+  For this reason, the grid constructed using $\alpha_k^{\round{}}$, i.e. by using the normal \mcode{round} function, has been used in the remainder of this chapter.
   \end{remark}
+
+  \begin{example} \label{eg:excitation:quasilogarithmicGrid:matlab}
+  An easy way to produce a quasi-logarithmic grid in \MATLAB is to first produce the logarithmic grid \code{fLog} as in  \egref{eg:excitation:logarithmicGrid:matlab} and reducing it to a quasi-logarithmic grid with resolution $\Delta f$ using \mcode[mathescape]{f = unique(round(fLog/$\Delta f$))*$\Delta f$}.
+  Note that this is a computationally efficient way since both \mcode{logspace} and \mcode{unique} require at most $\bigO{ F }$ time, where \mcode[mathescape]{$F\;$ = numel(fLog)}.
+  \end{example}
 
@@
 
-  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies within the `bulk' of the frequency grid with finite support.
-  \TODO{rule of thumb: when is it bulk or not? $f(\alpha,f_0,\Delta f, \wn, \damping)$}
-  This can be understood intuitively by inspecting the derivatives that constitute the Fisher information matrix (see \figref{fig:excitation:derivatives}): those derivatives are significantly larger near the resonance frequency than at other frequencies.
-
-  I.e. there should be a few excited frequency lines that are logarithmically spaced, outside of the resonance peak of the actual system.
+  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e.
+$\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
+  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
+  \begin{equation} 
+    \frac{2 \pi \Delta f}{alpha -1} \leq \left( 1 - \damping \right) \wn
+    \text{.}
+    \label{eq:excitation:systemInBulk:generic}
+  \end{equation}
+  For more reliable results, however, it is adviced to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
   In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.
+
+  The validity of this approximation can be understood intuitively by inspecting the derivatives that constitute the Fisher information matrix (see \figref{fig:excitation:derivatives}): those derivatives are significantly larger near the resonance frequency than at other frequencies.
 
@@
   In other words, the resonances of the systems at low frequencies, can no longer be considered to lie within the bulk of the logarithmic part of the quasi-logarithmic frequency grids.
-  We do see, however, that the variance in the vicinity of the resonance is lower than in the case of a linearly spaced excitation.
-  \TODO{determine rule-of-thumb: resonance peak $\tuple{\wn,\damping}$ in bulk of grid $\tuple{\alpha,\omega_0,\Delta f}$}
+  This can also be understood from equation \eqref{eq:excitation:systemInBulk:generic}.
+  In that equation, $\alpha = \alpha^{\star} = 1 + \damping$ such that
+  \begin{equation}
+    2 \pi \Delta f \leq (\damping - \damping^2) \wn
+    \label{eq:excitation:systemInBulk:tuned}
+  \end{equation}
+  is the necessary condition for the system bandwidth to lie within the bulk of the frequency grid when the frequency spacing has been tuned according to \secref{sec:excitation:optimAlpha}.
+  For this simulation, with $\Delta f=1\unit{Hz}$, $\damping=0.05$, this evaluates to $\wn \geq 132 \unit{rad/s} = 21 \unit{Hz}$.
+  The system with $\wR = 20 \unit{Hz} < 21 \unit{Hz}$ is still well-identified, even though `only' $3$ lines are excited in its bandwidth.
+  In that particular case, the frequency grid and the resonance peak are well-aligned ($\beta \approx 0$), which leads to a reduced variance (see also \figref{fig:excitation:worstCaseBeta}).
+
+  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation
 
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+
+\TODO{vuistregels herhalen in kader: $\alpha \sim \damping[\min]$, $\wn[\min] \sim \Delta \omega, \damping[\min]$}
+\TODO{evt. plot vuistregels voor freq.grid.}

### 2016-03-01 ch02-qlogms/excitation-design.tex
More references in CH02

@@
 Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design.
-There are two main solutions to this in the engineering literature:
+There are two main solutions to this in the engineering literature~\citep{Goodwin2006GBO}:
 \begin{enumerate}
-\item Iterative input design where the design updated as more information about the system is available, see e.g. \citep{Hjalmarsson2005,Gevers2005}.
+\item Iterative input design where the design updated as more information about the system is available, see e.g.~\citep{Hjalmarsson2005,Gevers2005}.
 The disadvantage of this approach is that multiple experiments are required to converge to the optimal design.
-Moreover, since the signal is optimized for a specific system model, it is likely that changes in the dynamics might be hard to observe using such a signal.
-
-\item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007} and references therein. 
+Moreover, since the signal is optimized for a specific system model, it is likely that changes in the dynamics are hard to observe using such a signal.
+
+\item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007,Goodwin2006GBO,Rojas2012} and references therein.
 While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
@@
   Hence, an excitation with a flat power spectrum and a linearly spaced frequency grid will over-excite the high end of the band at the cost of the low frequencies.
-  To restore equal excitation signal levels over the complete range of frequencies, we will need to distribute the power in $1/\omega$ over the frequency band.
-  \TODO{cite SYSID2006 papers: Rojas2006, Goodman2006, ...}
+  To restore equal excitation signal levels over the complete range of frequencies, we will need to distribute the power in $1/\omega$ over the frequency band~\citep{Goodwin2006,Goodwin2006GBO}.
   In a noise excitation context, this results in pink noise.

### 2016-03-02 ch02-qlogms/excitation-design.tex
Add guideline boxes

@@
 
+\begin{guideline}[Use quasi-logarithmic multisines as initial excitation.]
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
+\end{guideline}
+
+\begin{guideline}[Ensure $a$ ]
+   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} = \alpha \leq 1 + \damping[\min]$ is required.
+\end{guideline}
+
+\begin{guideline}[Ensure $\Delta \omega < (\damping - \damping^2) \wn \approx \damping \wn$]
+ A quasi-logarithmic multisine with frequency resolution $\Delta \omega$ and tuned frequency spacing $\alpha = 1 + \damping$ allows to identify resonance peaks with $\wn$ well.
+\end{guideline}
+
 \TODO{vuistregels herhalen in kader: $\alpha \sim \damping[\min]$, $\wn[\min] \sim \Delta \omega, \damping[\min]$}

### 2016-03-02 ch02-qlogms/excitation-design.tex
Guidelines improved

--- 2016-03-01 ch02-qlogms/excitation-design.tex
@@
   \begin{equation} 
-    \frac{2 \pi \Delta f}{alpha -1} \leq \left( 1 - \damping \right) \wn
+    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
     \text{.}
@@
 
+\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
+\end{guideline}
+
+\begin{guideline}[Design the logarithmic grid for the damping of the system: $\alpha \leq  1 + \xi_{\min}$]
+   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} \leq \alpha \leq 1 + \damping[\min]$ is recommended.
+   Smaller frequency ratios provide more measurement points at the cost of a reduced \gls{SNR} per frequency bin.
+   As such, $\alpha = 1 + \damping$ provides a nice trade-off: it has the required resolution and the best \gls{SNR} per bin.
+\end{guideline}
+
+\begin{guideline}[Ensure $\Delta \omega < (\damping - \damping^2) \wn \approx \damping \wn$]
+ A quasi-logarithmic multisine with frequency resolution $\Delta \omega$ and tuned frequency spacing $\alpha$ is only guaranteed to properly excite resonances
+\end{guideline}
+
 \TODO{vuistregels herhalen in kader: $\alpha \sim \damping[\min]$, $\wn[\min] \sim \Delta \omega, \damping[\min]$}

### 2016-03-02 ch05-initvals/initial-values.tex
Vuistregels etc.
Guidelines improved

@@
 \begin{algorithmic}[1]
-  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon(\theta)^{\TT} \epsilon(\theta)$. 
+  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \InnerProductSelf{\epsilon(\theta)}$. 
 \Function{LevenbergMarquardt}{$\epsilon(\theta),  \theta^{\mathrm{init}}$}
@@
 
+\begin{guideline}[Try regularization to improve convergence]
+\label{guide:initvals:try-regularization}
+Regularized estimators, such as \gls{RFIR}, sometimes provide better estimates than the `true' model parameters.
+\end{guideline}
+
+\begin{guideline}[Try different initial values for non-convex optimization]
+\label{guide:initvals:try-many-initial-values}
+Trying different initial values is quite inexpensive, but the quality of the final model may improve by several order of magnitude if a local minimum can be avoided.
+As such, using multiple initial values, especially ones that have been derived with good judgment, pays off.
+\end{guideline}
+
 \section{Conclusion}\label{se:Conclusion}

### 2016-03-03 config/styles.inc.tex
fix figure + small stuff
Update styles of grids

@@
 
-\definecolor{linms}{named}{TangoScarletRed3}
+\definecolor{linms}{named}{TangoSkyBlue3}
 \definecolor{logms}{named}{TangoChameleon2}
 \definecolor{qlogms}{named}{TangoPlum3}
-\definecolor{clogms}{named}{TangoSkyBlue3}
-\definecolor{plogms}{named}{black}
+\definecolor{clogms}{named}{TangoScarletRed3}
+\definecolor{plogms}{named}{TangoOrange3}
 
@@
 
-\definecolor{biaslinms}{named}{TangoScarletRed1}
+\definecolor{biaslinms}{named}{TangoSkyBlue1}
 \definecolor{biasqlogms}{named}{TangoPlum1}
-\definecolor{biasclogms}{named}{TangoSkyBlue1}
+\definecolor{biasclogms}{named}{TangoScarletRed1}
 
@@
 \definecolor{dbdcolor}{named}{TangoOrange2}
-
-\definecolor{linms}{named}{TangoScarletRed3}
-\definecolor{logms}{named}{TangoChameleon2}
-\definecolor{qlogms}{named}{TangoPlum3}
-\definecolor{clogms}{named}{TangoSkyBlue3}
-\definecolor{plogms}{named}{black}
 
@@
 \pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
+\pgfplotsset{signalhighlight/.style={ycomb,color=signal,solid,line width=1pt,mark=o,mark size=2pt}}
 
@@
 %TODO: change these styles?
-\pgfplotsset{linmsmeas/.style={color=linms,densely dashed,line width=0.7pt}}
-\pgfplotsset{qlogmsmeas/.style={color=qlogms,densely dotted,line width=0.7pt}}
+\pgfplotsset{linmsmeas/.style={color=linms,solid,line width=0.7pt}}
+\pgfplotsset{qlogmsmeas/.style={color=qlogms,solid,line width=0.7pt}}
 \pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}

### 2016-03-03 ch02-qlogms/excitation-design.tex
Guidelines improved

--- 2016-03-01 ch02-qlogms/excitation-design.tex
@@
       = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
-    \text{.}
-  \end{equation}
+  \end{equation}
+  if a common multiple exists, i.e. $T_{u(t)} = n_1 T_1 = \ldots = n_F T_F$ with $n_i \in \NaturalNumbersWithoutZero$ for $i \in \set{1,\ldots,F}$.
 
@@
     \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
-    \TODO{use same color conventions here}
     \label{fig:excitation:freqGrids}
@@
 
+   \begin{guideline}[Design the logarithmic grid for the damping of the system: $\alpha \leq  1 + \xi_{\min}$]
+   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} \leq \alpha \leq 1 + \damping[\min]$ is recommended.
+   Smaller frequency ratios provide more measurement points at the cost of a reduced \gls{SNR} per frequency bin.
+   As such, $\alpha = 1 + \damping \isdef \alpha^{\star}$ provides the required resolution and the best \gls{SNR} per bin.
+\end{guideline}
+
   Choosing a finer grid will not improve the estimated $G\left( \wM \right)$ significantly, but will rather produce an \gls{FRF} where the \gls{SNR} per bin is decreased.
@@
   This can also be understood from equation \eqref{eq:excitation:systemInBulk:generic}.
-  In that equation, $\alpha = \alpha^{\star} = 1 + \damping$ such that
+  In that equation, $\alpha = \alpha^{\star} = 1 + \damping$ (see \secref{sec:excitation:optimAlpha}) such that the following guideline is the necessary condition for the $3\unit{dB}$ bandwidth of the system to lie within the bulk of the frequency grid.
+
+\begin{guideline}[Choose $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
+\label{guide:excitation:systemInBulk:tuned}
+ A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonances peaks with damping $\damping$ and resonance frequency $\wn$ when
   \begin{equation}
     2 \pi \Delta f \leq (\damping - \damping^2) \wn 
+    \approx \damping \wn \text{ if $\damping \ll 1$}
+    \text{.}
     \label{eq:excitation:systemInBulk:tuned}
   \end{equation}
-  is the necessary condition for the system bandwidth to lie within the bulk of the frequency grid when the frequency spacing has been tuned according to \secref{sec:excitation:optimAlpha}.
-  For this simulation, with $\Delta f=1\unit{Hz}$, $\damping=0.05$, this evaluates to $\wn \geq 132 \unit{rad/s} = 21 \unit{Hz}$.
+  \end{guideline}
+
+  \begin{remark}
+  \guideref{guide:excitation:systemInBulk:tuned} can be interpreted either as
+  \begin{itemize}
+     \item  a lower limit on the allowable $\wn$ of the system (when the multisine has been designed ($\Delta f$ and $\damping$ are fixed)), or 
+     \item as a requirement on the measurement time $\Tm = (\Delta f)^{-1}$ when lower bounds on $\damping$ and $\wn$ are known.
+   \end{itemize}
+  \end{remark}
+
+  For this simulation, with $\Delta f=1\unit{Hz}$, $\damping=0.05$, \eqref{eq:excitation:systemInBulk:tuned} evaluates to $\wn \geq 132 \unit{rad/s} = 21 \unit{Hz}$.
   The system with $\wR = 20 \unit{Hz} < 21 \unit{Hz}$ is still well-identified, even though `only' $3$ lines are excited in its bandwidth.
@@
 
-  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation
+  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation.
 
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
-
-\TODO{vuistregels herhalen in kader: $\alpha \sim \damping[\min]$, $\wn[\min] \sim \Delta \omega, \damping[\min]$}
-\TODO{evt. plot vuistregels voor freq.grid.}

### 2016-03-03 front-and-back-matter/frontmatter.tex
Update title page + summary
List of Guidelines
Guidelines improved

@@
-\input{front-and-back-matter/summary.inc.tex}
 \input{front-and-back-matter/acknowledgements.inc.tex}
@@
 \listoftables
+
+%http://tex.stackexchange.com/questions/74857/toc-like-list-of-definitions-using-theorem-environments
+\renewcommand{\listtheoremname}{List of Guidelines}
+\listoftheorems[ignoreall,show=guideline]
+
 % \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this
 
-\printglossary[type=\acronymtype,style=long,toctitle={List of Acronyms}, title={List of Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
+\printglossary[type=\acronymtype,style=long,toctitle={List of Abbreviations}, title={List of Abbreviations}] %TODO: change format
+
 \glsaddall[types=symbols]

### 2016-03-03 ch02-qlogms/excitation-design.tex
Fix guidelines

@@
 Using the same logic as in \secref{sec:excitation:ex:sumOfSecondOrderSipmle}, this means that the variance of the complete system is approximately equal to the variance obtained for each sub-system, due to the decoupling of the Fisher information matrix.
-
-\paragraph{System and noise model}
-%TODO: move this paragraph forward (before Fi matrix)
-  In the remainder of this chapter, an \gls{OE} setting is used.
-  Denote
-    $U  \left(\omega\right)$ as the excitation signal,
-    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
-    $E  \left(\omega\right)$ for the output noise source,
-    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
-    The output noise is assumed to be zero-mean and white with a standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
-
-  \begin{figure}[h]
-    \centering
-    \input{\thisDir/figs/oesetup.tikz}
-    \caption[Output-error]{Output-error set-up.}
-    \label{fig:excitation:OE}
-  \end{figure}
 
@@
 
+  Denote
+    $U  \left(\omega\right)$ as the excitation signal,
+    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
+    $E  \left(\omega\right)$ for the output noise source,
+    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
+    The output noise is assumed to be zero-mean and white with a standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.
+
+  \begin{figure}[h]
+    \centering
+    \input{\thisDir/figs/oesetup.tikz}
+    \caption[Output-error]{Output-error set-up.}
+    \label{fig:excitation:OE}
+  \end{figure}
+
   As in \citep{Pintelon2012, Gallager2008, matrixcookbook}, and equivalently to the derivation in \secref{sec:excitation:inputDesign}, the covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function $G(\theta,\omega)$ can be shown to be approximately equal to
@@
   \end{equation}
-  For more reliable results, however, it is adviced to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
+  %TODO: turn this into a guideline?
+  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
   In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+
+\TODO{move this guideline somewhere else}
+\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
+\end{guideline}

### 2016-03-04 ch04-lrmhinf/paper.tex
Add some TODOs
Split out Avis photo
Improvements CH04

@@
-% \renewcommand{\glsgroupskip}{}
-% \glsdisablehyper
-
+\TODO{
+  \begin{itemize}
+    \item fix labels for chapter
+    \item add section from Benchmark paper
+    \item fix some bib entries
+    \item Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)
+  \end{itemize}
+}
 \input{\thisDir/styles.inc.tex}
@@
 $
-However, in a finite measurement time, non-parametric approaches only allow access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
+However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
 As such, \eqref{eq:HinfNormSISO} can be rewritten as
@@
 An example of such local models is shown in \figref{fig:interpol-quantities}.
-Two alternative methods allow to evaluate~\eqref{eq:gamma-inter-grid} practically.
+Two alternative methods allow evaluation of~\eqref{eq:gamma-inter-grid} in practice.
 
@@
   The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
+  \TODO{top subplot has a line connecting the last to the first point...}
 \label{fig:interpol-quantities}
@@
 The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
-
-Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems.
+Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE} and using the same logic as in \chapref{sec:excitation}.
 As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
@@
 This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
-By normalizing the conclusions for the time constant $\tau$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\xi$.
-Specifically, the system's $\tau \isdef (\xi\omega_{\mathrm{n}})^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\xi$ is the relative damping and $\omega_{\mathrm{n}}$ the undamped natural frequency.
+By normalizing the conclusions for the time constant $\timeconst$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\damping$.
+Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the undamped natural frequency.
 
@@
 \end{equation}
-which has $\tau = 50 \unit{samples}$ (i.e. $\xi=0.02$ and $\omega_{\mathrm{n}} = 1 \unit{rad/S}$).
+which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
 The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
@@
 To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:LPMHinf}.
-The values of $N \in \ClosedInterval{35}{16 000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
+The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
 These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
@@
   %\input{figures/runLength.tikz}
-  \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\tau$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
-  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \tau$).
+  \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
 A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}.
@@
 
-It can be seen in \figref{fig:MC-run-length} that $N \geq 20\tau$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
+It can be seen in \figref{fig:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
 $\expectedValue{\gamma_{\mathrm{FRF}}} \approx \gamma$.
-Starting from about $N=4 \text{ to } 5\tau$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
+Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
 For long experiments $(N \to \infty)$, the true $\norm{\Delta}$ is recovered.
@@
   \centering
+  \setlength\figurewidth{0.75\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
+  \caption{\Glsentryfirst{AVIS}.}
+  \label{fig:avis}
+\end{figure}
+
+\begin{figure}
+ \centering
     \setlength{\figurewidth}{0.75\columnwidth}
@@
  \label{fig:avis-frf}
- \label{fig:avis}
 \end{figure}

### 2016-03-04 ch05-initvals/initial-values.tex
CH05: some comments from Tom

@@
 The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
-Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
+Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
 Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.
@@
 Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}.
- Maximizing the likelihood function of the parameters probably yields a common, consistent, and efficient estimator.
- However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization.
- As for many nonlinear optimization problems, this often involves an iterative algorithm to produce the optimal model.
+Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.
+This often involves an iterative algorithm to produce the optimal model.
  The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima.
  Hence, good initial estimates are essential to obtain a high quality model estimate.
+ In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is both consistent and efficient and is a commonly used estimator.
+ Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values.
 

### 2016-03-04 ch05-initvals/initial-values.tex
Some comments from Tom (CH05)

@@
 
-The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
+The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using classical (deterministic) optimization algorithms.
 Hence, such techniques make it possible to increase the ``success rate'' (i.e.
 the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
-%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
 
@@
 These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
-%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).
 
@@
 \subsection{System Setup Framework and Model}
+\TODO{ hele subsectie verplaatsen na het param. sys. model?}
 \figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic \gls{LTI} discrete-time \gls{SISO} system, subjected to a known white random noise input.
@@
 \end{equation}
-%\comment{We don't have any results with colored noise yet!}
 where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
@@
 \begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{} \IntegerNumbers
+    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{}  \text{with}  n \in \IntegerNumbers
 \label{ABpolys}
@@
    +  |B(k,\theta)|^2\sigma_U^2(k) \\
-  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
+  &- 2\RealPart \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
 \end{split}
@@
 \begin{remark}
-Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
-This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
+Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since such algorithms use randomization either to select initial values or to iterate towards the optimum (or both).
+However, due to this random influence, their results are not always exactly reproducible and can incur a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
 Stochastic optimization is not discussed in the remainder of this chapter.
@@
 
-  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
+  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
+  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $n=3$, such that
 \begin{subequations}\label{lpmImplQuadG}
@@
 where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
-In this instance, $n=3$.
+\TODO{notatie LPM uniform maken met CH03/CH04}
 
@@
 
-The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
+The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.,
 \begin{equation}
@@
 The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
-Here, the \gls{DCkernel} is used. 
+Here, the \gls{DCkernel}~\citep{Chen2012,Pillonetto2010} is used. 
 Specifically, the element at $t_1,t_2$ of $P$ is given by
@@
  for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
- The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
+ The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2013}:
 \begin{align}

### 2016-03-06 ch05-initvals/code/testCost_ifv_SNR.m
Trial code: noise vs optima for simple case

@@ -1,0 +1,71 @@
+% Trial: noise introduces local minima in cost func
+%
+% Idea: use first order system (just pole)
+close all;
+clear variables;
+clc;
+
+p0    = 1;
+s     = tf('s');
+G0    = p0/(s-p0);
+model = @(p,w) p./(1i*w - p).';
+
+p     = logspace(-1,+1,101);
+% p     = linspace(0.5,5,101); % closer scale
+SNR   = logspace(-3,2,50);
+w     = logspace(log10(min(p))-1,log10(max(p))+1,50);
+
+FRF0  = squeeze(freqresp(G0, w));
+
+randccn = @(varargin) (randn(varargin{:}) + 1i*randn(varargin{:}))/sqrt(2);
+noise = randccn(size(FRF0)); % one noise realization
+
+noisy = @(FRF, SNR) FRF.*(1+noise/SNR);  % relative error
+%noisy = @(FRF, SNR) FRF+noise/SNR ; % absolute error
+
+L2cost = @(theta, SNR)(sum(abs(model(theta, w) - noisy(FRF0, SNR)).^2)/numel(w));
+
+cost  = L2cost;
+
+% cost  = @(theta, SNR) L2cost(theta, SNR)./L2cost(p0, SNR); % relative cost
+%  cost  = @(theta, SNR) L2cost(theta, SNR).*SNR.^2; % relative cost
+
+[pp, SNRSNR] = meshgrid(p, SNR);
+V = arrayfun(cost, pp, SNRSNR);
+
+
+%% find optimum per SNR
+[minV, idxMin] = min(V,[],2); % find minimizer over the parameter space (per SNR)
+Vminima = diag(V(:, idxMin));
+
+%% normalize plot
+[maxV, idxMax] = max(V,[],2); 
+dV = maxV - minV;
+Vscaled = bsxfun(@rdivide, bsxfun(@minus, V, minV), dV);
+VscMin = diag(Vscaled(:,idxMin));
+
+%%
+figure('name','Cost function'); hold on;
+% plotter = @waterfall;
+plotter = @mesh;
+
+plotter(p, SNR, (V));
+plot3(p(idxMin), SNR, Vminima, 'LineWidth', 2, 'Color','k')
+
+xlabel('\theta','interpreter','latex');
+ylabel('SNR')
+zlabel('Cost Function');
+set(gca,'XScale','log','YScale','log','ZScale','log','YDir','reverse')
+
+%% 
[…]

### 2016-03-06 ch05-initvals/initial-values.tex
Address some comments from Tom (CH05)

@@
 This often involves an iterative algorithm to produce the optimal model.
- The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima.
+ The resulting model, however, depends on which initial estimates are used to start up the optimization process: typically one can end up in local minima, leading to models of sub-optimal quality.
  Hence, good initial estimates are essential to obtain a high quality model estimate.
- In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is both consistent and efficient and is a commonly used estimator.
- Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values.
+ In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is commonly used and has desirable properties such as efficiency and consistency.
+ Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
+ Hence, the presented approach is orthogonal to initialization schemes such as the work of \citet{vanHerpen2014}.
 
@@
 
-The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using classical (deterministic) optimization algorithms.
+The main aim and contribution of this chapter is to demonstrate that smoothing a measured \gls{FRF} non-parametrically, helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using classical (deterministic) optimization algorithms.
 Hence, such techniques make it possible to increase the ``success rate'' (i.e.
@@
 
+\paragraph{Outline}
 The rest of the chapter is structured as follows. 
@@
 \section{Problem formulation}\label{se:ProbForm}
-%\begin{itemize}
-%\item
-%Block schematic of the output error framework
-
-%\JL{In this section, the assumptions on the system and the noise are given, and the associated Maximum Likelihood estimator, formulated in the frequency domain.
-The latter turns out to be a non-convex function in the parameters, requiring initial estimates.
-The obtention of those is discussed in the subsequent section.}
 
@@
 \end{equation}
-where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known?
-where do you use that?
-how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$.
-Isn't it the same thing?},
-%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
-and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
+where $\sigma_Y^2$ is independent of $k$ for white noise, and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
 Here, $\overline{B}$ denotes the complex conjugate of $B$.
-%\comment{use $\sigma^2_U$ instead}
 
@@
 
-%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}.
-These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$.
-These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$).
-Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}
-
 The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}.
@@
 where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
-Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
+Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
 Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
@@
  for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
- The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2013}:
+ The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes~\citep{Carlin2000,Gelman2014}, i.e.
+as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2012}:
 \begin{align}
@@
 
-An implementation of the \gls{RFIR} estimator is available as the \mcode{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \mcode{arxoptions}.
-The hyperparameters can be determined via \mcode{arxregul}.
+An implementation of the \gls{RFIR} estimator is available as the \mcode{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \mcode{arxOptions}.
+The hyperparameters can be determined via \mcode{arxRegul}.
 More information about the \gls{RFIR} estimator can be found in
@@
 
-A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
+A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
 
@@
 The capability is quantified by defining the success rate of the initial estimate as the probability that the identification algorithm reaches the \emph{best local optimum} when the selected initial estimate is used.
-%using the selected initial estimate.
-
-The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
-\begin{equation}
-\eta_{\bullet}=\Prob{\model{\bullet}=\model{\trueSymbol}}
+Note that probability in this context should be understood with respect to different realizations of the input signal and disturbing noise.
+
+The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is expressed mathematically as the probability function
+\begin{equation}
+\successRate_{\bullet} = 
+  \Prob{  \model{\bullet}=\model{\trueSymbol}  }
+\text{.}
 \end{equation}
@@
 \begin{equation}\label{eq:successrateTol}
-\eta_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < tol}
-\end{equation}
-with $tol$ a numerical tolerance that will be specified later on.
+\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance}
+\end{equation}
+with $\absoluteTolerance$ a numerical tolerance that will be specified later on.
+
 \begin{remark}
@@
 \begin{equation}
-\eta_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < rel.tol  \norm[2]{\true{G}}}
+\successRate_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < \relativeTolerance  \norm[2]{\true{G}}}
 \text{.}
@@
 In this chapter, the absolute criterion is used.
-However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\eta$ is only mildly sensitive towards the tolerance $tol$ (or $rel.tol$) when the tolerance is chosen with care.
-Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $tol = rel.tol \norm[2]{\true{G}}$.
+However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\successRate$ is not sensitive towards the tolerance $\absoluteTolerance$ (or $\relativeTolerance$) when the tolerance is chosen with care.
+Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $\absoluteTolerance = \relativeTolerance \norm[2]{\true{G}}$.
 \end{remark}
 
+\begin{remark}
+
+\end{remark}
+
 % \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered.
-Note that it is not obvious to determine a tolerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate.
+Note that it is not obvious to determine a gerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate.
 On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
@@
 
-The norm used in equation \eqref{eq:successrateTol} is defined as
+The $\mathcal{L}_2$ norm used in equation \eqref{eq:successrateTol} is defined~\citep{Skogestad2005} as
 \begin{align}
@@
  which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
-%\comment{EG: The exact implementation is in the L2Norm function.
-Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr.
-testDistance).
-I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
-%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
 The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.
-
-% !TEX root =  InitialValuesPaper.tex
-
 \section{Demonstration}\label{se:Demo}
@@
 Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
-This allows to empirically estimate the success rate $\eta$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
+This allows to empirically estimate the success rate $\successRate$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
 
@@
 In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
-This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
-This effectively shows an empirical cumulative distribution function of the distance measure $\norm{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}
+This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
+This effectively shows an empirical cumulative distribution function of the distance measure $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}
 
@@
 \begin{enumerate}
-  \item `good' estimates which have $\|\model{\bullet} - \model{\trueSymbol} \|_2 < tol \approx 6 \cdot 10^{-5}$,
+  \item `good' estimates which have $\norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance \approx 6 \cdot 10^{-5}$,
   \item `poor' estimates which are much further from $\model{\trueSymbol}$.  This is caused by the local optima.
@@
 The obvious jump of the observed distances of the final parametric estimates shows that both classes can be separated reliably.
-The index at which this jump occurs is a direct (visual) indication of the success rate $\eta$ of the corresponding strategy to obtain initial values.
+The index at which this jump occurs is a direct (visual) indication of the success rate $\successRate$ of the corresponding strategy to obtain initial values.
 This indicates $\frac{147}{200} \approx 74\%$ success for the existing methods, $\frac{189}{200} \approx 95\%$ for the truncation method and $100\%$ for RFIR in \figref{fig:single-sim}.
@@
 In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
-The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
-The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
+Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\successRate$.
+The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\successRate$ is real-valued (but limited to the interval $[0,1]$).
+The inherent discreteness of $\hat{\successRate} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
 A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
@@
 \begin{equation}
-\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
+\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\successRate} \pm z_{1-\alpha/2} \sqrt{\hat{\successRate} (1-\hat{\successRate}/N_{\MC})}
 \end{equation}
@@
 However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e.
-when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta \leq 1$~\citep{Ross2003}.
+when $\successRate \approx 0$ or $\successRate \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \successRate \leq 1$~\citep{Ross2003}.
 An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934}.
 In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
-In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
-\begin{align}
- \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
- \underline{\eta} &\isdef 
+In particular, the $(1-\alpha)$  confidence bounds on $\successRate$ are given by~\citep{Clopper1934}
+\begin{align}\label{eq:initvals:Binomial:CI}
+ \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\successRate}, \overline{\successRate} \right]\\
+ \underline{\successRate} &\isdef 
   \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
-  \overline{\eta} &\isdef
+  \overline{\successRate} &\isdef
   \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
 \end{align}
-where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution.
+where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution. %TODO: maybe add reference for Beta distribution
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
@@
 
-By aggregating the results for the different simulations and retaining the success rate $\eta$ only, a clearer view of the performance of the different methods is obtained.
+By aggregating the results for the different simulations and retaining the success rate $\successRate$ only, a clearer view of the performance of the different methods is obtained.
 
@@
 \paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
-A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.\ success rate~$\geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
+A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.
+$\successRate \geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
 The range of improvement is approximately 5 dB where the success rate is above $90\%$.
@@
   \input{\thisDir/fig/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\eta$  obtained using the smoothers, i.e.
+ \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e.
 $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
-The $95\%$ confidence intervals are indicated by bars.}
+The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
   \label{fig:successRateVS_SNR36N3dB}
@@
 \toprule
-\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta} [\%]$  &  $\eta_{\mathrm{exist}} [\%]$ &  $\eta_{\mathrm{trunc}} [\%]$   &  $\eta_{\mathrm{RFIR}} [\%]$  &  $\eta_{\mathrm{best}} [\%]$ \\
+\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\successRate} [\%]$  &  $\successRate_{\mathrm{exist}} [\%]$ &  $\successRate_{\mathrm{trunc}} [\%]$   &  $\successRate_{\mathrm{RFIR}} [\%]$  &  $\successRate_{\mathrm{best}} [\%]$ \\
 \midrule
@@
 The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
-In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}} < tol$.
+In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $\absoluteTolerance = 0.02$ is used when success is determined as $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}} < \absoluteTolerance$.
 This is equivalent to the relative criterion of success since $\norm[2]{\true{G}} = 1$ for all systems.
@@
 \begin{itemize}
-  \item In many of the tested situations (cases 1,3,13-16), all methods yield a good model quality.
+  \item In many of the tested situations (cases 1,3,13--16), all methods yield a good model quality.
   \item In some situations (cases 8, 10, 12), the model quality is generally poor. 
@@
   Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
-  \item The RFIR performs (significantly) better than the existing methods in various cases (4-7, 9, 11).
+  \item The RFIR performs (significantly) better than the existing methods in various cases (4--7, 9, 11).
   \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.

### 2016-03-06 ch05-initvals/initial-values.tex
Add systems from stress test

@@
 
-\TODO{bedoeling duidelijker stellen }
-
 \section{Introduction}
@@
  Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
- Hence, the presented approach is orthogonal to initialization schemes such as the work of \citet{vanHerpen2014}.
+ Hence, the presented approach is orthogonal to initialization schemes such as the work of~\citet{vanHerpen2014}.
 
@@
 In this section, the assumptions on the system and the noise are presented, together with the associated MLE (formulated in the frequency domain), which turns out to be a non-convex function in the parameters, requiring initial estimates.
-The procedure for obtaining the initial estimates is discussed in the subsequent sections.
+The procedure for obtaining the initial estimates is elaborated in the subsequent sections.
 
@@
 
-The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}.
-These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t.
-$\theta$.
+The \gls{GTLS} and the \gls{BTLS} have been presented in \citep{Pintelon1998}. 
+These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
 These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
@@
 %\JL{
-%The main contribution of this paper is to demonstrate that $\hat G_\mathrm{trunc}$ (third path) yields an improvement over $\hat G_\mathrm{exist}$ (second path).
+%The main contribution of this paper is to demonstrate that $\model{trunc}$ (third path) yields an improvement over $\model{exist}$ (second path).
 \comment{JL: these symbols haven't been introduced yet.
@@
 
-\begin{remark}
-
-\end{remark}
-
-% \comment{JL to EG: It is better to implement the success rate as given in \eqref{eq:successrateTol}, because that can more easily be adhered.
-Note that it is not obvious to determine a gerance on the difference between the estimated and the true model, because that depends on the noise variance of the estimate.
-On the other hand, the tolerance in \eqref{eq:successrateTol} and \eqref{eq:toldef} is independent of the noise variance.
-%\comment{\EG{it is implemented that way now}}
-% }
-
 The $\mathcal{L}_2$ norm used in equation \eqref{eq:successrateTol} is defined~\citep{Skogestad2005} as
@@
  which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
-The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.
+The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{se:CompuSR}.
+
+\begin{remark}
+The specific norm that is used in~\eqref{eq:successrateTol} can be adapted to suit the eventual purpose of the models the user wants to obtain.
+E.g. in robust control, it often makes sense to rather have a $\Hinf$ norm as in \chapref{sec:hinf} than an $\mathcal{L}_2$ norm.
+In this chapter, the $\mathcal{L}_2$ norm has been chosen since this is more closely related to the cost function~\eqref{eq:MLEcf}.
+\end{remark}
+
 \section{Demonstration}\label{se:Demo}
@@
 
-Two systems are considered. The first, with a quality factor $Q = 6\unit{dB}$, has the transfer function
-  \begin{equation}
-     \true{G}(z) \Big|_{Q=6\unit{dB}}
-    = 1.74 \cdot 10^{-3}
+Two systems are considered. 
+The first, with a quality factor $Q = 6\unit{dB}$, has the transfer function
+  \begin{equation}
+     \true{G}(z)
+    \approx 
+    1.74 \cdot 10^{-3}
     \frac{ z^2 + 2 z + 1 }
          { z^2 - 1.93 z + 0.94}
+    \qquad 
+    \text{ for } Q = 6 \unit{dB}
     \label{eq:systemundertest}
@@
   \begin{equation}
-    \true{G}(z) \Big|_{Q=20\unit{dB}}
-    = 309 \cdot 10^{-6}
+    \true{G}(z)
+    \approx
+    309 \cdot 10^{-6}
             \frac{z^2 + 2 z + 1}
                  {z^2 - 1.98 z + 0.989}
+    \qquad 
+    \text{ for } Q = 20 \unit{dB}
     \label{eq:systundertest-20dB}
@@
 
-Both systems are low-pass Chebyshev filters shown in \figref{fig:exampleFRF}. 
+Both systems are low-pass Chebyshev filters which have been generated using the \MATLAB command \mcode[mathescape]{cheby1(2, $\,Q$, 0.05)}. 
+Their transfer functions are shown in \figref{fig:exampleFRF}.
 Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
@@
  and different estimates $\model{exist}$
- %\comment{JL: does it matter whether it is $\hat G_\mathrm{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
+ %\comment{JL: does it matter whether it is $\model{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
  that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
- The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, discussed later.
+ The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, which are discussed later on in this chapter.
 
@@
  Estimation `failures' can be attributed to the optimization procedure getting stuck in local optima, resulting in very poor estimates of $\true{G}(\omega)$ over broad frequency ranges, as seen in \figref{fig:exampleFRF}.
- %In \figref{fig:exampleFRF}, it can be seen that these \ML{`failures' result inprovide a very poor estimate of $\true{G}(\omega)$ over the broad frequency ranges.
- %Consequently, such estimates are practically worthless as an approximation of $\true{G}$.
- Consequently, such estimates are practically worthless approximations of $\true{G}$.
+ Consequently, such estimates are approximations of $\true{G}$ that are practically worthless for most applications.
  %}
@@
 
-The success rates of $\hat G_\mathrm{exist}$, $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{RFIR}$ are depicted in  \figref{fig:successRateVS_SNR36N3dB} for two different numbers of sample points within the $3\unit{dB}$ bandwidth, and for a range of SNR values.
+The success rates of $\model{exist}$, $\model{trunc}$ and $\model{RFIR}$ are depicted in  \figref{fig:successRateVS_SNR36N3dB} for two different numbers of sample points within the $3\unit{dB}$ bandwidth, and for a range of SNR values.
 A close scrutiny of  \figref{fig:successRateVS_SNR36N3dB} reveals the following observations: \begin{itemize}
 \item The success rates increase with increasing SNR values, as expected.
-\item For very low SNR values (below $0\unit{dB}$), $\hat G_\mathrm{exist}$ and $\hat G_\mathrm{trunc}$ are unreliable, whereas $\hat G_\mathrm{RFIR}$ is reliably successful. 
+\item For very low SNR values (below $0\unit{dB}$), $\model{exist}$ and $\model{trunc}$ are unreliable, whereas $\model{RFIR}$ is reliably successful. 
 \item For relatively high SNR ($20\unit{dB}$), all three estimators perform equally well.
-\item For moderate SNR values, the success rate of $\hat G_\mathrm{trunc}$ lies above that of $\hat G_\mathrm{exist}$.
+\item For moderate SNR values, the success rate of $\model{trunc}$ lies above that of $\model{exist}$.
 \item The RFIR-based estimate exhibits a success rate of, at least, $97\%$ for all studied conditions. 
@@
 %\JL{An important conclusion can be drawn from the last observation, in the range of the SNR where the success rate almost reaches 100\%.
-Namely, it tells us to what extent the estimator $\hat G_\mathrm{trunc}$ allows the SNR to be decreased before the estimator gets a too high fail rate.
-In other words, it shows that $\hat G_\mathrm{trunc}$ is more reliable at lower SNRs than $\hat G_\mathrm{existing}$.}
+Namely, it tells us to what extent the estimator $\model{trunc}$ allows the SNR to be decreased before the estimator gets a too high fail rate.
+In other words, it shows that $\model{trunc}$ is more reliable at lower SNRs than $\model{existing}$.}
 %\JL{
-As far as $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{exist}$ are concerned, the observations on \figref{fig:successRateVS_SNR36N3dB} clearly reveal the extent to which the estimator $\hat G_\mathrm{trunc}$ allows for the SNR to be decreased before the estimator attains too high a fail rate.
-In other words, it shows that, at low SNR values $\hat G_\mathrm{trunc}$ is more reliable than $\hat G_\mathrm{exist}$.
-
-%\comment{JL: do we have the numerical results to add a remark like: At an SNR of xdB, the respective success rates of $\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{existing}$ are $90\%$ and $95\%$.
+As far as $\model{trunc}$ and $\model{exist}$ are concerned, the observations on \figref{fig:successRateVS_SNR36N3dB} clearly reveal the extent to which the estimator $\model{trunc}$ allows for the SNR to be decreased before the estimator attains too high a fail rate.
+In other words, it shows that, at low SNR values $\model{trunc}$ is more reliable than $\model{exist}$.
+
+%\comment{JL: do we have the numerical results to add a remark like: At an SNR of xdB, the respective success rates of $\model{trunc}$ and $\model{existing}$ are $90\%$ and $95\%$.
 This means that, for that SNR, chances of failure have been reduced by a factor of 2!
@@
 
-\paragraph*{Extension of the SNR range for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$}
+\paragraph*{Extension of the SNR range for $\model{trunc}$ over $\model{exist}$}
 A close inspection of \figref{fig:successRateVS_SNR36N3dB} reveals that the \gls{SNR} range associated with an acceptable success rate (e.g.
-$\successRate \geqslant 90\%$) is improved for $\hat G_\mathrm{trunc}$ over $\hat G_\mathrm{exist}$.
+$\successRate \geqslant 90\%$) is improved for $\model{trunc}$ over $\model{exist}$.
 The range of improvement is approximately 5 dB where the success rate is above $90\%$.
@@
 \end{itemize}
-discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \mcode{cheby1}, \mcode{cheby2}, \mcode{ellip} and \mcode{butter} are simulated.
+discrete-time filters~\citep{Zverev1967} of tenth degree generated by the \MATLAB code in \lstref{lst:initvals:stressSystems} are simulated.
 Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
-The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
-The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
+The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/s}$. 
+The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/s}$.
 Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
@@
 
-The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
+\lstinputlisting[float,style=matlab,mathescape,basicstyle=\ttfamily\scriptsize,caption={Code to generate the systems of the stress tests.},label={lst:initvals:stressSystems}]{\thisDir/code/systemsForStressTest.m}
+
+The input excitation and the disturbing output noise were $N=1\,024$ samples of white Gaussian noise such that and an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
 Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.

### 2016-03-06 ch05-initvals/code/systemsForStressTest.m

@@ -1,0 +1,26 @@
+function G0s = systemsForStressTest()
+    order = 10;        % [] degree of the filter
+    Qp    = 3;         % [dB] peak-to-peak ripple in pass-band
+    Qs    = 60;        % [dB] attenuation in stop-band
+    wPass = 0.5;       % [pi rad/sample] cross-over frequency
+    wBand = [0.4 0.6]; % [pi rad/sample] edges of the pass/stop band
+    G0s   = {DTFilter(@() cheby1(order, Qp,     wPass, 'low'      ))
+             DTFilter(@() cheby1(order, Qp,     wBand, 'bandpass' ))
+             DTFilter(@() cheby1(order, Qp,     wPass, 'high'     ))
+             DTFilter(@() cheby1(order, Qp,     wBand, 'stop'     ))
+             DTFilter(@() cheby2(order, Qp,     wPass, 'low'      ))
+             DTFilter(@() cheby2(order, Qp,     wBand, 'bandpass' ))
+             DTFilter(@() cheby2(order, Qp,     wPass, 'high'     ))
+             DTFilter(@() cheby2(order, Qp,     wBand, 'stop'     ))
+             DTFilter(@()  ellip(order, Qp, Qs, wPass, 'low'      ))
+             DTFilter(@()  ellip(order, Qp, Qs, wBand, 'bandpass' ))
+             DTFilter(@()  ellip(order, Qp, Qs, wPass, 'high'     ))
+             DTFilter(@()  ellip(order, Qp, Qs, wBand, 'stop'     ))
+             DTFilter(@() butter(order,         wPass, 'low'      ))
+             DTFilter(@() butter(order,         wBand, 'bandpass' ))
+             DTFilter(@() butter(order,         wPass, 'high'     ))
+             DTFilter(@() butter(order,         wBand, 'stop'     ))};
+function G = DTFilter(func)
+     [B, A] = feval(func);
+     G      = tf(B, A, 1);   % transfer function B/A and Ts = 1 [s]
+     G      = G/norm(G, 2);  % enforces norm(G,2) == 1 

### 2016-03-06 ch05-initvals/initial-values.tex
Add time constants of systems

@@
          { z^2 - 1.93 z + 0.94}
-    \qquad 
+    \text{ i.e. }
+    \timeconst \approx 32 \unit{s}
     \text{ for } Q = 6 \unit{dB}
     \label{eq:systemundertest}
-    \text{.}
-  \end{equation}
+    \text{,}
+  \end{equation}
+where $\timeconst = (\damping \wn)^{-1}$ denotes the time constant of the system (with $\damping$ the damping and $\wn$ the frequency of the dominant pole).
 The second system, with a quality factor $Q = 20\unit{dB}$, has the transfer function
@@
                  {z^2 - 1.98 z + 0.989}
-    \qquad 
+    \text{ i.e. }
+    \timeconst \approx 180 \unit{s}
     \text{ for } Q = 20 \unit{dB}
@@
  It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
-that their distances from the true system, given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
+that their distances from the true system, e.g. as given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
 On the other hand, the `failed' estimates are inaccurate descriptions of the true system.
@@
  % \caption{Results of an example of Monte Carlo simulation.}
- \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
+ \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
+ The `failed' estimates are caused by local minima in the cost function.
  Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
@@
 \subsubsection{Simulation}
-A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates for the following ranges %\comment{ML: To modify text!}
+A Monte Carlo simulation was set up to determine the success rate of the estimator with different initial estimates.
+In each run, both the realization of the excitation signal $u$ and the disturbing noise realization ($e$) are varied.
+Each run is repeated for the following ranges:
 \begin{itemize}
-\item of SNR: 
+\item of \gls{SNR}: 
               $-20   \unit{dB}$, 
@@
               $ 20   \unit{dB}$
-\item of number of samples $N$ is $3\,368$ or $4\,462$ for the first system whose quality factor $Q= 6 \unit{dB}$,
-\item and of number of samples $N$ is $20\,250$ or $26\,792$ for the second system whose quality factor $Q = 20\unit{dB}$.
+\item of number of samples $N$ is $3\,368\approx 104\timeconst$ or $4\,462\approx 138\timeconst$ for the first system whose quality factor $Q= 6 \unit{dB}$,
+\item and of number of samples $N$ is $20\,250\approx 113\timeconst$ or $26\,792\approx 149\timeconst$ for the second system whose quality factor $Q = 20\unit{dB}$.
 \end{itemize}
-\TODO{johan: tijdsconstantes geven}
 One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.

### 2016-03-06 ch05-initvals/code/timeconsts.m

@@ -1,0 +1,35 @@
+close all;
+clear variables;
+clc;
+
+Q   = [6 20]; % [dB]
+wCo = 0.05;   % [pi rad/s]
+
+G = cell(numel(Q), 1);
+for ii = 1:numel(G)
+    [B,A] = cheby1(2, Q(ii), wCo);
+    G{ii} = tf(B,A,1);
+    clear B A
+end
+
+[wn, xi] = cellfun(@damp, G,'Un', false);
+takeFirst = @(v) cellfun(@(x) x(1), v, 'Un', true); % only works for 1st/2nd order systems
+wn = takeFirst(wn);
+xi = takeFirst(xi);
+
+tau = 1./(xi.*wn); %[s] time constant
+NBW= [36;48];
+N = [3368 , 4462;
+     20250, 26792];
+
+for ii = 1:numel(G)
+    fprintf('System %d (Q = %g dB, wn = %g rad/s, xi = %g, tau = %g)\n', ...
+           ii, Q(ii), wn(ii), xi(ii), tau(ii))
+    fprintf('Experiment length:')
+    disp(N(ii, :));   
+    fprintf('# bins in 3dB BW:')
+    disp(NBW.');   
+    fprintf('Experiment length normalized for tau:')
+    disp(N(ii, :)./tau(ii));
+    fprintf('\n');
+end

### 2016-03-06 ch05-initvals/initial-values.tex
Comments Tom CH05: 99% verwerkt

@@
  The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
- $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
+ $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
   \label{fig:single-sim}
@@
 This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
-As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated, the time-domain counterpart $y(t)$ can be obtained using the \gls{IDFT}.
+As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.
 
@@
   \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
-  For each filter, two (randomly selected) instanced of the parametric estimates $\model{\bullet}$ are shown per method.
+  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
   % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
@@
 
-The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e.
+Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
+First, the \gls{LPM} solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e.
 $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
 The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
-Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
 
@@
 Whereas \gls{RFIR} is shown to provide reliable starting values, it remains advisable to have multiple initialization strategies available to improve the likelihood of attaining a good starting value.
-This is also the approach that toolboxes such as \citep{FDIDENT} and \citep{TDIDENT} employ.
+This is also the approach that toolboxes such as~\citep{FDIDENT} and~\citep{TDIDENT} employ.
 Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e.

### 2016-03-07 ch02-qlogms/excitation-design.tex
Address some TODOs

@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustics testing amongst others.
-%TODO reference acoustics (ISMA?)
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing~\citep{GarciaLopez2014,DAmico2014} amongst others.
 
@@
 
-  \begin{figure}
+  \begin{figure}[pht]
     \centering
-      \setlength\figurewidth{0.68\columnwidth}
+    \remakeNextFigure
+      \setlength\figurewidth{0.63\columnwidth}
       \setlength\figureheight{0.68\figurewidth}
@@
 
-  \begin{figure}[ht]
+  \begin{figure}[pht]
     \centering
-      \setlength\figurewidth{0.68\columnwidth}
+    \remakeNextFigure
+      \setlength\figurewidth{0.63\columnwidth}
       \setlength\figureheight{0.68\figurewidth}
@@
 
+\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality.
+\end{guideline}
+
 \section{Measurements} 
@@
     \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
-    \TODO{use styles from above}
       \label{fig:excitation:measurements}
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
-
-\TODO{move this guideline somewhere else}
-\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
-  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
-\end{guideline}

### 2016-03-07 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Address some TODOs

@@
 \researchBasedOn[This section]{Lumori2014TIM}
-
-\TODO{paper $\to$ section}
-
-\TODO{use gls commands in this part}
 
@@
 \paragraph{Formulation of the Linear LS LPM}
-The \gls{LPM} is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
+The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
 \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.

### 2016-03-07 ch04-lrmhinf/conference.tex
Address some TODOs

@@
-% arara: pdflatex: { shell : yes }
-% arara: bibtex
-% arara: makeglossaries
-% arara: pdflatex: { shell : yes, synctex : yes}
-
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{xspace}
-smart
-\usepackage{natbib}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\usepackage{tangocolors}
-\usepackage{tikz}
-\usetikzlibrary{spy}
-\usepackage{pgfplots}
-
-\usepackage{color}
-\newcommand{\EDIT}{\textcolor{red}{EDIT}}
-
-\newlength\figureheight 
-\newlength\figurewidth
-
-%\usepackage{hyperref}
-
 \input{definitions.inc.tex}
@@
 \input{styles.inc.tex}
-
-\usepackage{graphicx}
-\graphicspath{{./figures/}{.}{./tikz/}}
-
-\newcommand{\TODO}[1]{ {\color{red} #1} }
 
@@
 
-\begin{document}
+% \begin{document}
 
-\begin{frontmatter}
+% \begin{frontmatter}
 
-\title{Enhancing \Hinf{} Norm Estimation using Local LPM/LRM  Modeling: Applied to an AVIS\thanksref{thx}}
+% \title{Enhancing \Hinf{} Norm Estimation using Local LPM/LRM  Modeling: Applied to an AVIS\thanksref{thx}}
 
-\thanks[thx]{This work is supported by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem), and by the Belgian Government through the Interuniversity Poles of Attraction (IAP VII-Dysco) Program, the Innovational Research Incentives Scheme under the VENI grant ``Precision Motion: Beyond the Nanometer'' (no.
+% \thanks[thx]{This work is supported by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem), and by the Belgian Government through the Interuniversity Poles of Attraction (IAP VII-Dysco) Program, the Innovational Research Incentives Scheme under the VENI grant ``Precision Motion: Beyond the Nanometer'' (no.
 13073) awarded by NWO (Netherlands Organization for Scientific Research) and STW (Dutch Science Foundation).}
 
-\author[VUB]{Egon Geerardyn} 
-\author[TUE]{Tom Oomen} 
-\author[VUB]{Johan Schoukens}
+% \author[VUB]{Egon Geerardyn} 
+% \author[TUE]{Tom Oomen} 
+% \author[VUB]{Johan Schoukens}
 
-\address[VUB]{ELEC Department, Vrije Universiteit Brussel, Brussels, Belgium.
+% \address[VUB]{ELEC Department, Vrije Universiteit Brussel, Brussels, Belgium.
 \\ (e-mails: \href{mailto:egon.geerardyn@vub.ac.be}{egon.geerardyn}, \href{mailto:johan.schoukens@vub.ac.be}{johan.schoukens} @vub.ac.be)}
-\address[TUE]{Control System Technology Group, Mechanical Engineering Department, Technische Universiteit Eindhoven, Eindhoven, the Netherlands.
+% \address[TUE]{Control System Technology Group, Mechanical Engineering Department, Technische Universiteit Eindhoven, Eindhoven, the Netherlands.
 (e-mail: \href{mailto:t.a.e.oomen@tue.nl}{t.a.e.oomen@tue.nl})}
 
-\begin{keyword}
-Frequency-response;
-Uncertainty;
-Norms;
-Estimation;
-Polynomials;
-Signal Processing;
-System Identification;
-Robust Control.
-\end{keyword}
+% \begin{keyword}
+% Frequency-response;
+% Uncertainty;
+% Norms;
+% Estimation;
+% Polynomials;
+% Signal Processing;
+% System Identification;
+% Robust Control.
+% \end{keyword}
 
-\begin{abstract}~
-Accurate uncertainty modeling is of key importance in high performance robust control design. 
-The aim of this paper is to develop a new uncertainty modeling procedure that leads to enhanced accuracy for the $\mathcal{H}_\infty$ norm. 
-A frequency response based approach is adopted. 
-The key novelty of this paper is a new method to address the intergrid error using local parametric modeling methods. 
-These local polynomial and rational models enhance the estimates at the discrete frequency grid.
-Moreover, the presented methods are shown to enhance the intergrid error estimate.
-This is illustrated using simulations and experiments on an industrial active vibration isolation system.
-Compared to the local polynomial models, local rational models are able to handle lightly-damped resonances using far fewer data points, which means that measurement time can be kept short.
-\end{abstract}
+% \begin{abstract}~
+% Accurate uncertainty modeling is of key importance in high performance robust control design. 
+% The aim of this paper is to develop a new uncertainty modeling procedure that leads to enhanced accuracy for the $\mathcal{H}_\infty$ norm. 
+% A frequency response based approach is adopted. 
+% The key novelty of this paper is a new method to address the intergrid error using local parametric modeling methods. 
+% These local polynomial and rational models enhance the estimates at the discrete frequency grid.
+% Moreover, the presented methods are shown to enhance the intergrid error estimate.
+% This is illustrated using simulations and experiments on an industrial active vibration isolation system.
+% Compared to the local polynomial models, local rational models are able to handle lightly-damped resonances using far fewer data points, which means that measurement time can be kept short.
+% \end{abstract}
 
-\end{frontmatter}
+% \end{frontmatter}
 
@@
 
-%TODO: acknowledgments reviewers
-
-\bibliography{biblio/references,biblio/ownWork} 
-%\bibliographystyle{ifacconf}
-
 \end{document}

### 2016-03-08 ch04-lrmhinf/paper.tex
Remove line thingie in figure
Short cpations for CH04

@@
   \input{\thisDir/figs/interpolation-show.tikz}
-  \caption{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
+  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
   The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
-  \TODO{top subplot has a line connecting the last to the first point...}
 \label{fig:interpol-quantities}
@@
   %\input{\thisDir/figs/example-LRM-SNR1.tikz}
-  \caption{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
   Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
@@
   %\input{figures/runLength.tikz}
-  \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
   However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
@@
  \input{\thisDir/figs/tpcrobust.tikz}
- \caption{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
+ \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
  \label{fig:tpc}
@@
  \input{\thisDir/figs/dualYoula.tikz}
- \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
+ \caption[Dual-Youla parametrization.]{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
 \label{fig:dualYoula}
@@
     \input{\thisDir/figs/avis-frf.tikz}
- \caption{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
+ \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
  \label{fig:avis-frf}
@@
     \TODOfig{split plots}
- \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling.]{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation.
+The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
 \label{fig:avisMeas}
@@
    \input{\thisDir/figs/avis4.tikz}
- \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
 Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$.

### 2016-03-08 ch05-initvals/initial-values.tex
Algorithm formatting improved

@@
 \end{equation}
-where $A$ and $B$ are polynomials in $q^{-1}$. Thus, it follows from equation \eqref{lpmtd1} that
+where $A$ and $B$ are polynomials in $q^{-1}$. 
+Thus, it follows from equation \eqref{lpmtd1} that
 \begin{equation}
@@
 Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
-The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
+The Levenberg-Marquardt algorithm~\citep{Marquardt1963}, is used to solve this optimization problem deterministically and is shown in~\algoref{alg:initvals:levenberg-marquardt}.
 Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this chapter.
@@
 \begin{algorithm}
-\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
+\caption{Levenberg-Marquardt~\citep{Marquardt1963},~\citep[Sec. 9.L.4]{Pintelon2012}}
+\label{alg:initvals:levenberg-marquardt}
 \begin{algorithmic}[1]

### 2016-03-10 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Improve guideline 2.x
Update figure: exp. fitting

@@
 \researchBasedOn[This section]{Lumori2014TIM}
+\TODO{figures to TikZ}
+\TODO{re-introduce $F$-test truncator and box-carr averager}
 
@@
 \gls{FRF} measurement techniques are discussed, for instance, in
-\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others.
+\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
 Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
-This capability is very useful for model validation and/or selection \citep{Pintelon2012}.
+This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.
 
@@
    \includegraphics{\thisDir/figs/LPMfigOmegak}
-   \caption{Illustration of the \gls{LPM}.
+   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}.
 Top figures: input spectrum (left) and output spectrum (right).
@@
 \begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
+\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
 \end{align}
@@
 Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
-%In the remainder of this procedure description $\hat g_\mathrm{poly}(t)$ will be simply denoted $\hat g(t)$.
 
 \item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
-
 \begin{align}
@@
 \centering
-
-\includegraphics[scale=0.9]{\thisDir/figs/expFitest}
+\setlength\figurewidth{0.85\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+% \includegraphics[scale=0.9]{\thisDir/figs/expFitest}
+\input{\thisDir/figs/expfit.tikz}
 \caption{Truncation of the impulse response via the fit of  an exponential.
@@
 
-\item
-The bias error is highest in the vicinity of (sharp) resonance peaks.
+\item The bias error is highest in the vicinity of (sharp) resonance peaks. 
 If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
-%If the latter must be estimated with a high accuracy, a value $\gamma \ll 1$ must be preferred.
 
@@
     \centering
-
     \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-
     \caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$.
@@
 \begin{itemize}
-\item
-a decrease of the variance on the truncated estimate of about $10 \unit{dB}$,  i.e.
+\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$,  i.e.
 a decrease of the black crosses, compared to the gray ones, is observed.
@@
 
-\item
-the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
+\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
 
-\item
-an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
+\item an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
 Still, this bias lies below the variance of the non-truncated estimate.
@@
    \centering
-
 	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
@@
 Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
-
    \label{fig:pdfAndRMSeVStruncTime}

### 2016-03-10 ch02-qlogms/excitation-design.tex
Remove line thingie in figure
Improve guideline 2.x
small changes ch-2,ch04

@@
   \end{equation}
-  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:excitation:misalignment-logms}
-  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
+  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:excitation:misalignment-logms}.
+  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ has the same role as $\gamma$ factor in \eqref{eq:excitation:theoreticalBestVariationOmega}.
   If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the \gls{FRF} at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
@@
     \centering
-    \remakeNextFigure
       \setlength\figurewidth{0.63\columnwidth}
@@
     \input{\thisDir/figs/betaWC.tikz}
-    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
+    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
              The full lines depict the variance for a coarsely spaced signal.
@@
     \input{\thisDir/figs/Sys02-4.tikz}
-    \caption[Simulated \gls{FRF} and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
+    \caption[Simulated \gls{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
     \label{fig:excitation:FRF1}
@@
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.2$ for different excitation signals.]{%
+    \caption[Simulated \glspl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
        \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
@@
     \input{\thisDir/figs/damping005-cmp.tikz}
-    \caption[Simulated \glspl{FRF} and their variances of systems with $\damping=0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
+    \caption[Simulated \glspl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
     Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
@@
 
-\begin{guideline}[Choose $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
+\begin{guideline}[Use a sufficient grid resolution for each resonance: $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
 \label{guide:excitation:systemInBulk:tuned}
@@
   \input{\thisDir/figs/Sum02log0-2.tikz}
-  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
-           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
+  \caption[Simulated FRF of sum of two sub-systems.]{FRF for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
   \label{fig:excitation:sumSys}
@@
     \input{\thisDir/figs/qlog_a050mall.tikz}
-    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
+    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
       \label{fig:excitation:measurements}

### 2016-03-10 ch05-initvals/initial-values.tex
Bode BK1613 in ch05 downsized

@@
   The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
-  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
   \label{fig:bk1613}
@@
 Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
-First, the \gls{LPM} solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e.
-$n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
+First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2N_W + 1$ data points and a few degrees of freedom, i.e.
+$n_{\theta} \leq 2 N_W + 1$ or $\bigO{N_W} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
 The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
+As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N N_W^3}$.
 
@@
 \subsection{Implementation aspects}
-This section discusses some implications and recommendations for the implementation of  a system identification toolbox.
+This section presents some implications and recommendations for the implementation of  a system identification toolbox.
 

### 2016-03-12 ch06-concl/conclusions.tex
Some work on conclusion

@@
   \end{itemize}
-  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer a very easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
+  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
+  %TODO: for ny x nu MIMO system, alpha_MIMO = 1 + alpha_SISO/nu to satisfy the density of frequency lines.
+This means: lowest guaranteed observable resonance is at higher frequencies than for SISO (obviously).
+  %TODO: also zippered vs. orthogonal for non-linearities: sparsity destroys BLA relationship
 
   Also, in the related chapter, it has been assumed that the system is an \gls{LTI} system.
-  For weakly nonlinear systems, the proposed approach is likely to
-
-  \TODO{MIMO extension}
-  \TODO{zippered vs. orthogonal}
+  For weakly nonlinear systems, the proposed approach is likely to yield approximately valid results.
 
@@
   Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the the dimensionality in the parameter space.
-  By no means smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.
+  By no means were the  smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.
 
@@
   As such, those could provide a valuable initialization strategy if the redundant local pole/zero information of neighboring windows can be reduced to a single global pole/zero initial value.
-  Probably techniques in model order reduction could provide a good starting point to calculate such initial values.
-  \TODO{optimal smoother}
+  Techniques in model order reduction are likely to provide a good starting point to simplify the local pole/zero estimates to a global parametric model which could then be used to serve as initial estimate for the non-convex optimization steps.

### 2016-03-14 ch05-initvals/initial-values.tex
Some work on conclusion
Some legends pulled into plots

@@
 In this chapter we assume that the output signal is disturbed by random noise, resulting in noisy error-prone data.
-For the simulations, white noise is used ($H_0 = 1$ and $e(t) = v(t)$).
+For the simulations, white noise is used ($\true{H} = 1$ and $e(t) = v(t)$).
 It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{se:ExpMeas}.
@@
 \begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{}  \text{with}  n \in \IntegerNumbers
+    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{}  \text{ with }  n \in \IntegerNumbers
 \label{ABpolys}
@@
 \begin{align}
-A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
+A(e^{-j\omega_k})\true{Y}(k) = B(e^{-j\omega_k})\true{U}(k) + I(e^{-j\omega_k})
 \label{DFTspectra}
@@
   &=  |A(k,\theta)|^2\sigma_Y^2(k) 
-   +  |B(k,\theta)|^2\sigma_U^2(k) \\
-  &- 2\RealPart \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
+   +  |B(k,\theta)|^2\sigma_U^2(k)
+  - 2\RealPart \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
 \end{split}
@@
   \centering
-  \ref{leg:init:stress:bodes}
   \input{\thisDir/fig/bodeplots.tikz}
-  %TODO: put legend inside figure (note: subplot magic!!)
   \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
@@
   \centering
-  \ref{leg:distances}
   \input{\thisDir/fig/distances.tikz}
@@
   }
-  %TODO: put legend inside figure (note: subplot magic!!)
   \label{fig:distancesStress}
@@
 \label{guide:initvals:try-regularization}
-Regularized estimators, such as \gls{RFIR}, sometimes provide better estimates than the `true' model parameters.
+Regularized estimators, such as \gls{RFIR}, sometimes provide better initial estimates than the `true' model parameters.
 \end{guideline}
@@
 \label{guide:initvals:try-many-initial-values}
-Trying different initial values is quite inexpensive, but the quality of the final model may improve by several order of magnitude if a local minimum can be avoided.
+Trying different initial values is quite inexpensive, but the quality of the final model may improve by several orders of magnitude if a local minimum can be avoided.
 As such, using multiple initial values, especially ones that have been derived with good judgment, pays off.

### 2016-03-14 ch02-qlogms/excitation-design.tex
Add pole information initial model BK1613

@@
     \label{sec:excitation:measurement:setup}
-    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.
+    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer{} Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.
 
@@
     According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
-    A first guess to realize such a filter is a sixth-order Chebyshev band-pass filter of Type I~\citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
-    %TODO: datasheet FRF?, pzmap with \damping shown, evt. tabel: per pool-paar: \wn ifv \wc, \damping
+    This leads to a transfer function
+
+    This leads to a sixth-order Chebyshev band-pass filter of Type~I~\citep{Zverev1967} given in the transfer function
+    \begin{equation}
+       G_{\mathrm{init}}(s) \approx 
+      \frac{0.15922 s_{\mathrm{n}}^3 }{ s_{\mathrm{n}}^6 + 0.759 s_{\mathrm{n}}^5 + 3.564 s_{\mathrm{n}}^4 + 1.678 s_{\mathrm{n}}^3 + 3.564 s_{\mathrm{n}}^2 + 0.759 s_{\mathrm{n}} + 1}
+      \label{eq:excitation:bk1613:tf-init}
+     \end{equation}
+     where $s_{\mathrm{n}} \isdef s \wc^{-1}$ and $\wc=2\pi \fc$ is the center frequency of the respective filter.
+     It can be seen from \tabref{tbl:excitation:bk1613:poles} that each pole has $\damping \geq 0.09$.
     Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
     The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.
+
+    \begin{table}[b]
+      \centering
+      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter with center frequency $\wc$.}
+      \label{tbl:excitation:bk1613:poles}
+      \begin{tabular}{crr}
+        \toprule
+        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} \\
+        \midrule
+        $-(0.067 \pm 0.733j)\wc$ & $0.091$ & $0.736\wc$ \\ 
+        $-(0.190 \pm 0.982j)\wc$ & $0.190$ & $\wc$ \\ 
+        $-(0.123 \pm 1.350j)\wc$ & $0.091$ & $1.36\wc$ \\ 
+        \bottomrule
+      \end{tabular}
+    \end{table}
 
@@
     was estimated using \texttt{elis}~\citep{FDIDENT}.
-    The initial estimate was a sixth-order band-pass type I Chebyshev filter~\citep{Zverev1967} that conformed to the information given in the datasheet~\citep{datasheet_bk1613} to aid convergence to a good optimum.
+    To aid convergence to a good optimum, the initial estimate was a sixth-order band-pass type I Chebyshev filter given in \eqref{eq:excitation:bk1613:tf-init}.
 

### 2016-03-14 ch02-qlogms/excitation-design.tex
BK1613 filter described in more detail

@@
 \label{guide:excitation:systemInBulk:tuned}
- A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonances peaks with damping $\damping$ and resonance frequency $\wn$ when
+ A quasi-logarithmic multisine with frequency resolution $\Delta f$ and tuned frequency spacing $\alpha=1+\damping$ is only guaranteed to properly excite resonance peaks with damping $\damping$ and resonance frequency $\wn$ when
   \begin{equation}
@@
     According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
-    This leads to a transfer function
-
-    This leads to a sixth-order Chebyshev band-pass filter of Type~I~\citep{Zverev1967} given in the transfer function
+    This leads to a sixth-order Chebyshev band-pass filter of Type~I~\citep{Zverev1967} with transfer function
     \begin{equation}
        G_{\mathrm{init}}(s) \approx 
-      \frac{0.15922 s_{\mathrm{n}}^3 }{ s_{\mathrm{n}}^6 + 0.759 s_{\mathrm{n}}^5 + 3.564 s_{\mathrm{n}}^4 + 1.678 s_{\mathrm{n}}^3 + 3.564 s_{\mathrm{n}}^2 + 0.759 s_{\mathrm{n}} + 1}
+      \frac{0.15922 s_{\mathrm{n}}^3 }
+                {              s_{\mathrm{n}}^6 
+                + 0.759 s_{\mathrm{n}}^5 
+                + 3.564 s_{\mathrm{n}}^4 
+                + 1.678 s_{\mathrm{n}}^3 
+                + 3.564 s_{\mathrm{n}}^2 
+                + 0.759 s_{\mathrm{n}} 
+                + 1}
       \label{eq:excitation:bk1613:tf-init}
@@
      It can be seen from \tabref{tbl:excitation:bk1613:poles} that each pole has $\damping \geq 0.09$.
-    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
+    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed excitation signals.
     The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.
 
-    \begin{table}[b]
+    \begin{table}[bt]
       \centering
@@
       \label{tbl:excitation:bk1613:poles}
-      \begin{tabular}{crr}
+      \begin{tabular}{rrrr}
         \toprule
-        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} \\
+        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} & \textsc{Time constant ($\timeconst$)}\\
         \midrule
-        $-(0.067 \pm 0.733j)\wc$ & $0.091$ & $0.736\wc$ \\ 
-        $-(0.190 \pm 0.982j)\wc$ & $0.190$ & $\wc$ \\ 
-        $-(0.123 \pm 1.350j)\wc$ & $0.091$ & $1.36\wc$ \\ 
+        $-(0.067 \pm 0.733j)\,\wc$ & $0.091$ & $0.74\,\wc$ & $15.0\,\wc^{-1}$\\ 
+        $-(0.190 \pm 0.982j)\,\wc$ & $0.190$ & $\wc$ & $5.3\, \wc^{-1}$\\ 
+        $-(0.123 \pm 1.350j)\,\wc$ & $0.091$ & $1.36\,\wc$ & $8.1 \,\wc^{-1}$\\ 
         \bottomrule
@@
     \input{\thisDir/figs/qlog_a050mall.tikz}
-    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
+    \caption[Measurements of all BK1613 octave filters using different excitation signals.]{Measured FRFs of the different \bruelkjaer{} 1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
       \label{fig:excitation:measurements}

### 2016-03-14 ch02-qlogms/excitation-design.tex
Measurements CH2: crest factor

@@
     This amplitude was chosen such that the peak amplitude $\max \abs{u(t)}$ was approximately $1 \unit{V}$.
-
-    $R=50$ periods of the multisine were measured, from which the first period was discarded to suppress transient effects.
+    An attempt was made to use a random-phase multisine with a limited crest factor
+    \begin{equation}
+      \crest{u} \isdef \frac{\norm[\infty]{u(t)}}{\norm[2]{u(t)}} = \frac{\max{\abs{u(t)}}}{ \sqrt{\Tm^{-1} \int_{0}^{\Tm} u(t)^2 \dd{t}}}
+    \end{equation}
+    to avoid excessive effects of nonlinear behavior of the filter.
+    In particular, for each signal $1000$ realizations of the phase spectrum $\phi_k$ were sampled from a uniform distribution over $\LeftOpenInterval{0,2\pi}$; from these realizations only the multisine with the lowest crest factor was retained and applied to the filters.
+
+    $R=50$ periods of each multisine were measured, from which the first period was discarded to suppress transient effects.
     For each of the remaining periods, the \gls{FRF} of the filter is calculated and its average $G\left(\omega \right)$ over the periods is calculated.

### 2016-03-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
TODO
Some work on conclusion
Improve figures, short captions

@@
 \input{\thisDir/figs/expfit.tikz}
-\caption{Truncation of the impulse response via the fit of  an exponential.
+\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response via the fit of  an exponential. 
 The light gray line is the noisy impulse response, and the dark gray one is its absolute value. 
@@
 Black thick line: estimated exponential function \eqref{eq:expFit}.}
+\TODO{describe marker again!}
 \label{FRF_truncate_expfitter}
@@
     \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-    \caption{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$.
+    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$.
 The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc).
@@
 	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
-         \caption{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}).
+         \caption[RMS error of the FRF versus truncation time.]{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}).
 Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}

### 2016-03-14 ch05-initvals/initial-values.tex
Improve figures, short captions

@@
   \input{\thisDir/fig/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying \gls{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e.
+ \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e.
 $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
@@
   \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model \gls{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
+ \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
  In the bottom plot, the difference between both is shown.
@@
   \input{\thisDir/fig/elvis-spectra.tikz}
-  %TODO: simplify figure
   \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
@@
   \centering
-  \ref{leg:init:secondBest}
+  % \ref{leg:init:secondBest}
   \setlength{\figurewidth}{0.75\columnwidth}
@@
   \input{\thisDir/fig/special-histogram.tikz}
-  %TODO: put legend inside figure (note: subplot magic!!)
   \caption[Performance degradation/enhancement for selecting the second best model.]{

### 2016-03-17 ch03-lrm/smoothingRMSdecrease.tex
Clean up in CH03

@@
 
-To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated
-%measured
- impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments. One can then gradually determine whether these segments are noise or the actual impulse response.
+To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments.
+One can then gradually determine whether these segments are noise or the actual impulse response.
 
@@
   \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
-$L_S = \floor{\frac{N}{N_S}}$. If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
+$L_S = \floor{\frac{N}{N_S}}$. 
+If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
 The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.

### 2016-03-17 ch05-initvals/code/systemsForStressTest.m
Listing format improved

@@ -1,8 +1,8 @@
 function G0s = systemsForStressTest()
     order = 10;        % [] degree of the filter
-    Qp    = 3;         % [dB] peak-to-peak ripple in pass-band
+    Qp    =  3;        % [dB] peak-to-peak ripple in pass-band
     Qs    = 60;        % [dB] attenuation in stop-band
-    wPass = 0.5;       % [pi rad/sample] cross-over frequency
+    wPass =  0.5;      % [pi rad/sample] cross-over frequency
     wBand = [0.4 0.6]; % [pi rad/sample] edges of the pass/stop band
     G0s   = {DTFilter(@() cheby1(order, Qp,     wPass, 'low'      ))
              DTFilter(@() cheby1(order, Qp,     wBand, 'bandpass' ))

### 2016-03-17 config/styles.inc.tex
Config: remove some duplication

@@
 
-\newcommand{\dbamarker}{mark=x       ,mark options={solid}}
-\newcommand{\dbbmarker}{mark=o       ,mark options={solid}}
-\newcommand{\dbcmarker}{mark=square  ,mark options={solid}}
-\newcommand{\dbdmarker}{mark=triangle,mark options={solid}}
-
 \pgfplotsset{linms/.style={color=linms,solid,line width=0.5pt}}
@@
 \pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}
-
-\pgfplotsset{linmsconnect/.style={color=linms,%
-                                  solid,
-                                  line width=1pt,
-                                  mark=square*,
-                                  mark size=1pt,
-                                  mark options={solid}}}
-\pgfplotsset{qlogmsconnect/.style={color=qlogms,%
-                                  solid,
-                                  line width=1pt,%
-                                  mark=*,%
-                                  mark size=1pt,
-                                  mark options={solid}}}
-\pgfplotsset{clogmsconnect/.style={color=clogms,%
-                                   solid,
-                                   line width=1pt,%
-                                   mark=x,%
-                                   mark size=1pt,
-                                   mark options={solid}}}
 

### 2016-03-17 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Ch03: fix some references

@@
 \TODO{re-introduce $F$-test truncator and box-carr averager}
+\TODO{labels into standardized form}
 
@@
 
-Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework.
-A \gls{SISO} \gls{LTI} system is considered.
-%, based on  \citep{Schoukens2009LPM}.
+Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A \gls{SISO} \gls{LTI} system is considered.
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
 This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
-\begin{equation}\label{eq:lpm:TD}
+\begin{equation}\label{eq:nparam:trunc:LPM:TD}
 y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
@@
 where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-%\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}
 
-\begin{figure}[tbh] %top bottom here
+\begin{figure}
 \centering
@@
 
-In this section, however, a nonparametric technique is developed, %the identification problem is
-formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}. The following  choices are made:
+In this section, however, a nonparametric technique is developed, and
+formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.
+
+The following  choices are made:
 
@@
 
-\item
+\item The work in this section is for discrete-time systems.
+Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
 
-The work in this section is for discrete-time systems.
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
-\item
+\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
 
-Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
-\item
-
-Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
+\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
 
@@
 
-The rest of the section is structured as follows. \secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
+The rest of the section is structured as follows. 
+\secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
 \secref{se:smoothingFRFestimate} discusses the novel smoothing method.
-
 Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.
@@
 As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
-\begin{equation}\label{lpmleak}
+\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
 Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
@@
 In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors.
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:lpm:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
+%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:nparam:trunc:LPM:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
 Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
@@
 
-The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:lpm:TD} and \eqref{lpmleak}, \emph{viz}:
+The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
 \begin{equation}\label{lpm1spectra}
@@
 
-Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
+Note that \assref{ass:imprespdecay} and \assref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
 
@@
 
-According to Assumption~\ref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by Assumption~\ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
+According to \assref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by \assref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response.
 The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
@@
 \end{align}
-This is valid, as per Assumption \ref{ass:decay90perctime}.
+This is valid, as per \assref{ass:decay90perctime}.
 
@@
 A good practice would be to truncate the impulse response at the minimizer (black dot) of the \gls{RMS} error. 
-However, it should be noted that this minimizer is unknown in practice, because it would require
-the true \gls{FRF}.
+However, it should be noted that this minimizer is unknown in practice, because it would require the true \gls{FRF}.
 

### 2016-03-17 ch03-lrm/smoothingRMSdecrease.tex
Ch03: fix some references

@@
 The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
-  By Assumption \ref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
+  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
 
@@
 \end{enumerate}
-%In Fig.~\ref{FRF_truncate_stat_EG}, this procedure is shown on the system depicted in \eqref{eq:systemSimulations}. 
-This procedure is illustrated in Fig.~\ref{FRF_truncate_stat_EG} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
+This procedure is illustrated in \figref{FRF_truncate_stat_EG} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
 \begin{subequations}
@@
 \begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
+y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
 y(t)       &= y_0(t) + e(t),
@@
 
-\begin{figure}[tbh] %top bottom here
+\begin{figure}[tbh]
 \centering

### 2016-03-17 ch05-initvals/initial-values.tex
Listing format improved
Different figure names per chapter
Externalize tables in CH05

@@
 \gdef\thisDir{ch05-initvals}
+\tikzsetfigurename{ch05fig}
 \researchBasedOn{Geerardyn2015TIM}
@@
   \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
-% \input{\thisDir/table1.tex}
-\pgfplotstabletypeset[precision=0]{
-method            P000     P025     P050      P075       P100   
-\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
-\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
-\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
-\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
-\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
-}
+  \input{\thisDir/tables/meas-cost-quantiles.tbl.tex}
   \label{tbl:costMeasurements}
@@
   \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
-% \input{\thisDir/table2.tex}
-\pgfplotstabletypeset[zerofill=true,precision=2]{
-method              P000      P025      P050        P075     P100   
-\model{VXI}         0.47325   0.916589   1.06396   1.29177   2.4089
-\model{exist}       1.48252   1.88392   13.7177   19.3113   26.7984
-\model[init]{trunc} 1.35399   2.72412   14.9431   24.7154   85.3351
-\model{trunc}       1.27344   1.71872    2.34574  13.0301   63.8373
-\model[init]{RFIR}  1.10525   1.61051    1.7778    2.00318  18.211
-\model{RFIR}        1.20554   1.57398    1.72416   1.84941   4.55004
-\model{best}        1.20554   1.55725    1.72059   1.84593  15.0063
-}
+  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
 \label{tbl:validationMeasurements}
@@
   \caption{Overview of the test cases for the initialization stress test.}
-\begin{tabular}{crlrrrrr}
-\toprule
-\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\successRate} [\%]$  &  $\successRate_{\mathrm{exist}} [\%]$ &  $\successRate_{\mathrm{trunc}} [\%]$   &  $\successRate_{\mathrm{RFIR}} [\%]$  &  $\successRate_{\mathrm{best}} [\%]$ \\
-\midrule
-1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
-2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
-3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
-4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
-5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
-6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
-7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
-8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
-9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
-10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
-11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
-12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
-13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
-14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
-15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
-16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
-\bottomrule
-\end{tabular}
+  \input{\thisDir/tables/stresstest-cases.tbl.tex}
 \label{tbl:init:stresstest}
@@
   For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
-  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
-  % Left to right: low-pass, band-pass, high-pass and band-stop.
   }
@@
   \centering
-  \centering
   \caption{Observed timing of the different estimation steps.}
-% \input{\thisDir/table2.tex}
-\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
-    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
-    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
-    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
-    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
-    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
-    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
-]{%
-Q  NBW  method  tsmooth    tinit  tfinal
- % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
- % 6  36  \model{exist}   nan     nan     0.159937 
- 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
- 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
- % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
- % 6  48  \model{exist}   nan     nan     0.206823 
- 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
- 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
-% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
-% 20  36  \model{exist}   nan     nan     0.429752 
-20  36  \model{trunc}   4.83667     0.225876    0.454757 
-20  36  \model{RFIR}    6.92575     0.253981    0.482431 
-% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
-% 20  48  \model{exist}   nan     nan     0.457577 
-20  48  \model{trunc}   6.59726     0.312937    0.461114 
-20  48  \model{RFIR}    8.05168     0.312297    0.468905 
-}
+  \input{\thisDir/tables/timings.tbl.tex}
 \label{tbl:init:timing}

### 2016-03-17 ch05-initvals/tables/timings.tbl.tex
Externalize tables in CH05

\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0,empty cells with={\deemph{--}}, %round to 1 ms
    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
]{%
Q  NBW  method  tsmooth    tinit  tfinal
 % 6  36  \model{\trueSymbol}    nan     nan     0.197034 
 % 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 % 6  48  \model{\trueSymbol}    nan     nan     0.209216 
 % 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
% 20  36  \model{\trueSymbol}    nan     nan     0.445936 
% 20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
% 20  48  \model{\trueSymbol}    nan     nan     0.467081 
% 20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}

### 2016-03-19 ch06-concl/conclusions.tex
Different figure names per chapter
Reference to Annemiek & Rick: nD-LRM
Some musings in future research

@@
 \myEpigraph{Life can only be understood backwards; but it must be lived forwards.}{Søren Kierkegaard}{}
+\tikzsetfigurename{ch06fig}
 
@@
     \TODO{MIMO LRM}
-    \TODO{Slowly time-varying}
-    \TODO{Static LPV measurements}
+    The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
+    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc}.
+    As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
+    Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
+
+    As the non-parametric methods such as \gls{LPM} and \gls{LRM} were originally intended to serve the same purpose as windows in classical spectral analysis, this naturally leads to other applications of these methods where windows are otherwise used to reduce the effect of spectral leakage.
+
+    In particular, for slowly time-varying systems, windows can be used in combination with the \gls{STFT} to obtain a rough approximation of either the output spectrum or the transfer characteristic of time-varying systems.
+    In this context, the \gls{LPM} has already been used~\citep{Lataire2012}.
+    Preliminary tests using the \gls{LRM} in lieu of the \gls{LPM} have proven fruitful.
+    Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep[Chapter 4]{vanderMaas2016PhD}.
+    Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
+    E.g. it could prove useful to extend the \gls{LRM} also towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.
 

### 2016-03-19 ch03-lrm/lrm-paper.tex
Import LRM-paper draft

\section{Introduction}
Estimating a non-parametric \gls{FRF} is often a key step in the analysis and/or design of physical systems.
However, obtaining a good-quality non-parametric \gls{FRF} from a measured input-output data set can prove difficult due to the presence of noise and measurement time limitations to observe lightly-damped dynamics well.

\citep{Pintelon2010LPM1},\citep{Pintelon2010LPM2},\citep{McKelvey2012LRM}

\paragraph*{Contributions}
In this paper, the existing \gls{LRM} is extended to the \gls{LRIC} that does not suffer from  the bias that is present in the \gls{LRM}.
An extensive study is carried out to compare the performance of the \gls{LPM}, \gls{LRM} and \gls{LRIC} to describe resonant systems under varying conditions of the signal-to-noise ratio.
Also, a pragmatic model-order-selection tool for the \gls{LPM} and \gls{LRM} is introduced.

\paragraph*{Contents}
\secref{sec:theory} introduces theory of estimating \glspl{FRF} and the relevant local modeling techniques.
In \secref{sec:simulations} the performance of the different modeling methods is investigated by means of simulations.
The methods are then illustrated on measurements of mechanical systems in \secref{sec:measurements}.
Finally, conclusions are presented in \secref{sec:conclusion}.

\TODO{
\begin{itemize}
    \item choice $s$ or $z$
    \item bounds RMSE, Bias, StdDev
    \item derivation Bias
    \item comparison LPM/LRM
      \begin{itemize}
        \item Good LPM window
        \item Good LRM window
      \end{itemize}
    \item influence of noise filter: mismatch with model
    \item comparison LRM/LRik (LBTLS)
\end{itemize}
}

\section{Local modeling approaches}
\label{sec:theory}

Consider a discrete-time generalized output-error \gls{LTI} set-up, excited by the input signal $u[n]$.
For an infinite data length, such a system can be described in the time domain by
\begin{equation}
  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \ZZ
  \label{eq:output-error-TD-infinite}
\end{equation}
where $v[n]$ is filtered white noise, $v[n] = \true{H}(z) \true{e}[n]$ where $z^{-1}$ is the backward shift operator, i.e. $z^ {-1}x[n] = x[n-1]$.
The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are stable and causal.

During typical measurements, however, $y[n]$ and $u[n]$ are only measured over a limited time span, i.e. $n \in \set{0,1,\ldots,N-1}$.
This introduces transient terms $t_{\bullet}$ in this relationship~\citep{Pintelon1997ARB}:
\begin{equation}
y[n] = \true{G}(z) u[n] + \true{H}(z) \true{e}[n] + \ezbrace{t_G[n] + t_H[n]}{t[n]}
\label{eq:output-error-TD-finite}
\end{equation}
where $t_G[n]$ and $t_H[n]$ are due to the different state of respectively $\true{G}$ and $\true{H}$ at the beginning and end of the measurement record~\citep{Pintelon1997ARB}.
Both terms can be lumped together as $t[n]$, which is often~\citep{Pintelon2010LPM1} dominated by $t_G[n]$.

\begin{definition}\label{def:DFT}
The $N$-points \glsfirst{DFT} of a signal $x(n\Ts) = x[n]$ with $n \in \set{0,\ldots,N-1}$ is
\begin{equation}
  X \left[ k \right] =
  X \left( \omega_k \right)
  \isdef
  \frac{1}{\sqrt{N}}\sum_{n=0}^{N-1} x \left( n \Ts \right)  \exponent{- j \omega_k n \Ts }
  \label{eq:DFT}
\end{equation}
where $\omega_k \isdef \tfrac{2 \pi k }{N \Ts}$, $k \in \set{0,\ldots,N-1}$ and $\Ts$ is the sampling time.
\end{definition}

By applying the \gls{DFT}~\eqref{eq:DFT} to both sides of \eqref{eq:output-error-TD-finite}, one obtains its frequency-domain counterpart:
\begin{align}
    Y \left( \omega_k \right) 
    & = \true{G} \left( \omega_k \right) U \left( \omega_k \right) 
      + \true{H} \left( \omega_k \right) E \left( \omega_k \right)
      + T \left( \omega_k \right)\\
      &= \true{G} \left( \omega_k \right) U \left( \omega_k \right)  + V(\omega_k) + T(\omega_k)
      \text{.}
  \label{eq:output-error-FD}
\end{align}

In this paper, we focus on using local modeling to separate the different terms, i.e.
\begin{itemize}
  \item the transfer function $\true{G}$,
  \item the leakage term $T$, and
  \item the noise term $V$.
\end{itemize}

\subsection{Local modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\sum_{i=0}^{N_B} b_i d^i}
            {1 + \sum_{i=1}^{N_A} a_i d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\sum_{i=0}^{N_C} c_i d^i}
            {1 + \sum_{i=1}^{N_A} a_i d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold throughout this paper.
To alleviate the notations, the subscript $k$ is often omitted.

To estimate the local parameters $\LocalVector{\theta} = \mat{a_1\; \cdots\; b_0 \cdots\; c_0\; \cdots}^{\T}$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
\begin{equation}
  \LocalWindow[k] 
  \isdef
  \Set{
    \omega_{k+r} 
    | 
    r \in \LocalShifts{k}
  }
\end{equation}
with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
\begin{equation}
  \LocalVector{U}_k \isdef 
  \mat{
    U(\omega_{k-N_W})\\
    \vdots\\
    U(\omega_{k})\\
    \vdots\\
    U(\omega_{k+N_W})\\
  }
  \text{ and }
  \LocalVector{Y}_k \isdef 
  \mat{
    Y(\omega_{k-N_W})\\
    \vdots\\
    Y(\omega_{k})\\
    \vdots\\
    Y(\omega_{k+N_W})\\
  }
  \text{,}
\end{equation}
and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
$
  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
$, where $\hadamard$ denotes the entry-wise product (or Hadamard product).
Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
\begin{equation}
  \LocalVector{Y} 
  \approx 
  \hat{\LocalVector{Y}} 
    =
      \LocalModel{G} \hadamard \LocalVector{U} + \LocalModel{T}
      \text{.}
      \label{eq:local-system-equations}
\end{equation}
Note that this encompasses $\numel{\Window}$ complex equations in the $\numel{\theta} = \numel{A} + \numel{B} + \numel{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
Consequently, a necessary condition to compute the model parameters is that
\begin{equation}
  \DOF = \numel{\Window} - \numel{\theta}
       = 2 \numel{W} - \numel{A} - \numel{B} - \numel{C} - 1
\end{equation}
is positive.
To effectively compute the local model parameters, the equation error in \eqref{eq:local-system-equations} is minimized by formulating a quadratic cost function:
\begin{equation}
  \LocalVector{\CostFunc{\LRIC}} 
    \isdef 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)^{\HT} 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)
   \label{eq:costfunc:LRIC}
   \text{.}
\end{equation}
Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires time-consuming iterative optimization schemes to obtain a parameter estimate.

\subsection{The Local Rational Method}
The \gls{LRM} as first introduced by \citep{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A}\LocalVector{Y} \approx \LocalModel{B} \LocalVector{U}  - \LocalVector{C}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
\end{equation}
Equivalently, this can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalVector{K} \LocalVector{\theta} + \LocalModel{V}
\end{equation}
where $\LocalVector{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:design-matrix}
  \LocalVector{K} 
    & \isdef 
  \mat{
     \LocalVector{K}_A &
     \LocalVector{K}_B & 
     \LocalVector{K}_C
  }\\
  \LocalVector{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\numel{A}}
    }\\
  \LocalVector{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\numel{B}}
    }\\
  \LocalVector{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\numel{C}}
    }\\
    \LocalVector{d}^{n} & \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$.}
\end{align}
and $\LocalModel{V}$ are the model residuals.
This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \LocalVector{\theta}_{\LRM} 
    \isdef \pinv{\LocalVector{K}} \LocalVector{Y}
    = \left( \LocalVector{K}^{\HT} \LocalVector{K} \right)^{-1} \LocalVector{K}^{\HT} \LocalVector{Y}
\end{equation}
where $\pinv{K}$ denotes the Moore-Penroose pseudo-inverse of $K$.

\TODO{hier voortschrijven}

\subsection{The Local Rational Method with Iterative Cost}

\subsection{Notes}

Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:design-matrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G,eq:LRM:model:T}
\begin{equation}
\dw{r}{k} \isdef \frac{\omega_{k+r} - \omega_k}{\Delta \omega_k}
\label{eq:freqScaling}
\end{equation}
where
\begin{equation}
  \Delta \omega_k \isdef
  \max
  \Set{
    \abs{ \omega_k - \omega_j} |  \vphantom{\frac{a}{b}}  \omega_j \in \LocalWindow[k]
  }
\end{equation}
such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.

\TODO{define local cost}
\TODO{define local design matrix}

\section{Theory: bias}
\label{sec:biascalc}
Since the local design matrix \eqref{eq:designMatrix} contains the noisy output spectrum $\LocalVector{Y}$ when $\numel{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.

To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
Let us denote the expected value of the cost function over all measurements $\LocalVector{Z}$ as
\begin{align}
  \ELSCost{\theta}
              & \isdef 
                   \E[\LocalVector{Z}]%
                         {    
                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
              & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
    \ELSCost[0]{\theta} & \isdef 
            \frac{1}{F} 
                \sum_{r} 
                     \left| 
                             \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}
                          - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}
                          - \LocalModel{C}(r, \LocalVector{\theta}) 
                    \right|^2 \\
    \ELSCost[n]{\theta} & \isdef 
              \frac{1}{F} 
                     \sum_{r} 
                              \left| \LocalModel{A}(r,\LocalVector{\theta}) \right|^2 
                              \sigma_V^2
\end{align}
Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
\begin{multline}
  \ELSCost{\theta} = \ELSCost{\true\theta} 
  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right)\\
  + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \theta - \true\theta \right)
   \text{.}
\end{multline}
The minimizer $\estim\theta$ of this function can be obtained by equating the derivative
\begin{equation}
  \PartialDerivative{\ELSCost{\estim\theta}}{\estim\theta} = \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \estim\theta - \true\theta \right)
\end{equation}
to zero.
This is equivalent to 
\begin{equation}
  \left( \estim\theta - \true\theta \right) = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}
which expresses the bias $\Delta\theta = \left( \estim\theta - \true\theta \right)$ of the estimated parameters.
Since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$, this simplifies to
\begin{equation}
  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}

Do note that the estimated parameters are complex values but that $\ELSCost{\theta}$ is a real-valued function.
This implies that the derivatives with respect to $\theta$ have to be calculated with respect to the real and imaginary part of $\theta$ separately as explained in~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012}.

\TODO{write out subexpressions}
As a first order approximation, the bias on the \gls{FRF} can be written as
\begin{equation}
  \Delta \LocalModel{G}(\omega) \approx \PartialDerivative{\LocalModel{G}(\theta, \omega)}{\theta} \Delta \theta
\end{equation}

\section{Order selection}
Selecting suitable values of $\numel{W}$, $\numel{B}$, $\numel{A}$ and $\numel{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular $\numel{C} \leq \max\set{\numel{B},\numel{A}}$ and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that $2N_W + 1 \geq N_B + N_A + N_C + 2$.

Different heuristics exist to select the local bandwidth , e.g.~\citep{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
As such, we focus mainly on the selection of the model order hyper-parameters ($N_A$, $N_B$ and $N_C$) for a fixed value of $N$.

In this paper, we take an approach that decides amongst a group of candidate models, which model is a good model: i.e. one that captures that system dynamics but remains parsimonious.
To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g. value of the cost function, $R^2$, \ldots) and model complexity into account to ensure that the model captures only the systematic behavior and not random variations of the particular measurement.
The latter is often done using `cross-validation'.

In statistical learning, many relevant cross-validation approaches exist.
Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
\paragraph{Plug-in methods}
In plug-in methods, a goodness-of-fit criterion (e.g. the log-likelihood function $\mathcal{L}$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
\begin{equation}
  L_{\mathrm{AIC(c)}} = - 2  \mathcal{L}(M | Z) + 2 \numel{\theta} + c \frac{2 \numel{\theta} (\numel{\theta} + 1)}{\numel{\Window} - \numel{\theta} - 1}
\end{equation}
where $\numel{\Window}$ is the number of  estimated parameters in the model $M(\theta)$.
For \gls{AIC} $c=0$, and $c=1$ produces the \gls{AICc}.
In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\numel{Z} \to \infty$, which is obviously an unwarranted choice.
The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
\begin{equation}
  M_{\star} \isdef 
  \arg_{M} \min 
  \Set{
    L_{\mathrm{AIC(c)}}(M)
  }
\end{equation}
To select the best model $M_{\star}$ with such a criterion, the model $M_k$ among a set of models $\set{M_1, M_2, \ldots}$ that produces the smallest value of $L_{\mathrm{AICc}}$ is retained.

\begin{remark}
It should be noted that due to $\mathcal{L}(M | Z)$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is tightly coupled with the particular dataset $Z$.
Practically, this means that such criteria can only be used to compare local models that estimated from the same local dataset (i.e. they have the same $\numel{\Window}$ and center frequency).
\end{remark}

\paragraph{Holdout method}
The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g. $70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g. cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.

\begin{remark}
Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
\end{remark}

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = \frac{1}{2N_W+1} \sum_{r=-N_W}^{N_W} 
                          \abs{\ignoring{r}{\LocalVector{e}}}^2
                          \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\hat{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
The model with the smallest \gls{PRESS} is retained.
In general, this means that \gls{LOOCV} requires estimating $2N_W + 1$ additional models (one for each omitted data point) and hence can be very time-consuming.

For linear models (i.e. $\LocalVector{Y} = \LocalVector{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
\begin{equation}
\PRESS = \frac{\LocalVector{E}^{\HT} \LocalVector{W}^{-1} \LocalVector{E}}{2N_W + 1}
\end{equation}
where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
$\LocalVector{H} = \LocalVector{K} \pinv{\LocalVector{K}}$ is the so-called `hat-matrix' that is known to be idempotent.

\section{Simulation}
\label{sec:simulations}

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
G_0(z) = \frac{0.64587 z + 0.64143}
                             {47.9426 z^2 - 51.2955 z + 46.9933}
\end{equation}

\begin{figure}
 \centering
  \input{\thisDir/figs/generalized-output-error.tikz}
  \caption{Block schematic used in the simulations}
\end{figure}

\TODO{H0}

\TODO{SNR}
The \gls{SNR} in the system bandwidth $\BW$ is defined as
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int_{\BW} \abs{Y_0(\omega)}^2 \dd{\omega}}
            {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\BW$ is the frequency range where

\TODO{plot example spectrums}

  % \subsection{Implications of the model structure}
  \subsection{Implications of the noise level}
  % \subsection{Implications of the noise coloring}

\TODO{insert figure: Y(Y,E,T) vs freq}
\TODO{insert figure: err vs SNR}

  \section{Measurements}
  \label{sec:measurements}
   \subsection{AVIS}
   \subsection{F16}

  \section{Conclusion}
  \label{sec:conclusion}

  \begin{itemize}
    \item LRM: extension to LRIC
    \item LRM: derivation of bias
    \item LRM vs LPM: at which settings is LRM better than LPM
    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
  \end{itemize}

### 2016-03-19 config/glossaries.inc.tex
Import LRM Hinf files
Atually include figures + text from CH04
Some musings in future research
Import LRM-paper draft

@@
 \newacronym{ADC}{ADC}{analog-to-digital converter}
+\newacronym{AICc}{AICc}{Akaike's information criterion corrected for small sample sizes}
+\newacronym{AIC}{AIC}{Akaike's information criterion}
+\newacronym{AVIS}{AVIS}{active vibration isolation system}
 
@@
 
+\newacronym{EIV}{EIV}{errors-in-variables}
 \newacronym{ETFE}{ETFE}{empirical transfer function estimate}
@@
 
+\newacronym{LCF}{LCF}{left co-prime factorization}
+\newacronym{LFT}{LFT}{linear fractional transformation}
 \newacronym{LML}{LML}{log marginal likelihood}
+\newacronym{LOOCV}{LOOCV}{leave-one-out cross-validation}
+\newacronym{LMM}{LMM}{Local Modeling Method}
 \newacronym{LPM}{LPM}{Local Polynomial Method}
+\newacronym{LPV}{LPV}{linear parameter-varying}
 \newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
@@
 \newacronym{LTI}{LTI}{linear time-invariant}
+\newacronym{LTV}{LTV}{linear time-varying}
 
@@
 \newacronym{PDF}{PDF}{probability distribution function}
+\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
 \newacronym{PSD}{PSD}{power spectral density}
@@
 \newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
+\newacronym{RCF}{RCF}{right co-prime factorization}
 \newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
@@
 
+\newacronym{SA}{SA}{spectral analysis}
 \newacronym{SIMO}{SIMO}{single-input multiple-output}
@@
 \newacronym{SNR}{SNR}{signal to noise ratio}
+\newacronym{STFT}{STFT}{short-time Fourier transform}
 

### 2016-03-20 ch03-lrm/smoothingRMSdecrease.tex
Some small things

@@
 \newcommand{\segm}[2]{\ensuremath{{#1}^{[#2]}}}
-\newcommand{\RMS}{\ensuremath{\,\mathrm{rms}\,}}
-\newcommand{\rms}[1]{\ensuremath{\RMS\left(#1\right)}}
-\newcommand{\floor}[1]{\ensuremath{\lfloor #1 \rfloor}}
 
@@
 
-  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \cite{Parsons1974}, while accounting for the degrees of freedom in each segment.
+  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
   For zero-mean noise, these variances can be related to the RMS value of each noise segment.
@@
   \begin{equation}
-    s^2(i) = \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
+    s^2(i) 
+    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
     = \left( \rms{\hat{g}^{[i]}} \right)^2
@@
   \begin{align}
-     H_0 :&\,\, s^2(i-1) = s^2(i)\\
-     H_1 :&\,\, s^2(i-1) > s^2(i)
+     \nullHypothesis &: s^2(i-1) = s^2(i)\\
+     \altHypothesis    &: s^2(i-1) > s^2(i)
      \text{.}
@@
   Using the $F$-test on the RMS values of the two segments with a high confidence level of $\alpha=0.99$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
-  The high level of confidence ($\alpha=0.99$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \cite{Parsons1974}.
+  The high level of confidence ($\alpha=0.99$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \citep{Parsons1974}.
   In our case, such an error means that a part of the actual impulse response would falsely be regarded as noise, which could significantly increase the bias as information of the system is discarded.
@@
  \setlength\figurewidth{0.8\columnwidth}
-  \input{truncRMS.tikz}
-\caption{Schematic of statistical determination of a smooth (improved) FRF. The different segments are separated by dotted lines.}
+  \input{\thisDir/figs/truncRMS.tikz}
+\caption{Schematic of statistical determination of a smooth (improved) FRF. 
+The different segments are separated by dotted lines.}
 \label{FRF_truncate_stat_EG}

### 2016-03-20 ch05-initvals/initial-values.tex
'linear zoom' in captions
Some small things

@@
 \end{subequations}
-where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
+where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
 \TODO{notatie LPM uniform maken met CH03/CH04}
@@
   \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
-  The bottom plot shows a zoom of the top plot.
+  The bottom plot shows a linear zoom of the top plot.
   For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
@@
   $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
-  The bottom plot shows a zoom of the top plot.
+  The bottom plot shows a linear zoom of the top plot.
   The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.

### 2016-03-20 front-and-back-matter/frontmatter.tex
Address some TODOs
Different figure names per chapter
Some small things
Address some minor TODOs

@@
+\tikzsetfigurename{frontfig}
+
 \input{front-and-back-matter/acknowledgements.inc.tex}
@@
 
-% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this
-
-\printglossary[type=\acronymtype,style=long,toctitle={List of Abbreviations}, title={List of Abbreviations}] %TODO: change format
+\printglossary[type=\acronymtype,style=longheader,toctitle={List of Abbreviations}, title={List of Abbreviations}]
 
 \glsaddall[types=symbols]
-\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]
+\printglossary[type=symbols,style=longheader,title={List of Symbols},toctitle={List of Symbols}]
 

### 2016-03-21 ch03-lrm/figs/batchM2T.m
Import CH03 figures as TikZ

@@ -1,0 +1,22 @@
+files = dir('*.fig');
+
+asTikz = @(file) strrep(file.name, '.fig','.tikz');
+
+for file = files(:)'
+    fprintf(' %s \t -> \t %s \n', file.name, asTikz(file));
+    
+    hFig = open(file.name);
+    finallyCloseFigure = onCleanup(@() close(hFig));
+    try
+        matlab2tikz(asTikz(file), 'figurehandle', hFig, ...
+                    'width', '\figurewidth', ...
+                    'height', '\figureheight', ...
+                    'standalone', false, ...
+                    'externalData', true, ...
+                    'relativeDataPath', '\thisDir/figs/', ...
+                    'showInfo', false);
+    catch ME
+        fprintf(2,'Error "%s" during conversion of %s\n%s\n\n', ...
+                ME.identifier, file.name, getReport(ME));
+    end
+end

### 2016-03-21 ch03-lrm/figs/batchM2T.m
batchM2T improved

@@ -1,22 +1,43 @@
-files = dir('*.fig');
+function batchM2T(files, m2tOptions)
+% BATCHM2T batch conversion of FIG figures to TIKZ
+%
+% Converts all FIG files in the current directory to TikZ using
+% matlab2tikz.
+%
+% Usage:
+%
+%    BATCHM2T()
+%
+% See also: matlab2tikz
 
-asTikz = @(file) strrep(file.name, '.fig','.tikz');
-
-for file = files(:)'
-    fprintf(' %s \t -> \t %s \n', file.name, asTikz(file));
-    
-    hFig = open(file.name);
-    finallyCloseFigure = onCleanup(@() close(hFig));
-    try
-        matlab2tikz(asTikz(file), 'figurehandle', hFig, ...
-                    'width', '\figurewidth', ...
-                    'height', '\figureheight', ...
-                    'standalone', false, ...
-                    'externalData', true, ...
-                    'relativeDataPath', '\thisDir/figs/', ...
-                    'showInfo', false);
-    catch ME
-        fprintf(2,'Error "%s" during conversion of %s\n%s\n\n', ...
-                ME.identifier, file.name, getReport(ME));
+    %% Default options
+    if ~exist('files','var') || isempty(files)
+        files = dir('*.fig');
     end
+    if ~exist('m2tOptions','var')
+        m2tOptions = {'width', '\figurewidth', ...
+                      'height', '\figureheight', ...
+                      'standalone', false, ...
+                      'externalData', true, ...
+                      'relativeDataPath', '\thisDir/figs/', ...
+                      'showInfo', false};
+    end
+
+    asTikz = @(file) strrep(file.name, '.fig','.tikz');
+
+    %% Conversion
+    for file = files(:)'
+        fprintf(' %s \t -> \t %s \n', file.name, asTikz(file));
+        
+        hFig = open(file.name);
+        finallyCloseFigure = onCleanup(@() close(hFig));
+
+        try
+            matlab2tikz(asTikz(file), 'figurehandle', hFig, m2tOptions{:});
+        catch ME
+            fprintf(2,'Error "%s" during conversion of %s\n%s\n\n', ...
+                    ME.identifier, file.name, getReport(ME));
+        end
+    end
+
 end

### 2016-03-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some figures reimported as TikZ + text on truncation

@@
 \TODO{figures to TikZ}
-\TODO{re-introduce $F$-test truncator and box-carr averager}
 \TODO{labels into standardized form}
@@
 \centering
-\includegraphics{\thisDir/figs/tikz0.pdf}
+\setlength\figurewidth{0.85\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/oesetup.tikz}
 \caption{SISO LTI discrete-time system in an output error setup.}
@@
 
-\item
-Assuming that the impulse response decays exponentially in time, the noise is bound to predominate after a certain time interval.
+\item Assuming that the impulse response decays with the passing of time, the noise is bound to predominate after a certain time interval. 
+In particular, when $t > \truncTime$, the impulse response has decayed below the noise floor.
+In \secref{sec:nonparametric:truncation:Ftest} and \secref{sec:nonparametric:truncation:exponentialFit}, two approaches are introduced to estimate $\truncTime$.
 
-\item
-An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response.
+\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response.
 
-\item
-A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
+\item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
 
 This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
-An exponential fitting method is introduced to determine the truncation point.
 \end{enumerate}
@@
 \end{align}
+\end{enumerate}
+
+\subsection{Truncation Via the $F$-Test}
+\label{sec:nonparametric:truncation:ftest}
+To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments.
+One can then gradually determine whether these segments are noise or the actual impulse response.
+
+% 1) cut into NS segments of minimally NM samples
+% 2) assume last segment == noise
+%    start from back
+% 3) F-test on Var, Var==RMS if dc == 0 (i.e. noise)
+%    H0: s²(1) =  s²(2)
+%    H1: s²(1) >  s²(2)
+%    alpha >> ==> beta <<
+% 4) if H1 and RMS(signal)/RMS(noise) > f
+%    robustness, SNR
+%    select segment i
+% 5) refine until wanted resolution is obtained
+
+\begin{enumerate}
+  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
+$L_S = \floor{\frac{N}{N_S}}$. 
+If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
+The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
+  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
+
+  \item Iteration is then carried out from the last segment ($i = N_S$) towards the beginning of the impulse response.
+To determine whether the preceding segment $\segm{\hat{g}}{i-1}$ is completely dominated by noise,  both an $F$-test and an absolute criterion on the RMS are used.
+
+  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
+  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
+  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
+  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
+  \begin{equation}
+    s^2(i) 
+    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
+    = \left( \rms{\hat{g}^{[i]}} \right)^2
+           \text{.}
+  \end{equation}
+  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
+  \begin{align}
+     \nullHypothesis &: s^2(i-1) = s^2(i)\\
+     \altHypothesis    &: s^2(i-1) > s^2(i)
+     \text{.}
+  \end{align}
+  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
+  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
+  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
+  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
+  \begin{equation}
+    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
+  \end{equation}
+  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of an $F$ distribution with $n_{i-1}$ and $n_{i}$ degrees of freedom.
+  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.
+
+  The high level of confidence ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \citep{Parsons1974}.
+  In our case, such an error means that a part of the actual impulse response would be falsely classified as noise, which could significantly increase the bias as information of the system is discarded.
+  A Type~I error is less detrimental since, in that case, noise is falsely classified as a signal component and kept in the impulse response, thereby causing a sub-optimal value of the variance of the estimate.
+  As the \gls{LPM} samples are correlated over a short frequency span, the actual noise present in $\hat{g}$ may be slightly non-stationary.
+  To cope with this, one can introduce other criteria which must be satisfied together with the outcome of the $F$-test.
+  A criterion that shows good results is to check whether the segment $\segm{\hat{g}}{i-1}$ has an RMS value that is at least a factor $\kappa$ larger than the RMS of the noise.
+  Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed. 
+%  \JL{Q: doesn't this increase the probability of a Type II error?}
+%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}
+
+  \item This procedure is repeated until a segment $\segm{\hat{g}}{i-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
+  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{i-1}$.
+  One now has the choice to accept the last sample of $\segm{\hat{g}}{i-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
+  The accuracy of this estimate is limited by the length of the segment $L_S$.
+
+  \item
+  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{i-1}$ -- which may contain both the signal and noise -- yet again into smaller segments.
+The procedure described above is then repeated until a satisfactory, accurate $\truncTime$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values.
+%rely on the RMS values to be accurate.
+  To start this refinement, the last $\segm{\hat{g}}{i}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{i-1}$ cannot be asserted to be dominated by noise.
 
 \end{enumerate}
+This procedure is illustrated in \figref{fig:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
+\begin{subequations}
+\label{eq:systemSimulations}
+\begin{align}
+y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
+y(t)       &= y_0(t) + e(t),
+\end{align}
+\end{subequations}
+where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
+% \eqref{eq:systemSimulations}. 
+The figure shows segments of the estimated impulse response.
+The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions.
+The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.
+%after which all samples are fixed to a zero value for the smoothed estimate.
 
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}\label{se:truncImpulseResp}
+\begin{figure}[tbh]
+\centering
+\remakeNextFigure
+ \setlength\figurewidth{0.8\columnwidth}
+ \setlength\figureheight{0.68\figurewidth}
+  \input{\thisDir/figs/truncRMS.tikz}
+\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.
+The different segments are separated by dotted lines.}
+\label{fig:nonparametric:truncation:Ftest}
+\end{figure}
+
+\subsection{Truncation of the Impulse Response Via Exponential Fitting}
+\label{sec:nonparametric:truncation:exponentialfit}
 
@@
     \centering
+    \setlength\figurewidth{0.85\columnwidth}
+    \setlength\figureheight{0.68\figurewidth}
+
     \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
@@
    \centering
-	\includegraphics{\thisDir/figs/HistogramExpFitting.pdf}
-         \caption[RMS error of the FRF versus truncation time.]{Black full line (left hand side y-axis (ordinate)): total \gls{RMS} error as a function of the truncation time (the single black dot is the minimum of the \gls{RMS}).
-Gray histogram (right hand side y-axis (ordinate)): selected truncation times for 1000 noise realizations by the exponential fitting methods.}
+        \setlength\figurewidth{0.85\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/pdfs.tikz}
+         \caption[RMS error of the FRF versus truncation time.]{
+         The left y-axis shows the \gls{RMS} error of the estimated \gls{FRF} as a function of the chosen truncation time $\truncTime$.
+         The corresponding optimal $\truncTime$ is indicated as well.
+         Both bar plots (right y-axis) indicate for $\nMC =1000$ realizations of the disturbing noise and excitation signal, the number of times that $\truncTime$ has been selected by means of either the method using the $F$-test or the method that fits an exponential.
+         It can be seen that both methods allow to almost halve the \gls{RMS} error and approach the optimal truncation time.}
    \label{fig:pdfAndRMSeVStruncTime}
@@
 
-The truncation time is determined from the data as described in \secref{se:truncImpulseResp}.
+The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}.
 This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution.
-A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
+Clearly, both methoda for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of its distribution (around the $90^{\text{th}}$ sample).
 
-From the plot, we can conclude that the \gls{RMSE} increases rapidly when $t_{\mathrm{trunc}}$ is smaller than the optimal.
-On the other hand, selection of a value of $t_{\mathrm{trunc}}$ that is too large, is not nearly as detrimental to the modeling error.
+For the $F$-test based method, the obtained $\truncTime$ values only take a discrete set of values due to the limitation of the segment length.
+While most trials result in $\truncTime \in \Set{90, 80, 70}$, a few outliers can be observed.
+This can be attributed to the high power of the $F$-tests that are performed.
+
+For the exponential fitting approach, however, a closely grouped set of (continuous) values for $\truncTime$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
+Although this distribution has a mode quite a bit higher than the method using the $F$-test, due to the absence of outliers, this method is more reliable to use.
+
+From the plot, we can conclude that the \gls{RMSE} increases rapidly when $\truncTime$ is smaller than the optimal.
+On the other hand, selection of a value of $\truncTime$ that is too large, is not nearly as detrimental to the modeling error.
 The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
@@
 
-\subsection{Conclusion}\label{se:conclusion}
+\begin{guideline}[Check and reinforce assumptions in the data.]
+As illustrated by the presented smoothing operation, it pays off to check typical assumptions of the system (e.g.
+smoothness of the \gls{FRF}, finite support of the impulse response) and even artificially reinforce such assumptions to improve the model quality.
+\end{guideline}
+
+\subsection{Conclusion}
+\label{se:conclusion}
 

### 2016-03-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Include more figures into CH03

@@
   \end{equation}
-  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of an $F$ distribution with $n_{i-1}$ and $n_{i}$ degrees of freedom.
+  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom.
   In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.
@@
 \centering
-\remakeNextFigure
  \setlength\figurewidth{0.8\columnwidth}
@@
     \setlength\figureheight{0.68\figurewidth}
+    \input{\thisDir/figs/figLPMvsTrunc.tikz}
 
@@
 
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
+\begin{figure}
    \centering
-        \setlength\figurewidth{0.85\columnwidth}
+   \remakeNextFigure
+        \setlength\figurewidth{0.68\columnwidth}
         \setlength\figureheight{0.68\figurewidth}
@@
 A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
+
+\TODO{write about boxcar average, add reference}
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/expFitBoxAverager.tikz}
+         \caption{Exponential fit of a boxcar averager}
+\end{figure}
+
+\TODO{RMSE vs $\truncTime$ for boxcar figure}

### 2016-03-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
More figures CH03

@@
 \centering
- \setlength\figurewidth{0.8\columnwidth}
+ \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
   \input{\thisDir/figs/truncRMS.tikz}
-\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.
-The different segments are separated by dotted lines.}
+\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.}
 \label{fig:nonparametric:truncation:Ftest}
@@
    \centering
-   \remakeNextFigure
         \setlength\figurewidth{0.68\columnwidth}

### 2016-03-22 config/styles.inc.tex
Small consistency changes
Some figures reimported as TikZ + text on truncation
More figures CH03
More LPM-trunc figures

@@
 %% Colors
-  \definecolor{tangored}{named}{TangoScarletRed1}
-  \definecolor{tangoblue}{rgb}{0.203922,0.396078,0.643137}
-  \definecolor{tangogreen}{named}{TangoChameleon2}
-  \definecolor{tangogrey}{named}{TangoAluminium5}
+  \colorlet{tangored}{TangoScarletRed1}
+  \colorlet{tangoblue}{TangoSkyBlue2}
+  \colorlet{tangogreen}{TangoChameleon2}
+  \colorlet{tangogrey}{TangoAluminium5}
 
-  \definecolor{meas}{named}{TangoPlum2}
+  \colorlet{meas}{TangoPlum2}
 
-  \definecolor{goallight}{named}{TangoChameleon1}
-  \definecolor{goal}{named}{TangoChameleon2}
-  \definecolor{goaldark}{named}{TangoChameleon3}
+  \colorlet{goallight}{TangoChameleon1}
+  \colorlet{goal}{TangoChameleon2}
+  \colorlet{goaldark}{TangoChameleon3}
 
-  \definecolor{obtainedlight}{named}{TangoScarletRed1}
-  \definecolor{obtained}{named}{TangoScarletRed2}
-  \definecolor{obtaineddark}{named}{TangoScarletRed3}
+  \colorlet{obtainedlight}{TangoScarletRed1}
+  \colorlet{obtained}{TangoScarletRed2}
+  \colorlet{obtaineddark}{TangoScarletRed3}
 
-  \definecolor{model}{named}{tangogrey}
-  \definecolor{bg}{named}{TangoAluminium2}
+  \colorlet{model}{tangogrey}
+  \colorlet{bg}{TangoAluminium2}
 
-\definecolor{model}{named}{black}
-\definecolor{truesys}{named}{TangoAluminium5}
-% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper
+\colorlet{model}{black}
+\colorlet{truesys}{TangoAluminium5}
+% \colorlet{truesys}{TangoAluminium4} % from LRMHinf paper
 
-\definecolor{linms}{named}{TangoSkyBlue3}
-\definecolor{logms}{named}{TangoChameleon2}
-\definecolor{qlogms}{named}{TangoPlum3}
-\definecolor{clogms}{named}{TangoScarletRed3}
-\definecolor{plogms}{named}{TangoOrange3}
+\colorlet{linms}{TangoSkyBlue3}
+\colorlet{logms}{TangoChameleon2}
+\colorlet{qlogms}{TangoPlum3}
+\colorlet{clogms}{TangoScarletRed3}
+\colorlet{plogms}{TangoOrange3}
 
-\definecolor{sigmalinms}{named}{linms}
-\definecolor{sigmaqlogms}{named}{qlogms}
-\definecolor{sigmaclogms}{named}{clogms}
+\colorlet{sigmalinms}{linms}
+\colorlet{sigmaqlogms}{qlogms}
+\colorlet{sigmaclogms}{clogms}
 
-\definecolor{biaslinms}{named}{TangoSkyBlue1}
-\definecolor{biasqlogms}{named}{TangoPlum1}
-\definecolor{biasclogms}{named}{TangoScarletRed1}
+\colorlet{biaslinms}{TangoSkyBlue1}
+\colorlet{biasqlogms}{TangoPlum1}
+\colorlet{biasclogms}{TangoScarletRed1}
 
-\definecolor{dbacolor}{named}{TangoScarletRed2}
-\definecolor{dbbcolor}{named}{TangoSkyBlue2}
-\definecolor{dbccolor}{named}{TangoChameleon2}
-\definecolor{dbdcolor}{named}{TangoOrange2}
+\colorlet{dbacolor}{TangoScarletRed2}
+\colorlet{dbbcolor}{TangoSkyBlue2}
+\colorlet{dbccolor}{TangoChameleon2}
+\colorlet{dbdcolor}{TangoOrange2}
 
 \definecolor{compen}{rgb}{0.729,0.741,0.714}
-\definecolor{signal}{named}{TangoSkyBlue2}
-\definecolor{misalign}{named}{TangoScarletRed2}
+\colorlet{signal}{TangoSkyBlue2}
+\colorlet{misalign}{TangoScarletRed2}
 
-\definecolor{first}{named}{TangoScarletRed2}
-\definecolor{second}{named}{TangoOrange2}
-\definecolor{third}{named}{TangoChameleon3}
-\definecolor{fourth}{named}{TangoSkyBlue3}
-\definecolor{fifth}{named}{TangoPlum1}
-\definecolor{sixth}{named}{TangoChocolate2}
+\colorlet{first}{TangoScarletRed2}
+\colorlet{second}{TangoOrange2}
+\colorlet{third}{TangoChameleon3}
+\colorlet{fourth}{TangoSkyBlue3}
+\colorlet{fifth}{TangoPlum1}
+\colorlet{sixth}{TangoChocolate2}
 
-\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
-\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
-\definecolor{RFIR}{named}{TangoScarletRed3}
-\definecolor{RFIRInit}{named}{TangoScarletRed1}
-\definecolor{existing}{named}{TangoChameleon3}
-\definecolor{G0Hat}{named}{TangoOrange2}
-\definecolor{GVXI}{named}{G0Hat}
-\definecolor{reference}{named}{black}
+\colorlet{LPMTrunc}{TangoSkyBlue2}
+\colorlet{LPMTruncInit}{TangoSkyBlue2}
+\colorlet{RFIR}{TangoScarletRed3}
+\colorlet{RFIRInit}{TangoScarletRed1}
+\colorlet{existing}{TangoChameleon3}
+\colorlet{G0Hat}{TangoOrange2}
+\colorlet{GVXI}{G0Hat}
+\colorlet{reference}{black}
 
-\definecolor{heuristic}{named}{TangoPlum2}
-\definecolor{observed}{named}{TangoOrange3}
+\colorlet{heuristic}{TangoPlum2}
+\colorlet{observed}{TangoOrange3}
 
-\definecolor{best}{named}{TangoAluminium6}
+\colorlet{best}{TangoAluminium6}
 
-\definecolor{G0HatFill}{named}{TangoOrange1}
-\definecolor{GVXIFill}{named}{G0HatFill}
-\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
-\definecolor{RFIRFill}{named}{TangoScarletRed1}
-\definecolor{existingFill}{named}{TangoChameleon1}
-\definecolor{bestFill}{named}{TangoAluminium3}
+\colorlet{G0HatFill}{TangoOrange1}
+\colorlet{GVXIFill}{G0HatFill}
+\colorlet{LPMTruncFill}{TangoSkyBlue1}
+\colorlet{RFIRFill}{TangoScarletRed1}
+\colorlet{existingFill}{TangoChameleon1}
+\colorlet{bestFill}{TangoAluminium3}
 
-\definecolor{FRFMean}{named}{TangoPlum3}
-\definecolor{FRFSingle}{named}{TangoPlum1}
-\definecolor{FRFNoise}{named}{TangoChocolate1}
+\colorlet{FRFMean}{TangoPlum3}
+\colorlet{FRFSingle}{TangoPlum1}
+\colorlet{FRFNoise}{TangoChocolate1}
 
-\definecolor{LRM}{named}{TangoScarletRed3}
-\definecolor{LPM}{named}{TangoSkyBlue2}
-\definecolor{SA}{named}{TangoChameleon2}
+\colorlet{LRM}{TangoScarletRed3}
+\colorlet{LPM}{TangoSkyBlue2}
+\colorlet{SA}{TangoChameleon2}
 
-\definecolor{validation}{named}{TangoChameleon2}
+\colorlet{validation}{TangoChameleon2}
 
-\definecolor{LPMshade}{named}{TangoSkyBlue1}
-\definecolor{LRMshade}{named}{TangoScarletRed1}
-\definecolor{refColor}{named}{TangoAluminium6}
+\colorlet{LPMshade}{TangoSkyBlue1}
+\colorlet{LRMshade}{TangoScarletRed1}
+\colorlet{refColor}{TangoAluminium6}
 
-\definecolor{frf}{named}{TangoButter3} %TODO: replace
-\definecolor{param}{named}{TangoScarletRed2}
+\colorlet{frf}{TangoButter3} %TODO: replace
+\colorlet{param}{TangoScarletRed2}
 
-  \definecolor{bwfill}{named}{TangoAluminium1}
-  \definecolor{bwline}{named}{TangoAluminium5}
-
-  \definecolor{safezone}{named}{bwfill}
+  \colorlet{bwfill}{TangoAluminium1}
+  \colorlet{bwline}{TangoAluminium5}
 
@@
 
-%% marker styles
-
 %% pgfplots styles
@@
 \pgfplotsset{signalrectanglerobust/.style={fill=signal!50,fill opacity=0.5,color=signal!30}}
-
-\pgfplotsset{safezone/.style={fill=safezone,fill opacity=0.5,color=safezone}}
 
@@
 
+%TODO: replace *res -> *meas
 \pgfplotsset{results/.style={solid,line width=0.7pt}}
@@
 
-%TODO: change these styles?
-\pgfplotsset{linmsmeas/.style={color=linms,solid,line width=0.7pt}}
-\pgfplotsset{qlogmsmeas/.style={color=qlogms,solid,line width=0.7pt}}
-\pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}
-\pgfplotsset{plogmsmeas/.style={color=plogms,solid,line width=0.7pt}}
+\pgfplotsset{measline/.style={solid,line width=0.7pt}}
+\pgfplotsset{linmsmeas/.style={color=linms,measline}}
+\pgfplotsset{qlogmsmeas/.style={color=qlogms,measline}}
+\pgfplotsset{clogmsmeas/.style={color=clogms,measline}}
+\pgfplotsset{plogmsmeas/.style={color=plogms,measline}}
 
@@
 \pgfplotsset{biasclogms/.style={color=biasclogms,clogmsmarker,biasline}}
+\pgfplotsset{biasplogms/.style={color=biasplogms,clogmsmarker,biasline}}
 
@@
 \pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}
+
+%% Truncation
+\pgfplotsset{truncationline/.style={dashdotdotted,line width=1.5pt,line join=round,line cap=round}}
+
+\colorlet{FSmooth}{TangoScarletRed3}
+\colorlet{expFit}{TangoSkyBlue3}
+\colorlet{trunc}{clogms}
+
+\pgfplotsset{FRFLPM/.style={color=LPM}}
+\pgfplotsset{FRFtrunc/.style={color=trunc}}
+
+\pgfplotsset{sigmaLPM/.style={sigmalinms}}
+\pgfplotsset{sigmaTrunc/.style={sigmaplogms}}
+
+\pgfplotsset{biasLPM/.style={biaslinms}}
+\pgfplotsset{biasTrunc/.style={biasclogms}}
+
+\pgfplotsset{histogramSmootherFTest/.style={ycomb,line width=1.5pt,fill=white!40!black,draw=white!40!black,area legend}}
+\pgfplotsset{histogramSmootherExpFit/.style={ycomb,line width=1.5pt,fill=white!70!black,draw=white!70!black,opacity=0.8,area legend}}
+
+\pgfplotsset{rmsOfSegment/.style={color=gray,line width=1pt,densely dotted}}
 

### 2016-03-23 config/styles.inc.tex
More uniform image styles

@@
 \colorlet{FSmooth}{TangoScarletRed3}
+\colorlet{FSmoothLight}{TangoScarletRed2}
 \colorlet{expFit}{TangoSkyBlue3}
+\colorlet{expFitLight}{TangoSkyBlue2}
 \colorlet{trunc}{clogms}
@@
 
-\pgfplotsset{histogramSmootherFTest/.style={ycomb,line width=1.5pt,fill=white!40!black,draw=white!40!black,area legend}}
-\pgfplotsset{histogramSmootherExpFit/.style={ycomb,line width=1.5pt,fill=white!70!black,draw=white!70!black,opacity=0.8,area legend}}
+% adapted from xbar legend from pgfplots manual
+\pgfplotsset{logHistogramLegend/.style={/pgfplots/legend image code/.code={%
+            \draw[##1,/tikz/.cd,bar width=3pt,yshift=-0.2em,bar shift=0pt]
+            plot coordinates {(0.15cm,0.6em) (0.3cm,0.8em) (0.45cm,0.6em)};}
+}}
+
+\pgfplotsset{logHistogram/.style={ycomb,line width=1.5pt,logHistogramLegend}}
+\pgfplotsset{histogramSmootherFTest/.style={logHistogram,fill=FSmoothLight,draw=FSmoothLight}}
+\pgfplotsset{histogramSmootherExpFit/.style={logHistogram,fill=expFitLight,draw=expFitLight,opacity=0.8}}
+
+\pgfplotsset{mainCurve/.style={color=black,solid,line width=1.5pt}}
+\pgfplotsset{pointOfInterest/.style={color=black,mark size=1.5pt,only marks,mark=*,mark options={solid}}}
 

### 2016-03-23 ch04-lrmhinf/paper.tex
small changes ch-2,ch04
Improve bibliography

@@
-\TODO{
   \begin{itemize}
-    \item fix labels for chapter
-    \item add section from Benchmark paper
-    \item fix some bib entries
-    \item Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)
+    \item \TODO{fix labels for chapter}
+    \item \TODO{add section from Benchmark paper}
+    \item \TODO{fix some bib entries}
+    \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
   \end{itemize}
-}
-\input{\thisDir/styles.inc.tex}
 
@@
 
-Several approaches have been developed to determine bounds on the model uncertainty. First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
+Several approaches have been developed to determine bounds on the model uncertainty. 
+First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
 However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
@@
   \centering
-  \setlength{\figurewidth}{0.8\columnwidth}
+  \setlength{\figurewidth}{0.68\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}
@@
 
-Classical \gls{SA} techniques~\citep{Bendat1980} can estimate the \gls{FRF} of $\Delta$.
+Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
 This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.

### 2016-03-23 ch05-initvals/code/plotSystemsStressTest.m
Improve code for stress test

@@ -1,0 +1,50 @@
+close all;
+clear variables;
+clc;
+
+systems  = systemsForStressTest;
+systems  = reshape(systems, 4,4); % reshape here to assure we have 16 filters
+szSys    = num2cell(size(systems));
+
+[~,~,Ts] = tfdata(systems{1}, 'v');
+t        = [0:Ts:1024]; %[s] time vector for simulation
+Tmax     = 200;         %[s] number of taps used for RFIR filter
+
+%% make Bode 
+figure('name','Bode Plots');
+bo              = bodeoptions;
+bo.FreqScale    = 'linear';
+bo.PhaseVisible = 'off';
+bo.YLim         = [-70 10];
+bo.XLim         = [0.1 1]*pi;
+
+for iFilter = 1:numel(systems)
+    subplot(szSys{:}, iFilter);
+    bode(systems{iFilter}, bo);
+end
+
+%% make figure
+figure('name','Impulse responses');
+hAx = repmat(gca, szSys{:});
+
+scaling = NaN(size(systems));
+
+for iFilter = 1:numel(systems)
+    g = impulse(systems{iFilter}, t);
+    scaling(iFilter) = max(abs(g));
+    gNorm = g./scaling(iFilter);
+    % gNorm = g;
+    
+    hAx(iFilter) = subplot(szSys{:}, iFilter);
+    hold on;
+    % proj = @(x)x;
+    proj = @abs;
+    
+    plot(t(t<=Tmax), proj(gNorm(t<=Tmax)), 'k');
+    plot(t(t>Tmax) , proj(gNorm(t>Tmax)) , 'r');
+end
+% set(hAx, 'XLim', [min(t) max(t)], 'YLim', [-1 1],...
+%          'XAxisLocation','origin','YAxisLocation','origin','box','off')
+set(hAx,'YScale','log','XScale','lin')
+set(hAx,'YLim',[1e-3, 1],'XLim',[1 max(t)])
+linkObject = linkprop(hAx(:),'XLim','YLim');

### 2016-03-23 ch05-initvals/code/systemsForStressTest.m

@@ -4,23 +4,23 @@ function G0s = systemsForStressTest()
     Qs    = 60;        % [dB] attenuation in stop-band
     wPass =  0.5;      % [pi rad/sample] cross-over frequency
     wBand = [0.4 0.6]; % [pi rad/sample] edges of the pass/stop band
-    G0s   = {DTFilter(@() cheby1(order, Qp,     wPass, 'low'      ))
-             DTFilter(@() cheby1(order, Qp,     wBand, 'bandpass' ))
-             DTFilter(@() cheby1(order, Qp,     wPass, 'high'     ))
-             DTFilter(@() cheby1(order, Qp,     wBand, 'stop'     ))
-             DTFilter(@() cheby2(order, Qp,     wPass, 'low'      ))
-             DTFilter(@() cheby2(order, Qp,     wBand, 'bandpass' ))
-             DTFilter(@() cheby2(order, Qp,     wPass, 'high'     ))
-             DTFilter(@() cheby2(order, Qp,     wBand, 'stop'     ))
-             DTFilter(@()  ellip(order, Qp, Qs, wPass, 'low'      ))
-             DTFilter(@()  ellip(order, Qp, Qs, wBand, 'bandpass' ))
-             DTFilter(@()  ellip(order, Qp, Qs, wPass, 'high'     ))
-             DTFilter(@()  ellip(order, Qp, Qs, wBand, 'stop'     ))
-             DTFilter(@() butter(order,         wPass, 'low'      ))
-             DTFilter(@() butter(order,         wBand, 'bandpass' ))
-             DTFilter(@() butter(order,         wPass, 'high'     ))
-             DTFilter(@() butter(order,         wBand, 'stop'     ))};
-function G = DTFilter(func)
+    G0s   = {normFilterDT(@() cheby1(order, Qp,     wPass, 'low'      ))
+             normFilterDT(@() cheby1(order, Qp,     wBand, 'bandpass' ))
+             normFilterDT(@() cheby1(order, Qp,     wPass, 'high'     ))
+             normFilterDT(@() cheby1(order, Qp,     wBand, 'stop'     ))
+             normFilterDT(@() cheby2(order, Qp,     wPass, 'low'      ))
+             normFilterDT(@() cheby2(order, Qp,     wBand, 'bandpass' ))
+             normFilterDT(@() cheby2(order, Qp,     wPass, 'high'     ))
+             normFilterDT(@() cheby2(order, Qp,     wBand, 'stop'     ))
[…]

### 2016-03-23 ch02-qlogms/code/derivativesSubsys.m
Fix derivatives of O(2) system
 - In the text, there was a factor `s` missing
 - In the figures, the same factor was missing

 In the script, the factor was present. Now, we plot
 the derivatives from within MATLAB to doublecheck
 the plots in the thesis as well

@@ -4,10 +4,11 @@ clc;
 
 syms K wz s wn xi wp 
 syms m
-m = 5; % mupad refuses to check for equality when m is symbolic (prolly some restraint is needed)
+m = 1; % mupad refuses to check for equality when m is symbolic (prolly some restraint is needed)
 
 G1 = K/(s+wp)
 G2 = K*(s/wz+1)/(s^2/wn^2 + 2*xi*s/wn + 1)^m
+% G2 = K*wn^(2*m)*(s+wz)/wz/(s^2 + 2*xi*wn*s + wn^2)^m
 
 derivative = @(f, x) simplify(diff(f,x))
 
@@ -23,12 +24,49 @@ denom = (D)^m;
 
 assert(logical(simplify(G2 == numer/denom)))
 
-dG2dK_man = G2/K
-dGdwz_man = -K*wn^(2*m)*s/wz^2/D^m
-dGdwn_man =  2*m*K*wn^(2*m-1)/wz*(s+wz)*(s+xi*wn)*s/D^(m+1)
-dGdxi_man = -2*K*m*wn^(2*m+1)*s*(s+wz)/wz/D^(m+1)
+%% Manual calculations
+% as displayed in the thesis
+dG2dK_man  =  G2/K
+dG2dwz_man = -K*wn^(2*m)*s/wz^2/D^m
+dG2dwn_man =  2*m*K*wn^(2*m-1)*(s+wz)/wz*(s+xi*wn)*s/D^(m+1)
+dG2dxi_man = -2*K*m*wn^(2*m+1)*s*(s+wz)/wz/D^(m+1)
 
-assert(logical(simplify(dGdK_man  == dG2dK)) , 'dGdK is wrong')
-assert(logical(simplify(dGdwz_man == dG2dwz)), 'dGdwz is wrong')
-assert(logical(simplify(dGdwn_man == dG2dwn)), 'dGdwn is wrong')
-assert(logical(simplify(dGdxi_man == dG2dxi)), 'dGdxi is wrong')
+%% Check for equality between muPad and manual calculations
+symEqual = @(a,b) logical(simplify(a==b));
+
+assert(symEqual(dG2dK_man,  dG2dK) , 'dGdK is wrong')
+assert(symEqual(dG2dwz_man, dG2dwz), 'dGdwz is wrong')
+assert(symEqual(dG2dwn_man, dG2dwn), 'dGdwn is wrong')
[…]

### 2016-03-23 ch02-qlogms/excitation-design.tex
Different figure names per chapter
Some small things
Fix derivatives of O(2) system
 - In the text, there was a factor `s` missing
 - In the figures, the same factor was missing

 In the script, the factor was present. Now, we plot
 the derivatives from within MATLAB to doublecheck
 the plots in the thesis as well
Fix calculation of deriv in CH02

@@
 \def\thisDir{ch02-qlogms}
+\tikzsetfigurename{ch02fig}
 \myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
@@
 
-Direct calculations for $\damping < 1$ give
+Direct calculations for $\damping \ll 1$ give
 \begin{align}
 \label{eq:excitation:auto}
-\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
-\end{align}
+\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
+ = 
+ \frac{\pi}
+          {8\wn[1]^2}\damping^{-3} 
++ \mathcal{O}(\damping^{-1}).
+\end{align}
+\begin{personalNote} 
+Value computed using Sage:
+\begin{align*}
+\frac{\pi {K}^{2}}
+          {16  \sqrt{1 - \damping^2}\wn^{2} \damping^{3}} 
++
+\frac{{\left(2  \damping^{2} + 1 \right)}  {K}^{2}}
+         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
++ 
+\frac{{K}^{2} \arctan  
+                               \left(
+                                       \frac{(2  \damping^{2} - 1) \sqrt{1-\damping^{2}}}
+                                                {2  (\damping^{3} - \damping)}
+                              \right)}
+         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
+\end{align*}
+Remark that the latter term for $\damping \to 0$ becomes
+\begin{equation}
+  \frac{{K}^{2} \pi / 2}
+         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
+\end{equation}
+as the argument for the $\arctan$ function tends to $\infty$.
+\end{personalNote}
+%
 For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
@@
             {\wz} 
-  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
+  \frac{s \left( s + \wz \right) \left( s+ \damping \wn \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
@@
     \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
-    The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
+    The $3\unit{dB}$ bandwidth ($\wdB$) around the peak frequency $\wM$ of the system is highlighted.}
     \label{fig:excitation:misalignment-logms}

### 2016-03-24 ch02-qlogms/excitation-design.tex
More details on computation Fi

@@
 \IF &= \frac{1}{\pi}
-         \int\limits_0^\infty \mathrm{Re}
+         \int\limits_0^\infty \RealPart
            \left\{      \frac{\partial G(j\omega)}{\partial \theta}
@@
 \end{align}
-which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \cite{Rojas2007}
+which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.
 
@@
 \partial G_{i,j} &= \int_0^\infty
-                      \mathrm{Re}\left\{
+                      \RealPart\left\{
                           \frac{\partial G_i}
@@
 
-Direct calculations for $\damping \ll 1$ give
-\begin{align}
-\label{eq:excitation:auto}
-\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
- = 
- \frac{\pi}
-          {8\wn[1]^2}\damping^{-3} 
-+ \mathcal{O}(\damping^{-1}).
-\end{align}
-\begin{personalNote} 
-Value computed using Sage:
-\begin{align*}
-\frac{\pi {K}^{2}}
+The $(1,1)$ element of the $\partial G_{1,1}$ entry of the information matrix is
+\begin{align}
+  \int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
+\end{align}
+which yields
+\begin{equation}
+\frac{\pi }
           {16  \sqrt{1 - \damping^2}\wn^{2} \damping^{3}} 
 + 
-\frac{{\left(2  \damping^{2} + 1 \right)}  {K}^{2}}
-         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
-+ 
-\frac{{K}^{2} \arctan  
+\frac{ 2\arctan  
                                \left(
@@
                               \right)}
-         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
-\end{align*}
-Remark that the latter term for $\damping \to 0$ becomes
-\begin{equation}
-  \frac{{K}^{2} \pi / 2}
-         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
-\end{equation}
-as the argument for the $\arctan$ function tends to $\infty$.
-\end{personalNote}
-%
+         {16  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
++
+\frac{{\left(2  \damping^{2} + 1 \right)} }
+         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
+\label{eq:excitation:auto:full}
+\end{equation}
+after lengthy calculations.
+For $\damping \ll 1$ this can be simplified to
+\begin{equation}
+\label{eq:excitation:auto}
+\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
+ = 
+ \frac{\pi}
+          {8\wn[1]^2}\damping^{-3} 
++ \bigO{\damping^{-2}}
+\end{equation}
+since the $\arctan$ in \eqref{eq:excitation:auto:full} tends to $\frac{\pi}{2}$ for $\damping \to 0$.
 For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
 \begin{gather}
-\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
+\left|\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
 \qquad \qquad \qquad \qquad \qquad
@@
 \leq
-\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
+\int_0^\infty\left|\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
 \leq \\

### 2016-03-26 ch05-initvals/initial-values.tex
LPM illustration improved

@@
 \section{Introduction}
-\label{se:introd}
+\label{sec:initial-values:introd}
 The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
@@
 The rest of the chapter is structured as follows. 
-\secref{se:ProbForm} covers the problem formulation. 
-\secref{se:MethodEg} presents the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
-This is followed by \secref{se:Demo} and \secref{se:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
-In \secref{se:Generality} the generality of the results is investigated briefly.
+\secref{sec:initial-values:ProbForm} covers the problem formulation. 
+\secref{sec:initial-values:MethodEg} presents the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
+This is followed by \secref{sec:initial-values:Demo} and \secref{sec:initial-values:ExpMeas}, which are demonstrations of the improved initial estimates on simulation and experimental data, respectively.
+In \secref{sec:initial-values:Generality} the generality of the results is investigated briefly.
 The computational effort and recommendations for practical implementations are given in \secref{sec:initvals:computation}.
-Ultimately, concluding remarks are presented in \secref{se:Conclusion}.
-
-\section{Problem formulation}\label{se:ProbForm}
+Ultimately, concluding remarks are presented in \secref{sec:initial-values:Conclusion}.
+
+\section{Problem formulation}\label{sec:initial-values:ProbForm}
 
@@
 The full model of the system is
-\begin{equation}\label{lpmtd1}
+\begin{equation}
 y(t)=\true{G}(q^{-1})u_0(t)+H_0(q^{-1})e(t)
+\label{eq:initial-values:OE:TD}
 \end{equation}
@@
 We only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this chapter.
-However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.
+However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{sec:initial-values:ExpMeas}.
 
@@
 For the simulations, white noise is used ($\true{H} = 1$ and $e(t) = v(t)$).
-It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{se:ExpMeas}.
+It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{sec:initial-values:ExpMeas}.
 
@@
 
-With reference to equation \eqref{lpmtd1}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
+With reference to equation \eqref{eq:initial-values:OE:TD}, the relation between the noiseless input and the output signals ($v(t)= 0$) is assumed to be of the form
 \begin{equation}
@@
 where $A$ and $B$ are polynomials in $q^{-1}$. 
-Thus, it follows from equation \eqref{lpmtd1} that
+Thus, it follows from equation \eqref{eq:initial-values:OE:TD} that
 \begin{equation}
@@
 
-\subsection{Parametric Identification Algorithm}\label{se:paramIdentAlgo}
+\subsection{Parametric Identification Algorithm}\label{sec:initial-values:paramIdentAlgo}
 
@@
 
-\section{Methodology}\label{se:MethodEg}
+\section{Methodology}\label{sec:initial-values:MethodEg}
 In this section, the considered methods for obtaining the initial estimates of $\theta$ are briefly explained.
@@
 %\end{itemize}
-%\section{Example}\label{se:Example}
+%\section{Example}\label{sec:initial-values:Example}
 
@@
  which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
-The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{se:CompuSR}.
+The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{sec:initial-values:CompuSR}.
 
@@
 
-\section{Demonstration}\label{se:Demo}
+\section{Demonstration}\label{sec:initial-values:Demo}
 
@@
 %\subsection{Computing the success rates}
-\subsection{Computation of  the Success Rates}\label{se:CompuSR}
+\subsection{Computation of  the Success Rates}\label{sec:initial-values:CompuSR}
 
@@
 \section{Experimental Results}
-\label{se:ExpMeas}
+\label{sec:initial-values:ExpMeas}
 Measurements were performed on an electrical filter to assess the performance of the initial value generating methods in a physical setting.
@@
 \section{Remark on the generality}
-\label{se:Generality}
+\label{sec:initial-values:Generality}
 In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
@@
 
-To measure the timing of the different methods, essentially the same settings were used as in \secref{se:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $N_{3\unit{dB}} \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
+To measure the timing of the different methods, essentially the same settings were used as in \secref{sec:initial-values:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $N_{3\unit{dB}} \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
 For each of the branches in \figref{fig:flowgraph}, three different timings are recorded (when applicable):
@@
 
-\section{Conclusion}\label{se:Conclusion}
+\section{Conclusion}\label{sec:initial-values:Conclusion}
 The simulations have demonstrated that use of a smoothed non-parametric estimate of the \gls{FRF} can improve the success rate of minimizing the \gls{ML} cost function for the estimation of the transfer functions of \gls{LTI} systems, subjected to noisy signals.

### 2016-03-28 config/styles.inc.tex
Grid behind plots, axis+tick on top

@@
 \pgfplotsset{compat=newest}
+
+% http://tex.stackexchange.com/questions/287975/pgfplots-layer-issue
+\pgfplotsset{
+/pgfplots/layers/mylayer/.define layer set=
+{axis background,axis grid,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
+{/pgfplots/layers/standard}
+}
+\pgfplotsset{/dummy/workaround/.style={/pgfplots/axis on top}}
 
@@
 \pgfplotsset{every axis title/.append style={at={(0.5,1.025)}}}
+\pgfplotsset{every axis/.append style={set layers=mylayer, /dummy/workaround}}
 \pgfplotsset{every axis post/.style={unbounded coords=jump, line join=round}}
@@
 \pgfplotsset{frf/.style={color=black,solid,line width=1pt}}
-\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,area legend}}
+\pgfplotsset{bw/.style={fill=bwfill,draw=bwline,opacity=0.75,area legend}}
 \pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}

### 2016-03-28 code/batchTsvSimplify.m
Add mass-processing tools
Add some batch processing tools at top level for TSV files

@@ -1,0 +1,14 @@
+close all;
+clear variables;
+clc;
+
+files     = dir('*.tsv');
+filenames = arrayfun(@(d) d.name, files, 'UniformOutput', false);
+doSave    = false;
+
+for iFile = 1:numel(filenames);
+    file = filenames{iFile};
+    
+    simplifyTsv(file, doSave);
+end
+

### 2016-03-28 code/simplifyTsv.m

@@ -1,0 +1,80 @@
+function new = simplifyTsv(filename, doSave, cleanfigureArgs)
+    % SIMPLIFYTSV
+    
+    %% default arguments
+    if ~exist('doSave','var') || isempty(doSave)
+        doSave = nargout > 0;  % only save valid data by default
+    end
+    if ~exist('plotOptions','var') || isempty(plotOptions)
+        plotOptions = {'LineWidth', 1.5};
+    end
+    if ~exist('cleanfigureArgs', 'var') || isempty(cleanfigureArgs)
+        cleanfigureArgs = {};
+    end
+    
+    styleBefore = {'LineStyle', '-', 'DisplayName', 'Before'};
+    styleAfter  = {'LineStyle', '--', 'DisplayName', 'After'};
+    
+    
+    %% load file
+    [old] = loadFile(filename);
+    
+    %% show data 
+    hFig = figure('name',filename);
+    hData = plot(old.X, old.Y, styleAfter{:}, plotOptions{:});
+    
+    %% simplify data: clean last figure
+    cleanfigure('handle',hFig, cleanfigureArgs{:});
+    drawnow;
+    
+    %% extract data again from plot
+    new = struct();
+    new.old = old;
+    new.X = get(hData, 'XData');
+    new.Y = get(hData, 'YData');
+    new.nPoints = numel(new.X);
+    
+    %% plot old data again
+    hold all;
+    hOld = plot(old.X, old.Y, styleBefore{:}, plotOptions{:});
+    
+    message = sprintf('%d -> %d points (%02g%% compression)', ...
+                      nPoints(old), nPoints(new), ...
+                      (nPoints(new)/nPoints(old))*100);
+    disp([filename ' :  ' message]);
+    title(gca, message);
+    
+    uistack(hOld,'bottom');
+    legend('show','Location','Best');
+    
+    %% write out data to file
+    if doSave
+        data = [new.X(:), new.Y(:)];
+        fid = fopen(filename, 'w');
+        closeFileAfterwards = onCleanup(@() fclose(fid));
+        
+        FF     = '%g';
+        COLSEP = '\t';
+        ROWSEP = '\n';
+        fprintf(fid, [FF COLSEP FF ROWSEP], data(:));
+    end
+    
+end
+
+function N = nPoints(data)
+    N = numel(data.X);
+end
+
+function [data]  = loadFile(filename)
+    data = importdata(filename);
+    data = struct('data', data);
[…]

### 2016-03-28 code/batchTsvSimplify.m
Fix some bugs in simplifyTSV

@@ -1,14 +1,20 @@
+% This script iterates over all TSV files in the current directory
+% and uses `simplifyTsv` to reduce their size.
+%
 close all;
 clear variables;
 clc;
 
-files     = dir('*.tsv');
-filenames = arrayfun(@(d) d.name, files, 'UniformOutput', false);
-doSave    = false;
+file     = dir('*.tsv');
+doSave   = true;
+oneByOne = true;
 
-for iFile = 1:numel(filenames);
-    file = filenames{iFile};
+for iFile = 1:numel(file);
+    simplifyTsv(file(iFile).name, doSave);
     
-    simplifyTsv(file, doSave);
+    if oneByOne
+        pause(1);
+        close(gcf)
+    end
 end
 

### 2016-03-28 code/simplifyTsv.m

@@ -1,5 +1,23 @@
 function new = simplifyTsv(filename, doSave, cleanfigureArgs)
-    % SIMPLIFYTSV
+    % SIMPLIFYTSV simplifies TSV files using CLEANFIGURE
+    %
+    % This function uses the `cleanfigure` function from `matlab2tikz` to
+    % simplify the data contained in a TSV file. 
+    %
+    % Usage:
+    %  newData = SIMPLIFYTSV(filename, doSave, cleanfigureArgs)
+    %
+    % Arguments:
+    %  - filename: filename of TSV file to read (and write to)
+    %  - doSave: save the data back into the same file
+    %    (default value: false when "newData" is returned, true otherwise)
+    %  - cleanFigureArgs: extra arguments that are passed to `cleanfigure`
+    %    (default: {})
+    %
+    % Outputs:
+    %  - newData: structure containing the old and new data
+    %
+    % See also: matlab2tikz, cleanfigure
     
     %% default arguments
     if ~exist('doSave','var') || isempty(doSave)
@@ -56,7 +74,7 @@ function new = simplifyTsv(filename, doSave, cleanfigureArgs)
         FF     = '%g';
         COLSEP = '\t';
         ROWSEP = '\n';
-        fprintf(fid, [FF COLSEP FF ROWSEP], data(:));
+        fprintf(fid, [FF COLSEP FF ROWSEP], data.');
     end
     
 end

### 2016-03-29 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
More LPM-trunc figures
More uniform image styles
Improve bibliography
LPM illustration improved
Fix a lot of figures

@@
 \researchBasedOn[This section]{Lumori2014TIM}
-\TODO{figures to TikZ}
 \TODO{labels into standardized form}
@@
    \centering
-   \includegraphics[scale=0.92]{\thisDir/figs/spectUOmegak}
-   \includegraphics[scale=0.92]{\thisDir/figs/spectYOmegak}
-   \includegraphics{\thisDir/figs/LPMfigOmegak}
-   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}.
-Top figures: input spectrum (left) and output spectrum (right).
-A small band is selected (gray area, top figure), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
+   \setlength{\figurewidth}{0.8\columnwidth}
+   \setlength{\figureheight}{0.68\figurewidth}
+
+   \input{\thisDir/figs/LPMfig.tikz}
+   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
+   A small band is selected (gray area), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
 Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all $\Omega_k$.}
+This procedure is repeated for all frequencies $\Omega_k$.}
    \label{LPM_Schematic_EG}
@@
 \figref{figLPMvsTrunc} and \figref{fig:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
+Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
 They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{se:LPMFRFest}:
@@
 
-\begin{figure}[tbh] %top bottom here
+\begin{figure}
     \centering
@@
     \input{\thisDir/figs/figLPMvsTrunc.tikz}
-
-    \includegraphics[scale=0.9]{\thisDir/figs/figLPMvsTruncWlegend}
-    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{Comparison of the \gls{LPM} and Truncated \gls{LPM} estimates of the \gls{FRF} for an \gls{SNR} of $18.3\unit{dB}$.
-The gray plots pertain to the \gls{LPM} estimate without truncation, the black ones to the \gls{LPM} with truncation (trunc).
-Dots: \gls{FRF} estimates $\hat{G}$.
-Crosses: sample standard deviations $\hat{\sigma}$.
-Dashed lines: bias $\hat{b}$.
-White line: the true system $G_0$.}
+    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{The bias $\sampleBias{\placeholder}$ and standard deviation $\sampleStd{\placeholder}$ of the \gls{FRF} estimates using both the \gls{LPM} (blue) and truncated~\gls{LPM} (red) are shown.
+    It can be seen that the truncation reduces the variance at the cost of an increased bias, however, the overall \gls{RMS} error is reduced by the truncation.}
     \label{figLPMvsTrunc}
@@
 \begin{itemize}
-\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$,  i.e.
-a decrease of the black crosses, compared to the gray ones, is observed.
+\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.
 %i.e.
@@
 
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
+         \caption{RMSE vs $\truncTime$ for boxcar}
+\end{figure}
+
 \TODO{RMSE vs $\truncTime$ for boxcar figure}

### 2016-03-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
[xy]shift -> coordinate calculations
[xy]shift is not really compatible with some TikZ workarounds,
specifically the one from Cristian Feuersanger to have proper grid/tick
layering (plots were somewhat outside of the bounding box)

@@
-% \begin{abstract}
-% A statistical impulse response truncation technique is applied to the local-polynomial-method-estimate of the frequency response function, resulting in an improved, smooth frequency response function.
-Formulated as a nonparametric linear-least-squares-estimate, the local polynomial method is first applied to estimate the frequency response function from a full data record of a single-input-single-output system, systematically expressed in an output-error framework.
-The smooth characteristics of both the exact frequency response function and the leakage from transients allow for an optimal application of the local polynomial method, leading to the elimination of both the leakage and interpolation errors.
-The truncation method introduced in this section makes it possible for the user to fine-tune the trade-off between the uncertainty (variance) and the bias on the estimated instantaneous frequency response function.
-% \end{abstract}
-
 \researchBasedOn[This section]{Lumori2014TIM}
@@
 
-The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the LPM.
+The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}.
 This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
-The cutoff index (truncation point) is determined by a statistically sound method.
-It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.
+The truncation point (cut-off index) is determined by one of two statistically inspired methods.
+It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.
 
-Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A \gls{SISO} \gls{LTI} system is considered.
+Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
+A \gls{SISO} \gls{LTI} system is considered.
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
@@
 \setlength\figureheight{0.68\figurewidth}
-% \includegraphics[scale=0.9]{\thisDir/figs/expFitest}
 \input{\thisDir/figs/expfit.tikz}

### 2016-03-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some more uniformity in figure + text

@@
 
-The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.
-\gls{FRF} measurement techniques are discussed, for instance, in
-\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
-This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.
-
 This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
-The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e.
-no user interaction.
-Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}.
+The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
+Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}.
 Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
@@
   \end{align}
-  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
+  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
   The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
@@
 
-  \item This procedure is repeated until a segment $\segm{\hat{g}}{i-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
-  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{i-1}$.
-  One now has the choice to accept the last sample of $\segm{\hat{g}}{i-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
+  \item This procedure is repeated until a segment $\segm{\hat{g}}{\starred{i}-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
+  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{\starred{i}-1}$.
+  One now has the choice to accept the last sample of $\segm{\hat{g}}{\starred{i}-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
   The accuracy of this estimate is limited by the length of the segment $L_S$.
@@
   \item
-  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{i-1}$ -- which may contain both the signal and noise -- yet again into smaller segments.
+  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{\starred{i}-1}$ -- which may contain both the signal and noise -- yet again into smaller segments.
   The procedure described above is then repeated until a satisfactory, accurate $\truncTime$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values.
 %rely on the RMS values to be accurate.
-  To start this refinement, the last $\segm{\hat{g}}{i}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{i-1}$ cannot be asserted to be dominated by noise.
+  To start this refinement, the last $\segm{\hat{g}}{\starred{i}}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{\starred{i}-1}$ cannot be asserted to be dominated by noise.
 
@@
 The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions.
-The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.
-%after which all samples are fixed to a zero value for the smoothed estimate.
+The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.
 
@@
 \item
-Determine the first time-instant $t_\mathrm{trunc}$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
+Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
 \begin{align}\label{eq:truncTimeExpFit}
-t_\mathrm{trunc} = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
+\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
 \end{align}
@@
 \item
- Truncate the estimated impulse response for $t \geqslant t_\mathrm{trunc}$.
+ Truncate the estimated impulse response for $t \geqslant \truncTime$.
 
@@
 \input{\thisDir/figs/expfit.tikz}
-\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response via the fit of  an exponential. 
-The light gray line is the noisy impulse response, and the dark gray one is its absolute value. 
-Gray circles: monotonously decreasing maxima, greater than $5\hat\sigma$, as per \eqref{eq:TmaxDef}. 
-Black thick line: estimated exponential function \eqref{eq:expFit}.}
-\TODO{describe marker again!}
-\label{FRF_truncate_expfitter}
+\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
+\label{fig:nonparametric:trunc:impresp:expfit}
 \end{figure}
@@
 The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
-The result is depicted in \figref{FRF_truncate_expfitter}.
+The result is depicted in \figref{fig:nonparametric:trunc:impresp:expfit}. 
 An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $t_\mathrm{trunc}$ was selected as the time instant at which the fitted exponential fell below $0.4\hat\sigma_n$ (i.e.
+The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e.
 $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
@@
 
-In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $t_\mathrm{trunc}$ at which the impulse response is truncated.
-Its minimum is indicated by a black dot, to the left of which a steep increase is observed.
-This is due to a bias error. 
-To the right hand side of the minimum, the \gls{RMS} error increases very gradually, due to an increase of the noise variance.
+In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $\truncTime$ at which the impulse response is truncated.
+To the left of the optimal truncation length, the \gls{RMS} error increases steeply.
+In that region, one is essentially using a overly simplified impulse response to represent the system and hence the \gls{RMS} error is dominated by the bias error.
+To the right hand side of the minimum, the \gls{RMS} error increases more gradually, due to an increase of the noise variance.
 
@@
 This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
-Clearly, both methoda for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of its distribution (around the $90^{\text{th}}$ sample).
+Clearly, both methods for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of their distribution (around the $90^{\text{th}}$ sample).
 
@@
 The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied.
-Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$t_\mathrm{trunc}$, when truncating at times beyond that optimum.
+Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$\truncTime$, when truncating at times beyond that optimum.
 Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
@@
 
+The different methods to determine $\truncTime$ presented in this section, essentially enforce different prior knowledge of the impulse response of the system.
+The exponential fitting technique relies on the exponential decay present in most physical systems.
+The $F$-test based technique is better suited for systems where a sudden jump in the impulse response is present.
+
 The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the \gls{FRF}, resulting in a decreased variance. 
@@
         \input{\thisDir/figs/expFitBoxAverager.tikz}
-         \caption{Exponential fit of a boxcar averager}
+         \caption{Exponential fit of the impulse response of a  boxcar averager.}
 \end{figure}

### 2016-03-30 ch03-lrm/lrm-paper.tex
Fix mathbold stuff
Some small things
Some more uniformity in figure + text

@@
 
-\TODO{
 \begin{itemize}
-    \item choice $s$ or $z$
-    \item bounds RMSE, Bias, StdDev
-    \item derivation Bias
-    \item comparison LPM/LRM
+    \item \TODO{choice $s$ or $z$}
+    \item \TODO{bounds RMSE, Bias, StdDev}
+    \item \TODO{derivation Bias}
+    \item \TODO{comparison LPM/LRM}
       \begin{itemize}
-        \item Good LPM window
-        \item Good LRM window
+        \item \TODO{Good LPM window}
+        \item \TODO{Good LRM window}
       \end{itemize}
-    \item influence of noise filter: mismatch with model
-    \item comparison LRM/LRik (LBTLS)
+    \item \TODO{influence of noise filter: mismatch with model}
+    \item \TODO{comparison LRM/LRik (LBTLS)}
 \end{itemize}
-}
 
@@
 Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:design-matrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
-To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G,eq:LRM:model:T}
+To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
 \begin{equation}
@@
   \ELSCost{\theta} = \ELSCost{\true\theta} 
-  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right)\\
+  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right) %\\
   + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
@@
 \end{equation}
-where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\hat{Y}}}$, i.e.
+where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e.
 the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.

### 2016-03-30 ch03-lrm/nonparametric.tex
Remove epigraph from Milgram
Address some TODOs
Different figure names per chapter
Import LRM-paper draft
Some small things
Some more uniformity in figure + text

@@
 \def\thisDir{ch03-lrm}
+\tikzsetfigurename{ch03fig}
 \label{sec:nonparametric}
 
-\myEpigraph{The essence in obedience consists in the fact that a person comes to view himself as an instrument for carrying out another person's wishes and he therefore no longer regards himself as responsible for his actions.}{Stanley Milgram}{Obedience to Authority}
+\section{Introduction}
+\label{sec:nonparametric:introduction}
+
+Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received new research interest from the community.
+
+\begin{itemize}
+\item \TODO{explain non-parametric}
+\item \TODO{explain why non-parametric is good}
+\end{itemize}
+
+The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
+\gls{FRF} measurement techniques are discussed, for instance, in
+\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
+Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
+This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.
 
@@
 \section{\TODO{LRM}}
-\TODO{import LRM paper}
-\section{\TODO{LPM with impulse response truncation}}
+\input{\thisDir/lrm-paper.tex}
+
+\section{LPM with impulse response truncation}
 \input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}
@@
 \subsubsection{\TODO{AVIS}}
-\subsubsection{\TODO{F16}}
+% \subsubsection{\TODO{F16}}

### 2016-03-30 ch05-initvals/initial-values.tex
Some more uniformity in figure + text

@@
 
-\item \emph{Quadratic approximations of the ML}
+\item \emph{Quadratic approximations of the \gls{MLE}}
 
@@
 
-A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014TIM}.
-Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}.
-The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.
+A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
+Here, we repeat the main points briefly.
+The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
+The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient and noise suppressed.
 
@@
 
-%The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586$~Hz is illustrated in Fig. \ref{LPM_Schematic_EG}.
-
 \emph{Impulse response truncation}. 
-%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
-The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM}.
-%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.
-
-The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.,
+The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.
+
+The impulse response is truncated after the time $\truncTime$ where the signal becomes indistinguishable from the noise, i.e.,
 \begin{equation}
@@
   \begin{cases}
-    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
-    0                    & t \geq \tau_{\mathrm{trunc}}
+    g_{\text{poly}}(t) & t \leq \truncTime \\
+    0                              & t \geq \truncTime
   \end{cases}
@@
 \end{equation}
-To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
-Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
-\begin{equation}
-  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
+
+To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
+Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
+\begin{equation}
+  \truncTime = \min \Set{ t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g  }
   = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
@@
 where $\gamma=1$ was used in this chapter for simplicity.
-By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
+By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
 This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
@@
 
-%\JL{
 The \gls{RFIR} estimator is formulated in the time domain. 

### 2016-03-30 config/styles.inc.tex
Some more uniformity in figure + text

@@
 %% Truncation
-\pgfplotsset{truncationline/.style={dashdotdotted,line width=1.5pt,line join=round,line cap=round}}
-
 \colorlet{FSmooth}{TangoScarletRed3}
@@
 }}
+% adapted from line legend
+\pgfplotsset{verticalLineLegend/.style={
+  legend image code/.code={
+    \draw[mark repeat=2,mark phase=2,##1]
+      plot coordinates {
+         (0.3cm, 0cm)
+         (0.3cm, 0.25em)
+         (0.3cm, 0.5em)
+      };%
+  }
+}}
+
+\colorlet{impulseResponseFull}{TangoScarletRed1!50!white}
+\colorlet{impulseResponseAbs}{TangoChameleon1}
+\colorlet{impulseResponseTruncated}{TangoChameleon3}
+\colorlet{impulseResponsePeaks}{TangoScarletRed3}
+
+\pgfplotsset{imprespFull/.style={color=impulseResponseFull,solid}}
+\pgfplotsset{imprespAbs/.style={color=impulseResponseAbs,solid}}
+\pgfplotsset{imprespExpFit/.style={color=expFit, solid, line width=1.5pt}}
+\pgfplotsset{imprespPeaks/.style={color=TangoScarletRed3,mark=*,only marks,line width=1.25pt,mark size=0.5pt}}
+\pgfplotsset{imprespTrunc/.style={color=impulseResponseTruncated,solid}}
+
+\pgfplotsset{imprespDetectLevel/.style={color=black,dashed}}
+\pgfplotsset{imprespNoiseLevel/.style={color=black,dashed}}
+
+\pgfplotsset{truncationline/.style={dashdotdotted,line width=1.5pt,line join=round,line cap=round, verticalLineLegend}}
 

### 2016-03-30 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Smoothen out Truncation text

@@
+\label{sec:nonparametric:truncation}
 \researchBasedOn[This section]{Lumori2014TIM}
@@
 
-\subsection{Introduction}
-
-This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
-The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
-Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}.
-Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
-Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
+% This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
+% The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
+% Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}.
+% Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
+% Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
 
@@
 
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q,\theta)$ and parametric noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
-
-In this section, however, a nonparametric technique is developed, and
-formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.
+Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
+In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.
 
@@
 \paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
+The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
 In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
-%This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:nparam:trunc:LPM:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
 Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
@@
 The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}.
-As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\mathcal{O}({N}^{-1})$, for Hanning windowing, to $\mathcal{O}({N}^{-3})$ or better, for the \gls{LPM}.
+As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\bigO{{N}^{-1}}$, for Hanning windowing, to $\bigO{{N}^{-3}}$ or better, for the \gls{LPM}.
 
@@
 
-\section{Smoothing the \gls{FRF} estimate}\label{se:smoothingFRFestimate}
+\section{Smoothing the \gls{FRF} estimate}
+\label{se:smoothingFRFestimate}
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
@@
 In particular, when $t > \truncTime$, the impulse response has decayed below the noise floor.
-In \secref{sec:nonparametric:truncation:Ftest} and \secref{sec:nonparametric:truncation:exponentialFit}, two approaches are introduced to estimate $\truncTime$.
+In \secref{sec:nonparametric:truncation:ftest} and \secref{sec:nonparametric:truncation:exponentialfit}, two approaches are introduced to estimate $\truncTime$.
 
@@
 \TODO{write about boxcar average, add reference}
+
+\begin{align}
+  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
+\end{align}
+
 \begin{figure}
@@
         \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
-         \caption{RMSE vs $\truncTime$ for boxcar}
+         \caption{RMSE vs $\truncTime$ for boxcar \TODO{better caption}}
 \end{figure}
-
-\TODO{RMSE vs $\truncTime$ for boxcar figure}

### 2016-03-31 ch04-lrmhinf/ch04appendices.inc.tex
Lots of work on LRMHinf + description of AVIS setup

\section{Measurement set-up}
The measurements of the \gls{AVIS} are carried from within \Simulink model as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
  \caption{Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
  \label{fig:avis:simulink:setup}
\end{figure}

In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a single mechanical degree-of-freedom of the \gls{AVIS}, in order:
\begin{itemize}
  \item the translation in $x$ direction (horizontal),
  \item the translation in $y$ direction (horizontal),
  \item the translation in $z$ direction (vertical),
  \item the rotation along the $x$ axis,
  \item the rotation along the $y$ axis,
  \item the rotation along the $z$ axis.
\end{itemize}
In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
However, inside the feedback loop, all directions are controlled by the experimental controller $\experimental\Controller$.

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function that is implemented as a discrete state-space model.
This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively.

\TODO{show bode plot of controller directions}

For multisine excitations the \code{RepeatingSequence} block was used to load the \code{r2} signal from \MATLAB, for noise excitations, the \code{RandomNumber} block of \Simulink was used instead.
The signals \code{r2}, \code{u} and \code{y} are returned from \Simulink to \MATLAB where further processing of the data is carried out.
This allows to compute the transfer function from \code{r2} to \code{u} and \code{y} respectively, or, the transfer function of the \gls{AVIS} block in the \Simulink model.

The \gls{AVIS} block (\figref{fig:avis:simulink:avis}), conceptually, contains:
\begin{itemize}
  \item a static decoupling $(K_{\mathrm{act}}, K_{\mathrm{sens}})$ of the physical \gls{AVIS} system, as derived in \citep{Rademakers2005MSc},
  \item logic to communicate with the Quanser Q8 \gls{DAQ} board which is physically connected to the \gls{AVIS}, and
  \item signal conditioning.
\end{itemize}

Specifically, the static decoupling of the \gls{AVIS} is given by the following gain matrices: \TODO{use pgfplotstable to add these matrices}
\begin{align}
  K_{\mathrm{act}}    &\approx \\
  K_{\mathrm{sens}} &\approx
\end{align}
Note that $K_{\mathrm{act}} \in \RR^{8\times6}$ and hence produces signals for the $8$ actuators on the \gls{AVIS}.
These signals are limited to the range $\pm 5\unit{V}$ before they are sent to the \glspl{DAC} on the Q8 \gls{DAQ} board to avoid overdriving the \glspl{DAC}.

The $6$ velocity signals that are read from the Q8 \gls{DAQ} are each filtered to \TODO{filtered such that what?} using a filter  $F$ with transfer function
\begin{equation}
  F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
  \text{.}
\end{equation}
This filter is discretized automatically by \Simulink for the actual implementation, which obviously happens in discrete time.
\TODO{show bode plot of $F$}
The output \code{y} is clipped to $\pm 20$ for easier detection of errors.
However, during normal operation and all the measurements, the signal levels were well within the linear region of this saturation block.

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{Simulink model of the AVIS sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

### 2016-03-31 ch04-lrmhinf/ch04appendices.inc.tex
Some cleanup

@@
 with $\Identity{n}$ the $n\times n$ identify matrix.
-It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively.
+It can be seen that the controller is diagonal, i.e.
+the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively as shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
 
+\begin{figure}
 \TODO{show bode plot of controller directions}
+\caption{Bode plots of the $\experimental\Controller$ and sensor filter $F$.}
+\label{fig:avis:bodeplots:controllerAndSensor}
+\end{figure}
 
@@
   F(s) \approx \input{\thisDir/data/avis-setup/sensor-filter.inc.tex}
-  \text{.}
 \end{equation}
-This filter is discretized automatically by \Simulink for the actual implementation, which obviously happens in discrete time.
-\TODO{show bode plot of $F$}
+which is shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
+This filter is discretized automatically by \Simulink for the actual implementation, which happens in discrete time.
+
 The output \code{y} is clipped to $\pm 20$ for easier detection of errors.

### 2016-04-01 ch04-lrmhinf/ch04appendices.inc.tex
More info about AVIS

@@
-\section{Measurement set-up}
-The measurements of the \gls{AVIS} are carried from within \Simulink model as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.
+\section{\glsentrytext{AVIS} Measurement set-up}
+The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.
 
@@
 
-In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a single mechanical degree-of-freedom of the \gls{AVIS}, in order:
-\begin{itemize}
-  \item the translation in $x$ direction (horizontal),
-  \item the translation in $y$ direction (horizontal),
-  \item the translation in $z$ direction (vertical),
-  \item the rotation along the $x$ axis,
-  \item the rotation along the $y$ axis,
-  \item the rotation along the $z$ axis.
-\end{itemize}
+In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a mechanical degree-of-freedom of the \gls{AVIS}, i.e.
+\begin{enumerate}
+  \item the translational velocity in $x$ direction (horizontal),
+  \item the translational velocity in $y$ direction (horizontal),
+  \item the translational velocity in $z$ direction (vertical),
+  \item the rotational velocity around the $x$ axis,
+  \item the rotational velocity around the $y$ axis,
+  \item the rotational velocity around the $z$ axis.
+\end{enumerate}
 In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
@@
 It can be seen that the controller is diagonal, i.e.
-the directions are decoupled, and that the dynamics are shared among the translational directions and the rotational direction respectively as shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
+the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
+\begin{equation}
+  \experimental\Controller = 
+  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
+\end{equation}
+with
+\begin{align}
+\experimental\Controller_{\mathrm{tran}} &  \approx 
+   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
+  \experimental\Controller_{\mathrm{rot}} & \approx 
+    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
+\end{align}
+ as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.
 
 \begin{figure}
-\TODO{show bode plot of controller directions}
-\caption{Bode plots of the $\experimental\Controller$ and sensor filter $F$.}
+\setlength\figurewidth{0.75\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/avis-setup-filters.tikz}
+\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
 \label{fig:avis:bodeplots:controllerAndSensor}
@@
 \begin{itemize}
-  \item a static decoupling $(K_{\mathrm{act}}, K_{\mathrm{sens}})$ of the physical \gls{AVIS} system, as derived in \citep{Rademakers2005MSc},
+  \item static transformations $(K_{\mathrm{act}}, K_{\mathrm{sens}})$, as derived from first principles in \citep{Rademakers2005MSc}, which translates the sensor and actuator signals to physical velocities at the center of the payload,
   \item logic to communicate with the Quanser Q8 \gls{DAQ} board which is physically connected to the \gls{AVIS}, and
@@
 
-Specifically, the static decoupling of the \gls{AVIS} is given by the following gain matrices: \TODO{use pgfplotstable to add these matrices}
+Specifically, the static transformations of the \gls{AVIS} are given by the following gain matrices~\citep[Appendix A.4]{Rademakers2005MSc}:
 \begin{align}
-  K_{\mathrm{act}}    &\approx \\
-  K_{\mathrm{sens}} &\approx
+  K_{\mathrm{act}}    & \approx \input{\thisDir/data/avis-setup/actuator-gains.tab.tex}\\
+  K_{\mathrm{sens}} & \approx \input{\thisDir/data/avis-setup/sensor-gains.tab.tex}
 \end{align}
@@
 
-The $6$ velocity signals that are read from the Q8 \gls{DAQ} are each filtered to \TODO{filtered such that what?} using a filter  $F$ with transfer function
+The $6$ velocity signals that are digitized by the Q8 \gls{DAQ} are each filtered to transform the voltage induced in the coils of the geophones on the \gls{AVIS} into a velocity using a filter $F$ with transfer function
 \begin{equation}
@@
 which is shown in \figref{fig:avis:bodeplots:controllerAndSensor}.
-This filter is discretized automatically by \Simulink for the actual implementation, which happens in discrete time.
+More information regarding this design is given in \citep[Appendix A.3]{Rademakers2005MSc}.
+This filter is discretized automatically by \Simulink for the actual implementation.
 

### 2016-04-01 ch04-lrmhinf/code/plotAvis.m

@@ -1,0 +1,78 @@
+% This file loads and displays the AVIS setup
+% from MAT file. Note, it is advised to use
+% the `avisSetup.m` file from `LPMHinf/Code/Measurement/avis`
+% (private repository) instead for:
+%  - backwards compatibility
+%  - better understanding of the variables
+
+close all;
+clear variables;
+clc;
+
+addpath(fullfile('..','..','code'));
+load(fullfile('..','data','avis-setup','avis.mat'));
+
+Cexp  = avis.controller;
+Crot  = tf(Cexp(6,6));
+Ctran = tf(Cexp(1,1));
+
+filterSensor = avis.sensor.filter.z_trans;
+F            = tf(filterSensor.Numerator, filterSensor.Denominator);
+
+[~,~,Ts] = tfdata(Cexp);
+fNyquist = 2*pi*1/Ts/2;
+nPoints  = 100;
+w = logspace(log10(0.001), log10(fNyquist), nPoints);
+
+%% static transformations
+Kact  = avis.actuator.polarity * avis.actuator.matrix;
+Ksens = avis.sensor.matrix * avis.sensor.polarity;
+tabOpts = {'floatFormat', ff, 'col', ' & ', 'row', '\\\\\n'};
+printMatrix(Kact, tabOpts{:} )
+printMatrix(Ksens, tabOpts{:} )
+%% plots
+figure('name','Bode plots AVIS setup');
+
+filters = {Ctran, Crot, F};
+names   = {'Translation', 'Rotation','F'};
+yfuns   = {@(y) db(y);
+           @(y) angle(y)};
+xfun    =  @(w) w/2/pi;
+ylabels = {'Amplitude [dB]', 'Phase [rad]'};
+xlabels = {'Frequency \omega [Hz]'};
+plotStyle = {'Color','k','LineWidth',1.5};
+
+nFilters = numel(filters);
+nPlots   = numel(yfuns);
+
+hAx = repmat(gca, nFilters, nPlots);
+for iFilter = 1:nFilters;
+    FRF = squeeze(freqresp(filters{iFilter},w));
+    for jPlot = 1:nPlots
+        yfun = yfuns{jPlot};
+        
+        idx = (jPlot-1)*nFilters + iFilter;
+        hAx(idx) = subplot(nPlots, nFilters, idx);
+        
+        plot(xfun(w), yfun(FRF), plotStyle{:});
[…]

### 2016-04-01 code/printMatrix.m

@@ -1,0 +1,44 @@
+function str = printMatrix(mat, varargin)
+    args = parseInputs(mat, varargin{:});
+    %% 
+    [nCols] = size(mat, 2);
+    fmt = makeFormat(nCols, args);
+    
+    str = sprintf(fmt, mat.');
+    
+    %% display output
+    if nargout == 0
+        disp(str);
+        clear str;
+    end
+end
+
+function fmt = makeFormat(nColumns, args)
+    builder              = cell(2,nColumns);
+    [builder{1,:}]       = deal(args.floatFormat);
+    [builder{2,1:end-1}] = deal(args.columnSeparator);
+    builder{2,end}       = args.rowSeparator;
+    
+    fmt = [builder{:}];
+end
+
+function args = parseInputs(varargin)
+    persistent ipp
+    if isempty(ipp)
+        ipp = inputParser();
+        ipp.FunctionName    = mfilename;
+        ipp.CaseSensitive   = false;
+        ipp.StructExpand    = true;
+        ipp.KeepUnmatched   = true;
+        ipp.PartialMatching = true;
+
+        ipp.addRequired('mat');
+        ipp.addParameter('floatFormat', '%15g');
+        ipp.addParameter('columnSeparator', '\t');
+        ipp.addParameter('rowSeparator', '\n');
+    end
+    
+    ipp.parse(varargin{:});
+    args = ipp.Results;
+end
+    

### 2016-04-01 ch04-lrmhinf/ch04appendices.inc.tex
Add Axes of AVIS

@@
 \end{enumerate}
+The axes are indicated in \figref{fig:avis:withAxes}.
+
+\begin{figure}
+  \centering
+  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
+  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors.
+For each of the actuators and sensors, the color indicates the principal direction}
+  \label{fig:avis:withAxes}
+\end{figure}
+
 In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).

### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Small changes

@@
   \includegraphics{\thisDir/figs/avis-with-axes.pdf}
-  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors.
-For each of the actuators and sensors, the color indicates the principal direction}
+  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
+For each of the actuators and sensors, the color indicates the principal direction.}
   \label{fig:avis:withAxes}
@@
 
-Specifically, $\experimental\Controller$ is a $6\times6$ transfer function that is implemented as a discrete state-space model.
+Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
 This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below

### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Lots of changes to CH04

@@
 \section{\glsentrytext{AVIS} Measurement set-up}
+\label{app:avis-setup}
 The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.
@@
 \begin{enumerate}
-  \item the translational velocity in $x$ direction (horizontal),
-  \item the translational velocity in $y$ direction (horizontal),
-  \item the translational velocity in $z$ direction (vertical),
-  \item the rotational velocity around the $x$ axis,
-  \item the rotational velocity around the $y$ axis,
-  \item the rotational velocity around the $z$ axis.
+  \item $v_x$: the velocity in $x$ direction (horizontal),
+  \item $v_y$: the velocity in $y$ direction (horizontal),
+  \item $v_z$: the velocity in $z$ direction (vertical),
+  \item $\phi_x$: the angular velocity around the $x$ axis,
+  \item $\phi_y$: the angular velocity around the $y$ axis,
+  \item $\phi_z$: the angular velocity around the $z$ axis.
 \end{enumerate}
-The axes are indicated in \figref{fig:avis:withAxes}.
+The coordinate frame and axes are indicated in \figref{fig:avis:withAxes}.
 
@@
 
-In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
+In the main text, we have simplified this system to consider only $v_z$, the vertical translation (i.e. the third signal).
 For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
@@
 Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
-This controller was present beforehand~\citep{Rademakers2005MSc,vanderMaas2011MSc} and is given by the state-space matrices below
+This controller was constructed by~\citet{Rademakers2005MSc}
+ and is given by the state-space matrices below
 \begin{align}
-  \experimental\Controller & \isdef \stateSpace{A}{B}{C}{D}\\
+  \experimental\Controller & \isdef 
+  \begin{cases}
+     x[n+1] &= A x[n] + B u_c\\
+       y_c    &= C x + D u_c 
+  \end{cases}\\
   A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
@@
 
-\begin{figure}
+\begin{figure}[p]
 \setlength\figurewidth{0.75\columnwidth}
@@
 
+\begin{figure}[p]
+\setlength\figurewidth{\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
+  \caption{Simulink model of the AVIS sub-block.}
+  \label{fig:avis:simulink:avis}
+\end{figure}
+
 The \gls{AVIS} block (\figref{fig:avis:simulink:avis}), conceptually, contains:
 \begin{itemize}
-  \item static transformations $(K_{\mathrm{act}}, K_{\mathrm{sens}})$, as derived from first principles in \citep{Rademakers2005MSc}, which translates the sensor and actuator signals to physical velocities at the center of the payload,
+  \item static transformations $(K_{\mathrm{act}}, K_{\mathrm{sens}})$, as derived from first principles in~\citep{Rademakers2005MSc}, which translates the sensor and actuator signals to physical velocities at the center of the payload,
   \item logic to communicate with the Quanser Q8 \gls{DAQ} board which is physically connected to the \gls{AVIS}, and
@@
 
-Specifically, the static transformations of the \gls{AVIS} are given by the following gain matrices~\citep[Appendix A.4]{Rademakers2005MSc}:
+In \citet[Appendix A.4]{Rademakers2005MSc}, linear static relationships are derived to link the velocities at the center of the payload to the corresponding actuator voltages.
+This yields the matrix:
 \begin{align}
   K_{\mathrm{act}}    & \approx \input{\thisDir/data/avis-setup/actuator-gains.tab.tex}\\
-  K_{\mathrm{sens}} & \approx \input{\thisDir/data/avis-setup/sensor-gains.tab.tex}
 \end{align}
@@
 This filter is discretized automatically by \Simulink for the actual implementation.
+These velocities are then linked by a linear transformation to the (angular) velocities
 
@@
 
-\begin{figure}
-\setlength\figurewidth{\columnwidth}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
-  \caption{Simulink model of the AVIS sub-block.}
-  \label{fig:avis:simulink:avis}
-\end{figure}
+\begin{remark}
+It should be noted that while the benchmark paper by \citet{Voorhoeve2015SYSID} deals with the same physical \gls{AVIS}, the experimental data of the benchmark is fundamentally different from the data presented here.
+\Citet{Voorhoeve2015SYSID} only consider the `physical' \gls{AVIS} with $8$ inputs and $6$ outputs as indicated by the \code{QuanserQ8} block in \figref{fig:avis:simulink:avis} as the system under test.
+The measurements of the benchmark data were carried out in open-loop.
+Hence, the experimental controller ($\experimental\Controller_{\mathrm{benchmark}} = 0$),the saturations, the filter $F$ and the static matrices $K$ are different.
+Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) thanks to an upgrade of the real-time computer responsible for acquiring the signals.
+\end{remark}

### 2016-04-03 ch04-lrmhinf/paper.tex
Fix a lot of figures
Some changes to CH04
Lots of work on LRMHinf + description of AVIS setup
Lots of changes to CH04

@@
   \begin{itemize}
-    \item \TODO{fix labels for chapter}
     \item \TODO{add section from Benchmark paper}
-    \item \TODO{fix some bib entries}
     \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
@@
 
-\section{Introduction}
-\label{sec:Intro}
+% \section{Introduction}
+% \label{sec:lrmhinf:Intro}
 
@@
 The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
-However, the performance of skyhook damping is limited by high-frequent parasitic resonance phenomena. 
+However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
 Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
@@
 Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
-The aim of the present paper is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
+The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
 The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} as introduced in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
 Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
-In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the peak value, as is required for the $\Hinf{}$ norm. 
-The performance of these local parametric models with respect to robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
-Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
-The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
+In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
+The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
+% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+% The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
 
-\vspace{-1em}
 \paragraph*{Outline}
-\label{par:toc}
-The problem is formulated in \secref{sec:Problem}.
-In \secref{sec:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
-In \secref{sec:simulation} the method is illustrated on simulations, and the required measurement time is determined.
-The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:measurement}.
-Finally, the results and some challenges are discussed in \secref{sec:conclusion}.
+\label{par:lrmhinf:toc}
+The problem is formulated in \secref{sec:lrmhinf:Problem}.
+In \secref{sec:lrmhinf:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
+In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
+The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:lrmhinf:measurement}.
+Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.
 
-\glsresetall % reset the usage of all abbreviations s.t. intro and body get the explanation at first use
+%\glsresetall
 
 \section{Problem Formulation}
-\label{sec:Problem}
+\label{sec:lrmhinf:Problem}
 Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
 After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
-The \Hinf{} norm of the error system $\Delta$, i.e.
+The \Hinf{} norm of the error system $\Delta$ is
 \begin{equation}
@@
        \sup_{\omega} 
-         \abs{\Delta(\omega)}
-  \label{eq:HinfNormSISO}
+         \svdMax{\Delta(\omega)}
+  \label{eq:lrmhinf:HinfNorm}
 \end{equation}
-for a stable \gls{SISO} system, or its weighted form $\infnorm{W \Delta V}$, is a measure that serves an important purpose in many robust control design methodologies that specifies the `size' of the model class for which a controller is to be designed~\citep{Skogestad2005}.
+for a stable system where $\svdMax{\placeholder}$ denotes the maximum singular value of $\placeholder$.
+Note that for \gls{SISO} systems, $\svdMax{\Delta} = \abs{\Delta}$ and the definition above reduces to
+\begin{equation}
+  \gamma = \infnorm{\Delta} \isdef \sup_{\omega} \abs{\Delta(\omega)} \text{ for \gls{SISO} systems}
+  \text{.}
+  \label{eq:lrmhinf:HinfNormSISO}
+\end{equation}
+In robust control design methodologies, such \Hinf{} norms often play an important purpose to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.
+
+\begin{remark}
+It is even more common to use a weighted norm, e.g.  $\infnorm{W \Delta V}$ in robust control designs for some weighting filters $(W,V)$ that are stable and minimum-phase.
+Two cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters.
+In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e.
+by replacing $\svdMax{\Delta}$ with $\svdMax{W \Delta V}$ in the formulas.
+The other case is discussed in Remark~\ref{rem:lrmhinf:constructWeights} further on.
+\end{remark}
 
@@
   \text{.}
-  \label{eq:omega-star}
+  \label{eq:lrmhinf:omega-star}
 $
 However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
-As such, \eqref{eq:HinfNormSISO} can be rewritten as
+As such, \eqref{eq:lrmhinf:HinfNormSISO} can be rewritten as
 \begin{equation}
@@
                 \sup_{\omega \in \InterGrid} \abs{\Delta(\omega)}}{\gamma_{\mathrm{IG}}}}
-  \label{eq:gamma-split-grid}
+  \label{eq:lrmhinf:gamma-split-grid}
 \end{equation}
-where $\Omega \isdef \OpenInterval{0}{\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
+where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
 Two cases can be distinguished:
@@
 
-The main contribution of this paper is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
+The main contribution of this chapter is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
 Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
@@
       + H(q)e(n)
-  \label{eq:sysDeltaInfData}
+  \label{eq:lrmhinf:sysDeltaInfData}
 \end{equation}
@@
     \text{.}
-    \label{eq:sysDeltaFiniteData}
+    \label{eq:lrmhinf:sysDeltaFiniteData}
 \end{equation}
@@
          \forall k \in \mathbb{Z}
-  \label{eq:DFT}
+  \label{eq:lrmhinf:DFT}
 \end{equation} 
-to both sides of~\eqref{eq:sysDeltaFiniteData}, one obtains:
+to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
 \begin{equation}
@@
   \text{.}
-  \label{eq:sysDeltaFiniteDataFD}
+  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
 \end{equation}
@@
 
-The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:control}.
+The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:lrmhinf:control}.
 The results in this paper are presented in discrete time, but the extension to the continuous time case is straightforward.
@@
 \section{\Hinf{} Norm Estimation Procedure}
-\label{sec:LPMHinf}
+\label{sec:lrmhinf:LPMHinf}
 To estimate $\gamma_{\mathrm{IG}}$, we propose to identify local parametric models in the frequency domain.
@@
   \gamma_{\mathrm{IG}} = 
-    \sup \set{ \left. 
+    \sup \Set{ 
                 \sup_{\omega \in \Omega_k} \abs{\LocalModel{\Delta}_k(\omega)}
-                \right|
+                |
                 k = 1,\ldots,N-1
                 }
-   \label{eq:gamma-inter-grid}
+   \label{eq:lrmhinf:gamma-inter-grid}
 \end{equation}
 where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k$th) frequency $\omega_k$.
-An example of such local models is shown in \figref{fig:interpol-quantities}.
-Two alternative methods allow evaluation of~\eqref{eq:gamma-inter-grid} in practice.
+An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
+Two alternative methods allow evaluation of~\eqref{eq:lrmhinf:gamma-inter-grid} in practice.
 
@@
   The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
-\label{fig:interpol-quantities}
+\label{fig:lrmhinf:interpol-quantities}
 \end{figure}
 
-\vspace{-3em}
 \paragraph*{Direct method}
 % \subsubsection{Direct method}
-One can implement the definition~\eqref{eq:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
+One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
 Hence, it boils down to solving the optimization problems
 \begin{equation}
+  \estimated {\gammaIntergrid} = 
   % \gamma_{\mathrm{IG}}(k) 
@@
       \abs{\LocalModel{\Delta}_k(\omega)}
-      \label{eq:gamma-direct}
+      \label{eq:lrmhinf:gamma-direct}
 \end{equation}
@@
 
-\vspace{-2em}
 \paragraph*{Interpolation method}
-To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
+To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
 It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\abs{\omega_k-\omega}$ is small.
@@
   \text{.}
-  \label{eq:kL-kR-indexing-functions}
+  \label{eq:lrmhinf:kL-kR-indexing-functions}
 \end{align}
-Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
+Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained:lrmhinf: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
 In view of obtaining the maximum amplitude, these are `interpolated' to obtain a single estimate:
 \begin{equation}
-  \abs{\Delta_{\mathrm{LRM}}(\omega)}
+  \abs{\Delta_{\LMM}(\omega)}
     \isdef
@@
     }
-    \label{eq:DeltaLRMInterpolation}
+    \label{eq:lrmhinf:DeltaLRMInterpolation}
 \end{equation}
@@
 \begin{align}
-  \widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty} 
+  \widehat{\infnorm{\Delta_{\LMM}}}
     & \isdef
     \sup_{\omega\in\Omega}
-    \abs{\Delta_{\mathrm{LRM}}(\omega)} \\
+    \abs{\Delta_{\LMM}(\omega)} \\
    &  =
@@
                  \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
-  \label{eq:gammaInterpolOptim}
+  \label{eq:lrmhinf:gammaInterpolOptim}
   \text{.}
@@
 
-\vspace{-2em}
 \paragraph*{Remarks:}
-The optimization problems~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} can, e.g. be solved by griding the frequency $\omega$.
-The peak amplitudes obtained using~\eqref{eq:gammaInterpolOptim} and~\eqref{eq:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
+The optimization problems~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct} can, e.g. be solved by griding the frequency $\omega$.
+The peak amplitudes obtained using~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
 $% \begin{equation}
@@
 for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
-In \figref{fig:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
+In \figref{fig:lrmhinf:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
 
 \subsection{The \glsentrydesc{LRM}}
-\label{sec:LRM}
+\label{sec:lrmhinf:LRM}
 The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
-The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:sysDeltaFiniteDataFD} are smooth functions of the frequency.
+The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
 As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
@@
         \LocalModel{\Delta}_{k}(\omega_{k+r})
-      \label{eq:LRMTaylorSystem} \\
+      \label{eq:lrmhinf:LRMTaylorSystem} \\
   T_{\Delta}(\omega_{k+r}) 
@@
         \LocalModel{T}_{k}(\omega_{k+r})
-  \label{eq:LRMTaylorTransient}
+  \label{eq:lrmhinf:LRMTaylorTransient}
   \text{.}
 \end{align}
-Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
+Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
 This yields
@@
     \text{.}
-    \label{eq:LocalWindowSpectra}
+    \label{eq:lrmhinf:LocalWindowSpectra}
 \end{equation}
@@
     \text{.}
-    \label{eq:LocalWindowSpectraLRM}
+    \label{eq:lrmhinf:LocalWindowSpectraLRM}
 \end{align}
@@
   \right|^2
-  \label{eq:localCostLRM}
+  \label{eq:lrmhinf:localCostLRM}
 \end{equation}
@@
 \section{Simulation}
-\label{sec:simulation}
+\label{sec:lrmhinf:simulation}
 To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
 The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
-Any real-rational system $\Delta$ can be decomposed in a parallel structure of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE} and using the same logic as in \chapref{sec:excitation}.
+Concretely, any proper real-rational system $\Delta$ can be decomposed in a parallel connection of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE}.
+For clarity, we repeat the expression here again:
+It is well-known in the mechanical engineering community (see e.g. \citet{Gawronski2004}), that around re
+ and using the same logic as in \chapref{sec:excitation}.
 As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
 mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
-To estimate $\norm{\Delta}$ mainly the resonant sub-systems are of interest.
+To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest.
 Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
@@
 By normalizing the conclusions for the time constant $\timeconst$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\damping$.
-Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the undamped natural frequency.
+Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the natural frequency of the dominant pole.
 
 \subsection{A concrete simulation}
-Consider a discrete time system $\Delta$ (see \figref{fig:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
+Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
 \begin{equation}
@@
             {z^2 - 1.0595 z + 0.96079}
-  \label{eq:O2sysDT}
+  \label{eq:lrmhinf:O2sysDT}
   \text{,}
@@
        \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
-  \label{eq:SNR}
+  \label{eq:lrmhinf:SNR}
 \end{equation}
@@
 
-\figref{fig:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
+\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
 The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to linear models ($N_B=1$). 
@@
   %\input{\thisDir/figs/example-LRM-SNR1.tikz}
-  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
   Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
-  Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
-  \label{fig:exampleIntergrid}
+  Hence, $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
+  \label{fig:lrmhinf:exampleIntergrid}
 \end{figure}
 
-It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
+It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
 Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
@@
 
-We simulate the system \eqref{eq:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
-To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:LPMHinf}.
+We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
+To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
 The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
 These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
-The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:MC-run-length}.
+The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.
 
@@
   \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
-  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
-A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}.
-The shaded areas show the $\pm \sigma$ intervals which are mostly due to the noise.
+  However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
+A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}.
+The shaded areas show the $\pm \sigma$ intervals which are due to the noise.
   }
-\label{fig:MC-run-length}
+\label{fig:lrmhinf:MC-run-length}
 \end{figure}
 
-It can be seen in \figref{fig:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
+It can be seen in \figref{fig:lrmhinf:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
 $\expectedValue{\gamma_{\mathrm{FRF}}} \approx \gamma$.
 Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
-For long experiments $(N \to \infty)$, the true $\norm{\Delta}$ is recovered.
+For long experiments $(N \to \infty)$, the true $\infnorm{\Delta}$ is recovered.
 Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.
 
+\begin{remark} \label{rem:lrmhinf:constructWeights}
+The construction of weighting filters $(W,V)$ for the design of a robust controller typically happens based on measurement data which is available non-parametrically, i.e.
+only available at a limited frequency grid.
+The goal of the filter design is to construct low-order minimum-phase filters that form a tight overbound of particular real-valued functions of the frequency.
+Concretely, such a real-valued function is often a singular value of e.g.
+the loop gain or one of the loop sensitivity functions~\citep{Boeren2013,Scheid1995,Bibel1992,Skogestad2005} such that the design entails practical control objectives (disturbance rejection, input tracking, \ldots).
+However, since such a function is only measured at a limited amount of frequency points, such overbounds can be hard to construct when resonances are present.
+E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but notes in Section~IV that limited frequency resolution can hamper construction of these filters.
+The obvious solution to collect more densely-sampled data, is often not desirable (e.g. due to time constraints, limited access to the actual plant, cost of experimentation, \ldots).
+However, the method proposed  in this chapter can provide more densely-sampled view of the data without an increase in measurement time.
+\end{remark}
+
 \section{Application to an \glsentryname{AVIS}}
-\label{sec:measurement}
-The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:avis}.
+\label{sec:lrmhinf:measurement}
+The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
 The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
@@
 \subsection{Measurement \& control framework}
-\label{sec:control}
-The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:tpc}) with $r_2 = 0$.
-The controller $\Controller=\experimental\Controller$  stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
-The $r_1$ input consists of five periods of a random phase multisine~\citep{Geerardyn2013TIM} of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
+\label{sec:lrmhinf:control}
+The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
+The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
+See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
+The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
+See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.
 
@@
  \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
- \label{fig:tpc}
+ \label{fig:lrmhinf:tpc}
 \end{figure}
@@
  \caption[Dual-Youla parametrization.]{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
-\label{fig:dualYoula}
+\label{fig:lrmhinf:dualYoula}
 \end{figure}
@@
         }
-  \label{eq:dualYoulaModelSet}
+  \label{eq:lrmhinf:dualYoulaModelSet}
   \text{,}
 \end{equation}
-where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:dualYoula}).
-To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:dualYoula} are required.
+where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
+To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
 These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
-In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:LPMHinf} applies.
+In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
 
@@
       \infnorm{W \ClosedLoop{\Plant,\Controller} V}
-  \label{eq:controlCrit}
+  \label{eq:lrmhinf:controlCrit}
   \text{,}
@@
 % Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
-I.e. even for a weighted control criterion \eqref{eq:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
-In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:avis-frf}) is estimated.
-Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:avisMeas}).
+I.e.
+even for a weighted control criterion \eqref{eq:lrmhinf:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
+In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
+Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).
 
@@
   \caption{\Glsentryfirst{AVIS}.}
-  \label{fig:avis}
+  \label{fig:lrmhinf:avis}
 \end{figure}
@@
  \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
- \label{fig:avis-frf}
+ \label{fig:lrmhinf:avis-frf}
 \end{figure}
@@
 \subsection{Results}
-\label{sec:resultsAvis}
+\label{sec:lrmhinf:resultsAvis}
 To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
@@
 
-The measured $\Delta$ is shown in \figref{fig:avisMeas} for the whole frequency band and \figref{fig:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
+The measured $\Delta$ is shown in \figref{fig:lrmhinf:avisMeas} for the whole frequency band and \figref{fig:lrmhinf:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
 Two aspects of the proposed method are examined.
@@
     \setlength{\figureheight}{0.68\figurewidth}
-    % \input{\thisDir/figs/avis-delta-full.tikz}
-    \TODOfig{split plots}
+    \input{\thisDir/figs/avis-delta-full.tikz}
+    %\TODOfig{split plots}
  \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling.]{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation.
-The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
-\label{fig:avisMeas}
+The data in the rectangle is also shown in \figref{fig:lrmhinf:avisMeasZoom}.}
+\label{fig:lrmhinf:avisMeas}
 \end{figure}
@@
    \input{\thisDir/figs/avis4.tikz}
- \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
-Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
-The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
-\label{fig:avisMeasZoom}
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:lrmhinf:avis4-LRMi} and the proposed interpolation.
+Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:lrmhinf:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
+The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:lrmhinf:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:lrmhinf:avis4-valid-hinf}.}
+\label{fig:lrmhinf:avisMeasZoom}
 \end{figure}
 
-\vspace{-2em}
 \paragraph*{Interpolation performance}
-\label{sec:avis-interpol}
-\figref{fig:avisMeas} and \figref{fig:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
-In the frequency range shown in \figref{fig:avisMeasZoom}, the relative difference between both is at most $2\%$.
+\label{sec:lrmhinf:avis-interpol}
+\figref{fig:lrmhinf:avisMeas} and \figref{fig:lrmhinf:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
+In the frequency range shown in \figref{fig:lrmhinf:avisMeasZoom}, the relative difference between both is at most $2\%$.
 
-\vspace{-2em}
 \paragraph*{Peak value estimates}
-\label{sec:avis-peak-value}
+\label{sec:lrmhinf:avis-peak-value}
 Near $296\unit{Hz}$, a modest improvement of the peak estimate from $-15.3 \unit{dB}$ (at-grid) to $-14.0 \unit{dB}$ is obtained by the interpolation.
 The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
-The proposed method \eqref{eq:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
+The proposed method \eqref{eq:lrmhinf:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
 $\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
@@
 \section{Conclusion and Further Research}
-\label{sec:conclusion}
+\label{sec:lrmhinf:conclusion}
 A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
-In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\norm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
-It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\norm{\Delta}$.
+In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
+It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.
 The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.

### 2016-04-03 ch04-lrmhinf/paper.tex
Clean up on aisle CH04

@@
     \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
+    \item \TODO{refer to book chapter of Tom}
   \end{itemize}
@@
 The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
-The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM}~\citep{Schoukens2009LPM} and \gls{LRM}~\citep{McKelvey2012LRM} as introduced in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM} \citep{Schoukens2009LPM} and \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
 Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
-In the present paper, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
+Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
 The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
 % Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
-% The present paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
+% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
 
@@
 \begin{equation}
-  \gamma = \infnorm{\Delta} \isdef \sup_{\omega} \abs{\Delta(\omega)} \text{ for \gls{SISO} systems}
+  \gamma 
+    = 
+       \infnorm{\Delta} 
+    \isdef 
+         \sup_{\omega} 
+         \abs{\Delta(\omega)}
+  \text{ for \gls{SISO} systems}
   \text{.}
@@
 \begin{remark}
-It is even more common to use a weighted norm, e.g.  $\infnorm{W \Delta V}$ in robust control designs for some weighting filters $(W,V)$ that are stable and minimum-phase.
-Two cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters.
+It is even more common to use a weighted norm $\infnorm{W \Delta V}$ in robust control designs where $(W,V)$ are stable and minimum-phase weighting filters.
+Two use cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters from data.
 In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e.
@@
 To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
-$ \omega_{\star} 
+\begin{equation}
+ \omega_{\star} 
      \isdef 
@@
          \sup_{\omega} 
-           \abs{\Delta(\omega)}
+           \svdMax{\Delta(\omega)}
   \text{.}
   \label{eq:lrmhinf:omega-star}
-$
+\end{equation}
 However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
-As such, \eqref{eq:lrmhinf:HinfNormSISO} can be rewritten as
-\begin{equation}
-  \gamma \isdef \sup_{\omega} \abs{\Delta(\omega)}
-         = \sup 
-             \set{
-                \ezbrace{\sup_{\omega \in \DFTGrid  } \abs{\Delta(\omega)}}{\gamma_{\mathrm{FRF}}}
+As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
+\begin{align}
+  \gamma &\isdef 
+    \sup_{\omega} 
+      \svdMax{\Delta(\omega)}
+         = \max 
+             \Set{
+                \max_{\omega \in \DFTGrid  } 
+                  \svdMax{\Delta(\omega)}
                 \;,\;
-                \ezbrace{
-                \sup_{\omega \in \InterGrid} \abs{\Delta(\omega)}}{\gamma_{\mathrm{IG}}}}
-  \label{eq:lrmhinf:gamma-split-grid}
-\end{equation}
+                \sup_{\omega \in \InterGrid} 
+                  \svdMax{\Delta(\omega)}
+                }
+  \label{eq:lrmhinf:gamma-split-grid}\\
+  \gammaAtGrid & \isdef 
+    \max_{\omega \in \DFTGrid  } 
+      \svdMax{\Delta(\omega)}
+  \label{eq:lrmhinf:gamma:atGrid}\\
+  \gammaIntergrid & \isdef 
+    \sup_{\omega \in \InterGrid} 
+      \svdMax{\Delta(\omega)}
+   \label{eq:lrmhinf:gamma:interGrid}
+\end{align}
 where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
+Direct inspection of the \gls{FRF} data only allows access to $\gammaAtGrid$.
 Two cases can be distinguished:
 \begin{enumerate}
-  \item $\omega_{\star} \in \DFTGrid$ such that $\abs{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
-  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\abs{\Delta(\omega_{\star})}  = \gamma = \gamma_{\mathrm{IG}}$ is determined by the inter-grid behavior.
+  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
+  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
 \end{enumerate}
 The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
-Its expected value over different realizations of the input signal $\expectedValue{\gamma_{\mathrm{FRF}}} \leq \gamma$ due to the limited frequency resolution.
+Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
 Such an underestimate may lead to overly optimistic controller designs.
 
-The main contribution of this chapter is to  estimate the inter-grid term $\gamma_{\mathrm{IG}}$ without the need for a (global) parametric model.
+The main contribution of this chapter is to  estimate the inter-grid term $\gammaIntergrid$ without the need for a (global) parametric model.
 Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
@@
 \subsection{Set-up}
-\TODO{overgang $\Delta(q)$ naar output-error}
-
 Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
@@
     = 
-      y_{\Delta0}
+      y_{\Delta0}(n)
       + v(n) 
@@
 where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
-For a limited data record ($n \in \set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
+For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
 \begin{equation}
@@
 \end{equation}
-The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
+The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
 
 The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:lrmhinf:control}.
-The results in this paper are presented in discrete time, but the extension to the continuous time case is straightforward.
+The results in this chapter are presented in discrete time, but the extension to the continuous time case is straightforward.
 
@@
 \label{sec:lrmhinf:LPMHinf}
-To estimate $\gamma_{\mathrm{IG}}$, we propose to identify local parametric models in the frequency domain.
-The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} }{ \omega_{k+1} }$ in view of the local validity of the local models.
+To estimate $\gammaIntergrid$, we propose to identify local parametric models in the frequency domain.
+The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} , \omega_{k+1} }$ in view of the local validity of the local models.
 In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
 \begin{equation}
-  \gamma_{\mathrm{IG}} = 
+  \gammaIntergrid = 
     \sup \Set{ 
-                \sup_{\omega \in \Omega_k} \abs{\LocalModel{\Delta}_k(\omega)}
+                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel{\Delta}_k(\omega)}
                 |
@@
 \end{equation}
-where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k$th) frequency $\omega_k$.
+where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k^{\text{th}}$) frequency bin $\omega_k$.
 An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
@@
   \input{\thisDir/figs/interpolation-show.tikz}
-  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
-  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
+  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\Set{1,\ldots,6}$.
+  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
 \label{fig:lrmhinf:interpol-quantities}
@@
 % \subsubsection{Direct method}
-One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gamma_{\mathrm{IG}}$ directly.
+One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
 Hence, it boils down to solving the optimization problems
-\begin{equation}
-  \estimated {\gammaIntergrid} = 
-  % \gamma_{\mathrm{IG}}(k) 
-  % = 
-      \max_{\omega \in \Omega_k} 
-      \abs{\LocalModel{\Delta}_k(\omega)}
+\begin{align}
+  \estimated{\gammaIntergrid}(k) & \isdef 
+      \sup_{\omega \in \Omega_k}
+      \svdMax{\LocalModel{\Delta}_k(\omega)}
+       \quad \forall k \in \Set{1,\ldots,N-1} \\
+  \estimated {\gammaIntergrid} &= 
+  \max \Set{
+    \estimated{\gammaIntergrid}(k) 
+    | 
+    k \in \Set{1,\ldots,N-1}
+  }
       \label{eq:lrmhinf:gamma-direct}
-\end{equation}
-for $k \in \set{1,\ldots,N-1}$.
-These are tractable since $\omega$ is one-dimensional and restricted to the intervals $\Omega_k$.
-Unfortunately, this approach offers no insight in the behavior of $\abs{\Delta(\omega)}$, e.g. around the peak amplitude.
+\end{align}
+These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
+Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.
 
-\paragraph*{Interpolation method}
-To allow inspection of $\abs{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\abs{\Delta(\omega)}$.
-It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\abs{\omega_k-\omega}$ is small.
+\paragraph{Interpolation method}
+To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
+It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
 To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
@@
                   \max
-                  \set{k 
-                    \given{
-                      \omega_k \in \DFTGrid, 
-                      \omega_k \leq \omega}
+                  \Set{
+                    k 
+                    |
+                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                   }\\
@@
                   \min
-                  \set{k 
-                    \given{
-                      \omega_k \in \DFTGrid, 
-                      \omega_k \geq \omega}
+                  \Set{
+                    k
+                    |
+                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                   }
@@
 \end{align}
-Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\abs{\Delta(\omega)}$ are obtained:lrmhinf: $\abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
-In view of obtaining the maximum amplitude, these are `interpolated' to obtain a single estimate:
+Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained: $\svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
+In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
 \begin{equation}
-  \abs{\Delta_{\LMM}(\omega)}
+  \svdMax{\Delta_{\LMM}(\omega)}
     \isdef
-    \sup \set{
-       \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
-        \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+    \sup \Set{
+       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
+        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
     }
@@
     \sup_{\omega\in\Omega}
-    \abs{\Delta_{\LMM}(\omega)} \\
+    \svdMax{\Delta_{\LMM}(\omega)} \\
    &  =
       \sup_{\omega\in\Omega} \; 
-      \sup \set{
-                 \abs{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
-                 \abs{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
+      \sup \Set{
+                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
+                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
   \label{eq:lrmhinf:gammaInterpolOptim}
@@
 $% \begin{equation}
-  \Omega_k = \set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
+  \Omega_k = \Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
 $ % \end{equation}
@@
 \end{align}
-Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \set{-N_W,\ldots,+N_W}$ around each bin $k$.
+Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \Set{-N_W,\ldots,+N_W}$ around each bin $k$.
 This yields
@@
 
-For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM}.
+For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} and \chapref{sec:nonparametric}.
 
@@
 The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
-Concretely, any proper real-rational system $\Delta$ can be decomposed in a parallel connection of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE}.
-For clarity, we repeat the expression here again:
-It is well-known in the mechanical engineering community (see e.g. \citet{Gawronski2004}), that around re
- and using the same logic as in \chapref{sec:excitation}.
+Concretely, any proper real-rational system $\Delta$ can be decomposed in a parallel connection of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE}, i.e.
+\begin{equation}
+\Delta(s) = 
+         \deemph{
+         \sum_{i=1}^{I_1} 
+          \sum_{\multiplicity=1}^{M_{1,i}} 
+            \frac{\dc[i]}
+                      { \left( s - \pole[i] \right)^{\multiplicity}}
+            + 
+        }
+        \sum_{i=1}^{I_2} 
+          \deemph{\sum_{\multiplicity=1}^{M_{2,i}}}
+           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
+                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
+\end{equation}
+with the same notations as in \chapref{sec:excitation}, most importantly, each resonant pole can be characterized by its frequency $\wn[i]$ and damping $\damping[i]$.
+In the structural engineering community (see e.g.
+\citet[Chapter 2]{Gawronski2004}) it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function: the gray terms in the equation above are negligible such that only a single second-order term needs to be accounted for.
 As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
 mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
-To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest.
+To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest as those are responsible for large gains of the system.
 Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
@@
 By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
-In this paper a Hann window and $N_S=1$ are used.
+In this chapter a Hann window and $N_S=1$ are used.
 Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
@@
 \figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
-The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to linear models ($N_B=1$). 
+The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($N_B=1$). 
 Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.
@@
   \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
-  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
+  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
@@
 
-It can be observed for $\gamma_{\mathrm{IG}}$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
+It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
 Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
 The \gls{LPM}, on the other hand, does not provide a reliable estimate.
+This behavior is related to the Runge phenomenon~\citep{Runge1901}.
 
@@
   %\input{figures/runLength.tikz}
-  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
   However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
@@
 
-It can be seen in \figref{fig:lrmhinf:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gamma_{\mathrm{FRF}}$, i.e.
-$\expectedValue{\gamma_{\mathrm{FRF}}} \approx \gamma$.
-Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gamma_{\mathrm{IG}}$.
+It can be seen in \figref{fig:lrmhinf:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gammaAtGrid$, i.e.
+$\expectedValue{\gammaAtGrid} \approx \gamma$.
+Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gammaIntergrid$.
 For long experiments $(N \to \infty)$, the true $\infnorm{\Delta}$ is recovered.
@@
 However, since such a function is only measured at a limited amount of frequency points, such overbounds can be hard to construct when resonances are present.
-E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but notes in Section~IV that limited frequency resolution can hamper construction of these filters.
+E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but note in Section~IV that limited frequency resolution can hamper construction of these filters.
 The obvious solution to collect more densely-sampled data, is often not desirable (e.g. due to time constraints, limited access to the actual plant, cost of experimentation, \ldots).
@@
     \isdef 
-      \set{
-          \left. 
+      \Set{
             \frac{\hat{N} + D_c \Delta}
                  {\hat{D} - N_c \Delta} 
-          \right| 
+          |
             \hinfnorm{\Delta} \leq \gamma
@@
 To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
-These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
+These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
+
 In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
@@
 even for a weighted control criterion \eqref{eq:lrmhinf:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
-In this paper, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
+In this chapter, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
 Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).
@@
   \caption{\Glsentryfirst{AVIS}.}
+  %TODO: add figure of isolation module as well
   \label{fig:lrmhinf:avis}
@@
     \input{\thisDir/figs/avis-frf.tikz}
- \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
+ \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsentryname{AVIS}.}
  \label{fig:lrmhinf:avis-frf}
@@
 
-\begin{figure}
+\begin{figure}[p]
  \centering
-    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figurewidth}{0.7\columnwidth}
     \setlength{\figureheight}{0.68\figurewidth}
     \input{\thisDir/figs/avis-delta-full.tikz}
-    %\TODOfig{split plots}
  \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling.]{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation.
@@
 
-\begin{figure}
+\begin{figure}[p]
  \centering
-    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figurewidth}{0.7\columnwidth}
     \setlength{\figureheight}{0.68\figurewidth}
    \input{\thisDir/figs/avis4.tikz}
- \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:lrmhinf:avis4-LRMi} and the proposed interpolation.
-Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:lrmhinf:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
-The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:lrmhinf:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:lrmhinf:avis4-valid-hinf}.}
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
+Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
+The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
 \label{fig:lrmhinf:avisMeasZoom}
@@
 The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
-The proposed method \eqref{eq:lrmhinf:gammaInterpolOptim} yields $\gamma_{\mathrm{IG}}=-2.5\unit{dB}$.
+The proposed method \eqref{eq:lrmhinf:gammaInterpolOptim} yields $\gammaIntergrid=-2.5\unit{dB}$.
 $\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
@@
 
-\section{Conclusion and Further Research}
+\section{Conclusions}
 \label{sec:lrmhinf:conclusion}
@@
 It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.
+
 The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
@@
 Furthermore, the results are validated by a detailed validation measurement.
-Ongoing research focuses on extending the technique to \gls{MIMO} systems and the study of its stochastic properties.
+Ongoing research focuses on extending the technique to \gls{MIMO} systems.

### 2016-04-03 ch04-lrmhinf/paper.tex
Improve intro Ch04

@@
     \item \TODO{add section from Benchmark paper}
-    \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
-    \item \TODO{refer to book chapter of Tom}
   \end{itemize}
-
 \newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
@@
 % \label{sec:lrmhinf:Intro}
+
+For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
+However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
+Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
+In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
+The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.
 
@@
 \paragraph*{Direct method}
-% \subsubsection{Direct method}
 One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
@@
 \end{align}
-Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained: $\svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
+Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
+\begin{itemize}
+ \item $\svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$, and 
+ \item $\svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
+\end{itemize}
 In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
@@
     \isdef
-    \sup \Set{
+    \max \Set{
        \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
@@
       \sup_{\omega\in\Omega} \; 
-      \sup \Set{
+      \max \Set{
                  \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 

### 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
Some small things

@@
   \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
-  \caption{Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
+  \caption[\Simulink model used on the \glsentryshort{AVIS}]{\Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
   \label{fig:avis:simulink:setup}
@@
   \includegraphics{\thisDir/figs/avis-with-axes.pdf}
-  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
+  \caption[\glsentryshort{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
 For each of the actuators and sensors, the color indicates the principal direction.}
@@
 \input{\thisDir/figs/avis-setup-filters.tikz}
-\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
+\caption[\glsentryshort{AVIS} controller and filters]{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
 \label{fig:avis:bodeplots:controllerAndSensor}
@@
   \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
-  \caption{Simulink model of the AVIS sub-block.}
+  \caption{\Simulink model of the \glsentryshort{AVIS} sub-block.}
   \label{fig:avis:simulink:avis}

### 2016-04-03 config/glossaries.inc.tex
Address some minor TODOs
Lots of work on LRMHinf + description of AVIS setup
Lots of changes to CH04
Some small things

@@
 \newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
-\newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}
+% \newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}
 
@@
 \newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
-\newsymbolglos{operator-ln}{\ln \placeholder}{Natural logarithm of \placeholder}
+\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
 \newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
-\newsymbolglos{operator-log}{\log_{B} \placeholder}{Logarithm in base $B$ of \placeholder{}  (when $B$ is omitted, $B=10$ is implied)}
+\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
 \newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
@@
 \newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
+\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
+\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
+\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
 \newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
@@
 
-\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
-\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
-\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}
+\newsymbolglos{sys-damping}{\damping}{Relative damping of a pole or system}
+\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
+\newsymbolglos{sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}
 
@@
 \newacronym{DAC}{DAC}{digital-to-analog converter}
+\newacronym{DAQ}{DAQ}{data acquisition}
 \newacronym{DC}{DC}{direct current (also: mean value)}
@@
 \newacronym{PDF}{PDF}{probability distribution function}
+\newacronym{PI}{PI}{proportional-integral}
 \newacronym{PRESS}{PRESS}{prediction residual error sum of squares}

### 2016-04-04 ch04-lrmhinf/paper.tex
Add guideline to CH04

@@
-  \begin{itemize}
-    \item \TODO{add section from Benchmark paper}
-  \end{itemize}
+  % \begin{itemize}
+  %   \item \TODO{add section from Benchmark paper}
+  % \end{itemize}
 \newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
@@
 The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
+This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
 These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
@@
 \end{remark}
+
+\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
+After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
+For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
+\end{guideline}
 

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
Add epigraphs
Some changes from Tom
Add some TODOs
Different figure names per chapter
Lots of work on LRMHinf + description of AVIS setup
Lots of changes to CH04
Clean up on aisle CH04
Add photo details of AVIS

@@
-\chapter{Non-parametric resonance modeling}
+\chapter{Non-parametric Resonance Peak Modeling}
 \label{sec:hinf}
+\def\thisDir{ch04-lrmhinf}
+\tikzsetfigurename{ch04fig}
+\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
+\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
+\glsresetall
+
+%TODO: add section from Benchmark paper
+
+\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
+\newcommand{\dampingValue}{\ensuremath{0.025}}
+\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}
+
+% \section{Introduction}
+% \label{sec:lrmhinf:Intro}
+
+For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
+However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
+Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
+In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
+The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.
+
+Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability.
+An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
+The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
+However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
+Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
+However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
+On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
+On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.
+
+Several approaches have been developed to determine bounds on the model uncertainty. 
+First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
+However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
+Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
+Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
+In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
+In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
+However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
+Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
+These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
+A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
+Unfortunately, these methods require a sequence of dedicated iterative experiments.
+This increases the measurement time significantly, especially for \gls{MIMO} plants.
+When measurement time is expensive, this is a severe impediment.
+
+Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
+The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
+The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM} \citep{Schoukens2009LPM} and \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
+Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
+The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
+% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
+
+\paragraph*{Outline}
+\label{par:lrmhinf:toc}
+The problem is formulated in \secref{sec:lrmhinf:Problem}.
+In \secref{sec:lrmhinf:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
+In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
+The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:lrmhinf:measurement}.
+Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.
+
+%\glsresetall
+
+\section{Problem Formulation}
+\label{sec:lrmhinf:Problem}
+Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
+After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
+The \Hinf{} norm of the error system $\Delta$ is
+\begin{equation}
+  \gamma 
+     = 
+       \infnorm{\Delta} 
+    \isdef 
+       \sup_{\omega} 
+         \svdMax{\Delta(\omega)}
+  \label{eq:lrmhinf:HinfNorm}
+\end{equation}
+for a stable system where $\svdMax{\placeholder}$ denotes the maximum singular value of $\placeholder$.
+Note that for \gls{SISO} systems, $\svdMax{\Delta} = \abs{\Delta}$ and the definition above reduces to
+\begin{equation}
+  \gamma 
+    = 
+       \infnorm{\Delta} 
+    \isdef 
+         \sup_{\omega} 
+         \abs{\Delta(\omega)}
+  \text{ for \gls{SISO} systems}
+  \text{.}
+  \label{eq:lrmhinf:HinfNormSISO}
+\end{equation}
+In robust control design methodologies, such \Hinf{} norms often play an important purpose to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.
+
+\begin{remark}
+It is even more common to use a weighted norm $\infnorm{W \Delta V}$ in robust control designs where $(W,V)$ are stable and minimum-phase weighting filters.
+Two use cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters from data.
+In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e.
+by replacing $\svdMax{\Delta}$ with $\svdMax{W \Delta V}$ in the formulas.
+The other case is discussed in Remark~\ref{rem:lrmhinf:constructWeights} further on.
+\end{remark}
+
+To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
+\begin{equation}
+ \omega_{\star} 
+     \isdef 
+       \arg
+         \sup_{\omega} 
+           \svdMax{\Delta(\omega)}
+  \text{.}
+  \label{eq:lrmhinf:omega-star}
+\end{equation}
+However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
+As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
+\begin{align}
+  \gamma &\isdef 
+    \sup_{\omega} 
+      \svdMax{\Delta(\omega)}
+         = \max 
+             \Set{
+                \max_{\omega \in \DFTGrid  } 
+                  \svdMax{\Delta(\omega)}
+                \;,\;
+                \sup_{\omega \in \InterGrid} 
+                  \svdMax{\Delta(\omega)}
+                }
+  \label{eq:lrmhinf:gamma-split-grid}\\
+  \gammaAtGrid & \isdef 
+    \max_{\omega \in \DFTGrid  } 
+      \svdMax{\Delta(\omega)}
+  \label{eq:lrmhinf:gamma:atGrid}\\
+  \gammaIntergrid & \isdef 
+    \sup_{\omega \in \InterGrid} 
+      \svdMax{\Delta(\omega)}
+   \label{eq:lrmhinf:gamma:interGrid}
+\end{align}
+where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
+Direct inspection of the \gls{FRF} data only allows access to $\gammaAtGrid$.
+Two cases can be distinguished:
+\begin{enumerate}
+  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
+  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
+\end{enumerate}
+The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
+Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
+Such an underestimate may lead to overly optimistic controller designs.
+
+The main contribution of this chapter is to  estimate the inter-grid term $\gammaIntergrid$ without the need for a (global) parametric model.
+Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
+
+\subsection{Set-up}
+Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
+For an infinitely long data record, this can be described in the time-domain as
+\begin{equation}
+  y_{\Delta}(n) 
+    = 
+      y_{\Delta0}(n)
+      + v(n) 
+    = 
+      \Delta(q)u_{\Delta}(n) 
+      + H(q)e(n)
+  \label{eq:lrmhinf:sysDeltaInfData}
+\end{equation}
+where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
+For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
+\begin{equation}
+    y_{\Delta}(n) 
+      = 
+        \Delta(q)u(n) 
+        + H(q)e(n) 
+        + t_{\Delta}(n)
+    \text{.}
+    \label{eq:lrmhinf:sysDeltaFiniteData}
+\end{equation}
+By applying the \gls{DFT}
+\begin{equation}
+  X(k) 
+       = 
+         \frac{1}
+              {\sqrt{N}} 
+         \sum_{n=0}^{N-1} 
+            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
+         \quad   
+         \forall k \in \mathbb{Z}
+  \label{eq:lrmhinf:DFT}
+\end{equation} 
+to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
+\begin{equation}
+  Y_{\Delta}(k) 
+                = 
+                  \Delta(\omega_k) U_{\Delta}(k) 
+                  + T_{\Delta}(\omega_k) 
+                  + V(k) 
+  \text{.}
+  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
+\end{equation}
+The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
+
+The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:lrmhinf:control}.
+The results in this chapter are presented in discrete time, but the extension to the continuous time case is straightforward.
+
+\section{\Hinf{} Norm Estimation Procedure}
+\label{sec:lrmhinf:LPMHinf}
+To estimate $\gammaIntergrid$, we propose to identify local parametric models in the frequency domain.
+The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} , \omega_{k+1} }$ in view of the local validity of the local models.
+In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
+\begin{equation}
+  \gammaIntergrid = 
+    \sup \Set{ 
+                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel{\Delta}_k(\omega)}
+                |
+                k = 1,\ldots,N-1
+                }
+   \label{eq:lrmhinf:gamma-inter-grid}
+\end{equation}
+where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k^{\text{th}}$) frequency bin $\omega_k$.
+An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
+Two alternative methods allow evaluation of~\eqref{eq:lrmhinf:gamma-inter-grid} in practice.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.68\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/interpolation-show.tikz}
+  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\Set{1,\ldots,6}$.
+  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
+\label{fig:lrmhinf:interpol-quantities}
+\end{figure}
+
+\paragraph*{Direct method}
+One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
+Hence, it boils down to solving the optimization problems
+\begin{align}
+  \estimated{\gammaIntergrid}(k) & \isdef 
+      \sup_{\omega \in \Omega_k}
+      \svdMax{\LocalModel{\Delta}_k(\omega)}
+       \quad \forall k \in \Set{1,\ldots,N-1} 
+       \label{eq:lrmhinf:gamma-direct:optimizations}\\
+  \estimated {\gammaIntergrid} &= 
+  \max \Set{
+    \estimated{\gammaIntergrid}(k) 
+    | 
+    k \in \Set{1,\ldots,N-1}
+  }
+      \label{eq:lrmhinf:gamma-direct}
+\end{align}
+These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
+Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.
+
+\paragraph{Interpolation method}
+To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
+It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
+To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
+\begin{align}
+  k_L(\omega) & 
+                \isdef
+                  \max
+                  \Set{
+                    k 
+                    |
+                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
+                  }\\
+  k_R(\omega) & 
+                \isdef
+                  \min
+                  \Set{
+                    k
+                    |
+                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
+                  }
+  \text{.}
+  \label{eq:lrmhinf:kL-kR-indexing-functions}
+\end{align}
+Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
+\begin{equation*}
+ \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)} 
+ \quad \text{ and } \quad
+ \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+\end{equation*}
+In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
+\begin{equation}
+  \svdMax{\Delta_{\LMM}(\omega)}
+    \isdef
+    \max \Set{
+       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
+        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+    }
+    \label{eq:lrmhinf:DeltaLRMInterpolation}
+\end{equation}
+by retaining the largest both.
+It follows that
+\begin{align}
+  \widehat{\infnorm{\Delta_{\LMM}}}
+    & \isdef
+    \sup_{\omega\in\Omega}
+    \svdMax{\Delta_{\LMM}(\omega)} \\
+   &  =
+      \sup_{\omega\in\Omega} \; 
+      \max \Set{
+                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
+                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
+  \label{eq:lrmhinf:gammaInterpolOptim}
+  \text{.}
+\end{align}
+
+\paragraph*{Remarks:}
+The optimization problems~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct:optimizations} each amount to one-dimensional optimization problems, hence they be solved easily by griding the frequency $\omega$.
+The peak amplitudes obtained using~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
+ \begin{equation}
+  \Omega_k = \Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
+ \end{equation}
+for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
+In \figref{fig:lrmhinf:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
+
+\subsection{The \glsentrydesc{LRM}}
+\label{sec:lrmhinf:LRM}
+The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
+The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
+As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
+\begin{align}
+  \Delta(\omega_{k+r})     
+    &\approx 
+        \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
+      = 
+        \frac{B_k(r)}{A_k(r)} 
+      \isdef 
+        \LocalModel{\Delta}_{k}(\omega_{k+r})
+      \label{eq:lrmhinf:LRMTaylorSystem} \\
+  T_{\Delta}(\omega_{k+r}) 
+    &\approx 
+        \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
+      = 
+        \frac{T_k'(r)}{A_k(r)} 
+      \isdef 
+        \LocalModel{T}_{k}(\omega_{k+r})
+  \label{eq:lrmhinf:LRMTaylorTransient}
+  \text{.}
+\end{align}
+Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \Set{-N_W,\ldots,+N_W}$ around each bin $k$.
+This yields
+\begin{equation}
+  Y_{\Delta}(k+r) 
+                 \approx
+                    \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
+                    + T_{\Delta}(\omega_{k+r}) 
+    \quad
+    \forall r \in \LocalWindow
+    \text{.}
+    \label{eq:lrmhinf:LocalWindowSpectra}
+\end{equation}
+By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
+\begin{align}
+  Y_{\Delta}(k+r) 
+                  & \approx
+                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
+                    + \LocalModel{T}_k(\omega_{k+r}) 
+                    & \forall r \in \LocalWindow \\
+                  & = 
+                    \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
+                    + 
+                    \frac{T'_k(r)}{A_k(r)} 
+                    & \forall r \in \LocalWindow
+    \text{.}
+    \label{eq:lrmhinf:LocalWindowSpectraLRM}
+\end{align}
+To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
+By doing so, the local linear-least-squares cost function
+\begin{equation}
+  \sum_{r=-N_W}^{N_W} 
+  \left| 
+    A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
+  \right|^2
+  \label{eq:lrmhinf:localCostLRM}
+\end{equation}
+ around each bin $k$ can be constructed.
+We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
+For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.
+
+For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} and \chapref{sec:nonparametric}.
+
+\section{Simulation}
+\label{sec:lrmhinf:simulation}
+To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
+The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
+Concretely, any proper real-rational system $\Delta$ can be decomposed in a parallel connection of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE}, i.e.
+\begin{equation}
+\Delta(s) = 
+         \deemph{
+         \sum_{i=1}^{I_1} 
+          \sum_{\multiplicity=1}^{M_{1,i}} 
+            \frac{\dc[i]}
+                      { \left( s - \pole[i] \right)^{\multiplicity}}
+            + 
+        }
+        \sum_{i=1}^{I_2} 
+          \deemph{\sum_{\multiplicity=1}^{M_{2,i}}}
+           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
+                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
+\end{equation}
+with the same notations as in \chapref{sec:excitation}, most importantly, each resonant pole can be characterized by its frequency $\wn[i]$ and damping $\damping[i]$.
+In the structural engineering community (see e.g.
+\citet[Chapter 2]{Gawronski2004}) it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function: the gray terms in the equation above are negligible such that only a single second-order term needs to be accounted for.
+As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
+mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
+To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest as those are responsible for large gains of the system.
+Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
+This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
+By normalizing the conclusions for the time constant $\timeconst$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\damping$.
+Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the natural frequency of the dominant pole.
+
+\subsection{A concrete simulation}
+Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
+\begin{equation}
+  \Delta(z) 
+    =  \frac{0.45373 z + 0.44752}
+            {z^2 - 1.0595 z + 0.96079}
+  \label{eq:lrmhinf:O2sysDT}
+  \text{,}
+\end{equation}
+which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
+The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
+\begin{equation}
+  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
+              {\sqrt{\inv{N}\sum_n v^2(n) }}
+       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
+       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
+  \label{eq:lrmhinf:SNR}
+\end{equation}
+of $10$ is obtained.
+
+Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
+This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
+By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
+In this chapter a Hann window and $N_S=1$ are used.
+Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
+
+\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
+The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($N_B=1$). 
+Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/example-both.tikz}
+  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
+  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
+  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
+  Hence, $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
+  \label{fig:lrmhinf:exampleIntergrid}
+\end{figure}
+
+It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
+Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
+The \gls{LPM}, on the other hand, does not provide a reliable estimate.
+This behavior is related to the Runge phenomenon~\citep{Runge1901}.
+
+\subsection{Study of the experiment length}
+Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
+In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.
+
+We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
+To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
+The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
+This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
+These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
+The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.75\columnwidth}
+  \setlength{\figureheight}{0.68\figurewidth}
+  \input{\thisDir/figs/MC-runlength.tikz}
+  %\input{figures/runLength.tikz}
+  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
+A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}.
+The shaded areas show the $\pm \sigma$ intervals which are due to the noise.
+  }
+\label{fig:lrmhinf:MC-run-length}
+\end{figure}
+
+It can be seen in \figref{fig:lrmhinf:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gammaAtGrid$, i.e.
+$\expectedValue{\gammaAtGrid} \approx \gamma$.
+Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gammaIntergrid$.
+For long experiments $(N \to \infty)$, the true $\infnorm{\Delta}$ is recovered.
+Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.
+
+\begin{remark} \label{rem:lrmhinf:constructWeights}
+The construction of weighting filters $(W,V)$ for the design of a robust controller typically happens based on measurement data which is available non-parametrically, i.e.
+only available at a limited frequency grid.
+The goal of the filter design is to construct low-order minimum-phase filters that form a tight overbound of particular real-valued functions of the frequency.
+Concretely, such a real-valued function is often a singular value of e.g.
+the loop gain or one of the loop sensitivity functions~\citep{Boeren2013,Scheid1995,Bibel1992,Skogestad2005} such that the design entails practical control objectives (disturbance rejection, input tracking, \ldots).
+However, since such a function is only measured at a limited amount of frequency points, such overbounds can be hard to construct when resonances are present.
+E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but note in Section~IV that limited frequency resolution can hamper construction of these filters.
+The obvious solution to collect more densely-sampled data, is often not desirable (e.g. due to time constraints, limited access to the actual plant, cost of experimentation, \ldots).
+However, the method proposed  in this chapter can provide more densely-sampled view of the data without an increase in measurement time.
+\end{remark}
+
+\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
+After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
+For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
+\end{guideline}
+
+\section{Application to an \glsentryname{AVIS}}
+\label{sec:lrmhinf:measurement}
+The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
+The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
+Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
+To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
+
+\subsection{Measurement \& control framework}
+\label{sec:lrmhinf:control}
+The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
+The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
+See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
+The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
+See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.
+
+\begin{figure}
+ \centering
+ \input{\thisDir/figs/tpcrobust.tikz}
+ \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
+ \label{fig:lrmhinf:tpc}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \input{\thisDir/figs/dualYoula.tikz}
+ \caption[Dual-Youla parametrization.]{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
+\label{fig:lrmhinf:dualYoula}
+\end{figure}
+
+The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
+\begin{equation}
+  \ModelSet[] 
+    \isdef 
+      \Set{
+            \frac{\hat{N} + D_c \Delta}
+                 {\hat{D} - N_c \Delta} 
+          |
+            \hinfnorm{\Delta} \leq \gamma
+        }
+  \label{eq:lrmhinf:dualYoulaModelSet}
+  \text{,}
+\end{equation}
+where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
+To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
+These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
+
+In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
+
+The non-uniqueness of the \gls{RCF} can be exploited to satisfy additional conditions.
+In view of the robust control criterion
+\begin{equation}
+  \Crit(\Plant,\Controller) 
+    \isdef 
+      \infnorm{W \ClosedLoop{\Plant,\Controller} V}
+  \label{eq:lrmhinf:controlCrit}
+  \text{,}
+\end{equation}
+the \glspl{RCF} are constructed such that
+$
+  \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
+  \leq
+  \Crit \left( \estimated\Plant, \experimental\Controller \right)
+  + \gamma
+$
+where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
+% Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.
+I.e.
+even for a weighted control criterion \eqref{eq:lrmhinf:controlCrit}, there is no need to incorporate weights $W'$ and $V'$ into the estimation of the uncertainty bound as $\infnorm{W' \Delta V'}$.
+In this chapter, an eighth-order $\estimated\Plant$~(\figref{fig:lrmhinf:avis-frf}) is estimated.
+Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).
+
+\begin{figure}
+  \centering
+  \setlength\figurewidth{0.75\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
+  \caption{\Glsentryfirst{AVIS}.}
+  \label{fig:lrmhinf:avis}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.475\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
+  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
+  The left photo shows one of the air mounts providing passive vibration isolation.
+  The right photo shows two linear motors that play a role in the active vibration isolation.}
+  \label{fig:lrmhinf:avis:details}
+\end{figure}
+
+\begin{figure}
+ \centering
+    \setlength{\figurewidth}{0.75\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
+    \input{\thisDir/figs/avis-frf.tikz}
+ \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsentryname{AVIS}.}
+ \label{fig:lrmhinf:avis-frf}
+\end{figure}
+
+\subsection{Results}
+\label{sec:lrmhinf:resultsAvis}
+To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
+The full dataset that includes bins not used in the estimation is used to validate the interpolation results.
+
+The measured $\Delta$ is shown in \figref{fig:lrmhinf:avisMeas} for the whole frequency band and \figref{fig:lrmhinf:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
+Two aspects of the proposed method are examined.
+First, the interpolation results for a continuous frequency range are validated.
+Second, the peak amplitudes of $\Delta(\omega)$ are inspected as these are  indicators for $\infnorm{\Delta}$.
+
+\begin{figure}[p]
+ \centering
+    \setlength{\figurewidth}{0.7\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
+    \input{\thisDir/figs/avis-delta-full.tikz}
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling.]{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation.
+The data in the rectangle is also shown in \figref{fig:lrmhinf:avisMeasZoom}.}
+\label{fig:lrmhinf:avisMeas}
+\end{figure}
+
+\begin{figure}[p]
+ \centering
+    \setlength{\figurewidth}{0.7\columnwidth}
+    \setlength{\figureheight}{0.68\figurewidth}
+   \input{\thisDir/figs/avis4.tikz}
+ \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation.
+Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$.
+The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
+\label{fig:lrmhinf:avisMeasZoom}
+\end{figure}
+
+\paragraph*{Interpolation performance}
+\label{sec:lrmhinf:avis-interpol}
+\figref{fig:lrmhinf:avisMeas} and \figref{fig:lrmhinf:avisMeasZoom} show that the estimation and validation data for \gls{LRM} are generally in agreement.
+In the frequency range shown in \figref{fig:lrmhinf:avisMeasZoom}, the relative difference between both is at most $2\%$.
+
+\paragraph*{Peak value estimates}
+\label{sec:lrmhinf:avis-peak-value}
+Near $296\unit{Hz}$, a modest improvement of the peak estimate from $-15.3 \unit{dB}$ (at-grid) to $-14.0 \unit{dB}$ is obtained by the interpolation.
+The estimate near $\omega_{\star} \approx 328\unit{Hz}$ is improved more substantially.
+The proposed method \eqref{eq:lrmhinf:gammaInterpolOptim} yields $\gammaIntergrid=-2.5\unit{dB}$.
+$\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
+This peak agrees well with the validation data, where the nearest (at-grid) value has an amplitude of $-3.2\unit{dB}$ (i.e. $8\%$ difference).
+
+This suggests that the local rational models with interpolation are a very good approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
+
+\section{Conclusions}
+\label{sec:lrmhinf:conclusion}
+A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
+In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
+It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.
+
+The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
+It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
+Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
+Furthermore, the results are validated by a detailed validation measurement.
+Ongoing research focuses on extending the technique to \gls{MIMO} systems.
+
+\begin{subappendices}
+  \input{\thisDir/ch04appendices.inc.tex}
+\end{subappendices}

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
More detailed photos of AVIS

@@
 The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
-The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
-Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
+The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
+Six geophones measure the payload velocity and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform.
+Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up.
 To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
+%TODO: include benchmark section about vibration isolation
 

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
Add figures about vibration isolation

@@
 An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
-The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
+The underlying feedback control principle is skyhook damping~\citep{Karnopp1995,Collette2011}. 
 However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
@@
 The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
-The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
-Six geophones measure the payload velocity and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform.
+%TODO: include benchmark section about vibration isolation
+The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload (e.g.
+passengers in a car, sensitive equipment such as atomic force microscopes or wafer-scanners used for lithography) is not disturbed by vibrations generated by either the payload itself or by the outside world.
+
+\begin{figure}
+ \centering
+  \setlength{\figurewidth}{0.45\columnwidth}
+  \begin{subfigure}[b]{0.49\columnwidth}
+  \remakeNextFigure
+    \input{\thisDir/figs/vibrationisolation-classical.tikz}
+    \caption{Using relative velocity measurements.}  
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\columnwidth}
+  \remakeNextFigure
+    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
+    \caption{Using an absolute velocity measurements.}  
+  \end{subfigure}
+  \caption{Vibration isolation}
+\end{figure}
+%TODO: include benchmark section about vibration isolation
+
+The particular \gls{AVIS} used for the experiments, consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
+Six geophones measure the payload velocity in an absolute reference frame and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform using the principle of `sky-hook damping'.
 Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up.
 To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
-%TODO: include benchmark section about vibration isolation
 

### 2016-04-04 config/mechanical.inc.tex
Add figures about vibration isolation

\usetikzlibrary{calc}
\usetikzlibrary{patterns}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\usepackage{contour}
% http://tex.stackexchange.com/questions/18472/tikz-halo-around-text
% http://tex.stackexchange.com/questions/19348/how-to-draw-a-line-passing-through-a-point-and-perpendicular-to-another
% http://tex.stackexchange.com/questions/13933/drawing-mechanical-systems-in-latex

\tikzstyle{spring}=[thick,decorate,decoration={coil,pre length=0.5em,post length=0.5em,segment length=0.5em,amplitude=0.75em}] %try decoration=zigzag
\tikzstyle{damper}=[thick,decoration={markings,  
  mark connection node=dmp,
  mark=at position 0.5 with 
  {
    \node (dmp) [thick,inner sep=0pt,transform shape,rotate=-90,minimum width=15pt,minimum height=3pt,draw=none] {};
    \draw [thick] ($(dmp.north east)+(2pt,0)$) -- (dmp.south east) -- (dmp.south west) -- ($(dmp.north west)+(2pt,0)$);
    \draw [thick] ($(dmp.north)+(0,-5pt)$) -- ($(dmp.north)+(0,5pt)$);
  }
}, decorate]

\tikzstyle{force}=[everyMechanical,-latex,thick]
\tikzstyle{sensorLine}=[everyMechanical,<->,very thick]

\colorlet{gndcolor}{TangoAluminium5}
\colorlet{skycolor}{TangoSkyBlue2}
\colorlet{darkSkycolor}{TangoSkyBlue3}
\colorlet{masscolor}{TangoAluminium1}

\tikzstyle{everyMechanical}=[draw,outer sep=0pt,thick,font=\bfseries]

\tikzstyle{mass}=[everyMechanical,minimum width=3em,minimum height=1.5em,draw=black,fill=masscolor]
\tikzstyle{mechController}=[mass,very thick,fill=white,minimum height=2.5em,minimum width=2em]

\tikzstyle{ground}=[everyMechanical,pattern color=gndcolor,pattern=north east lines,draw=none,minimum width=3em,minimum height=1.5em]
\tikzstyle{sky}=[ground, pattern color=skycolor,font={\color{darkSkycolor}}]

\tikzstyle{groundline}=[everyMechanical,color=gndcolor,line width=1pt]
\tikzstyle{skyline}=[groundline,color=skycolor]

### 2016-04-05 ch04-lrmhinf/lrmhinf.tex
More info on AVIS/VI setup

--- 2016-04-04 ch04-lrmhinf/lrmhinf.tex
@@
 \glsresetall
-
-%TODO: add section from Benchmark paper
 
@@
 The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
-The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
-Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
-To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
+The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload (e.g.
+passengers in a car, sensitive equipment such as atomic force microscopes or wafer-scanners used for lithography) is not disturbed by vibrations generated by either the payload itself ($F_{\mathrm{d(pl)}}$) or by the outside world ($F_{\mathrm{d(pl)}}$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.
+
+\begin{figure}
+ \centering
+  \setlength{\figurewidth}{0.45\columnwidth}
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \input{\thisDir/figs/vibrationisolation-classical.tikz}
+    \caption{Traditional set-up.}  
+    \label{fig:lrmhinf:vibration-isolation:traditional}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
+    \caption{Principle of sky-hook damping.}  
+    \label{fig:lrmhinf:vibration-isolation:skyhook}
+  \end{subfigure}
+  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
+  \caption{Conceptual illustration of (active) vibration isolation set-ups.
+In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
+  If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
+  When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
+  }
+  \label{fig:lrmhinf:vibration-isolation}
+\end{figure}
+
+The typical set-up for vibration isolation is illustrated in \figref{fig:lrmhinf:vibration-isolation:traditional}.
+If the controller $C$ is removed, the set-up reduces to a passive isolation system where the suspension is to be designed such that the payload velocity $y=v_z$ is influenced as little as possible by both the internal disturbances ($F_{\mathrm{d(pl)}}$) and the external disturbances ($F_{\mathrm{d(pl)}}$).
+To suppress $F_{\mathrm{d(ext)}}$, a compliant suspension is required such that the payload and the floor are decoupled.
+However, to enable suppression of the system disturbances $F_{\mathrm{d(pl)}}$, a stiff suspension is desirable to minimize the deflection of the payload~\citep{Voorhoeve2015SYSID}.
+This obviously leads to a trade-off in the design.
+In active vibration isolation, measurements of the position, velocity and even acceleration of the payload allow more freedom in tuning the suspension of the payload.
+Typically, the controller $C$ acts as an additional damping term.
+However, when such measurements are relative to the floor or other objects which are subject to the external disturbances $F_{\mathrm{d(ext)}}$ themselves, the trade-off for passive vibration isolation remains applicable.
+
+On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
+Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,Vandermaas2011MSc}.
+In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.
+By observing the relative movement of the inertial mass and the payload, the absolute velocity of the payload can be measured~\citep{Collette2011}.
+Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $F_{\mathrm{d(ext)}}$ for an ideal sensor.
+Consequently, the trade-off that exists in passive isolation is no longer relevant.
+A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $F_{\mathrm{d(pl)}}$ is suppressed.
+
+The particular \gls{AVIS} used for the experiments, consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}) providing passive vibration isolation.
+The payload platform is able to move in six mechanical degrees of freedom.
+Six geophones measure the payload velocity in an inertial reference frame, hence providing absolute velocity measurements, and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform using the principle of `sky-hook damping'.
+Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up, placement of the sensor and the signal processing involved.
+To facilitate the presentation, only the vertical translative velocity ($v_z$), i.e. a \gls{SISO} system, is considered.
+
+\begin{figure}
+  \centering
+  \setlength\figurewidth{0.75\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
+  \caption{\Glsentryfirst{AVIS}.}
+  \label{fig:lrmhinf:avis}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.475\columnwidth}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
+  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
+  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
+  The left photo shows one of the air mounts providing passive vibration isolation.
+  The right photo shows two linear motors that play a role in the active vibration isolation.}
+  \label{fig:lrmhinf:avis:details}
+\end{figure}
 
@@
 To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
-These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
-
+These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
+%TODO{formules Hansen schema}
 In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
@@
 Some dynamics are left unmodeled and are hence part of $\Delta$~(\figref{fig:lrmhinf:avisMeas}).
-
-\begin{figure}
-  \centering
-  \setlength\figurewidth{0.75\columnwidth}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
-  \caption{\Glsentryfirst{AVIS}.}
-  \label{fig:lrmhinf:avis}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.475\columnwidth}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
-  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
-  The left photo shows one of the air mounts providing passive vibration isolation.
-  The right photo shows two linear motors that play a role in the active vibration isolation.}
-  \label{fig:lrmhinf:avis:details}
-\end{figure}
 

### 2016-04-05 ch04-lrmhinf/lrmhinf.tex
Small stuff in CH04:

@@
 In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
-  If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
-  When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
+  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
+  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
   }
@@
 On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
-Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,Vandermaas2011MSc}.
+Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,vanderMaas2011MSc}.
 In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.

### 2016-04-05 ch04-lrmhinf/ch04appendices.inc.tex
Add photo details of AVIS
Fix some captions

--- 2016-04-03 ch04-lrmhinf/ch04appendices.inc.tex
@@
   \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
-  \caption{Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
+  \caption[\Simulink model used on the \glsentrytext{AVIS}]{\Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
   \label{fig:avis:simulink:setup}
@@
   \includegraphics{\thisDir/figs/avis-with-axes.pdf}
-  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
+  \caption[\glsentrytext{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
 For each of the actuators and sensors, the color indicates the principal direction.}
@@
   \begin{cases}
-     x[n+1] &= A x[n] + B u_c\\
-       y_c    &= C x + D u_c 
+     x[n+1] &= A x[n] + B u_c[n]\\
+       y_c[n]   &= C x[n] + D u_c[n] 
   \end{cases}\\
@@
 \input{\thisDir/figs/avis-setup-filters.tikz}
-\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
+\caption[\glsentrytext{AVIS} controller and filters]{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
 \label{fig:avis:bodeplots:controllerAndSensor}
@@
   \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
-  \caption{Simulink model of the AVIS sub-block.}
+  \caption{\Simulink model of the \glsentrytext{AVIS} sub-block.}
   \label{fig:avis:simulink:avis}

### 2016-04-07 ch02-qlogms/excitation-design.tex
LPM illustration improved
Externalize some frequency grids
 - also computed alpha, delta for example grid.

@@
 \end{align}
-which yields
+which evaluates to
 \begin{equation}
@@
     \centering
+      \remakeNextFigure
       \setlength\figurewidth{0.8\columnwidth}
@@
     \input{\thisDir/figs/freqGrid.tikz}
-    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
+    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.
+    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions. }%
     \label{fig:excitation:freqGrids}
@@
   The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e.
-$\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
+$\RightOpenInterval{\omegaLinLog, +\infty}$, where
+  \begin{equation}
+    \omegaLinLog \isdef \frac{2\pi \Delta f}{\alpha - 1}
+    \label{eq:excitation:linearLogTransitionFrequency}
+  \end{equation}
+  indicates the lowest frequency where the quasi-logarithmic grid can effectively reproduce the logarithmic spacing.
   In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when

### 2016-04-07 ch02-qlogms/code/loadGrids.m

@@ -1,0 +1,80 @@
+ccc;
+
+asCell = {'UniformOutput', false};
+
+directory = fullfile('..','data','freqGrid');
+output    = @(v) strrep(v, 'freqGrid','gridProps');
+
+files     = dir(fullfile(directory,'*.tsv'));
+files     = arrayfun(@(fn) fullfile(directory, fn.name), files, asCell{:});
+data      = cellfun(@loadFile, files, asCell{:});
+
+dataFunc = @(f) (@(data) feval(f, data.X, data.Y));
+
+doSave = false;
+
+%% compute power per signal
+P = NaN(size(files));
+N = NaN(size(files));
+scale = NaN(size(files));
+for iFile = 1:numel(files)
+    D = data{iFile};
+    region = D.X <= 1016;
+    power = @(Ak) sum(Ak.^2)/numel(Ak);
+    
+    P(iFile) = power(D.Y(region));
+    N(iFile) = numel(D.Y(region));
+    scale(iFile) = sqrt(150)./sqrt(P(iFile));
+    Ysc = D.Y * scale(iFile);
+    Psc = power(Ysc(region));
+%     fprintf('%30s\t N = %g \t P = %g \t (scale = %g, Psc = %g)\n', ...
+%            files{iFile}, N(iFile), P(iFile), scale(iFile), Psc);
+end
+
+%% compute frequency spacing and ratio
+computeDelta = @(f) reshape(diff([f(1);f(:)]), size(f));
+computeAlpha = @(f) 10.^(computeDelta(log10(f)));
+
+for iFile = 1:numel(files)
+    D = data{iFile};
+    D.deltaF = computeDelta(D.X);
+    D.alphaF = computeAlpha(D.X);
+    data{iFile} = D;
+end
+
+%% amplitude plot
+figure;
+hold all;
+for iFile = 1:numel(files)
+    D = data{iFile};
+    region = D.X <= 1016;
+    stem(D.X(region), D.Y(region)*scale(iFile)/sqrt(nnz(region)), 'DisplayName', files{iFile})
+end
+
+legend('show','Location','NorthEast')
+set(gca,'XScale','log');
+
+%% 
+figure('Name','Grid properties');
+for iFile = 1:numel(files)
+    D = data{iFile};
+    hAx(1) = subplot(1,2,1); hold all; xlabel('Frequency'); ylabel('\Delta_k f');
[…]

### 2016-04-07 code/ccc.m

@@ -1,0 +1,4 @@
+close all;
+clear variables;
+clear classes;
+clc;

### 2016-04-07 code/loadFile.m

@@ -1,0 +1,13 @@
+function [data]  = loadFile(filename)
+    data = importdata(filename);
+    data = struct('data', data);
+    data.X = data.data(:,1);
+    data.Y = data.data(:,2);
+    
+    data.nPoints = numel(data.X);
+    if size(data.data, 2) >= 3
+        sz = size(data.data);
+        warning('simplifyTsv:TooManyDimensions', ...
+                'File has dimensions %d x %d. Only 2D is handled!', sz(1), sz(2));
+    end
+end

### 2016-04-07 code/simplifyTsv.m

@@ -70,29 +70,14 @@ function new = simplifyTsv(filename, doSave, cleanfigureArgs)
         data = [new.X(:), new.Y(:)];
         fid = fopen(filename, 'w');
         closeFileAfterwards = onCleanup(@() fclose(fid));
-        
-        FF     = '%g';
-        COLSEP = '\t';
-        ROWSEP = '\n';
-        fprintf(fid, [FF COLSEP FF ROWSEP], data.');
+
+        fprintf(fid, printMatrix(data, ...
+                                 'floatFormat','%g', ...
+                                 'columnSep','\t', ...
+                                 'rowSep','\n'));
     end
     
 end
-
 function N = nPoints(data)
     N = numel(data.X);
-end
-
-function [data]  = loadFile(filename)
-    data = importdata(filename);
-    data = struct('data', data);
-    data.X = data.data(:,1);
-    data.Y = data.data(:,2);
-    
-    data.nPoints = numel(data.X);
-    if size(data.data, 2) >= 3
-        sz = size(data.data);
-        warning('simplifyTsv:TooManyDimensions', ...
-                'File has dimensions %d x %d. Only 2D is handled!', sz(1), sz(2));
-    end
 end

### 2016-04-07 ch02-qlogms/excitation-design.tex
Plots with grid summaries

@@
     \centering
-      \remakeNextFigure
       \setlength\figurewidth{0.8\columnwidth}
@@
   \centering
+  \label{tbl:excitation:gridProperties}
    \caption{Summary of  properties of the different frequency grids.}
@@
 
-  \TODO{plot: $\alpha $ (evt. $\cdot A_k^2$) i.f.v. $\omega$ voor verschillende signalen.}
-  \TODO{plot: $\Delta f $ i.f.v. $\omega$ voor verschillende signalen} 
-  \TODO{plot: $\# \omega / \mathrm{decade}$ i.f.v. $\omega$ voor verschillende signalen}
+  \begin{figure}
+    \centering
+    \setlength\figurewidth{0.85\columnwidth}
+    \setlength\figureheight{0.68\figurewidth}
+    \input{\thisDir/figs/gridProps.tikz}
+    \caption[Actual frequency grid spacing and ratio for different grids]{Actual frequency grid spacing $\Delta f_k$ and ratio $\alpha_k$ as a function of the frequency, for the different grid types with $f_0 =1\unit{Hz}$, $\Delta f = 1\unit{Hz}$ and $\alpha =1.05$ as in \figref{fig:excitation:freqGrids}.
+$\omegaLinLog$ marks the transition between linear and logarithmic regime in the quasi-logarithmic grid.}
+    \label{fig:excitation:gridPropertyPlots}
+  \end{figure}
 
@@
   The amplitudes of the compensated and pink quasi-log lines show that the compensation only has effect at the lower frequencies since the uncompensated counterpart has an amplitude spectrum close to $1$.
+  The properties of these frequency grids are summarized in \tabref{tbl:excitation:gridProperties} and \figref{fig:excitation:gridPropertyPlots}.
+
   We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.

### 2016-04-07 ch02-qlogms/code/loadGrids.m

@@ -32,7 +32,7 @@ for iFile = 1:numel(files)
 end
 
 %% compute frequency spacing and ratio
-computeDelta = @(f) reshape(diff([f(1);f(:)]), size(f));
+computeDelta = @(f) reshape(diff([f(:);f(end)]), size(f));
 computeAlpha = @(f) 10.^(computeDelta(log10(f)));
 
 for iFile = 1:numel(files)

### 2016-04-08 ch02-qlogms/excitation-design.tex
Improve coupling figure

@@
 
-This results extends mutatis mutandis to systems consisting of more sub-systems.
+This results extends \latin{mutatis mutandis} to systems consisting of more sub-systems.
 
@@
 \caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
-         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
+         The different plots are for different separations of the resonance frequencies, from $4\wdB$ to $64\wdB$.
          The arrow indicates the direction of increasing separation.}

### 2016-04-08 config/styles.inc.tex
Externalize some frequency grids
 - also computed alpha, delta for example grid.
Plots with grid summaries
Improve coupling figure

@@
 
-%TODO: avoid duplicated styles !!
+% style to plot only every Nth point (1st, N+1st, ...)
+% use as: `mark repeat=N`
+% http://tex.stackexchange.com/questions/116690/pgfplots-marks-mandatory-for-1st-and-last-point
+\pgfplotsset{
+    mark repeat*/.style={
+        scatter,
+        scatter src=x,
+        scatter/@pre marker code/.code={
+            \pgfmathtruncatemacro\usemark{
+                or(mod(\coordindex,#1)==0, (\coordindex==(\numcoords-1))
+            }
+            \ifnum\usemark=0
+                \pgfplotsset{mark=none}
+            \fi
+        },
+        scatter/@post marker code/.code={}
+    }
+}
 
@@
 
-\pgfplotsset{gridline/.style={ycomb,solid,line width=0.7pt,mark size=1pt}}
+\pgfplotsset{gridline/.style={ycomb,solid,line width=0.7pt,mark size=1pt},line legend}
 \pgfplotsset{biggrid/.style={ycomb,solid,line width=1pt,mark size=1pt}}
@@
 \pgfplotsset{linmsconnect/.style={color=linms,connectline,linmsmarker}}
+\pgfplotsset{logmsconnect/.style={color=logms,connectline,logmsmarker}}
 \pgfplotsset{qlogmsconnect/.style={color=qlogms,connectline,qlogmsmarker}}

### 2016-04-09 ch02-qlogms/excitation-design.tex
Place definition of 3dB BW
Externalize data in {alpha,beta}WC

@@
 \end{align*}
-With this input spectrum, the power inside $\wdB$ is
+With this input spectrum, the power inside $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$ is
 \begin{align}
@@
 
-  \begin{figure}[pht]
+  \begin{figure}
     \centering
-      \setlength\figurewidth{0.63\columnwidth}
+      \setlength\figurewidth{0.75\columnwidth}
       \setlength\figureheight{0.68\figurewidth}
@@
     \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
-             grid multisines and systems with different peak amplitudes.
-             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
+             grid multisines and systems with different peak amplitudes.}
     \label{fig:excitation:worstCaseAlpha}

### 2016-04-10 ch05-initvals/initial-values.tex
Fix some inconsistencies

@@
   \isdef 
-  \norm{\model{\bullet} - G_{\mathrm{VXI}}}
+  \norm[2]{\model{\bullet} - G_{\mathrm{VXI}}}
   \text{.}
@@
   \centering
-  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
+  \caption{Observed percentiles of the validation distance $\norm[2]{\model{\bullet}-G_{\mathrm{VXI}}}$.}
   \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
@@
   Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
-  Both latter methods often produce models that perform poorly compared to $\| G_{VXI} \|$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
+  Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\mathrm{VXI}} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
   This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}

### 2016-04-10 code/coordinatesToTable.m
Code: externalize TikZ data

@@ -1,0 +1,27 @@
+function [ str ] = coordinatesToTable( str )
+    % Converts Tikz coordinates to table
+    
+    BEGINTOKEN = 'coordinates{';
+    ENDTOKEN   = '}';
+    
+    parts = extractDataSegments(str, BEGINTOKEN, ENDTOKEN);
+    
+    %% replace data segments with tables
+    nDataSegments = size(parts,1)-1;
+
+    for iData = 1:nDataSegments
+        dataStr = parts{iData,2};
+        
+        EOL = sprintf('\n');
+        dataStr = regexprep(dataStr,'\s|\n','');
+        dataStr = strrep(dataStr,sprintf(','),sprintf('\t'));
+        dataStr = strrep(dataStr,'(','');
+        dataStr = strrep(dataStr,')',['\\' EOL]);
+        dataStr = strrep(dataStr, BEGINTOKEN, ['table[row sep=crcr]{' EOL]);
+        
+        parts{iData,2} = dataStr;
+    end
+    
+    str = strjoin(parts','');
+end
+

### 2016-04-10 code/externalizeTables.m

@@ -1,0 +1,75 @@
+function str = externalizeTables(str, datafile, datapath, flag)
+    if ~exist('flag','var')
+        flag = '';
+    end
+    dryrun = strcmpi(flag, 'dryrun');
+    
+    BEGINTOKEN = 'table[';
+    ENDTOKEN   = '}';
+    
+    parts = extractDataSegments(str, BEGINTOKEN, ENDTOKEN);
+    
+    nSegments = size(parts,1)-1;
+    cntExternalFiles = 0;
+    for iSegment = 1:nSegments
+        origDataStr = parts{iSegment,2};
+        if ~isInline(origDataStr)
+            continue; % don't externalize when the data is already external
+        end
+                
+        dataStr = strrep(origDataStr,'\\','');
+        dataStr = regexprep(dataStr,'row sep\s*=\s*crcr\s*','');
+        dataStr = strrep(dataStr,',,',','); % remove superfluous commas
+        dataStr = strrep(dataStr,'[,','[');
+        
+        %% make file names
+        cntExternalFiles = cntExternalFiles + 1;
+        fname = datafile(cntExternalFiles, parts{iSegment,1});
+        fpath = datapath(cntExternalFiles, parts{iSegment,1});
+        
+        %% extract data/spec part
+        idxDataStart = strfind(dataStr,'{')+1;
+        idxDataStop  = strfind(dataStr,'}')-1;
+        
+        data = dataStr(idxDataStart:idxDataStop);
+        spec = [ dataStr(1:idxDataStart) fpath dataStr((idxDataStop+1):end) ];
+        
+        %% clean up data further
+        data = regexprep(data, '^\s+', ''); % remove heading spaces
+        
+        %% clean up spec further
+        EOL = sprintf('\n');
+        spec = strrep(spec,EOL,'');
+        spec = strrep(spec,'%','');
+        
+        %% save output
+        outputFile(fname, data, dryrun)
+        
+        parts{iSegment,2} = spec;
+    end
+    
+    str = strjoin(parts','');    
+end
+function bool = isInline(data)
+    bool = ~isempty(strfind(data, '\\'));
+end
+function outputFile(filename, data, dryrun)
+    switch dryrun
+        case true
+            msg = '(not really)';
+        case false
+            msg = '';
+    end
+    fprintf('Writing to data file "%s"...%s\n', filename, msg)
+    
+    if ~dryrun
+        dataDir = fileparts(filename);
[…]

### 2016-04-10 code/extractDataSegments.m

@@ -1,0 +1,38 @@
+function [ parts ] = extractDataSegments( str , BEGINTOKEN, ENDTOKEN)
+    %EXTRACTDATASEGMENTS splits a string into segments separated by TOKENS
+    %
+    % The second column are the data segments (in-between the tokens)
+    % The first column is everything else
+    
+    idxStart   = strfind(str,BEGINTOKEN);
+    idxStopAll = strfind(str,ENDTOKEN);
+    
+    
+    [idxStart, idxStop] = findDataSegments(idxStart, idxStopAll);
+    idx = makeIndexRanges(idxStart, idxStop, numel(ENDTOKEN), numel(str));
+    
+    parts = cellfun(@(idx) str(idx), idx, 'Un', false);
+end
+
+
+function [idxStart, idxStop] = findDataSegments(idxStart, idxStopAll)
+    % find first occurrence of END token after each BEGIN token
+    idxStop = idxStart;
+    for iPart = 1:numel(idxStart);
+        idxStop(iPart) = idxStopAll(find(idxStopAll>idxStart(iPart), 1));
+    end
+end
+function idx = makeIndexRanges(idxStart, idxStop, nEnd, totalLength)
+    nDataSegments = numel(idxStart);
+    idx = cell(nDataSegments+1,2);
+    
+    idx1Start = [1 idxStop+nEnd+1];
+    idx1Stop  = [idxStart-1 totalLength];
+    
+    EMPTY     = totalLength;
+    idx2Start = [idxStart EMPTY+1];
+    idx2Stop  = [idxStop+nEnd EMPTY];
+    
+    idx(:,1) = arrayfun(@(a,b) a:b, idx1Start, idx1Stop, 'UniformOutput', false)';
+    idx(:,2) = arrayfun(@(a,b) a:b, idx2Start, idx2Stop, 'UniformOutput', false)';
+end

### 2016-04-10 code/processTikzFile.m

@@ -1,0 +1,36 @@
+function [ str ] = processTikzFile( filename , isInteractive)
+    %PROCESSTIKZFILE Summary of this function goes here
+    %   Detailed explanation goes here
+    
+    if ~exist('isInteractive','var')
+        isInteractive = true;
+    end
+    
+    str = fileread(filename);
+    [pathPart, namePart, ext] = fileparts(filename);
+    basename ='';
+    str = coordinatesToTable(str);
+    
+    str = externalizeTables(str, @dataFile, @relativeDataPath);
+    
+    % write out file
+    fid = fopen(filename,'w');
+    fprintf(fid,'%s',str);
+    fclose(fid);
+    
+    %% subfunctions
+    function str = dataFile(idx, prevPart)
+        if isInteractive
+            fprintf(2,'%s\n',prevPart);
+            basename = input('What filename do you want for this data?','s');
+        else
+            basename = sprintf('dat%03d.tsv',idx);
+        end
+        str= fullfile(pathPart,'..','data',namePart,basename);
+    end
+    function str = relativeDataPath(idx, prevPart)
+        str =  sprintf('\\thisDir/data/%s/%s',namePart, basename);
+    end
+end
+
+

### 2016-04-11 ch04-lrmhinf/ch04appendices.inc.tex
First corrections of Johan (CH04)

@@
 \label{app:avis-setup}
-The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.
+The measurements of the \gls{AVIS} are carried out using a \Simulink model that configures the \gls{DAQ} card, implements a digital controller and provides some basic signal processing.
+\Simulink executes the code, as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis},  using a constant time step $\Ts = 1\unit{ms}$ on a real-time computer equipped with \code{xPC Target} (nowadays: \Simulink Real-Time).
 
@@
   \caption[\glsentrytext{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners.
-For each of the actuators and sensors, the color indicates the principal direction.}
+For each of the actuators and sensors, the color indicates the principal direction (x:red, y:green, z:blue).}
   \label{fig:avis:withAxes}

### 2016-04-11 ch04-lrmhinf/lrmhinf.tex
TODO: colormatch avis photos
Shift hue in one of the AVIS pics
Externalize some frequency grids
 - also computed alpha, delta for example grid.
First corrections of Johan (CH04)

@@
 In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
-The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.
+The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of a system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.
 
@@
 The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
-The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM} \citep{Schoukens2009LPM} and \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
 Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
@@
 \end{equation}
-In robust control design methodologies, such \Hinf{} norms often play an important purpose to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.
+In robust control design methodologies, such \Hinf{} norms often play an important role to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.
 
@@
 \end{equation}
-However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
+However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid $, i.e.
+$\DFTGrid \isdef{\omega_1, \omega_2, \ldots, \omega_{N-1}}$.
 As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
-\begin{align}
-  \gamma &\isdef 
+\begin{equation}
+  \gamma \isdef 
     \sup_{\omega} 
@@
                 }
-  \label{eq:lrmhinf:gamma-split-grid}\\
+  \label{eq:lrmhinf:gamma-split-grid}
+  \text{.}
+\end{equation}
+For convenience, we extract both contributions above as:
+\begin{align}
   \gammaAtGrid & \isdef 
@@
 \subsection{Set-up}
-Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
+Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
 For an infinitely long data record, this can be described in the time-domain as
@@
 \end{equation}
+The $T_{\Delta}$ contribution models the difference between the begin and end conditions of the filters $\Delta$ and $H$ in the measurement~\citep{Pintelon1997ARB}.
 The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.
@@
 \label{sec:lrmhinf:LRM}
+\TODO{remove whole LRM section in favor for \chapref{sec:nonparametric}}
 The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
@@
 By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
+\TODO{formules}
 In this chapter a Hann window and $N_S=1$ are used.
@@
 \subsection{Study of the experiment length}
-Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
+The frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
 In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.
 
-We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
+We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $2\tau=100$ samples to randomize the initial conditions.
 To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
@@
   \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
-  \caption{Conceptual illustration of (active) vibration isolation set-ups.
+  \caption[Vibration isolation set-ups (traditional, sky-hook dampinng)]{Conceptual illustration of (active) vibration isolation set-ups.
 In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
@@
 \label{sec:lrmhinf:conclusion}
-A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
+A reliable local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
 In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.

### 2016-04-11 ch04-lrmhinf/lrmhinf.tex
More corrections from Johan

@@
 To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
-It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
+It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when the distance $\abs{\omega_k-\omega}$ is small.
+As the local models are each constructed around the frequency $\omega_k$, for an arbitrary $\omega \in \Omega$, one can find two adjacent frequencies around which such local models are available.
 To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
@@
 \label{sec:lrmhinf:LRM}
-\TODO{remove whole LRM section in favor for \chapref{sec:nonparametric}}
+
+\disclaimer{
+The \gls{LRM} and \gls{LPM} are described in \chapref{sec:nonparametric} and \citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} in more detail.
+Below, we give briefly re-iterate some pertinent aspects and notations.
+}
+
 The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
@@
  around each bin $k$ can be constructed.
+
 We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
 For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.
-
-For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} and \chapref{sec:nonparametric}.
 
@@
 The \gls{LPM}, on the other hand, does not provide a reliable estimate.
-This behavior is related to the Runge phenomenon~\citep{Runge1901}.
 

### 2016-04-11 ch04-lrmhinf/ch04appendices.inc.tex
Add figure to illustrate SNR

--- 2016-04-05 ch04-lrmhinf/ch04appendices.inc.tex
@@
 \label{app:avis-setup}
-The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.
+The measurements of the \gls{AVIS} are carried out using a \Simulink model that configures the \gls{DAQ} card, implements a digital controller and processes the signals.
+\Simulink executes the code, as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis},  using a constant time step $\Ts = 1\unit{ms}$ on a real-time computer running \code{xPC Target} (nowadays: \Simulink Real-Time) equiped with a Quanser Q8 \gls{DAQ} card that is connected to the physical \gls{AVIS} setup.
 

### 2016-04-11 ch04-lrmhinf/lrmhinf.tex
Add figure to illustrate SNR

@@
 The \gls{LRM} and \gls{LPM} are described in \chapref{sec:nonparametric} and \citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} in more detail.
-Below, we give briefly re-iterate some pertinent aspects and notations.
+Below, we briefly re-iterate some pertinent aspects and notations.
 }
@@
 
-\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
+\begin{guideline}[Measure $4$ to $5\timeconst\,$ to observe its peak value using the local models]
+\begin{minipage}{0.725\textwidth}
 After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
 For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
+\end{minipage}
+\hfill
+\begin{minipage}{0.25\textwidth}
+\setlength\figurewidth{\columnwidth}
+\setlength\figureheight{0.618\figurewidth}
+\input{\thisDir/figs/sketch-SNR.tikz}
+\end{minipage}
 \end{guideline}

### 2016-04-11 ch04-lrmhinf/code/plotAvis.m

@@ -27,7 +27,7 @@ w = logspace(log10(0.001), log10(fNyquist), nPoints);
 %% static transformations
 Kact  = avis.actuator.polarity * avis.actuator.matrix;
 Ksens = avis.sensor.matrix * avis.sensor.polarity;
-tabOpts = {'floatFormat', ff, 'col', ' & ', 'row', '\\\\\n'};
+tabOpts = {'floatFormat', '%g', 'col', ' & ', 'row', '\\\\\n'};
 printMatrix(Kact, tabOpts{:} )
 printMatrix(Ksens, tabOpts{:} )
 %% plots

### 2016-04-11 ch04-lrmhinf/code/plot_sketch_SNR.m

@@ -1,0 +1,38 @@
+addpath(fullfile(pwd, '..','..','code'));
+ccc;
+
+doSave = false;
+
+G0 = tf([1],[1 0.5 1]);
+scale = norm(G0,Inf);
+G0 = G0/scale;
+SP = SamplingProp('N',512,'Ts',1);
+
+U     = ones(size(SP.w));
+Y     = squeeze(freqresp(G0,SP.w));
+
+noise = randn(size(SP.t))*0.001/scale;
+Noise = fft(noise);
+
+figure;
+hold all;
+plot(SP.w_pos, db(Y(SP.sel_pos)), '.-',...
+     'DisplayName' ,'System', 'LineWidth',2,'Color','k');
+plot(SP.w_pos, db(Noise(SP.sel_pos)),...
+     '.:','DisplayName','Noise','MarkerSize',8,...
+     'Color',[0.5 0.5 0.5]);
+
+if doSave
+    dataPath = fullfile('..','data','sketch-SNR');
+    if ~exist(dataPath, 'dir')
+        mkdir(dataPath);
+    end
+    matlab2tikz(fullfile('..','figs','sketch-SNR.tikz'), ...
+                'width','\figurewidth',...
+                'height','\figureheight',...
+                'standalone',false,...
+                'externalData',true,...
+                'dataPath', dataPath,...
+                'relativeDataPath', strrep(dataPath, '..','\thisDir'));
+end
+    

### 2016-04-11 code/Codegeneratable.m

@@ -1,0 +1,10 @@
+classdef(HandleCompatible,Abstract) Codegeneratable
+    % CODEGENERATABLE interface that allows to generate code for this
+    % item.
+    methods(Abstract)
+        % function [str, tag, cind] = gencode(item, tag, ctagx)
+        [str, sts] = gencode_rvalue(item)
+        % function [str] = gencode_substruct(subs, name)
+    end
+end
+

### 2016-04-11 code/Describable.m

@@ -1,0 +1,27 @@
+classdef(HandleCompatible,Abstract) Describable
+    %DESCRIBABLE Class with a description (describe method)
+
+    methods(Abstract,Access=protected)
+        str = describe_(obj)
+    end
+
+    methods(Sealed)
+        function str = describe(obj)
+            % DESCRIBE description of the object
+            %
+            % Usage:
+            %  str = describe(obj)
+            %  describe(obj)
+            %
+            % When no output argument is provided, the description is
+            % displayed in the console.
+            str = describe_(obj);
+            if nargout == 0
+                disp(str);
+                clear('str');
+            end
+        end
+    end
+
+end
+

### 2016-04-11 code/SamplingProp.m

@@ -1,0 +1,357 @@
+classdef SamplingProp < handle & Describable & WithUserData & Codegeneratable
+    %SAMPLINGPROP Properties of equidistant time sampling
+    %
+    % This object tracks basic properties for equidistant time/frequency
+    % sampling. All scalar properties can be set by the user, the other
+    % properties will be adapted accordingly. The vector properties
+    % can also be set, but are coerced into a format that is compatible
+    % with the internal storage. I.e. when t is set, a number of samples N
+    % and mean time step dt are extracted, but the exact time instance are
+    % not enforced. For non-equidistant sampling, this can result in
+    % significant errors (for which a heuristic warning will be shown).
+    %
+    % The properties are based on two fundamental properties: 
+    %   - the sampling time    : Ts_ (stored in Ts__) 
+    %   - the number of samples: N_ (stored in N__)
+    % 
+    % The relationships that are enforced by this object are:
+    %  Tm = N * Ts
+    %  fs = 1 / Ts
+    %  dt = Ts
+    %  df = 1 / Tm = 1 / ( N * Ts )
+    %  t  = n * Ts
+    %  w  = 2 * pi * f
+    %  k  = 0:N-1 (frequency index)
+    %  n  = 0:N-1 (time index)
+    %  wn = 2*pi*k/N
+    %
+    % Some of these properties (e.g. the measurement time Tm) depend on
+    % both Ts_ and N_. When such properties are set, either N_ or Ts_ has
+    % to be adapted to fulfill all relations. This is done by keeping track
+    % of which basic property has been set the last (stored in
+    % lastProperty_). The last set property is considered fixed for the
+    % calculation. So when N has been set, and Tm is set afterwards, this
+    % will be done by changing Ts.
+    
+    %% Dependent properties
+    properties(Dependent)
+        % resolution
+        dt % [s] sampling time
+        df % [Hz] frequency resolution
+        dw % [rad/s] pulsation resolution
+        % range
+        fs % [Hz] sampling frequency
+        ws % [rad/s] sampling pulsation
+        N  % [] number of samples
+        Tm % [s] measurement time
+        % time axis
+        n  % [] time index
+        t  % [s] physical time
+        % frequency axis
+        k  % [] frequency index
+        w  % [rad/s] pulsation
+        wn % [rad] normalized pulsation
+        f  % [Hz] frequency
+        w_pos % [rad/s] negative frequency axis
+        f_pos % [Hz] positive frequency axis
+        sel_pos % [] logical array indicating positive frequency spectrum
[…]

### 2016-04-11 code/WithUserData.m

@@ -1,0 +1,6 @@
+classdef(HandleCompatible) WithUserData
+    %WITHUSERDATA Class with userData field
+    properties(Hidden)
+        UserData;
+    end
+end

### 2016-04-12 ch02-qlogms/excitation-design.tex
Fix some inconsistencies
Externalized lots of data files in CH02
Fix references in Ch02

@@
 
-Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing~\citep{GarciaLopez2014,DAmico2014} amongst others.
+Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances \citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy \citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics \citep{Munir2011}, mechatronics \citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing \citep{GarciaLopez2014,DAmico2014} amongst others.
 
@@
   As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
-  %TODO: mention crest factor? (here compensation/pink hurts)
 
@@
   \begin{equation} 
-    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
+    \omegaLinLog =\frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
     \text{.}

### 2016-04-13 ch04-lrmhinf/ch04appendices.inc.tex
Some comments from Adam and Tom

@@
 Hence, the experimental controller ($\experimental\Controller_{\mathrm{benchmark}} = 0$),the saturations, the filter $F$ and the static matrices $K$ are different.
-Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) thanks to an upgrade of the real-time computer responsible for acquiring the signals.
+Moreover, the sample rate of the benchmark data is much higher ($\fs  = 20 \unit{kHz}$) compared to the data in this work ($\fs = 1\unit{kHz}$) after an upgrade of the real-time computer responsible for acquiring the signals.
 \end{remark}

### 2016-04-13 ch04-lrmhinf/lrmhinf.tex
Some comments from Adam and Tom

@@
-\chapter{Non-parametric Resonance Peak Modeling}
+\chapter{Non-parametric Peak Modeling}
 \label{sec:hinf}
@@
 For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
-However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
+Recent trends in many disciplines have produced increasingly complicated systems.
+Consequently, building a full-complexity model rapidly becomes disproportionately expensive for a required model fidelity.
 Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
@@
 Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
-Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
-In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
-In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
+Third, non-parametric identification approaches have been adopted~\citep[][see e.g.]{vandeWal2002,deVries1994}. 
+In~\citet{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
+In~\citet{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
 However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
-Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
-These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
-A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
+Fourth, recently a data-driven \Hinf{} norm estimation has been developed in \citet{Wahlberg2010,Oomen2014ILH}.
+These methods rely on a sequence of iterative experiments and directly deliver an estimate of the \Hinf{} norm, and combine an optimal experiment design while essentially taking inter-grid errors into account.
+A recent application of this method in \citet{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
 Unfortunately, these methods require a sequence of dedicated iterative experiments.
@@
 The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
-The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
+The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citet{Geerardyn2014IFAC,Geerardyn2014ISMA}.
 Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
@@
 The problem is formulated in \secref{sec:lrmhinf:Problem}.
-In \secref{sec:lrmhinf:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
+In \secref{sec:lrmhinf:LPMHinf} the proposed method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
 In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
@@
 Two use cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters from data.
-In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e.
-by replacing $\svdMax{\Delta}$ with $\svdMax{W \Delta V}$ in the formulas.
-The other case is discussed in Remark~\ref{rem:lrmhinf:constructWeights} further on.
+In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e., by replacing $\svdMax{\Delta}$ with $\svdMax{W \Delta V}$ in the formulas.
+The other case is explained in Remark~\ref{rem:lrmhinf:constructWeights}.
 \end{remark}
@@
 \end{equation}
-However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid $, i.e.
+If the measurement time is finite, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid $, i.e.
 $\DFTGrid \isdef{\omega_1, \omega_2, \ldots, \omega_{N-1}}$.
+Typically, this discrete grid is the frequency grid of the \gls{DFT}.
 As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
@@
 \end{enumerate}
-The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
-Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
-Such an underestimate may lead to overly optimistic controller designs.
 
-The main contribution of this chapter is to  estimate the inter-grid term $\gammaIntergrid$ without the need for a (global) parametric model.
-Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.
+The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citet{vandeWal2002}.
+However, the expected value of  $\gamma_{\mathrm{FRF}}$  for different realizations of the input signal and noise for a fixed measurement time, underestimates the actual peak gain $\gamma$, i.e.
+$\expectedValue{\gammaAtGrid} \leq \gamma$.
+This is due to the limited frequency resolution imposed by the measurement time: the frequency where the actual peak gain occurs might not coincide with the excited frequency grid.
+Such an underestimate of $\gamma$ leads to overly optimistic controller designs which in turn can cause unstable behavior of the plant.
+
+The main contribution of this chapter is to  estimate the inter-grid term $\gammaIntergrid$ without the need for a (global) parametric model or imposing worst-case prior knowledge that leads to conservatism.
+Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over a finite frequency range.
 
@@
 \end{equation}
-where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
+where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance such that $v(n) = H(q)e(n)$ can be colored noise, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
 For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
@@
 An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
-Two alternative methods allow evaluation of~\eqref{eq:lrmhinf:gamma-inter-grid} in practice.
 
@@
 
-\paragraph*{Direct method}
-One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
-Hence, it boils down to solving the optimization problems
-\begin{align}
-  \estimated{\gammaIntergrid}(k) & \isdef 
-      \sup_{\omega \in \Omega_k}
-      \svdMax{\LocalModel{\Delta}_k(\omega)}
-       \quad \forall k \in \Set{1,\ldots,N-1} 
-       \label{eq:lrmhinf:gamma-direct:optimizations}\\
-  \estimated {\gammaIntergrid} &= 
-  \max \Set{
-    \estimated{\gammaIntergrid}(k) 
-    | 
-    k \in \Set{1,\ldots,N-1}
-  }
-      \label{eq:lrmhinf:gamma-direct}
-\end{align}
-These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
-Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.
+Direct implementation of \eqref{eq:lrmhinf:gamma-inter-grid} allows a simple and efficient evaluation of $\gammaIntergrid$ that matches well to parallel computation frameworks such as \code{MapReduce}~\citep{Dean2008}.
+In particular, the inner $\sup_{\omega\in\Omega_k}$ can be understood as a \code{map} operation that maps a local model to its peak value and the outer $\sup$ is a \code{reduce} that only retains the global peak value given the peak value of each local model.
+Unfortunately, such an implementation offers no access to the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.
 
@@
 \end{equation}
-by retaining the largest both.
+by retaining the largest of both.
 It follows that
@@
 
-\paragraph*{Remarks:}
-The optimization problems~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct:optimizations} each amount to one-dimensional optimization problems, hence they be solved easily by griding the frequency $\omega$.
-The peak amplitudes obtained using~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
+\begin{remark}
+The construction of $ \svdMax{\Delta_{\LMM}(\omega)}$  makes it more involved to implement the interpolation approach in an efficient and/or parallel fashion.
+\end{remark}
+
+\begin{remark}
+The optimization problems \eqref{eq:lrmhinf:gammaInxterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
+The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
  \begin{equation}
@@
 In \figref{fig:lrmhinf:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
+\end{remark}
 
@@
 By normalizing the conclusions for the time constant $\timeconst$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\damping$.
-Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the natural frequency of the dominant pole.
+Specifically, the time constant $\timeconst \isdef (\damping \wn)^{-1}$ of the dominant pole dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the natural frequency of the dominant pole.
 
@@
   %\input{figures/runLength.tikz}
-  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
+  \caption[Estimated $\gamma$ versus measurement time.]{This Monte Carlo simulation shows that the $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
   However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
@@
 \begin{remark} \label{rem:lrmhinf:constructWeights}
-The construction of weighting filters $(W,V)$ for the design of a robust controller typically happens based on measurement data which is available non-parametrically, i.e.
-only available at a limited frequency grid.
-The goal of the filter design is to construct low-order minimum-phase filters that form a tight overbound of particular real-valued functions of the frequency.
-Concretely, such a real-valued function is often a singular value of e.g.
-the loop gain or one of the loop sensitivity functions~\citep{Boeren2013,Scheid1995,Bibel1992,Skogestad2005} such that the design entails practical control objectives (disturbance rejection, input tracking, \ldots).
-However, since such a function is only measured at a limited amount of frequency points, such overbounds can be hard to construct when resonances are present.
-E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but note in Section~IV that limited frequency resolution can hamper construction of these filters.
-The obvious solution to collect more densely-sampled data, is often not desirable (e.g. due to time constraints, limited access to the actual plant, cost of experimentation, \ldots).
-However, the method proposed  in this chapter can provide more densely-sampled view of the data without an increase in measurement time.
+In robust control design, often the interest is not only in determining the peak value of the uncertainty, but also in obtaining a tight overbound of the uncertainty, e.g. as in \citet{Scheid1995}.
+This is closely related to the design of (parametric) weighting filters $(W,V)$ such that $\abs{W \Delta V}$ is almost a constant function of the frequency in the frequency bands of interest for control design.
+Essentially, this is done to ensure that a synthesized robust controller is largely invariant under the choice of uncertainty structure chosen in the model set.
+
+The proposed local parametric approach can be extended straightforwardly to accommodate for this.
+In particular, the overbound of $\Delta$ can be generated for an arbitrarily dense frequency grid---i.e.
+this includes the inter-grid behavior--- such that the approach of \citet{Scheid1995} can be used directly.
 \end{remark}
 
-\begin{guideline}[Measure $4$ to $5\timeconst\,$ to observe its peak value using the local models]
+\begin{guideline}[Measure at least $5\timeconst\,$ to observe its peak value using the local models]
 \begin{minipage}{0.725\textwidth}
@@
 The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
-The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload (e.g.
-passengers in a car, sensitive equipment such as atomic force microscopes or wafer-scanners used for lithography) is not disturbed by vibrations generated by either the payload itself ($F_{\mathrm{d(pl)}}$) or by the outside world ($F_{\mathrm{d(pl)}}$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.
+The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload---e.g.
+passengers in a car, sensitive equipment such as atomic force microscopes and wafer-scanners used for lithography---is not disturbed by vibrations generated by either the payload itself ($\systemDisturbance$) or by the outside world ($\systemDisturbance$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.
 
@@
 The typical set-up for vibration isolation is illustrated in \figref{fig:lrmhinf:vibration-isolation:traditional}.
-If the controller $C$ is removed, the set-up reduces to a passive isolation system where the suspension is to be designed such that the payload velocity $y=v_z$ is influenced as little as possible by both the internal disturbances ($F_{\mathrm{d(pl)}}$) and the external disturbances ($F_{\mathrm{d(pl)}}$).
-To suppress $F_{\mathrm{d(ext)}}$, a compliant suspension is required such that the payload and the floor are decoupled.
-However, to enable suppression of the system disturbances $F_{\mathrm{d(pl)}}$, a stiff suspension is desirable to minimize the deflection of the payload~\citep{Voorhoeve2015SYSID}.
+If the controller $C$ is removed, the set-up reduces to a passive isolation system where the suspension is to be designed such that the payload velocity $y=v_z$ is influenced as little as possible by both the internal disturbances ($\systemDisturbance$) and the external disturbances ($\externalDisturbance$).
+To suppress $\externalDisturbance$, a compliant suspension is required such that the payload and the floor are decoupled.
+However, to enable suppression of the system disturbances $\systemDisturbance$, a stiff suspension is desirable to minimize the deflection of the payload~\citep{Voorhoeve2015SYSID}.
 This obviously leads to a trade-off in the design.
@@
 Typically, the controller $C$ acts as an additional damping term.
-However, when such measurements are relative to the floor or other objects which are subject to the external disturbances $F_{\mathrm{d(ext)}}$ themselves, the trade-off for passive vibration isolation remains applicable.
+However, when such measurements are relative to the floor or other objects which are subject to the external disturbances $\externalDisturbance$ themselves, the trade-off for passive vibration isolation remains applicable.
 
@@
 By observing the relative movement of the inertial mass and the payload, the absolute velocity of the payload can be measured~\citep{Collette2011}.
-Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $F_{\mathrm{d(ext)}}$ for an ideal sensor.
-Consequently, the trade-off that exists in passive isolation is no longer relevant.
-A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $F_{\mathrm{d(pl)}}$ is suppressed.
+Conceptually, the active controller $C$ can be seen as connected to an imaginary fixed point in the `sky' (\figref{fig:lrmhinf:vibration-isolation:skyhook}), which is not disturbed by $\externalDisturbance$ for an ideal sensor.
+Consequently, the trade-off that exists in passive isolation is eliminated.
+A compliant passive suspension can decouple the payload from external disturbances while the active controller acts as a stiff damper to the `sky' such that the effect $\systemDisturbance$ is suppressed.
 
@@
   \setlength\figurewidth{0.75\columnwidth}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
+  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}}
   \caption{\Glsentryfirst{AVIS}.}
@@
   \setlength{\figurewidth}{0.475\columnwidth}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
-  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
+  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}}
+  \hfill
+  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
+  %TODO: right figure is just a tad too small
   \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
@@
 %TODO{formules Hansen schema}
-In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies.
+In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.
 
@@
 \label{sec:lrmhinf:conclusion}
-A reliable local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
-In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
+A reliable local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is presented.
+In this chapter, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
 It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.

### 2016-04-13 ch04-lrmhinf/lrmhinf.tex
Comments CH04

@@
 
-For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
-Recent trends in many disciplines have produced increasingly complicated systems.
-Consequently, building a full-complexity model rapidly becomes disproportionately expensive for a required model fidelity.
-Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
+For mechatronic design and many other engineering disciplines it is important to obtain good  models that approximate the physical reality.
+Recent trends in many disciplines have led to increasingly complicated systems.
+Consequently, building a full-complexity parametric model rapidly becomes disproportionately expensive for a required model fidelity.
+Often, such parametric models are required to understand elementary properties of the system such as the resonance frequencies, damping of different poles, the maximal gain of the system.
 In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
-The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of a system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.
+The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system.
+This is a problem that is important in the design of robust controllers~\citep{Oomen2016} to characterize the effect of unmodeled dynamics in low-complexity models used for control.
+Such analysis allows one to verify that the eventually designed controller stabilizes the system.
 
@@
 If the measurement time is finite, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid $, i.e.
-$\DFTGrid \isdef{\omega_1, \omega_2, \ldots, \omega_{N-1}}$.
+$\DFTGrid \isdef \set{\omega_1, \omega_2, \ldots, \omega_{N-1}}$.
 Typically, this discrete grid is the frequency grid of the \gls{DFT}.
@@
 The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citet{vandeWal2002}.
-However, the expected value of  $\gamma_{\mathrm{FRF}}$  for different realizations of the input signal and noise for a fixed measurement time, underestimates the actual peak gain $\gamma$, i.e.
+However, when the measurement time is finite, the expected value of  $\gamma_{\mathrm{FRF}}$  for different realizations of the input signal and noise, may underestimate the actual peak gain $\gamma$, i.e.
 $\expectedValue{\gammaAtGrid} \leq \gamma$.
@@
 To estimate $\gammaIntergrid$, we propose to identify local parametric models in the frequency domain.
-The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} , \omega_{k+1} }$ in view of the local validity of the local models.
+The frequency axis is partitioned into continuous segments $\Omega_k \isdef \ClosedInterval{ \omega_{k-1} , \omega_{k+1} }$ in view of the local validity of the local models.
 In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
@@
 with the same notations as in \chapref{sec:excitation}, most importantly, each resonant pole can be characterized by its frequency $\wn[i]$ and damping $\damping[i]$.
-In the structural engineering community (see e.g.
-\citet[Chapter 2]{Gawronski2004}) it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function: the gray terms in the equation above are negligible such that only a single second-order term needs to be accounted for.
-As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g.
-mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
+In the structural engineering community\citep[Section 2.2.2][see e.g.{Gawronski2004} it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function.
+In many practical situations, this means that the gray terms in the equation often have a negligible influence.
+For local modeling, the response is hence well-approximated by only considering the poles and zeros in the local frequency window.
 To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest as those are responsible for large gains of the system.
@@
 of $10$ is obtained.
+%TODO: give the SNR also in frequency domain
 
 Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
-This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
-By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
-\TODO{formules}
-In this chapter a Hann window and $N_S=1$ are used.
-Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).
+This is done by first splitting the input and output signals ($u(n)$ and $y(n)$)  into $\nSegments$ segments of $N/\nSegments$ samples that we will denote as
+\begin{equation}
+  x^{[i]}(n) = x\left( (i-1) \nSegments + n \right) 
+  \text{ with }
+  n \in \set{0, \ldots N/\nSegments - 1}
+  \text{ and }
+  i \in \set{1, \ldots, \nSegments}
+  \text{.}
+  \label{eq:lrmhinf:SA:segmentation}
+\end{equation}
+Each of these segments is windowed using a function $w_{N/\nSegments}(n)$ to reduce leakage such that 
+\begin{equation}
+x^{[i]}_{w}(n) = x^{[i]}(n) \cdot w_{N/\nSegments}(n)
+\text{.}
+\end{equation}
+The frequency domain counterparts are obtained by means of the \gls{DFT}, and are denoted 
+\begin{equation}
+X^{[i]}_W(k) = \DFT(x^{[i]}_w(n))
+\text{,}
+\end{equation}
+where it should be noted that $k \in \set{0,N/\nSegments}$ such that the frequency resolution is $\frac{2\pi \nSegments}{N}$.
+By dividing the resulting auto- and cross-spectra, the \gls{FRF} of $\Delta$ can be estimated
+\begin{equation}
+  \hat{\Delta}_{\mathrm{SA}}(k) \isdef 
+  \frac{\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} Y_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
+           {\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} U_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
+  \
+\end{equation}
+In this chapter a Hann window ($w_{N/\nSegments}(n) = \sin^2 (\frac{\pi n}{N/\nSegments -1})$) and $\nSegments=1$ are used.
+Note that $\nSegments>1$  increases the measurement time by a factor $\nSegments$ to attain the same frequency resolution (but would improve transient and noise rejection).
 
@@
 On the other hand, when a measurement of the absolute velocity of the payload is available, the external disturbances can be reduced effectively.
-Absolute velocity measurements can be obtained e.g. from inertial sensors~\citep{Collette2011} such as geophones~\citep{Rademakers2005MSc,vanderMaas2011MSc}.
+Absolute velocity measurements can be obtained e.g. from inertial sensors such as geophones~\citep{MunnigSchmidt2014}.
 In particular, such sensors suspend an inertial mass using suspension with very low resonance frequency to the payload.
@@
 \label{sec:lrmhinf:resultsAvis}
-To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, an estimation dataset consisting of only a fourth of the excited bins is used.
-The full dataset that includes bins not used in the estimation is used to validate the interpolation results.
+To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, a short estimation dataset is used.
+This estimation dataset is sampled from a larger dataset that contains four times more excited frequency lines (and hence produces a four times more densely sampled \gls{FRF}).
+The full dataset, i.e. including the bins not seen during the estimation phase, is used to validate the interpolation results.
 
-The measured $\Delta$ is shown in \figref{fig:lrmhinf:avisMeas} for the whole frequency band and \figref{fig:lrmhinf:avisMeasZoom} for a frequency range containing $\omega_{\star}$.
+The measured $\Delta$ is shown in \figref{fig:lrmhinf:avisMeas} for the whole frequency band and \figref{fig:lrmhinf:avisMeasZoom} for a frequency subrange containing $\omega_{\star}$.
 Two aspects of the proposed method are examined.
@@
 
-This suggests that the local rational models with interpolation are a very good approximation to the actual $\Delta$ and also to estimate $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
+This suggests that the local rational models with interpolation enable accurate estimation of  $\abs{\Delta}$ and hence also $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
 
@@
 \label{sec:lrmhinf:conclusion}
-A reliable local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is presented.
+A local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is presented.
 In this chapter, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
-It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.
+It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$, at least for lightly-damped systems.
 
-The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a reliable estimate of the $\Hinf{}$ norm.
+The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
 It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.

### 2016-04-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some changes to CH04
Add reference for CDFs

@@
 \begin{equation}\label{lpmThetaEst}
-\theta^\top(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
+\theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
 \end{equation}
@@
   \end{equation}
-  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom.
+  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
   In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.
 
-  The high level of confidence ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$ \citep{Parsons1974}.
+  The high level of confidence ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$~\citep{Parsons1974}.
   In our case, such an error means that a part of the actual impulse response would be falsely classified as noise, which could significantly increase the bias as information of the system is discarded.

### 2016-04-14 ch05-initvals/initial-values.tex
Add reference for CDFs

@@
 \end{align}
-where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution. %TODO: maybe add reference for Beta distribution
+where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution~\citep{EncyclopediaOfMathematics}.
 This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

### 2016-04-14 ch01-intro/introduction.tex
Different figure names per chapter
Fix: biblatex 3.3 -> 3.4
Small changes here and there

@@
 \def\thisDir{ch01-intro}
+\tikzsetfigurename{ch01fig}
 \myEpigraph{It's a dangerous business, Frodo, going out your door.
@@
 % http://tex.stackexchange.com/questions/18664/underline-my-name-in-the-bibliography
+% Plus see release notes of BIBLATEX 3.3/3.4
 \DeclareNameFormat{author}{%
-\ifthenelse{\equal{#1}{Geerardyn}}%
-    {\textbf{\ifblank{#3}{}{#3\space}#1}}%
-    {\ifblank{#3}{}{#3\space}\ifblank{#5}{}{#5\space}#1}%
+  \nameparts{#1}%
+\ifthenelse{\equal{\namepartfamily}{Geerardyn}}%
+    {\textbf{\ifblank{\namepartgiven}{}{\namepartgiven\space}\namepartfamily}}%
+    {\ifblank{\namepartgiven}{}{\namepartgiven\space}\ifblank{\namepartprefix}{}{\namepartprefix\space}\namepartfamily}%
 \ifthenelse{\value{listcount}<\value{liststop}}%
@@
 
-The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript:
-\begin{itemize}
-  \item \TODO{Geerardyn2016LRM}
-\end{itemize}
-and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
 \begin{itemize}

### 2016-04-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Changes all over the place

@@
 The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
-This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
+This is done by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
 The truncation point (cut-off index) is determined by one of two statistically inspired methods.
@@
 
-Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
+Based on \citet{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
 A \gls{SISO} \gls{LTI} system is considered.
@@
 
-Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
+Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector~\citep{Ljung1999,Soderstrom1989}.
 In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.
@@
 \item The work in this section is for discrete-time systems. 
-Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
+Denote the $k^{\text{th}}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
 
-\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
+\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{\text{th}}$ frequency.
 
-\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.
+\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{\text{th}}$ frequency.
 
@@
 The rest of the section is structured as follows. 
-\secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
-\secref{se:smoothingFRFestimate} discusses the novel smoothing method.
-Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.
+\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
+\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
+Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\Omega_k)$.
 
 These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$.
-Discussion of the simulation results is then followed by a conclusion in \secref{se:conclusion}.
+Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.
 
 \subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}
-\label{se:theoryLPMandWindowing}
+\label{sec:nparam:trunc:theoryLPMandWindowing}
 
-Details of the theory pertaining to this section may be found in \citep{Schoukens2009LPM}, basic aspects of which are presented below.
+Details of the theory pertaining to this section may be found in \citet{Schoukens2009LPM}, basic aspects of which are presented below.
 
@@
 Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
+As shown in \citet{Pintelon2012} and \citet{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
 \begin{equation}\label{eq:nparam:trunc:LPM:leakage}
@@
 where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
-In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}
+In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}
 
@@
 
-The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (\figref{lpmtdrep}):
+The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{lpmtdrep}):
 \begin{assumption}
@@
 \begin{assumption}
-
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$.
-\TODO{assumption is not complete! some expectation is missing!}
+The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\cite{Schoukens2009LPM}.
 \end{assumption}
@@
 The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-\end{assumption}
-
-\begin{assumption}
 The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
@@
 
-\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
+\subsubsection{The Hanning Window and the \glsentrytext{LPM}}
+\label{sec:nparam:trunc:LPMFRFest}
 \paragraph{Windowing}
@@
 \begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
+\hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
 \end{equation}
 
-The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
+The estimation of $\hat{G}_{\LPM}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
@@
    \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
-   A small band is selected (gray area), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained.
+   A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
+Only its central value $\hat G_{\LPM}(\Omega_k)$ (white circle) is retained.
 This procedure is repeated for all frequencies $\Omega_k$.}
@@
 the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries).
-This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.
+This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\Omega_k)$.
 
 \section{Smoothing the \gls{FRF} estimate}
-\label{se:smoothingFRFestimate}
+\label{sec:nparam:trunc:smoothingFRFestimate}
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
-After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from \secref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\Omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
 \begin{enumerate}
-\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.
+\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\Omega_k)$.
 
@@
 \begin{assumption}
-The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
+The estimate $\hat G_{\LPM}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
 \end{assumption}
@@
 
-The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
+The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
+}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
 
 \begin{align}\label{eq:impRespiDFT}
-\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
+\hat g_{{\LPM}\setminus \mathrm{DC
+}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\Omega_k)e^{\frac{j2\pi kt}{N}}
 \end{align}
@@
 \begin{align}
-\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
+\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
 \end{align}
-(with $\conj{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$) to ensure $\hat g_\mathrm{poly}(t)$ to be real.
+(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.
 
@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response.
-Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
+Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:trunc:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
 \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
@@
 
-\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}
+\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
 The correct mean value of the impulse response accounts for (i.e.
@@
 \begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$, estimated by the \gls{LPM}, as %$\hat g_\mathrm{poly}(t)$ as
+\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{{\LPM}\setminus \mathrm{DC
+}}(t)$, estimated by the \gls{LPM}, as %$\hat g_{\LPM}(t)$ as
 \begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
+m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{{\LPM}\setminus \mathrm{DC
 }}(t)
@@
 
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:
+\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
+}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \emph{viz}:
 
 \begin{align}
-\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
+\hat g_{\LPM}(t) = \hat g_{{\LPM}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
 \end{align}
@@
 \label{sec:nonparametric:truncation:ftest}
-To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments.
+To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_{\LPM}$ is split into smaller segments.
 One can then gradually determine whether these segments are noise or the actual impulse response.
@@
 \begin{enumerate}
-  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
+  \item The impulse response $\hat{g}_{\LPM}(t)$ is split into $N_S$ segments of approximate equal lengths
 $L_S = \floor{\frac{N}{N_S}}$. 
@@
 \end{enumerate}
-This procedure is illustrated in \figref{fig:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
+This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{sec:nparam:trunc:LPMFRFest}:
 \begin{subequations}
@@
 \caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.}
-\label{fig:nonparametric:truncation:Ftest}
+\label{fig:nparam:trunc:nonparametric:truncation:Ftest}
 \end{figure}
@@
 \begin{enumerate}
-\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{se:DCvalueEst}. 
-Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.
+\item Obtain the estimate of the impulse response $\hat g_{\LPM}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{sec:nparam:trunc:DCvalueEst}. 
+Henceforth, $\hat g_{\LPM}(t)$ will simply be denoted as $\hat g(t)$.
 
@@
 \caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
-\label{fig:nonparametric:trunc:impresp:expfit}
+\label{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}
 \end{figure}
@@
 The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
-The result is depicted in \figref{fig:nonparametric:trunc:impresp:expfit}. 
+The result is depicted in \figref{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}. 
 An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
@@
 
-\subsection{Simulation Results}\label{se:simResults}
+\subsection{Simulation Results}\label{sec:nparam:trunc:simResults}
 
-\figref{figLPMvsTrunc} and \figref{fig:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
+\figref{fig:nparam:trunc:LPMvsTRunc} and \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
 Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
-They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{se:LPMFRFest}:
+They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
 \begin{subequations}
@@
     \setlength\figureheight{0.68\figurewidth}
-    \input{\thisDir/figs/figLPMvsTrunc.tikz}
+    \input{\thisDir/figs/figLPMvsTRunc.tikz}
     \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{The bias $\sampleBias{\placeholder}$ and standard deviation $\sampleStd{\placeholder}$ of the \gls{FRF} estimates using both the \gls{LPM} (blue) and truncated~\gls{LPM} (red) are shown.
     It can be seen that the truncation reduces the variance at the cost of an increased bias, however, the overall \gls{RMS} error is reduced by the truncation.}
-    \label{figLPMvsTrunc}
+    \label{fig:nparam:trunc:LPMvsTRunc}
 \end{figure}
 
-In \figref{figLPMvsTrunc} one observes the following:
+In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
 \begin{itemize}
@@
          It can be seen that both methods allow to almost halve the \gls{RMS} error and approach the optimal truncation time.}
-   \label{fig:pdfAndRMSeVStruncTime}
+   \label{fig:nparam:trunc:pdfAndRMSeVStruncTime}
 \end{figure}
 
-In \figref{fig:pdfAndRMSeVStruncTime}, the black graph is the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $\truncTime$ at which the impulse response is truncated.
+In \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime}, the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $\truncTime$ at which the impulse response is truncated, is shown.
 To the left of the optimal truncation length, the \gls{RMS} error increases steeply.
@@
 A good practice would be to truncate the impulse response at the minimizer (black dot) of the \gls{RMS} error. 
-However, it should be noted that this minimizer is unknown in practice, because it would require the true \gls{FRF}.
+However, this minimizer is unknown in practice, since it depends on the true underlying system.
+Nevertheless, the proposed approaches provide a reasonable way to approximate the optimal truncation length.
 
 The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}. 
-This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
+This was done on $1000$ realizations of the noise, and depicted in \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} by the histogram.
 Clearly, both methods for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of their distribution (around the $90^{\text{th}}$ sample).
@@
 For the exponential fitting approach, however, a closely grouped set of (continuous) values for $\truncTime$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
-Although this distribution has a mode quite a bit higher than the method using the $F$-test, due to the absence of outliers, this method is more reliable to use.
+Although this distribution has a mode that is quite a bit higher than the method using the $F$-test, due to the absence of outliers, this method is more reliable to use for the particular system that we studied.
 
@@
 \subsection{Conclusion}
-\label{se:conclusion}
+\label{sec:nparam:trunc:conclusion}
 
@@
 A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
-
-\TODO{write about boxcar average, add reference}
-
-\begin{align}
-  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
-\end{align}
-
-\begin{figure}
-   \centering
-        \setlength\figurewidth{0.68\columnwidth}
-        \setlength\figureheight{0.68\figurewidth}
-        \input{\thisDir/figs/expFitBoxAverager.tikz}
-         \caption{Exponential fit of the impulse response of a  boxcar averager.}
-\end{figure}
-
-\begin{figure}
-   \centering
-        \setlength\figurewidth{0.68\columnwidth}
-        \setlength\figureheight{0.68\figurewidth}
-        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
-         \caption{RMSE vs $\truncTime$ for boxcar \TODO{better caption}}
-\end{figure}

### 2016-04-14 code/SamplingProp.m

@@ -52,10 +52,12 @@ classdef SamplingProp < handle & Describable & WithUserData & Codegeneratable
         w  % [rad/s] pulsation
         wn % [rad] normalized pulsation
         f  % [Hz] frequency
-        w_pos % [rad/s] negative frequency axis
+        w_pos % [rad/s] positive frequency axis
         f_pos % [Hz] positive frequency axis
         sel_pos % [] logical array indicating positive frequency spectrum
-        %TODO: sel_DC, sel_Nyquist, sel_DCNyquist
+        sel_DC % [] logical array indicating DC
+        sel_Nyquist % [] logical array indicating Nyquist frequency
+        sel_DCNyquist % [] logical array indicating DC and Nyquist frequency
     end
     %% Conveniance aliasses
     properties(Hidden,Dependent)
@@ -184,6 +186,15 @@ classdef SamplingProp < handle & Describable & WithUserData & Codegeneratable
         end
         function value = get.w_pos(obj)
             value = obj.w(obj.sel_pos);
+        end
+        function value = get.sel_DC(obj)
+            value = obj.f == 0;
+        end
+        function value = get.sel_Nyquist(obj)
+            value = obj.f == obj.fs/2
+        end
+        function value = get.sel_DCNyquist(obj)
+            value = ismember(obj.f,[0 obj.fs/2]);
         end
         
         % setters

### 2016-04-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some work on boxcar + FIX BUG

@@
 Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \citet{Pintelon2012} and \citet{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
+As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
 \begin{equation}\label{eq:nparam:trunc:LPM:leakage}
@@
 \begin{assumption}
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\cite{Schoukens2009LPM}.
+The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\citep{Schoukens2009LPM}.
 \end{assumption}
@@
 
-\paragraph{Formulation of the Linear LS LPM}
-The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
-\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
-The formulation in this section is a summary for a \gls{SISO} system.
+%TODO: re-use into LPM/LRM sections
+% \paragraph{Formulation of the Linear LS LPM}
+% The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
+% \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
+% The formulation in this section is a summary for a \gls{SISO} system.
 
-The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
-\begin{equation}\label{lpm1spectra}
-Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
-\end{equation}
-where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
+% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
+% \begin{equation}\label{lpm1spectra}
+% Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
+% \end{equation}
+% where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
 The latter is the sum of the system and the noise leakage terms, i.e.
@@
 
-The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
-\begin{align}\label{lpmGTaylorS}
-G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
-\bigO{\left(\frac{r}{N}\right)^{R+1}},
-\\
-\label{lpmTTaylorS}
-T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
-\bigO{  \left(\frac{r}{N}\right)^{R+1}  }
-,
-\\
-\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-\end{align}
+% The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
+% \begin{align}\label{lpmGTaylorS}
+% G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
+% \bigO{\left(\frac{r}{N}\right)^{R+1}},
+% \\
+% \label{lpmTTaylorS}
+% T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
+% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
+% ,
+% \\
+% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
+% \end{align}
 
-The choice of the tunable parameters $n$ and $R$ is discussed later on.
+% The choice of the tunable parameters $n$ and $R$ is discussed later on.
 
-Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
-\begin{equation}\label{lpmGTMatrix}
-Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-\end{equation}
-where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-\begin{align}
-K(k,r) = &\left[
-\begin{matrix}
-U_0(k+r) & U_0(k+r)r & \dots
-\end{matrix}
-\right.
-\\
-&\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-\end{align}
+% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
+% \begin{equation}\label{lpmGTMatrix}
+% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
+% \end{equation}
+% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
+% \begin{align}
+% K(k,r) = &\left[
+% \begin{matrix}
+% U_0(k+r) & U_0(k+r)r & \dots
+% \end{matrix}
+% \right.
+% \\
+% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
+% \end{align}
 
-Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-\begin{equation}\label{lpmGTMatrixStack}
-Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-\end{equation}
-where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
-\begin{align}\label{eq:LSsolutionLPM}
-\hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-\end{align}
+% Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
+% \begin{equation}\label{lpmGTMatrixStack}
+% Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
+% \end{equation}
+% where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
+% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
+% \begin{align}\label{eq:LSsolutionLPM}
+% \hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
+% \end{align}
 
-The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
+% The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
 The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.
 
-The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
+% The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
+In this section, the $\lpm{3,2,2}$ is used.
 
-When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
-\begin{align}
-G_0(\Omega_{k+r})
-  &\approx 
-  G_0(\Omega_k)+g_1r+g_2r^2
-  \label{eq:lpm:expansionG:quadratic}
-\\
-  T(\Omega_{k+r})
-    &\approx 
-    T(\Omega_k)+t_1r+t_2r^2
-    \label{eq:lpm:expansionT:quadratic}
-\end{align}
-with ($r\in\mathbb{W}_3$) and the vector of parameters:
-\begin{equation}\label{lpmThetaEst}
-\theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-\end{equation}
-The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
-\begin{equation}
-\hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
-\end{equation}
+% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
+% \begin{align}
+% G_0(\Omega_{k+r})
+%   &\approx 
+%   G_0(\Omega_k)+g_1r+g_2r^2
+%   \label{eq:lpm:expansionG:quadratic}
+% \\
+%   T(\Omega_{k+r})
+%     &\approx 
+%     T(\Omega_k)+t_1r+t_2r^2
+%     \label{eq:lpm:expansionT:quadratic}
+% \end{align}
+% with ($r\in\mathbb{W}_3$) and the vector of parameters:
+% \begin{equation}\label{lpmThetaEst}
+% \theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
+% \end{equation}
+% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
+% \begin{equation}
+% \hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
+% \end{equation}
 
@@
 
+\paragraph{Alternative system}
+%% BEGIN BOXCAR
+\TODO{write about boxcar average, add reference}
+\begin{align}
+  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
+\end{align}
+
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/expFitBoxAverager.tikz}
+         \caption{Exponential fit of the impulse response of a boxcar averager.}
+         \label{fig:nparam:trunc:boxcar:impresp}
+\end{figure}
+
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
+         \caption[RMS error of the FRF versus truncation time (boxcar)]{RMSE of a boxcar averager as a function of the truncation time $\truncTime$.
+         Empirical histograms of $\truncTime$ as determined using both the $F$-test and exponential fitting are shown.
+         For this system, the $F$-test based method is clearly superior.
+         The exponential fitting method is not effective in most cases.}
+         \label{fig:nparam:trunc:boxcar:trunctime}
+\end{figure}
+%% END BOXCAR
+
 \subsection{Conclusion}

### 2016-04-15 ch05-initvals/initial-values.tex
More conclusion + order of RFIR

@@
 
+\begin{remark} \label{rem:initvals:orders:RFIR}
+In this chapter, all results are obtained using $n_g=200$ since this exceeds the length of most impulse responses used.
+However, for general use, the model complexity $n_g$ might need to be increased.
+One could use $n_g \approx N$ and rely on regularization to reduce the effective model complexity.
+Unfortunately, this scales very poorly for long measurement records as explained in \secref{sec:initvals:computation}.
+\end{remark}
+
 \begin{remark}

### 2016-04-15 ch06-concl/conclusions.tex
More conclusion + order of RFIR

@@
   Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
-  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time:
+  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time~\citep[Section 2.7]{Pintelon2012}:
   \begin{itemize}
@@
 This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
-    \item Orthogonal multisines, which are computationally more involved to process.
+    \item Orthogonal multisines, which are computationally more involved to process, require multiple experiments but allow for finer frequency resolution.
   \end{itemize}
@@
 This means: lowest guaranteed observable resonance is at higher frequencies than for SISO (obviously).
-  %TODO: also zippered vs. orthogonal for non-linearities: sparsity destroys BLA relationship
 
@@
   Techniques in model order reduction are likely to provide a good starting point to simplify the local pole/zero estimates to a global parametric model which could then be used to serve as initial estimate for the non-convex optimization steps.
+
+As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
+There are a few approaches that we think are worthwhile to investigate.
+On the one hand, the truncation methods explained in \secref{sec:nparam:trunc} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
+On the other hand, one could devise crude model order selection procedures, e.g.
+estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
+Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
+This doesn't do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.

### 2016-04-15 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
More uniform notation in trunc

@@
 \item The work in this section is for discrete-time systems. 
-Denote the $k^{\text{th}}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
+Denote the $k^{\text{th}}$ discretized frequency as $\omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
 
-\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{\text{th}}$ frequency.
+\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\omega_k)$  at the $k^{\text{th}}$ frequency.
 
-\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{\text{th}}$ frequency.
+\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\omega_k)$ at the $k^{\text{th}}$ frequency.
 
@@
 \secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
-Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\Omega_k)$.
+Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.
 
-These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$.
+These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
 Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.
@@
 Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
+As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
 \begin{equation}\label{eq:nparam:trunc:LPM:leakage}
-Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
+Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
 \end{equation}
-where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
+where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
 In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}
@@
 \begin{equation}\label{eq:defDFT}
-X(\Omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
+X(\omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
 \end{equation}
@@
 % \begin{equation}\label{lpm1spectra}
-% Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
+% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
 % \end{equation}
-% where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term.
+% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term.
 The latter is the sum of the system and the noise leakage terms, i.e.
-$T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.
+$T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.
 
-% The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
+% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
 % \begin{align}\label{lpmGTaylorS}
-% G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
+% G_0(\Omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
 % \bigO{\left(\frac{r}{N}\right)^{R+1}},
@@
 % \label{lpmTTaylorS}
-% T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
+% T(\Omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
 % \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
@@
 % \end{equation}
-% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\Omega_k)$, $T(\Omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
+% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\omega_k)$, $T(\omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
 % \begin{align}
@@
 %   &\approx 
-%   G_0(\Omega_k)+g_1r+g_2r^2
+%   G_0(\omega_k)+g_1r+g_2r^2
 %   \label{eq:lpm:expansionG:quadratic}
@@
 %     &\approx 
-%     T(\Omega_k)+t_1r+t_2r^2
+%     T(\omega_k)+t_1r+t_2r^2
 %     \label{eq:lpm:expansionT:quadratic}
@@
 % \begin{equation}\label{lpmThetaEst}
-% \theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
+% \theta^{\TT}(k)=\left[G_0(\omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
 % \end{equation}
@@
 % \begin{equation}
-% \hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
+% \hat{G}_{\LPM}(\omega_k) = \hat\theta_1(k)
 % \end{equation}
 
-The estimation of $\hat{G}_{\LPM}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
+The estimation of $\hat{G}_{\LPM}(\omega_k)$ at a single frequency $\omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
@@
    A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_{\LPM}(\Omega_k)$ (white circle) is retained.
-This procedure is repeated for all frequencies $\Omega_k$.}
+Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained.
+This procedure is repeated for all frequencies $\omega_k$.}
    \label{LPM_Schematic_EG}
 \end{figure}
-This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e.
+This procedure is repeated at each central frequency $\omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e.
 the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries).
-This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\Omega_k)$.
+This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\omega_k)$.
 
@@
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
-After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\Omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
 \begin{enumerate}
-\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\Omega_k)$.
+\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.
 
@@
 \begin{assumption}
-The estimate $\hat G_{\LPM}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
+The estimate $\hat G_{\LPM}(\omega_k)$ is available at all frequencies $\omega_k$ for $k\in\{1,2,\dots,N/2\}$.
 \end{assumption}
@@
 The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
+}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
 
@@
 \hat g_{{\LPM}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\Omega_k)e^{\frac{j2\pi kt}{N}}
+}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
 \end{align}
@@
 \begin{align}
-\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
+\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
 \end{align}

### 2016-04-15 ch04-lrmhinf/lrmhinf.tex
Small changes here and there
Some small things

@@
 \glsresetall
+
+%TODO: The quality of the estimate of the H-infinity norm of Delta is completely unknown.
+In other words, there is no theoretical guarantee about the error.
+--> Tom: addresseren.
+Feitelijk hangt dit samen met de kwaliteit van standaard lpm/lrm, toch?
 
@@
 To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
-These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
-%TODO{formules Hansen schema}
-In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.
+These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
+\begin{align}
+  u_{\Delta}(t) &= \left(\hat{D} + C \hat{N} \right)^{-1} \mat{C & \I} \mat{y(t)\\u(t)}\\
+  y_{\Delta}(t) &= \left(D_c + \hat{P} N_c \right)^{-1} \mat{\I & -\hat{P}} \mat{y(t)\\u(t)}
+\end{align}
+In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989} and uncorrelated to $y_{\Delta}$. 
+Hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.
 

### 2016-04-15 ch05-initvals/initial-values.tex
Some small things

@@
 \item \emph{Local polynomial method (LPM) with truncation}
-
+\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nparam:trunc} in more detail. The pertinent details are repeated here to aid readability.}
 A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
@@
   With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
-  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $n=3$, such that
+  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
 \begin{subequations}\label{lpmImplQuadG}
@@
 \end{subequations}
-where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
-\TODO{notatie LPM uniform maken met CH03/CH04}
+where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,B_W\}$ and $N_W$ is a tunable parameter. 
+%TODO notation LPM uniform maken met CH03/CH04
 
@@
 \begin{equation}
-\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
+\hat{G}_\text{LPM}(\Omega_k) = \hat{G}_k
 \text{.}
@@
 \emph{Impulse response truncation}. 
-The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.
+The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \mathrm{IDFT}\, \left( \hat{G}_{\LPM}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.
 
@@
 \begin{equation}
-  g_{\mathrm{trunc}}(t) = 
+  g_{\trunc}(t) = 
   \begin{cases}
-    g_{\text{poly}}(t) & t \leq \truncTime \\
+    g_{\LPM}(t) & t \leq \truncTime \\
     0                              & t \geq \truncTime
@@
 
-To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
+To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\LPM}(t)}$ using a linear least-squares approach.
 Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
@@
 where $\gamma=1$ was used in this chapter for simplicity.
-By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
+By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\Omega_k) = \mathrm{DFT} \left( g_{\trunc}(t)\right)$ further.
 This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.

### 2016-04-17 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some uniformity stuff

@@
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
+This is depicted in \figref{fig:nparam:trunc:oe} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
 \begin{equation}\label{eq:nparam:trunc:LPM:TD}
@@
 \caption{SISO LTI discrete-time system in an output error setup.}
-\label{lpmtdrep}
+\label{fig:nparam:trunc:oe}
 \end{figure}
@@
 \item The work in this section is for discrete-time systems. 
-Denote the $k^{\text{th}}$ discretized frequency as $\omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
+Denote the $k^{\text{th}}$ discretized frequency as $\omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $\fs$ the sample frequency and $N$ the total number of sample points.
 
@@
 \secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
-Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.
+Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following \gls{FRF} estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.
 
-These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
+These \gls{FRF} estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
 Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.
@@
 
-Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
+Using convolution, the noiseless output signal in \figref{fig:nparam:trunc:oe} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
 As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
@@
 
-The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{lpmtdrep}):
+The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:trunc:oe}):
 \begin{assumption}
@@
 
-% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
+% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:trunc:oe} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
 % \begin{equation}\label{lpm1spectra}
@@
 }}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
-
 \begin{align}\label{eq:impRespiDFT}
@@
 where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
-
 \begin{align}
-\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
+\hat G_{\LPM}(\omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
 \end{align}
@@
 
-\TODO{fix reference Section II}
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
-Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:trunc:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e.
-\gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}.
+Unfortunately, the \gls{LPM} presented in \TODO{\secref{sec:nparam:trunc:theoryLPMandWindowing}} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\omega_0$ (i.e.
+\gls{DC} value of the \gls{FRF}), hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 

### 2016-04-17 ch03-lrm/lrm-paper.tex
Changes all over the place
More uniform notation in trunc
Some uniformity stuff

@@
 \begin{equation}
-  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \ZZ
+  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \IntegerNumbers
   \label{eq:output-error-TD-infinite}
@@
 \end{equation}
-where $t_G[n]$ and $t_H[n]$ are due to the different state of respectively $\true{G}$ and $\true{H}$ at the beginning and end of the measurement record~\citep{Pintelon1997ARB}.
-Both terms can be lumped together as $t[n]$, which is often~\citep{Pintelon2010LPM1} dominated by $t_G[n]$.
+where $t_G[n]$ and $t_H[n]$ are due to the different conditions of respectively $\true{G}$ and $\true{H}$ at the beginning and end of the measurement record~\citep{Pintelon1997ARB}.
+Both terms can be lumped together as $t[n]$, which is often~\citep{Pintelon2010LPM1} determined predominantly by $t_G[n]$.
 
@@
    \subsection{AVIS}
-   \subsection{F16}
+   % \subsection{F16}
 

### 2016-04-17 ch04-lrmhinf/lrmhinf.tex
Some uniformity stuff

@@
 
-\begin{guideline}[Measure at least $5\timeconst\,$ to observe its peak value using the local models]
+\begin{guideline}[Measure at least $5\timeconst\,$ to observe the peak value using the local models]
 \begin{minipage}{0.725\textwidth}
@@
   \hfill
-  \photobox{\includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
-  %TODO: right figure is just a tad too small
+  \photobox{\includegraphics[width=1.005\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
   \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 

### 2016-04-17 ch06-concl/conclusions.tex
Some uniformity stuff

@@
 
-    In particular, for slowly time-varying systems, windows can be used in combination with the \gls{STFT} to obtain a rough approximation of either the output spectrum or the transfer characteristic of time-varying systems.
+    In particular, for slowly time-varying systems, windows can be used in combination with the \gls{STFT} to obtain a rough approximation of either the output spectrum or the transfer characteristic of (slowly) time-varying systems.
     In this context, the \gls{LPM} has already been used~\citep{Lataire2012}.
@@
     Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
-    E.g. it could prove useful to extend the \gls{LRM} also towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.
+    E.g. it could prove useful to extend the \gls{LRM} towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.
 

### 2016-04-17 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
LPM-trunc finished

@@
 
-The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
+The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
 \begin{align}\label{eq:impRespiDFT}
@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
-Unfortunately, the \gls{LPM} presented in \TODO{\secref{sec:nparam:trunc:theoryLPMandWindowing}} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\omega_0$ (i.e.
-\gls{DC} value of the \gls{FRF}), hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
+Unfortunately, the \gls{LPM} presented in \TODO{\secref{sec:nparam:trunc:theoryLPMandWindowing}} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
@@
 \begin{align}
-m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)
+   m_{g10} 
+   = 
+   \frac{1}{\lceil0.1N - 1\rceil}
+   \sum_{t=\lfloor0.9N\rfloor}^{N-1}
+      \hat g_{{\LPM}\setminus \mathrm{DC}}(t)
 \end{align}
@@
 }}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \emph{viz}:
-
 \begin{align}
@@
 For the $F$-test based method, the obtained $\truncTime$ values only take a discrete set of values due to the limitation of the segment length.
-While most trials result in $\truncTime \in \Set{90, 80, 70}$, a few outliers can be observed.
-This can be attributed to the high power of the $F$-tests that are performed.
+While most trials result in $\truncTime \in \Set{70, 80, 90}$, a few outliers with much higher truncation times can be observed.
+These outliers can be attributed to the high power of the $F$-tests.
 
@@
 
-\begin{guideline}[Check and reinforce assumptions in the data.]
-As illustrated by the presented smoothing operation, it pays off to check typical assumptions of the system (e.g.
-smoothness of the \gls{FRF}, finite support of the impulse response) and even artificially reinforce such assumptions to improve the model quality.
-\end{guideline}
+\paragraph{Interaction of the truncation method and the system properties}
+As seen in the previous simulation example, the exponential fitting method is well-suited to determine $\truncTime$ when the underlying system exhibits an exponential decay.
+However, if the system under test is not part of this class of systems, the exponential fitting method may provide sub-optimal results or even be ineffective.
 
-\paragraph{Alternative system}
-%% BEGIN BOXCAR
-\TODO{write about boxcar average, add reference}
+Consider instead that we are measuring a boxcar averager, i.e. a moving-average filter.
+Such a system is governed by the difference equation:
 \begin{align}
-  y(t) = \sum_{i=1}^{\Nbc} \Nbc^{-1} u(t-i)
+  y(t) = \sum_{i=0}^{\Nbc-1} \Nbc^{-1} u(t-i) 
+  \text{,}
 \end{align}
+where $\Nbc = 88$.
+Since this system is a trivial \gls{FIR}, it is easy to see that $\truncTime = \Nbc$ provides the optimal truncation point.
+
+We simulate the boxcar averager for a white noise input $u(t)$ and add white noise with standard deviation $\sigma_e \approx 0.1$ to the output $y(t)$ for $2\,048$ samples from which the first $1\,024$ samples are discarded to randomize the state of the system under test.
+A single realization of the impulse response function is shown in \figref{fig:nparam:trunc:boxcar:impresp} together with the $\truncTime$ and other relevant quantities of the exponential fitting method.
+It is easy to observe that the exponential fitting provides sub-optimal results since it truncates well past the end of the finite impulse response.
 
@@
         \input{\thisDir/figs/expFitBoxAverager.tikz}
-         \caption{Exponential fit of the impulse response of a boxcar averager.}
+         \caption{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
          \label{fig:nparam:trunc:boxcar:impresp}
 \end{figure}
+
+By repeating the experiment above $\nMC = 1\,000$ times as a Monte Carlo simulation where both the input signal and disturbing noise are varied, we gain insight into the behavior of both truncation methods.
+The histograms of the observed values of $\truncTime$ for both methods is shown in \figref{fig:nparam:trunc:boxcar:trunctime} together with the \gls{RMS} error as a function of $\truncTime$.
+It can be seen that the $F$-test based method mostly selects the optimal truncation point.
+On the other hand, the exponential fitting method is largely ineffective and doesn't truncate the response in most of the cases.
 
@@
 \end{figure}
-%% END BOXCAR
+
+It can be seen that both the $F$-test method and the exponential fitting method each have their own strengths and weaknesses.
+Particularly, the $F$-test method can only select $\truncTime$ from a discrete set of values, but works well for specifically designed \gls{FIR} filters where there is a clear jump in the amplitude of the impulse response.
+On the other hand, the exponential fitting method relies on the exponential decay of the impulse response to obtain sensible values of $\truncTime$ and is hence a better match for `physical' systems.
+One should remember, however, that for the studied examples, both approaches only very seldomly select a $\truncTime$ that increases the \gls{RMS} error on the impulse response compared to not truncating the response.
+As such, a use has little to lose by trying out both methods: the model quality is very unlikely to decrease and the additional computational effort is minimal.
+
+\begin{guideline}[Check and reinforce assumptions in the data.]
+As illustrated by the presented smoothing operation, it pays off to check typical assumptions of the system (e.g.
+smoothness of the \gls{FRF}, finite support of the impulse response) and even reinforce such assumptions to improve the model quality.
+For the truncation approaches, even if the assumptions do not hold, the methods are constructed such that the unavoidable model error is unlikely to increase.
+\end{guideline}
 
@@
 
-The section introduced a novel time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 
+This section introduced a time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 
 It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.

### 2016-04-17 ch05-initvals/initial-values.tex
CH05: Tau(DAQ) -> \tau_{MUX}

@@
 The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
-Although acquisition and generation were synchronized, there is a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
+Although acquisition and generation were synchronized, there is a small delay $\tau_{\mathrm{MUX}} \approx 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
 Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
 This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
-As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.
+As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau_{\mathrm{MUX}} \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.
 

### 2016-04-18 ch04-lrmhinf/lrmhinf.tex
More uniform notations

@@
     \sup \Set{ 
-                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel{\Delta}_k(\omega)}
+                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel[k(\omega)]{\Delta}}
                 |
@@
 \end{equation}
-where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k^{\text{th}}$) frequency bin $\omega_k$.
+where the $\LocalModel[k]{\Delta}$ is the local model around the ($k^{\text{th}}$) frequency bin $\omega_k$.
 An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
@@
   \input{\thisDir/figs/interpolation-show.tikz}
-  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\Set{1,\ldots,6}$.
-  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
+  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel[k]{\Delta}$ around each frequency bin $\omega_k$ for $k\in\Set{1,\ldots,6}$.
+  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\Set{\omega \given{\leftAdjacent(\omega) = k \vee \rightAdjacent(\omega) = k}}$.}
 \label{fig:lrmhinf:interpol-quantities}
@@
 To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
-It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when the distance $\abs{\omega_k-\omega}$ is small.
+It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel[k(\omega)]{\Delta}$ when the distance $\abs{\omega_k-\omega}$ is small.
 As the local models are each constructed around the frequency $\omega_k$, for an arbitrary $\omega \in \Omega$, one can find two adjacent frequencies around which such local models are available.
@@
 \begin{align}
-  k_L(\omega) & 
+  \leftAdjacent(\omega) & 
                 \isdef
@@
                   }\\
-  k_R(\omega) & 
+  \rightAdjacent(\omega) & 
                 \isdef
@@
 \end{align}
-Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
+Using the $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
 \begin{equation*}
- \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)} 
+ \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)} 
  \quad \text{ and } \quad
- \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+ \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
 \end{equation*}
@@
     \max \Set{
-       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
-        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
+       \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)},
+        \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}
     }
@@
       \max \Set{
-                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
-                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
+                 \svdMax{\LocalModel[\leftAdjacent(\omega)]{\Delta}(\omega)}, 
+                 \svdMax{\LocalModel[\rightAdjacent(\omega)]{\Delta}(\omega)}}
   \label{eq:lrmhinf:gammaInterpolOptim}
@@
 The optimization problems \eqref{eq:lrmhinf:gammaInxterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
-The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
+The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel[k]{\Delta}$ are evaluated over identical frequency ranges
  \begin{equation}
-  \Omega_k = \Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
+  \Omega_k 
+     = 
+       \Set{
+           \omega 
+           | 
+               \leftAdjacent(\omega) = k 
+               \vee 
+               \rightAdjacent(\omega) = k
+      }
  \end{equation}
 for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
-In \figref{fig:lrmhinf:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
+In \figref{fig:lrmhinf:interpol-quantities} the functions $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
 \end{remark}
@@
 
-The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
+The local models $\LocalModel[k]{\Delta}$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
 The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
@@
       \isdef 
-        \LocalModel{\Delta}_{k}(\omega_{k+r})
+        \LocalModel[k]{\Delta}(\omega_{k+r})
       \label{eq:lrmhinf:LRMTaylorSystem} \\
@@
       \isdef 
-        \LocalModel{T}_{k}(\omega_{k+r})
+        \LocalModel[k]{T}(\omega_{k+r})
   \label{eq:lrmhinf:LRMTaylorTransient}
@@
 \end{equation}
-By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
+By substituting the local models $\LocalModel[k]{\Delta}$ and $\LocalModel[k]{T}$, one obtains
 \begin{align}
@@
                   & \approx
-                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
-                    + \LocalModel{T}_k(\omega_{k+r}) 
+                    \LocalModel[k]{\Delta}(\omega_{k+r}) U_{\Delta}(k+r) 
+                    + \LocalModel[k]{T}(\omega_{k+r}) 
                     & \forall r \in \LocalWindow \\

### 2016-04-18 ch03-lrm/nonparametric.tex
Changes all over the place
Add some info PRESS/LOOCV

@@
 
-\section{\TODO{LPM}}
-\section{\TODO{LRM}}
 \input{\thisDir/lrm-paper.tex}
@@
 \section{\TODO{Bias-variance trade-off }}
-\TODO{import LRM paper}
 
@@
 \subsubsection{\TODO{AVIS}}
-% \subsubsection{\TODO{F16}}
+
+\begin{subappendices}
+  \section{Proof of the \glsentrytext{LOOCV} statistic for linear models}
+
+  We follow an approach similar to \citet{Hyndman2014LOOCV} and \citet[Section 12.3.2]{Seber2003} to prove that for a linear model, one can easily compute the \gls{PRESS}/\gls{LOOCV} statistic by means of the so-called `hat-diagonals`, the diagonal entries of the hat matrix $H$.
+  This is relevant, e.g. for local linear models used in the \gls{LRM} and hence also the \gls{LPM}.
+
+  We consider the linear model
+  \begin{equation}
+    Z = K \theta + V
+  \end{equation}
+  with $Z \in \ComplexMatrix{N\times1}$, $\theta \in \ComplexMatrix{\nth \times 1}$, $K \in \ComplexMatrix{N \times \nth}$.
+$V \in \ComplexMatrix{N \times 1}$ is a \gls{iid} complex gaussian random variable.
+The least-squares solution of such a linear model is:
+\begin{equation}
+  \hat{\theta} = \left(K^{\HT} K \right)^{-1} K^{\HT} Z = \pinv{K} Z
+\end{equation}
+such that the estimated output $\hat{Z}$ is given by
+\begin{equation}
+  \hat{Z} = K \pinv{K} Z = H Z
+\end{equation}
+where $H$ is the so-called `hat matrix' that projects the measurements $Z$ onto the estimates $\hat{Z}$.
+
+The \gls{PRESS} statistic used in \gls{LOOCV} is defined as~\citep[Chapter 12]{Seber2003}
+\begin{equation}
+  \PRESS \isdef 
+    \frac{1}{N} 
+      \sum_{i=1}^{N}
+      \abs{
+        Z_i - \ignoring{i}{\hat{Z}}
+      }^2
+\end{equation}
+where $\hat{Z}_i$ is the $i^{\text{th}}$ row of $\hat{Z}$ and $\ignoring{i}{\hat{Z}}$ denotes the estimated $\hat{Z}_i$ when the $i^{\text{th}}$ data point (i.e.
+row) is removed from the estimation problem.
+For linear models, this is equivalent to
+\begin{equation}
+  \PRESS_{\mathrm{linear}} = 
+     \frac{1}{N}
+     \sum_{i=1}^{N}
+     \abs{
+       \frac{Z_i - \hat{Z}_i}
+                {1 - H_{ii}}
+     }^2
+     \text{.}
+\end{equation}
+Note that in this last expression, no terms $\ignoring{i}{\hat{Z}}$ occur, such that the statistic can be computed without having to compute $N$ additional linear models.
+In this appendix, we prove that these last two expressions are equivalent for linear models.
+
+\paragraph{Proof}
+\TODO{proof}
+\TODO{matrix inversion lemma}
+\TODO{evt. Seber2003/ChristensenXXXX: QR decomposition to compute $H$}
+
+\end{subappendices}

### 2016-04-19 ch03-lrm/lrm-paper.tex
LRM: part of bias, some intro

@@
-\section{Introduction}
 Estimating a non-parametric \gls{FRF} is often a key step in the analysis and/or design of physical systems.
@@
 
+Recently, there has been a renewed interest in the development of non-parametric estimators to estimate the \gls{FRF} of a system.
+Many of these approaches have focused on separating the periodic response (i.e.
+the \gls{FRF}), the measurement noise and leakage contributions of the spectrum by exploiting the structure that those different contributions exhibit.
+
 \citep{Pintelon2010LPM1},\citep{Pintelon2010LPM2},\citep{McKelvey2012LRM}
 
-\paragraph*{Contributions}
-In this paper, the existing \gls{LRM} is extended to the \gls{LRIC} that does not suffer from  the bias that is present in the \gls{LRM}.
-An extensive study is carried out to compare the performance of the \gls{LPM}, \gls{LRM} and \gls{LRIC} to describe resonant systems under varying conditions of the signal-to-noise ratio.
-Also, a pragmatic model-order-selection tool for the \gls{LPM} and \gls{LRM} is introduced.
+% \paragraph*{Contributions}
+% In this paper, the existing \gls{LRM} is extended to the \gls{LRIC} that does not suffer from  the bias that is present in the \gls{LRM}.
+% An extensive study is carried out to compare the performance of the \gls{LPM}, \gls{LRM} and \gls{LRIC} to describe resonant systems under varying conditions of the signal-to-noise ratio.
+% Also, a pragmatic model-order-selection tool for the \gls{LPM} and \gls{LRM} is introduced.
 
-\paragraph*{Contents}
+\paragraph*{Outline}
 \secref{sec:theory} introduces theory of estimating \glspl{FRF} and the relevant local modeling techniques.
@@
   \isdef 
-  \left( \LocalModel{A} \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
-      \left( \LocalModel{A} \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
+  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
+      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
       \text{.}
@@
 \begin{align}
-  \label{eq:design-matrix}
+  \label{eq:nparam:designMatrix}
   \LocalVector{K} 
@@
 
-Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:design-matrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
+Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
 To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
@@
 \label{sec:biascalc}
-Since the local design matrix \eqref{eq:designMatrix} contains the noisy output spectrum $\LocalVector{Y}$ when $\numel{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
+Since the local design matrix \eqref{eq:nparam:designMatrix} contains the noisy output spectrum $\LocalVector{Y}$ when $\numel{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
 In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.
@@
 \end{align}
+where $\true{\LocalVector{U}}$ and $\true{\LocalVector{Y}}$ denote the `true' (noiseless) input-output spectra in the local window.
 Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
@@
 \begin{equation}
-  \left( \estim\theta - \true\theta \right) = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
+  \left( \estim\theta - \true\theta \right) 
+  = 
+  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  
+     \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
   \text{.}
@@
 which expresses the bias $\Delta\theta = \left( \estim\theta - \true\theta \right)$ of the estimated parameters.
-Since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$, this simplifies to
+Remark that 
 \begin{equation}
-  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
+  \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  
+  = 
+  \PartialDerivative{\ELSCost[0]{\theta} + \ELSCost[n]{\theta} }{\true\theta} 
+  = 
+  \PartialDerivative{\ELSCost[n]{\theta} }{\true\theta} 
+\end{equation}
+since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$ by definition.
+As such, the bias on the parameters can be simplified to
+\begin{equation}
+  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
   \text{.}
@@
 Do note that the estimated parameters are complex values but that $\ELSCost{\theta}$ is a real-valued function.
-This implies that the derivatives with respect to $\theta$ have to be calculated with respect to the real and imaginary part of $\theta$ separately as explained in~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012}.
+In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
+Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function of $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables which will be derived with respect to the real and imaginary part of $\theta$.
+Let us introduce the notations
+\begin{equation}
+  \ReIm{X} 
+  \isdef 
+  \begin{bmatrix}
+    \real{X}\\
+    \imag{X}
+  \end{bmatrix}
+  \quad  \text{,} \quad
+  \ReImImRe{X} 
+  \isdef 
+  \begin{bmatrix}
+    \real{X} & -\imag{X}\\
+    \imag{X} & \real{X}
+  \end{bmatrix}
+\end{equation}
+and the shorthand $\ReIm{\theta} = \ReImTheta$.
+E.g.
+in \citet[Section 15.9]{Pintelon2012} and \citet[Section 5.1]{Seber2007}, it is stated that $\ReImImRe{X}$ is isomorphic with $X$ such that operations on a complex matrix $X$ can be written as equivalent operations on the real matrix $\ReImImRe{X}$.
+Consequently, \citep[Equation 15-60]{Pintelon2012}:
+\begin{equation}
+  \left(
+     \PartialDerivative{\ELSCost{\theta,\conj{\theta}}}{\ReImTheta}
+  \right)^{\TT}
+  = 
+  2 
+  \ReIm{ \left(
+        \left(
+            \PartialDerivative{\ELSCost{\theta,\conj{\theta}}}{\theta}
+        \right)^{\HT}
+    \right) }
+  \text{.}
+\end{equation}
+To facilitate the derivations, we rewrite the expected cost functions in terms of $\theta$ and $\conj{\theta}$:
+\begin{align}
+   \ELSCost[0]{\theta,\conj{\theta}} & =
+      \frac{1}{F}
+           \sum_{r}
+           \LocalModel{Q}(      r,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
+           \LocalModel{Q}(\conj{r}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
+   \\
+   \LocalModel{Q}(r, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
+                 \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}(r)
+               - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}(r)
+               - \LocalModel{C}(r, \LocalVector{\theta})
+    \\             
+    \ELSCost[n]{\theta,\conj{\theta}} & =
+              \frac{\sigma_V^2}{F} 
+                     \sum_{r} 
+                               \LocalModel{A}(      r,        \LocalVector{\theta} ) 
+                               \LocalModel{A}(\conj{r}, \conj{\LocalVector{\theta}}) 
+\end{align}
+since $\conj{ \LocalModel{A}(r,\theta)} =  \LocalModel{A}(\conj{r},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
+
+\paragraph{Contributions to the first order derivative}
+
+\begin{align}
+  \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{a_i} 
+     &= 
+     \frac{\sigma_V^2}{F}
+     \sum_r r^i \LocalModel{A}(\conj{r},\conj{\LocalVector{\theta}}) 
+     & \forall i \in \set{1,\ldots,N_A}
+     \\
+   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{b_i} 
+   &= 0
+   & \forall i \in \set{0,\ldots,N_B}
+   \\
+   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{c_i} 
+   &= 0
+   &\forall i \in \set{0,\ldots,N_C}
+\end{align}
 
@@
 \begin{equation}
-  \Delta \LocalModel{G}(\omega) \approx \PartialDerivative{\LocalModel{G}(\theta, \omega)}{\theta} \Delta \theta
+  \Delta \LocalModel{G}(\omega) 
+     \approx 
+        \PartialDerivative{\LocalModel{G}(\theta, \omega)}
+                                          {\theta} 
+      \Delta \theta
 \end{equation}

### 2016-04-19 ch03-lrm/proofLOOCV.tex
LRM: part of bias, some intro

\begin{subappendices}
  \section{Proof of the \glsentrytext{LOOCV} statistic for linear models}

  We follow an approach similar to \citet{Hyndman2014LOOCV} and \citet[Section 12.3.2]{Seber2003} to prove that for a linear model, one can easily compute the \gls{PRESS}/\gls{LOOCV} statistic by means of the so-called `hat-diagonals', the diagonal entries of the hat matrix $H$.
  This is relevant, e.g. for local linear models used in the \gls{LRM} and hence also the \gls{LPM}.

  We consider the linear model
  \begin{equation}
    Z = K \theta + V
  \end{equation}
  with $Z \in \ComplexMatrix{N\times1}$, $\theta \in \ComplexMatrix{\nth \times 1}$, $K \in \ComplexMatrix{N \times \nth}$.
$V \in \ComplexMatrix{N \times 1}$ is a \gls{iid} complex gaussian random variable.
The least-squares solution of such a linear model is:
\begin{equation}
  \hat{\theta} = \left(K^{\HT} K \right)^{-1} K^{\HT} Z = \pinv{K} Z
\end{equation}
such that the estimated output $\hat{Z}$ is given by
\begin{equation}
  \hat{Z} = K \pinv{K} Z = H Z
\end{equation}
where $H$ is the so-called `hat matrix' that projects the measurements $Z$ onto the estimates $\hat{Z}$.

The \gls{PRESS} statistic used in \gls{LOOCV} is defined as~\citep[Chapter 12]{Seber2003}
\begin{equation}
  \PRESS \isdef 
    \frac{1}{N} 
      \sum_{i=1}^{N}
      \abs{
        Z_i - \ignoring{i}{\hat{Z}}
      }^2
\end{equation}
where $\hat{Z}_i$ is the $i^{\text{th}}$ row of $\hat{Z}$ and $\ignoring{i}{\hat{Z}}$ denotes the estimated $\hat{Z}_i$ when the $i^{\text{th}}$ data point (i.e. row) is removed from the estimation problem.
For linear models, this is equivalent to
\begin{equation}
  \PRESS_{\mathrm{linear}} = 
     \frac{1}{N}
     \sum_{i=1}^{N}
     \abs{
       \frac{Z_i - \hat{Z}_i}
                {1 - H_{ii}}
     }^2
     \text{.}
\end{equation}
Note that in this last expression, no terms $\ignoring{i}{\hat{Z}}$ occur, such that the statistic can be computed without having to compute $N$ additional linear models.
In this appendix, we prove that these last two expressions are equivalent for linear models.

\paragraph{Proof}
\TODO{proof}
Denote the design matrix $\ignoring{i}{K}$ to be the design matrix $K$ where the $i^{\text{th}}$ row has been removed:
\begin{equation}
  \ignoring{i}{K}
  \isdef
  \begin{bmatrix}
    K_{1,1} & K_{1,2} & \cdots & K_{1,\nth}\\
   && \vdots\\
    K_{i-1,1} & K_{i-1,1} & \cdots & K_{i-1,\nth}\\
    K_{i+1,1} & K_{i+1,1} & \cdots & K_{i+1,\nth}\\
    && \vdots\\
    K_{N,1} & K_{N,2} & \cdots & K_{N,\nth}\\
  \end{bmatrix}
\end{equation}

\begin{lemma}[Matrix Inversion Lemma]\label{lem:matrix-inversion-lemma}
The Woodbury formula, states that
\begin{equation*}
\left(A+UCV \right)^{-1} 
= 
A^{-1} - A^{-1} U \left(C^{-1}+VA^{-1}U \right)^{-1} VA^{-1}
\end{equation*}
when the dimensions of the matrices allow for the multiplications~\citep[Section 3.2.2]{matrixcookbook}.
\end{lemma}

\TODO{evt. Seber2003/ChristensenXXXX: QR decomposition to compute $H$}

\end{subappendices}

### 2016-04-20 ch03-lrm/lrm-paper.tex
More detail: bias LRM

@@
 \end{equation}
-Equivalently, this can be rewritten as a linear regression problem
+Here, $A\hadamard B$ denotes the Hadamard, or element-wise, product of matrices $A$ and $B$ which have identical dimensions.
+In \MATLAB the corresponding operator is \mcode{.*}.
+Equivalently, the last equation can be rewritten as a linear regression problem
 \begin{equation}
@@
 \begin{equation}
-  \Delta\theta = - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1}  \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
+  \Delta\theta = 
+  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} 
+     \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
   \text{.}
+  \label{eq:nparam:bias-basic}
 \end{equation}
@@
     \real{X} & -\imag{X}\\
-    \imag{X} & \real{X}
+    \imag{X} & \hphantom{-} \real{X}
   \end{bmatrix}
@@
 in \citet[Section 15.9]{Pintelon2012} and \citet[Section 5.1]{Seber2007}, it is stated that $\ReImImRe{X}$ is isomorphic with $X$ such that operations on a complex matrix $X$ can be written as equivalent operations on the real matrix $\ReImImRe{X}$.
-Consequently, \citep[Equation 15-60]{Pintelon2012}:
-\begin{equation}
-  \left(
-     \PartialDerivative{\ELSCost{\theta,\conj{\theta}}}{\ReImTheta}
-  \right)^{\TT}
-  = 
-  2 
-  \ReIm{ \left(
-        \left(
-            \PartialDerivative{\ELSCost{\theta,\conj{\theta}}}{\theta}
-        \right)^{\HT}
-    \right) }
-  \text{.}
-\end{equation}
-To facilitate the derivations, we rewrite the expected cost functions in terms of $\theta$ and $\conj{\theta}$:
+As a result,
+\begin{align}
+  \Delta\theta &=
+  \left( \mat{1 & j} \kron \Identity{\nth[]}  \right) 
+  \ReIm{\Delta\theta}
+  \\
+  \ReIm{\Delta\theta} &= 
+  - \ReImImRe{ \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} }
+    \ReIm{ \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}}
+\end{align}
+To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
 \begin{align}
@@
 since $\conj{ \LocalModel{A}(r,\theta)} =  \LocalModel{A}(\conj{r},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
+Remember also that $\theta = \mat{\theta_A^{\TT} & \theta_B^{\TT} & \theta_C^{\TT}}$.
 
 \paragraph{Contributions to the first order derivative}
-
+The last term, i.e. the first order derivative, 
+\begin{equation}
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta}
+  = 
+  \begin{bmatrix}
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_A} &
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_B} &
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C} &
+  \end{bmatrix}
+\end{equation}
+is broken up into the parts pertaining to respectively the $A$, $B$ and $C$ polynomials.
+The respective components are given by:
 \begin{align}
@@
    &\forall i \in \set{0,\ldots,N_C}
+   \text{.}
 \end{align}
+It can be seen that only the factors pertaining to $\LocalModel{A}$ are present.
+As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
 

### 2016-04-21 ch03-lrm/lrm-paper.tex
Lots of work on CH03

@@
   &\approx
-  \frac{\sum_{i=0}^{N_B} b_i d^i}
-            {1 + \sum_{i=1}^{N_A} a_i d^i}
+  \frac{\sum_{i=0}^{\order{B}} b_i d^i}
+            {1 + \sum_{i=1}^{\order{A}} a_i d^i}
     &\isdef
@@
   \true{T}(\omega_k + d) &\approx
-  \frac{\sum_{i=0}^{N_C} c_i d^i}
-            {1 + \sum_{i=1}^{N_A} a_i d^i}
+  \frac{\sum_{i=0}^{\order{C}} c_i d^i}
+            {1 + \sum_{i=1}^{\order{A}} a_i d^i}
     &\isdef 
@@
 
-Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} easily leads to ill-conditioned systems, additional measures are taken to improve numerical conditioning.
+Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
 To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
@@
 \end{multline}
-The minimizer $\estim\theta$ of this function can be obtained by equating the derivative
+The minimizer $\estimated\theta$ of this function can be obtained by equating the derivative
 \begin{equation}
-  \PartialDerivative{\ELSCost{\estim\theta}}{\estim\theta} = \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
-   \left( \estim\theta - \true\theta \right)
+  \PartialDerivative{\ELSCost{\estimated\theta}}
+                                          {\estimated\theta} 
+  = 
+  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} 
+  + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \left( \estimated\theta - \true\theta \right)
 \end{equation}
@@
 \begin{equation}
-  \left( \estim\theta - \true\theta \right) 
+  \left( \estimated\theta - \true\theta \right) 
   = 
@@
 \end{equation}
-which expresses the bias $\Delta\theta = \left( \estim\theta - \true\theta \right)$ of the estimated parameters.
+which expresses the bias $\Delta\theta = \left( \estimated\theta - \true\theta \right)$ of the estimated parameters.
 Remark that 
@@
 
-Do note that the estimated parameters are complex values but that $\ELSCost{\theta}$ is a real-valued function.
+Do note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
 In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
-Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function of $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables which will be derived with respect to the real and imaginary part of $\theta$.
-Let us introduce the notations
-\begin{equation}
-  \ReIm{X} 
-  \isdef 
-  \begin{bmatrix}
-    \real{X}\\
-    \imag{X}
-  \end{bmatrix}
-  \quad  \text{,} \quad
-  \ReImImRe{X} 
-  \isdef 
-  \begin{bmatrix}
-    \real{X} & -\imag{X}\\
-    \imag{X} & \hphantom{-} \real{X}
-  \end{bmatrix}
-\end{equation}
-and the shorthand $\ReIm{\theta} = \ReImTheta$.
-E.g.
+Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables~\citep{Hjorungnes2007,Hjorungnes2011}.
+The derivatives are then computed with respect to these variables.
+% Let us introduce the notations
+% \begin{equation}
+%   \ReIm{X} 
+%   \isdef 
+%   \begin{bmatrix}
+%     \real{X}\\
+%     \imag{X}
+%   \end{bmatrix}
+%   \quad  \text{,} \quad
+%   \ReImImRe{X} 
+%   \isdef 
+%   \begin{bmatrix}
+%     \real{X} & -\imag{X}\\
+%     \imag{X} & \hphantom{-} \real{X}
+%   \end{bmatrix}
+% \end{equation}
+% and the shorthand $\ReIm{\theta} = \ReImTheta$.
+% E.g.
 in \citet[Section 15.9]{Pintelon2012} and \citet[Section 5.1]{Seber2007}, it is stated that $\ReImImRe{X}$ is isomorphic with $X$ such that operations on a complex matrix $X$ can be written as equivalent operations on the real matrix $\ReImImRe{X}$.
-As a result,
-\begin{align}
-  \Delta\theta &=
-  \left( \mat{1 & j} \kron \Identity{\nth[]}  \right) 
-  \ReIm{\Delta\theta}
-  \\
-  \ReIm{\Delta\theta} &= 
-  - \ReImImRe{ \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} }
-    \ReIm{ \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}}
-\end{align}
+% As a result,
+% \begin{align}
+%   \Delta\theta &=
+%   \left( \mat{1 & j} \kron \Identity{\nth[]}  \right) 
+%   \ReIm{\Delta\theta}
+%   \\
+%   \ReIm{\Delta\theta} &= 
+%   - \ReImImRe{ \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} }
+%     \ReIm{ \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}}
+% \end{align}
+% where $\kron$ denotes the Kronecker product~\citep{Brewer1978}.
 To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
@@
 \paragraph{Contributions to the first order derivative}
-The last term, i.e. the first order derivative, 
+The last term in \eqref{eq:nparam:bias-basic}, i.e. the first order derivative,  is given by
 \begin{equation}
@@
 \end{equation}
-is broken up into the parts pertaining to respectively the $A$, $B$ and $C$ polynomials.
+and split into the parts pertaining to respectively $\LocalModel{A}$, $\LocalModel{B}$ and, $\LocalModel{C}$.
 The respective components are given by:
@@
      \sum_r r^i \LocalModel{A}(\conj{r},\conj{\LocalVector{\theta}}) 
-     & \forall i \in \set{1,\ldots,N_A}
+     & \forall i \in \set{1,\ldots,\order{A}}
      \\
@@
    &= 0
-   & \forall i \in \set{0,\ldots,N_B}
+   & \forall i \in \set{0,\ldots,\order{B}}
    \\
@@
    &= 0
-   &\forall i \in \set{0,\ldots,N_C}
+   &\forall i \in \set{0,\ldots,\order{C}}
    \text{.}
@@
 As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
+Consequently, only the poles are shifted by the presence of noise.
 
@@
       \Delta \theta
+      \text{.}
+\end{equation}
+The derivative in that expression can be evaluated easily
+\begin{align}
+    \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta} 
+     &=
+     \begin{bmatrix}
+       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_A} &
+       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_B} &
+       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_C} 
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_A} 
+     &=
+     \begin{bmatrix}
+         r^1 & r^2 & \deemph{\cdots} & r^{\order{A}}
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_B} 
+     &=
+     \begin{bmatrix}
+         1 & r^1 & r^2 & \deemph{\cdots} & r^{\order{B}}
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_C} 
+     &=
+     \Zero{1 \times \order{C}+1}
+     \text{.}
+\end{align}
+
+However, the sparsity of $\Delta\theta$ can be exploited such that the bias on the \gls{FRF} is expressed as:
+\begin{equation}
+  \Delta \LocalModel{G}(\theta,r)
+  \approx
+  - \LocalModel{A}(r,\theta)^{-2}
 \end{equation}
@@
 \section{Order selection}
-Selecting suitable values of $\numel{W}$, $\numel{B}$, $\numel{A}$ and $\numel{C}$ obviously affects the quality of the obtained local models.
+Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
 For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
-In particular $\numel{C} \leq \max\set{\numel{B},\numel{A}}$ and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that $2N_W + 1 \geq N_B + N_A + N_C + 2$.
+In particular~\citep{Pintelon2010LPM1}:
+\begin{equation}
+\order{C} \leq \max\set{\order{B},\order{A}}
+\end{equation}
+ and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
+ \begin{equation}
+ \nWind \geq \order{B} + \order{A} + \order{C} + 2
+ \text{.}
+ \end{equation}
 
-Different heuristics exist to select the local bandwidth , e.g.~\citep{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
-As such, we focus mainly on the selection of the model order hyper-parameters ($N_A$, $N_B$ and $N_C$) for a fixed value of $N$.
+Different heuristics exist to select the local bandwidth $\nWind$, e.g.~\citet{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
+As such, we focus mainly on the selection of the model order hyper-parameters ($\order{A}$, $\order{B}$ and $\order{C}$) for a fixed value of $\nWind$.
 
-In this paper, we take an approach that decides amongst a group of candidate models, which model is a good model: i.e. one that captures that system dynamics but remains parsimonious.
+Here, we take an approach that decides amongst a group of candidate models $\Set{M_1, \ldots, M_N}$, which model $M_i$ is the best model according to some criterion: i.e.
+one that captures that system dynamics but remains parsimonious.
 To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g.
@@
 Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
+In the following, a short overview is given of different approaches.
+
 \paragraph{Plug-in methods}
 In plug-in methods, a goodness-of-fit criterion (e.g.
-the log-likelihood function $\mathcal{L}$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
+the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
 E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
-\begin{equation}
-  L_{\mathrm{AIC(c)}} = - 2  \mathcal{L}(M | Z) + 2 \numel{\theta} + c \frac{2 \numel{\theta} (\numel{\theta} + 1)}{\numel{\Window} - \numel{\theta} - 1}
-\end{equation}
-where $\numel{\Window}$ is the number of  estimated parameters in the model $M(\theta)$.
-For \gls{AIC} $c=0$, and $c=1$ produces the \gls{AICc}.
-In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\numel{Z} \to \infty$, which is obviously an unwarranted choice.
+\begin{align}
+L_{\mathrm{\AIC}} &=
+ - 2  \loglikelihood{M | Z} 
+ + 2 \numel{\theta}\\
+L_{\mathrm{\AICc}} &= 
+- 2  \loglikelihood{M | Z} 
++   \frac{2 \nth\nWind}{\nWind - \nth - 1}
+\end{align}
+where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
+In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e.
+$\nWind \to \infty$, which is obviously an unwarranted choice in this context.
 The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
@@
 \begin{remark}
-It should be noted that due to $\mathcal{L}(M | Z)$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is tightly coupled with the particular dataset $Z$.
-Practically, this means that such criteria can only be used to compare local models that estimated from the same local dataset (i.e. they have the same $\numel{\Window}$ and center frequency).
+It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
+Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
+Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
 \end{remark}
@@
 \begin{equation}
- \PRESS = \frac{1}{2N_W+1} \sum_{r=-N_W}^{N_W} 
-                          \abs{\ignoring{r}{\LocalVector{e}}}^2
+ \PRESS = 
+ \frac{1}{\nWind} 
+  \sum_{r \in \LocalShifts{}}
+    \abs{\ignoring{r}{\LocalVector{E}}}^2
     \text{,}
@@
 \end{equation}
-where $\ignoring{r}{\LocalVector{e}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e.
+where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e.
 the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
-The model with the smallest \gls{PRESS} is retained.
-In general, this means that \gls{LOOCV} requires estimating $2N_W + 1$ additional models (one for each omitted data point) and hence can be very time-consuming.
+To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
+In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.
 
@@
 \begin{equation}
-G_0(z) = \frac{0.64587 z + 0.64143}
+\true{G}(z) = \frac{0.64587 z + 0.64143}
                                       {47.9426 z^2 - 51.2955 z + 46.9933}
@@
 \end{equation}
-where $\BW$ is the frequency range where
+where $\BW$ is the frequency range of the $3 \unit{dB}$ bandwidth of the system, i.e. where $\abs{G_0} \geq \norm[\infty]{\true G} - 3 \unit{dB}$.
 
 \TODO{plot example spectrums}
+
+We then compute basic statistics of the estimated \glspl{FRF} over all  Monte Carlo runs.
+Specifically, the mean value
+\begin{align}
+  \sampleMean{\bullet}(\omega_k) & 
+  \isdef
+    \frac{1}{\nMC}
+    \sum_{i=1}^{\nMC}
+    \atSimulation[i]{\model{\bullet}(\omega_k)}
+  &
+  \approx
+  \expectedValue{\model{\bullet}(\omega_k)}
+  \\
+  \sampleBias{\bullet}(\omega_k) &
+    \isdef
+    \frac{1}{\nMC}
+    \sum_{i=1}^{\nMC}
+    \atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k)
+    &
+    \approx
+    \Bias{\model{\bullet}(\omega_k)}
+    \\
+    \sampleVariance{\bullet}(\omega_k) &
+    \isdef
+    \frac{1}{\nMC - 1}
+    \sum_{i=1}^{\nMC}
+    \left(\atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k) \right)
+    \conj { \left(\atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k) \right) }
+    &
+    \approx
+    \Var{\model{\bullet}(\omega_k)}
+\end{align}
 
@@
 \TODO{insert figure: err vs SNR}
+\paragraph{Noiseless case}
+In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM} and \gls{ETFE}.
+For the \gls{ETFE}, it can be seen that the error is very high.
+This can be expected since the \gls{ETFE} does not separate transient and leakage contributions.
+this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
+As such, 
+\TODO{figure: RMS, bias, std voor inf SNR}
+
+\TODO{figure: RMS, bias, std voor high SNR}
+\TODO{figure: RMS, bias, std voor 20 dB SNR}
+\TODO{figure: RMS, bias, std voor 10 dB SNR}
 

### 2016-04-21 ch03-lrm/lrm-paper.tex
Quite some work on CH03

@@
   &\approx
-  \frac{\sum_{i=0}^{\order{B}} b_i d^i}
-            {1 + \sum_{i=1}^{\order{A}} a_i d^i}
+  \frac{\Sum_{i=0}^{\order{B}} b_i d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
     &\isdef
@@
   \true{T}(\omega_k + d) &\approx
-  \frac{\sum_{i=0}^{\order{C}} c_i d^i}
-            {1 + \sum_{i=1}^{\order{A}} a_i d^i}
+  \frac{\Sum_{i=0}^{\order{C}} c_i d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
     &\isdef 
@@
 In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
-Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold throughout this paper.
-To alleviate the notations, the subscript $k$ is often omitted.
+Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
+To alleviate the notations, the subscript $k$ is omitted unless
 
-To estimate the local parameters $\LocalVector{\theta} = \mat{a_1\; \cdots\; b_0 \cdots\; c_0\; \cdots}^{\T}$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
+The local parameters $\theta$  
+\begin{equation}
+\theta \isdef 
+\begin{bmatrix}
+\theta_A\\ 
+\theta_B\\
+\theta_C
+\end{bmatrix}
+\qquad \text{ with }
+\theta_A \isdef
+\begin{bmatrix}
+a_1\\ \vdots\\ a_{\order{A}}
+\end{bmatrix}
+\text{, }
+\theta_B \isdef
+\begin{bmatrix}
+b_0\\ \vdots\\ b_{\order{B}}
+\end{bmatrix}
+\text{, and }
+\theta_C \isdef
+\begin{bmatrix}
+c_0\\ \vdots\\ c_{\order{C}}
+\end{bmatrix}
+\end{equation}
+in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
 \begin{equation}
@@
 and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
-$
+\begin{equation}
   \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
-$, where $\hadamard$ denotes the entry-wise product (or Hadamard product).
+\text{,}
+\end{equation} 
+where $\hadamard$ denotes the element-wise product (also, Hadamard product).
 Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
@@
 \end{equation}
-Note that this encompasses $\numel{\Window}$ complex equations in the $\numel{\theta} = \numel{A} + \numel{B} + \numel{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
+Note that this encompasses $\nWind$ complex equations in the $\nth = \numel{A} + \numel{B} + \numel{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
 Consequently, a necessary condition to compute the model parameters is that
 \begin{equation}
-  \DOF = \numel{\Window} - \numel{\theta}
+  \DOF = \nWind - \nth
        = 2 \numel{W} - \numel{A} - \numel{B} - \numel{C} - 1
@@
 \begin{equation}
-  \LocalModel{A}\LocalVector{Y} \approx \LocalModel{B} \LocalVector{U}  - \LocalVector{C}
+  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
   \text{,}
@@
 \end{equation}
-Here, $A\hadamard B$ denotes the Hadamard, or element-wise, product of matrices $A$ and $B$ which have identical dimensions.
-In \MATLAB the corresponding operator is \mcode{.*}.
+where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e.
+the disturbing noise is assumed white over the local frequency window.
 Equivalently, the last equation can be rewritten as a linear regression problem
 \begin{equation}
-  \LocalVector{Y} = \LocalVector{K} \LocalVector{\theta} + \LocalModel{V}
+  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
 \end{equation}
-where $\LocalVector{K}$ is the so-called design matrix (or observation matrix):
+where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
 \begin{align}
   \label{eq:nparam:designMatrix}
-  \LocalVector{K} 
+  \LocalMatrix{K} 
     & \isdef 
   \mat{
-     \LocalVector{K}_A &
-     \LocalVector{K}_B & 
-     \LocalVector{K}_C
+     \LocalMatrix{K}_A &
+     \LocalMatrix{K}_B & 
+     \LocalMatrix{K}_C
   }\\
-  \LocalVector{K}_A 
+  \LocalMatrix{K}_A 
     &\isdef
@@
     }\\
-  \LocalVector{K}_B 
+  \LocalMatrix{K}_B 
     &\isdef
@@
     }\\
-  \LocalVector{K}_C
+  \LocalMatrix{K}_C
     &\isdef
@@
 \end{align}
-and $\LocalModel{V}$ are the model residuals.
 This formulation facilitates to solve the problem in a one-step approach:
@@
   \LocalVector{\theta}_{\LRM} 
-    \isdef \pinv{\LocalVector{K}} \LocalVector{Y}
-    = \left( \LocalVector{K}^{\HT} \LocalVector{K} \right)^{-1} \LocalVector{K}^{\HT} \LocalVector{Y}
+    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
+    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
 \end{equation}
-where $\pinv{K}$ denotes the Moore-Penroose pseudo-inverse of $K$.
+where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.
 
 \TODO{hier voortschrijven}
-
-\subsection{The Local Rational Method with Iterative Cost}
-
-\subsection{Notes}
 
@@
 
+\subsection{The Local Rational Method with Iterative Cost}
+
 \TODO{define local cost}
@@
 To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
-Let us denote the expected value of the cost function over all measurements $\LocalVector{Z}$ as
+Let us denote the expected value of the cost function over all measurements $\LocalVector{Z} = \mat{\LocalMatrix{Y}, \LocalMatrix{U}}$ as
 \begin{align}
@@
     \ELSCost[0]{\theta} & \isdef 
-            \frac{1}{F} 
+            \frac{1}{\nWind} 
                 \sum_{r} 
@@
     \ELSCost[n]{\theta} & \isdef 
-              \frac{1}{F} 
+              \frac{1}{\nWind} 
                      \sum_{r} 
@@
    \ELSCost[0]{\theta,\conj{\theta}} & =
-      \frac{1}{F}
+      \frac{1}{\nWind}
            \sum_{r}
@@
     \ELSCost[n]{\theta,\conj{\theta}} & =
-              \frac{\sigma_V^2}{F} 
+              \frac{\sigma_V^2}{\nWind} 
                      \sum_{r} 
@@
   \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_B} &
-  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C} &
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C}
   \end{bmatrix}
@@
      &= 
-     \frac{\sigma_V^2}{F}
+     \frac{\sigma_V^2}{\nWind}
      \sum_r r^i \LocalModel{A}(\conj{r},\conj{\LocalVector{\theta}}) 
-     & \forall i \in \set{1,\ldots,\order{A}}
+     && \forall i \in \set{1,\ldots,\order{A}}
      \\
@@
    &= 0
-   & \forall i \in \set{0,\ldots,\order{B}}
+   && \forall i \in \set{0,\ldots,\order{B}}
    \\
@@
    &= 0
-   &\forall i \in \set{0,\ldots,\order{C}}
+   &&\forall i \in \set{0,\ldots,\order{C}}
    \text{.}
 \end{align}
-It can be seen that only the factors pertaining to $\LocalModel{A}$ are present.
+It can be seen that only the factors pertaining to $\theta_{A}$ are present.
 As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
-Consequently, only the poles are shifted by the presence of noise.
+Consequently, only the poles can shifted by the presence of noise.
+As such, the bias term $\Delta \theta$ can be written in the following sparse form:
+\begin{equation}
+  \Delta \theta = 
+  \begin{bmatrix}
+    \Delta \theta_A\\
+    \Delta \theta_B\\
+    \Delta \theta_C
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    \Delta \theta_A\\
+    \deemph{\Zero{\order{B}+1\times1}}\\
+    \deemph{\Zero{\order{C}+1\times1}}
+  \end{bmatrix}
+  \text{.}
+  \label{eq:nparam:lrm:bias:sparse}
+\end{equation}
 
 \TODO{write out subexpressions}
+\paragraph{Bias on the \glsentrydesc{FRF}}
 As a first order approximation, the bias on the \gls{FRF} can be written as
@@
      &=
+     - \frac{\LocalModel{B}(\theta, r)}{\LocalModel{A}^2(\theta, r)}
      \begin{bmatrix}
@@
      &=
+     \frac{1}{\LocalModel{A}(\theta, r)}
      \begin{bmatrix}
@@
 
-However, the sparsity of $\Delta\theta$ can be exploited such that the bias on the \gls{FRF} is expressed as:
+However, the sparsity of $\Delta\theta$, see \eqref{eq:nparam:lrm:bias:sparse}, can be exploited such that the bias on the \gls{FRF} can be expressed as:
 \begin{equation}
@@
   \approx
-  - \LocalModel{A}(r,\theta)^{-2}
+  \frac{\LocalModel{G}(\theta, r)}{\LocalModel{}}
 \end{equation}
@@
  - 2  \loglikelihood{M | Z} 
- + 2 \numel{\theta}\\
+ + 2 \nth\\
 L_{\mathrm{\AICc}} &= 
@@
   }
+  \text{,}
 \end{equation}
-To select the best model $M_{\star}$ with such a criterion, the model $M_k$ among a set of models $\set{M_1, M_2, \ldots}$ that produces the smallest value of $L_{\mathrm{AICc}}$ is retained.
+which is the only model that is hence retained.
 
@@
 For linear models (i.e.
-$\LocalVector{Y} = \LocalVector{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
+$\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
 \begin{equation}
@@
 where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
-$\LocalVector{H} = \LocalVector{K} \pinv{\LocalVector{K}}$ is the so-called `hat-matrix' that is known to be idempotent.
+$\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.
 
@@
 
-We then compute basic statistics of the estimated \glspl{FRF} over all  Monte Carlo runs.
-Specifically, the mean value
+We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over all  Monte Carlo runs.
+Specifically, the following values
 \begin{align}
@@
     \sum_{i=1}^{\nMC}
-    \atSimulation[i]{\model{\bullet}(\omega_k)}
-  &
-  \approx
-  \expectedValue{\model{\bullet}(\omega_k)}
+    \model[\atSimulation{i}]{\bullet}(\omega_k)
   \\
@@
     \sum_{i=1}^{\nMC}
-    \atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k)
-    &
-    \approx
-    \Bias{\model{\bullet}(\omega_k)}
+    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
+    = 
+    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
     \\
@@
     \sum_{i=1}^{\nMC}
-    \left(\atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k) \right)
-    \conj { \left(\atSimulation[i]{\model{\bullet}(\omega_k)} - \true{G}(\omega_k) \right) }
-    &
-    \approx
-    \Var{\model{\bullet}(\omega_k)}
+                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
+    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
 \end{align}
+are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
+Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$.
 

### 2016-04-21 ch03-lrm/lrm-paper.tex
Some TODOfigs

@@
     \item \TODO{choice $s$ or $z$}
-    \item \TODO{bounds RMSE, Bias, StdDev}
     \item \TODO{derivation Bias}
-    \item \TODO{comparison LPM/LRM}
       \begin{itemize}
@@
     \item \TODO{influence of noise filter: mismatch with model}
-    \item \TODO{comparison LRM/LRik (LBTLS)}
 \end{itemize}
@@
 
-\subsection{The Local Rational Method with Iterative Cost}
-
-\TODO{define local cost}
-\TODO{define local design matrix}
+\TODO{define notations for LPM etc.}
 
@@
 
-\section{Order selection}
-Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
-For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
-In particular~\citep{Pintelon2010LPM1}:
-\begin{equation}
-\order{C} \leq \max\set{\order{B},\order{A}}
-\end{equation}
- and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
- \begin{equation}
- \nWind \geq \order{B} + \order{A} + \order{C} + 2
- \text{.}
- \end{equation}
-
-Different heuristics exist to select the local bandwidth $\nWind$, e.g.~\citet{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
-As such, we focus mainly on the selection of the model order hyper-parameters ($\order{A}$, $\order{B}$ and $\order{C}$) for a fixed value of $\nWind$.
-
-Here, we take an approach that decides amongst a group of candidate models $\Set{M_1, \ldots, M_N}$, which model $M_i$ is the best model according to some criterion: i.e.
-one that captures that system dynamics but remains parsimonious.
-To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g.
-value of the cost function, $R^2$, \ldots) and model complexity into account to ensure that the model captures only the systematic behavior and not random variations of the particular measurement.
-The latter is often done using `cross-validation'.
-
-In statistical learning, many relevant cross-validation approaches exist.
-Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
-In the following, a short overview is given of different approaches.
-
-\paragraph{Plug-in methods}
-In plug-in methods, a goodness-of-fit criterion (e.g.
-the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
-E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
-\begin{align}
-L_{\mathrm{\AIC}} &=
- - 2  \loglikelihood{M | Z} 
- + 2 \nth\\
-L_{\mathrm{\AICc}} &= 
-- 2  \loglikelihood{M | Z} 
-+   \frac{2 \nth\nWind}{\nWind - \nth - 1}
-\end{align}
-where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
-In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e.
-$\nWind \to \infty$, which is obviously an unwarranted choice in this context.
-The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
-\begin{equation}
-  M_{\star} \isdef 
-  \arg_{M} \min 
-  \Set{
-    L_{\mathrm{AIC(c)}}(M)
-  }
-  \text{,}
-\end{equation}
-which is the only model that is hence retained.
-
-\begin{remark}
-It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
-Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
-Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
-\end{remark}
-
-\paragraph{Holdout method}
-The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g.
-$70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g.
-cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
-By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.
-
-\begin{remark}
-Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
-As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
-\end{remark}
-
-\paragraph{Leave-out cross-validation}
-Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
-Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
-In effect, such an approach calculates the \gls{PRESS} for each local model:
-\begin{equation}
- \PRESS = 
- \frac{1}{\nWind} 
-  \sum_{r \in \LocalShifts{}}
-    \abs{\ignoring{r}{\LocalVector{E}}}^2
-    \text{,}
-\label{eq:PRESS-general}
-\end{equation}
-where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e.
-the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
-To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
-In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.
-
-For linear models (i.e.
-$\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
-\begin{equation}
-\PRESS = \frac{\LocalVector{E}^{\HT} \LocalVector{W}^{-1} \LocalVector{E}}{2N_W + 1}
-\end{equation}
-where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
-$\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.
-
 \section{Simulation}
@@
 
-\TODO{SNR}
 The \gls{SNR} in the system bandwidth $\BW$ is defined as
@@
 \TODO{plot example spectrums}
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[Example spectra]
+  \label{fig:nparam:spectra}
+\end{figure}
 
@@
 
-\TODO{insert figure: Y(Y,E,T) vs freq}
-\TODO{insert figure: err vs SNR}
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[Y(Y,E,T) vs freq of single simulation]
+\end{figure}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
+\end{figure}
+
+\TODO{describe aggregation over $\omega$}
+
 \paragraph{Noiseless case}
@@
 this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
-As such, 
-\TODO{figure: RMS, bias, std voor inf SNR}
+As such, \TODO{afschrijven}
 
-\TODO{figure: RMS, bias, std voor high SNR}
-\TODO{figure: RMS, bias, std voor 20 dB SNR}
-\TODO{figure: RMS, bias, std voor 10 dB SNR}
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[ RMS, bias, std for $\SNR = \infty$]
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in a relative approximation error of $-100\unit{dB}$.}
+  \label{fig:nparam:comparison:noiseless}
+\end{figure}
+
+\paragraph{Good signal-to-noise ratios}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[ RMS, bias, std for $\SNR = 60\unit{dB}$]
+  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system.
+A relative approximation error of $-100 \unit{dB}$ is observed.}
+  \label{fig:nparam:comparison:hiSNR}
+\end{figure}
+
+\paragraph{Poor signal-to-noise ratios}
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[ RMS, bias, std for $\SNR = 20\unit{dB}$]
+  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.
+The \gls{LRM} outperforms the \gls{LPM}.}
+  \label{fig:nparam:comparison:lowSNR}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOfig[ RMS, bias, std for $\SNR = 10\unit{dB}$]
+  \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.
+An approximation error of $-100 \unit{dB}$ is observed.}
+  \label{fig:nparam:comparison:terribleSNR}
+\end{figure}
+
+\begin{guideline}{For resonant systems, use the LRM when $\SNR \geq 20 \unit{dB}$}
+\end{guideline}
+
+\begin{guideline}{For long measurements, the choice of local modeling method does not matter}
+\end{guideline}
+
+\begin{remark}
+In all the simulations, it can be seen that for $\nWind \to \infty$, the error tapers off.
+\TODO{andere pieken gaan in de praktijk alles om zeep helpen en dus bovengrens stellen}
+\end{remark}
 

### 2016-04-21 ch03-lrm/nonparametric.tex
LRM: part of bias, some intro
Lots of work on CH03
Some TODOfigs

--- 2016-03-30 ch03-lrm/nonparametric.tex
@@
-\chapter{Non-parametric modeling}
+\chapter{Non-parametric Modeling}
 \def\thisDir{ch03-lrm}
@@
 \label{sec:nonparametric}
+% \myEpigraph{}{}{}
 
@@
 
-\section{\TODO{LPM}}
-\section{\TODO{LRM}}
 \input{\thisDir/lrm-paper.tex}
+
+\section{Trading off the bias and variance}
+
+\subsection{Order selection}
+Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
+For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
+In particular~\citep{Pintelon2010LPM1}:
+\begin{equation}
+\order{C} \leq \max\set{\order{B},\order{A}}
+\end{equation}
+ and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
+ \begin{equation}
+ \nWind \geq \order{B} + \order{A} + \order{C} + 2
+ \text{.}
+ \end{equation}
+
+Different heuristics exist to select the local bandwidth $\nWind$, e.g.~\citet{Fan1995,Thummala2012LPMBW,Stenman2000ASETFE} in the framework of local modeling approaches.
+As such, we focus mainly on the selection of the model order hyper-parameters ($\order{A}$, $\order{B}$ and $\order{C}$) for a fixed value of $\nWind$.
+
+Here, we take an approach that decides amongst a group of candidate models $\Set{M_1, \ldots, M_N}$, which model $M_i$ is the best model according to some criterion: i.e.
+one that captures that system dynamics but remains parsimonious.
+To do so, one needs to define a criterion that both takes `goodness-of-fit' (e.g.
+value of the cost function, $R^2$, \ldots) and model complexity into account to ensure that the model captures only the systematic behavior and not random variations of the particular measurement.
+The latter is often done using `cross-validation'.
+
+In statistical learning, many relevant cross-validation approaches exist.
+Within the system identification community a few simple approaches have been widely adopted~\citep[Chapter 11]{Pintelon2012} to ensure that one does not overmodel the data.
+In the following, a short overview is given of different approaches.
+
+\paragraph{Plug-in methods}
+In plug-in methods, a goodness-of-fit criterion (e.g.
+the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
+E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
+\begin{align}
+L_{\mathrm{\AIC}} &=
+ - 2  \loglikelihood{M | Z} 
+ + 2 \nth\\
+L_{\mathrm{\AICc}} &= 
+- 2  \loglikelihood{M | Z} 
++   \frac{2 \nth\nWind}{\nWind - \nth - 1}
+\end{align}
+where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
+In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e.
+$\nWind \to \infty$, which is obviously an unwarranted choice in this context.
+The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
+\begin{equation}
+  M_{\star} \isdef 
+  \arg_{M} \min 
+  \Set{
+    L_{\mathrm{AIC(c)}}(M)
+  }
+  \text{,}
+\end{equation}
+which is the only model that is hence retained.
+
+\begin{remark}
+It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
+Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
+Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
+\end{remark}
+
+\paragraph{Holdout method}
+The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g.
+$70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g.
+cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
+By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.
+
+\begin{remark}
+Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
+As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
+\end{remark}
+
+\paragraph{Leave-out cross-validation}
+Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
+Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
+In effect, such an approach calculates the \gls{PRESS} for each local model:
+\begin{equation}
+ \PRESS = 
+ \frac{1}{\nWind} 
+  \sum_{r \in \LocalShifts{}}
+    \abs{\ignoring{r}{\LocalVector{E}}}^2
+    \text{,}
+\label{eq:PRESS-general}
+\end{equation}
+where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e.
+the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
+To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
+In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.
+
+For linear models (i.e.
+$\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
+\begin{equation}
+\PRESS = \frac{\LocalVector{E}^{\HT} \LocalVector{W}^{-1} \LocalVector{E}}{2N_W + 1}
+\end{equation}
+where $\LocalVector{E}$ is the residual vector of the full estimation and $\LocalVector{W}$ is a diagonal weighting matrix with $\LocalVector{W}_{ii} = (1 - \LocalVector{H}_{ii})^{\HT} (1 - \LocalVector{H}_{ii})$ and
+$\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.
 
@@
 
-\section{\TODO{Bias-variance trade-off }}
-\TODO{import LRM paper}
-
-\subsection{\TODO{Tuning rules}}
-\subsubsection{\TODO{Tuning using an Oracle}}
-\subsubsection{\TODO{Cross-validation}}
-
-\subsection{\TODO{Application}}
-
-\subsubsection{\TODO{AVIS}}
-% \subsubsection{\TODO{F16}}
+\input{\thisDir/proofLOOCV.tex}

### 2016-04-21 ch05-initvals/initial-values.tex
Some TODOfigs

@@
 
-  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
+  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
   In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
@@
 \begin{align}
-\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
+\true{G}(\omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
 \\
-T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
+T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
 \end{align}
@@
 \begin{equation}
-\hat{G}_\text{LPM}(\Omega_k) = \hat{G}_k
+\hat{G}_\text{LPM}(\omega_k) = \hat{G}_k
 \text{.}
@@
 \emph{Impulse response truncation}. 
-The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \mathrm{IDFT}\, \left( \hat{G}_{\LPM}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.
+The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \IDFT \left( \hat{G}_{\LPM}(\omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.
 
@@
 where $\gamma=1$ was used in this chapter for simplicity.
-By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\Omega_k) = \mathrm{DFT} \left( g_{\trunc}(t)\right)$ further.
+By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\omega_k) = \DFT \left( g_{\trunc}(t)\right)$ further.
 This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
@@
 \end{align}
- which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
+ which, in practice, is computed by using the adaptive global quadrature algorithm provided by the \MATLAB function \code{integral}.
 The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in \secref{sec:initial-values:CompuSR}.

### 2016-04-21 ch02-qlogms/excitation-design.tex
Changes all over the place
Some uniformity stuff
LRM: part of bias, some intro
Uniform commands: part 1

@@
-\chapter{Design of excitation signals}
+\chapter{Design of Excitation Signals}
 \label{sec:excitation}
@@
 \begin{align}
-\IF & = \lim_{N\rightarrow\infty}
+\Fi{\theta} & = \lim_{N\rightarrow\infty}
           \frac{1}{N}
@@
 \end{align}
-By Parseval's theorem, $\IF$ can be expressed as
-\begin{align}
-\IF &= \frac{1}{\pi}
+By Parseval's theorem, $\Fi{\theta}$ can be expressed as
+\begin{align}
+\Fi{\theta} &= \frac{1}{\pi}
          \int\limits_0^\infty \RealPart
@@
 The information matrix is a function of the input power spectrum $\powerspec{u}$, which is the only entity that can be used to improve the quality of the estimates. 
-A common optimality criterion is D-optimality where $\det{\IF}$ is maximized~\citep{Goodwin1977}.
+A common optimality criterion is D-optimality where $\det{\Fi{\theta}}$ is maximized~\citep{Goodwin1977}.
 
@@
 \begin{align}
-\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
+\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\Fi{\theta}^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
 \label{eq:excitation:varG}
@@
 \begin{align}
-\IF &= \frac{1}{\pi}
+\Fi{\theta} &= \frac{1}{\pi}
 \begin{bmatrix}
@@
 \begin{align}
-\IF &=
+\Fi{\theta} &=
        \begin{bmatrix}
@@
 It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling.
-The diagonal blocks of the normalized $\IF$ in all cases have some elements close to $1$. 
+The diagonal blocks of the normalized $\Fi{\theta}$ in all cases have some elements close to $1$. 
 In this example, the $\damping$ is set to be the same in both sub-systems. 
@@
 \begin{align}
-\IF&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
+\Fi{\theta}&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
                         \deemph{0}&\partial G_{2,2}\end{bmatrix}.
@@
     \begin{align}
-      \fMin{k} &= \mean{f_{k-1}}{f_k}\\
-      \fMax{k} &= \mean{f_{k+1}}{f_k}
+      \fMin{k} &= \geomean{f_{k-1}}{f_k}\\
+      \fMax{k} &= \geomean{f_{k+1}}{f_k}
     \label{eq:excitation:fRange}
@@
   We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
-  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
+  Using the \MATLAB\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
   These can be represented by a transfer function of the form:

### 2016-04-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Lots of work on CH03
Uniform commands: part 1

@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
-Unfortunately, the \gls{LPM} presented in \TODO{\secref{sec:nparam:trunc:theoryLPMandWindowing}} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
+Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:LRM} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
@@
 \end{align}
-where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found.
-This is discussed below.
-%(see the discussion below).
-% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.
+where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below.
 
@@
 
-\subsection{Simulation Results}\label{sec:nparam:trunc:simResults}
+\subsection{Simulation Results}
+\label{sec:nparam:trunc:simResults}
 
@@
 \item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.
-%i.e.
-a decrease of the black crosses w.r.t.~the gray ones is observed.
 

### 2016-04-21 ch03-lrm/lrm-paper.tex
Uniform commands: part 1

@@
 \subsection{The Local Rational Method}
+\label{sec:nparam:LRM}
 The \gls{LRM} as first introduced by \citep{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
@@
 
-\TODO{plot example spectrums}
 \begin{figure}
@@
 
-\begin{guideline}{For resonant systems, use the LRM when $\SNR \geq 20 \unit{dB}$}
+\begin{guideline}[Use the LRM when $\SNR \geq 20 \unit{dB}$ for resonant systems]
 \end{guideline}
 
-\begin{guideline}{For long measurements, the choice of local modeling method does not matter}
+\begin{guideline}[Use the LPM when $\SNR \leq 20 \unit{dB}$]
+\end{guideline}
+
+\begin{guideline}[For long measurements, LPM and LRM are similar]
 \end{guideline}
@@
    % \subsection{F16}
-
-  \section{Conclusion}
-  \label{sec:conclusion}
-
-  \begin{itemize}
-    \item LRM: extension to LRIC
-    \item LRM: derivation of bias
-    \item LRM vs LPM: at which settings is LRM better than LPM
-    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
-    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
-  \end{itemize}

### 2016-04-21 ch03-lrm/nonparametric.tex
Uniform commands: part 1

@@
 \begin{remark}
-Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
-As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
+The typical approaches, such as the holdout and plug-in methods, either assume that an abundantly large dataset is available or  assume the models are estimated on a fixed dataset.
+As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $\nWind$ over the frequency.
 \end{remark}
@@
 
+  \section{Conclusion}
+  \label{sec:conclusion}
+
+  \begin{itemize}
+    \item LRM: extension to LRIC
+    \item LRM: derivation of bias
+    \item LRM vs LPM: at which settings is LRM better than LPM
+    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
+    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
+  \end{itemize}
+
 \input{\thisDir/proofLOOCV.tex}

### 2016-04-21 ch04-lrmhinf/lrmhinf.tex
Uniform commands: part 1

@@
           |
-            \hinfnorm{\Delta} \leq \gamma
+            \infnorm{\Delta} \leq \gamma
         }
@@
 where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
-To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
+To estimate $\Delta$ and $\infnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
 These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
@@
 \label{sec:lrmhinf:resultsAvis}
-To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, a short estimation dataset is used.
+To estimate $\Delta(\omega_k)$ and $\infnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, a short estimation dataset is used.
 This estimation dataset is sampled from a larger dataset that contains four times more excited frequency lines (and hence produces a four times more densely sampled \gls{FRF}).
@@
 
-This suggests that the local rational models with interpolation enable accurate estimation of  $\abs{\Delta}$ and hence also $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
+This suggests that the local rational models with interpolation enable accurate estimation of  $\abs{\Delta}$ and hence also $\infnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.
 
@@
 It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
-Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
+Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\infnorm{\Delta}$ and/or reduce the measurement time four-fold.
 Furthermore, the results are validated by a detailed validation measurement.

### 2016-04-22 ch03-lrm/figs/exportMCfigs.m
Extract MC figures

@@ -1,0 +1,31 @@
+basePath = dropbox('VUB','PhD','thesis','ch03-lrm');
+makeFileName = @(SNR) fullfile(basePath ,'figs', sprintf('MC-SNR-%d', SNR));
+makeDataPath = @(SNR) fullfile(basePath ,'data', sprintf('MC-SNR-%d', SNR));
+
+
+relativeDataPath = @(SNR) sprintf('\\thisDir/data/MC-SNR-%d', SNR);
+allfigs = findall(groot,'type','figure');
+
+titleOfFigAxes = @(h) get(get(findall(h,'type','axes'),'Title'), 'String');
+arrayfun(@(h) set(h, 'name', titleOfFigAxes(h)), allfigs);
+
+for iFile = 1:numel(allfigs)
+    fig = allfigs(iFile);
+    
+    SNR = textscan(titleOfFigAxes(fig),'SNR = %f dB');
+    SNR = SNR{1};
+    
+    filename = makeFileName(SNR);
+    dataPath = makeDataPath(SNR);
+    if ~exist(dataPath,'dir')
+        mkdir(dataPath);
+    end
+    
+    saveas(fig, [filename '.fig']);
+    matlab2tikz([filename '.tikz'], 'figurehandle', fig, ...
+                'width', '\figurewidth', ...
+                'height', '\figureheight', ...
+                'externalData', true, ...
+                'dataPath', dataPath, ...
+                'relativeDataPath', relativeDataPath(SNR));
+end

### 2016-04-22 code/splitsubplots.m

@@ -1,0 +1,19 @@
+function [hFig] = splitsubplots(hFigWithSubplots)
+
+if ~exist('hFigWithSubplots','var')
+    hFigWithSubplots = findall(groot,'type','figure');
+end
+
+hProto = figure;
+hAx = axes;
+defaultPos   = get(hAx,'Position');
+defaultUnits = get(hAx,'Units');
+delete(hProto)
+    
+hAxes = findall(hFigWithSubplots, 'type', 'axes');
+hFig  = repmat(groot, size(hAxes));
+
+for iAx = 1:numel(hAxes);
+    hFig(iAx) = figure();
+    set(hAxes(iAx),'Parent',hFig(iAx),'Units',defaultUnits, 'Position',defaultPos);
+end

### 2016-04-22 ch03-lrm/lrm-paper.tex
Extract MC figures
Actually include MC figures

@@
     \item \TODO{choice $s$ or $z$}
-    \item \TODO{derivation Bias}
-      \begin{itemize}
-        \item \TODO{Good LPM window}
-        \item \TODO{Good LRM window}
-      \end{itemize}
     \item \TODO{influence of noise filter: mismatch with model}
@@
 
+\begin{table}
+\centering
+\caption{Local modeling methods used in the Monte Carlo analysis.}
+\label{tbl:nparam:methods}
+\begin{tabular}{lcccr} \toprule
+\textsc{Method} & \DOF & $\nWind$ & $\nth$ & $\Delta$ SNR (dB)\\
+\midrule
+\color{rgb:red,196;green,160;blue,0} $\ETFE$ & 1 & 0  & 1 & 0 \\
+\color{rgb:red,92;green,53;blue,102} $\lrm{7,1,1,1}$ & 15 & 10 & 5 & 4.77121 \\
+\color{rgb:red,78;green,154;blue,6} $\lric{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
+\color{rgb:red,32;green,74;blue,135} $\lrm{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
+\color{rgb:red,206;green,92;blue,0} $\lrm{6,2,2,2}$ &  135 & 8 & 2.10853 \\
+\color{rgb:red,164;green,0;blue,0} $\lpm{7,4,4}$ &  15&5 & 10 & 1.76091 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \paragraph{Noiseless case}
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[ RMS, bias, std for $\SNR = \infty$]
-  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in a relative approximation error of $-100\unit{dB}$.}
+  \input{\thisDir/figs/MC-SNR-Inf.tikz}
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.}
   \label{fig:nparam:comparison:noiseless}
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[ RMS, bias, std for $\SNR = 60\unit{dB}$]
+  \input{\thisDir/figs/MC-SNR-60.tikz}
   \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system.
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[ RMS, bias, std for $\SNR = 20\unit{dB}$]
+  \input{\thisDir/figs/MC-SNR-20.tikz}
   \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[ RMS, bias, std for $\SNR = 10\unit{dB}$]
+  \input{\thisDir/figs/MC-SNR-10.tikz}
   \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.

### 2016-04-23 ch03-lrm/lrm-paper.tex
Some things
Some discussion on LRM results

@@
 \label{tbl:nparam:methods}
-\begin{tabular}{lcccr} \toprule
-\textsc{Method} & \DOF & $\nWind$ & $\nth$ & $\Delta$ SNR (dB)\\
+\begin{tabular}{lccccr} 
+\toprule
+\textsc{Method} & \textsc{Color} & $\nWind$ & $\nth$ & \DOF & $\Delta$ SNR (dB)\\
 \midrule
-\color{rgb:red,196;green,160;blue,0} $\ETFE$ & 1 & 0  & 1 & 0 \\
-\color{rgb:red,92;green,53;blue,102} $\lrm{7,1,1,1}$ & 15 & 10 & 5 & 4.77121 \\
-\color{rgb:red,78;green,154;blue,6} $\lric{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
-\color{rgb:red,32;green,74;blue,135} $\lrm{7,2,2,2}$ &  15&7 & 8 & 2.73001 \\
-\color{rgb:red,206;green,92;blue,0} $\lrm{6,2,2,2}$ &  135 & 8 & 2.10853 \\
-\color{rgb:red,164;green,0;blue,0} $\lpm{7,4,4}$ &  15&5 & 10 & 1.76091 \\
+ $\ETFE$ &\color{etfe} --- & 1  & 1  & 0 & 0 \\
+ $\lrm{7,1,1,1}$ & \color{lrm7111} --- & 15  & 5 & 10  & 4.77 \\
+ $\lric{7,2,2,2}$ &\color{lric7222} --- &   15 & 8 & 7  & 2.73 \\
+ $\lrm{7,2,2,2}$ &\color{lrm7222} --- &   15 & 8 & 7  & 2.73 \\
+ $\lrm{6,2,2,2}$ &\color{lrm6222} --- &   13 & 8 & 5  & 2.11 \\
+ $\lpm{7,4,4}$ &\color{lpm744} --- &   15 & 10 & 5  & 1.76 \\
 \bottomrule
@@
 \paragraph{Noiseless case}
-In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM} and \gls{ETFE}.
+In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM}, \gls{LRIC} and \gls{ETFE}.
 For the \gls{ETFE}, it can be seen that the error is very high.
-This can be expected since the \gls{ETFE} does not separate transient and leakage contributions.
-this error only disappears very slowly by measuring a longer record due to the presence of the leakage term.
-As such, \TODO{afschrijven}
+This can be expected since the \gls{ETFE} does not separate transient/leakage contributions.
+Consequently, the leakage contributions (which change over the different Monte Carlo runs), lead to a large variance error for the \gls{ETFE}.
+The approximation error of the \gls{LPM} for short datasets ($\nBW \leq 8$) is dominated by the bias error.
+The is to be expected since the resonance in the band of interest is modeled using only polynomials instead of the full rational form.
+For longer datasets, 
+For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-60 \unit{dB}$ for the first-order method, $-120\unit{dB}$ for second-order methods).
+For short datasets ($\nBW \leq 16$), the $\lrm{7,1,1,1}$ error has a bias contribution that is slightly larger ($1$ to $4\unit{dB}$) than the variance contribution.
+For larger datasets ($\nBW \geq 16$), this bias contribution starts to diminish significantly as $\bigO{\frac{}{}}$
 

### 2016-04-23 ch03-lrm/lrm-paper.tex
Link to Stenman

@@
   \mat{
-    U(\omega_{k-N_W})\\
+    U(\omega_{k-\numel{W}})\\
     \vdots\\
@@
     \vdots\\
-    U(\omega_{k+N_W})\\
+    U(\omega_{k+\numel{W}})\\
   }
@@
   \mat{
-    Y(\omega_{k-N_W})\\
+    Y(\omega_{k-\numel{W}})\\
     \vdots\\
@@
     \vdots\\
-    Y(\omega_{k+N_W})\\
+    Y(\omega_{k+\numel{W}})\\
   }
@@
 \end{equation}
-Note that this encompasses $\nWind$ complex equations in the $\nth = \numel{A} + \numel{B} + \numel{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
+Note that this encompasses $\nWind$ complex equations in the $\nth = \order{A} + \order{B} + \order{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
 Consequently, a necessary condition to compute the model parameters is that
@@
   \DOF = \nWind - \nth
-       = 2 \numel{W} - \numel{A} - \numel{B} - \numel{C} - 1
+       = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
 \end{equation}
@@
 \end{equation}
-Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires time-consuming iterative optimization schemes to obtain a parameter estimate.
+Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
+We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.
 
@@
       \text{.}
+      \label{eq:nparam:LRM:costFunc}
 \end{equation}
@@
       \cdots &
-      \LocalVector{Y} \hadamard \LocalVector{d}^{\numel{A}}
+      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
     }\\
@@
       \cdots &
-      \LocalVector{U} \hadamard \LocalVector{d}^{\numel{B}}
+      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
     }\\
@@
       \cdots &
-      \LocalVector{d}^{\numel{C}}
-    }\\
-    \LocalVector{d}^{n} & \isdef
+      \LocalVector{d}^{\order{C}}
+    }
+    \text{.}
+\end{align}
+In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
+\begin{equation}
+    \LocalVector{d}^{n} 
+    \isdef
     \mat{
@@
     }^{\T}
-    \text{ with $n \in \mathbb{Z}$.}
-\end{align}
+    \text{ with $n \in \mathbb{Z}$}
+\end{equation}
+where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.
+
 This formulation facilitates to solve the problem in a one-step approach:
@@
     = \KTK{\LocalMatrix{K}} \LocalVector{Y}
+    \label{eq:nparam:LRM:normalEquations}
 \end{equation}
@@
 
+\begin{remark}
 Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
@@
 such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.
+\end{remark}
 
-\TODO{define notations for LPM etc.}
+We denote a method that solves \eqref{eq:nparam:LRM:costFunc} for given bandwidth and local orders as $\lrm{\numel{W}, \order{B},\order{A},\order{C}}$.
+
+\subsection{The Local Polynomial Method}
+The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
+The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.
+
+The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
+As such, we can use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, 0, \order{C}}$.
+
+\begin{remark}
+The trivial setting for local `modeling' where a window with a total width of $1\unit{bin}$ and no transient estimation ($\order{C} = -1$), actually corresponds to the simple \gls{ETFE}~\citep{Broersen1995,Stenman2000ASETFE,Stenman2001ASFRF} when no further smoothing or windowing is applied:
+\begin{equation}
+  \estimated{G}_{\ETFE}(\omega_k) \isdef \frac{Y(\omega_k)}{U(\omega_k)}
+  \label{eq:nparam:ETFE}
+\end{equation}
+As such, $\ETFE \equiv \lrm{0,0,0,-1} \equiv \lpm{0,0,-1}$.
+\end{remark}
+
+\begin{remark}
+The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
+It should be noted, however, that such methods differ significantly from the \gls{LPM}.
+Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
+Moreover, the methods proposed by \citet{Stenman2001ASFRF} build upon `local regression` approaches such as \gls{LOWESS}.
+See e.g. \citet{Loader1999} for more information regarding these `local regression' approaches.
+\end{remark}
 
@@
 \label{sec:biascalc}
-Since the local design matrix \eqref{eq:nparam:designMatrix} contains the noisy output spectrum $\LocalVector{Y}$ when $\numel{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
+Since the local design matrix \eqref{eq:nparam:designMatrix} of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
 In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.
@@
             \frac{1}{\nWind} 
-                \sum_{r} 
+                \sum_{\dW} 
                      \left| 
-                             \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}
-                          - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}
-                          - \LocalModel{C}(r, \LocalVector{\theta}) 
+                             \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}
+                          - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}
+                          - \LocalModel{C}(\dW, \LocalVector{\theta}) 
                     \right|^2 \\
@@
               \frac{1}{\nWind} 
-                     \sum_{r} 
-                              \left| \LocalModel{A}(r,\LocalVector{\theta}) \right|^2 
+                     \sum_{\dW} 
+                              \left| \LocalModel{A}(\dW,\LocalVector{\theta}) \right|^2 
                               \sigma_V^2
@@
       \frac{1}{\nWind}
-           \sum_{r}
-           \LocalModel{Q}(      r,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
-           \LocalModel{Q}(\conj{r}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
+           \sum_{\dW}
+           \LocalModel{Q}(      \dW,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
+           \LocalModel{Q}(\conj{\dW}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
    \\
-   \LocalModel{Q}(r, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
-                 \LocalModel{A}(r, \LocalVector{\theta}) \true{\LocalVector{Y}}(r)
-               - \LocalModel{B}(r, \LocalVector{\theta}) \true{\LocalVector{U}}(r)
-               - \LocalModel{C}(r, \LocalVector{\theta})
+   \LocalModel{Q}(\dW, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
+                 \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}(\dW)
+               - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}(\dW)
+               - \LocalModel{C}(\dW, \LocalVector{\theta})
     \\             
@@
                      \sum_{r} 
-                               \LocalModel{A}(      r,        \LocalVector{\theta} ) 
-                               \LocalModel{A}(\conj{r}, \conj{\LocalVector{\theta}}) 
+                               \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
+                               \LocalModel{A}(\conj{\dW}, \conj{\LocalVector{\theta}}) 
 \end{align}
-since $\conj{ \LocalModel{A}(r,\theta)} =  \LocalModel{A}(\conj{r},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
+since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
 Remember also that $\theta = \mat{\theta_A^{\TT} & \theta_B^{\TT} & \theta_C^{\TT}}$.
@@
      \frac{\sigma_V^2}{\nWind}
-     \sum_r r^i \LocalModel{A}(\conj{r},\conj{\LocalVector{\theta}}) 
+     \sum_{\dW} \dW^i \LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}}) 
      && \forall i \in \set{1,\ldots,\order{A}}
@@
 \begin{equation}
-  \Delta \LocalModel{G}(\omega) 
+  \Delta \LocalModel{G}(\omega_k) 
+  =
+  \Delta \LocalModel{G}(\dw{0}{k}) 
      \approx 
-        \PartialDerivative{\LocalModel{G}(\theta, \omega)}
+        \PartialDerivative{\LocalModel{G}(\theta, \dw{0}{k})}
                                           {\theta} 
@@
 \begin{align}
-    \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta} 
+    \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta} 
      &=
      \begin{bmatrix}
-       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_A} &
-       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_B} &
-       \PartialDerivative{\LocalModel{G}(\theta,r)}{\theta_C} 
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_A} &
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_B} &
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_C} 
      \end{bmatrix}
      \\
-     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_A} 
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_A} 
      &=
@@
      \begin{bmatrix}
-         r^1 & r^2 & \deemph{\cdots} & r^{\order{A}}
+         \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{A}}
      \end{bmatrix}
      \\
-     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_B} 
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_B} 
      &=
-     \frac{1}{\LocalModel{A}(\theta, r)}
+     \frac{1}{\LocalModel{A}(\theta, \dW)}
      \begin{bmatrix}
-         1 & r^1 & r^2 & \deemph{\cdots} & r^{\order{B}}
+         1 & \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{B}}
      \end{bmatrix}
      \\
-     \PartialDerivative{\LocalModel{G}(\theta, r)}{\theta_C} 
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_C} 
      &=
@@
 \begin{equation}
-  \Delta \LocalModel{G}(\theta,r)
+  \Delta \LocalModel{G}(\theta,\dW)
   \approx
-  \frac{\LocalModel{G}(\theta, r)}{\LocalModel{}}
+  \frac{\LocalModel{G}(\theta, \dW)}
+           {\LocalModel{A}(\theta, \dW)}
+  \begin{bmatrix}
+    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
+  \end{bmatrix}
+  \Delta \theta_A
+  \text{.}
+\end{equation}
+Equivalently, the relative bias of the \gls{FRF} can be written as
+\begin{equation}
+\frac{\Delta \LocalModel{G}(\theta,\dw{0}{k})}{\LocalModel{G}(\theta,\dw{0}{k})}
+\approx
+\LocalModel{A}(\theta,\dW)^{-1}
+\begin{bmatrix}
+    \dw{0}{k}^1 & \deemph{\cdots} & \dw{0}{k}^{\order{A}}
+  \end{bmatrix}
 \end{equation}

### 2016-04-23 ch03-lrm/lrm-paper.tex
MC: SNR 40

@@
   \SNR_{\BW} \isdef
-  \frac{\int_{\BW} \abs{Y_0(\omega)}^2 \dd{\omega}}
+  \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
             {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
 \end{equation}
-where $\BW$ is the frequency range of the $3 \unit{dB}$ bandwidth of the system, i.e. where $\abs{G_0} \geq \norm[\infty]{\true G} - 3 \unit{dB}$.
+where $\BW$ is the $3 \unit{dB}$ bandwidth of the system.
 
@@
 \toprule
-\textsc{Method} & \textsc{Color} & $\nWind$ & $\nth$ & \DOF & $\Delta$ SNR (dB)\\
+\textsc{Method} & \textsc{Color} & $\nWind$ & $\nth$ & \DOF & $\Delta\SNR \axisunit{dB}$ \\
 \midrule
@@
 \paragraph{Noiseless case}
-In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM}, \gls{LRIC} and \gls{ETFE}.
+In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM}, \gls{LRIC} and \gls{ETFE} as shown in \figref{fig:nparam:comparison:noiseless}.
 For the \gls{ETFE}, it can be seen that the error is very high.
@@
 For longer datasets, 
-For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-60 \unit{dB}$ for the first-order method, $-120\unit{dB}$ for second-order methods).
+For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-64 \unit{dB}$ for the first-order method, $-114\unit{dB}$ for second-order methods).
 For short datasets ($\nBW \leq 16$), the $\lrm{7,1,1,1}$ error has a bias contribution that is slightly larger ($1$ to $4\unit{dB}$) than the variance contribution.
-For larger datasets ($\nBW \geq 16$), this bias contribution starts to diminish significantly as $\bigO{\frac{}{}}$
+For larger datasets ($\nBW \geq 16$), this bias contribution starts to diminish significantly as $\bigO{\nBW^{-2}}$.
+For second-order rational methods, the error is dominated by the variance and is about $50\unit{dB}$ smaller than for the first-order methods.
+Practically, this approximation error is very likely to be negligible in measurements as such an error level corresponds to the quantization noise level of a $19\unit{bit}$ \gls{ADC}.
 
@@
   \input{\thisDir/figs/MC-SNR-Inf.tikz}
-  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.}
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.
+See \tabref{tbl:nparam:methods} for the color legend.}
   \label{fig:nparam:comparison:noiseless}
@@
 \paragraph{Good signal-to-noise ratios}
+The next situation we consider is when $\SNR=60\unit{dB}$ as shown in \figref{fig:nparam:comparison:hiSNR}.
+Here, the \gls{LPM} remains severly biased for small datasets ($\nBW < 12$).
+However, for sufficiently long experiments ($\nBW > 32$), the bias becomes negligible.
+For the \gls{LRM} and \gls{LRIC}, the bias is always much smaller than the variance.
+In contrast to \gls{LPM}, the \gls{LPM} already reaches a constant variance level when $\nBW > 10$.
+It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
+It is hence not advantageous to use the \gls{LRIC} as-is.
+For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches
+\begin{equation}
+  \lim_{\nBW \to \infty} \RMSE \approx \frac{\SNR}{\Delta \SNR}
+\end{equation}
+where
+\begin{equation}
+  \Delta\SNR = \sqrt{\frac{\nth}{\nWind}}
+\end{equation}
+accounts for the smoothing action of local modeling (see \tabref{tbl:nparam:methods} for numerical values of $\Delta \SNR$).
 

### 2016-04-23 code/mvMCdata.sh

@@ -1,0 +1,19 @@
+#!/bin/sh
+mv MC-SNR-*-1.tsv  LRM7222-rmse.tsv
+mv MC-SNR-*-2.tsv  LRM7222-bias.tsv
+mv MC-SNR-*-3.tsv  LRM7222-std.tsv
+mv MC-SNR-*-4.tsv  LPM744-rmse.tsv
+mv MC-SNR-*-5.tsv  LPM744-bias.tsv
+mv MC-SNR-*-6.tsv  LPM744-std.tsv
+mv MC-SNR-*-7.tsv  ETFE-rmse.tsv
+mv MC-SNR-*-8.tsv  ETFE-bias.tsv
+mv MC-SNR-*-9.tsv  ETFE-std.tsv
+mv MC-SNR-*-10.tsv LRM7111-rmse.tsv
+mv MC-SNR-*-11.tsv LRM7111-bias.tsv
+mv MC-SNR-*-12.tsv LRM7111-std.tsv
+mv MC-SNR-*-13.tsv LRM6222-rmse.tsv
+mv MC-SNR-*-14.tsv LRM6222-bias.tsv
+mv MC-SNR-*-15.tsv LRM6222-std.tsv
+mv MC-SNR-*-16.tsv LRIC7222-rmse.tsv
+mv MC-SNR-*-17.tsv LRIC7222-bias.tsv
+mv MC-SNR-*-18.tsv LRIC7222-std.tsv

### 2016-04-23 ch03-lrm/lrm-paper.tex
Add Hessian + a lot

@@
 
-\TODO{write out subexpressions}
+\paragraph{Contributions to the Hessian}
+Computing the Hessian in \eqref{eq:nparam:bias-basic} also boils down to recognizing the block structure.
+This results in the following block matrix:
+\begin{equation}
+  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} =
+  \begin{bmatrix}
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_A } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_A } \\
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_B } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_B } \\
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_C } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_C } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
+  \end{bmatrix}
+  \label{eq:nparam:lrm:bias:hessian}
+\end{equation}
+where every sub-block consists of the different second-order derivatives and exhibit a similar pattern.
+
+The different contributions are given below:
+\begin{align}
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_1}} \pd a_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{Y}}(\dW)}^2\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd b_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{U}}(\dW)}^2\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd c_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2}\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd a_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd b_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \conj{\true{\LocalVector{U}}(\dW)} \true{\LocalVector{Y}}(\dW)\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd a_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd c_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{Y}}(\dW)\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd b_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_2}} \pd b_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{U}}(\dW)
+  \text{.}
+\end{align}
+
+\begin{remark}
+Computing the inverse of this Hessian cannot, to the knowledge of the author, be reduced to a form that yields more insight.
+However, if the non-diagonal blocks can be neglected, this would lead to an inverse that is also block-diagonal:
+\begin{equation}
+   \begin{bmatrix}
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
+    \deemph{0} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
+    \deemph{0} \\
+    \deemph{0} &
+    \deemph{0} & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
+  \end{bmatrix}^{-1}
+  \!\!\!=
+  \begin{bmatrix}
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A }\right)^{-1} &
+    \deemph{0} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B }\right)^{-1} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \deemph{0} & 
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }\right)^{-1}
+  \end{bmatrix}
+  % \text{.}
+\end{equation}
+\end{remark}
 \paragraph{Bias on the \glsentrydesc{FRF}}
@@
   \end{bmatrix}
+  H^{-1}
+  \begin{bmatrix}
+
+  \end{bmatrix}
 \end{equation}
 
-\section{Simulation}
+\section{Simulations}
 \label{sec:simulations}
@@
   \input{\thisDir/figs/MC-SNR-60.tikz}
-  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system.
-A relative approximation error of $-100 \unit{dB}$ is observed.}
+  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:hiSNR}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-40.tikz}
+  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
   \label{fig:nparam:comparison:hiSNR}
@@
 \paragraph{Poor signal-to-noise ratios}
-\begin{figure}
+In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
+Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
+
+\begin{figure}[p]
   \centering
@@
   \input{\thisDir/figs/MC-SNR-20.tikz}
-  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.
-The \gls{LRM} outperforms the \gls{LPM}.}
+  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
   \label{fig:nparam:comparison:lowSNR}
@@
   \input{\thisDir/figs/MC-SNR-10.tikz}
-  \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{The \gls{RMSE}, bias and variance of different local modeling methods is compared as a function of the number of points in the $3\unit{dB}$ bandwidth of the system when $\SNR = 20\unit{dB}$.
-An approximation error of $-100 \unit{dB}$ is observed.}
+ \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
   \label{fig:nparam:comparison:terribleSNR}

### 2016-04-23 ch03-lrm/lrm-paper.tex
Stuff :-)

@@
 the \gls{FRF}), the measurement noise and leakage contributions of the spectrum by exploiting the structure that those different contributions exhibit.
-
-\citep{Pintelon2010LPM1},\citep{Pintelon2010LPM2},\citep{McKelvey2012LRM}
 
@@
 \secref{sec:theory} introduces theory of estimating \glspl{FRF} and the relevant local modeling techniques.
-In \secref{sec:simulations} the performance of the different modeling methods is investigated by means of simulations.
-The methods are then illustrated on measurements of mechanical systems in \secref{sec:measurements}.
+In \secref{sec:biascalc}, the bias of the \gls{LRM} is derived.
+In \secref{sec:simulations} the performance of the different modeling methods are compared by means of simulations.
 Finally, conclusions are presented in \secref{sec:conclusion}.
-
-\begin{itemize}
-    \item \TODO{choice $s$ or $z$}
-    \item \TODO{influence of noise filter: mismatch with model}
-\end{itemize}
+%TODO: choice s vs z
+%TODO: influence of resonant noise filter
 
@@
 
-\TODO{hier voortschrijven}
+\TODO{hier voortschrijven: ruisvariantie berekenen}
+
+\begin{remark}
+This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
+In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution.
+This can be obtained e.g. using random phase multisines or random input signals.
+\end{remark}
 
@@
 since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
-Remember also that $\theta = \mat{\theta_A^{\TT} & \theta_B^{\TT} & \theta_C^{\TT}}$.
 
@@
     \Delta \theta_A\\
-    \deemph{\Zero{\order{B}+1\times1}}\\
-    \deemph{\Zero{\order{C}+1\times1}}
+    \deemph{0}\\
+    \deemph{0}
   \end{bmatrix}
@@
 \begin{equation}
-\frac{\Delta \LocalModel{G}(\theta,\dw{0}{k})}{\LocalModel{G}(\theta,\dw{0}{k})}
+\frac{\Delta \LocalModel{G}(\theta,\dW)}{\LocalModel{G}(\theta,\dW)}
 \approx
@@
 \begin{bmatrix}
-    \dw{0}{k}^1 & \deemph{\cdots} & \dw{0}{k}^{\order{A}}
+    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
   \end{bmatrix}
-  H^{-1}
+  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}
   \begin{bmatrix}
-
+  \Delta\theta_A\\
+  0\\
+  0\\
   \end{bmatrix}
+  \text{.}
 \end{equation}
@@
  $\ETFE$ &\color{etfe} --- & 1  & 1  & 0 & 0 \\
- $\lrm{7,1,1,1}$ & \color{lrm7111} --- & 15  & 5 & 10  & 4.77 \\
- $\lric{7,2,2,2}$ &\color{lric7222} --- &   15 & 8 & 7  & 2.73 \\
- $\lrm{7,2,2,2}$ &\color{lrm7222} --- &   15 & 8 & 7  & 2.73 \\
- $\lrm{6,2,2,2}$ &\color{lrm6222} --- &   13 & 8 & 5  & 2.11 \\
- $\lpm{7,4,4}$ &\color{lpm744} --- &   15 & 10 & 5  & 1.76 \\
+ $\lrm{7,1,1,1}$ & \color{lrm7111}\bfseries --- & 15  & 5 & 10  & 4.77 \\
+ $\lric{7,2,2,2}$ &\color{lric7222} \bfseries --- &   15 & 8 & 7  & 2.73 \\
+ $\lrm{7,2,2,2}$ &\color{lrm7222} \bfseries --- &   15 & 8 & 7  & 2.73 \\
+ $\lrm{6,2,2,2}$ &\color{lrm6222} \bfseries --- &   13 & 8 & 5  & 2.11 \\
+ $\lpm{7,4,4}$ &\color{lpm744} \bfseries --- &   15 & 10 & 5  & 1.76 \\
 \bottomrule
@@
 
-\begin{guideline}[Use the LRM when $\SNR \geq 20 \unit{dB}$ for resonant systems]
-\end{guideline}
-
-\begin{guideline}[Use the LPM when $\SNR \leq 20 \unit{dB}$]
+\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
+For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
+When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
 \end{guideline}
@@
 \begin{guideline}[For long measurements, LPM and LRM are similar]
+For very long measurements, the difference between \gls{LPM} and \gls{LRM} becomes negligible if the different resonances are well-separated.
 \end{guideline}
@@
 
-  \section{Measurements}
-  \label{sec:measurements}
-   \subsection{AVIS}
+  % \section{Measurements}
+  % \label{sec:measurements}
+  %  \subsection{AVIS}
    % \subsection{F16}

### 2016-04-23 ch03-lrm/nonparametric.tex
Clean up most definitions
Actually include MC figures
Some things
Stuff :-)

@@
 \label{sec:nonparametric}
-% \myEpigraph{}{}{}
+\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.
+}{Douglas Adams}{}
 
@@
 
-Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received new research interest from the community.
+Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received renewed interest from the community.
 
@@
 
-\input{\thisDir/proofLOOCV.tex}
+% \input{\thisDir/proofLOOCV.tex}

### 2016-04-24 ch03-lrm/lrm-paper.tex
Many TODOs in ch03

@@
                                       {47.9426 z^2 - 51.2955 z + 46.9933}
+                                      \text{,}
 \end{equation}
-
-\begin{figure}
- \centering
-  \input{\thisDir/figs/generalized-output-error.tikz}
-  \caption{Block schematic used in the simulations}
-\end{figure}
-
-\TODO{H0}
-
-The \gls{SNR} in the system bandwidth $\BW$ is defined as
+this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$.
+The system is scaled such that its peak amplitude is $3\unit{dB}$ and the 
+As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
+The gain of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
 \begin{equation}
@@
 \end{equation}
-where $\BW$ is the $3 \unit{dB}$ bandwidth of the system.
+where $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to $\set{10, 20, 40, 60, \infty} \unit{dB}$.
+
+\begin{figure}
+ \centering
+  \input{\thisDir/figs/generalized-output-error.tikz}
+  \caption{Block schematic used in the simulations. }
+  \label{fig:nparam:blockH0}
+\end{figure}
+
+The input signal used is a random-phase multisine with a full linear grid.
+A number of samples of the input- and output are measured, in such a way that the \gls{DFT} grid excited $\nBW$ bins within the $3\unit{dB}$ bandwidth of the system.
+The different values for $\nBW \in \set{2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 14, 16, 32, 40, 64, 80, 92, 128, 256}$ are tried.
+
+The \gls{FRF} is estimated using the local modeling approaches indicated in \tabref{tbl:nparam:methods}.
 
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[Example spectra]
-  \label{fig:nparam:spectra}
+  \TODOfig[Y(Y,E,T) vs freq of single simulation]
 \end{figure}
 
-We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over all  Monte Carlo runs.
+We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=2000$ Monte Carlo runs of the simulations above.
 Specifically, the following values
@@
   % \subsection{Implications of the model structure}
-  \subsection{Implications of the noise level}
+  % \subsection{Implications of the noise level}
   % \subsection{Implications of the noise coloring}
@@
   \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[Y(Y,E,T) vs freq of single simulation]
+  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
+  \label{}
 \end{figure}
 
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.62\figurewidth}
-  \TODOfig[RMSE, var, bias for (SNR, NBW) over freq]
-\end{figure}
-
-\TODO{describe aggregation over $\omega$}
+As the Monte Carlo simulations yield the estimated \gls{FRF}, the bias and variance for the different methods as a function of frequency, a huge amount of data is generated.
+To interpret the data, we aggregate the observed values over the frequencies to obtain:
+\begin{align}
+  \sampleVariance{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleVariance{\bullet}(\omega_k)} \\
+  \sampleBias{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleBias{\bullet}(\omega_k)}
+\end{align}
+which can be visualized for the different values of the $\SNR$, $\nBW$ and for each method.
 
@@
 
+For the more noisy situation where $\SNR = 40 \unit{dB}$ (\figref{fig:nparam:comparison:midSNR}), the situation is qualitatively equal except the bias incurred by the \gls{LRM} is similar to the noise level.
+
 \begin{figure}[p]
@@
   \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
-  \label{fig:nparam:comparison:hiSNR}
+  \label{fig:nparam:comparison:SNR}
 \end{figure}
@@
   \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
-  \label{fig:nparam:comparison:hiSNR}
+  \label{fig:nparam:comparison:midSNR}
 \end{figure}
@@
 
-\begin{remark}
-In all the simulations, it can be seen that for $\nWind \to \infty$, the error tapers off.
-\TODO{andere pieken gaan in de praktijk alles om zeep helpen en dus bovengrens stellen}
-\end{remark}
-
   % \section{Measurements}

### 2016-04-24 ch03-lrm/nonparametric.tex
Many TODOs in ch03

@@
   \label{sec:conclusion}
+In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
+Since the \gls{LRM} is an inherently biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
+Hence, expressions for the bias of the \gls{LRM} were derived.
+For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LRM}.
+For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
+For
+In this chapter, the \gls{LRIC} was introduced.
+This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
+However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
+Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.
 
-  \begin{itemize}
-    \item LRM: extension to LRIC
-    \item LRM: derivation of bias
-    \item LRM vs LPM: at which settings is LRM better than LPM
-    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
-    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
-  \end{itemize}
+Relatedly, two approaches to aid in performing the bias-variance trade-off for these local methods are illustrated.
+First, a short study of cross-validation for local models is given.
+Secondly, an approach to truncate the impulse response obtained from the \gls{LPM} is illustrated.
+The latter can improve the performance of the \gls{LPM} considerably if a large number of noisy samples is measured.
 

### 2016-04-25 ch03-lrm/nonparametric.tex
Lots of work on CH03

@@
 Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received renewed interest from the community.
-
-\begin{itemize}
-\item \TODO{explain non-parametric}
-\item \TODO{explain why non-parametric is good}
-\end{itemize}
+One of the reasons for this is that non-parametric techniques typically require less assumptions and knowledge of the system than building parametric models.
+As a consequence, non-parametric methods are often more robust to wrong assumptions than fully parametric methods.
+Besides, \glspl{FRF} have been shown to provide a quick insight into the basic dynamic properties of \gls{LTI} systems.
+This capability is very useful for system design, controller design, model validation and model selection for parametric models~\citep{Pintelon2012}.
 
 The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
+However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can prove difficult due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
 \gls{FRF} measurement techniques are discussed, for instance, in
 \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
-Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
-This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.
 
-\input{\thisDir/lrm-paper.tex}
+In this chapter, we will investigate local modeling techniques to capture the \gls{FRF} of resonant systems.
+In particular, a comparison between the \gls{LPM} and \gls{LRM} will be made such that it can be decided which method is to be preferred over the other in what conditions of \gls{SNR} and frequency resolution (or, equivalently, measurement time).
+
+\paragraph*{Outline}
+\secref{sec:theory} introduces theory of estimating \glspl{FRF} using local modeling techniques.
+In \secref{sec:biascalc}, the bias of the \gls{LRM} is derived.
+In \secref{sec:simulations} the performance of the different modeling methods are compared by means of simulations.
+In \secref{sec:nparam:orderSelection}, some options for model order selection are discussed.
+In \secref{sec:nonparametric:truncation}, an approach is developed to further reduce the variance of the \gls{LPM} estimate by truncation of the impulse response.
+Finally, conclusions are presented in \secref{sec:conclusion}.
+
+\section{Local modeling approaches}
+\label{sec:theory}
+
+Consider a discrete-time generalized output-error \gls{LTI} set-up, excited by the input signal $u[n]$.
+For an infinite data length, such a system can be described in the time domain by
+\begin{equation}
+  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \IntegerNumbers
+  \label{eq:output-error-TD-infinite}
+\end{equation}
+where $v[n]$ is filtered white noise, $v[n] = \true{H}(z) \true{e}[n]$ where $z^{-1}$ is the backward shift operator, i.e. $z^ {-1}x[n] = x[n-1]$.
+The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are stable and causal.
+
+During typical measurements, however, $y[n]$ and $u[n]$ are only measured over a limited time span, i.e. $n \in \set{0,1,\ldots,N-1}$.
+This introduces transient terms $t_{\bullet}$ in this relationship~\citep{Pintelon1997ARB}:
+\begin{equation}
+y[n] = \true{G}(z) u[n] + \true{H}(z) \true{e}[n] + \ezbrace{t_G[n] + t_H[n]}{t[n]}
+\label{eq:output-error-TD-finite}
+\end{equation}
+where $t_G[n]$ and $t_H[n]$ are due to the different conditions of respectively $\true{G}$ and $\true{H}$ at the beginning and end of the measurement record~\citep{Pintelon1997ARB}.
+Both terms can be lumped together as $t[n]$, which is often~\citep{Pintelon2010LPM1} determined predominantly by $t_G[n]$.
+
+\begin{definition}\label{def:DFT}
+The $N$-points \glsfirst{DFT} of a signal $x(n\Ts) = x[n]$ with $n \in \set{0,\ldots,N-1}$ is
+\begin{equation}
+  X \left[ k \right] =
+  X \left( \omega_k \right)
+  \isdef
+  \frac{1}{\sqrt{N}}\sum_{n=0}^{N-1} x \left( n \Ts \right)  \exponent{- j \omega_k n \Ts }
+  \label{eq:DFT}
+\end{equation}
+where $\omega_k \isdef \tfrac{2 \pi k }{N \Ts}$, $k \in \set{0,\ldots,N-1}$ and $\Ts$ is the sampling time.
+\end{definition}
+
+By applying the \gls{DFT}~\eqref{eq:DFT} to both sides of \eqref{eq:output-error-TD-finite}, one obtains its frequency-domain counterpart:
+\begin{align}
+    Y \left( \omega_k \right) 
+    & = \true{G} \left( \omega_k \right) U \left( \omega_k \right) 
+      + \true{H} \left( \omega_k \right) E \left( \omega_k \right)
+      + T \left( \omega_k \right)\\
+      &= \true{G} \left( \omega_k \right) U \left( \omega_k \right)  + V(\omega_k) + T(\omega_k)
+      \text{.}
+  \label{eq:output-error-FD}
+\end{align}
+
+Here, we focus on using local modeling to separate the different terms, i.e.
+\begin{itemize}
+  \item the transfer function $\true{G}$,
+  \item the leakage term $T$, and
+  \item the noise term $V$.
+\end{itemize}
+The main term of interest, however, is the transfer function $\true{G}$ and a secondary concern is estimating the noise variance $\Var{V}$.
+
+\subsection{Local modeling}
+Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
+In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
+On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
+As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
+\begin{align}
+  \true{G}(\omega_{k}+d) 
+  &\approx
+  \frac{\Sum_{i=0}^{\order{B}} b_i d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
+    &\isdef
+    \frac{\LocalModel[k]{B}(d)}%
+           {\LocalModel[k]{A}(d)} 
+           = \LocalModel[k]{G}(d)
+  \text{,}
+  \label{eq:LRM:model:G}
+  \\
+  \true{T}(\omega_k + d) &\approx
+  \frac{\Sum_{i=0}^{\order{C}} c_i d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
+    &\isdef 
+      \frac{\LocalModel[k]{C}(d)}%
+           {\LocalModel[k]{A}(d)}
+      = \LocalModel[k]{T}(d)
+  \text{.}
+  \label{eq:LRM:model:T}
+\end{align}
+
+In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
+Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
+To alleviate the notations, the subscript $k$ is omitted unless
+
+The local parameters $\theta$  
+\begin{equation}
+\theta \isdef 
+\begin{bmatrix}
+\theta_A\\ 
+\theta_B\\
+\theta_C
+\end{bmatrix}
+\qquad \text{ with }
+\theta_A \isdef
+\begin{bmatrix}
+a_1\\ \vdots\\ a_{\order{A}}
+\end{bmatrix}
+\text{, }
+\theta_B \isdef
+\begin{bmatrix}
+b_0\\ \vdots\\ b_{\order{B}}
+\end{bmatrix}
+\text{, and }
+\theta_C \isdef
+\begin{bmatrix}
+c_0\\ \vdots\\ c_{\order{C}}
+\end{bmatrix}
+\end{equation}
+in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
+\begin{equation}
+  \LocalWindow[k] 
+  \isdef
+  \Set{
+    \omega_{k+r} 
+    | 
+    r \in \LocalShifts{k}
+  }
+\end{equation}
+with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
+such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
+If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
+\begin{equation}
+  \LocalVector{U}_k \isdef 
+  \mat{
+    U(\omega_{k-\numel{W}})\\
+    \vdots\\
+    U(\omega_{k})\\
+    \vdots\\
+    U(\omega_{k+\numel{W}})\\
+  }
+  \text{ and }
+  \LocalVector{Y}_k \isdef 
+  \mat{
+    Y(\omega_{k-\numel{W}})\\
+    \vdots\\
+    Y(\omega_{k})\\
+    \vdots\\
+    Y(\omega_{k+\numel{W}})\\
+  }
+  \text{,}
+\end{equation}
+and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
+\begin{equation}
+  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
+\text{,}
+\end{equation} 
+where $\hadamard$ denotes the element-wise product (also, Hadamard product).
+Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
+\begin{equation}
+  \LocalVector{Y} 
+  \approx 
+  \hat{\LocalVector{Y}} 
+    =
+      \LocalModel{G} \hadamard \LocalVector{U} + \LocalModel{T}
+      \text{.}
+      \label{eq:local-system-equations}
+\end{equation}
+Note that this encompasses $\nWind$ complex equations in the $\nth = \order{A} + \order{B} + \order{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
+Consequently, a necessary condition to compute the model parameters is that
+\begin{equation}
+  \DOF = \nWind - \nth
+       = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
+\end{equation}
+is positive.
+To effectively compute the local model parameters, the equation error in \eqref{eq:local-system-equations} is minimized by formulating a quadratic cost function:
+\begin{equation}
+  \LocalVector{\CostFunc{\LRIC}} 
+    \isdef 
+      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)^{\HT} 
+      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)
+   \label{eq:costfunc:LRIC}
+   \text{.}
+\end{equation}
+Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
+We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.
+
+\subsection{The Local Rational Method}
+\label{sec:nparam:LRM}
+The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
+I.e. the \gls{LRM} procedure tries to minimize the equation error in
+\begin{equation}
+  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
+  \text{,}
+\end{equation}
+for which the corresponding cost function is
+\begin{equation}
+  \LocalVector{\CostFunc{\LRM}}
+  \isdef 
+  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
+      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
+      \text{.}
+      \label{eq:nparam:LRM:costFunc}
+\end{equation}
+where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e.
+the disturbing noise is assumed white over the local frequency window.
+Equivalently, the last equation can be rewritten as a linear regression problem
+\begin{equation}
+  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
+\end{equation}
+where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
+\begin{align}
+  \label{eq:nparam:designMatrix}
+  \LocalMatrix{K} 
+    & \isdef 
+  \mat{
+     \LocalMatrix{K}_A &
+     \LocalMatrix{K}_B & 
+     \LocalMatrix{K}_C
+  }\\
+  \LocalMatrix{K}_A 
+    &\isdef
+    \mat{
+      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
+      \cdots &
+      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
+    }\\
+  \LocalMatrix{K}_B 
+    &\isdef
+    \mat{
+      \LocalVector{U} \hadamard \LocalVector{d}^0 &
+      \cdots &
+      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
+    }\\
+  \LocalMatrix{K}_C
+    &\isdef
+    \mat{
+      \LocalVector{d}^0 &
+      \cdots &
+      \LocalVector{d}^{\order{C}}
+    }
+    \text{.}
+\end{align}
+In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
+\begin{equation}
+    \LocalVector{d}^{n} 
+    \isdef
+    \mat{
+      (-\numel{W})^{n} &
+      \cdots &
+      (\numel{W})^{n}
+    }^{\T}
+    \text{ with $n \in \mathbb{Z}$}
+\end{equation}
+where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.
+
+This formulation facilitates to solve the problem in a one-step approach:
+\begin{equation}
+  \LocalVector{\theta}_{\LRM} 
+    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
+    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
+    \label{eq:nparam:LRM:normalEquations}
+\end{equation}
+where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.
+
+\TODO{hier voortschrijven: ruisvariantie berekenen}
+
+\begin{remark}
+This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
+In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution.
+This can be obtained e.g. using random phase multisines or random input signals.
+\end{remark}
+
+\begin{remark}
+Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
+To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
+\begin{equation}
+\dw{r}{k} \isdef \frac{\omega_{k+r} - \omega_k}{\Delta \omega_k}
+\label{eq:freqScaling}
+\end{equation}
+where
+\begin{equation}
+  \Delta \omega_k \isdef
+  \max
+  \Set{
+    \abs{ \omega_k - \omega_j} |  \vphantom{\frac{a}{b}}  \omega_j \in \LocalWindow[k]
+  }
+\end{equation}
+such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.
+\end{remark}
+
+We denote a method that solves \eqref{eq:nparam:LRM:costFunc} for given bandwidth and local orders as $\lrm{\numel{W}, \order{B},\order{A},\order{C}}$.
+
+\subsection{The Local Polynomial Method}
+The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
+The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.
+
+The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
+As such, we can use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, 0, \order{C}}$.
+
+\begin{remark}
+The trivial setting for local `modeling' where a window with a total width of $1\unit{bin}$ and no transient estimation ($\order{C} = -1$), actually corresponds to the simple \gls{ETFE}~\citep{Broersen1995,Stenman2000ASETFE,Stenman2001ASFRF} when no further smoothing or windowing is applied:
+\begin{equation}
+  \estimated{G}_{\ETFE}(\omega_k) \isdef \frac{Y(\omega_k)}{U(\omega_k)}
+  \label{eq:nparam:ETFE}
+\end{equation}
+As such, $\ETFE \equiv \lrm{0,0,0,-1} \equiv \lpm{0,0,-1}$.
+\end{remark}
+
+\begin{remark}
+The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
+It should be noted, however, that such methods differ significantly from the \gls{LPM}.
+Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
+Moreover, the methods proposed by \citet{Stenman2001ASFRF} build upon `local regression` approaches such as \gls{LOWESS}.
+See e.g. \citet{Loader1999} for more information regarding these `local regression' approaches.
+\end{remark}
+
+\section{Derivation of the Bias of the \glsentrytext{LRM}}
+\label{sec:biascalc}
+Since the local design matrix \eqref{eq:nparam:designMatrix} of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
+In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.
+
+To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
+Let us denote the expected value of the cost function over all measurements $\LocalVector{Z} = \mat{\LocalMatrix{Y}, \LocalMatrix{U}}$ as
+\begin{align}
+  \ELSCost{\theta}
+              & \isdef 
+                   \E[\LocalVector{Z}]%
+                         {    
+                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
+              & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
+    \ELSCost[0]{\theta} & \isdef 
+            \frac{1}{\nWind} 
+                \sum_{\dW} 
+                     \left| 
+                             \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}
+                          - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}
+                          - \LocalModel{C}(\dW, \LocalVector{\theta}) 
+                    \right|^2 \\
+    \ELSCost[n]{\theta} & \isdef 
+              \frac{1}{\nWind} 
+                     \sum_{\dW} 
+                              \left| \LocalModel{A}(\dW,\LocalVector{\theta}) \right|^2 
+                              \sigma_V^2
+\end{align}
+where $\true{\LocalVector{U}}$ and $\true{\LocalVector{Y}}$ denote the `true' (noiseless) input-output spectra in the local window.
+Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
+\begin{multline}
+  \ELSCost{\theta} = \ELSCost{\true\theta} 
+  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right) %\\
+  + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
+  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
+   \left( \theta - \true\theta \right)
+   \text{.}
+\end{multline}
+The minimizer $\estimated\theta$ of this function can be obtained by equating the derivative
+\begin{equation}
+  \PartialDerivative{\ELSCost{\estimated\theta}}
+                                          {\estimated\theta} 
+  = 
+  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} 
+  + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \left( \estimated\theta - \true\theta \right)
+\end{equation}
+to zero.
+This is equivalent to 
+\begin{equation}
+  \left( \estimated\theta - \true\theta \right) 
+  = 
+  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  
+     \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
+  \text{.}
+\end{equation}
+which expresses the bias $\Delta\theta = \left( \estimated\theta - \true\theta \right)$ of the estimated parameters.
+Remark that 
+\begin{equation}
+  \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  
+  = 
+  \PartialDerivative{\ELSCost[0]{\theta} + \ELSCost[n]{\theta} }{\true\theta} 
+  = 
+  \PartialDerivative{\ELSCost[n]{\theta} }{\true\theta} 
+\end{equation}
+since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$ by definition.
+As such, the bias on the parameters can be simplified to
+\begin{equation}
+  \Delta\theta = 
+  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} 
+     \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
+  \text{.}
+  \label{eq:nparam:bias-basic}
+\end{equation}
+
+Do note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
+In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
+Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables~\citep{Hjorungnes2007,Hjorungnes2011}.
+The derivatives are then computed with respect to these variables.
+
+To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
+\begin{align}
+   \ELSCost[0]{\theta,\conj{\theta}} & =
+      \frac{1}{\nWind}
+           \sum_{\dW}
+           \LocalModel{Q}(      \dW,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
+           \LocalModel{Q}(\conj{\dW}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
+   \\
+   \LocalModel{Q}(\dW, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
+                 \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}(\dW)
+               - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}(\dW)
+               - \LocalModel{C}(\dW, \LocalVector{\theta})
+    \\             
+    \ELSCost[n]{\theta,\conj{\theta}} & =
+              \frac{\sigma_V^2}{\nWind} 
+                     \sum_{r} 
+                               \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
+                               \LocalModel{A}(\conj{\dW}, \conj{\LocalVector{\theta}}) 
+\end{align}
+since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.
+
+\paragraph{Contributions to the first order derivative}
+The last term in \eqref{eq:nparam:bias-basic}, i.e. the first order derivative,  is given by
+\begin{equation}
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta}
+  = 
+  \begin{bmatrix}
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_A} &
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_B} &
+  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C}
+  \end{bmatrix}
+\end{equation}
+and split into the parts pertaining to respectively $\LocalModel{A}$, $\LocalModel{B}$ and, $\LocalModel{C}$.
+The respective components are given by:
+\begin{align}
+  \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{a_i} 
+     &= 
+     \frac{\sigma_V^2}{\nWind}
+     \sum_{\dW} \dW^i \LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}}) 
+     && \forall i \in \set{1,\ldots,\order{A}}
+     \\
+   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{b_i} 
+   &= 0
+   && \forall i \in \set{0,\ldots,\order{B}}
+   \\
+   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{c_i} 
+   &= 0
+   &&\forall i \in \set{0,\ldots,\order{C}}
+   \text{.}
+\end{align}
+It can be seen that only the factors pertaining to $\theta_{A}$ are present.
+As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
+Consequently, only the poles can shifted by the presence of noise.
+As such, the bias term $\Delta \theta$ can be written in the following sparse form:
+\begin{equation}
+  \Delta \theta = 
+  \begin{bmatrix}
+    \Delta \theta_A\\
+    \Delta \theta_B\\
+    \Delta \theta_C
+  \end{bmatrix}
+  =
+  \begin{bmatrix}
+    \Delta \theta_A\\
+    \deemph{0}\\
+    \deemph{0}
+  \end{bmatrix}
+  \text{.}
+  \label{eq:nparam:lrm:bias:sparse}
+\end{equation}
+
+\paragraph{Contributions to the Hessian}
+Computing the Hessian in \eqref{eq:nparam:bias-basic} also boils down to recognizing the block structure.
+This results in the following block matrix:
+\begin{equation}
+  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} =
+  \begin{bmatrix}
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_A } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_A } \\
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_B } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_B } \\
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_C } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_C } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
+  \end{bmatrix}
+  \label{eq:nparam:lrm:bias:hessian}
+\end{equation}
+where every sub-block consists of the different second-order derivatives and exhibits a similar pattern.
+
+The different contributions are given below:
+\begin{align}
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_1}} \pd a_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{Y}}(\dW)}^2\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd b_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{U}}(\dW)}^2\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd c_{i_2}} & = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2}\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd a_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd b_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \conj{\true{\LocalVector{U}}(\dW)} \true{\LocalVector{Y}}(\dW)\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd a_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd c_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{Y}}(\dW)\\
+  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd b_{i_2}}  =
+  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_2}} \pd b_{i_1}} }& = 
+  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{U}}(\dW)
+  \text{.}
+\end{align}
+
+\begin{remark}
+Computing the inverse of this Hessian cannot, to the knowledge of the author, be reduced to a form that yields more insight.
+However, if the non-diagonal blocks can be neglected, this would lead to an inverse that is also block-diagonal:
+\begin{equation}
+   \begin{bmatrix}
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
+    \deemph{0} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
+    \deemph{0} \\
+    \deemph{0} &
+    \deemph{0} & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
+  \end{bmatrix}^{-1}
+  \!\!\!=
+  \begin{bmatrix}
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A }\right)^{-1} &
+    \deemph{0} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B }\right)^{-1} & 
+    \deemph{0} \\
+    \deemph{0} &
+    \deemph{0} & 
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }\right)^{-1}
+  \end{bmatrix}
+  % \text{.}
+\end{equation}
+\end{remark}
+\paragraph{Bias on the \glsentrydesc{FRF}}
+As a first order approximation, the bias on the \gls{FRF} can be written as
+\begin{equation}
+  \Delta \LocalModel{G}(\omega_k) 
+  =
+  \Delta \LocalModel{G}(\dw{0}{k}) 
+     \approx 
+        \PartialDerivative{\LocalModel{G}(\theta, \dw{0}{k})}
+                                          {\theta} 
+      \Delta \theta
+      \text{.}
+\end{equation}
+The derivative in that expression can be evaluated easily
+\begin{align}
+    \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta} 
+     &=
+     \begin{bmatrix}
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_A} &
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_B} &
+       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_C} 
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_A} 
+     &=
+     - \frac{\LocalModel{B}(\theta, r)}{\LocalModel{A}^2(\theta, r)}
+     \begin{bmatrix}
+         \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{A}}
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_B} 
+     &=
+     \frac{1}{\LocalModel{A}(\theta, \dW)}
+     \begin{bmatrix}
+         1 & \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{B}}
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_C} 
+     &=
+     \Zero{1 \times \order{C}+1}
+     \text{.}
+\end{align}
+
+However, the sparsity of $\Delta\theta$, see \eqref{eq:nparam:lrm:bias:sparse}, can be exploited such that the bias on the \gls{FRF} can be expressed as:
+\begin{equation}
+  \Delta \LocalModel{G}(\theta,\dW)
+  \approx
+  \frac{\LocalModel{G}(\theta, \dW)}
+           {\LocalModel{A}(\theta, \dW)}
+  \begin{bmatrix}
+    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
+  \end{bmatrix}
+  \Delta \theta_A
+  \text{.}
+\end{equation}
+Equivalently, the relative bias of the \gls{FRF} can be written as
+\begin{equation}
+\frac{\Delta \LocalModel{G}(\theta,\dW)}{\LocalModel{G}(\theta,\dW)}
+\approx
+\LocalModel{A}(\theta,\dW)^{-1}
+\begin{bmatrix}
+    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
+  \end{bmatrix}
+  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}
+  \begin{bmatrix}
+  \Delta\theta_A\\
+  0\\
+  0\\
+  \end{bmatrix}
+  \text{.}
+\end{equation}
+
+\section{Simulations}
+\label{sec:simulations}
+
+In the simulations, we consider a discrete-time second order system with transfer function
+\begin{equation}
+\true{G}(z) = \frac{0.64587 z + 0.64143}
+                                      {47.9426 z^2 - 51.2955 z + 46.9933}
+                                      \text{,}
+\end{equation}
+this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$.
+The system is scaled such that its peak amplitude is $3\unit{dB}$ and the 
+As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
+The gain of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
+\begin{equation}
+  \SNR_{\BW} \isdef
+  \frac{\int\limits_{\BW} \powerspec{\true{Y}}(\omega) \dd\omega}
+            {\int\limits_{\BW} \powerspec{V}(\omega) \dd{\omega}}
+  % \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
+  %           {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
+\end{equation}
+where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to $\set{10, 20, 40, 60, \infty} \unit{dB}$
+
+\begin{figure}
+ \centering
+  \input{\thisDir/figs/generalized-output-error.tikz}
+  \caption{Block schematic used in the simulations. }
+  \label{fig:nparam:blockH0}
+\end{figure}
+
+The input signal used is a random-phase multisine with a full linear grid.
+A number of samples of the input- and output are measured, in such a way that the \gls{DFT} grid excited $\nBW$ bins within the $3\unit{dB}$ bandwidth of the system.
+The different values for 
+\[\nBW \in \set{2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 14, 16, 32, 40, 64, 80, 92, 128, 256}\] are tried. 
+The use of $\nBW$ makes that the experiment length is normalized to take the bandwidth of the resonance into account.
+This means that the obtained results generalize to systems with a different relative damping.
+
+The \gls{FRF} is estimated using the local modeling approaches indicated in \tabref{tbl:nparam:methods}.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOtikzfig[figure with G and errors for 1 simulation]
+  \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods.
+The $3\unit{dB}$ bandwidth of the system is highlighted.}
+\end{figure}
+
+We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=\num{2000}$ Monte Carlo runs of the simulations above.
+Specifically, the following values
+\begin{align}
+  \sampleMean{\bullet}(\omega_k) & 
+  \isdef
+    \frac{1}{\nMC}
+    \sum_{i=1}^{\nMC}
+    \model[\atSimulation{i}]{\bullet}(\omega_k)
+  \\
+  \sampleBias{\bullet}(\omega_k) &
+    \isdef
+    \frac{1}{\nMC}
+    \sum_{i=1}^{\nMC}
+    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
+    = 
+    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
+    \\
+    \sampleVariance{\bullet}(\omega_k) &
+    \isdef
+    \frac{1}{\nMC - 1}
+    \sum_{i=1}^{\nMC}
+                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
+    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
+    \\
+    \RMSE_{\bullet}(\omega_k) & \isdef \sqrt{\sampleVariance{\bullet}(\omega_k) + \sampleBias{\bullet}^{2}(\omega_k)}
+\end{align}
+are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
+Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$. 
+For $\nMC=\num{2000}$, this means that we can detect the bias only when it is at most $20 \log \sqrt{\num{2000}} \unit{dB} \approx 33 \unit{dB}$ smaller than $\sampleStd{\bullet}$ and smaller biasses cannot be detected by the simulations.
+
+  % \subsection{Implications of the model structure}
+  % \subsection{Implications of the noise level}
+  % \subsection{Implications of the noise coloring}
+
+\begin{figure}
+  \centering
+  \remakeNextFigure
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
+  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system.}
+  \label{fig:nparam:mc:singleTuple}
+\end{figure}
+
+As the Monte Carlo simulations yield the estimated \gls{FRF}, the bias and variance for the different methods as a function of frequency, a huge amount of data is generated.
+In \figref{fig:nparam:mc:singleTuple}, two such sets of data are shown as an example.
+It can be seen that the \gls{RMSE} of \gls{LRIC} behaves erratically and exhibits spikes over the whole frequency band.
+For a short data length ($\nBW=8$), the \gls{LPM} and \gls{ETFE} shows a significant bias, whereas the \gls{LRM}-based methods have a very small bias and variance that lies below the noise floor of each experiment.
+However, the variance of the \gls{LRM} is still elevated by a few decibels near the resonance frequency.
+For long data lengths ($\nBW=64$), both \gls{LPM} and \gls{LRM} perform comparably.
+
+To interpret the data from the whole Monte Carlo simulation, we aggregate the observed values over the frequencies to obtain:
+\begin{align}
+  \sampleVariance{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleVariance{\bullet}(\omega_k)} \\
+  \sampleBias{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleBias{\bullet}(\omega_k)}
+\end{align}
+which can be visualized for the different values of the $\SNR$, $\nBW$ and for each method.
+Note that this aggregation is limited to the $3\unit{dB}$ bandwidth of the system, which is where the worst-case behavior is typically encountered.
+
+\begin{table}
+\centering
+\caption{Local modeling methods used in the Monte Carlo analysis.}
+\label{tbl:nparam:methods}
+\begin{tabular}{lccccr} 
+\toprule
+\textsc{Method} & \textsc{Color} & $\nWind$ & $\nth$ & \DOF & $\Delta\SNR \axisunit{dB}$ \\
+\midrule
+ $\ETFE$ & \ref{leg:nparam:etfe} & 1  & 1  & 0 & 0 \\
+ $\lrm{7,1,1,1}$ &  \ref{leg:nparam:lrm7111} & 15  & 5 & 10  & 4.77 \\
+ $\lric{7,2,2,2}$ & \ref{leg:nparam:lric7222} &   15 & 8 & 7  & 2.73 \\
+ $\lrm{7,2,2,2}$ & \ref{leg:nparam:lrm7222}  &   15 & 8 & 7  & 2.73 \\
+ $\lrm{6,2,2,2}$ & \ref{leg:nparam:lrm6222}  &   13 & 8 & 5  & 2.11 \\
+ $\lpm{7,4,4}$ & \ref{leg:nparam:lpm744} &   15 & 10 & 5  & 1.76 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\paragraph{Noiseless case}
+In the noiseless case, one can observe the approximation error that is made by using the \gls{LRM}, \gls{LPM}, \gls{LRIC} and \gls{ETFE} as shown in \figref{fig:nparam:comparison:noiseless}.
+For the \gls{ETFE}, it can be seen that the error is very high.
+This can be expected since the \gls{ETFE} does not separate transient/leakage contributions.
+Consequently, the leakage contributions (which change over the different Monte Carlo runs), lead to a large variance error for the \gls{ETFE}.
+The approximation error of the \gls{LPM} for short datasets ($\nBW \leq 8$) is dominated by the bias error.
+The is to be expected since the resonance in the band of interest is modeled using only polynomials instead of the full rational form.
+For longer datasets, 
+For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-64 \unit{dB}$ for the first-order method, $-114\unit{dB}$ for second-order methods).
+For short datasets ($\nBW \leq 16$), the $\lrm{7,1,1,1}$ error has a bias contribution that is slightly larger ($1$ to $4\unit{dB}$) than the variance contribution.
+For larger datasets ($\nBW \geq 16$), this bias contribution starts to diminish significantly as $\bigO{\nBW^{-2}}$.
+For second-order rational methods, the error is dominated by the variance and is about $50\unit{dB}$ smaller than for the first-order methods.
+Practically, this approximation error is very likely to be negligible in measurements as such an error level corresponds to the quantization noise level of a $19\unit{bit}$ \gls{ADC}.
+
+\begin{figure}[htb]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-Inf.tikz}
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.
+See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:noiseless}
+\end{figure}
+
+\paragraph{Good signal-to-noise ratios}
+The next situation we consider is when $\SNR=60\unit{dB}$ as shown in \figref{fig:nparam:comparison:hiSNR}.
+Here, the \gls{LPM} remains severly biased for small datasets ($\nBW < 12$).
+However, for sufficiently long experiments ($\nBW > 32$), the bias becomes negligible.
+For the \gls{LRM} and \gls{LRIC}, the bias is always much smaller than the variance.
+In contrast to \gls{LPM}, the \gls{LPM} already reaches a constant variance level when $\nBW > 10$.
+It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
+It is hence not advantageous to use the \gls{LRIC} as-is.
+For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches
+\begin{equation}
+  \lim_{\nBW \to \infty} \RMSE \approx \frac{\SNR}{\Delta \SNR}
+\end{equation}
+where
+\begin{equation}
+  \Delta\SNR = \sqrt{\frac{\nth}{\nWind}}
+\end{equation}
+accounts for the smoothing action of local modeling (see \tabref{tbl:nparam:methods} for numerical values of $\Delta \SNR$).
+
+For the more noisy situation where $\SNR = 40 \unit{dB}$ (\figref{fig:nparam:comparison:midSNR}), the situation is qualitatively equal except the bias incurred by the \gls{LRM} is similar to the noise level.
+
+\begin{figure}[phtb]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-60.tikz}
+  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:hiSNR}
+\end{figure}
+
+\begin{figure}[phbt]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-40.tikz}
+  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:midSNR}
+\end{figure}
+
+\paragraph{Poor signal-to-noise ratios}
+In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
+Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
+The
+
+\begin{figure}[phtb]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-20.tikz}
+  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:lowSNR}
+\end{figure}
+
+\begin{figure}[phbt]
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \input{\thisDir/figs/MC-SNR-10.tikz}
+ \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \label{fig:nparam:comparison:terribleSNR}
+\end{figure}
+
+\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
+For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
+When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
+\end{guideline}
+
+\begin{guideline}[For long measurements, LPM and LRM are similar]
+For very long measurements, the difference between \gls{LPM} and \gls{LRM} becomes negligible if the different resonances are well-separated.
+\end{guideline}
+
+  % \section{Measurements}
+  % \label{sec:measurements}
+  %  \subsection{AVIS}
+   % \subsection{F16}
 
@@
 \subsection{Order selection}
+\label{sec:nparam:orderSelection}
 Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
@@
 
-\section{LPM with impulse response truncation}
-\input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}
+Note that since the \gls{PRESS} can be interpreted similar to the residuals, this forms a convenient metric to select models on.
+In particular, when there is a large difference between the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{0.62\figurewidth}
+  \TODOtikzfig[PRESS and noise for single simulation]
+  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
+  \label{fig:nparam:PRESS}
+\end{figure}
+
+\TODO{discuss experiment + figure about PRESS}
+
+\subsection{LPM with impulse response truncation}
+\input{\thisDir/truncation.tex}
 

### 2016-04-25 ch03-lrm/truncation.tex
Lots of work on CH03

--- 2016-04-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
@@
 \researchBasedOn[This section]{Lumori2014TIM}
-\TODO{labels into standardized form}
+%TODO: {labels into standardized form}
 
@@
 The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
-This is depicted in \figref{fig:nparam:trunc:oe} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
+This is depicted in \figref{fig:nparam:blockH0} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
 \begin{equation}\label{eq:nparam:trunc:LPM:TD}
@@
 where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
-
-\begin{figure}
-\centering
-\setlength\figurewidth{0.85\columnwidth}
-\setlength\figureheight{0.68\figurewidth}
-\input{\thisDir/figs/oesetup.tikz}
-\caption{SISO LTI discrete-time system in an output error setup.}
-\label{fig:nparam:trunc:oe}
-\end{figure}
 
@@
 
-\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}
+\subsection*{Theory on the LPM and Windowing}
 \label{sec:nparam:trunc:theoryLPMandWindowing}
@@
 
-%TODO: re-use into LPM/LRM sections
 % \paragraph{Formulation of the Linear LS LPM}
@@
 % \begin{align}\label{lpmGTaylorS}
-% G_0(\Omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
+% G_0(\omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
 % \bigO{\left(\frac{r}{N}\right)^{R+1}},
@@
 % \label{lpmTTaylorS}
-% T(\Omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
+% T(\omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
 % \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
@@
 
-% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
+% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\omega_{k}$:
 % \begin{align}
-% G_0(\Omega_{k+r})
+% G_0(\omega_{k+r})
 %   &\approx 
@@
 % \\
-%   T(\Omega_{k+r})
+%   T(\omega_{k+r})
 %     &\approx 
@@
    \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
-   A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
+   A small band is selected (gray area), in which $\hat G_{\LPM}(\omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
 Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained.
@@
 
-\section{Smoothing the \gls{FRF} estimate}
+\subsubsection{Smoothing the \gls{FRF} estimate}
 \label{sec:nparam:trunc:smoothingFRFestimate}
@@
 
-\subsection{Truncation Via the $F$-Test}
+\subsubsection{Truncation Via the $F$-Test}
 \label{sec:nonparametric:truncation:ftest}
@@
 
-\subsection{Truncation of the Impulse Response Via Exponential Fitting}
+\subsubsection{Truncation of the Impulse Response Via Exponential Fitting}
 \label{sec:nonparametric:truncation:exponentialfit}
@@
 
-\subsection{Simulation Results}
+\subsubsection{Simulation Results}
 \label{sec:nparam:trunc:simResults}
@@
 
-\subsection{Conclusion}
+\subsubsection{Conclusion}
 \label{sec:nparam:trunc:conclusion}

### 2016-04-25 code/mvMCdataFreq.sh

@@ -1,0 +1,21 @@
+#!/bin/sh
+mv MC-SNR40-NBW*-1.tsv  H0.tsv
+mv MC-SNR40-NBW*-2.tsv  G0.tsv
+mv MC-SNR40-NBW*-3.tsv  LRM7222-rmse.tsv
+mv MC-SNR40-NBW*-4.tsv  LRM7222-bias.tsv
+mv MC-SNR40-NBW*-5.tsv  LRM7222-std.tsv
+mv MC-SNR40-NBW*-6.tsv  LPM744-rmse.tsv
+mv MC-SNR40-NBW*-7.tsv  LPM744-bias.tsv
+mv MC-SNR40-NBW*-8.tsv  LPM744-std.tsv
+mv MC-SNR40-NBW*-9.tsv  ETFE-rmse.tsv
+mv MC-SNR40-NBW*-10.tsv ETFE-bias.tsv
+mv MC-SNR40-NBW*-11.tsv ETFE-std.tsv
+mv MC-SNR40-NBW*-12.tsv LRM7111-rmse.tsv
+mv MC-SNR40-NBW*-13.tsv LRM7111-bias.tsv
+mv MC-SNR40-NBW*-14.tsv LRM7111-std.tsv
+mv MC-SNR40-NBW*-15.tsv LRM6222-rmse.tsv
+mv MC-SNR40-NBW*-16.tsv LRM6222-bias.tsv
+mv MC-SNR40-NBW*-17.tsv LRM6222-std.tsv
+mv MC-SNR40-NBW*-18.tsv LRIC7222-rmse.tsv
+mv MC-SNR40-NBW*-19.tsv LRIC7222-bias.tsv
+mv MC-SNR40-NBW*-20.tsv LRIC7222-std.tsv

### 2016-04-25 ch03-lrm/nonparametric.tex
Noise variance

@@
        = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
+       \label{eq:nparam:DOF}
 \end{equation}
@@
 
+Note that the estimated \gls{FRF} is given by evaluating the local model $\LocalModel{G}$:
+\begin{equation}
+  \hat{G}_{\LRIC}(\omega_k) \isdef \LocalModel[k]{G}(d=0)
+  \text{.}
+\end{equation}
+
 \subsection{The Local Rational Method}
@@
   \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
+  \label{eq:nparam:linearRegression}
 \end{equation}
@@
 \begin{equation}
-  \LocalVector{\theta}_{\LRM} 
+  \estimated{\LocalVector{\theta}}_{\LRM} 
     \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
@@
 where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.
-
-\TODO{hier voortschrijven: ruisvariantie berekenen}
+Furthermore, it is possible to define the relationship between the measured output spectrum $\LocalVector{Y}$ and the periodic output spectrum $\estimated{\LocalVector{Y}}$:
+\begin{equation}
+  \estimated{\LocalVector{Y}} 
+  = \LocalMatrix{K} \LocalVector{\theta}_{\LRM} 
+  = \LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalVector{Y}
+  = \LocalMatrix{H} \LocalVector{Y}
+\end{equation}
+where $\LocalMatrix{H}$ is sometimes called the `hat' matrix since it projects measurements ($\LocalVector{Y}$) onto the estimates ($\estimated{\LocalVector{Y}}$).
+It should be noted that the hat matrix is idempotent~\citep[Section 2.1.1]{Cook1982}.
+
+Following the approach in \citet[equation (12) and further]{Pintelon2010LPM1} or \citet[Chapter 2]{Cook1982}, the (ordinary) residuals $\LocalVector{E}$ of the fit are given by
+\begin{equation}
+  \LocalVector{E} = \LocalVector{Y} - \estimated{\LocalVector{Y}}
+  = \LocalVector{Y} - \LocalMatrix{H}\LocalVector{Y}
+  =  \left( \Identity{\nWind} - \LocalMatrix{H} \right) \LocalVector{Y}
+  \text{.}
+\end{equation}
+Substitution of \eqref{eq:nparam:linearRegression} in this equation yields
+\begin{align}
+  \LocalVector{E}  
+  &= (\I - \LocalMatrix{H})(\LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V})\\
+  &= (\I - \LocalMatrix{H}) \LocalVector{V} + (\I - \LocalMatrix{H})\LocalMatrix{K}\LocalVector{\theta}\\
+  &= (\I - \LocalMatrix{H}) \LocalVector{V} + \LocalMatrix{K}\LocalVector{\theta} - \LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalMatrix{K} \LocalVector{\theta}\\
+   &= (\I - \LocalMatrix{H}) \LocalVector{V}
+\end{align}
+since $\LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalMatrix{K} = \LocalMatrix{K}$ by construction of the pseudo-inverse~\citep{Penrose1955}.
+This equation relates the residuals $\LocalVector{E}$ to the noise $\LocalVector{V}$, which aids to estimate the noise variance:
+\begin{equation}
+  \estimated{\sigma}^2_{\LocalVector{V}} =
+    \frac{1}{\DOF} 
+     \LocalVector{E}^{\HT} \LocalVector{E}
+\end{equation}
+as elaborated in~\citep[Appendix B]{Pintelon2010LPM1}.
+Note that $\DOF$ indicates the degrees of freedom of the residuals as in \eqref{eq:nparam:DOF} and could also be computed as either the rank or the trace of the idempotent matrix $(\I - \LocalMatrix{H})$.
 
@@
 This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
-In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution.
+In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution from the contribution $\LocalModel{G} \LocalModel{U}$.
 This can be obtained e.g. using random phase multisines or random input signals.
@@
 \end{equation}
-this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$.
-The system is scaled such that its peak amplitude is $3\unit{dB}$ and the 
+this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$, $\damping=0.05$.
+The system is scaled such that its peak amplitude is $3\unit{dB}$ and hence its $3\unit{dB}$ bandwidth can be read easily from bode plots.
 As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
-The gain of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
+The gain $\kappa$ of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
 \begin{equation}
@@
 \end{equation}
-where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to $\set{10, 20, 40, 60, \infty} \unit{dB}$
+where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to \[
+\SNR_{\BW} \in \set{10, 20, 40, 60, \infty} \unit{dB}\text{.}
+\]
 
@@
   \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
-  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system.}
+  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system which has been highlighted.}
   \label{fig:nparam:mc:singleTuple}
@@
 
-\TODO{discuss experiment + figure about PRESS}
-
 \subsection{LPM with impulse response truncation}

### 2016-04-25 config/styles.inc.tex
Actually include MC figures
Some discussion on LRM results
Noise variance

@@
 /pgfplots/layers/mylayer/.define layer set=
-{axis background,axis grid,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
+{axis background,axis grid,pre main,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
 {/pgfplots/layers/standard}
@@
 }
+
+\pgfplotsset{slopegrid/.style={
+  mark phase=2,mark repeat=1,samples=2,mark=text,
+  color={black!15},forget plot,
+  text mark style={}
+}}
 
@@
 
+\colorlet{etfe}{TangoButter3}
+\colorlet{lrm7111}{TangoPlum3}
+\colorlet{lric7222}{TangoChameleon3}
+\colorlet{lrm7222}{TangoSkyBlue3}
+\colorlet{lrm6222}{TangoOrange3}
+\colorlet{lpm744}{TangoScarletRed3}
+
 %% Marker sizes
@@
 
-%TODO: replace *res -> *meas
-\pgfplotsset{results/.style={solid,line width=0.7pt}}
-\pgfplotsset{linmsres/.style={color=linms,results}}
-\pgfplotsset{qlogmsres/.style={color=qlogms,results}}
-\pgfplotsset{clogmsres/.style={color=clogms,results}}
-\pgfplotsset{plogmsres/.style={color=plogms,results}}
+% \pgfplotsset{results/.style={solid,line width=0.7pt}}
+% \pgfplotsset{linmsres/.style={color=linms,results}}
+% \pgfplotsset{qlogmsres/.style={color=qlogms,results}}
+% \pgfplotsset{clogmsres/.style={color=clogms,results}}
+% \pgfplotsset{plogmsres/.style={color=plogms,results}}
 
@@
 \pgfplotsset{clogms/.style={color=clogms,solid,line width=0.5pt}}
+
+%% MC LRM
+\pgfplotsset{mcrmse/.style={dotted}}
+\pgfplotsset{mcbias/.style={solid}}
+\pgfplotsset{mcvar/.style={dashed}}
 

### 2016-04-25 ch03-lrm/nonparametric.tex
Remove PRESS figure and spectra plot

@@
               \frac{\sigma_V^2}{\nWind} 
-                     \sum_{r} 
+                     \sum_{\delta} 
                                \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
@@
 \]
+This ensures that the excited bins in the $3\unit{dB}$ bandwidth of the system each receive a pre-defined \gls{SNR}.
 
@@
 
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.62\figurewidth}
-  \TODOtikzfig[figure with G and errors for 1 simulation]
-  \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods.
+% \begin{figure}
+%   \centering
+%   \setlength{\figurewidth}{0.85\columnwidth}
+%   \setlength{\figureheight}{0.62\figurewidth}
+%   \TODOtikzfig[figure with G and errors for 1 simulation]
+%   \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods.
 The $3\unit{dB}$ bandwidth of the system is highlighted.}
-\end{figure}
+% \end{figure}
 
@@
     \sum_{i=1}^{\nMC}
-                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
-    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
+                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \sampleMean{\bullet}(\omega_k) \right)
+    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \sampleMean{\bullet}(\omega_k) \right) }
     \\
@@
   \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
-  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system which has been highlighted.}
+  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
   \label{fig:nparam:mc:singleTuple}
@@
 Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
-The
+At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
+For larger datasets ($\nBW \geq 16$), all methods perform similarly and at a nearly constant level of (variance) error.
+The \gls{LRM}, in contrast to the \gls{LPM}, still contains an observable bias in the simulations.
+At even lower $\SNR=10\unit{dB}$,  most methods perform quite poorly for short datasets ($\nBW < 6$).
+However, here it can be seen that the $\lpm{7,4,4}$ outperforms both the $\lrm{7,1,1,1}$ and $\lrm{7,2,2,2}$ and slightly worse than $\lrm{6,2,2,2}$.
+It can be seen that the bias error of the \gls{LPM} drops off more quickly ($\bigO{\nBW^{-3}}$) than the \gls{LRM} bias which drops in approximately $\bigO{\nBW^{-1}}$.
 
@@
 Note that since the \gls{PRESS} can be interpreted similar to the residuals, this forms a convenient metric to select models on.
-In particular, when there is a large difference between the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.
-
-\begin{figure}
-  \centering
-  \setlength{\figurewidth}{0.85\columnwidth}
-  \setlength{\figureheight}{0.62\figurewidth}
-  \TODOtikzfig[PRESS and noise for single simulation]
-  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
-  \label{fig:nparam:PRESS}
-\end{figure}
+In particular, when there is a large difference between the level of the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.
+
+% \begin{figure}
+%   \centering
+%   \setlength{\figurewidth}{0.85\columnwidth}
+%   \setlength{\figureheight}{0.62\figurewidth}
+%   \TODOtikzfig[PRESS and noise for single simulation]
+%   \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
+%   \label{fig:nparam:PRESS}
+% \end{figure}
 

### 2016-04-25 ch03-lrm/truncation.tex
Fix some references

@@
 
-Using convolution, the noiseless output signal in \figref{fig:nparam:trunc:oe} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
+Using convolution, the noiseless output signal in \figref{fig:nparam:blockH0} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
 As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
@@
 
-The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:trunc:oe}):
+The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:blockH0}):
 \begin{assumption}
@@
 
-% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:trunc:oe} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
+% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
 % \begin{equation}\label{lpm1spectra}

### 2016-04-25 ch04-lrmhinf/lrmhinf.tex
Fix some references

@@
 \begin{remark}
-The optimization problems \eqref{eq:lrmhinf:gammaInxterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
+The optimization problems \eqref{eq:lrmhinf:gammaInterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
 The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel[k]{\Delta}$ are evaluated over identical frequency ranges

### 2016-04-25 ch06-concl/conclusions.tex
Fix some references

@@
 There are a few approaches that we think are worthwhile to investigate.
-On the one hand, the truncation methods explained in \secref{sec:nparam:trunc} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
+On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
 On the other hand, one could devise crude model order selection procedures, e.g.

### 2016-04-26 ch06-concl/conclusions.tex
Some work on conclusions

@@
   In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
-  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid should conform to
+  Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid with frequency resolution $\Delta f$ should conform to
   \begin{equation}
@@
   to attain a reliable estimate of the resonances present in the system.
-  The choice to use the equality $\alpha = 1+ \damping[\min]$ is the optimal choice within the framework presented in \chapref{sec:excitation}. 
+  The choice to use the equality $\alpha = 1+ \damping[\min]$ is the optimal choice within the framework presented in \chapref{sec:excitation} such that resonances with $\damping \geq \damping[\min]$ and $\wn \geq \omegaLinLog = \frac{2 \pi \Delta f}{\alpha-1} = \frac{2 \pi \Delta f}{\damping[\min]}$ are well-represented in the \gls{FRF}.
   Decreasing $ \alpha$ further comes at the cost of more excited frequency bins and consequently a lower power per bin, or, a reduced \gls{SNR} per bin if the overall signal power is limited.
 
-  In practical terms of a layman user, this means that the design of a quasi-logarithmic multisines discussed in this thesis, requires only limited prior knowledge from the user:
+  In practical terms of a layman user, this means that the design of a quasi-logarithmic multisines--- as discussed in this thesis--- requires only limited prior knowledge:
   \begin{itemize}
-    \item the allowable measurement time (or equivalently, the minimal relevant frequency),
+    \item the available measurement time (or equivalently, the minimal relevant frequency $\omegaLinLog$),
     \item the allowable total excitation power,
@@
   \subsection{Non-parametric estimation}
+
   \subsection{Initialization of parametric estimation}
+  To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
+  However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
+  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
+  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
+  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
 
@@
   Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
-  %TODO: for ny x nu MIMO system, alpha_MIMO = 1 + alpha_SISO/nu to satisfy the density of frequency lines.
-This means: lowest guaranteed observable resonance is at higher frequencies than for SISO (obviously).
 
@@
   \subsection{Non-parametric estimators}
-    \TODO{Order selection / BW selection}
-    \TODO{MIMO LRM}
     The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
-    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc}.
+    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc} has shown.
     As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
     Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
+    Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.
 
@@
 
+    Another application where the \gls{LPM} is more developed is the handling of missing data~\citep{Ugryumova2015}.
+    In particular, the frequency domain relationship between the input $U$ and output $Y$ is augmented by a term $M_Y$ that accounts for the missing output data samples:
+    \begin{equation}
+      Y(\omega_k) = G(\omega_k) U(\omega_k) + T(\omega_k) + M_Y(\omega_k) + \mathrm{noise}\text{,}
+    \end{equation}
+    since $G(\omega_k)$ is captured by local polynomials, this allows to construct a design matrix as discussed in \chapref{sec:nonparametric} which only depends on $U$ and the time instances where the data is missing.
+    For the \gls{LRM}, on the other hand, the design matrix depends on the output $Y$ which is not known.
+    Consequently, extending the \gls{LRM} to handle missing data is non-trivial.
+
+    Finally, a comparison between different approaches for non-parametric modeling~\citep{Hagg2012,Stenman2001ASFRF,Gevers2011lpm} could be made.
+    This could be done from a theoretical point of view to find correspondences between different approaches (e.g.
+\citep{Hagg2012} reduces to \gls{ETFE} as does the \gls{LRM} for specific settings) and from a qualitative point of view to find the best operating regions of each approach.
+    Eventually, this could even lead to hybrid methods that either select the best method for a specific setting or use results from different methods to overcome weaknesses of individual methods such as high computational complexity, high bias, high variance, \ldots
+    Especially in the view of \gls{LRM} as a form of local regression~\citep{Loader1999}, it could be worthwhile to also investigate suitable (frequency-domain) kernels instead of the uniform kernel that is implicitly used in the \gls{LRM}.
+
   \subsection{Non-parametric estimation and interpolation}
-  \TODO{Link between local models and weighting function design}
+  As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
+  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
+  Hence, the link between local models and the design of weighting filters and parametric overbounds needs to be made more explicit and verified experimentally.
+
+  Another possibility for future research is approach the problem of $\Hinf$ gain estimation purely form the aspect of local regression such that combining multiple models is no longer necessary.
 

### 2016-04-26 ch06-concl/code/trialNlin.m

@@ -1,0 +1,18 @@
+w = unique(round(logspace(log10(1),log10(1000),50)));
+w = w(mod(w,2)~=0);
+
+makeNLinCombo = @(w, ord) unique(sum(combnk(unique([w(:); -w(:)].'), ord),2));
+plotStems = @(w,ord,varargin) stem(w(w>0), 1/ord*ones(size(w(w>0))), 'DisplayName',num2str(ord), varargin{:});
+
+w1 = makeNLinCombo(w, 1);
+w2 = makeNLinCombo(w, 2);
+w3 = makeNLinCombo(w, 3);
+w4 = makeNLinCombo(w, 4);
+
+%%
+figure; hold all;
+plotStems(w1, 1);
+plotStems(w2, 2);
+plotStems(w3, 3);
+plotStems(w4, 4);
+set(gca,'XScale','log')

### 2016-04-27 config/glossaries.inc.tex
Lots of work on CH03
Uniform commands: part 1
Link to Stenman
Solve some warnings

@@
-\usepackage[sanitize={symbol=false},toc,acronym,section=section,nonumberlist,xindy]{glossaries}
+\usepackage[toc,acronym,section=section,nonumberlist,xindy]{glossaries}
 
@@
 name={#3},
+short={#3},
+long={#4},
+shortplural={#3\glspluralsuffix},
+longplural={#4\glspluralsuffix},
 description={#4},
@@
 
-\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identity matrix}
+\newsymbolglos{matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
+\newsymbolglos{matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
+\newsymbolglos{matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}
 
@@
 
+\newsymbolglos{operator-bias}{\bias{\placeholder}}{Bias of \placeholder}
 \newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
-\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
+\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
+\newsymbolglos{operator-exp}{\E{\placeholder}}{Expected value of \placeholder}
 \newsymbolglos{operator-ln}{\ln}{Natural logarithm}
-\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
 \newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
+\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
+\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
 \newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
+\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
 \newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
 \newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
-\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
-\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
-\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
 \newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
@@
 \newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
+\newsymbolglos{operator-var}{\var{\placeholder}}{Variance of \placeholder}
 
@@
 \newacronym{LOOCV}{LOOCV}{leave-one-out cross-validation}
+\newacronym{LOWESS}{LOWESS}{locally weighted scatterplot smoothing}
 \newacronym{LMM}{LMM}{Local Modeling Method}

### 2016-04-27 ch02-qlogms/excitation-design.tex
Improved MC figures
Fix some references
Some work on conclusions
More conclusion + small stuff everywhere

@@
   Note that this is a computationally efficient way since both \mcode{logspace} and \mcode{unique} require at most $\bigO{ F }$ time, where \mcode[mathescape]{$F\;$ = numel(fLog)}.
+  % computational complexity: 
+  % `logspace` := O(F) in both time and space (just a for-loop)
+  % `unique` := O(F) in both time and space (values are sorted beforehand, so just for-loop, flag items that are equal to the last and return unflagged items)
   \end{example}
@@
   \centering
+   \caption{Summary of  properties of the different frequency grids.}
    \label{tbl:excitation:gridProperties}
-   \caption{Summary of  properties of the different frequency grids.}
     \begin{tabular}{rccc} 
@@
   The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
-  The value of $N$ will not influence the `shape` (and uncertainty) of the FRF.
+  The value of $N$ will not influence the `shape` (and uncertainty) of the \gls{FRF}.
 
@@
     \input{\thisDir/figs/Sys02-4.tikz}
-    \caption[Simulated \gls{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
+    \caption[Simulated \glsentryshort{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
     \label{fig:excitation:FRF1}
@@
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption[Simulated \glspl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
+    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
        \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
@@
     \input{\thisDir/figs/damping005-cmp.tikz}
-    \caption[Simulated \glspl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
+    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
     Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
@@
   \input{\thisDir/figs/Sum02log0-2.tikz}
-  \caption[Simulated FRF of sum of two sub-systems.]{FRF for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
+  \caption[Simulated \glsentryshort{FRF} of sum of two sub-systems.]{\gls{FRF} for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
   \label{fig:excitation:sumSys}

### 2016-04-27 ch03-lrm/nonparametric.tex
Fix some references
More conclusion + small stuff everywhere

@@
   \centering
-  \remakeNextFigure
   \setlength{\figurewidth}{0.85\columnwidth}
@@
   \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
-  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
+  \caption[Bias, variance for $\nBW \in \set{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
   \label{fig:nparam:mc:singleTuple}

### 2016-04-27 ch03-lrm/truncation.tex
More conclusion + small stuff everywhere

@@
    \setlength{\figureheight}{0.68\figurewidth}
-
    \input{\thisDir/figs/LPMfig.tikz}
@@
 \end{enumerate}
-This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{sec:nparam:trunc:LPMFRFest}:
+This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
 \begin{subequations}
-\label{eq:systemSimulations}
+\label{eq:trunc:systemODEs}
 \begin{align}
@@
 \end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
-% \eqref{eq:systemSimulations}. 
+where $e(t)$ is a white noise sequence, such that the SNR of the output signal is $78.2\unit{dB}$.
 The figure shows segments of the estimated impulse response.
@@
 Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
-They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
-\begin{subequations}
-\label{eq:systemSimulations}
-\begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
-\\
-y(t) &= y_0(t) + e(t),
-\end{align}
-\end{subequations}
-where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.
+They were obtained from simulations on the system in \eqref{eq:trunc:systemODEs} where the noise variance was set such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.
 

### 2016-04-27 ch06-concl/conclusions.tex
More conclusion + small stuff everywhere

@@
 \tikzsetfigurename{ch06fig}
-
-\section{Conclusions of this research}
 
@@
 
-\section{Future perspectives}
-  \subsection{Excitation design}
+\section{Future Perspectives}
+  \subsection{Excitation Design}
   In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
@@
 
-  \subsection{Non-parametric estimators}
+  \subsection{Non-parametric Estimators}
     The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
@@
     Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.
+
+    As has been seen in \chapref{sec:nonparametric}, the \gls{LRIC} is affected by a high variance.
+    This is due to pole-zero cancellations that arise when the local bandwidth does not contain data that is informative enough to estimate models of the required complexity.
+    As such, future research needs to be undertaken to overcome such hurdles, by means of model order selection or reduction of those local models.
+    If these hurdles can be overcome, the bias of local modeling can be reduced significantly.
+    This is important for short datasets with very noisy data.
+
+    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
+    \begin{equation}
+      \LocalModel[\CT]{G}(\dW) 
+      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
+      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
+    \end{equation}
+    There have already been some experiments with other model structures such as local discrete time models where
+    \begin{equation}
+      \LocalModel[\DT]{G}(\dW) 
+      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
+      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
+    \end{equation}
+    but these have proven more difficult to estimate numerically and hence unreliable.
+    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} for complex coefficients.
 
@@
     \end{equation}
-    since $G(\omega_k)$ is captured by local polynomials, this allows to construct a design matrix as discussed in \chapref{sec:nonparametric} which only depends on $U$ and the time instances where the data is missing.
+    since $G(\omega_k)$ is captured by local polynomials, this allows to construct a design matrix as discussed in \chapref{sec:nonparametric} which only depends on $U$ and the time instances where the data $y(t)$ is missing.
     For the \gls{LRM}, on the other hand, the design matrix depends on the output $Y$ which is not known.
-    Consequently, extending the \gls{LRM} to handle missing data is non-trivial.
+    Consequently, extending the \gls{LRM} to handle missing data is non-trivial and could be an interesting topic for further research.
 
@@
 
-  \subsection{Non-parametric estimation and interpolation}
+  \subsection{Non-parametric Estimation and Interpolation}
   As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
@@
 
-  \subsection{Parametric initialization}
+  \subsection{Construction of Initial Values}
   In \chapref{sec:initvals} it was already illustrated that smoother can provide improved initial estimates of a system. 

### 2016-04-27 ch06-concl/conclusions.tex
Finished conclusions

@@
   \subsection{Non-parametric estimation}
+  Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
+  It has been shown that the most general \gls{LRIC} is very sensitive to the use of the `correct' local model order.
+  The pre-existing \gls{LRM} and \gls{LPM}, however, are not as sensitive.
+  It has been shown that the inherent bias of the \gls{LRM} becomes the dominant source of errors, in contrast to the variance, when an \gls{SNR} of less than $20\unit{dB}$ is available in the frequency bands of interest.
+  For resonant systems, the \gls{LRM} is superior to the \gls{LPM} in terms of both bias and \gls{RMS} error in almost all cases.
+  The \gls{LPM} is slightly superior for very noisy datasets ($\SNR < 20 \unit{dB}$) that have a very limited frequency resolution.
+
+  It has also been illustrated that the use of such local models allows to extract the resonance peak and thereby the $\Hinf$ gain of a system.
+  In that setting, the \gls{LPM} is not reliable due to its limited model flexibility.
+  The \gls{LRM}, on the other hand, has been shown to be yield estimates of the $\Hinf$ gain that improved greatly compared to pure \gls{FRF} measurements.
+  For systems that consist of complex dynamic behavior, this allows one to extract reasonable peak values without the hassle of building a global parametric model.
+  The use of such local models, in practice, has been validated and can provide good estimates using a dataset that is four times smaller than what would be required for other \gls{FRF}-based methods.
+  As such, the measurement time (and hence cost) can also be reduced by the same amount.
 
@@
   It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
+  These smoothers allow one to obtain good models from noisier data than what existing techniques.
+  The improvement of the initial values has been verified both on simulations, measurements and a simulation stress test consisting of different filters.
+  While overall the \gls{RFIR} provides the best starting values from the different smoothers, combining multiple initial values remains a very valuable approach to make a system identification toolbox robust for the measurement data.
 
@@
     but these have proven more difficult to estimate numerically and hence unreliable.
-    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} for complex coefficients.
+    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
 

### 2016-04-27 ch06-concl/conclusions.tex
Conclusions finished? + some minor stuff

@@
   The \gls{LPM} is slightly superior for very noisy datasets ($\SNR < 20 \unit{dB}$) that have a very limited frequency resolution.
+
+  In addition, an approach has been developed that allows to reduce the variance of the estimated \gls{FRF} when it is captured in a long data record.
+  This method works by examining the estimated impulse response, i.e.
+the inverse \gls{DFT} of the \gls{FRF}, and estimating a truncation time $\truncTime$ beyond which the impulse response is overwhelmed by the noise.
+  By truncating past this point and transforming the result back into the frequency domain, an \gls{FRF} is obtained that has a reduced \gls{RMS} error by reducing the variance due to the noise.
+  Two complementary approaches to determine $\truncTime$ have been developed.
+  Both methods estimate the noise level on the impulse response by assuming the last $10\%$ of the samples are only noise.
+  The first method exploits the fact that many physical systems exhibit an exponential decay.
+  This exponential decay is estimated roughly, such that the truncation point is determined as the instant where decay is below the noise level.
+  The second method divides the impulse response into segments.
+  Starting from the last segment, it is tested statistically whether the preceding segment is significantly different from the noise, such that $\truncTime$ is estimated.
 

### 2016-04-28 ch06-concl/conclusions.tex
Comments Tom: conclusion

@@
 
-  \subsection{Excitation design}
+\section{Results of this Research}
+\TODO{general introduction, claim the title, reaffirm the structure of the book}
+
+  \subsection{Excitation Design}
   In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
@@
   As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
-  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed relative uncertainty of the identified \gls{FRF} near the resonance peaks.
+  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed (relative) uncertainty of the identified \gls{FRF} near the resonance peaks as caused by the measurement noise.
   Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid with frequency resolution $\Delta f$ should conform to
@@
 
-  \subsection{Non-parametric estimation}
+  \subsection{Non-parametric Estimation}
   Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
@@
 
-  \subsection{Initialization of parametric estimation}
+  \subsection{Initialization of Parametric Estimation}
   To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
@@
   Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.
+  The use of \gls{LRM}/\gls{LPM} may help to overcome that the frequency grids for the different input/output channels do not coincide for zippered signals.
 
@@
       = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
-      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
+      = \frac{\Sum_i  b_i \exp (ji\dW\Ts)}{\Sum_i  a_i \exp (ji\dW\Ts) }
     \end{equation}
@@
     Preliminary tests using the \gls{LRM} in lieu of the \gls{LPM} have proven fruitful.
-    Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep[Chapter 4]{vanderMaas2016PhD}.
+    Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep{vanderMaas2015CDC}.
     Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
@@
   \subsection{Non-parametric Estimation and Interpolation}
-  As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
+  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
   In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
-  Hence, the link between local models and the design of weighting filters and parametric overbounds needs to be made more explicit and verified experimentally.
+  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.
 
-  Another possibility for future research is approach the problem of $\Hinf$ gain estimation purely form the aspect of local regression such that combining multiple models is no longer necessary.
+  Another possibility for future research is to approach the problem of $\Hinf$ gain estimation purely from the aspect of local regression such that combining multiple local models is no longer necessary.
 
@@
 Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
-This doesn't do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.
+This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.

### 2016-04-28 ch03-lrm/nonparametric.tex
Some comments from Johan, tom

@@
 \begin{equation}
-  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \IntegerNumbers
+  y[n] = \ezbrace{\true{G}(q) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(q) \true{e}[n]}{v[n]} \text{ with } n \in \IntegerNumbers
   \label{eq:output-error-TD-infinite}
 \end{equation}
-where $v[n]$ is filtered white noise, $v[n] = \true{H}(z) \true{e}[n]$ where $z^{-1}$ is the backward shift operator, i.e. $z^ {-1}x[n] = x[n-1]$.
-The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are stable and causal.
+where $v[n]$ is filtered white noise, $v[n] = \true{H}(q) \true{e}[n]$ where $q^{-1}$ is the backward shift operator, i.e. $q^ {-1}x[n] = x[n-1]$.
+The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are causal and stable.
 
@@
 \begin{equation}
-y[n] = \true{G}(z) u[n] + \true{H}(z) \true{e}[n] + \ezbrace{t_G[n] + t_H[n]}{t[n]}
+y[n] = \true{G}(q) u[n] + \true{H}(q) \true{e}[n] + \ezbrace{t_G[n] + t_H[n]}{t[n]}
 \label{eq:output-error-TD-finite}
@@
 \end{itemize}
-The main term of interest, however, is the transfer function $\true{G}$ and a secondary concern is estimating the noise variance $\Var{V}$.
+The main term of interest, however, is the transfer function $\true{G}$ and a secondary concern is estimating the noise variance $\sigma_{V}$.
 
@@
 
-The local parameters $\theta$  
+To estimate the local parameters $\theta$  
 \begin{equation}
@@
 with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
-such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
+such that the local window around $\omega_k$ consists of $\nWind = 2 \numel{W} + 1$ bins. 
 If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
@@
 Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
-We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.
+We hence call this method the \gls{LRIC} and denote specific configurations of this method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.
 
@@
     & \isdef 
+    \phantom{+}
   \mat{
@@
     &\isdef
+    \phantom{+}
     \mat{
@@
     &\isdef
-    \mat{
+    - \mat{
       \LocalVector{U} \hadamard \LocalVector{d}^0 &
@@
     &\isdef
-    \mat{
+    - \mat{
       \LocalVector{d}^0 &
@@
 
-We denote a method that solves \eqref{eq:nparam:LRM:costFunc} for given bandwidth and local orders as $\lrm{\numel{W}, \order{B},\order{A},\order{C}}$.
+We denote a method that solves \eqref{eq:nparam:LRM:costFunc} as $\lrm{\numel{W}, \order{B},\order{A},\order{C}}$ where $\numel{W}$ is the half-bandwidth, and $\order{B}$, $\order{A}$ and $\order{C}$ are the local model orders.
 
@@
 The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
-As such, we can use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, 0, \order{C}}$.
+As such, we use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, \order{B}, 0, \order{C}}$.
 
@@
 \end{multline}
+We use the notation
+\begin{equation}
+  \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}
+  \isdef
+  \evaluate{\PartialDerivative{\ELSCost(\theta)}{\theta}}{\theta = \true\theta}
+\end{equation}
+for the derivative of $\ELSCost{\theta}$ with respect to $\theta$, evaluated in $\true\theta$.
 The minimizer $\estimated\theta$ of this function can be obtained by equating the derivative
@@
 \begin{equation}
-  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta}
+  \PartialDerivative{\ELSCost[n]{\true\theta, \conj{\true\theta}}}{\theta}
   = 
   \begin{bmatrix}
-  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_A} &
-  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_B} &
-  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C}
+  \PartialDerivative{\ELSCost[n]{\true\theta, \conj{\true\theta}}}{\theta_A} &
+  \PartialDerivative{\ELSCost[n]{\true\theta, \conj{\true\theta}}}{\theta_B} &
+  \PartialDerivative{\ELSCost[n]{\true\theta, \conj{\true\theta}}}{\theta_C}
   \end{bmatrix}
@@
 
-\begin{figure}
+\begin{figure}[p]
   \centering 
@@
   \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
-  \caption[Bias, variance for $\nBW \in \set{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
+  \caption[Bias, variance for $\nBW \in \set{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the \gls{FRF} using the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).
+See \tabref{tbl:nparam:methods} for the color legend.}
   \label{fig:nparam:mc:singleTuple}
@@
 
-As the Monte Carlo simulations yield the estimated \gls{FRF}, the bias and variance for the different methods as a function of frequency, a huge amount of data is generated.
-In \figref{fig:nparam:mc:singleTuple}, two such sets of data are shown as an example.
-It can be seen that the \gls{RMSE} of \gls{LRIC} behaves erratically and exhibits spikes over the whole frequency band.
-For a short data length ($\nBW=8$), the \gls{LPM} and \gls{ETFE} shows a significant bias, whereas the \gls{LRM}-based methods have a very small bias and variance that lies below the noise floor of each experiment.
-However, the variance of the \gls{LRM} is still elevated by a few decibels near the resonance frequency.
-For long data lengths ($\nBW=64$), both \gls{LPM} and \gls{LRM} perform comparably.
-
-To interpret the data from the whole Monte Carlo simulation, we aggregate the observed values over the frequencies to obtain:
-\begin{align}
-  \sampleVariance{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleVariance{\bullet}(\omega_k)} \\
-  \sampleBias{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleBias{\bullet}(\omega_k)}
-\end{align}
-which can be visualized for the different values of the $\SNR$, $\nBW$ and for each method.
-Note that this aggregation is limited to the $3\unit{dB}$ bandwidth of the system, which is where the worst-case behavior is typically encountered.
-
-\begin{table}
+\begin{table}[p]
 \centering
@@
 
+As the Monte Carlo simulations yield the estimated \gls{FRF}, the bias and variance for the different methods as a function of frequency, a huge amount of data is generated.
+In \figref{fig:nparam:mc:singleTuple}, two such sets of data are shown as an example.
+It can be seen that the \gls{RMSE} of \gls{LRIC} behaves erratically and exhibits spikes over the whole frequency band.
+For a short data length ($\nBW=8$), the \gls{LPM} and \gls{ETFE} shows a significant bias, whereas the \gls{LRM}-based methods have a very small bias and variance that lies below the noise floor of each experiment.
+However, the variance of the \gls{LRM} is still elevated by a few decibels near the resonance frequency.
+For long data lengths ($\nBW=64$), both \gls{LPM} and \gls{LRM} perform comparably.
+
+To interpret the data from the whole Monte Carlo simulation, we combine the observed values over the frequencies to obtain the \term{aggregated error}, respectively:
+\begin{align}
+  \sampleVariance{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleVariance{\bullet}(\omega_k)} \\
+  \sampleBias{\bullet} &= \frac{1}{\nBW} \sum_{\omega_k \in \BW} \abs{\sampleBias{\bullet}(\omega_k)}\\
+  \RMSE_{\bullet} &= \sqrt{\sampleBias{\bullet}^2 + \sampleVariance{\bullet}}
+\end{align}
+which can be visualized for the different values of the $\SNR$, $\nBW$ and for each method.
+Note that this aggregation is limited to the $3\unit{dB}$ bandwidth of the system, which is where the worst-case behavior is typically encountered.
+
 \paragraph{Noiseless case}
@@
 The is to be expected since the resonance in the band of interest is modeled using only polynomials instead of the full rational form.
-For longer datasets, 
+For longer datasets, the error decays approximately as $\bigO{\nBW^{-6}}$.
+This is in line with the theoretical derivation from \citet{Schoukens2013LPMerror} that state that the approximation error decays as $\bigO{ \nBW^{-(\order{B}+2)}}$.
 For the \gls{LRM} and \gls{LRIC}, the \gls{RMS} error is already very low for small datasets ($-64 \unit{dB}$ for the first-order method, $-114\unit{dB}$ for second-order methods).
@@
   \input{\thisDir/figs/MC-SNR-Inf.tikz}
-  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses.
-See \tabref{tbl:nparam:methods} for the color legend.}
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses. }
   \label{fig:nparam:comparison:noiseless}
@@
   \input{\thisDir/figs/MC-SNR-60.tikz}
-  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:hiSNR}
@@
   \input{\thisDir/figs/MC-SNR-40.tikz}
-  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:midSNR}
@@
   \input{\thisDir/figs/MC-SNR-20.tikz}
-  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.
+  The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:lowSNR}
@@
   \input{\thisDir/figs/MC-SNR-10.tikz}
- \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. See \tabref{tbl:nparam:methods} for the color legend.}
+ \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:terribleSNR}
@@
 In plug-in methods, a goodness-of-fit criterion (e.g.
-the log-likelihood function $\LogLikelihood$ of the estimated model $M$ given the estimation dataset $Z$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
+the log-likelihood function $\LogLikelihood$ of the estimated local model $\LocalModel{M}$ given the estimation dataset $\LocalVector{Z}$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
 E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
@@
 L_{\mathrm{\AIC}} &=
- - 2  \loglikelihood{M | Z} 
+ - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
  + 2 \nth\\
 L_{\mathrm{\AICc}} &= 
-- 2  \loglikelihood{M | Z} 
+- 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
 +   \frac{2 \nth\nWind}{\nWind - \nth - 1}
 \end{align}
-where $\nth$ is the number of  estimated parameters in the model $M(\theta)$.
+where $\nth$ is the number of  estimated parameters in the model $\LocalModel{M}(\theta)$.
 In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e.
@@
 \begin{remark}
-It should be noted that due to $\loglikelihood{M | Z}$ , the value of $L_{\mathrm{AIC(c)}}(M,Z)$ is inherently coupled with the particular dataset $Z$.
+It should be noted that due to $\loglikelihood{\LocalModel{M} | \LocalVector{Z}}$ , the value of $L_{\mathrm{AIC(c)}}(\LocalModel{M},\LocalVector{Z})$ is inherently coupled with the particular dataset $\LocalVector{Z}$.
 Practically, this means that such criteria can only be used to compare local models that are estimated from the same local dataset (i.e. they have the same $\nWind$ and center frequency).
-Consequently, the \gls{AICc} criterion cannot be used to select a proper $\nWind$.
+Consequently, the \gls{AICc} criterion cannot be used to select $\nWind$, but only $\order{A},\order{B},\order{C}$ when $\nWind$ is fixed.
 \end{remark}
@@
 For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
-For
 In this chapter, the \gls{LRIC} was introduced.

### 2016-04-29 ch01-intro/introduction.tex
More conclusion + small stuff everywhere
Some stuff, here and there

@@
 You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}
+
+In this chapter, we first discuss some basic aspects of system identification, some typical choices and how those relate to user-friendly system identification and this dissertation.
+
 \section{System idenfication}
+\subsection{Linear System theory}
+\subsection{System Identification Approaches}
+
+\subsubsection{White Box, Black Box or Grey Box}
+\subsubsection{Time or Frequency Domain}
+\subsubsection{Linear or nonlinear?}
+\subsubsection{Time invariant or non?}
+
+\section{User-friendly System Identification}
+In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
+User-friendly should be understood as having a good user experience for two groups of users:
+\begin{itemize}
+  \item novice users, without formal training in system identification, optimization, \ldots and,
+  \item well-seasoned identification practitioners that are already able to build good models.
+\end{itemize}
+Concretely, for novice users it is important to have straightforward techniques that require little interaction.
+In practice, this boils down to methods that work well for a wide class of systems.
+As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.
 
 \begin{figure}
-
   \centering
@@
 \section{Publications}
-   The lion's share of this thesis has been published either in peer-reviewed scientific journals and conferences or has been submitted to such venues at the time of writing.
+   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
    This section links my different publications to the different sections in this thesis.
-   For an overview of publications grouped by type, please refer to \pageref{publicationList}.
+   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.
 
@@
 \end{itemize}
-The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
+The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
 \begin{itemize}

### 2016-04-29 ch03-lrm/nonparametric.tex
Some stuff, here and there

@@
   &\approx
-  \frac{\Sum_{i=0}^{\order{B}} b_i d^i}
-            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
+  \frac{\Sum_{i=0}^{\order{B}} b_i(k) d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
     &\isdef
@@
   \true{T}(\omega_k + d) &\approx
-  \frac{\Sum_{i=0}^{\order{C}} c_i d^i}
-            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
+  \frac{\Sum_{i=0}^{\order{C}} c_i(k) d^i}
+            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
     &\isdef 
@@
 \end{equation}
+
+\begin{remark}
+It should be noted that \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T} are essentially isomorphic to a continuous-time transfer function model with complex coefficients.
+The discrete-time counterparts (i.e. substituting $d^i \to \exp (ji d \Ts)$ in the expressions), have been tried as well.
+However, these preliminary experiments did not yield estimates that were numerically reliable.
+\end{remark}
 
@@
 \label{sec:biascalc}
-Since the local design matrix \eqref{eq:nparam:designMatrix} of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
+Since the local design matrix $\LocalMatrix{K}$, see \eqref{eq:nparam:designMatrix}, of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
 In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.
@@
 
-Do note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
+Note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
 In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
@@
   \input{\thisDir/figs/MC-SNR-Inf.tikz}
-  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses. }
+  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is small enough for many practical uses. }
   \label{fig:nparam:comparison:noiseless}
@@
 \begin{equation}
-  \Delta\SNR = \sqrt{\frac{\nth}{\nWind}}
+  \Delta\SNR \isdef \sqrt{\frac{\nth}{\nWind}}
+  \label{eq:nparam:deltaSNR}
 \end{equation}
@@
 
-\begin{figure}[phtb]
+\begin{figure}[p]
   \centering
@@
 
-\begin{figure}[phbt]
+\begin{figure}[p]
   \centering
@@
 Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
+However
 At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
@@
 
+\subsection{Summary}
+\TODO{discussie}
+
 \begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
@@
 When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
+The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
 \end{guideline}
@@
 \section{Trading off the bias and variance}
+
+\TODO{introduction}
 

### 2016-04-29 ch03-lrm/truncation.tex
Conclusions finished? + some minor stuff
Some stuff, here and there

@@
 %    alpha >> ==> beta <<
-% 4) if H1 and RMS(signal)/RMS(noise) > f
+% 4) if H1 and RMS(signal)/RMS(noise) < f
 %    robustness, SNR
@@
   Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
-  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
+  In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
   \begin{equation}
-    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
+    F \isdef \frac{s^2(i-1)}{s^2(i)} \geq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
   \end{equation}
@@
 This is done by solving the following expression
-
 \begin{align}\label{eq:expFit}
@@
 \item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.
-
-\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
+Note also that the improvement in variance is proportional to the measurement time, i.e.
+\begin{equation}
+  \frac{\sampleStd{\trunc}}{\sampleStd{\LPM}} \approx \sqrt{\frac{\truncTime}{\Tm}}
+\end{equation}
+where $\Tm$ is the total measurement time.
+Equivalently, this means that for \glspl{FRF} estimated with a finer frequency resolution, are improved more by truncation than coarsely spaced \glspl{FRF}.
 
@@
 This bias depends on the time instant at which the truncation is performed, as discussed below.
+
+\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
+It is, however, advised to use the raw data instead of such smoothed \glspl{FRF} to estimate a parametric model such that no bias is introduced into the parametric estimate.
+In \chapref{sec:initvals}, however, it will be shown that smoothed \glspl{FRF} can lead to improved starting values.
 
@@
         \input{\thisDir/figs/expFitBoxAverager.tikz}
-         \caption{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
+         \caption[Exponential fit of boxcar averager]{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
          \label{fig:nparam:trunc:boxcar:impresp}

### 2016-04-29 ch06-concl/conclusions.tex
Some stuff, here and there

@@
   \subsection{Excitation Design}
-  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within an \gls{LTI} framework.
+  In this thesis, multisine signals are proposed to measure \gls{SISO} systems within a \gls{LTI} framework.
   Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
-  As such, they are more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
+  As such, they are a more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
   In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed (relative) uncertainty of the identified \gls{FRF} near the resonance peaks as caused by the measurement noise.
@@
   \subsection{Non-parametric Estimation}
+
+  \paragraph{Leakage reduction}
   Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
@@
 
+  \paragraph{Smoothing (noise reduction)}
   In addition, an approach has been developed that allows to reduce the variance of the estimated \gls{FRF} when it is captured in a long data record.
@@
 
+  \paragraph{Peak value estimation}
   It has also been illustrated that the use of such local models allows to extract the resonance peak and thereby the $\Hinf$ gain of a system.
@@
   \subsection{Construction of Initial Values}
-  In \chapref{sec:initvals} it was already illustrated that smoother can provide improved initial estimates of a system. 
-  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the the dimensionality in the parameter space.
+  In \chapref{sec:initvals} it was already illustrated that smoothers can provide improved initial estimates of a system. 
+  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the dimensionality in the parameter space.
   By no means were the  smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.
@@
 As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
-There are a few approaches that we think are worthwhile to investigate.
-On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
+There are a few approaches that are worthwhile to investigate.
+On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to an initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
 On the other hand, one could devise crude model order selection procedures, e.g.

### 2016-04-29 ch01-intro/introduction.tex
Some work on introduction

@@
 \section{System idenfication}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
+  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
+  \label{fig:intro:identification-cycle}
+\end{figure}
+
 \subsection{Linear System theory}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
-  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
-  \label{fig:intro:identification-cycle}
-\end{figure}
+For seasoned identification practitioners, methods that require little interaction are an opportunity for automation.
+This is especially important for complex systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, \ldots
+For such complex systems, building a model can be time-consuming and laborious if one has to supervise every step of the process.
+For more advanced users, user-friendly methods can hence allow to deal with more complex systems in a shorter amount of time such that the economical cost of building a model is reduced.
 
-\section{Publications}
+In this dissertation, the focus lies on \gls{LTI} systems.
+While this might seem as a very restrictive choice, this is one of the fundamental settings for system identification.
+In particular, \gls{LTI} systems are a first step for many people to build a system model.
+In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
+When such a linear model is not adequate, a more flexible model, e.g. a time-varying model, a nonlinear model or parameter-varying model needs to be constructed.
+However, many of those advanced modeling approaches build upon \gls{LTI} models.
+As such, improvements in estimating \gls{LTI} models also indirectly benefit more advanced models.
+
+\section{Outline and Publications}
    The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
@@
 
-The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished journal manuscript and the truncated \gls{LPM} presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished manuscript.
+ The so-called time-truncated \gls{LPM} that is presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
 \begin{itemize}
@@
 \end{itemize}
+In particular, this smoother enables one to reduce the effect of noise on an estimated \gls{FRF} using an automated approach.
 Relatedly, a preliminary study of the \gls{LPM} in the context of lightly-damped \gls{MIMO} systems has been presented at the (non-refereed) Benelux Meeting on Systems and Control:
@@
 
-The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and
+The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and the 2014 Leuven Conference on Noise and Vibration Engineering (ISMA) in Leuven:
 \begin{itemize}
@@
 \end{itemize}
-The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
+Experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
 \begin{itemize}

### 2016-04-30 ch01-intro/introduction.tex
Some intro work

@@
 
-\section{System idenfication}
+\section{System Idenfication}
+
+System identification is the scientific approach of converting observations of a system into mathematical models that describe the behavior of the system under test.
+In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
+Note that this is a simplified view, different authors
 
@@
   \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
-  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
+  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
   \label{fig:intro:identification-cycle}
@@
 While this might seem as a very restrictive choice, this is one of the fundamental settings for system identification.
-In particular, \gls{LTI} systems are a first step for many people to build a system model.
+In particular, \gls{LTI} systems are a first step to build a system model.
 In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
-When such a linear model is not adequate, a more flexible model, e.g. a time-varying model, a nonlinear model or parameter-varying model needs to be constructed.
-However, many of those advanced modeling approaches build upon \gls{LTI} models.
-As such, improvements in estimating \gls{LTI} models also indirectly benefit more advanced models.
+Also, most engineers and scientists have a good understanding of linear systems such that \gls{LTI} models align well with their prior knowledge and experience.
+Nevertheless, when a linear model is not adequate, a more flexible model needs to be constructed.
+Such a model could be more flexible, e.g. by relinquishing the time-invariance and/or its linearity.
+However, many of those advanced modeling approaches employ \gls{LTI} models as starting values or intermediate result in building the actual non-linear~\citep{Giri2010} or time-varying model~\citep{Lataire2012,Louarroudi2014}.
+As such, improvements in estimating \gls{LTI} models also indirectly improve more advanced methods.
+
+\subsection{Contributions}
+In this dissertation, we look into a few aspects of the identification workflow with the goal to make the whole process more user-friendly.
+
+\paragraph{How should a good experiment be designed?}
+Can we design a `good experiment' to identify a \gls{LTI} model?
+Particularly, this means a robust input signal needs to be constructed without relying on extensive prior knowledge of the system.
+Such a signal should cover a wide frequency band to excite all dynamics of the system during the experiment.
+However, the signal should ensure that systems in different frequency bands can be identified with a specified level of accuracy.
+
+\paragraph{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}
+
+\paragraph{Can we }
 

### 2016-04-30 ch01-intro/introduction.tex
CH01:

@@
 
-System identification is the scientific approach of converting observations of a system into mathematical models that describe the behavior of the system under test.
+System identification is the science---and often art---to deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
 In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
@@
 
-\paragraph{Can we }
+\paragraph{Can we avoid local minima by using smoothers?}
 

### 2016-04-30 ch01-intro/code/testLocalMinimum.m

@@ -1,0 +1,37 @@
+% Just a tiny script to show local minima
+%
+% In practice, one would not use this kind of algorithm for fitting those
+% complex exponentials (exactly due to these local minima)
+
+%% Settings
+dt     = 0.1;
+N      = 128;
+t      = (0:N-1)*dt;
+a0     = 0.01;
+b0     = pi;
+theta0 = a0 + b0*1j;
+thetaInit = a0 + 2.3j;
+model0 = model0;
+model  = @(theta,t) real(exp(-theta.*t));
+cost   = @(theta) sum(abs(model(theta,t) - model0(theta0,t)).^2)/N;
+
+%% 
+bRange = linspace(2,4,200);
+theta   = a0+bRange*1j;
+
+costVal = arrayfun(cost, theta);
+
+%% Optimization
+thetaHat = fminsearch(cost, thetaInit);
+
+%% model
+figure; hold on;
+plot(t, model(theta0, t),'-k');
+plot(t, model(thetaHat, t),'-r');
+
+%% cost
+figure; hold on;
+plot(bRange, costVal)
+plot(imag(theta0)  , cost(theta0),'ok')
+plot(imag(thetaHat), cost(thetaHat),'xr');
+plot(imag(thetaInit), cost(thetaInit),'.r');

### 2016-05-01 ch01-intro/introduction.tex
some work on intro

--- 2016-04-30 ch01-intro/introduction.tex
@@
 
-\section{System Idenfication}
+\section{System Identification}
 
-System identification is the scientific approach of converting observations of a system into mathematical models that describe the behavior of the system under test.
+System identification is the science that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
+Successfully identifying a system often hinges on a plethora of choices that are to be made by the user.
+As a result, system identification can also be seen as an art for which the practitioner needs to learn the tricks of the trade.
 In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
-Note that this is a simplified view, different authors
+These are the following steps:
+
+\paragraph{Experiment design}
+In the first step, an experiment is constructed to gain insight into the behavior of a system.
+For system identification, experiment design is a question of designing input signals that will be applied to the system under test.
+Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Goodwin2006GBO}.
+On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Narasimhan2011}.
+Typically, the design is very sensitive to the prior knowledge of the system.
+This is necessary to focus all the energy in the signal towards exciting the system dynamics as to reduce the uncertainty in the model.
+However, when the prior knowledge is incomplete, uncertain or even incorrect, optimal signals can lead to very poor models as they might not excite other dynamics.
+An alternative approach is to incorporate the uncertainty of the prior knowledge into the signal design.
+This leads to so-called robust optimal experiment design~\citep{Rojas2012,Goodwin2006} that construct signals that optimize the worst-case model uncertainty.
+Paradoxically, this means that for robust optimal designs, more prior knowledge, rather than less is required.
+
+The design of good experiments hence already forces the user to make a choice that can have far-reaching consequences for the model quality.
+
+\paragraph{Select a model structure}
+Once an experiment has been performed, the obtained input-output data is to be processed.
+In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and/or complexity based on both his prior knowledge and on the data.
+A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
+One such tool is the frequency response function.
+For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \ldots
+This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
+However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
+
+\paragraph{Estimate the model}
+Once the model structure has been chosen, its parameters are to be estimated.
+This is done by formulating an optimization problem which serves to minimize a particular cost function.
+The cost function is in essence a measure of the differences between the measured data and the model evaluated for particular parameter values.
+By minimizing the cost function, the optimization procedure yields parameter values that try to minimize the misfit between the data and the model.
+Unfortunately, for many identification settings, these optimization problems are non-convex~\citep{Boyd2004}.
+This means that initial values need to be available to start the optimization process.
+Moreover, for poor starting values, optimization algorithms may get stuck in local minima of the cost function.
+Consequently, without reasonable starting values, the `optimized' model may also be of poor quality.
+
+\paragraph{Validate the model}
+Finally, the estimated model is validated.
+Essentially, one checks whether the obtained model meets the predefined requirements, e.g. with respect to allowable uncertainty, compexity, \ldots
+This can happen in a few different ways.
+On the one hand, in-sample measures such as statistical tests on the value of the cost function, correlation tests on the residuals, \ldots allow to verify that the model performs well on the measured dataset.
+Such approaches help to detect underfitting, where the model is not flexible enough to describe the measurements.
+On the other hand, the ultimate test is to validate the model against new measurements that have not been used during the estimation.
+This prevents overfitting of the model, where the model not only captures the behavior of the system but also describes the particular realization of the noise in the measurements.
+The latter leads to models that are overly tuned to the measurements such that their results cannot be replicated for new measurements.
+In case the model is not validated, this provides the user with new knowledge: that particular model is not good enough and at least one of the previous steps (or the prior knowledge) has to be altered.
 
@@
 
-\subsection{Linear System theory}
 \subsection{System Identification Approaches}
+In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
+\subsubsection{White Box, Black Box or Grey Box}
 
-\subsubsection{White Box, Black Box or Grey Box}
 \subsubsection{Time or Frequency Domain}
 \subsubsection{Linear or nonlinear?}
-\subsubsection{Time invariant or non?}
+\subsubsection{Time invariant or not?}
+\subsubsection{Parametric or non-parametric}
 
@@
 \paragraph{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}
+Developing a full parametric model for complicated systems requires considerable effort.
+Instead, could we leverage non-parametric or locally parametric approaches to obtain insight in the behavior of the system?
+In particular, can local modeling methods be used to characterize the resonances of a system, or even work around the typical frequency resolution limitations of a discrete frequency grid?
 
-\paragraph{Can we }
+\paragraph{Can we avoid local minima by using smoothers?}
+When a parametric model is required, this often involves solving a nonlinear optimization problem.
+Such optimization problems require good initial parameter estimates to allow iterative methods to converge to a good local optimum, or, preferably even the global optimum.
+Can non-parametric smoothers be used to help avoid such local optima?
 

### 2016-05-01 ch01-intro/code/testLocalMinimum.m

@@ -11,8 +11,8 @@ a0     = 0.01;
 b0     = pi;
 theta0 = a0 + b0*1j;
 thetaInit = a0 + 2.3j;
-model0 = model0;
 model  = @(theta,t) real(exp(-theta.*t));
+model0 = model;
 cost   = @(theta) sum(abs(model(theta,t) - model0(theta0,t)).^2)/N;
 
 %% 

### 2016-05-01 ch01-intro/introduction.tex
Ch01: black vs white

@@
 In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
-These are the following steps:
+For the technical details, we refer to the many textbooks on system identification~\citep{Soderstrom1989,Ljung1999,Pintelon2012}.
+Here, we give the high-level overview of the different steps and choice.
 
@@
 Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Goodwin2006GBO}.
-On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Narasimhan2011}.
+On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Gevers2011ExpDesign}.
 Typically, the design is very sensitive to the prior knowledge of the system.
@@
 In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
-\subsubsection{White Box, Black Box or Grey Box}
+We cover some typical traits of different methods and describe why a particular approach is favored in this thesis.
+
+\subsubsection{White Box, Black Box or Grey Box?}
+Modeling can be divided into two diametrical groups depending on the starting point of modeling~\citep{Ljung2010}.
+One the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
+The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \ldots
+This is the typical kind of modeling practices in school.
+Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
+In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.
+
+On the other hand, the diametrically opposed approach is called \term{`black box'} modeling.
+Here, the model structure is chosen such that a wide variety of phenomena can be described.
+Regardless of the nature of the underlying system, be it mechanical, chemical, electrical, structural, \ldots, most dynamic phenomena can be described using differential equations (or difference equations).
+In particular, for black-box models, the structure of the model is chosen such that the data is well-approximated.
+The downside of this is that giving physical interpretations of the model is not always possible, but for many applications (e.g. controller design) that is not the main goal of the model.
+
+Obviously, in practice nothing is ever as black and white and neither is modeling.
+In many cases, one can or even has to incorporate knowledge about the physics of the system in the modeling process.
+In particular when one has black box models where some parameters are related to physical phenomena, the resulting model is called \term{`gray box'}.
+
+In this dissertation, we use mainly black box models (or very dark gray ones) as those are independent from the actual application.
+Hence, the proposed techniques should be applicable for different areas of engineering: electrochemical, electronics, mechatronics, structural engineering, \ldots
+
+\subsubsection{Parametric or non-parametric}
+
+\subsubsection{Linear or nonlinear?}
+\subsubsection{Time invariant or not?}
 
 \subsubsection{Time or Frequency Domain}
-\subsubsection{Linear or nonlinear?}
-\subsubsection{Time invariant or not?}
-\subsubsection{Parametric or non-parametric}
 
@@
 In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
-User-friendly should be understood as having a good user experience for two groups of users:
+The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
+In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
 \begin{itemize}

### 2016-05-01 ch01-intro/introduction.tex
Ch01 finished?

@@
 \section{System Identification}
-
 System identification is the science that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
@@
 For the technical details, we refer to the many textbooks on system identification~\citep{Soderstrom1989,Ljung1999,Pintelon2012}.
-Here, we give the high-level overview of the different steps and choice.
+Here, we give the high-level overview of the different steps.
 
@@
 
-\subsection{System Identification Approaches}
+\subsection{System Identification Choices}
 In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
@@
 
-\subsubsection{Parametric or non-parametric}
+\subsubsection{Linear or nonlinear?}
+A preliminary choice that is often made, is to first try linear models.
+Linear models guarantee that superposition of input-signals results in the superposition of the corresponding output signals.
+Specifically, if a linear system maps the output $u_i$ to the output signal $y_i$ (for any value of $i$), then an input $\sum_i u_i$ is mapped to the output $\sum_i y_i$.
+As such, the output of a system is (linearly) proportional to its input.
+This is a very powerful property that allows to simplify reasoning about such systems.
+The implications of this powerful property can be verified textbooks covering signals and systems~\citep{Oppenheim1996,Mandal2007,Kailath1980}.
+For non-linear systems, the superposition property is no longer guaranteed.
 
-\subsubsection{Linear or nonlinear?}
-\subsubsection{Time invariant or not?}
+In practice, all systems behave in a nonlinear way to some degree.
+Just imagine riding a bike: when you are cruising at a constant speed, pedaling at a faster pace will make the bike go proportionally faster.
+However, once you come to a full stop at a traffic light and want to start riding again, you need to apply a disproportionate amount of force to put the bike to motion again (due to friction).
 
-\subsubsection{Time or Frequency Domain}
+In this dissertation, we assume the system behaves in a dominantly linear way.
+No specific care is taken of nonlinearities.
+However, even with dominantly linear models~\citep{Schoukens2004}, nonlinear systems can often be well-described.
+Nevertheless, building a model to characterize the nonlinearities in a structured way requires a lot more effort~\citep{Ljung2010,Giri2010,Sjoberg1995}.
+However, e.g. for block-oriented nonlinear models~\citep{Giri2010}, some of the intermediate steps require identification of linear blocks.
 

### 2016-05-02 ch06-concl/conclusions.tex
Conclusions: comments from Johan

@@
   Particularly, the proposed multisine signals employ a quasi-logarithmic frequency grid and a power spectrum in $1/f$ akin to pink noise to ensure a good quality of the \gls{FRF} over the whole excited frequency band.
-  As such, they are a more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation with the same total signal power and duration.
-  In this thesis it has been proven that when the user has prior knowledge about the expected minimal damping $\damping[\min]$ of the poles present in the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed (relative) uncertainty of the identified \gls{FRF} near the resonance peaks as caused by the measurement noise.
+  As such, for a constant total signal power and duration, they are a more robust excitation signal than e.g. typical general-use signals such as linear grid multisines or white noise excitation.
+  In this thesis it has been proven that when the user knows the minimal damping $\damping[\min]$ of the poles of the system, this sets the required logarithmic frequency grid spacing to attain a guaranteed (relative) uncertainty of the identified \gls{FRF} near the resonance peaks.
   Concretely, the grid spacing $\alpha \isdef \frac{f_{k+1}}{f_k}$ of the (quasi-)logarithmic grid with frequency resolution $\Delta f$ should conform to
@@
   This method works by examining the estimated impulse response, i.e.
-the inverse \gls{DFT} of the \gls{FRF}, and estimating a truncation time $\truncTime$ beyond which the impulse response is overwhelmed by the noise.
-  By truncating past this point and transforming the result back into the frequency domain, an \gls{FRF} is obtained that has a reduced \gls{RMS} error by reducing the variance due to the noise.
+the inverse \gls{DFT} of the \gls{FRF}, and estimating a truncation time $\truncTime$ beyond which the impulse response measurement is dominated by the noise.
+  By truncating past this point, and transforming the result back into the frequency domain, an \gls{FRF} is obtained that has a reduced \gls{RMS} error by reducing the variance due to the noise.
   Two complementary approaches to determine $\truncTime$ have been developed.
@@
   Starting from the last segment, it is tested statistically whether the preceding segment is significantly different from the noise, such that $\truncTime$ is estimated.
+  For physical systems that exhibit an exponentially decaying impulse response, the exponential fitting method is to be preferred.
 
@@
   In that setting, the \gls{LPM} is not reliable due to its limited model flexibility.
-  The \gls{LRM}, on the other hand, has been shown to be yield estimates of the $\Hinf$ gain that improved greatly compared to pure \gls{FRF} measurements.
+  The \gls{LRM}, on the other hand, has been shown to yield estimates of the $\Hinf$ gain that improved greatly compared to pure \gls{FRF} measurements.
   For systems that consist of complex dynamic behavior, this allows one to extract reasonable peak values without the hassle of building a global parametric model.
@@
   However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
-  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
-  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
+  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers; in particular when many data points are only a poor \gls{SNR} is attained.
+  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM}, and the \gls{RFIR}.
   It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
   These smoothers allow one to obtain good models from noisier data than what existing techniques.
-  The improvement of the initial values has been verified both on simulations, measurements and a simulation stress test consisting of different filters.
+  The improvement of the initial values has been verified both on simulations, measurements, and a simulation stress test consisting of different filters.
   While overall the \gls{RFIR} provides the best starting values from the different smoothers, combining multiple initial values remains a very valuable approach to make a system identification toolbox robust for the measurement data.
@@
     \end{equation}
-    but these have proven more difficult to estimate numerically and hence unreliable.
+    but these have proven more difficult to estimate numerically and hence unreliable~\citep[Section 2.4]{Pintelon2006BJ1}.
     A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
@@
     Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep{vanderMaas2015CDC}.
-    Given these successes of \gls{LRM} to estimate a preliminary model of both parameter-varying and time-varying models in more complicated experimental settings.
+    Given the successful application of \gls{LRM} in a frozen parameter-varying system, it seems worthwhile to investigate if the\gls{LRM} can be extended to work in more challenging experimental settings.
     E.g. it could prove useful to extend the \gls{LRM} towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.
 
-    Another application where the \gls{LPM} is more developed is the handling of missing data~\citep{Ugryumova2015}.
+    Another application where the \gls{LPM} is developed further, is the handling of missing data~\citep{Ugryumova2015}.
     In particular, the frequency domain relationship between the input $U$ and output $Y$ is augmented by a term $M_Y$ that accounts for the missing output data samples:
@@
     This could be done from a theoretical point of view to find correspondences between different approaches (e.g.
-\citep{Hagg2012} reduces to \gls{ETFE} as does the \gls{LRM} for specific settings) and from a qualitative point of view to find the best operating regions of each approach.
+both \gls{TRIMM}~\citep{Hagg2012} and \gls{LRM} are generalizations of the \gls{ETFE} for specific settings).
+    A comparison from a qualitative point of view would be of more practical use, as this would allow to find the best operating regions of each approach.
     Eventually, this could even lead to hybrid methods that either select the best method for a specific setting or use results from different methods to overcome weaknesses of individual methods such as high computational complexity, high bias, high variance, \ldots
-    Especially in the view of \gls{LRM} as a form of local regression~\citep{Loader1999}, it could be worthwhile to also investigate suitable (frequency-domain) kernels instead of the uniform kernel that is implicitly used in the \gls{LRM}.
+    When regarding the \gls{LRM} as a specific form of local regression~\citep{Loader1999}, this allows to reuse the ideas from that community.
+    In particular, local regression often uses a so-called kernel that weights the least-squares fit (where the \gls{LRM} implicitly uses a uniform kernel).
+    In view of \gls{FRF} estimation, a worthwhile endeavor could be to study the influence of these kernels on both the \gls{FRF} estimate and the estimated noise level.
+    Moreover, this could even lead to the design of new kernels.
 
@@
   In \chapref{sec:initvals} it was already illustrated that smoothers can provide improved initial estimates of a system. 
-  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the dimensionality in the parameter space.
+  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption, and on the other hand by the reduction in the dimensionality in the parameter space.
   By no means were the  smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.

### 2016-05-02 ch03-lrm/nonparametric.tex
Most comments of Johan on CH03

@@
 \end{itemize}
-The main term of interest, however, is the transfer function $\true{G}$ and a secondary concern is estimating the noise variance $\sigma_{V}$.
+The main term of interest, however, is the transfer function $\true{G}$ and the noise variance $\sigma^2_{V}$.
 
@@
 As such, we use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, \order{B}, 0, \order{C}}$.
+In the remainder of this text, we refer to \gls{LRM} as a group of methods which have $\order{A} \neq 0$ to make the distinction with \gls{LPM} more obvious.
 
@@
      \approx 
-        \PartialDerivative{\LocalModel{G}(\theta, \dw{0}{k})}
+        \PartialDerivative{\LocalModel{G}(\dw{0}{k},\theta)}
                                           {\theta} 
@@
 \begin{align}
-    \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta} 
+    \PartialDerivative{\LocalModel{G}(\dW, \theta)}{\theta} 
      &=
      \begin{bmatrix}
-       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_A} &
-       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_B} &
-       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_C} 
-     \end{bmatrix}
-     \\
-     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_A} 
+       \PartialDerivative{\LocalModel{G}(\dW,\theta)}{\theta_A} &
+       \PartialDerivative{\LocalModel{G}(\dW,\theta)}{\theta_B} &
+       \PartialDerivative{\LocalModel{G}(\dW,\theta)}{\theta_C} 
+     \end{bmatrix}
+     \\
+     \PartialDerivative{\LocalModel{G}(\dW, \theta)}{\theta_A} 
      &=
-     - \frac{\LocalModel{B}(\theta, r)}{\LocalModel{A}^2(\theta, r)}
+     - \frac{\LocalModel{B}(\dW, \theta)}{\LocalModel{A}^2(\dW, \theta)}
      \begin{bmatrix}
@@
      \\
-     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_B} 
+     \PartialDerivative{\LocalModel{G}(\dW, \theta)}{\theta_B} 
      &=
-     \frac{1}{\LocalModel{A}(\theta, \dW)}
+     \frac{1}{\LocalModel{A}(\dW, \theta)}
      \begin{bmatrix}
@@
      \\
-     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_C} 
+     \PartialDerivative{\LocalModel{G}(\dW, \theta)}{\theta_C} 
      &=
@@
 \begin{equation}
-  \Delta \LocalModel{G}(\theta,\dW)
+  \Delta \LocalModel{G}(\dW,\theta)
   \approx
-  \frac{\LocalModel{G}(\theta, \dW)}
-           {\LocalModel{A}(\theta, \dW)}
+  \frac{\LocalModel{G}(\dW, \theta)}
+           {\LocalModel{A}(\dW, \theta)}
   \begin{bmatrix}
@@
 Equivalently, the relative bias of the \gls{FRF} can be written as
-\begin{equation}
-\frac{\Delta \LocalModel{G}(\theta,\dW)}{\LocalModel{G}(\theta,\dW)}
-\approx
-\LocalModel{A}(\theta,\dW)^{-1}
-\begin{bmatrix}
-    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
-  \end{bmatrix}
-  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}
-  \begin{bmatrix}
-  \Delta\theta_A\\
-  0\\
-  0\\
-  \end{bmatrix}
-  \text{.}
-\end{equation}
+\begin{align}
+\frac{\Delta \LocalModel{G}(\dw{\omega}{}, \theta)}{\LocalModel{G}(\dw{\omega}{}, \theta)}
+&\approx
+\LocalModel{A}(\dw{\omega}{}, \theta)^{-1}
+\begin{bmatrix}
+    \dw{\omega}{}^1 & \deemph{\cdots} & \dw{\omega}{}^{\order{A}}
+  \end{bmatrix}
+  \evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}
+  \PartialDerivative{\ELSCost[n]{\true\theta}}{\theta_A}^{\TT}
+  \\
+  &=
+  \frac{\sigma_V^2}{\nWind}
+\begin{bmatrix}
+    \dw{\omega}{}^1 & \deemph{\cdots} & \dw{\omega}{}^{\order{A}}
+  \end{bmatrix}
+  \evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}
+  \begin{bmatrix}
+     \Sum_{\dW} \dW^1 
+     \frac{\LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}})}
+               {\LocalModel{A}(\dw{\omega}{}, \theta)}\\
+  \deemph{\vdots}\\
+     \Sum_{\dW} \dW^{\order{A}} 
+     \frac{\LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}})}
+               {\LocalModel{A}(\dw{\omega}{}, \theta)}\\
+  \end{bmatrix}
+\end{align}
+where $\evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}$ denotes the upper left $\order{A}\times\order{A}$ subblock of $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}$ which pertains to the parameters of $\LocalModel{A}$.
+From the leading factor, it can be seen that the bias on the \gls{FRF} is $\bigO{\sigma_V^2}$.
+Consequently, one can expect that the bias is inherently linked to the \gls{SNR} of the output signal in the frequency domain.
 
@@
 The \gls{FRF} is estimated using the local modeling approaches indicated in \tabref{tbl:nparam:methods}.
+This table also indicate $\Delta\SNR$ which indicates the expected gain in \gls{SNR} if the error is mainly determined by the variance.
+Concretely,
+\begin{equation}
+  \Delta\SNR \isdef \sqrt{\frac{\nth}{\nWind}}
+  \label{eq:nparam:deltaSNR}
+\end{equation}
+accounts for the smoothing action of local modeling.
 
@@
 For the \gls{LRM} and \gls{LRIC}, the bias is always much smaller than the variance.
-In contrast to \gls{LPM}, the \gls{LPM} already reaches a constant variance level when $\nBW > 10$.
+In contrast to \gls{LPM}, the \gls{LRM} already reaches a constant variance level when $\nBW > 10$.
 It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
 It is hence not advantageous to use the \gls{LRIC} as-is.
-For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches
-\begin{equation}
-  \lim_{\nBW \to \infty} \RMSE \approx \frac{\SNR}{\Delta \SNR}
-\end{equation}
-where
-\begin{equation}
-  \Delta\SNR \isdef \sqrt{\frac{\nth}{\nWind}}
-  \label{eq:nparam:deltaSNR}
-\end{equation}
-accounts for the smoothing action of local modeling (see \tabref{tbl:nparam:methods} for numerical values of $\Delta \SNR$).
+For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches the noise floor minus $\Delta \SNR$.
 
@@
 Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
-However
+However, its bias for small datasets is much lower than for the other methods.
 At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
@@
 
-\TODO{introduction}
+\TODO{introduction, probleem, oplossingen die besproken worden}
 
@@
  - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
- + 2 \nth\\
+ + 2 \nth
+\label{eq:nparam:AIC}\\
 L_{\mathrm{\AICc}} &= 
@@
 +   \frac{2 \nth\nWind}{\nWind - \nth - 1}
+\label{eq:nparam:AICc}
 \end{align}
@@
 \begin{remark}
+From a theoretical point of view, equations \eqref{eq:nparam:AIC} and \eqref{eq:nparam:AICc}, require full knowledge of the likelihood function.
+This means specifically that the noise variance $\sigma^{2}_{V}$ needs to be known beforehand.
+When the variance is unknown, however, it is more robust to incorporate the \gls{AIC} as a penalty factor on the cost function as indicated in \citet[Section 7.4]{Ljung1999} and \citet[Section  11.3 and 19.7]{Pintelon2012}.
+\end{remark}
+
+\begin{remark}
 It should be noted that due to $\loglikelihood{\LocalModel{M} | \LocalVector{Z}}$ , the value of $L_{\mathrm{AIC(c)}}(\LocalModel{M},\LocalVector{Z})$ is inherently coupled with the particular dataset $\LocalVector{Z}$.
@@
 In particular, when there is a large difference between the level of the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.
+
+\subsection{Results}
+
+%TODO: discussie: 1 globale modelorder of verschillende
+% voor parametrische schatting: vensterbreedte constant houden, DOF constant houden over alle geselecteerde modellen
+% voor niet-parametrisch: orde kan per frequentielijn verschillen, geeft betere smoothing \citep{Thummala2012LPMBW,Fan1996}
 
@@
 
-\subsection{LPM with impulse response truncation}
+\section{LPM with impulse response truncation}
 \input{\thisDir/truncation.tex}
@@
 Hence, expressions for the bias of the \gls{LRM} were derived.
-For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LRM}.
+%TODO: tom: "inherently biased": verrgaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
+For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.
 For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.

### 2016-05-02 ch03-lrm/truncation.tex
Most comments of Johan on CH03

@@
 It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.
+It should be noted, however, that such smoothing is merely of importance when inspecting the \gls{FRF} visually.
+In particular, a slight bias is incurred when smoothing the \gls{FRF}.
+If one is to fit a parametric model to the smoothed \gls{FRF}, one essentially ends up with a biased model (which is often undesirable).
 
@@
 
-\subsection*{Theory on the LPM and Windowing}
-\label{sec:nparam:trunc:theoryLPMandWindowing}
+% \subsection*{Theory on the LPM and Windowing}
+% \label{sec:nparam:trunc:theoryLPMandWindowing}
 
-Details of the theory pertaining to this section may be found in \citet{Schoukens2009LPM}, basic aspects of which are presented below.
+% Details of the theory pertaining to this section may be found in \citet{Schoukens2009LPM}, basic aspects of which are presented below.
 
-\subsubsection{Spectral Nonparametric Model and Assumptions}
+% \subsubsection{Spectral Nonparametric Model and Assumptions}
 
-Using convolution, the noiseless output signal in \figref{fig:nparam:blockH0} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
-\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
-Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
-\end{equation}
-where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
-In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}
+% Using convolution, the noiseless output signal in \figref{fig:nparam:blockH0} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
+% As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
+% \begin{equation}\label{eq:nparam:trunc:LPM:leakage}
+% Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
+% \end{equation}
+% where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
+% In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}
 
-\begin{equation}\label{eq:defDFT}
-X(\omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-\end{equation}
+% \begin{equation}\label{eq:defDFT}
+% X(\omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
+% \end{equation}
 
-The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:blockH0}):
-\begin{assumption}
-The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-\end{assumption}
+% The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:blockH0}):
+% \begin{assumption}
+% The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
+% \end{assumption}
 
-\begin{assumption}
-The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\citep{Schoukens2009LPM}.
-\end{assumption}
+% \begin{assumption}
+% The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\citep{Schoukens2009LPM}.
+% \end{assumption}
 
-In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
+% In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
 
-\begin{assumption}
-The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
-\end{assumption}
+% \begin{assumption}
+% The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
+% The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
+% \end{assumption}
 
-\subsubsection{The Hanning Window and the \glsentrytext{LPM}}
-\label{sec:nparam:trunc:LPMFRFest}
-\paragraph{Windowing}
-The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
-In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
-Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
+% \subsubsection{The Hanning Window and the \glsentrytext{LPM}}
+% \label{sec:nparam:trunc:LPMFRFest}
+% \paragraph{Windowing}
+% The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
+% In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
+% Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
 
-The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}. 
-As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\bigO{{N}^{-1}}$, for Hanning windowing, to $\bigO{{N}^{-3}}$ or better, for the \gls{LPM}.
+% The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}. 
+% As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\bigO{{N}^{-1}}$, for Hanning windowing, to $\bigO{{N}^{-3}}$ or better, for the \gls{LPM}.
 
@@
    \input{\thisDir/figs/LPMfig.tikz}
-   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
+   \caption[Illustration of local modeling.]{Illustration of local modeling. Top figures: input spectrum (left) and output spectrum (right). 
    A small band is selected (gray area), in which $\hat G_{\LPM}(\omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
 Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained.
-This procedure is repeated for all frequencies $\omega_k$.}
+This procedure is repeated for all frequencies $\omega_k$.
+\disclaimer{Figure based on \citep[Fig.~2]{Lumori2014TIM}.}}
    \label{LPM_Schematic_EG}
@@
 The impulse response $g(t)$ decays exponentially over time, i.e. 
-$\exists A \in \PositiveRealNumbers, \exists a \in \NegativeRealNumbers \without \Set{0}, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
+\[
+  \exists A \in \PositiveRealNumbers, 
+  \exists a > 0 ,
+  \exists t_0 > 0,
+  \forall t > t_0: 
+     \abs{g(t)} \leq A \exp(- a t) \text{.}
+\]
 \end{assumption}
@@
 To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_{\LPM}$ is split into smaller segments.
-One can then gradually determine whether these segments are noise or the actual impulse response.
+One can then gradually determine if in each of these segments, the observed impulse response is dominated by the noise.
 

### 2016-05-02 ch03-lrm/nonparametric.tex
Small stuff in CH03

@@
 
-Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received renewed interest from the community.
+Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have received renewed interest from the community over the last decade.
 One of the reasons for this is that non-parametric techniques typically require less assumptions and knowledge of the system than building parametric models.
-As a consequence, non-parametric methods are often more robust to wrong assumptions than fully parametric methods.
+As a consequence, non-parametric methods are often more robust than fully parametric methods.
 Besides, \glspl{FRF} have been shown to provide a quick insight into the basic dynamic properties of \gls{LTI} systems.
-This capability is very useful for system design, controller design, model validation and model selection for parametric models~\citep{Pintelon2012}.
+This capability is very useful for system design, manual controller tuning, model validation and model selection for parametric models~\citep{Pintelon2012}.
 
 The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
-However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can prove difficult due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
+However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can be challenging due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
 \gls{FRF} measurement techniques are discussed, for instance, in
@@
 \begin{equation}
-  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
+  \LocalVector{Y}_k  = {\LocalVector{G}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
 \text{,}
@@
   \end{bmatrix}
-  \evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}
+  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}
   \PartialDerivative{\ELSCost[n]{\true\theta}}{\theta_A}^{\TT}
@@
   \end{bmatrix}
-  \evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}
+  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}
   \begin{bmatrix}
@@
 \end{align}
-where $\evaluate{\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}}{A}$ denotes the upper left $\order{A}\times\order{A}$ subblock of $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}$ which pertains to the parameters of $\LocalModel{A}$.
+where $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}$ denotes the upper left $\order{A}\times\order{A}$ subblock of $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}$ which pertains to the parameters of $\LocalModel{A}$.
 From the leading factor, it can be seen that the bias on the \gls{FRF} is $\bigO{\sigma_V^2}$.

### 2016-05-02 ch03-lrm/truncation.tex
Small stuff in CH03

@@
 \begin{align}\label{eq:impRespiDFT}
-\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
+\hat g_{{\LPM}\setminus \mathrm{DC}}(t) 
+&= 
+\frac{1}{\sqrt{N}}
+\sum_{k=1}^{N-1}
+\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
 \end{align}
@@
 \end{enumerate}
-This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
+This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following equations:
 \begin{subequations}
@@
 \end{subequations}
-where $e(t)$ is a white noise sequence, such that the SNR of the output signal is $78.2\unit{dB}$.
+where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $78.2\unit{dB}$.
 The figure shows segments of the estimated impulse response.

### 2016-05-02 ch03-lrm/nonparametric.tex
Move LPM illustration

@@
 Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
-To alleviate the notations, the subscript $k$ is omitted unless
+To alleviate the notations, the subscript $k$ is omitted whenever this does not cause ambiguity.
 
@@
 \end{equation}
+In \figref{fig:nparam:illustration}, the local window $\LocalWindow[k]$, the local input-output spectra ($\LocalVector[k]{U}$ and $\LocalVector[k]{U}$) are illustrated.
+
+\begin{figure}[htb] %  figure placement: here, top, bottom, or page
+   \centering
+   \setlength{\figurewidth}{0.8\columnwidth}
+   \setlength{\figureheight}{0.68\figurewidth}
+   \input{\thisDir/figs/LPMfig.tikz}
+   \caption[Illustration of local modeling.]{Illustration of local modeling. Top figures: input spectrum (left) and output spectrum (right). 
+   A small frequency window $\LocalWindow[k]$ is selected, in which the local model $\LocalModel[k]{G}$ is estimated.
+Its central value $\hat{G}(\omega_k)$ is an estimate of the \gls{FRF}.
+This procedure is repeated for all frequencies $\omega_k$.
+\disclaimer{Figure based on \citep[Fig.~2]{Lumori2014TIM}.}}
+   \label{fig:nparam:illustration}
+\end{figure}
 
@@
 However, these preliminary experiments did not yield estimates that were numerically reliable.
+This is in correspondence with the remark from \citet{Pintelon2006BJ1}.
 \end{remark}
@@
 \label{sec:nparam:LRM}
-The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
+The \gls{LRM} as first introduced by \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
 I.e. the \gls{LRM} procedure tries to minimize the equation error in

### 2016-05-02 ch03-lrm/truncation.tex
Move LPM illustration

@@
 % \end{equation}
-
-The estimation of $\hat{G}_{\LPM}(\omega_k)$ at a single frequency $\omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
-\begin{figure}[htb] %  figure placement: here, top, bottom, or page
-   \centering
-   \setlength{\figurewidth}{0.8\columnwidth}
-   \setlength{\figureheight}{0.68\figurewidth}
-   \input{\thisDir/figs/LPMfig.tikz}
-   \caption[Illustration of local modeling.]{Illustration of local modeling. Top figures: input spectrum (left) and output spectrum (right). 
-   A small band is selected (gray area), in which $\hat G_{\LPM}(\omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial.
-Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained.
-This procedure is repeated for all frequencies $\omega_k$.
-\disclaimer{Figure based on \citep[Fig.~2]{Lumori2014TIM}.}}
-   \label{LPM_Schematic_EG}
-\end{figure}
-This procedure is repeated at each central frequency $\omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e.
-the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries).
-This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\omega_k)$.
 

### 2016-05-03 ch05-initvals/initial-values.tex
Fix some references
Clean up CH05 figure directory

@@
 \centering
-\input{\thisDir/fig/oesetup.tikz}
+\input{\thisDir/figs/oesetup.tikz}
 \caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
+  \includegraphics[width=\columnwidth]{\thisDir/figs/flowgraph}
   \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convex optimization problem.
@@
 \item \emph{Local polynomial method (LPM) with truncation}
-\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nparam:trunc} in more detail. The pertinent details are repeated here to aid readability.}
+\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nonparametric:truncation} in more detail. The pertinent details are repeated here to aid readability.}
 A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
@@
   \setlength{\figureheight}{0.6\figurewidth}
-  \input{\thisDir/fig/exampleSystems.tikz}
+  \input{\thisDir/figs/exampleSystems.tikz}
  % \caption{Results of an example of Monte Carlo simulation.}
@@
   \setlength{\figureheight}{0.6\figurewidth}
-  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
+  \input{\thisDir/figs/MC-SNR1.1dB-NBW36-Q6dB.tikz}
  \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/successRates.tikz}
+  \input{\thisDir/figs/successRates.tikz}
  \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
+  \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
  \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{\thisDir/fig/measurement.pdf}
+  \includegraphics[width=0.6\columnwidth]{\thisDir/figs/measurement.pdf}
   \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/bode-bk1613.tikz}
+  \input{\thisDir/figs/bode-bk1613.tikz}
   \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/elvis-spectra.tikz}
+  \input{\thisDir/figs/elvis-spectra.tikz}
   \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
@@
   \setlength{\figurewidth}{0.75\columnwidth}
-  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
+  \input{\thisDir/figs/CostFunctionsMLE-measurement.tikz}
   \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
@@
   \setlength{\figurewidth}{0.75\columnwidth}
-  \input{\thisDir/fig/meas-validation.tikz}
+  \input{\thisDir/figs/meas-validation.tikz}
   \caption[Validation cost of the different measurements.]{Validation of the measured models. 
@@
   \setlength{\figureheight}{0.68\figurewidth}
-  \input{\thisDir/fig/overview-cost-val.tikz}
+  \input{\thisDir/figs/overview-cost-val.tikz}
   \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
@@
   \setlength{\figureheight}{0.60\figurewidth}
-  \input{\thisDir/fig/special-histogram.tikz}
+  \input{\thisDir/figs/special-histogram.tikz}
   \caption[Performance degradation/enhancement for selecting the second best model.]{
@@
   \centering
-  \input{\thisDir/fig/bodeplots.tikz}
+  \input{\thisDir/figs/bodeplots.tikz}
   \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
@@
   \centering
-  \input{\thisDir/fig/distances.tikz}
+  \input{\thisDir/figs/distances.tikz}
   \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).

### 2016-05-03 ch03-lrm/nonparametric.tex
Structure in LPMtrunc

@@
 \subsection{The Local Polynomial Method}
+\label{sec:nparam:LPM}
 The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:conclusion}
 In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
-Since the \gls{LRM} is an inherently biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
+Since the \gls{LRM} is a biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
 Hence, expressions for the bias of the \gls{LRM} were derived.
-%TODO: tom: "inherently biased": verrgaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
+%TODO: tom: "inherently biased": verregaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
 For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.

### 2016-05-03 ch03-lrm/truncation.tex
Structure in LPMtrunc

@@
 The rest of the section is structured as follows. 
-\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
 \secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
@@
 
-% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
+% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \latin{viz}:
 % \begin{equation}\label{lpm1spectra}
@@
 
-% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
+% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \latin{viz}:
 % \begin{align}\label{lpmGTaylorS}
@@
 
-% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
+% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \latin{viz}:
 % \begin{equation}\label{lpmGTMatrix}
@@
 % where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
+% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \latin{viz}:
 % \begin{align}\label{eq:LSsolutionLPM}
@@
 % \end{equation}
-% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
+% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \latin{viz}:
 % \begin{equation}
@@
 
-\subsubsection{Smoothing the \gls{FRF} estimate}
+\subsection{Smoothing the \gls{FRF} estimate}
 \label{sec:nparam:trunc:smoothingFRFestimate}
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
-After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
 \begin{enumerate}
@@
 \item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-
 This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
@@
 
-\subsubsection{Obtaining the Impulse Response Function}
+\subsection{Obtaining the Impulse Response Function}
 
-The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
+The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF}, \latin{viz}:
 \begin{align}\label{eq:impRespiDFT}
@@
 
-\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
+\subsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
 The correct mean value of the impulse response accounts for (i.e.
@@
 \item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \emph{viz}:
+}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \latin{viz}:
 \begin{align}
@@
 \end{enumerate}
+
+\subsection{Determining the Truncation Time}
+In this section, two methods will be discussed to determine the truncation time, i.e. the time beyond which the measured impulse response cannot be separated from the noise level.
+Specifically, the first method uses an $F$-test to distinguish between signal and noise.
+The second method fits an exponential through a well-chosen subset of the data to obtain $\truncTime$.
 
@@
   This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
-  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
+  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \latin{viz}:
   \begin{equation}
@@
 
-\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
+\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \latin{viz}:
 \begin{align}
@@
 \item
-Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
+Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \latin{viz}:
 \begin{align}\label{eq:truncTimeExpFit}
@@
 
-\subsubsection{Simulation Results}
+\subsection{Simulation Results}
 \label{sec:nparam:trunc:simResults}
@@
 
-\subsubsection{Conclusion}
+\subsection{Conclusion}
 \label{sec:nparam:trunc:conclusion}

### 2016-05-03 ch02-qlogms/excitation-design.tex
Small stuff

@@
   \end{equation}
-  indicates the lowest frequency where the quasi-logarithmic grid can effectively reproduce the logarithmic spacing.
-  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
+  indicates the lowest frequency where the quasi-logarithmic grid could effectively reproduce the logarithmic spacing.
+  In particular for lightly-damped sub-systems, 
+  \begin{equation}
+  \wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}
+  \text{,}
+  \end{equation}
+  such that the resonance peak is in the bulk of the frequency grid when
   \begin{equation} 
@@
   \end{equation}
-  %TODO: turn this into a guideline?
+
   For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.

### 2016-05-03 ch02-qlogms/excitation-design.tex
More small things

@@
 
-  \subsubsection{Exploiting the grid misalignment between the system and the grid}
+  \subsubsection[Exploiting the grid misalignment]{Exploiting the grid misalignment between the system and the grid}
   Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.

### 2016-05-03 ch05-initvals/initial-values.tex
Some small cleanup

@@
  In this chapter, the \gls{MLE} is used as a proxy for any parametric transfer function estimator, since the \gls{MLE} is commonly used and has desirable properties such as efficiency and consistency.
+ Numerous other parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989,Pintelon2012}.
  Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
- Hence, the presented approach is orthogonal to initialization schemes such as the work of~\citet{vanHerpen2014}.
+ Hence, the presented approach is orthogonal to initialization schemes such as the work of~\citet{vanHerpen2014} that focuses on improving the optimization algorithm, rather than the starting values.
 
@@
 
-\section{Problem formulation}\label{sec:initial-values:ProbForm}
+\section{Problem formulation}
+\label{sec:initial-values:ProbForm}
 
@@
 
-\subsection{System Setup Framework and Model}
-\TODO{ hele subsectie verplaatsen na het param. sys. model?}
+\subsection{System Framework and Model}
 \figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic \gls{LTI} discrete-time \gls{SISO} system, subjected to a known white random noise input.
@@
 
-\TODO{paragraaf naar intro verplaatsen}
-Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.
-
 In this chapter we assume that the output signal is disturbed by random noise, resulting in noisy error-prone data.
@@
 It is also possible to apply the estimation procedure in this chapter to a system that is disturbed by colored noise, as will be demonstrated in \secref{sec:initial-values:ExpMeas}.
-
-\subsection{Parametric System Model}
 
@@
 \\
-T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
+T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2
+\label{lpmImplQuadT}
 \end{align}
 \end{subequations}
-where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,B_W\}$ and $N_W$ is a tunable parameter. 
-%TODO notation LPM uniform maken met CH03/CH04
+where, in general,$r \in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,N_W\}$ and $N_W$ is a tunable parameter.
 
@@
 \begin{equation}
-\hat{G}_\text{LPM}(\omega_k) = \hat{G}_k
+\hat{G}_{\LPM}(\omega_k) = \hat{G}_k
 \text{.}
@@
 The \gls{RFIR} method is a special case of the \gls{RARX} method.
-%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.
 

### 2016-05-03 ch01-intro/introduction.tex
Comments from Péter

@@
 In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
-For the technical details, we refer to the many textbooks on system identification~\citep{Soderstrom1989,Ljung1999,Pintelon2012}.
+For the technical details, we refer to the many textbooks on system identification~\citep{Keesman2011,Norton1986,Soderstrom1989,Ljung1999,Pintelon2012}.
 Here, we give the high-level overview of the different steps.
@@
 One such tool is the frequency response function.
-For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \ldots
+For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
 This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
 However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
+%TODO: peter: also discuss model selection for nonparametric here
 
-\paragraph{Estimate the model}
+\paragraph{Estimate the model parameters}
 Once the model structure has been chosen, its parameters are to be estimated.
@@
 This can happen in a few different ways.
-On the one hand, in-sample measures such as statistical tests on the value of the cost function, correlation tests on the residuals, \ldots allow to verify that the model performs well on the measured dataset.
+On the one hand, in-sample measures such as statistical tests on the value of the cost function, correlation tests on the residuals, \latin{etc.} allow to verify that the model performs well on the measured dataset.
 Such approaches help to detect underfitting, where the model is not flexible enough to describe the measurements.
@@
 One the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
-The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \ldots
-This is the typical kind of modeling practices in school.
+The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
+This is the typical kind of modeling practiced in school.
 Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
@@
 Here, the model structure is chosen such that a wide variety of phenomena can be described.
-Regardless of the nature of the underlying system, be it mechanical, chemical, electrical, structural, \ldots, most dynamic phenomena can be described using differential equations (or difference equations).
+Regardless of the nature of the underlying system, be it mechanical, chemical, electrical, structural, \ldots; most dynamic phenomena can be described using differential equations (or difference equations).
 In particular, for black-box models, the structure of the model is chosen such that the data is well-approximated.
@@
 In this dissertation, we use mainly black box models (or very dark gray ones) as those are independent from the actual application.
-Hence, the proposed techniques should be applicable for different areas of engineering: electrochemical, electronics, mechatronics, structural engineering, \ldots
+Hence, the proposed techniques should be applicable for different areas of engineering: electrochemical, electronics, mechatronics, structural engineering, \latin{etc.}
 
@@
 For seasoned identification practitioners, methods that require little interaction are an opportunity for automation.
-This is especially important for complex systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, \ldots
+This is especially important for complex systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, and networked systems amongst others.
 For such complex systems, building a model can be time-consuming and laborious if one has to supervise every step of the process.

### 2016-05-03 ch03-lrm/nonparametric.tex
Ch03: summary of simulations

@@
   % \subsection{Implications of the model structure}
-  % \subsection{Implications of the noise level}
   % \subsection{Implications of the noise coloring}
@@
 \subsection{Summary}
-\TODO{discussie}
+In general, it can be seen that the \gls{LRM} performs better than \gls{LPM} unless the \gls{SNR} near the resonance is very low ($10\unit{dB}$).
+For the \gls{LPM}, it should be noted that near resonances,it more advantageous to use even model orders~\citep{Schoukens2013LPMerror}.
+The results for the $\lpm{7,4,4}$ in the previous section are representative of the best-case performance of an $\lpm{7,\order{B},\order{A}}$ technique.
+Concretely, for small $\nBW$, the dominant error in the \gls{LPM} is due to the bias.
+Reducing the model order of the \gls{LPM} further will only increase the \gls{RMS} error.
+Increasing the model order of the \gls{LPM} (e.g.
+to $\lpm{7,6,6}$) would result in an estimation where the residuals have very few degrees of freedom ($\DOF=1$ for $\lpm{7,6,6}$) such that estimated noise level is less reliable~\citep{Pintelon2010LPM1}.
+
+For the \gls{LRM}, it can be seen that its model order as a significant influence on the approximation error.
+In small datasets with high \gls{SNR} ($\SNR=60\unit{dB},\nBW<3$), and in datasets with low \gls{SNR} ($\SNR < 40 \unit{dB}$), selecting a better local model can reduce the bias significantly.
+Nevertheless, the bias of the \gls{LRM} is only a significant contributor to the \gls{RMS} error for short datasets with low \gls{SNR}.
+As such, selection of a better local model is only reduces the \gls{RMS} error for those settings.
+Practically, this means that in most other settings of \gls{SNR} and frequency resolution, either a first-order or second-order \gls{LRM} ($\order{A},\order{B} \in \set{1,2}$) will perform almost equally well.
+From an intuitive point of view: this works well when each local bandwidth $\LocalWindow$ is affected by at most two resonances.
+
+The \gls{LRIC} is not practically viable due to the high variability.
+However, since its bias is much lower than for the other methods, \gls{LRIC} offers perspectives for improving the overall performance significantly.
 
@@
 
+\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
+For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
+When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
+The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
+\end{guideline}
+
 \begin{guideline}[For long measurements, LPM and LRM are similar]
@@
 
-  % \section{Measurements}
-  % \label{sec:measurements}
-  %  \subsection{AVIS}
-   % \subsection{F16}
-
 \section{Trading off the bias and variance}
-
-\TODO{introduction, probleem, oplossingen die besproken worden}
+In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
+This is specifically the case for small and noisy datasets.
+Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}.
+As such, it makes sense to ask ourselves the question: ``can we determine a good local model order''?
+That is the question we will investigate in this section.
+First, some classical approaches are compared in the context of local modeling, i.e. relatively small (local) datasets.
 

### 2016-05-03 config/styles.inc.tex
Some comments from Johan, tom
Remove FRF style
Simplify styles
Improve some figures

@@
 %% Colors
-  \colorlet{tangored}{TangoScarletRed1}
-  \colorlet{tangoblue}{TangoSkyBlue2}
-  \colorlet{tangogreen}{TangoChameleon2}
-  \colorlet{tangogrey}{TangoAluminium5}
-
   \colorlet{meas}{TangoPlum2}
@@
 
-  \colorlet{model}{tangogrey}
+  \colorlet{model}{TangoAluminium5}
   \colorlet{bg}{TangoAluminium2}
@@
 \colorlet{truesys}{TangoAluminium5}
-% \colorlet{truesys}{TangoAluminium4} % from LRMHinf paper
+\colorlet{frf}{truesys}
 
@@
 
-\colorlet{frf}{TangoButter3} %TODO: replace
 \colorlet{param}{TangoScarletRed2}
@@
 
+  \colorlet{noisefill}{TangoAluminium1}
+  \colorlet{noiseline}{TangoAluminium5}
+
 \colorlet{etfe}{TangoButter3}
-\colorlet{lrm7111}{TangoPlum3}
+\colorlet{lrm7111}{TangoPlum2}
 \colorlet{lric7222}{TangoChameleon3}
 \colorlet{lrm7222}{TangoSkyBlue3}
-\colorlet{lrm6222}{TangoOrange3}
+\colorlet{lrm6222}{TangoSkyBlue1}
 \colorlet{lpm744}{TangoScarletRed3}
@@
 \pgfplotsset{bw/.style={fill=bwfill,draw=bwline,opacity=0.75,area legend}}
+\pgfplotsset{noiselevel/.style={fill=noisefill,draw=noiseline,opacity=0.75,area legend}}
 \pgfplotsset{signal/.style={ycomb,color=signal,solid,line width=1pt}}
@@
 \pgfplotsset{compen/.style={fill,fill opacity=0.65,color=compen,smooth,forget plot}}
-\pgfplotsset{truesys/.style={color=tangogrey,line width=1pt}}
+\pgfplotsset{truesys/.style={color=truesys,line width=1pt}}
 \pgfplotsset{mainsys/.style={color=black,line width=1pt}}
@@
 \tikzset{annotation/.style={align=left,draw=black!0.2,font=\scriptsize,fill=white,fill opacity=0.8}}
+\tikzset{trace/.style={align=left,font=\scriptsize,fill opacity=0.8,fill=#1}}
+\tikzset{trace/.default=white}
 
@@
 
-%TODO: redefine this thingie for LRM chapters
 % \pgfplotsset{truesys/.style={color=truesys,densely dotted,line width=1.5pt}}
+\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}}
 
@@
 \pgfplotsset{SAgrid/.style={color=SA,densely dotted,solid,mark=triangle*,mark size=1.5pt,mark options={solid}}}
-
-\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=0.2pt}} %TODO: replace
 

### 2016-05-03 ch06-concl/conclusions.tex
Finished conclusions

@@
 
+In this thesis, user-friendly system identification methods have been developed.
+These methods require little to no user interaction and are designed such that the method work for a broad range of systems.
+As such, many of the obtained improvements can be obtained without bothering the user for further information and tuning.
+Throughout this dissertation, so-called `Guidelines' have been scattered that offer a bird's eye view of the work from a practical point of view.
+In the following sections, the main results of this work are summarized and perspectives are sketched for further (and ongoing) research paths.
+
 \section{Results of this Research}
-\TODO{general introduction, claim the title, reaffirm the structure of the book}
 

### 2016-05-03 ch03-lrm/truncation.tex
More small things
Improve structure in CH03, add workflow figure

@@
 The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
-This is done by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
+The smoothing of the \gls{FRF} happens by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
 The truncation point (cut-off index) is determined by one of two statistically inspired methods.
@@
 It should be noted, however, that such smoothing is merely of importance when inspecting the \gls{FRF} visually.
-In particular, a slight bias is incurred when smoothing the \gls{FRF}.
+In particular, a slight bias might be incurred when smoothing the \gls{FRF}.
 If one is to fit a parametric model to the smoothed \gls{FRF}, one essentially ends up with a biased model (which is often undesirable).
@@
 In this section, the $\lpm{3,2,2}$ is used.
+However, since the techniques discussed in this section are not specifically geared towards the \gls{LPM}, one can just as well use the concepts with other non-parametric \gls{FRF} estimators such as the \gls{LRM}.
 
@@
 
-\subsection{Smoothing the \gls{FRF} estimate}
+\subsection{Smoothing the \glsentryshort{FRF} estimate}
 \label{sec:nparam:trunc:smoothingFRFestimate}
 The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions.
-After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures (see \figref{fig:nparam:truncation:workflow}), which will be elaborated on later:
 \begin{enumerate}
 \item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.
+
+\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response and this is subtracted from the impulse response.
+
+\item From the estimated impulse response $\hat{g}(t)$, the noise floor is estimated.
 
@@
 
-\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response.
+\item A truncation is effected at the point beyond which the estimated impulse response is buried in noise.
+This action results in smoothing of the \gls{FRF} when the truncated impulse response is transformed to the frequency domain using the \gls{DFT}.
+\end{enumerate}
 
-\item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
-This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
-\end{enumerate}
+\begin{figure}
+   \centering
+   \setlength{\figurewidth}{0.75\columnwidth}
+   \includegraphics[width=\figurewidth]{\thisDir/figs/workflow-truncation.pdf}
+   \caption{Workflow for impulse response truncation.}
+   \label{fig:nparam:truncation:workflow}
+ \end{figure}
 

### 2016-05-04 ch03-lrm/nonparametric.tex
Improve structure in CH03, add workflow figure
Add thumb index
Some cleanup here and there

@@
 \chapter{Non-parametric Modeling}
+\AddThumb{Non-parametric Modeling}
+\label{sec:nonparametric}
 \def\thisDir{ch03-lrm}
 \tikzsetfigurename{ch03fig}
-\label{sec:nonparametric}
-\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.
-}{Douglas Adams}{}
+\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
 
@@
 In the remainder of this text, we refer to \gls{LRM} as a group of methods which have $\order{A} \neq 0$ to make the distinction with \gls{LPM} more obvious.
+For more information regarding \gls{LPM}, we refer to e.g. \citet{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,Gevers2011lpm}.
 
@@
 The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
-It should be noted, however, that such methods differ significantly from the \gls{LPM}.
+It should be noted, however, that such methods differ in a few aspects from the \gls{LPM}.
 Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
@@
 
-\section{LPM with impulse response truncation}
+\section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}
 \input{\thisDir/truncation.tex}

### 2016-05-04 ch02-qlogms/excitation-design.tex
Add thumb index
Some work: local parameters -> global parameter selection

@@
   This is a maximum likelihood estimator that fits a parametric model to the measured data in the frequency domain.
-  %TODO: add formulas with cost function etc.
-  To improve convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $G_0(z)$, so that we can focus completely on the variance of the estimations.
+  To improve convergence and avoid local minima, the initial values for the model are chosen equal to the parameters of the true system $\true{G}(z)$, so that we can focus completely on the variance of the estimations.
 
@@
   The observed results were similar and hence are not elaborated further in this text.
-  For more information, please refer to~\citep{Larsson2012SYSID}.
+  For more information, please refer to~\citet{Larsson2012SYSID}.
   \end{remark}

### 2016-05-04 ch03-lrm/nonparametric.tex
Revert "Add thumb index"
This reverts commit 18177995b597a30e5df7c5f1278b7fb207af0692.
It does include some small fixes here and there (so not a full revert)
Some work: local parameters -> global parameter selection

@@
 \chapter{Non-parametric Modeling}
-\AddThumb{Non-parametric Modeling}
-\label{sec:nonparametric}
 \def\thisDir{ch03-lrm}
 \tikzsetfigurename{ch03fig}
+\label{sec:nonparametric}
 \myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
@@
 
-% \begin{figure}
-%   \centering
-%   \setlength{\figurewidth}{0.85\columnwidth}
-%   \setlength{\figureheight}{0.62\figurewidth}
-%   \TODOtikzfig[figure with G and errors for 1 simulation]
-%   \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods.
-The $3\unit{dB}$ bandwidth of the system is highlighted.}
-% \end{figure}
-
 We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=\num{2000}$ Monte Carlo runs of the simulations above.
@@
 \begin{align}
-L_{\mathrm{\AIC}} &=
+\LocalVector{L}_{\AIC} &=
  - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
@@
 \label{eq:nparam:AIC}\\
-L_{\mathrm{\AICc}} &= 
+\LocalVector{L}_{\AICc} &= 
 - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
@@
 $\nWind \to \infty$, which is obviously an unwarranted choice in this context.
-The best model among a set of $q$ possible models $\Set{M_1, \ldots, M_q}$ is then
-\begin{equation}
-  M_{\star} \isdef 
-  \arg_{M} \min 
+The best model among a set of $q$ possible models $\Set{\LocalModel{M}^1, \ldots, \LocalModel{M}^q}$ is then
+\begin{equation}
+  \LocalModel{M}^{\star} \isdef 
+  \arg\limits_{\LocalModel{M}} \min 
   \Set{
-    L_{\mathrm{AIC(c)}}(M)
+    \LocalVector{L}_{\mathrm{AIC(c)}}( \LocalModel{M}^i  )
+    |
+    i = 1,\ldots,q
   }
@@
 This means specifically that the noise variance $\sigma^{2}_{V}$ needs to be known beforehand.
-When the variance is unknown, however, it is more robust to incorporate the \gls{AIC} as a penalty factor on the cost function as indicated in \citet[Section 7.4]{Ljung1999} and \citet[Section  11.3 and 19.7]{Pintelon2012}.
+When the variance is unknown, however, it is more robust to incorporate the \gls{AIC} as a penalty factor on the cost function as indicated in \citet[Section 7.4]{Ljung1999} and \citet[Section  11.3 and 19.7]{Pintelon2012} such that the \gls{AIC} criterion becomes
+\begin{equation}
+  \LocalVector{L}_{\mathrm{AIC,cost}} = \LocalVector{L} \cdot \left( 1 + \frac{\nth}{\nWind} \right)
+\end{equation}
+with $\LocalVector{L}$ the original local cost function.
 \end{remark}
@@
 
-\subsection{Results}
-
-%TODO: discussie: 1 globale modelorder of verschillende
-% voor parametrische schatting: vensterbreedte constant houden, DOF constant houden over alle geselecteerde modellen
-% voor niet-parametrisch: orde kan per frequentielijn verschillen, geeft betere smoothing \citep{Thummala2012LPMBW,Fan1996}
+\subsubsection{Combining different local model orders}
+In the previous section, different methods were introduced to select the local model order.
+This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
+The answer to this, depends on the ultimate purpose of the \gls{FRF}.
+
+When the goal is to inspect the \gls{FRF} visually or to obtain a smooth representation of the transfer function, one can use different model orders per frequency bin.
+\Citet{Stenman2001ASFRF,Fan1996,Thummala2012LPMBW} show that a varying model order can reduce both bias and variance depending on the characteristic of the system.
+Near resonances one might need a higher local model order than in regions with constant slopes (e.g. $20\cdot n \unit{dB/decade}$).
+For non-parametric purposes, this means that one can select the optimal local model for each frequency bin and combine those local models to obtain the optimal \gls{FRF}.
+
+For estimating a global parametric model using the \gls{FRF} obtained from local modeling, one has to take extra care.
+\Citet{Pintelon2010LPM2} prove asymptotic properties of the sample \gls{MLE} in conjunction with an \gls{FRF} obtained from local modeling.
+Assuming $\DOF > 4$ and a constant model order, \citet{Pintelon2010LPM2} gives expressions for the expected value and variance of the (global) cost function and the asymptotic loss in efficiency for using the sample \gls{MLE} instead of the actual \gls{MLE} based on the work of \citet{Mahata2006}.
+For varying local model complexity, deriving these asymptotic properties analytically becomes intractable.
+As such, for estimating a (global) parametric model, a fixed local model order complexity should be used over the whole frequency axis.
+
+When an optimal model order is to be selected for the whole frequency range, the local optimality criteria need to be reformulated in the global context of all local models over the frequency.
+In practice, the formulas of the previous section extend quite ``naturally'' to this global context.
+Particularly for the \gls{PRESS}:
+\begin{equation}
+  \PRESS_{\mathrm{global}} = \sum_k \PRESS_k
+\end{equation}
+where $\PRESS_k$ denotes the \gls{PRESS} for the $k^{\text{th}}$ local model.
+One should realize that for all local models together ($M =  \cup_k \LocalModel[k]{M}$) and the global dataset $Z$, the global log-likelihood, cost function and number of parameters can be related to their local counterparts:
+\begin{align}
+  \loglikelihood{M | Z}   &= \sum_k \loglikelihood{\LocalModel[k]{M} | \LocalVector{Z}_{k}} \\
+  L_{\mathrm{global}} &= \sum_k \LocalVector{L}_k\\
+  \nth^{\mathrm{global}} &= \sum_k \nth(k)
+  \text{.}
+\end{align}
+These global quantities can be substituted in the expressions of the local \gls{AIC} and \gls{AICc} of the previous section. 
+Note that one should also $\nWind$ as the total number of data points (and not the number of points in each window).
+
+\subsection{Discussion}
 

### 2016-05-05 ch02-qlogms/excitation-design.tex
(sub)+sections: title case + some \gls{...}

@@
 
-\subsection{General purpose robust excitation signals}
+\subsection{General Purpose Robust Excitation Signals}
 \label{sec:excitation:intro:approach}
@@
 
-\section{Input design}
+\section{Input Design}
 \label{sec:excitation:inputDesign}
@@
 
-\section{Logarithmic power distributions}
+\section{Logarithmic Power Distributions}
 \label{sec:excitation:logarithmic}
@@
 
- \subsection{A second order system}
+ \subsection{A Second Order System}
 Consider the second order system
@@
 
-\subsection{Sums of second order systems}
+\subsection{Sums of Second Order Systems}
 This section extends the previous section to more general systems than second order.
@@
 
-\subsubsection{Example: Sum of two second-order systems}
+\subsubsection{Example: Sum of Two Second-Order Systems}
 \label{sec:excitation:ex:sumOfSecondOrderSipmle}
@@
 \begin{align}
-G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
-%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
+G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)\\
+&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} 
+   + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping[2]}{\wn[2]}s + 1},
 \end{align}
@@
          \partial G_{2,1}  & \partial G_{2,2}
-       \end{bmatrix}.
+       \end{bmatrix}
+       \text{.}
 \label{eq:excitation:infoEx}
@@
 To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.
+
+%FIXME: clean up latex math here, e.g. \frac{\partial ...}{\partial} -> \partialDerivative{...}{...}; use \abs{}; ...
 
@@
 
-\section{System parametrization} 
+\section{System Parametrization} 
 \label{sec:excitation:parametrization}
@@
 
-  \subsection{Comparison of the frequency grids}
+  \subsection{Comparison of the Frequency Grids}
   To gain some insight into these different grids, \figref{fig:excitation:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
@@
 
-\section{Optimization of the frequency spacing} 
+\section{Optimization of the Frequency Spacing} 
 \label{sec:excitation:optimAlpha}
-  \subsection{Calculation of the model uncertainty}
+  \subsection{Calculation of the Model Uncertainty}
   In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing $\alpha$, has not been designed.
@@
 
-  \subsection{Relation between the frequency grid and the system resonance} 
+  \subsection{Relation Between the Frequency Grid and the System Resonance} 
   \label{sec:excitation:relationLogGridSystem}
@@
 
-  \subsection{Exploiting the shape of the derivatives}
+  \subsection{Exploiting the Shape of the Derivatives}
    In particular, from \figref{fig:excitation:derivatives}, it can be seen that the derivatives with respect to $(\wn, \damping)$ exhibit a sharper resonance and hence $(\wn, \damping)$ will prove the hardest to identify.
@@
 
-  \subsection{Selection of the frequency grid spacing $\alpha$}
+  \subsection{Selection of the Frequency Grid Spacing $\Alpha$}
   Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
@@
 
-  \subsection{Systems with a `high' damping}
+  \subsection{Systems With a `High' Damping}
   To test the signals for systems with a high damping with respect to the frequency ratio in the excitation signal, systems with a damping $\damping = 0.2$ are used.
@@
 
-  \subsection{Systems with a lower damping}
+  \subsection{Systems With a Lower Damping}
   Given the optimal frequency ratio \eqref{eq:excitation:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
@@
 
-  \subsection{Simulation example on higher order systems}
+  \subsection{Simulation Example on Higher Order Systems}
 To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:excitation:secondOrderSystemDTidentifiable} in parallel.

### 2016-05-05 ch03-lrm/nonparametric.tex
(sub)+sections: title case + some \gls{...}

@@
 
-\section{Local modeling approaches}
+\section{Local Modeling Approaches}
 \label{sec:theory}
@@
 
-\subsection{Local modeling}
+\subsection{Local Modeling}
 Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
@@
 
-\subsection{The Local Rational Method}
+\subsection{The \glsentrydesc{LRM}}
 \label{sec:nparam:LRM}
@@
 
-\subsection{The Local Polynomial Method}
+\subsection{The \glsentrydesc{LPM}}
 \label{sec:nparam:LPM}
@@
 
-  % \subsection{Implications of the model structure}
-  % \subsection{Implications of the noise coloring}
+  % \subsection{Implications of the Model Structure}
+  % \subsection{Implications of the Noise Coloring}
 
@@
 
-\section{Trading off the bias and variance}
+\section{Trading Off the Bias and Variance}
 In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
@@
 
-\subsection{Order selection}
+\subsection{Order Selection}
 \label{sec:nparam:orderSelection}
@@
 
-\subsubsection{Combining different local model orders}
+\subsubsection{Combining Different Local Model Orders}
 In the previous section, different methods were introduced to select the local model order.

### 2016-05-05 ch04-lrmhinf/lrmhinf.tex
More conclusion + small stuff everywhere
Add thumb index
(sub)+sections: title case + some \gls{...}

@@
 
-\subsection{Set-up}
+\subsection{Set-Up}
 Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
@@
 
-\subsection{A concrete simulation}
+\subsection{A Concrete Simulation}
 Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
@@
 
-\subsection{Study of the experiment length}
+\subsection{Study of the Experiment Length}
 The frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
@@
   \photobox{\includegraphics[width=1.005\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}}
-  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
+  \caption[\glsentryshort{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
   The left photo shows one of the air mounts providing passive vibration isolation.
@@
 
-\subsection{Measurement \& control framework}
+\subsection{Measurement \& Control Framework}
 \label{sec:lrmhinf:control}

### 2016-05-05 ch05-initvals/initial-values.tex
Add thumb index
Revert "Add thumb index"
This reverts commit 18177995b597a30e5df7c5f1278b7fb207af0692.
It does include some small fixes here and there (so not a full revert)
(sub)+sections: title case + some \gls{...}

@@
-\chapter{Initialization of parametric estimators}
+\chapter{Initialization of Parametric Estimators}
 \label{sec:initvals}
@@
 
-\section{Problem formulation}
+\section{Problem Formulation}
 \label{sec:initial-values:ProbForm}
@@
 It is important to note that invoking the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the \glspl{FRF} from methods 3) and 4) will yield a different result from applying the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the raw data.
-This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance.
+This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance, but might be biased slightly.
 \end{remark}
-%}
-
-%\comment{JL: one could remove the subsection below (why?
-see my comments below), and mention that the the above initial estimates are then fed to the MLE, with the raw data, to obtain the final estimates.}
-
-%\subsection{Genesis of the Initial Estimates} 
-%\comment{JL: why `genesis'? This section is actually where you use the initial estimates, not their origin.}
-%{Deploying the initial estimates}
-
-%\comment{ML: Fig. \ref{fig:flowgraph} should include an additional path for RFIR/RARX, and the accompanying text (below) is to be modified accordingly.}
-%Fig.
-\ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart?
-It has actually been explained in further details in \secref{sec:init:procedures}.}
-%\begin{enumerate}
-%\item (Left (first) path of the flowchart): The true model $\true{G}$ as initial values,
-%\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
-%\item (Third path from the left of the flowchart): The LPM-truncated initial values with BTLS and GTLS, and  
-%%\item (Right (fourth) path of the flowchart): The RFIR initial values with BTLS and GTLS.  
-%\end{enumerate}
-
-%\JL{
-%The main contribution of this paper is to demonstrate that $\model{trunc}$ (third path) yields an improvement over $\model{exist}$ (second path).
-\comment{JL: these symbols haven't been introduced yet.
-I'm getting quite confident that this subsection can be removed.}The quantification of this improvement is formally introduced in the next section.
-%}
-
-%The latter 2 ....schematic is configured to include connections of the initial values and the input to the LPM block and/or to the MLE block(s) for estimation purposes.
-%\end{itemize}
-%\section{Example}\label{sec:initial-values:Example}
 
 \subsection{Success Rates of the Initial Estimates}
-
-The initial estimates described above are then fed to the MLE together with the raw data to obtain the final estimates.
+The initial estimates described above are then fed to the \gls{MLE} together with the raw data to obtain the final estimates.
 
@@
     \item $\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
-    \item $\model{exist}$ is obtained via GTLS and BTLS,
-    \item $\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
-    \item $\model{RFIR}$, initialized by means of the RFIR method. 
+    \item $\model{exist}$ is obtained via \gls{GTLS} and \gls{BTLS},
+    \item $\model{trunc}$ by the use of the \gls{LPM} with truncation as an initial estimate,
+    \item $\model{RFIR}$, initialized by means of the \gls{RFIR} method. 
 \end{itemize}
 
-A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
+A particular initial estimate is deemed \emph{successful} if the optimization of the \gls{MLE} cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.
 
@@
 $\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
-%}%}
-
-%\JL{
-%\subsection{Successful VS failed estimation}
+
 \subsection{Comparison of Successful and Failed Estimates}
-
-%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $\true{G}$, $\hat \true{G}$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
-%}
-%\EG{
- \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black
-%\comment{JL: in what color? (EG) black},
- and different estimates $\model{exist}$
- %\comment{JL: does it matter whether it is $\model{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
- that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
+ \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black and different estimates $\model{exist}$ that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
  The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, which are discussed later on in this chapter.
 
- It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
-that their distances from the true system, e.g. as given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
+ It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. 
+ This means that their distances from the true system, e.g. as given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
 On the other hand, the `failed' estimates are inaccurate descriptions of the true system. 
 It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.
-   %Given the 2-norm \eqref{eq:successrateTol} employed 
-   %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t.
-the relative error, except when $\abs{\true{G}(\omega)}$ is small.
- %Practically, 
- %In practice, this means that a successful estimate provides reasonable estimates of the pass-band of the system, but may perform poorly in the stop-band.
-\comment{Further discussion required: what about the absolute error?
-Isn't it more or less white over the complete frequency band?} \ML{To be discussed}
 
@@
   \input{\thisDir/figs/exampleSystems.tikz}
- % \caption{Results of an example of Monte Carlo simulation.}
  \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
@@
 
-%\subsection{Computing the success rates}
-\subsection{Computation of  the Success Rates}\label{sec:initial-values:CompuSR}
+\subsection{Computation of  the Success Rates}
+\label{sec:initial-values:CompuSR}
 
@@
 
-\subsection{Identification procedure}
+\subsection{Identification Procedure}
 The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
@@
 
-\subsection{Reference model measurements}
+\subsection{Reference Model Measurements}
 
@@
 
-\subsection{Model estimation}
+\subsection{Model Estimation}
   The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
@@
 
-\subsection{Model validation}
-\subsubsection{Cost function limitations}
+\subsection{Model Validation}
+\subsubsection{Cost Function Limitations}
 In the previous section, the cost function was studied to determine the effectiveness of the starting values.
@@
 
-\subsubsection{Validation criterion}
+\subsubsection{Validation Criterion}
 To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
@@
 
-\subsubsection{Validation performance}
+\subsubsection{Validation Performance}
 The observed median and \gls{IQR} of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
@@
 
-\section{Consequences of selecting the `best` model}
+\section{Consequences of Selecting the `Best` Model}
 To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
@@
 
-\section{Remark on the generality}
+\section{Remark on the Generality}
 \label{sec:initial-values:Generality}
@@
 
-\subsection{Limitations of the smoothers}
+\subsection{Limitations of the Smoothers}
 On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g.
@@
 
-\subsection{Stress test of the smoothers}
+\subsection{Stress Test of the Smoothers}
 To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
@@
 
-\section{Computational effort}\label{sec:initvals:computation}
+\section{Computational Effort}\label{sec:initvals:computation}
 While improved initial values yield better models of an improved quality, their generation does require some computational effort.
@@
 
-\subsection{Practical runtime}
+\subsection{Practical Runtime}
 In practical measurements of the computation time for any piece of software, one typically distinguishes between different kinds of `time'.
@@
 
-\subsection{Asymptotic runtime}
+\subsection{Asymptotic Runtime}
 For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e.
@@
 
-\subsection{Implementation aspects}
+\subsection{Implementation Aspects}
 This section presents some implications and recommendations for the implementation of  a system identification toolbox.

### 2016-05-05 ch06-concl/conclusions.tex
Add thumb index
(sub)+sections: title case + some \gls{...}

@@
 
-\section{Results of this Research}
+\section{Results of This Research}
 
@@
 
-  \subsection{Non-parametric Estimation}
+  \subsection{Non-Parametric Estimation}
 
@@
 
-  \subsection{Non-parametric Estimators}
+  \subsection{Non-Parametric Estimators}
     The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
@@
 
-  \subsection{Non-parametric Estimation and Interpolation}
+  \subsection{Non-Parametric Estimation and Interpolation}
   As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.

### 2016-05-05 ch01-intro/introduction.tex
Add thumb index
(sub)+sections: title case + some \gls{...}
Most comments of Tom on intro addressed

@@
 
-In this chapter, we first discuss some basic aspects of system identification, some typical choices and how those relate to user-friendly system identification and this dissertation.
+\section{Modeling}
+Models play an important role in today's world, even though we often are not always aware of them.
+In particular, models enable us to predict the future (within a certain bound of uncertainty):
+\begin{itemize}
+  \item supermarkets try to predict how many produce their patrons will buy such that they can order a large enough supply,
+  \item traders on the stock market aim to predict whether companies such as Tesla or Apple will continue to prosper over the next quarter such that they can decide if it's time to buy more stock or rather sell,
+  \item weather forecasters hope to predict what weather it might become tomorrow,
+  \item how much electricity will the whole country use next week (do we need to start up a new power plant or not),
+\end{itemize}
+and so on.
 
-\section{System Identification}
-System identification is the science that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
-Successfully identifying a system often hinges on a plethora of choices that are to be made by the user.
-As a result, system identification can also be seen as an art for which the practitioner needs to learn the tricks of the trade.
+Models help us to keep an oversight of complicated matters.
+Once we understand the behavior of a few systems, this offers great opportunities to understand how those systems work together or even how we can control the world around us.
+For engineers, models enable us to design larger and more complicated things than ever before.
+E.g. consider a \gls{CPU} in a computer: with a few billion transistors, it is no longer possible for a sole human being to understand what every single transistor does in the grand scheme.
+Instead, models of larger parts of the circuit allow us to retain insight (`this part of the \gls{CPU} caches some variables', `these transistors multiply two numbers', and so on).
+
+\subsection{How to Obtain a Model?}
+
+To successfully model a system, one has to delimit what part of the world one actually wants to model, i.e. the \term{system}.
+Since a system is mostly useful if it interacts with the world around it, one often also has to define \term{inputs} through which one can influence the system, and \term{outputs} which are influenced by the system.
+
+Modeling can be divided into two diametrical groups depending on what one uses as a starting point.
+\paragraph{White box}
+One the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
+The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
+This is the typical kind of modeling practiced in school.
+Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
+In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.
+
+\paragraph{Black box}
+On the other hand, the diametrically opposed approach is called \term{`black box'} modeling.
+Here, the model structure is chosen such that a wide variety of phenomena can be described.
+Regardless of the nature of the underlying system, be it mechanical, chemical, electrical, structural, \ldots; most dynamic phenomena can be described using differential equations (or difference equations).
+In particular, for black-box models, the structure of the model is chosen such that the data is well-approximated.
+The downside of this is that interpreting the model physically is not always possible.
+Fortunately, the goal of a model is often not to interpret the physical reality but to approximate it well enough to allow engineering
+
+\paragraph{Gray box}
+Obviously, in practice nothing is ever as black and white, and neither is modeling.
+In many cases, one can or even has to incorporate knowledge about the physics of the system in the modeling process.
+In particular when one has black box models where some parameters are related to physical phenomena, the resulting model is called \term{`gray box'}.
+
+\section{Elements of System Identification}
+System identification is the science (and often art) that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
+As such, system identification rather fits in the category of black box modeling (or at least dark gray).
+Successfully identifying a system hinges on a plethora of choices that are to be made by the user.
+To make these choices well, a practitioner needs a considerable amount of experience. 
 In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
@@
 Here, we give the high-level overview of the different steps.
+For a more complete overview, we also refer to \citet{Ljung2010}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
+  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
+  \label{fig:intro:identification-cycle}
+\end{figure}
 
@@
 Unfortunately, for many identification settings, these optimization problems are non-convex~\citep{Boyd2004}.
+Practically, this means that 
 This means that initial values need to be available to start the optimization process.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
-  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
-  \label{fig:intro:identification-cycle}
-\end{figure}
+\section{User-friendly System Identification}
+In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and/or craftsmanship of the user to make good choices.
 
-\subsection{System Identification Choices}
-In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
-We cover some typical traits of different methods and describe why a particular approach is favored in this thesis.
-
-\subsubsection{White Box, Black Box or Grey Box?}
-Modeling can be divided into two diametrical groups depending on the starting point of modeling~\citep{Ljung2010}.
-One the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
-The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
-This is the typical kind of modeling practiced in school.
-Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
-In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.
-
-On the other hand, the diametrically opposed approach is called \term{`black box'} modeling.
-Here, the model structure is chosen such that a wide variety of phenomena can be described.
-Regardless of the nature of the underlying system, be it mechanical, chemical, electrical, structural, \ldots; most dynamic phenomena can be described using differential equations (or difference equations).
-In particular, for black-box models, the structure of the model is chosen such that the data is well-approximated.
-The downside of this is that giving physical interpretations of the model is not always possible, but for many applications (e.g. controller design) that is not the main goal of the model.
-
-Obviously, in practice nothing is ever as black and white and neither is modeling.
-In many cases, one can or even has to incorporate knowledge about the physics of the system in the modeling process.
-In particular when one has black box models where some parameters are related to physical phenomena, the resulting model is called \term{`gray box'}.
-
-In this dissertation, we use mainly black box models (or very dark gray ones) as those are independent from the actual application.
-Hence, the proposed techniques should be applicable for different areas of engineering: electrochemical, electronics, mechatronics, structural engineering, \latin{etc.}
-
-\subsubsection{Linear or nonlinear?}
-A preliminary choice that is often made, is to first try linear models.
-Linear models guarantee that superposition of input-signals results in the superposition of the corresponding output signals.
-Specifically, if a linear system maps the output $u_i$ to the output signal $y_i$ (for any value of $i$), then an input $\sum_i u_i$ is mapped to the output $\sum_i y_i$.
-As such, the output of a system is (linearly) proportional to its input.
-This is a very powerful property that allows to simplify reasoning about such systems.
-The implications of this powerful property can be verified textbooks covering signals and systems~\citep{Oppenheim1996,Mandal2007,Kailath1980}.
-For non-linear systems, the superposition property is no longer guaranteed.
-
-In practice, all systems behave in a nonlinear way to some degree.
-Just imagine riding a bike: when you are cruising at a constant speed, pedaling at a faster pace will make the bike go proportionally faster.
-However, once you come to a full stop at a traffic light and want to start riding again, you need to apply a disproportionate amount of force to put the bike to motion again (due to friction).
-
-In this dissertation, we assume the system behaves in a dominantly linear way.
-No specific care is taken of nonlinearities.
-However, even with dominantly linear models~\citep{Schoukens2004}, nonlinear systems can often be well-described.
-Nevertheless, building a model to characterize the nonlinearities in a structured way requires a lot more effort~\citep{Ljung2010,Giri2010,Sjoberg1995}.
-However, e.g. for block-oriented nonlinear models~\citep{Giri2010}, some of the intermediate steps require identification of linear blocks.
-
-\section{User-friendly System Identification}
 In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
@@
 \begin{itemize}
-  \item novice users, without formal training in system identification, optimization, \ldots and,
+  \item novices, without formal training in system identification, optimization, \ldots and,
   \item well-seasoned identification practitioners that are already able to build good models.
@@
 For seasoned identification practitioners, methods that require little interaction are an opportunity for automation.
-This is especially important for complex systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, and networked systems amongst others.
+This is especially important for complicated systems: systems that have high-order dynamics, \gls{MIMO} systems with a high dimensionality, and networked systems amongst others.
 For such complex systems, building a model can be time-consuming and laborious if one has to supervise every step of the process.
@@
 In particular, \gls{LTI} systems are a first step to build a system model.
-In many cases, such a linear model is accurate enough, e.g. to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
-Also, most engineers and scientists have a good understanding of linear systems such that \gls{LTI} models align well with their prior knowledge and experience.
+In many cases, such a linear model is accurate enough~\citep{Schoukens2004}, e.g.
+to build a nominal controller, to design electrical filters and obtain a reasonable intuition of the system under test.
+Also, most engineers and scientists have a good understanding of linear systems~\citep{Oppenheim1996,Mandal2007,Kailath1980} such that \gls{LTI} models align well with their prior knowledge and experience.
 Nevertheless, when a linear model is not adequate, a more flexible model needs to be constructed.
@@
 In this dissertation, we look into a few aspects of the identification workflow with the goal to make the whole process more user-friendly.
+Each of these aspects will be dealt with in its own chapter.
 
-\paragraph{How should a good experiment be designed?}
+\subsubsection{How should a good experiment be designed?}
 Can we design a `good experiment' to identify a \gls{LTI} model?
@@
 
-\paragraph{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}
+\subsubsection{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}
 Developing a full parametric model for complicated systems requires considerable effort.
 Instead, could we leverage non-parametric or locally parametric approaches to obtain insight in the behavior of the system?
-In particular, can local modeling methods be used to characterize the resonances of a system, or even work around the typical frequency resolution limitations of a discrete frequency grid?
 
-\paragraph{Can we avoid local minima by using smoothers?}
+\subsubsection{Can we estimate the peak gain of a system in a non-parametric way?}
+To robustly control complicated systems, it can be overly cumbersome and even unwanted to construct high-order parametric models.
+As a result, some lightly damped resonances can dominate the model uncertainty.
+For robust control, this poses serious problems as such very sharp resonances are hard to observe in an \gls{FRF} measurement.
+Instead, can we capture the peak gain of resonances using non-parametric models (i.e. without resorting to a global parametric model)?
+
+\subsubsection{Can we avoid local minima by using smoothers?}
 When a parametric model is required, this often involves solving a nonlinear optimization problem.
@@
 
-\section{Outline and Publications}
+\subsection{Outline and Publications}
    The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
@@
 
-The quasi-logarithmic multisines presented in \chapref{sec:excitation} are based on a journal article published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+In \chapref{sec:excitation}, quasi-logarithmic multisines are proposed as a good (robust) excitation signal. 
+That chapter is based on a journal article published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
 \begin{itemize}
@@
 
-The non-parametric estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished manuscript.
+The non-parametric \gls{FRF} estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished manuscript.
 The so-called time-truncated \gls{LPM} that is presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:

### 2016-05-05 ch03-lrm/truncation.tex
Some cleanup here and there
Some cleanup in truncation

@@
 \researchBasedOn[This section]{Lumori2014TIM}
-%TODO: {labels into standardized form}
-
-% This section uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion.
-% The advantage of using the nonparametric models is basically that the `models` often are very simple and hence require little user interaction to construct.
-% Among the current nonparametric methods, the \gls{LPM} method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors~\citep{Bendat1993,Oppenheim1983,Schoukens2006LPM}.
-% Consequently, the \gls{LPM} estimate of the \gls{FRF} is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. 
-% Note that a more general discussion on the \gls{LPM}, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.
+%FIXME: {labels into standardized form}
 
@@
 
-% \subsection*{Theory on the LPM and Windowing}
-% \label{sec:nparam:trunc:theoryLPMandWindowing}
-
-% Details of the theory pertaining to this section may be found in \citet{Schoukens2009LPM}, basic aspects of which are presented below.
-
-% \subsubsection{Spectral Nonparametric Model and Assumptions}
-
-% Using convolution, the noiseless output signal in \figref{fig:nparam:blockH0} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise.
-% As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
-% \begin{equation}\label{eq:nparam:trunc:LPM:leakage}
-% Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
-% \end{equation}
-% where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
-% In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}
-
-% \begin{equation}\label{eq:defDFT}
-% X(\omega_k) = \frac{1}{\sqrt{N}}\sum_{t=0}^{N-1}x(t)e^{-\frac{j2\pi kt}{N}}
-% \end{equation}
-
-% The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:blockH0}):
-% \begin{assumption}
-% The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
-% \end{assumption}
-
 % \begin{assumption}
@@
 
-% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \latin{viz}:
-% \begin{align}\label{lpmGTaylorS}
-% G_0(\omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
-% \bigO{\left(\frac{r}{N}\right)^{R+1}},
-% \\
-% \label{lpmTTaylorS}
-% T(\omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
-% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
-% ,
-% \\
-% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
-% \end{align}
-
-% The choice of the tunable parameters $n$ and $R$ is discussed later on.
-
-% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \latin{viz}:
-% \begin{equation}\label{lpmGTMatrix}
-% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
-% \end{equation}
-% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\omega_k)$, $T(\omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
-% \begin{align}
-% K(k,r) = &\left[
-% \begin{matrix}
-% U_0(k+r) & U_0(k+r)r & \dots
-% \end{matrix}
-% \right.
-% \\
-% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
-% \end{align}
-
-% Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
-% \begin{equation}\label{lpmGTMatrixStack}
-% Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
-% \end{equation}
-% where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
-% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \latin{viz}:
-% \begin{align}\label{eq:LSsolutionLPM}
-% \hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
-% \end{align}
-
-% The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$.
-The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}.
-
-% The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
 In this section, the $\lpm{3,2,2}$ is used.
 However, since the techniques discussed in this section are not specifically geared towards the \gls{LPM}, one can just as well use the concepts with other non-parametric \gls{FRF} estimators such as the \gls{LRM}.
-
-% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\omega_{k}$:
-% \begin{align}
-% G_0(\omega_{k+r})
-%   &\approx 
-%   G_0(\omega_k)+g_1r+g_2r^2
-%   \label{eq:lpm:expansionG:quadratic}
-% \\
-%   T(\omega_{k+r})
-%     &\approx 
-%     T(\omega_k)+t_1r+t_2r^2
-%     \label{eq:lpm:expansionT:quadratic}
-% \end{align}
-% with ($r\in\mathbb{W}_3$) and the vector of parameters:
-% \begin{equation}\label{lpmThetaEst}
-% \theta^{\TT}(k)=\left[G_0(\omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
-% \end{equation}
-% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \latin{viz}:
-% \begin{equation}
-% \hat{G}_{\LPM}(\omega_k) = \hat\theta_1(k)
-% \end{equation}
 
@@
 
-The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF}, \latin{viz}:
+The estimated impulse response function  $\hat g_{{\LPM}\without \DC}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF}, \latin{viz}:
 \begin{align}\label{eq:impRespiDFT}
-\hat g_{{\LPM}\setminus \mathrm{DC}}(t) 
+\hat g_{{\LPM}\without \DC}(t) 
 &= 
@@
 Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
-Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:LRM} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}.
+Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:LRM} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\without\DC$'' in equation \eqref{eq:impRespiDFT}.
 Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
@@
 \begin{enumerate}
-\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)$, estimated by the \gls{LPM}, as %$\hat g_{\LPM}(t)$ as
+\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{{\LPM}\without \DC}(t)$, estimated by the \gls{LPM}, as %$\hat g_{\LPM}(t)$ as
 \begin{align}
@@
    \sum_{t=\lfloor0.9N\rfloor}^{N-1}
-      \hat g_{{\LPM}\setminus \mathrm{DC}}(t)
+      \hat g_{{\LPM}\without \DC}(t)
 \end{align}
 
-\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
-}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \latin{viz}:
+\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\without \DC}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \latin{viz}:
 \begin{align}
-\hat g_{\LPM}(t) = \hat g_{{\LPM}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
+\hat g_{\LPM}(t) = \hat g_{{\LPM}\without \DC}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
 \end{align}
@@
 
-\subsection{Determining the Truncation Time}
+\subsection{Determining the Truncation Time of the Impulse Response}
 In this section, two methods will be discussed to determine the truncation time, i.e. the time beyond which the measured impulse response cannot be separated from the noise level.
@@
 
-\subsubsection{Truncation of the Impulse Response Via Exponential Fitting}
+\subsubsection{Truncation Via Exponential Fitting}
 \label{sec:nonparametric:truncation:exponentialfit}

### 2016-05-06 ch01-intro/introduction.tex
Research questions as theorems

@@
 
-\section{User-friendly System Identification}
+\section{User-Friendly System Identification}
 In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and/or craftsmanship of the user to make good choices.
@@
 
-\subsubsection{How should a good experiment be designed?}
+\begin{question}[How should a good experiment be designed?]
 Can we design a `good experiment' to identify a \gls{LTI} model?
@@
 However, the signal should ensure that systems in different frequency bands can be identified with a specified level of accuracy.
+\end{question}
 
-\subsubsection{Can we process the input/output data in a non-parametric way that offers more insight than a standard frequency response function?}
+\begin{question}[Which non-parametric method should be used for an \gls{FRF}?]
 Developing a full parametric model for complicated systems requires considerable effort.
 Instead, could we leverage non-parametric or locally parametric approaches to obtain insight in the behavior of the system?
+Methods such as the \gls{LPM} and \gls{LRM} can offer good results.
+However, it is not clear how these should be tuned for different circumstances (near sharp resonance peaks, in low noise circumstances, \ldots).
+Can we devise simple rules that allow one to obtain good \glspl{FRF}?
+\end{question}
 
-\subsubsection{Can we estimate the peak gain of a system in a non-parametric way?}
+\begin{question}[Can we estimate the peak gain of a system in a non-parametric way?]
 To robustly control complicated systems, it can be overly cumbersome and even unwanted to construct high-order parametric models.
@@
 Instead, can we capture the peak gain of resonances using non-parametric models (i.e. without resorting to a global parametric model)?
+\end{question}
 
-\subsubsection{Can we avoid local minima by using smoothers?}
+\begin{question}[Can we avoid local minima by using smoothers?]
 When a parametric model is required, this often involves solving a nonlinear optimization problem.
@@
 Can non-parametric smoothers be used to help avoid such local optima?
+\end{question}
 

### 2016-05-06 ch05-initvals/initial-values.tex
Small things in CH05

@@
   \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
-  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.}
+  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\VXI}$~\legref{leg:bk1613:vxi}.}
   \label{fig:bk1613}
@@
 Additional measurements were performed using a \gls{VXI} measurement setup, which allowed for a signal-to-noise ratio of more than $60\unit{dB}$. 
-Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\mathrm{VXI}$, and used as a reference model. 
+Virtually noiseless, these measurements provided a very high quality model of the system, denoted as $G_\VXI$, and used as a reference model. 
 The \gls{VXI} measurement setup is summarized as follows.
@@
 \end{itemize}
-This yielded the model $G_\mathrm{VXI}$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.
-Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\mathrm{VXI}}$ as an initial estimate.
-Furthermore, $G_\mathrm{VXI}$ was used to play the role of $\true{G}$ from the previous section.
+This yielded the model $G_\VXI$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.
+Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\VXI}$ as an initial estimate.
+Furthermore, $G_\VXI$ was used to play the role of $\true{G}$ from the previous section.
 
 \subsection{Model Estimation}
-  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
+  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\VXI}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
   The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
@@
   \isdef 
-  \norm[2]{\model{\bullet} - G_{\mathrm{VXI}}}
+  \norm[2]{\model{\bullet} - G_{\VXI}}
   \text{.}
@@
   For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
-  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
+  $\norm{G_{\VXI}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
   The bottom plot shows a linear zoom of the top plot.
@@
   \centering
-  \caption{Observed percentiles of the validation distance $\norm[2]{\model{\bullet}-G_{\mathrm{VXI}}}$.}
+  \caption{Observed percentiles of the validation distance $\norm[2]{\model{\bullet}-G_{\VXI}}$.}
   \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
@@
 
-\section{Consequences of Selecting the `Best` Model}
+\section{Consequences of Selecting the `Best' Model}
 To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
@@
   Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
-  Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\mathrm{VXI}} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
+  Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\VXI} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
   This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
@@
 
-\section{Conclusion}\label{sec:initial-values:Conclusion}
+\section{Conclusion}
+\label{sec:initial-values:Conclusion}
 The simulations have demonstrated that use of a smoothed non-parametric estimate of the \gls{FRF} can improve the success rate of minimizing the \gls{ML} cost function for the estimation of the transfer functions of \gls{LTI} systems, subjected to noisy signals.

### 2016-05-06 ch02-qlogms/excitation-design.tex
Small stuff
Fix $\Alpha$ -> $\alpha$

@@
 \myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
-\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }
+\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}
 
@@
 
-  \subsection{Selection of the Frequency Grid Spacing $\Alpha$}
+  \subsection{Selection of the Frequency Grid Spacing $\alpha$}
   Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.

### 2016-05-06 ch02-qlogms/excitation-design.tex
Clean up math + SNR in FD in ch04

@@
             \sum_{t=1}^{N}
-              {\left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)
-               \left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)^{\T}},\\
-\frac{\partial\hat{y}(t)}{\partial\theta}
-    & =\frac{\partial G(s,\theta)}{\partial \theta}u(t).
+              {\left(\PartialDerivative{\hat{y}(t)}{\theta}\right)
+               \left(\PartialDerivative{\hat{y}(t)}{\theta}\right)^{\T}},\\
+\PartialDerivative{\hat{y}(t)}{\theta}
+    & =\PartialDerivative{G(s,\theta)}{\theta}u(t).
 \end{align}
@@
 \Fi{\theta} &= \frac{1}{\pi}
-         \int\limits_0^\infty \RealPart
-           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
-                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
-           \right\}
+         \int\limits_0^\infty
+        \real{
+                  \PartialDerivative{G(j\omega)}{\theta}
+                  \left(\PartialDerivative{G(j\omega)}{\theta}\right)^{\HT}
+         }
            \powerspec{u}(j\omega)
@@
 \begin{align}
-\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\Fi{\theta}^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
+\var{\hat{G}(j\omega)} &
+  \approx 
+  \left(\PartialDerivative{G(j\omega)}{\theta}\right)^{\HT}
+  \Fi{\theta}^{-1}
+  \PartialDerivative{G(j\omega)}{\theta}
 \label{eq:excitation:varG}
+\text{.}
 \end{align}
@@
   \begin{align}
-   \left| G\left(\wM \right) \right| & \isdef
-          \max_{\omega} \left| G\left( \omega \right)  \right|
+   \abs{G\left(\wM \right) }
+   & \isdef
+          \max_{\omega} 
+            \abs{G\left( \omega \right)}  
         = \frac{1}
@@
 \begin{align}
-\omega^\star =\frac%
-{\wn
-  \sqrt{
-    \left(1-2\damping^2\right)
-    +
-    \sqrt{\left(1-2\damping^2\right)^2+15}
-    }
-  }
-{\sqrt{5}}.
+\omega^\star =
+\frac{\wn   \sqrt{     \left(1-2\damping^2\right)      +     \sqrt{\left(1-2\damping^2\right)^2+15}    }}
+{\sqrt{5}}
 \label{eq:excitation:optFreq}
+\text{.}
 \end{align}
@@
                       \RealPart\left\{
-                          \frac{\partial G_i}
-                               {\partial \theta_i}
-                          \frac{\partial G_j^{\HT}}
-                               {\partial \theta_j}
+                          \PartialDerivative{G_i}
+                               {\theta_i}
+                          \PartialDerivative{G_j^{\HT}}
+                               {\theta_j}
                                 \right\}
@@
 
-%FIXME: clean up latex math here, e.g. \frac{\partial ...}{\partial} -> \partialDerivative{...}{...}; use \abs{}; ...
-
 The $(1,1)$ element of the $\partial G_{1,1}$ entry of the information matrix is
 \begin{align}
-  \int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
+  \int_0^\infty
+    \real{
+         \PartialDerivative{G_1}{\wn[1]}
+         \cdot
+         \PartialDerivative{G_1^{\HT}}{\wn[1]}
+    }
+      \frac{1}{\omega}
+      \dd\omega
 \end{align}
@@
 \label{eq:excitation:auto}
-\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
+\int_0^\infty
+\real{
+   \PartialDerivative{G_1}{\wn[1]}
+   \cdot
+   \PartialDerivative{G_1^{\HT}}{\wn[1]}
+   }
+\frac{1}{\omega}
+\dd\omega
  = 
@@
 \begin{gather}
-\left|\int_0^\infty\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
+\abs{
+    \int_0^\infty
+    \real{
+       \PartialDerivative{G_1}{\wn[1]}
+       \cdot
+       \PartialDerivative{G_2^{\HT}}{\wn[2]}
+    }
+    \frac{1}{\omega}
+    \dd\omega
+}
 \qquad \qquad \qquad \qquad \qquad
@@
 \leq
-\int_0^\infty\left|\RealPart\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
+\int_0^\infty
+\abs{
+  \real{
+    \PartialDerivative{G_1}{\wn[1]}
+    \cdot
+    \PartialDerivative{G_2^{\HT}}{\wn[2]}
+  }
+}
+\frac{1}{\omega}
+\dd\omega
 \leq \\
 \qquad \qquad \qquad \qquad \qquad
-\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
+\int_0^\infty
+\abs{
+  \PartialDerivative{G_1}{\wn[1]}\PartialDerivative{G_2^{\HT}}{\wn[2]}
+}
+\frac{1}{\omega}
+\dd\omega
+\label{eq:excitation:cross}
+\text{.}
 \end{gather}
@@
 \begin{align}
-\frac{\partial G_1}{\partial \wn[1]} 
-  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
+\PartialDerivative{G_1}{\wn[1]} 
+  &= 
+     \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
                {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
 \end{align}
-which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
-Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
+which has zeros in $j\omega=\Set{0, \damping\wn[1]}$. 
+Hence $\abs{\PartialDerivative{G_1}{\wn[1]} }$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
 There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
-The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.
+The shape of $\PartialDerivative{G_1}{\wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.
 
@@
 \end{align}
-where $\partial G_1^\infty = \left\|\frac{\partial G_1}{\partial \wn[1]}\right\|_\infty$. 
+where $\partial G_1^\infty = \left\|\PartialDerivative{G_1}{\wn[1]}\right\|_\infty$. 
 Again, direct calculations give
 \begin{align}
-\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \mathcal{O}(1).
-\end{align}
-Hence \eqref{eq:excitation:cross1} cannot grow faster than $\mathcal{O}(\damping^{-2})$ as $\damping\rightarrow0$. From this analysis we conclude that:
+\int_0^\infty f\left(\omega,\theta_1,\theta_2\right)\dd\omega = \frac{\wn[1]\left(2-\ln{\frac{\wn[1]^2}{\wn[2]^2}}\right)}{\wn[2]^2}\damping^{-2} + \bigO{1}.
+\end{align}
+Hence \eqref{eq:excitation:cross1} cannot grow faster than $\bigO{\damping^{-2}}$ as $\damping\rightarrow0$. From this analysis we conclude that:
 \begin{itemize}
@@
 \begin{align}
-\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
-                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
-&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
+\var{\hat{G}(\omega)} &
+\approx 
+   \PartialDerivative{G^{\HT}(e^{j\omega})}{ \theta}
+\begin{bmatrix}
+    \partial G_{1,1} &\deemph{0}\\
+    \deemph{0}&\partial G_{2,2}
+ \end{bmatrix}^{-1}
+\PartialDerivative{G(e^{j\omega})}{\theta}\\
+&=
+     \var{\hat{G}_1(\omega)} 
+  + \var{\hat{G}_2(\omega)}
+  \text{.}
 \end{align}
@@
   The choice of the damping is more important.
-  Instead of choosing the damping directly, we choose the peak gain $\left| G\left( \wM \right) \right| \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:excitation:peakAmplitude} to study the effect of differently damped systems.
+  Instead of choosing the damping directly, we choose the peak gain $\abs{ G\left( \wM \right) } \in \set{5 \unit{dB}, 10 \unit{dB}, 20 \unit{dB}, 40 \unit{dB} }$ of the transfer function \eqref{eq:excitation:peakAmplitude} to study the effect of differently damped systems.
   However, do remember that $\abs{G(\wM)} = (2\damping\sqrt{1-\damping^2})^{-1}$ for the simplifications introduced above as in \eqref{eq:excitation:peakAmplitude}.
@@
 
-  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\left| G\left( \wM \right) \right|$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
+  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.

### 2016-05-08 ch01-intro/introduction.tex
Small stuff
Reset acronyms etc. per chapter
Some cleanup, more references input design

@@
 \tikzsetfigurename{ch01fig}
+\glsresetall
 \myEpigraph{It's a dangerous business, Frodo, going out your door.
@@
 For system identification, experiment design is a question of designing input signals that will be applied to the system under test.
-Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Goodwin2006GBO}.
-On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Gevers2011ExpDesign}.
+Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Mehra1974,Goodwin2006GBO,Levadi1966}.
+On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Gagliardi1967,Karlin1966,Gevers2011ExpDesign,Zarrop1979}.
 Typically, the design is very sensitive to the prior knowledge of the system.
@@
 This leads to so-called robust optimal experiment design~\citep{Rojas2012,Goodwin2006} that construct signals that optimize the worst-case model uncertainty.
-Paradoxically, this means that for robust optimal designs, more prior knowledge, rather than less is required.
 
@@
 However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
-%TODO: peter: also discuss model selection for nonparametric here
 

### 2016-05-08 ch03-lrm/nonparametric.tex
Reset acronyms etc. per chapter
Some cleanup, more references input design

@@
 \myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
+\glsresetall
 
@@
 
-\subsection{Order Selection}
+\subsection{Local Model Order Selection}
 \label{sec:nparam:orderSelection}
@@
 
-\paragraph{Plug-in methods}
+\subsubsection{Plug-in methods}
 In plug-in methods, a goodness-of-fit criterion (e.g.
@@
 
-\paragraph{Holdout method}
+\subsubsection{Holdout method}
 The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g.
@@
 
-\paragraph{Leave-out cross-validation}
-Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
+\subsubsection{Leave-out cross-validation}
+Instead, we use a better-suited cross-validation approach known as \gls{LOOCV}.
+ that is related to the \gls{AIC}~\citep{Stone1977}.
 Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
@@
 
-\subsubsection{Combining Different Local Model Orders}
+\subsection{Combining Different Local Model Orders}
 In the previous section, different methods were introduced to select the local model order.

### 2016-05-08 ch05-initvals/initial-values.tex
Small stuff
Reset acronyms etc. per chapter
Some cleanup, more references input design

@@
 \tikzsetfigurename{ch05fig}
+\glsresetall
 \researchBasedOn{Geerardyn2015TIM}
@@
 \label{sec:initial-values:introd}
-The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
+The task of interpreting measurement data from dynamic systems often involves the estimation of a \gls{TF}. 
 Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
@@
 
-  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
-  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
+  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $\omega_{k+r}\in\LocalWindow$.
+  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $\numel{W}=3$, such that
 \begin{subequations}\label{lpmImplQuadG}
@@
 \end{subequations}
-where, in general,$r \in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,N_W\}$ and $N_W$ is a tunable parameter.
+where $r \in \LocalShifts{k}$ with $\LocalShifts{k} = \{-\numel{W},-\numel{W}+1,\dots,\numel{W}\}$ and $\numel{W}$ is a tunable parameter.
 
@@
 \begin{align}\label{eq:hRFIRdef}
-\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
+\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \conv u }^2 + \sigma^2 g^{\TT}P^{-1}g
 \end{align}
 where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
-Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
+Furthermore, $g\conv u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
 Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
@@
   \input{\thisDir/figs/distances.tikz}
-  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
-  Note that since $\norm{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
+  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
+  Note that since $\norm[2]{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
   }
@@
 Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
-First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2N_W + 1$ data points and a few degrees of freedom, i.e.
-$n_{\theta} \leq 2 N_W + 1$ or $\bigO{N_W} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
+First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2\numel{W} + 1$ data points and a few degrees of freedom, i.e.
+$n_{\theta} \leq 2 \numel{W} + 1$ or $\bigO{\numel{W}} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
 The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
-As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N N_W^3}$.
+As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N \numel{W}^3}$.
 
@@
 $200$ in this chapter) than the number of local parameters (or bandwidth) of the \gls{LPM} (e.g.
-$N_W = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
+$\numel{W} = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
 Intuitively, the local modeling methods benefit from their locality since that enables them to be flexible without a huge amount of parameters.

### 2016-05-08 ch03-lrm/nonparametric.tex
Quite some comments about PRESS

@@
                                       {47.9426 z^2 - 51.2955 z + 46.9933}
+    \label{eq:nparam:mc:system}
       \text{,}
@@
 In general, it can be seen that the \gls{LRM} performs better than \gls{LPM} unless the \gls{SNR} near the resonance is very low ($10\unit{dB}$).
-For the \gls{LPM}, it should be noted that near resonances,it more advantageous to use even model orders~\citep{Schoukens2013LPMerror}.
+For the \gls{LPM}, it should be noted that near resonances, it is more advantageous to use even model orders~\citep{Schoukens2013LPMerror}.
 The results for the $\lpm{7,4,4}$ in the previous section are representative of the best-case performance of an $\lpm{7,\order{B},\order{A}}$ technique.
@@
 
-For the \gls{LRM}, it can be seen that its model order as a significant influence on the approximation error.
+For the \gls{LRM}, it can be seen that its model order has a significant influence on the approximation error.
 In small datasets with high \gls{SNR} ($\SNR=60\unit{dB},\nBW<3$), and in datasets with low \gls{SNR} ($\SNR < 40 \unit{dB}$), selecting a better local model can reduce the bias significantly.
@@
 
-The \gls{LRIC} is not practically viable due to the high variability.
+The \gls{LRIC} is not practically viable due to its high variability.
 However, since its bias is much lower than for the other methods, \gls{LRIC} offers perspectives for improving the overall performance significantly.
 
-\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
+\begin{guideline}[Use the \glsentryshort{LRM} for resonant systems when $\SNR > 10 \unit{dB}$]
 For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
-When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
+When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a slightly better than \gls{LRM}.
 The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
@@
 
-\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
+\begin{guideline}[Use a second-order \glsentryshort{LRM} for resonant systems]
 For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
-When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
-The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
+In the assumption that difference resonances are well-separated in the frequency, a second-order \gls{LRM} (e.g. $\lrm{7,2,2,2}$) is a reliable method to estimate the \gls{FRF}.
 \end{guideline}
 
-\begin{guideline}[For long measurements, LPM and LRM are similar]
+\begin{guideline}[For long measurements, \glsentryshort{LPM} and \glsentryshort{LRM} are similar]
 For very long measurements, the difference between \gls{LPM} and \gls{LRM} becomes negligible if the different resonances are well-separated.
@@
 \section{Trading Off the Bias and Variance}
-In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
+In the last section, it was illustrated that the model order of the local \gls{LRM} models, can affect the obtained \gls{RMS} error.
 This is specifically the case for small and noisy datasets.
-Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}.
-As such, it makes sense to ask ourselves the question: ``can we determine a good local model order''?
+For larger datasets (or when $\SNR>20\unit{dB}$), the order of the \gls{LRM} plays a less significant role.
+Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}, i.e. a model order that is too high.
+As such, it makes sense to ask ourselves the question: ``can we determine a good local model order'' from the data?
 That is the question we will investigate in this section.
@@
 \label{sec:nparam:orderSelection}
-Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
+Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$  affects the quality of the obtained local models.
 For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
@@
 In the following, a short overview is given of different approaches.
+For a more complete overview, we refer to \citet{Arlot2010}.
 
@@
 \begin{equation}
-  \PRESS_{\mathrm{global}} = \sum_k \PRESS_k
+  \PRESS_{\mathrm{global}} \propto \sum_k \PRESS_k
 \end{equation}
@@
 
-\subsection{Discussion}
-
-% \begin{figure}
-%   \centering
-%   \setlength{\figurewidth}{0.85\columnwidth}
-%   \setlength{\figureheight}{0.62\figurewidth}
-%   \TODOtikzfig[PRESS and noise for single simulation]
-%   \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
-%   \label{fig:nparam:PRESS}
-% \end{figure}
+\subsection{Example}
+The system as in \eqref{eq:nparam:mc:system} has been simulated for $1\,200$ samples such that $\nBW=3$.
+Two different noise levels have been tried: one with poor $\SNR\approx10\unit{dB}$ and a better $\SNR=40\unit{dB}$.
+The resulting \gls{FRF} has been estimated with the different \gls{LRM} and \gls{LPM} estimators as in the Monte Carlo simulations.
+In \figref{fig:nparam:PRESS} the hence estimated noise variance $\sampleStd{V}$ and $\PRESS$  are shown as a function of the frequency.
+
+\begin{figure}
+  \centering
+  \setlength{\figurewidth}{0.85\columnwidth}
+  \setlength{\figureheight}{1.24\figurewidth}
+  \input{ch03-lrm/figs/tune-NBW3-pressAndNoise.tikz}
+  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the \glsentryshort{PRESS} (left plots) and the noise variance (right plots).
+The theoretical noise level is shaded and the transfer function is shown in bold.}
+  \label{fig:nparam:PRESS}
+\end{figure}
+
+For the high \gls{SNR} case, it can be seen in \figref{fig:nparam:PRESS} that the \gls{LPM} is heavily biased and hence results in a large overestimate of the noise variance near the resonance peak.
+As a result, the \gls{PRESS} in the same region is also elevated for the \gls{LPM}.
+Outside the resonance peak, the \gls{LPM} and \gls{LRM} estimate very similar noise variances.
+The \gls{PRESS} the different methods are in agreement with the observations regarding the \gls{RMS} error from the Monte Carlo simulations in \figref{fig:nparam:comparison:midSNR}: all tested \gls{LRM} perform similarly (with a slight advantage for the first-order method), the \gls{LPM} produces much larger errors near the resonance.
+Nevertheless, this figure illustrates that for the \gls{LRM}, the error is quite flat over the frequency.
+Note also that the \gls{PRESS} suffers from a quite high variance over the frequency, which is a well-known drawback~\citep{Seber2003,Arlot2010}.
+
+For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
+The values of the \gls{PRESS} are again quite noisy.
+\TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}
 

### 2016-05-09 ch01-intro/introduction.tex
Corrections Johan intro

@@
 \begin{itemize}
-  \item supermarkets try to predict how many produce their patrons will buy such that they can order a large enough supply,
+  \item supermarkets try to predict how much fruit and vegetables their regular customers buy such that they can order a large enough supply,
   \item traders on the stock market aim to predict whether companies such as Tesla or Apple will continue to prosper over the next quarter such that they can decide if it's time to buy more stock or rather sell,
@@
   \item how much electricity will the whole country use next week (do we need to start up a new power plant or not),
+  \item how much noise the bodywork of a car will produce when it is driving over a bumpy road,
+  \item what the exhaust of nitrogen oxides of a car will be for a certain operating point of a diesel engine, 
+  \item are the vibrations in a robot are small enough for it to perform very precise tasks such as positioning electronic components with sub-millimeter precision,
 \end{itemize}
@@
 Once we understand the behavior of a few systems, this offers great opportunities to understand how those systems work together or even how we can control the world around us.
-For engineers, models enable us to design larger and more complicated things than ever before.
+For engineers, models enable us to design larger and more complicated devices and constructions than ever before.
 E.g. consider a \gls{CPU} in a computer: with a few billion transistors, it is no longer possible for a sole human being to understand what every single transistor does in the grand scheme.
@@
 
-To successfully model a system, one has to delimit what part of the world one actually wants to model, i.e. the \term{system}.
-Since a system is mostly useful if it interacts with the world around it, one often also has to define \term{inputs} through which one can influence the system, and \term{outputs} which are influenced by the system.
+To successfully model a system, one has to delimit what part of the world should be captured in the model, i.e. the \term{system}.
+Since a system is mostly useful if it interacts with the world around it, one often also has to define \term{inputs} that influence the system, and \term{outputs} which are influenced by the system.
 
-Modeling can be divided into two diametrical groups depending on what one uses as a starting point.
+Modeling can be divided into two diametrical groups depending on the starting point that is assumed.
+
 \paragraph{White box}
-One the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
+On the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
 The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
-This is the typical kind of modeling practiced in school.
+This is the kind of modeling that is practiced in school, which explains why it is also popular in industry.
 Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
@@
 In many cases, one can or even has to incorporate knowledge about the physics of the system in the modeling process.
-In particular when one has black box models where some parameters are related to physical phenomena, the resulting model is called \term{`gray box'}.
+In particular black box models where some parameters are related to physical phenomena, the resulting model is called a \term{`gray box'} model.
 
@@
 Once the model structure has been chosen, its parameters are to be estimated.
-This is done by formulating an optimization problem which serves to minimize a particular cost function.
+This is often done by formulating an optimization problem which serves to minimize a particular cost function.
 The cost function is in essence a measure of the differences between the measured data and the model evaluated for particular parameter values.
-By minimizing the cost function, the optimization procedure yields parameter values that try to minimize the misfit between the data and the model.
+By minimizing the cost function, the optimization procedure yields parameter values that minimize the misfit between the data and the model.
 Unfortunately, for many identification settings, these optimization problems are non-convex~\citep{Boyd2004}.
-Practically, this means that 
 This means that initial values need to be available to start the optimization process.
@@
 Can we design a `good experiment' to identify a \gls{LTI} model?
-Particularly, this means a robust input signal needs to be constructed without relying on extensive prior knowledge of the system.
-Such a signal should cover a wide frequency band to excite all dynamics of the system during the experiment.
+Particularly, this means that a robust input signal needs to be constructed without relying on extensive prior knowledge of the system.
+Such a signal should cover a wide frequency band to excite all dynamics of interest in the system during the experiment.
 However, the signal should ensure that systems in different frequency bands can be identified with a specified level of accuracy.

### 2016-05-09 ch01-intro/introduction.tex
Some improvements in figures, consistency

@@
 \tikzsetfigurename{ch01fig}
-\glsresetall
+\glsresetall{}
 \myEpigraph{It's a dangerous business, Frodo, going out your door.
@@
 On the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
-The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
+The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchhoff's laws for electrical circuits, \latin{etc.}
 This is the kind of modeling that is practiced in school, which explains why it is also popular in industry.

### 2016-05-09 ch03-lrm/nonparametric.tex
Some improvements in figures, consistency

@@
 \myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
-\glsresetall
+\glsresetall{}
 
@@
   \input{ch03-lrm/figs/tune-NBW3-pressAndNoise.tikz}
-  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the \glsentryshort{PRESS} (left plots) and the noise variance (right plots).
+  \caption[Example: \glsentryshort{PRESS} and noise spectrum]{It is convenient to compare the \glsentryshort{PRESS} (left plots) and the noise variance (right plots) when good \gls{SNR} is available.
 The theoretical noise level is shaded and the transfer function is shown in bold.}
@@
 Nevertheless, this figure illustrates that for the \gls{LRM}, the error is quite flat over the frequency.
-Note also that the \gls{PRESS} suffers from a quite high variance over the frequency, which is a well-known drawback~\citep{Seber2003,Arlot2010}.
+Note also that the \gls{PRESS} suffers from a quite high variance over the frequency, which is a well-known drawback~\citep{Arlot2010}.
 
 For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
-The values of the \gls{PRESS} are again quite noisy.
+The values of the \gls{PRESS} are again very noisy.
 \TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}
@@
 Hence, expressions for the bias of the \gls{LRM} were derived.
-%TODO: tom: "inherently biased": verregaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
 For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.

### 2016-05-09 ch04-lrmhinf/lrmhinf.tex
Clean up math + SNR in FD in ch04
Some improvements in figures, consistency

@@
 \researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
-\glsresetall
+\glsresetall{}
 
@@
 \newcommand{\TsValue}{\ensuremath{1 \unit{s}}}
-
-% \section{Introduction}
-% \label{sec:lrmhinf:Intro}
 
@@
 The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
-% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
-% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.
 
@@
 Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.
-
-%\glsresetall
 
@@
 
-We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
-For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.
+We denote $\lrm{N_W,\order{B},\order{A},\order{T}}$ to be the \gls{LRM} with the orders $\order{B}$, $\order{A}$, $\order{T}$ and bandwidth $N_W$ defined above.
+For $\order{A}=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,\order{B},\order{T}}$.
 
@@
 of $10$ is obtained.
-%TODO: give the SNR also in frequency domain
+In the frequency domain, this corresponds to $\SNR_{\BW} \approx 26 \unit{dB}$ in the $3\unit{dB}$ bandwidth of this resonance peak.
 
@@
            {\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} U_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
-  \
 \end{equation}
@@
 \figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
-The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($N_B=1$). 
+The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($\order{B}=1$). 
 Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.
@@
   \input{\thisDir/figs/example-both.tikz}
-  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
-  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  \caption[Example: \glsentryshort{FRF} underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
   Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
-  Hence, $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
+  Hence, $\widehat{\infnorm{\Delta_{\LRM}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
   \label{fig:lrmhinf:exampleIntergrid}
@@
 
-It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
+It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\LRM}} = 24$ in the simulation.
 Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
@@
   \caption[Estimated $\gamma$ versus measurement time.]{This Monte Carlo simulation shows that the $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
-  However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
+  However, the proposed $\widehat{\infnorm{\Delta_{\LRM}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$).
 A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}.

### 2016-05-09 ch05-initvals/initial-values.tex
Some improvements in figures, consistency

@@
 \begin{align}\label{eq:hRFIRdef}
-\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \conv u }^2 + \sigma^2 g^{\TT}P^{-1}g
+\hat g_{\RFIR} &= \argmin_{g} \norm[2]{y - g \conv u }^2 + \sigma^2 g^{\TT}P^{-1}g
 \end{align}
@@
 Furthermore, $g\conv u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
-Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
+Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\RFIR}$ can be computed analytically in a single step.
 The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
@@
 \end{equation}
- for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
+ for $t_1,t_2 \in \set{0,1,\cdots,n_h - 1}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$.
  The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes~\citep{Carlin2000,Gelman2014}, i.e.
@@
 ~\citep{Pillonetto2010,Chen2012}. 
-The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the \gls{FRF}.
+The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\RFIR}$ of the system yields a smoothed estimate of the \gls{FRF}.
 \end{enumerate}
@@
 \begin{equation}
-  U_{\mathrm{FRF}}(\omega_k) \isdef 1 
+  U_{\FRF}(\omega_k) \isdef 1 
   \qquad \text{and} \qquad
-  Y_{\mathrm{FRF}}(\omega_k)  \isdef G_{\bullet}(\omega_k)
+  Y_{\FRF}(\omega_k)  \isdef G_{\bullet}(\omega_k)
   \text{.}
@@
 \begin{equation}
-    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm{\true{G}}}{\SNR} 
+    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm[2]{\true{G}}}{\SNR} 
     \label{eq:heur-RMSE}
@@
 It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
-When the RMSE is then divided by $\norm{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
+When the RMSE is then divided by $\norm[2]{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
 
@@
   \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
-  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\VXI}$~\legref{leg:bk1613:vxi}.}
+  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and their average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\VXI}$~\legref{leg:bk1613:vxi}.}
   \label{fig:bk1613}
@@
   For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
-  $\norm{G_{\VXI}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
+  $\norm[2]{G_{\VXI}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
   The bottom plot shows a linear zoom of the top plot.

### 2016-05-09 ch03-lrm/truncation.tex
Truncation: labels uniform

@@
 \researchBasedOn[This section]{Lumori2014TIM}
-%FIXME: {labels into standardized form}
 
@@
 
-\begin{assumption}\label{ass:imprespdecay}
+\begin{assumption}\label{ass:trunc:impulseReponse:decay}
 The impulse response $g(t)$ decays exponentially over time, i.e. 
@@
 
-\begin{assumption}\label{ass:decay90perctime}
-Within $90\%$ of the measurement window, the impulse response decays
- to a level that is indistinguishable from the noise.
+\begin{assumption}\label{ass:trunc:impulseResponse:lastSegmentNoise}
+Within $90\%$ of the measurement window, the impulse response decays to a level that is indistinguishable from the noise.
 \end{assumption}
 
-Note that \assref{ass:imprespdecay} and \assref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.
+Note that \assref{ass:trunc:impulseReponse:decay} and \assref{ass:trunc:impulseResponse:lastSegmentNoise} exclude the possibility of considering a system that is a pure integrator.
 
@@
 
-According to \assref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by \assref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the    average value of the impulse response.
+According to \assref{ass:trunc:impulseReponse:decay}, the true impulse response tends to zero asymptotically; and by \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the    average value of the impulse response.
 The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
@@
 The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
-  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
+  By \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
 
@@
 \end{align}
-This is valid, as per \assref{ass:decay90perctime}.
+This is valid, as per \assref{ass:trunc:impulseResponse:lastSegmentNoise}.
 
@@
 \label{sec:nparam:trunc:conclusion}
-
 This section introduced a time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 

### 2016-05-09 ch03-lrm/truncation.tex
Improve list of symbols

@@
 \begin{equation}\label{eq:nparam:trunc:LPM:TD}
-y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
+y(t)=\true{G}(q)u_0(t)+\true{H}(q)e(t)=\true{G}(q)u_0(t)+v(t)
 \end{equation}
-where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
+where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
 
@@
 % The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
-% The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
+% The filtered white noise $v(t) = \true{H}(q)e(t)$ is the disturbing noise source at the output.
 % \end{assumption}
@@
 % \begin{equation}\label{lpm1spectra}
-% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
+% Y(k)=\true{G}(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
 % \end{equation}
-% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term.
+% where $V_0(k) = \true{H}(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term.
 The latter is the sum of the system and the noise leakage terms, i.e.

### 2016-05-09 config/glossaries.inc.tex
Some stuff, here and there
Some cleanup, more references input design
Improve list of symbols

@@
 
-\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
-\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
-\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
-\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
-\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
-\newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
-\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
-\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
-\newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}
+\newsymbolglos{A1-SetN}{\NaturalNumbers}{Set of the natural numbers}
+\newsymbolglos{A2-SetZ}{\IntegerNumbers}{Set of integer numbers}
+\newsymbolglos{A3-SetQ}{\RationalNumbers}{Set of the rational numbers}
+\newsymbolglos{A4-SetR}{\RealNumbers}{Set of the real numbers}
+\newsymbolglos{A5-SetC}{\ComplexNumbers}{Set of the complex numbers}
+\newsymbolglos{A6-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
+\newsymbolglos{A7-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
+\newsymbolglos{A8-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
+\newsymbolglos{A9-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}
 
 \newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
+\newsymbolglos{B-w}{\omega}{Frequency ($\unit{Hz}$) or angular frequency ($\unit{rad/s}$)}
 % \newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}
+\newsymbolglos{B-sys-damping}{\damping}{Relative damping of a pole or system}
+\newsymbolglos{B-sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
+\newsymbolglos{B-sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}
+\newsymbolglos{B-sys-shiftoperator}{q}{Forward shift operator ($qu(t) = u(t+1)$)}
+\newsymbolglos{B-sys-laplaceoperator}{s}{Laplace variable}
 
@@
 \newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}
+\newsymbolglos{count-window}{\nWind}{Bandwidth of local window}
+\newsymbolglos{count-order}{\order{A},\order{B},\order{C}}{Order of local models $\LocalModel{A}, \LocalModel{B},\LocalModel{C}$}
 
 \newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
-\newsymbolglos{E-bydef}{\isdef}{is defined as \ldots}
+\newsymbolglos{E-def}{\isdef}{is defined as \ldots}
+\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
+\newsymbolglos{E-equiv}{\equiv}{is equivalent with \ldots}
 \newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
-\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
 \newsymbolglos{E-ll}{\ll}{is much smaller than \ldots}
@@
 
-\newsymbolglos{lcm}{\lcm}{Least common multiple}
+\newsymbolglos{F-lcm}{\lcm}{Least common multiple}
+\newsymbolglos{F-ln}{\ln}{Natural logarithm}
+\newsymbolglos{F-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
 
-\newsymbolglos{matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
-\newsymbolglos{matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
-\newsymbolglos{matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}
+\newsymbolglos{G-statOperator-bias}{\bias{\placeholder}}{Bias of \placeholder}
+\newsymbolglos{G-statOperator-var}{\var{\placeholder}}{Variance of \placeholder}
+\newsymbolglos{G-statOperator-exp}{\E{\placeholder}}{Expected value of \placeholder}
 
-\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
-\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
-\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
+\newsymbolglos{M-matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
+\newsymbolglos{M-matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
+\newsymbolglos{M-matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}
 
-\newsymbolglos{operator-bias}{\bias{\placeholder}}{Bias of \placeholder}
-\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
-\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
-\newsymbolglos{operator-exp}{\E{\placeholder}}{Expected value of \placeholder}
-\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
-\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
-\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
-\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
-\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
-\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
-\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
-\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
-\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
-\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
-\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
-\newsymbolglos{operator-var}{\var{\placeholder}}{Variance of \placeholder}
+\newsymbolglos{O-matrix-operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
+\newsymbolglos{O-matrix-operator-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
+\newsymbolglos{O-matrix-operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
+\newsymbolglos{O-matrix-operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
+\newsymbolglos{O-operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
+\newsymbolglos{O-operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
+\newsymbolglos{O-operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
+\newsymbolglos{O-operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
+\newsymbolglos{O-operator-bigO}{\bigO{\placeholder}}{Bachmann-Landau ``big oh'' notation for the order of a function}
 
-\newsymbolglos{sys-damping}{\damping}{Relative damping of a pole or system}
-\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
-\newsymbolglos{sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}
+\newsymbolglos{P-product-kron}{\kron}{Kronecker product of matrices (\code{kron})}
+\newsymbolglos{P-product-conv}{\conv}{Convolution}
+\newsymbolglos{P-product-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
 
-\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}
+\newsymbolglos{N-norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
+\newsymbolglos{N-norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
+\newsymbolglos{N-norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
 
 %% ACRONYMS
-\setulcolor{gray}
-%\newcommand{\abbrev}[1]{\ul{#1}}
-\newcommand{\abbrev}[1]{#1}
-
 \newacronym{ADC}{ADC}{analog-to-digital converter}
@@
 
-\newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
+\newacronym{BLA}{BLA}{best linear approximation}
 \newacronym{BK}{B\&K}{\bruelkjaer}
 \newacronym{BNC}{BNC}{Bayonet Neill-Concelman (connector)}
-\newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}
+\newacronym{BTLS}{BTLS}{bootstrapped total least squares}
 
-\newacronym{CDF}{CDF}{cumulative distribution function}
+\newacronym{CDF}{CDF}{cumulative density function}
 \newacronym{CPU}{CPU}{central processing unit}
@@
 \newacronym{DAQ}{DAQ}{data acquisition}
-\newacronym{DC}{DC}{direct current (also: mean value)}
+\newacronym{DC}{DC}{static}
 \newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
@@
 
-\newacronym{PDF}{PDF}{probability distribution function}
+\newacronym{PDF}{PDF}{probability density function}
 \newacronym{PI}{PI}{proportional-integral}
@@
 \newacronym{RAM}{RAM}{random-access memory}
-\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
+\newacronym{RARX}{RARX}{regularized auto-regressive exogenous}
 \newacronym{RCF}{RCF}{right co-prime factorization}
-\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
-\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
-\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}
+\newacronym{RFIR}{RFIR}{regularized finite impulse response}
+\newacronym{RMS}{RMS}{root-mean-square}
+\newacronym{RMSE}{RMSE}{root mean squared error}
 
@@
 \newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
-\newacronym{VXI}{VXI}{\abbrev{V}ME e\abbrev{x}tensions for \abbrev{i}nstrumentation}
+\newacronym{VXI}{VXI}{VME extensions for instrumentation}
 

### 2016-05-09 ch04-lrmhinf/lrmhinf.tex
Some common commands introduced

@@
 \begin{enumerate}
-  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
+  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\FRF}$ is observed directly on the discrete frequency grid,
   \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
@@
 
-The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citet{vandeWal2002}.
-However, when the measurement time is finite, the expected value of  $\gamma_{\mathrm{FRF}}$  for different realizations of the input signal and noise, may underestimate the actual peak gain $\gamma$, i.e.
+The use of $\gamma_{\FRF}$ is standard in \gls{FRF}-based approaches, e.g.~\citet{vandeWal2002}.
+However, when the measurement time is finite, the expected value of  $\gamma_{\FRF}$  for different realizations of the input signal and noise, may underestimate the actual peak gain $\gamma$, i.e.
 $\expectedValue{\gammaAtGrid} \leq \gamma$.
@@
 
-\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
+\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\FRF}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
 The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($\order{B}=1$). 
@@
   \input{\thisDir/figs/example-both.tikz}
-  \caption[Example: \glsentryshort{FRF} underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
-  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
+  \caption[Example: \glsentryshort{FRF} underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\FRF}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
+  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\FRF}$) and intergrid~($\gammaIntergrid$) estimate are improved.
   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
@@
 To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
-The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
+The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\FRF}(N)}$ is a non-decreasing function of $N$.
 This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
@@
 The proposed method \eqref{eq:lrmhinf:gammaInterpolOptim} yields $\gammaIntergrid=-2.5\unit{dB}$.
-$\gamma_{\mathrm{FRF}}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
+$\gamma_{\FRF}\approx -9.9\unit{dB}$ for the estimation data, which means that a $7.4\unit{dB}$ improvement is achieved by the proposed method.
 This peak agrees well with the validation data, where the nearest (at-grid) value has an amplitude of $-3.2\unit{dB}$ (i.e. $8\%$ difference).

### 2016-05-09 ch03-lrm/nonparametric.tex
Inline truncation.tex

@@
 \section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}
-\input{\thisDir/truncation.tex}
+\label{sec:nonparametric:truncation}
+\researchBasedOn[This section]{Lumori2014TIM}
+
+The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
+The smoothing of the \gls{FRF} happens by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction.
+The truncation point (cut-off index) is determined by one of two statistically inspired methods.
+It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.
+It should be noted, however, that such smoothing is merely of importance when inspecting the \gls{FRF} visually.
+In particular, a slight bias might be incurred when smoothing the \gls{FRF}.
+If one is to fit a parametric model to the smoothed \gls{FRF}, one essentially ends up with a biased model (which is often undesirable).
+
+Based on \citet{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
+A \gls{SISO} \gls{LTI} system is considered.
+The input signal is a known random noise signal and the output signal is corrupted by measurement noise.
+This is depicted in \figref{fig:nparam:blockH0} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
+\begin{equation}\label{eq:nparam:trunc:LPM:TD}
+y(t)=\true{G}(q)u_0(t)+\true{H}(q)e(t)=\true{G}(q)u_0(t)+v(t)
+\end{equation}
+where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
+
+Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector~\citep{Ljung1999,Soderstrom1989}.
+In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.
+
+The following  choices are made:
+
+\begin{itemize}
+
+\item The work in this section is for discrete-time systems. 
+Denote the $k^{\text{th}}$ discretized frequency as $\omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $\fs$ the sample frequency and $N$ the total number of sample points.
+
+\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\omega_k)$  at the $k^{\text{th}}$ frequency.
+
+\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\omega_k)$ at the $k^{\text{th}}$ frequency.
+
+\end{itemize}
+
+The rest of the section is structured as follows. 
+\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
+Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following \gls{FRF} estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.
+
+These \gls{FRF} estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
+Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.
+
+% \begin{assumption}
+% The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\citep{Schoukens2009LPM}.
+% \end{assumption}
+
+% In other words, for the excitation signal to be rough: the magnitude of the spectral difference $|U_0(k+1) - U_0(k)|$ must have a probability of 1 (unity) for it to remain in the same order of magnitude as $|U_0(k)|$, irrespective of the record length $N\rightarrow\infty$ and the corresponding  frequency resolution $f_0\rightarrow{0}$.
+
+% \begin{assumption}
+% The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
+% The filtered white noise $v(t) = \true{H}(q)e(t)$ is the disturbing noise source at the output.
+% \end{assumption}
+
+% \subsubsection{The Hanning Window and the \glsentrytext{LPM}}
+% \label{sec:nparam:trunc:LPMFRFest}
+% \paragraph{Windowing}
+% The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
+% In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
+% Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.
+
+% The anomalies due to interpolation errors, associated with windowing, can easily be mitigated or circumvented by use of the \gls{LPM}. 
+% As shown in \citep{Pintelon2012}, the leakage errors are reduced from  $\bigO{{N}^{-1}}$, for Hanning windowing, to $\bigO{{N}^{-3}}$ or better, for the \gls{LPM}.
+
+% \paragraph{Formulation of the Linear LS LPM}
+% The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
+% \citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
+% The formulation in this section is a summary for a \gls{SISO} system.
+
+% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \latin{viz}:
+% \begin{equation}\label{lpm1spectra}
+% Y(k)=\true{G}(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
+% \end{equation}
+% where $V_0(k) = \true{H}(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term.
+The latter is the sum of the system and the noise leakage terms, i.e.
+$T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.
+
+In this section, the $\lpm{3,2,2}$ is used.
+However, since the techniques discussed in this section are not specifically geared towards the \gls{LPM}, one can just as well use the concepts with other non-parametric \gls{FRF} estimators such as the \gls{LRM}.
+
+\subsection{Smoothing the \glsentryshort{FRF} estimate}
+\label{sec:nparam:trunc:smoothingFRFestimate}
+The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions.
+After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures (see \figref{fig:nparam:truncation:workflow}), which will be elaborated on later:
+\begin{enumerate}
+\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.
+
+\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response and this is subtracted from the impulse response.
+
+\item From the estimated impulse response $\hat{g}(t)$, the noise floor is estimated.
+
+\item Assuming that the impulse response decays with the passing of time, the noise is bound to predominate after a certain time interval. 
+In particular, when $t > \truncTime$, the impulse response has decayed below the noise floor.
+In \secref{sec:nonparametric:truncation:ftest} and \secref{sec:nonparametric:truncation:exponentialfit}, two approaches are introduced to estimate $\truncTime$.
+
+\item A truncation is effected at the point beyond which the estimated impulse response is buried in noise.
+This action results in smoothing of the \gls{FRF} when the truncated impulse response is transformed to the frequency domain using the \gls{DFT}.
+\end{enumerate}
+
+\begin{figure}
+   \centering
+   \setlength{\figurewidth}{0.75\columnwidth}
+   \includegraphics[width=\figurewidth]{\thisDir/figs/workflow-truncation.pdf}
+   \caption{Workflow for impulse response truncation.}
+   \label{fig:nparam:truncation:workflow}
+ \end{figure}
+
+These procedures require that the following assumptions are satisfied.
+
+\begin{assumption}
+The estimate $\hat G_{\LPM}(\omega_k)$ is available at all frequencies $\omega_k$ for $k\in\{1,2,\dots,N/2\}$.
+\end{assumption}
+
+This assumption ensures that the impulse response corresponding to the \gls{FRF} can be computed (up to its mean value).
+It requires that the input signal excites the whole unit circle.
+This is satisfied, for instance, by using white noise as an excitation signal.
+
+\begin{assumption}\label{ass:trunc:impulseReponse:decay}
+The impulse response $g(t)$ decays exponentially over time, i.e. 
+\[
+  \exists A \in \PositiveRealNumbers, 
+  \exists a > 0 ,
+  \exists t_0 > 0,
+  \forall t > t_0: 
+     \abs{g(t)} \leq A \exp(- a t) \text{.}
+\]
+\end{assumption}
+
+\begin{assumption}\label{ass:trunc:impulseResponse:lastSegmentNoise}
+Within $90\%$ of the measurement window, the impulse response decays to a level that is indistinguishable from the noise.
+\end{assumption}
+
+Note that \assref{ass:trunc:impulseReponse:decay} and \assref{ass:trunc:impulseResponse:lastSegmentNoise} exclude the possibility of considering a system that is a pure integrator.
+
+\subsection{Obtaining the Impulse Response Function}
+
+The estimated impulse response function  $\hat g_{{\LPM}\without \DC}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF}, \latin{viz}:
+\begin{align}\label{eq:impRespiDFT}
+\hat g_{{\LPM}\without \DC}(t) 
+&= 
+\frac{1}{\sqrt{N}}
+\sum_{k=1}^{N-1}
+\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
+\end{align}
+where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
+\begin{align}
+\hat G_{\LPM}(\omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
+\end{align}
+(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.
+
+Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
+Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:LRM} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\without\DC$'' in equation \eqref{eq:impRespiDFT}.
+Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
+This limitation is lifted by developing a simple estimator of the mean value, presented below.
+
+\subsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
+The correct mean value of the impulse response accounts for (i.e.
+estimates) the \gls{DC} value of the \gls{FRF}.
+A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}.
+%The first is a frequency-domain technique and the second is a time-domain technique.
+
+According to \assref{ass:trunc:impulseReponse:decay}, the true impulse response tends to zero asymptotically; and by \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the    average value of the impulse response.
+The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
+To this end, the following procedure is executed:
+
+\begin{enumerate}
+\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{{\LPM}\without \DC}(t)$, estimated by the \gls{LPM}, as %$\hat g_{\LPM}(t)$ as
+\begin{align}
+   m_{g10} 
+   = 
+   \frac{1}{\lceil0.1N - 1\rceil}
+   \sum_{t=\lfloor0.9N\rfloor}^{N-1}
+      \hat g_{{\LPM}\without \DC}(t)
+\end{align}
+
+\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\without \DC}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \latin{viz}:
+\begin{align}
+\hat g_{\LPM}(t) = \hat g_{{\LPM}\without \DC}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
+\end{align}
+\end{enumerate}
+
+\subsection{Determining the Truncation Time of the Impulse Response}
+In this section, two methods will be discussed to determine the truncation time, i.e. the time beyond which the measured impulse response cannot be separated from the noise level.
+Specifically, the first method uses an $F$-test to distinguish between signal and noise.
+The second method fits an exponential through a well-chosen subset of the data to obtain $\truncTime$.
+
+\subsubsection{Truncation Via the $F$-Test}
+\label{sec:nonparametric:truncation:ftest}
+To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_{\LPM}$ is split into smaller segments.
+One can then gradually determine if in each of these segments, the observed impulse response is dominated by the noise.
+
+% 1) cut into NS segments of minimally NM samples
+% 2) assume last segment == noise
+%    start from back
+% 3) F-test on Var, Var==RMS if dc == 0 (i.e. noise)
+%    H0: s²(1) =  s²(2)
+%    H1: s²(1) >  s²(2)
+%    alpha >> ==> beta <<
+% 4) if H1 and RMS(signal)/RMS(noise) < f
+%    robustness, SNR
+%    select segment i
+% 5) refine until wanted resolution is obtained
+
+\begin{enumerate}
+  \item The impulse response $\hat{g}_{\LPM}(t)$ is split into $N_S$ segments of approximate equal lengths
+$L_S = \floor{\frac{N}{N_S}}$. 
+If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
+The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
+  By \assref{ass:trunc:impulseResponse:lastSegmentNoise}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.
+
+  \item Iteration is then carried out from the last segment ($i = N_S$) towards the beginning of the impulse response.
+To determine whether the preceding segment $\segm{\hat{g}}{i-1}$ is completely dominated by noise,  both an $F$-test and an absolute criterion on the RMS are used.
+
+  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
+  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
+  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
+  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \latin{viz}:
+  \begin{equation}
+    s^2(i) 
+    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
+    = \left( \rms{\hat{g}^{[i]}} \right)^2
+           \text{.}
+  \end{equation}
+  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
+  \begin{align}
+     \nullHypothesis &: s^2(i-1) = s^2(i)\\
+     \altHypothesis    &: s^2(i-1) > s^2(i)
+     \text{.}
+  \end{align}
+  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
+  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
+  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
+  In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
+  \begin{equation}
+    F \isdef \frac{s^2(i-1)}{s^2(i)} \geq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
+  \end{equation}
+  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
+  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.
+
+  The high level of confidence ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$~\citep{Parsons1974}.
+  In our case, such an error means that a part of the actual impulse response would be falsely classified as noise, which could significantly increase the bias as information of the system is discarded.
+  A Type~I error is less detrimental since, in that case, noise is falsely classified as a signal component and kept in the impulse response, thereby causing a sub-optimal value of the variance of the estimate.
+  As the \gls{LPM} samples are correlated over a short frequency span, the actual noise present in $\hat{g}$ may be slightly non-stationary.
+  To cope with this, one can introduce other criteria which must be satisfied together with the outcome of the $F$-test.
+  A criterion that shows good results is to check whether the segment $\segm{\hat{g}}{i-1}$ has an RMS value that is at least a factor $\kappa$ larger than the RMS of the noise.
+  Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed. 
+%  \JL{Q: doesn't this increase the probability of a Type II error?}
+%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}
+
+  \item This procedure is repeated until a segment $\segm{\hat{g}}{\starred{i}-1}$ is found that is dominated by the actual impulse response according to the outcome of the $F$-test and the absolute \gls{RMS} value of the segment.
+  At that point, it is very likely that the transition from noise to the actual impulse response happens within the segment $\segm{\hat{g}}{\starred{i}-1}$.
+  One now has the choice to accept the last sample of $\segm{\hat{g}}{\starred{i}-1}$ to be the last meaningful sample $\truncTime$ for the impulse response.
+  The accuracy of this estimate is limited by the length of the segment $L_S$.
+
+  \item
+  A more accurate estimate can be obtained by dividing the segment $\segm{\hat{g}}{\starred{i}-1}$ -- which may contain both the signal and noise -- yet again into smaller segments.
+  The procedure described above is then repeated until a satisfactory, accurate $\truncTime$ is obtained, or until the subsegments have a length that is too short ($L_{S\min} = 10$) to guarantee the accuracy of the RMS values.
+%rely on the RMS values to be accurate.
+  To start this refinement, the last $\segm{\hat{g}}{\starred{i}}$ should be used to compare the RMS with the $F$-test, since the last subsegment of $\segm{\hat{g}}{\starred{i}-1}$ cannot be asserted to be dominated by noise.
+
+\end{enumerate}
+This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following equations:
+\begin{subequations}
+\label{eq:trunc:systemODEs}
+\begin{align}
+y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
+y(t)       &= y_0(t) + e(t),
+\end{align}
+\end{subequations}
+where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $78.2\unit{dB}$.
+The figure shows segments of the estimated impulse response.
+The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions.
+The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.
+
+\begin{figure}[tbh]
+\centering
+ \setlength\figurewidth{0.68\columnwidth}
+ \setlength\figureheight{0.68\figurewidth}
+  \input{\thisDir/figs/truncRMS.tikz}
+\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.}
+\label{fig:nparam:trunc:nonparametric:truncation:Ftest}
+\end{figure}
+
+\subsubsection{Truncation Via Exponential Fitting}
+\label{sec:nonparametric:truncation:exponentialfit}
+
+The \gls{FRF} estimate is smoothed by truncating the estimated impulse response function. 
+The truncation is applied at the time index beyond which the signal is indistinguishable from the noise.
+
+This is done via the fit of an exponential function on the maxima of the impulse response, implemented as follows.
+
+\begin{enumerate}
+\item Obtain the estimate of the impulse response $\hat g_{\LPM}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{sec:nparam:trunc:DCvalueEst}. 
+Henceforth, $\hat g_{\LPM}(t)$ will simply be denoted as $\hat g(t)$.
+
+\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \latin{viz}:
+\begin{align}
+\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
+\end{align}
+This is valid, as per \assref{ass:trunc:impulseResponse:lastSegmentNoise}.
+
+%This assumes that the impulse response of the system is not longer than 90\% of the length of the measured time interval.
+
+\item Obtain $\mathbb{T}_\mathrm{HSNR}$ as the set of time instants where $\hat g(t)$ is significantly above the standard deviation of the noise.
+Only samples with absolute values of at least $5\hat\sigma_\mathrm{n}$ are retained: %Only samples with an absolute value of at least $5\hat\sigma_\mathrm{n}$ have been retained:
+\begin{align}
+\mathbb{T}_\mathrm{HSNR} = \left\{
+t:|\hat g(t)|\geqslant 5\hat\sigma_\mathrm{n}
+\right\}.
+\end{align}
+(Subscript HSNR stands for High \gls{SNR}.)
+
+%This choice leaves a probability of $6\times10^{-7}$ of retaining a pure noise sample, in the case of Gaussian noise.
+
+\item Find the set $\mathbb{T}_\mathrm{max}$ of indices corresponding to monotonically decreasing maxima of the impulse response:
+\begin{align}\label{eq:TmaxDef}
+\mathbb{T}_\mathrm{max} = \left\{
+t: \left| \hat g(t)\right|>
+\left|\hat g(t')\right|,
+t < t' < N \land t'\in\mathbb{T}_\mathrm{HSNR}
+\right\},
+\end{align}
+
+\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. 
+This is done by solving the following expression
+\begin{align}\label{eq:expFit}
+\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
+\end{align}
+for $\ln A$ and $a$ in a least squares sense.
+This is a quadratic problem in the parameters and, thus, amount to a convex optimization problem that can be solved directly.
+Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
+
+\item
+Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \latin{viz}:
+\begin{align}\label{eq:truncTimeExpFit}
+\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
+\end{align}
+where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below.
+
+\item
+ Truncate the estimated impulse response for $t \geqslant \truncTime$.
+
+\end{enumerate}
+
+\begin{figure}[tbh] %top bottom here
+\centering
+\setlength\figurewidth{0.85\columnwidth}
+\setlength\figureheight{0.68\figurewidth}
+\input{\thisDir/figs/expfit.tikz}
+\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
+\label{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}
+\end{figure}
+
+As an illustration, this procedure was applied to the noisy impulse response of the system described by the following difference equation:
+
+\begin{equation}
+y_0(t) = 2.583y_0(t - 1) -2.176y_0(t - 2)+0.592y_0(t-3) + u(t)
+\end{equation}
+
+The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
+The result is depicted in \figref{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}. 
+An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
+The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e.
+$\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
+
+\paragraph*{Considerations on the choice of $\gamma$}
+
+\begin{itemize}
+\item The tuning parameter $\gamma$ is application- and system-dependent.  A higher value lowers the variance of the estimated \gls{FRF}, but increases its bias, and vice versa.
+
+\item The bias error is highest in the vicinity of (sharp) resonance peaks. 
+If the latter is to be estimated with a high accuracy, a value $\gamma \ll 1$ must be used.
+
+\item If one is interested in obtaining a smooth initial estimate of the \gls{FRF}, a (small) bias error is acceptable, and choosing $\gamma \approx 1$ was found to be a good rule of thumb.
+\end{itemize}
+
+\subsection{Simulation Results}
+\label{sec:nparam:trunc:simResults}
+
+\figref{fig:nparam:trunc:LPMvsTRunc} and \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
+Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
+They were obtained from simulations on the system in \eqref{eq:trunc:systemODEs} where the noise variance was set such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.
+
+\begin{figure}
+    \centering
+    \setlength\figurewidth{0.85\columnwidth}
+    \setlength\figureheight{0.68\figurewidth}
+    \input{\thisDir/figs/figLPMvsTRunc.tikz}
+    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{The bias $\sampleBias{\placeholder}$ and standard deviation $\sampleStd{\placeholder}$ of the \gls{FRF} estimates using both the \gls{LPM} (blue) and truncated~\gls{LPM} (red) are shown.
+    It can be seen that the truncation reduces the variance at the cost of an increased bias, however, the overall \gls{RMS} error is reduced by the truncation.}
+    \label{fig:nparam:trunc:LPMvsTRunc}
+\end{figure}
+
+In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
+\begin{itemize}
+\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.
+Note also that the improvement in variance is proportional to the measurement time, i.e.
+\begin{equation}
+  \frac{\sampleStd{\trunc}}{\sampleStd{\LPM}} \approx \sqrt{\frac{\truncTime}{\Tm}}
+\end{equation}
+where $\Tm$ is the total measurement time.
+Equivalently, this means that for \glspl{FRF} estimated with a finer frequency resolution, are improved more by truncation than coarsely spaced \glspl{FRF}.
+
+\item an increase of the bias of the truncated estimate, especially in the vicinity of the resonance frequency.
+Still, this bias lies below the variance of the non-truncated estimate.
+As such, for a single experiment, the increase in bias still yields a better estimate when truncation is invoked.
+
+This bias depends on the time instant at which the truncation is performed, as discussed below.
+
+\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
+It is, however, advised to use the raw data instead of such smoothed \glspl{FRF} to estimate a parametric model such that no bias is introduced into the parametric estimate.
+In \chapref{sec:initvals}, however, it will be shown that smoothed \glspl{FRF} can lead to improved starting values.
+
+\end{itemize}
+
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/pdfs.tikz}
+         \caption[RMS error of the FRF versus truncation time.]{
+         The left y-axis shows the \gls{RMS} error of the estimated \gls{FRF} as a function of the chosen truncation time $\truncTime$.
+         The corresponding optimal $\truncTime$ is indicated as well.
+         Both bar plots (right y-axis) indicate for $\nMC =1000$ realizations of the disturbing noise and excitation signal, the number of times that $\truncTime$ has been selected by means of either the method using the $F$-test or the method that fits an exponential.
+         It can be seen that both methods allow to almost halve the \gls{RMS} error and approach the optimal truncation time.}
+   \label{fig:nparam:trunc:pdfAndRMSeVStruncTime}
+\end{figure}
+
+In \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime}, the \gls{RMS} error of the estimated \gls{FRF} (without the \gls{DC} value) as a function of the time $\truncTime$ at which the impulse response is truncated, is shown.
+To the left of the optimal truncation length, the \gls{RMS} error increases steeply.
+In that region, one is essentially using a overly simplified impulse response to represent the system and hence the \gls{RMS} error is dominated by the bias error.
+To the right hand side of the minimum, the \gls{RMS} error increases more gradually, due to an increase of the noise variance.
+
+A good practice would be to truncate the impulse response at the minimizer (black dot) of the \gls{RMS} error. 
+However, this minimizer is unknown in practice, since it depends on the true underlying system.
+Nevertheless, the proposed approaches provide a reasonable way to approximate the optimal truncation length.
+
+The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}. 
+This was done on $1000$ realizations of the noise, and depicted in \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} by the histogram.
+Clearly, both methods for selecting the truncation time $\truncTime$ have a good overall performance, based on the mode of their distribution (around the $90^{\text{th}}$ sample).
+
+For the $F$-test based method, the obtained $\truncTime$ values only take a discrete set of values due to the limitation of the segment length.
+While most trials result in $\truncTime \in \Set{70, 80, 90}$, a few outliers with much higher truncation times can be observed.
+These outliers can be attributed to the high power of the $F$-tests.
+
+For the exponential fitting approach, however, a closely grouped set of (continuous) values for $\truncTime$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.
+Although this distribution has a mode that is quite a bit higher than the method using the $F$-test, due to the absence of outliers, this method is more reliable to use for the particular system that we studied.
+
+From the plot, we can conclude that the \gls{RMSE} increases rapidly when $\truncTime$ is smaller than the optimal.
+On the other hand, selection of a value of $\truncTime$ that is too large, is not nearly as detrimental to the modeling error.
+The graph also shows that the \gls{RMSE} of the model can be decreased from $0.62$ (without truncation) to $0.18$ when the optimal truncation is applied. 
+Also, one observes a low sensitivity of the \gls{RMSE} w.r.t.~$\truncTime$, when truncating at times beyond that optimum. 
+Therefore, a somewhat conservative truncation method is still likely to yield a close to optimal result.
+
+\paragraph{Interaction of the truncation method and the system properties}
+As seen in the previous simulation example, the exponential fitting method is well-suited to determine $\truncTime$ when the underlying system exhibits an exponential decay.
+However, if the system under test is not part of this class of systems, the exponential fitting method may provide sub-optimal results or even be ineffective.
+
+Consider instead that we are measuring a boxcar averager, i.e. a moving-average filter.
+Such a system is governed by the difference equation:
+\begin{align}
+  y(t) = \sum_{i=0}^{\Nbc-1} \Nbc^{-1} u(t-i) 
+  \text{,}
+\end{align}
+where $\Nbc = 88$.
+Since this system is a trivial \gls{FIR}, it is easy to see that $\truncTime = \Nbc$ provides the optimal truncation point.
+
+We simulate the boxcar averager for a white noise input $u(t)$ and add white noise with standard deviation $\sigma_e \approx 0.1$ to the output $y(t)$ for $2\,048$ samples from which the first $1\,024$ samples are discarded to randomize the state of the system under test.
+A single realization of the impulse response function is shown in \figref{fig:nparam:trunc:boxcar:impresp} together with the $\truncTime$ and other relevant quantities of the exponential fitting method.
+It is easy to observe that the exponential fitting provides sub-optimal results since it truncates well past the end of the finite impulse response.
+
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/expFitBoxAverager.tikz}
+         \caption[Exponential fit of boxcar averager]{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
+         \label{fig:nparam:trunc:boxcar:impresp}
+\end{figure}
+
+By repeating the experiment above $\nMC = 1\,000$ times as a Monte Carlo simulation where both the input signal and disturbing noise are varied, we gain insight into the behavior of both truncation methods.
+The histograms of the observed values of $\truncTime$ for both methods is shown in \figref{fig:nparam:trunc:boxcar:trunctime} together with the \gls{RMS} error as a function of $\truncTime$.
+It can be seen that the $F$-test based method mostly selects the optimal truncation point.
+On the other hand, the exponential fitting method is largely ineffective and doesn't truncate the response in most of the cases.
+
+\begin{figure}
+   \centering
+        \setlength\figurewidth{0.68\columnwidth}
+        \setlength\figureheight{0.68\figurewidth}
+        \input{\thisDir/figs/pdfs-rmse-boxcar.tikz}
+         \caption[RMS error of the FRF versus truncation time (boxcar)]{RMSE of a boxcar averager as a function of the truncation time $\truncTime$.
+         Empirical histograms of $\truncTime$ as determined using both the $F$-test and exponential fitting are shown.
+         For this system, the $F$-test based method is clearly superior.
+         The exponential fitting method is not effective in most cases.}
+         \label{fig:nparam:trunc:boxcar:trunctime}
+\end{figure}
+
+It can be seen that both the $F$-test method and the exponential fitting method each have their own strengths and weaknesses.
+Particularly, the $F$-test method can only select $\truncTime$ from a discrete set of values, but works well for specifically designed \gls{FIR} filters where there is a clear jump in the amplitude of the impulse response.
+On the other hand, the exponential fitting method relies on the exponential decay of the impulse response to obtain sensible values of $\truncTime$ and is hence a better match for `physical' systems.
+One should remember, however, that for the studied examples, both approaches only very seldomly select a $\truncTime$ that increases the \gls{RMS} error on the impulse response compared to not truncating the response.
+As such, a use has little to lose by trying out both methods: the model quality is very unlikely to decrease and the additional computational effort is minimal.
+
+\begin{guideline}[Check and reinforce assumptions in the data.]
+As illustrated by the presented smoothing operation, it pays off to check typical assumptions of the system (e.g.
+smoothness of the \gls{FRF}, finite support of the impulse response) and even reinforce such assumptions to improve the model quality.
+For the truncation approaches, even if the assumptions do not hold, the methods are constructed such that the unavoidable model error is unlikely to increase.
+\end{guideline}
+
+\subsection{Conclusion}
+\label{sec:nparam:trunc:conclusion}
+This section introduced a time domain method to smooth the \gls{LPM}-estimate of an \gls{FRF}. 
+It consisted of, after obtaining the \gls{FRF} from the \gls{LPM}, computing the associated estimated impulse response via the \gls{IDFT}.
+Then, it was determined statistically at which time index the impulse response had decayed below the noise floor, yielding a point beyond which the response may be set to zero.
+
+The different methods to determine $\truncTime$ presented in this section, essentially enforce different prior knowledge of the impulse response of the system.
+The exponential fitting technique relies on the exponential decay present in most physical systems.
+The $F$-test based technique is better suited for systems where a sudden jump in the impulse response is present.
+
+The results clearly indicate that the truncation technique lowers the impact of the noise on the estimate of the \gls{FRF}, resulting in a decreased variance. 
+A bias-variance trade-off is possible by tuning the time beyond which the impulse response is indistinguishable from the noise.
 

### 2016-05-09 ch03-lrm/nonparametric.tex
Press for low SNR

@@
 For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
-The values of the \gls{PRESS} are again very noisy.
-\TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}
+The values of the \gls{PRESS} are again very noisy, especially for the \gls{LPM} estimates.
+Near the resonance, the $\lrm{7,1,1,1}$ results in the smalles \gls{PRESS} value.
+This is in correspondence with the observations of the variance for similar noise levels in \figref{fig:nparam:comparison:terribleSNR}.
+Note however that the results do not carry over to the \gls{RMS} error: since the \gls{LRM} is severely biased, the \gls{PRESS} becomes unreliable to detect model errors.
 

### 2016-05-09 ch02-qlogms/excitation-design.tex
Reset acronyms etc. per chapter
Diction on CH06

@@
 \tikzsetfigurename{ch02fig}
+\glsresetall
 \myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
@@
 \item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007,Goodwin2006GBO,Rojas2012} and references therein.
-While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
+Although the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
 E.g. the approach followed by~\citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
@@
 We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
-It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
+It is, however, not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
 

### 2016-05-09 ch06-concl/conclusions.tex
Reset acronyms etc. per chapter
Diction on CH06

@@
 \tikzsetfigurename{ch06fig}
+\glsresetall
 
@@
   \subsection{Non-Parametric Estimation and Interpolation}
-  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
+  As with the regular \gls{LRM}, ongoing research focuses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
   In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
@@
 Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
-This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.
+This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since fewer parameters are needed to approximate a particular system.

### 2016-05-10 ch01-intro/introduction.tex
Some diction suggestions

@@
   \item what the exhaust of nitrogen oxides of a car will be for a certain operating point of a diesel engine, 
-  \item are the vibrations in a robot are small enough for it to perform very precise tasks such as positioning electronic components with sub-millimeter precision,
+  \item are the vibrations in a robot are small enough for it to carry out very precise tasks such as positioning electronic components with sub-millimeter precision,
 \end{itemize}
@@
 Typically, the design is very sensitive to the prior knowledge of the system.
-This is necessary to focus all the energy in the signal towards exciting the system dynamics as to reduce the uncertainty in the model.
+This is necessary to focus all the energy in the signal towards exciting the system dynamics to the end of reducing the model uncertainty.
 However, when the prior knowledge is incomplete, uncertain or even incorrect, optimal signals can lead to very poor models as they might not excite other dynamics.
@@
 \paragraph{Select a model structure}
-Once an experiment has been performed, the obtained input-output data is to be processed.
-In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and/or complexity based on both his prior knowledge and on the data.
+Once an experiment has been performed, the obtained input-output data are to be processed.
+In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and complexity based on both his prior knowledge and on the data.
 A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
@@
 This means that initial values need to be available to start the optimization process.
-Moreover, for poor starting values, optimization algorithms may get stuck in local minima of the cost function.
-Consequently, without reasonable starting values, the `optimized' model may also be of poor quality.
+Moreover, for poor starting values, optimization algorithms can get stuck in local minima of the cost function.
+Consequently, without reasonable starting values, the `optimized' model can also be of poor quality.
 
@@
 \section{User-Friendly System Identification}
-In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and/or craftsmanship of the user to make good choices.
+In the previous section, it has been seen that some of the system identification steps require a significant amount of prior knowledge and craftsmanship of the user to make good choices.
 

### 2016-05-10 ch03-lrm/nonparametric.tex
Remark: quality Hinf estimate
Some diction suggestions

@@
 Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have received renewed interest from the community over the last decade.
-One of the reasons for this is that non-parametric techniques typically require less assumptions and knowledge of the system than building parametric models.
+One of the reasons for this is that non-parametric techniques typically require fewer assumptions and knowledge of the system than building parametric models.
 As a consequence, non-parametric methods are often more robust than fully parametric methods.
@@
 In \secref{sec:biascalc}, the bias of the \gls{LRM} is derived.
-In \secref{sec:simulations} the performance of the different modeling methods are compared by means of simulations.
+In \secref{sec:nparam:simulations} the performance of the different modeling methods are compared by means of simulations.
 In \secref{sec:nparam:orderSelection}, some options for model order selection are discussed.
@@
 \begin{remark}
-This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
+This system can be solved reliably only if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
 In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution from the contribution $\LocalModel{G} \LocalModel{U}$.
@@
 \section{Simulations}
-\label{sec:simulations}
+\label{sec:nparam:simulations}
 
@@
 The next situation we consider is when $\SNR=60\unit{dB}$ as shown in \figref{fig:nparam:comparison:hiSNR}.
-Here, the \gls{LPM} remains severly biased for small datasets ($\nBW < 12$).
+Here, the \gls{LPM} remains severely biased for small datasets ($\nBW < 12$).
 However, for sufficiently long experiments ($\nBW > 32$), the bias becomes negligible.
@@
 In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
-Since the \gls{LRM} is a biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
+Since the \gls{LRM} is a biased estimator and the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
 Hence, expressions for the bias of the \gls{LRM} were derived.

### 2016-05-10 ch04-lrmhinf/lrmhinf.tex
Remark: quality Hinf estimate
Small diction find

@@
 \glsresetall{}
-
-%TODO: The quality of the estimate of the H-infinity norm of Delta is completely unknown.
-In other words, there is no theoretical guarantee about the error.
---> Tom: addresseren.
-Feitelijk hangt dit samen met de kwaliteit van standaard lpm/lrm, toch?
 
@@
 
+\begin{remark}
+Since the \gls{LRM} is used to locally estimate the \gls{FRF} based on measurements, this sets a limit on the accuracy of the ensuing estimate of the peak value.
+This was treated in \secref{sec:nparam:simulations}.
+\end{remark}
+
 \section{Simulation}
@@
 The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
-It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
+It is observed that the measurement time is reduced by almost an order of magnitude compared with techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
 Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\infnorm{\Delta}$ and/or reduce the measurement time four-fold.

### 2016-05-10 ch01-intro/introduction.tex
Comments from Anna

@@
 
-\begin{question}[Which non-parametric method should be used for an \gls{FRF}?]
+\begin{question}[Which non-parametric method should be used for a \gls{FRF}?]
 Developing a full parametric model for complicated systems requires considerable effort.

### 2016-05-10 ch05-initvals/initial-values.tex
Comments from Anna

@@
 
-In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
+In particular, two different smoothing techniques:
+\begin{itemize}
+ \item the time-truncated \gls{LPM}~\citep{Lumori2014TIM}, and
+ \item the \gls{RFIR}~\citep{Pillonetto2010,Chen2012}
+\end{itemize}
+are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
 These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
@@
 \begin{equation}
-y(t)=\true{G}(q^{-1})u_0(t)+H_0(q^{-1})e(t)
+y(t)=\true{G}(q^{-1})\true{u}(t)+\true{H}(q^{-1})e(t)
 \label{eq:initial-values:OE:TD}
 \end{equation}
-where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics,
+where $\true{G}(q^{-1})$ represents the dynamics of the system to be estimated, $\true{u}(t)$ is the input signal, $v(t)= \true{H}(q^{-1})e(t)$ is the noise source at the output, $\true{H}(q^{-1})$ is the noise dynamics,
 $e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
@@
 \begin{equation}
-    A(q^{-1}) y_0(t) = B(q^{-1}) u_0(t) \quad \forall t \in n \Ts{}  \text{ with }  n \in \IntegerNumbers
+    A(q^{-1}) \true{y}(t) = B(q^{-1}) \true{u}(t) \quad \forall t \in n \Ts{}  \text{ with }  n \in \IntegerNumbers
 \label{ABpolys}
@@
     = \frac{\sigma_v}
-           {\rms{y_0}}
+           {\rms{\true{y}}}
     \approx \frac{\sigma_{v}}
-                 {\left\| \true{G} \right\|_2 \rms{u_0}}
+                 {\left\| \true{G} \right\|_2 \rms{\true{u}}}
     =  \frac{\sigma_{v}}

### 2016-06-06 ch02-qlogms/code/subsystems.m
Add some figures for presentation

@@ -1,0 +1,20 @@
+
+w  = logspace(-1.5,1.5,200);
+FRF = @(sys) squeeze(freqresp(sys, w));
+
+G1 = tf(1,[1 1]);
+G2 = tf(1,[1 0.05 1]);
+
+%%
+figure;
+hAx(1) = subplot(1,2,1);
+plot(w, db(FRF(G1)), 'LineWidth', 2,'Color', tango('blue',3))
+set(gca,'XScale','log')
+
+
+hAx(2) = subplot(1,2,2);
+plot(w, db(FRF(G2)), 'LineWidth', 2,'Color', tango('blue',3))
+set(gca,'XScale','log')
+
+set(hAx,'YLim',[-30,30],'XLim',[min(w) max(w)],'Visible','off','Color','none')
+

### 2016-06-07 ch05-initvals/code/exampleSystem.m
Example: noisy vs nonnoisy

@@ -1,0 +1,29 @@
+close all;
+clear variables;
+clc;
+
+tfO2 = @(K,wn,z) tf(K*wn^2,[1 2*z*wn wn.^2]);
+randccn = @(varargin) (randn(varargin{:}) + 1i*randn(varargin{:}))/sqrt(2);
+
+G = tfO2(1,1,0.05) + tfO2(2,5,0.05) + tfO2(1,10,0.01) + tfO2(5, 20,0.2);
+
+
+w     = logspace(-1,2,200);
+FRF   = squeeze(freqresp(G,w));
+Noise = randccn(size(FRF))*2;
+
+
+%% plot
+figure;
+
+hAx(1) = subplot(1,2,1);
+plot(w, db(FRF), 'LineWidth', 2,'Color',tango('green',3));
+
+hAx(2) = subplot(1,2,2);
+plot(w, db(FRF+Noise), 'LineWidth', 2,'Color',tango('red',2));
+
+set(hAx, 'XScale','log','XLim',[min(w) max(w)], 'YLim',[-20 40], 'Visible','off')
+
+
+%% export
+matlab2tikz('../figs/example-noise.tikz','width','\figurewidth','height','\figureheight')

### 2016-06-16 ch01-intro/introduction.tex
Some notes Tomas McKelvey

@@
 This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
-However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
+However, since most nonparametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
 
@@
 In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
+%TODO: more groups ("two groups")
 \begin{itemize}

### 2016-06-18 ch02-qlogms/excitation-design.tex
Some diction suggestions
Some recommendations private defense
Add some TODOs from Jury/self

@@
 
+%TODO: define robustness upon first use
 \section{Introduction}
@@
 \end{align}
-which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.
+which is independent of $\wn$. 
+The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.
+%TODO: please define the meaning of "robustness"
 
@@
 To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
+%TODO: very limited model (K=1). Comment.
 
@@
 In this example, the $\damping$ is set to be the same in both sub-systems. 
+%TODO: !! (EG) Comment on that this is not a requirement
 Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
@@
   Note that it has more frequency lines per decade (or octave) at higher frequencies.
-  Therefore, the excitation power per octave is larger at higher frequencies
-  when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
+  Therefore, the excitation power per octave is larger at higher frequencies when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
   This is a rather common choice in multisine excitations when no other constraints are taken into account.
@@
 
-  Therefore a signal with an equidistant frequency grid is undesirable for
-  our situation as it wastes signal power at high frequencies at the cost of an increased variance in the lower side of the band.
+  Therefore a signal with an equidistant frequency grid is undesirable for our situation as it wastes signal power at high frequencies at the cost of an increased variance in the lower side of the band.
+  %TODO: Not clear at this stage
 
@@
 electrical circuit simulators such as \gls{SPICE}~\citep{Kundert1995}, measurement equipment such as \glspl{DSA} and programming languages, it is more common to specify the spacing of a logarithmic grid using the total number of frequencies ($F$) or the number of frequencies per decade ($F_{\decade}$) instead of the grid ratio $\alpha$.
-    Obviously, such alternative specifications are equivalent.
+    Obviously, such alternate specifications are equivalent.
   \end{remark}
@@
   \end{equation}
+  \begin{remark}
+  To introduce only limited prior knowledge into the input design, we shall assume that the noise is white.
+  Hence, $\sigma^2_E(\omega) = \sigma^2_E$ is constant over the whole frequency band of interest.
+  If the noise coloring is known beforehand (or measured in a previous experiment), the design can be adapted in a straightforward manner.
+  \end{remark}
 
@@
   Thereby it yields a smaller variance at those lines.
-  It is better tailored to systems which are closely aligned to the excited frequency grid.
+  It is better tailored to systems that are closely aligned to the excited frequency grid.
   However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance increases significantly.

### 2016-06-20 config/styles.inc.tex
Last figure?
Some improvements in figures, consistency
Thicker lines in MC figures

@@
 
+\pgfplotsset{individualSamples/.append style={mark size=0.5pt,opacity=0.7,draw=none,solid,only marks}}
+\pgfplotsset{boxplotBox/.append style={area legend,solid,draw=none,opacity=0.7}}
+\pgfplotsset{boxplotBoxInit/.append style={area legend,solid,draw=none,opacity=0.15}}
+\pgfplotsset{boxplotQuantiles/.append style={solid}}
+
 %% TikZ styles
@@
 %% MC LRM
-\pgfplotsset{mcrmse/.style={dotted}}
-\pgfplotsset{mcbias/.style={solid}}
-\pgfplotsset{mcvar/.style={dashed}}
+\pgfplotsset{mcline/.append style={line width=0.75pt}}
+\pgfplotsset{mcrmse/.append style={mcline, dotted}}
+\pgfplotsset{mcbias/.append style={mcline, solid}}
+\pgfplotsset{mcvar/.append style={mcline, dashed}}
+\pgfplotsset{mcnoise/.append style={mcline, solid}}
+\pgfplotsset{mcpress/.append style={mcline, solid}}
 

### 2016-06-21 config/styles.inc.tex
Improve some figures

@@
 
+\pgfplotsset{finalmodel/.append style={line width=0.75pt}}
+\pgfplotsset{initmodel/.append style={line width=0.75pt}}
+
 \pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
 \pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
-\pgfplotsset{existing/.style={color=existing}}
-\pgfplotsset{LPMTruncInit/.style={color=LPMTruncInit,densely dashed}}
-\pgfplotsset{LPMTrunc/.style={color=LPMTrunc}}
-\pgfplotsset{RFIRInit/.style={color=RFIRInit,densely dashed}}
-\pgfplotsset{RFIR/.style={color=RFIR}}
-\pgfplotsset{best/.style={color=best}}
+\pgfplotsset{existing/.style={finalmodel,color=existing}}
+\pgfplotsset{LPMTruncInit/.style={initmodel,color=LPMTruncInit,densely dashed}}
+\pgfplotsset{LPMTrunc/.style={finalmodel,color=LPMTrunc}}
+\pgfplotsset{RFIRInit/.style={initmodel,color=RFIRInit,densely dashed}}
+\pgfplotsset{RFIR/.style={finalmodel,color=RFIR}}
+\pgfplotsset{best/.style={finalmodel,color=best}}
 

### 2016-06-21 ch05-initvals/initial-values.tex
Some recommendations private defense
Use glossaries for some parts of ch5

@@
 
+%TODO: more references, further back than Ljung
 \section{Introduction}
@@
   \input{\thisDir/figs/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e.
+ \caption[Simulated success rate of the different initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e.
 $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
@@
   \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
+ \caption[Simulated model \glsentryshort{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
  In the bottom plot, the difference between both is shown.
@@
 In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\trueSymbol}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\trueSymbol}$ itself might be ill-suited.
-A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
-In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
+A straightforward tool to analyze the error associated with $\model{\trueSymbol}$ is to examine its relative \gls{RMS} error, with respect to the true system $\true{G}$, over different realizations of the experiment.
+In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the \gls{SNR} of the signals and the quality of the estimated parametric model.
 In this context this heuristic boils down to: 
@@
 In \figref{fig:RMSE}, the empirical $\RMSE(\model{\trueSymbol})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
-It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
-When the RMSE is then divided by $\norm[2]{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
+It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the \gls{RMSE} of the parametric estimate.
+When the \gls{RMSE} is then divided by $\norm[2]{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.
 
@@
   \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter.
-The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized.
+The \glsentryfirst{AWG} and \glsentryfirst{DAQ} hardware share the same clock and are thus synchronized.
   Blue arrows indicate coax cables. 
@@
 The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
-Although acquisition and generation were synchronized, there is a small delay $\tau_{\mathrm{MUX}} \approx 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
+Although acquisition and generation were synchronized, there is a small delay $\tau_{\mathrm{MUX}} \approx 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis~II.
 Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.

### 2016-06-24 ch03-lrm/nonparametric.tex
Some recommendations private defense
Carry out some small changes

@@
 \label{sec:nonparametric:introduction}
+%TODO: go back further in time for refs
 
@@
 \begin{equation}
-  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
+  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalModel{C} + \LocalVector{V}
   \text{,}
@@
 For linear models (i.e.
-$\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep[Sec.~12.3.2]{Seber2003}:
+$\LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta}$, such as for the \gls{LRM} and \gls{LPM}), however, the \gls{PRESS} can be calculated in a single step without estimating any additional models~\citep{Golub1979}:
 \begin{equation}
@@
 $\LocalVector{H} = \LocalMatrix{K} \pinv{\LocalMatrix{K}}$ is the so-called `hat-matrix' that is known to be idempotent.
+The proof for this can also be found in \citet[Sec.~12.3.2]{Seber2003}.
 
@@
 These global quantities can be substituted in the expressions of the local \gls{AIC} and \gls{AICc} of the previous section. 
-Note that one should also $\nWind$ as the total number of data points (and not the number of points in each window).
+Note that one should interpret $\nWind$ as the total number of data points (and not the number of points in each window) for the global case.
 
@@
 The values of the \gls{PRESS} are again very noisy, especially for the \gls{LPM} estimates.
-Near the resonance, the $\lrm{7,1,1,1}$ results in the smalles \gls{PRESS} value.
+Near the resonance, the $\lrm{7,1,1,1}$ results in the smallest \gls{PRESS} value.
 This is in correspondence with the observations of the variance for similar noise levels in \figref{fig:nparam:comparison:terribleSNR}.

### 2016-06-24 ch04-lrmhinf/lrmhinf.tex
Add some TODOs from Jury/self
Carry out some small changes

@@
 with the same notations as in \chapref{sec:excitation}, most importantly, each resonant pole can be characterized by its frequency $\wn[i]$ and damping $\damping[i]$.
-In the structural engineering community\citep[Section 2.2.2][see e.g.{Gawronski2004} it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function.
+In the structural engineering community~\citep[see e.g.][Section 2.2.2]{Gawronski2004} it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function.
 In many practical situations, this means that the gray terms in the equation often have a negligible influence.

### 2016-06-24 build.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+# Builds both response and PhD thesis
+
+arara -v response.tex && arara -v phdthesis.tex

### 2016-06-26 ch01-intro/introduction.tex
Small changes (CH01, some CH04)

@@
   \item how much noise the bodywork of a car will produce when it is driving over a bumpy road,
-  \item what the exhaust of nitrogen oxides of a car will be for a certain operating point of a diesel engine, 
-  \item are the vibrations in a robot are small enough for it to carry out very precise tasks such as positioning electronic components with sub-millimeter precision,
+  \item how many nitrogen oxides will a car exhaust for a certain operating point of its diesel engine, 
+  \item the vibrations in a robot are small enough for it to carry out very precise tasks such as positioning electronic components with sub-millimeter precision,
 \end{itemize}
@@
 Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
-In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.
+In general, many man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.
 
@@
 The downside of this is that interpreting the model physically is not always possible.
-Fortunately, the goal of a model is often not to interpret the physical reality but to approximate it well enough to allow engineering
+Fortunately, the goal of a model is often not to interpret the physical reality but to approximate it well enough to allow engineering.
 
@@
 One such tool is the frequency response function.
-For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
+For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in terms of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
 This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
-However, since most nonparametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
+However, since most nonparametric estimators enforce very little prior knowledge about the system, it can sometimes be problematic to clearly distinguish noise in the measurements and the actual systematic behavior.
 
@@
 Finally, the estimated model is validated.
-Essentially, one checks whether the obtained model meets the predefined requirements, e.g. with respect to allowable uncertainty, compexity, \ldots
+Essentially, one checks whether the obtained model meets the predefined requirements, e.g. with respect to allowable uncertainty, complexity, \ldots
 This can happen in a few different ways.
@@
 The non-parametric \gls{FRF} estimation methods in \chapref{sec:nonparametric} are based on a yet-unpublished manuscript.
-The so-called time-truncated \gls{LPM} that is presented in the same chapter is based on a journal published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
+The so-called time-truncated \gls{LPM} that is presented in the same chapter is based on a journal  article published in \gls{IEEE} Transactions on Instrumentation \& Measurement:
 \begin{itemize}
@@
 
-The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and the 2014 Leuven Conference on Noise and Vibration Engineering (ISMA) in Leuven:
+The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Congress in South Africa and the 2014 Leuven Conference on Noise and Vibration Engineering (ISMA) in Leuven:
 \begin{itemize}
@@
 \end{itemize}
-Experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
+Experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (SYSID) and at the 2015 workshop of the \gls{ERNSI}:
 \begin{itemize}

### 2016-06-26 ch04-lrmhinf/lrmhinf.tex
Small changes (CH01, some CH04)

@@
 Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
-For an infinitely long data record, this can be described in the time-domain as
+This can be described in the time-domain as
 \begin{equation}
@@
 where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance such that $v(n) = H(q)e(n)$ can be colored noise, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
-For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
+For a limited data record ($n \in \Set{0,\ldots,N-1}$ with $N$ the number of data points), the transient contributions $t_{\Delta}(n)$ lead to:
 \begin{equation}

### 2016-06-26 config/glossaries.inc.tex
Some common commands introduced
Some notes Tomas McKelvey
More entries for list of symbols
Small changes (CH01, some CH04)

@@
 \newsymbolglos{A6-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
-\newsymbolglos{A7-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
+\newsymbolglos{A7-SetRnozero}{\RealNumbersWithoutZero}{Set of the real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
 \newsymbolglos{A8-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
@@
 \newsymbolglos{B-sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}
-\newsymbolglos{B-sys-shiftoperator}{q}{Forward shift operator ($qu(t) = u(t+1)$)}
+\newsymbolglos{B-sys-shiftoperator}{q}{Forward shift operator ($q u(t) = u(t+1)$)}
 \newsymbolglos{B-sys-laplaceoperator}{s}{Laplace variable}
@@
 \newsymbolglos{count-window}{\nWind}{Bandwidth of local window}
+\newsymbolglos{count-bw}{n_{\mathrm{BW}}}{Number of excited lines in the $3\unit{dB}$ bandwidth of a resonance}
 \newsymbolglos{count-order}{\order{A},\order{B},\order{C}}{Order of local models $\LocalModel{A}, \LocalModel{B},\LocalModel{C}$}
@@
 \newacronym{EIV}{EIV}{errors-in-variables}
+\newacronym{ERNSI}{ERNSI}{European Research Network on System Identification}
 \newacronym{ETFE}{ETFE}{empirical transfer function estimate}

### 2016-06-26 ch05-initvals/initial-values.tex
Add more references (ch05)

@@
 
-Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}.
+Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998,Soderstrom1989,Goodwin1977,Brillinger1981,Sanathanan1963,McKelvey2002}.
 Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.

### 2016-06-26 ch02-qlogms/excitation-design.tex
Small corrections CH02

@@
 A complicating issue in identification of dynamic system is the fact that the information matrix often depends on the true parameter values. 
-Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not know at the time of the design.
+Consequently, an optimal input design, based on the information matrix, will depend on quantities that are not known at the time of the design.
 There are two main solutions to this in the engineering literature~\citep{Goodwin2006GBO}:
 \begin{enumerate}
-\item Iterative input design where the design updated as more information about the system is available, see e.g.~\citep{Hjalmarsson2005,Gevers2005}.
+\item Iterative input design where the design is updated as more information about the system is available, see e.g.~\citep{Hjalmarsson2005,Gevers2005}.
 The disadvantage of this approach is that multiple experiments are required to converge to the optimal design.
@@
 \begin{remark}
-D-optimal input designs are quite popular since this criterion minimizes the volume of uncertainty ellipsoid of the parameters.
+D-optimal input designs are quite popular since this criterion minimizes the volume of the uncertainty ellipsoid of the parameters.
 Moreover, the D-optimal input design is independent of the parametrization of the system (as long as the different parametrizations can be related by a bijective function)~\citep[Chapter 6]{Goodwin1977}.
@@
 
-Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements off-diagonal blocks become small.
+Furthermore, when the damping of the systems is low or the resonances of the sub-systems are well separated, the estimates decouple in the sense that the elements of the off-diagonal blocks become small.
 The effect is that the variance of the estimated transfer function approximately becomes the sum of the variances of the sub-systems.
@@
 \begin{assumption}
-The resonance frequencies $\wn[i]$ and $\wn[j]$ of all the different sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain.
+The resonance frequencies $\wn[i]$ and $\wn[j]$ of all the different sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain. %TODO: how well-separated?
 \end{assumption}
@@
 Under these assumptions, the Fisher information matrix will be approximately a diagonal block matrix, where the $i^{\text{th}}$ block corresponds to the parameters $\left[\wn[i], \wz[i], \damping[i], \dc[i,1], \ldots, \dc[i,M_{2,i}] \right]$ of a particular sub-system.
-Using the same logic as in \secref{sec:excitation:ex:sumOfSecondOrderSipmle}, this means that the variance of the complete system is approximately equal to the variance obtained for each sub-system, due to the decoupling of the Fisher information matrix.
+Using the same logic as in \secref{sec:excitation:ex:sumOfSecondOrderSipmle}, this means that the variance of the complete system is approximately equal to the sum of the variances obtained for each sub-system, due to the decoupling of the Fisher information matrix.
 
@@
 
-  When designing an excitation signal, it is common only to specify a (large) frequency band by its boundary frequencies $f_{\min}$ and $f_{\max}$.
+  When designing an excitation signal, it is common to only specify a (large) frequency band by its boundary frequencies $f_{\min}$ and $f_{\max}$.
   For a given $\alpha$ it is easy to determine the number of excited lines within the frequency range of interest:
@@
     The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
+    %TODO: make sure "\gls{FRF}" has already been used before this point
     This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
@@
                 }
-  \end{equation}
-  where $\left[ \fMin{k}, \fMax{k} \right] $ denote the frequency range over which \gls{PSD} of the pink noise is to be approximated by the power at frequency line $f_k$.
+    \label{eq:excitation:pinkMS:Ak}
+  \end{equation}
+  where $\left[ \,\fMin{k}, \fMax{k}\, \right] $ denotes the frequency range over which the \gls{PSD} of pink noise is to be approximated by the power at frequency line $f_k$.
 
@@
     \input{\thisDir/figs/freqGrid.tikz}
-    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.
-    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions. }%
+    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine covering the frequency band $\ClosedInterval{1\unit{Hz}, 1 \unit{kHz}}$.
+    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions in the lower two decades of the excited frequency band.}%
     \label{fig:excitation:freqGrids}
@@
   We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
-  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
+  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pinkMS:Ak}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
 
@@
 \end{quote}
-Also for the design of robust excitation signals, this is worthwhile observation.
+Also for the design of robust excitation signals, this is a worthwhile observation.
 \end{remark}
@@
   We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
+  %TODO: clarify previous sentence
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.
@@
 
-  We do see, however, that the variance in the vicinity of the resonance of every system is lower than in the case of a linearly spaced excitation.
+  We do see, however, that the variance in the vicinity of the resonance of most systems is lower than in the case of a linearly spaced excitation.
 
@@
 For example, a system composed of two second order systems with $\damping = 0.2$ and $\fR = 400 \unit{Hz}$ for the first system and $\fR=4 \unit{kHz}$ for the second system was simulated similarly to the previous examples.
-The standard deviation of the noise $\sigma_e$ was put at $0.0678$.
-The corresponding results are  shown in \figref{fig:excitation:sumSys}.
+The standard deviation of the noise $\sigma_e$ was put at $0.0678$. The corresponding results are  shown in \figref{fig:excitation:sumSys}.
 
@@
 
-We observe that the amplitude of the transfer function is $9.8\unit{dB}$ and $8.1\unit{dB}$ at the resonant frequencies.
+We observe that the amplitude of the transfer function is $9.8\unit{dB}$ and $8.1\unit{dB}$ at the resonance frequencies.
 The standard deviation on the \glspl{FRF} lies respectively $59.7 \unit{dB}$ and $59.6 \unit{dB}$ lower than the \gls{FRF} at these frequencies. 
@@
 
-In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.
+In this chapter we have illustrated that quasi-logarithmic multisine excitations are well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.
 The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in an even wider frequency band with a constant uncertainty.

### 2016-06-27 ch03-lrm/nonparametric.tex
Small corrections Ch03

@@
 In \secref{sec:biascalc}, the bias of the \gls{LRM} is derived.
-In \secref{sec:nparam:simulations} the performance of the different modeling methods are compared by means of simulations.
+In \secref{sec:nparam:simulations} the performance of the different modeling methods is compared by means of simulations.
 In \secref{sec:nparam:orderSelection}, some options for model order selection are discussed.
@@
 where $v[n]$ is filtered white noise, $v[n] = \true{H}(q) \true{e}[n]$ where $q^{-1}$ is the backward shift operator, i.e. $q^ {-1}x[n] = x[n-1]$.
-The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are causal and stable.
+The transfer functions $\true{G}$ and $\true{H}$ are rational functions.
 
@@
     & = \true{G} \left( \omega_k \right) U \left( \omega_k \right) 
-      + \true{H} \left( \omega_k \right) E \left( \omega_k \right)
+      + \true{H} \left( \omega_k \right) \true{E} \left( \omega_k \right)
       + T \left( \omega_k \right)\\
@@
 
+\begin{remark}
+The starting values for the \gls{LRIC} are obtained by means of the \gls{LRM}, the details of which are explained in \secref{sec:nparam:LRM}.
+\end{remark}
+
 Note that the estimated \gls{FRF} is given by evaluating the local model $\LocalModel{G}$:
@@
 However, these preliminary experiments did not yield estimates that were numerically reliable.
-This is in correspondence with the remark from \citet{Pintelon2006BJ1}.
+This is in correspondence with the remark from \citet[Section 2.4]{Pintelon2006BJ1}.
 \end{remark}
@@
 \begin{remark}
-Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
+Since it is well-known that the Vandermonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
 To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
@@
 \label{sec:nparam:LPM}
-The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
+The \gls{LPM} is a method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
 The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.
@@
 \begin{remark}
-The trivial setting for local `modeling' where a window with a total width of $1\unit{bin}$ and no transient estimation ($\order{C} = -1$), actually corresponds to the simple \gls{ETFE}~\citep{Broersen1995,Stenman2000ASETFE,Stenman2001ASFRF} when no further smoothing or windowing is applied:
+The trivial setting for local `modeling' where a window with a total width of $1\unit{bin}$ and no transient estimation ($\order{C} = -1$) are used, corresponds to the simple \gls{ETFE}~\citep{Broersen1995,Stenman2000ASETFE,Stenman2001ASFRF} when no further smoothing or windowing is applied:
 \begin{equation}
@@
 To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
-Let us denote the expected value of the cost function over all measurements $\LocalVector{Z} = \mat{\LocalMatrix{Y}, \LocalMatrix{U}}$ as
+
+Let us denote the expected value of the cost function \eqref{eq:nparam:LRM:costFunc} over all measurements $\LocalVector{Z} = \mat{\LocalMatrix{Y}, \LocalMatrix{U}}$ as
 \begin{align}
@@
                          {    
-                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
+                                \LocalVector{L}_{\LRM} (\LocalVector{\theta}, \LocalVector{Z}}) \\
               & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
@@
   + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
-  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
+  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} 
    \left( \theta - \true\theta \right)
@@
   \isdef
-  \evaluate{\PartialDerivative{\ELSCost(\theta)}{\theta}}{\theta = \true\theta}
+  \evaluate{\PartialDerivative{\ELSCost{\theta}}{\theta}}{\theta = \true\theta}
 \end{equation}
@@
 \begin{equation}
-  \PartialDerivative{\ELSCost{\estimated\theta}}
-                                          {\estimated\theta} 
+  \left(\PartialDerivative{\ELSCost{\estimated\theta}}
+                                          {\estimated\theta} \right)^{\T}
   = 
   \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} 
-  + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \left( \estimated\theta - \true\theta \right)
+  + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \left( \estimated\theta - \true\theta \right)
 \end{equation}
@@
   = 
-  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  
+  - \left( \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1}  
      \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
@@
 As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
-Consequently, only the poles can shifted by the presence of noise.
+Consequently, only the poles can be shifted by the presence of output noise.
 As such, the bias term $\Delta \theta$ can be written in the following sparse form:
@@
   \approx
+  - 
  \frac{\LocalModel{G}(\dW, \theta)}
@@
 \begin{align}
-\frac{\Delta \LocalModel{G}(\dw{\omega}{}, \theta)}{\LocalModel{G}(\dw{\omega}{}, \theta)}
+\frac{\Delta \LocalModel{G}(\dw{\omega}{}, \theta)}
+          {\LocalModel{G}(\dw{\omega}{}, \theta)}
 &\approx
+-
 \LocalModel{A}(\dw{\omega}{}, \theta)^{-1}
@@
   \end{bmatrix}
-  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}
-  \PartialDerivative{\ELSCost[n]{\true\theta}}{\theta_A}^{\TT}
+  \left(  \PartialDerivative[2]{\ELSCost{\true\theta}}{ \theta^2 } \right)^{-1}_{A}
+  \PartialDerivative{\ELSCost[n]{\true\theta}}{\true{\theta_A}}^{\TT}
   \\
   &=
+  -
   \frac{\sigma_V^2}{\nWind}
@@
   \end{bmatrix}
-  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}
+  \left(  \PartialDerivative[2]{\ELSCost{\true\theta}}{ \true\theta^2 } \right)^{-1}_{A}
   \begin{bmatrix}
      \Sum_{\dW} \dW^1 
-     \frac{\LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}})}
+     \frac{\LocalModel{A}(\conj{\dW},\conj{\true{\LocalVector{\theta}}})}
                {\LocalModel{A}(\dw{\omega}{}, \theta)}\\
@@
      \Sum_{\dW} \dW^{\order{A}} 
-     \frac{\LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}})}
+     \frac{\LocalModel{A}(\conj{\dW},\conj{\true{\LocalVector{\theta}}})}
                {\LocalModel{A}(\dw{\omega}{}, \theta)}\\
@@
 \end{align}
-where $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}_{A}$ denotes the upper left $\order{A}\times\order{A}$ subblock of $\left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}$ which pertains to the parameters of $\LocalModel{A}$.
+where $\left(  \PartialDerivative[2]{\ELSCost{\true\theta}}{ \true\theta^2 } \right)^{-1}_{A}$ denotes the upper left $\order{A}\times\order{A}$ sub-block of $\left(  \PartialDerivative[2]{\ELSCost{\true\theta}}{ \true\theta^2 } \right)^{-1}$ which pertains to the parameters of $\LocalModel{A}$.
 From the leading factor, it can be seen that the bias on the \gls{FRF} is $\bigO{\sigma_V^2}$.
@@
 The input signal used is a random-phase multisine with a full linear grid.
-A number of samples of the input- and output are measured, in such a way that the \gls{DFT} grid excited $\nBW$ bins within the $3\unit{dB}$ bandwidth of the system.
+A number of samples of the input and output are measured, in such a way that the \gls{DFT} grid excited $\nBW$ bins within the $3\unit{dB}$ bandwidth of the system.
 The different values for 
@@
 \begin{equation}
-  \Delta\SNR \isdef \sqrt{\frac{\nth}{\nWind}}
+  \Delta\SNR \isdef \frac{\nth}{\nWind}
   \label{eq:nparam:deltaSNR}
@@
 In contrast to \gls{LPM}, the \gls{LRM} already reaches a constant variance level when $\nBW > 10$.
-It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
+It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LRM} method.
 It is hence not advantageous to use the \gls{LRIC} as-is.
@@
 
-For the more noisy situation where $\SNR = 40 \unit{dB}$ (\figref{fig:nparam:comparison:midSNR}), the situation is qualitatively equal except the bias incurred by the \gls{LRM} is similar to the noise level.
+For the more noisy situation where $\SNR = 40 \unit{dB}$ (\figref{fig:nparam:comparison:midSNR}), the situation is qualitatively equal except the bias incurred by the \gls{LPM} reaches the level of the noise floor for a smaller data set ($\nBW = 12$).
+It can be seen that the bias of the \gls{LPM} behaves independently of the noise level ($40\unit{dB}$ versus $60\unit{dB}$), while the bias of the  \gls{LRM} clearly depends on the noise level.
 
@@
 For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
-When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a slightly better than \gls{LRM}.
+When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may performs slightly better than \gls{LRM}.
 The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
@@
 For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
-In the assumption that difference resonances are well-separated in the frequency, a second-order \gls{LRM} (e.g. $\lrm{7,2,2,2}$) is a reliable method to estimate the \gls{FRF}.
+In the assumption that different resonances are well-separated in the frequency, a second-order \gls{LRM} (e.g. $\lrm{7,2,2,2}$) is a reliable method to estimate the \gls{FRF}.
 \end{guideline}
@@
 In the previous section, different methods were introduced to select the local model order.
-This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
-The answer to this, depends on the ultimate purpose of the \gls{FRF}.
+This begs the question whether it is advantageous to use the same local model complexity globally over all frequencies or whether the local model order can be allowed to vary for different frequency bands.
+In fact, both approaches have their merits and which of both is to be preferred, depends on the ultimate purpose of the \gls{FRF}.
 
@@
 Outside the resonance peak, the \gls{LPM} and \gls{LRM} estimate very similar noise variances.
-The \gls{PRESS} the different methods are in agreement with the observations regarding the \gls{RMS} error from the Monte Carlo simulations in \figref{fig:nparam:comparison:midSNR}: all tested \gls{LRM} perform similarly (with a slight advantage for the first-order method), the \gls{LPM} produces much larger errors near the resonance.
+The \gls{PRESS} of the different methods are in agreement with the observations regarding the \gls{RMS} error from the Monte Carlo simulations in \figref{fig:nparam:comparison:midSNR}: all tested \gls{LRM} perform similarly (with a slight advantage for the first-order method), the \gls{LPM} produces much larger errors near the resonance.
 Nevertheless, this figure illustrates that for the \gls{LRM}, the error is quite flat over the frequency.
@@
 \end{equation}
-where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
+where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backward shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
 
@@
   The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
-  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
+  Using the $F$-test on the \gls{RMS} values of the two segments with a high significance level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
   In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
@@
 
-  The high level of confidence ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$~\citep{Parsons1974}.
+  The high level of significance ($\alpha=0.999$) ensures that the probability of a Type~II error is smaller than $1-\alpha$~\citep{Parsons1974}.
   In our case, such an error means that a part of the actual impulse response would be falsely classified as noise, which could significantly increase the bias as information of the system is discarded.
@@
   Even for a moderate $\kappa = 1.1$, a large improvement in the detection was observed.
-%  \JL{Q: doesn't this increase the probability of a Type II error?}
-%  \EG{A: This slightly increases for small $\kappa$ and increases significantly for large values of $\kappa$. But it is needed to overcome nonstationarity of the noise.}
 
@@
 for $\ln A$ and $a$ in a least squares sense.
-This is a quadratic problem in the parameters and, thus, amount to a convex optimization problem that can be solved directly.
+This is a quadratic problem in the parameters and, thus, amounts to a convex optimization problem that can be solved directly.
 Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.
@@
 The result is depicted in \figref{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}. 
-An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line).
-The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e.
+An exponential function (black thick line) is fitted on the peaks of the absolute value of a noisy impulse response. 
+The truncation time (vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e.
 $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).
@@
 
-The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit}. 
+The truncation time is determined from the data as described in \secref{sec:nonparametric:truncation:exponentialfit} and \secref{sec:nonparametric:truncation:ftest}. 
 This was done on $1000$ realizations of the noise, and depicted in \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} by the histogram.

### 2016-06-27 ch04-lrmhinf/lrmhinf.tex
Small corrections Ch04

@@
   \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\FRF}$ is observed directly on the discrete frequency grid,
-  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
+  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the \gls{IG} behavior.
 \end{enumerate}
@@
     \sup \Set{ 
-                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel[k(\omega)]{\Delta}}
+                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel[k]{\Delta}(\omega)}
                 |
@@
 by retaining the largest of both.
+%TODO: remark that this notation is deceiving: there is no $\Delta_{\LMM}$, and hence, its Hinf norm does not exist. Both notations are just to indicate
 It follows that
@@
   The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
-  Hence, $\widehat{\infnorm{\Delta_{\LRM}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
+  Hence, $\widehat{\infnorm{\Delta_{\LRM}}}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
   \label{fig:lrmhinf:exampleIntergrid}
@@
 The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload---e.g.
-passengers in a car, sensitive equipment such as atomic force microscopes and wafer-scanners used for lithography---is not disturbed by vibrations generated by either the payload itself ($\systemDisturbance$) or by the outside world ($\systemDisturbance$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.
+passengers in a car, sensitive equipment such as atomic force microscopes and wafer-scanners used for lithography---is not disturbed by vibrations generated by either the payload itself ($\systemDisturbance$) or by the outside world ($\externalDisturbance$) as indicated in \figref{fig:lrmhinf:vibration-isolation}.
 
@@
   \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
-  \caption[Vibration isolation set-ups (traditional, sky-hook dampinng)]{Conceptual illustration of (active) vibration isolation set-ups. 
+  \caption[Vibration isolation set-ups (traditional, sky-hook damping)]{Conceptual illustration of (active) vibration isolation set-ups. 
   In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
@@
 Six geophones measure the payload velocity in an inertial reference frame, hence providing absolute velocity measurements, and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform using the principle of `sky-hook damping'.
-Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up, placement of the sensor and the signal processing involved.
+Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up, placement of the sensors and the signal processing involved.
 To facilitate the presentation, only the vertical translative velocity ($v_z$), i.e. a \gls{SISO} system, is considered.
@@
 The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
+%TODO: define T(P,C) formally
 The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
@@
 
-The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
+The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields an accurate estimate of the $\Hinf{}$ norm.
 It is observed that the measurement time is reduced by almost an order of magnitude compared with techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.

### 2016-06-27 ch05-initvals/initial-values.tex
Small corrections in Ch05 + some requested ones

@@
  Numerous other parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector \citep{Ljung1999,Soderstrom1989,Pintelon2012}.
- Since the initial value generation method are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
- Hence, the presented approach is orthogonal to initialization schemes such as the work of~\citet{vanHerpen2014} that focuses on improving the optimization algorithm, rather than the starting values.
+ Since the initial value generation methods are not specifically tailored towards the \gls{MLE}, other parametric identification frameworks are likely to benefit from these improved starting values as well.
+ Hence, the presented approach is complementary to initialization schemes such as the work of~\citet{vanHerpen2014} that focuses on improving the optimization algorithm, rather than the starting values.
 
@@
 \begin{align}
-A(e^{-j\omega_k})\true{Y}(k) = B(e^{-j\omega_k})\true{U}(k) + I(e^{-j\omega_k})
+A(e^{-j\omega_k})\true{Y}(k) = B(e^{-j\omega_k})\true{U}(k) + T(e^{-j\omega_k})
 \label{DFTspectra}
 \end{align}
-with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the \gls{DFT} frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the difference between the initial and end conditions of the filters $\true{G}$ and $\true{H}$ during the measurement record.
+with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the \gls{DFT} frequencies, and $T$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the difference between the initial and end conditions of the filters $\true{G}$ and $\true{H}$ during the measurement record.
 
@@
 \begin{assumption}
-It is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.
+It is assumed that the orders of the polynomials $A$, $B$ and $T$ are known.
 \end{assumption}
@@
 
-The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
+The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $T$  polynomials is obtained by solving the optimization problem
 \begin{equation}
@@
 \begin{align}
-\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
+\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - T(k,\theta)\text{.}
 \end{align}
@@
       \If{$\lambda$ is undefined}
-        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{nn}})/100$
+        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{\numel{\theta}\numel{\theta}}})/100$
       \EndIf
-      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, n}$
+      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, \numel{\theta}}$
       \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon(\atIter[i-1]{\theta})$
@@
 A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
-Here, we repeat the main points briefly.
 The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
@@
   With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $\omega_{k+r}\in\LocalWindow$.
-  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $\numel{W}=3$, such that
+  In this chapter, we limit the notations to quadratic polynomials ($\order{B} = \order{T} = 2$) in a window with half-width $\numel{W}=3$, such that
 \begin{subequations}\label{lpmImplQuadG}
@@
 \end{subequations}
-where $r \in \LocalShifts{k}$ with $\LocalShifts{k} = \{-\numel{W},-\numel{W}+1,\dots,\numel{W}\}$ and $\numel{W}$ is a tunable parameter.
+where $r \in \LocalShifts{k}$ with $\LocalShifts{k} = \{-\numel{W},-\numel{W}+1,\dots,\numel{W}\}$.
+In general (see \chapref{sec:nonparametric}), $\numel{W}$, $\order{B}$, and $\order{T}$ are tunable parameters.
 
@@
 This problem is solved using \mcode{fmincon} in \MATLAB.
+%TODO: check convexity of this problem
 
@@
 A corresponding parametric estimate is obtained as follows. 
-A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $I$ set to zero:
+A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $T$ set to zero:
 \begin{equation}
@@
 
-The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is expressed mathematically as the probability function
+The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is defined as the probability that it reaches the \emph{best local optimum}, i.e.
 \begin{equation}
 \successRate_{\bullet} = 
-  \Prob{  \model{\bullet}=\model{\trueSymbol}  }
+  \Prob{  \model{\bullet} \approx \model{\trueSymbol}  }
 \text{.}
 \end{equation}
-In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
+In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is implemented practically as
 \begin{equation}\label{eq:successrateTol}
@@
 Their transfer functions are shown in \figref{fig:exampleFRF}.
-Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
+Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white Gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
 \begin{equation}
@@
 \end{itemize}
-One can, equivalently, express the experiment length as the number $N_{3\unit{dB}}$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
+One can, equivalently, express the experiment length as the number $\nBW$ of frequency bins that lie within the $3\unit{dB}$ bandwidth of the system.
 The $3\unit{dB}$ bandwidth is defined as the frequency band where the magnitude of the transfer function is, at most, $3\unit{dB}$ below its maximum as indicated in \figref{fig:exampleFRF}.
-For both systems, $N$ was chosen such that $N_{3\unit{dB}}$ is respectively $36$ or $48$.
-For each value-pair $(\SNR, N_{3\mathrm{dB}})$ and both systems, $n_{\mathrm{MC}} = 200$  simulations and estimations were performed.
+For both systems, $N$ was chosen such that $\nBW$ is respectively $36$ or $48$.
+For each value-pair $(\SNR, \nBW)$ and both systems, $\nMC = 200$  simulations and estimations were performed.
 Each individual simulation yields an estimate of the model based on which one can determine whether the estimation was successful or not.
-This allows to empirically estimate the success rate $\successRate$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $N_{\MC} = 200$ runs.
+This allows to empirically estimate the success rate $\successRate$ in equation \eqref{eq:successrateTol} as the proportion of the successes from the $\nMC = 200$ runs.
 
@@
 \subsubsection{Illustrative Example}
-In particular, the simulation for each pair $(\mathrm{SNR}, N_{3\mathrm{dB}})$ yields 200 estimates per initial value strategy.
+In particular, the simulation for each pair $(\mathrm{SNR}, \nBW)$ yields 200 estimates per initial value strategy.
 This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
@@
 In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
-Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\successRate$.
-The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\successRate$ is real-valued (but limited to the interval $[0,1]$).
-The inherent discreteness of $\hat{\successRate} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
-A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
+Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $\nMC$ total observations is binomially distributed with success rate $\successRate$.
+The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, \nMC}$ whereas the true success rate $\successRate$ is real-valued (but limited to the interval $[0,1]$).
+The inherent discreteness of $\hat{\successRate} \isdef n_{\mathrm{success}}/\nMC$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
+A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/\nMC$ is approximately normally distributed when $\nMC \to \infty$.
 In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
 \begin{equation}
-\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\successRate} \pm z_{1-\alpha/2} \sqrt{\hat{\successRate} (1-\hat{\successRate}/N_{\MC})}
+\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\successRate} \pm z_{1-\alpha/2} \sqrt{\hat{\successRate} (1-\hat{\successRate}/\nMC)}
 \end{equation}
@@
  \underline{\successRate} &\isdef 
-  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
+  \mathrm{CDF}_B^{-1}(\phantom{1-\;}\alpha/2; n_{\mathrm{success}}, \nMC - n_{\mathrm{success}} + 1)\\
   \overline{\successRate} &\isdef
-  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
+  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, \nMC - n_{\mathrm{success}})
 \end{align}
@@
 %\EG{
-  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $N_{3\unit{dB}}=48$ and $-1.1 \unit{dB}$ \gls{SNR}, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
+  \figref{fig:successRateVS_SNR36N3dB} shows that, typically, for the system with $Q=6\unit{dB}$ when $\nBW=48$ and $-1.1 \unit{dB}$ \gls{SNR}, the existing initial values will fail to deliver a good transfer function estimate for one in four trials ($\approx 74\%$ success rate).
 However, by using the truncated \gls{LPM}'s initial estimates, the number of failures is reduced fivefold ($\approx 95\%$ success rate) over the existing initial estimates.
@@
   \item A total of $558$ frequency bins were used for the estimation, in the excited frequency band $[0.1,20] \unit{kHz}$, with a frequency resolution of $35.7\unit{Hz}$, giving a measurement time of $28\unit{ms}$.
-The excitation signal was band-limited periodic noise with an \gls{RMS} of $100\unit{mV}$.
+The excitation signal was band-limited periodic noise whose \gls{RMS} value was $100\unit{mV}$.
   \item The input and output signals were buffered and anti-alias filtered.
 \end{itemize}
-This yielded the model $G_\VXI$ (shown in \figref{fig:bk1613}) with a relative error  of less than $0.3\%$ in the pass-band.
-Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\VXI}$ as an initial estimate.
-Furthermore, $G_\VXI$ was used to play the role of $\true{G}$ from the previous section.
+This yielded the parametric model $G_\VXI$ (shown in \figref{fig:bk1613}) with a relative error of less than $0.3\%$ in the pass-band with respect to the measured \gls{FRF}.  
+Denote $\model{VXI}$ to be the parametric estimate obtained using $G_{\VXI}$ as an initial estimate. Furthermore, $G_\VXI$ was used to play the role of $\true{G}$ from the previous section.
 
@@
   \caption[Validation cost of the different measurements.]{Validation of the measured models. 
-  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
+  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $G_{\mathrm{VXI}}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
   $\norm[2]{G_{\VXI}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
@@
 \subsection{Stress Test of the Smoothers}
-To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
+To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $\nMC = 100$ Monte Carlo simulations were performed.
 In particular, all combinations of
@@
 
-The input excitation and the disturbing output noise were $N=1\,024$ samples of white Gaussian noise such that and an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
+The input excitation and the disturbing output noise were $N=1\,024$ samples of white Gaussian noise such that an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
 Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
@@
   The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
-  \item In all cases except 8, 10 and 12, the RFIR performed as well or better than the existing methods.
+  \item In all cases except 10 and 12, the RFIR performed as well or better than the existing methods.
   \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
@@
 \end{itemize}
-This distinction is necessary for multi-tasking environments (such as computer), since during the execution of the program under test, the \gls{CPU} may spend a while to execute other programs in the background.
+This distinction is necessary for multi-tasking environments (such as modern computers): during the execution of the program under test, the \gls{CPU} may spend some time executing other programs in the background.
 The latter obviously requires a small amount of wall-clock time, but it does not increase the \gls{CPU} time of the program:
@@
 
-To measure the timing of the different methods, essentially the same settings were used as in \secref{sec:initial-values:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $N_{3\unit{dB}} \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
+To measure the timing of the different methods, essentially the same settings were used as in \secref{sec:initial-values:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $\nBW \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
 For each of the branches in \figref{fig:flowgraph}, three different timings are recorded (when applicable):
@@
 
+%TODO: TM: maybe look into power consumption aspects?
+
 \begin{guideline}[Try regularization to improve convergence]

### 2016-06-27 ch05-initvals/tables/timings.tbl.tex
Small corrections in Ch05 + some requested ones

@@
     columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
-    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
+    columns/NBW/.style={column type=c,column name={$\nBW$},zerofill=false},
     columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},

### 2016-06-28 ch06-concl/conclusions.tex
Small changes Conclusions + Summary

@@
 In this thesis, user-friendly system identification methods have been developed.
-These methods require little to no user interaction and are designed such that the method work for a broad range of systems.
+These methods require little to no user interaction and are designed such that the methods work for a broad range of systems.
 As such, many of the obtained improvements can be obtained without bothering the user for further information and tuning.
@@
 
-  In practical terms of a layman user, this means that the design of a quasi-logarithmic multisines--- as discussed in this thesis--- requires only limited prior knowledge:
+  In practical terms of a layman user, this means that the design of quasi-logarithmic multisines--- as discussed in this thesis--- requires only limited prior knowledge:
   \begin{itemize}
@@
   \paragraph{Leakage reduction}
-  Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
+  Different non-parametric estimators, specifically from the family of local estimators, \latin{i.e.} \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
   It has been shown that the most general \gls{LRIC} is very sensitive to the use of the `correct' local model order.
@@
   The first method exploits the fact that many physical systems exhibit an exponential decay.
-  This exponential decay is estimated roughly, such that the truncation point is determined as the instant where decay is below the noise level.
+  This exponential decay is estimated roughly, such that the truncation point is determined as the instant where the decay is below the noise level.
   The second method divides the impulse response into segments.
@@
   However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
-  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers; in particular when many data points are only a poor \gls{SNR} is attained.
+  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers; in particular when many noisy data points are available.
   A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM}, and the \gls{RFIR}.
-  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
-  These smoothers allow one to obtain good models from noisier data than what existing techniques.
+  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} which improves convergence to a good optimum compared to the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
+  These smoothers allow one to obtain good models from noisier data than what existing techniques can achieve.
   The improvement of the initial values has been verified both on simulations, measurements, and a simulation stress test consisting of different filters.
@@
     Similarly, for \gls{LPV} systems, the \gls{LRM} allows to extract non-parametric models from \gls{LPV} systems where the scheduling parameter is fixed during the experiment~\citep{vanderMaas2015CDC}.
-    Given the successful application of \gls{LRM} in a frozen parameter-varying system, it seems worthwhile to investigate if the\gls{LRM} can be extended to work in more challenging experimental settings.
+    Given the successful application of \gls{LRM} in a frozen parameter-varying system, it seems worthwhile to investigate if the \gls{LRM} can be extended to work in more challenging experimental settings.
     E.g. it could prove useful to extend the \gls{LRM} towards measurements of \gls{LPV} systems where the scheduling parameter is allowed to vary continuously during the experiment.
@@
   As with the regular \gls{LRM}, ongoing research focuses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
-  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
+  In that context, the design of weighting filters also becomes even more important~\citep{Boeren2013}.
   Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.

### 2016-06-28 ch02-qlogms/excitation-design.tex
Oppenheim1983->1996, some small things in response

@@
 
-  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion~\citep{Oppenheim1983}.
+  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion~\citep{Oppenheim1996}.
   Therefore the performance of the proposed method is assessed on a prototype system of second order.
@@
 
-When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in the amplitude of the transfer function~\citep{Oppenheim1983}:
+When $\damping < \frac{1}{\sqrt{2}}$, such a second order system exhibits a peak in the amplitude of the transfer function~\citep{Oppenheim1996}:
   \begin{align}
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1983} to the continuous time system \eqref{eq:excitation:secondOrderSubsystem}.
+  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrderSubsystem}.
 

### 2016-06-30 ch02-qlogms/excitation-design.tex
Ch02: figure + clarification variance reduction

@@
 where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
-$G$ is a rational, time invariant transfer function in continuous time.
+$G$ is a rational, time-invariant transfer function in continuous time.
 For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
@@
 To increase the robustness of the design, one could take a small fraction $\delta$, from the optimal power and redistribute this power over the whole frequency band of interest.
-From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the input power by $1-\delta$, gives the transfer function variance
-\begin{align}
-\var{\hat{G}(j\omega)}\frac{1}{1-\delta}.
-\end{align}
-This is a small loss while the increase in robustness can be significant if the added signal is robust. Such a robust signal is studied in the following parts of the chapter.
+From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the optimal input power by $1-\delta$, has the following effect on the variance of the estimate:
+\begin{align}
+\var{\hat{G}(j\omega)}_{{(1-\delta)\mathrm{optimal} + \delta \mathrm{robust}}} \approx \frac{1}{1-\delta} \var{\hat{G}(j\omega)}_{\mathrm{optimal}} 
+\text{.}
+\end{align}
+This is a small loss while the increase in robustness can be significant if the added signal is robust. 
+Such a robust signal is studied in the following parts of the chapter.
 

### 2016-06-30 ch06-concl/conclusions.tex
IRF truncation + stability issues

@@
 
+    \subsubsection{Impulse Response Truncation}
+    With respect to the impulse response truncation approaches introduced in \secref{sec:nonparametric:truncation}, a few paths could be investigated further to broaden the class of systems where these methods are applicable and have a more subtle smoothing behavior of the transfer function.
+
+    The crude truncation approach that is discussed in this thesis, can be interpreted as equivalent to windowing the \gls{IRF} with a rectangular window.
+    In the frequency domain, this causes a very obvious correlation in the \gls{FRF}.
+    By choosing a different window function (e.g. an exponential window, Hann window, \ldots), one could try to reduce this adverse effect.
+
+   Another alternative for this crude rectangular windowing approach, which still uses a \gls{DFT} for the full size of the measurement record, could be to reduce the size of the \gls{DFT}.
+   The introduced algorithms that determine a truncation length $\truncTime$, could also give a good indication of what size of \gls{DFT} would be suitable to represent the system well for the given measurements.
+   However, further studies are required to compare the performance of these different alternatives.
+
+   Currently, the truncation approach works based on the assumption that the last fragment of the \gls{IRF} is dominated by noise influences.
+   The consequence of this is that the system is assumed to be stable and causal.
+   It would be a worthwhile extension to relax this assumption to deal with unstable systems as well.
+   For those systems, the last fragment of the \gls{IRF} will be dominated by the unstable (or anti-causal) part of the system. 
+   Hence, the problem will become much harder to deal with, since a segment in the middle of the \gls{IRF} needs to be found where the noise level can be estimated.
+   Afterwards, one could try to split up the \gls{IRF} in a part attributed to the stable poles and one caused by unstable poles and apply truncation on both parts separately and recombining the results.
+
   \subsection{Non-Parametric Estimation and Interpolation}

### 2016-06-30 ch06-concl/conclusions.tex
Add Richard's and Warburg variables for LRM

@@
     A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
+    The \gls{LRM} (and hence also \gls{LPM}) could be extended to other model structures that are fine-tuned for specific applications as is also sometimes done for fully parametric system identification in the frequency domain~\citep[p.
+179]{Pintelon2012}.
+    E.g. in electrochemistry it is common~\citep{Wang1987} to describe diffusion phenomena using Warburg impedances which are proportional to $\sqrt{s}$ (with $s$ the Laplace variable).
+    On the other hand, in microwave engineering~\citep{Rizzi1988,Pozar2005}, commensurate filters are easily described using Richard's variable $R=\tanh (\tau s)$ with $\tau$ the delay of the considered transmission lines.
+    For these altered models, however, it should be verified whether numerical conditioning becomes a similar nuisance as for discrete-time models.
 

### 2016-06-30 ch02-qlogms/excitation-design.tex
Move guideline 2.3
Address some smaller requests

@@
 In this example, the $\damping$ is set to be the same in both sub-systems. 
-%TODO: !! (EG) Comment on that this is not a requirement
-Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
+Using different dampings in the sub-systems would, however, not change the argument, as the sub-systems with the lowest damping will be the limiting factor.
 
@@
   Hence, $\sigma^2_E(\omega) = \sigma^2_E$ is constant over the whole frequency band of interest.
-  If the noise coloring is known beforehand (or measured in a previous experiment), the design can be adapted in a straightforward manner.
+  If the noise coloring is known beforehand (or measured in a previous experiment), the design can be adapted in a straightforward manner, e.g. by coloring the amplitude spectrum accordingly.
   \end{remark}
@@
 This shows that both resonances are captured with a practically identical relative error.
-
-\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
-  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality.
-\end{guideline}
 
@@
 In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+
+\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality.
+\end{guideline}

### 2016-06-30 ch02-qlogms/excitation-design.tex
Define robustness

@@
 It is, however, not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
+In short, we consider an input signal to be \term{robust}, if such signal allows one to measure the \gls{FRF} of a wide variety of systems well, without requiring a lot of specific prior information regarding the system.
+Moreover, a robust input signal should not be very sensitive towards assumptions regarding the system under test (or should be easily adaptable if the assumptions are only approximately valid).
 

### 2016-07-04 ch03-lrm/nonparametric.tex
Add more historical references in Ch3

@@
 \gls{FRF} measurement techniques are discussed, for instance, in
-\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
+\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012,Bendat2010,Bendat1993,Jenkins1968,Box2008,Bendat1978,Blackman1959,}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010,White1969}, among others.
 

### 2016-07-05 ch03-lrm/nonparametric.tex
Small changes, mostly removal of TODOs

@@
 \label{sec:nonparametric:introduction}
-%TODO: go back further in time for refs
-
 Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have received renewed interest from the community over the last decade.

### 2016-07-05 ch02-qlogms/excitation-design.tex
Add most assumptions

@@
 
-%TODO: define robustness upon first use
 \section{Introduction}
@@
 \begin{align}
-y(t) &=G(s,\theta)u(t)  + e(t),
+y(t) &=G(s,\theta)u(t)  + H(s,\vartheta)e(t),
 \end{align}
 where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
-$G$ is a rational, time-invariant transfer function in continuous time.
+$G$ and $H$ are rational, time-invariant transfer function in continuous time.
 For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
@@
 These parameters are unknown and hence we are interested in estimating their values.
+\begin{assumption}
+The noise filter $H(s,\vartheta)$ is assumed to be independently parametrized from the plant $G(s,\theta)$, i.e. $\vartheta$ and $\theta$ are independent.
+\end{assumption}
+\begin{assumption}
+For the derivations, $H(s,\vartheta) = 1$ is used as a working assumption such that the disturbing noise on the output is zero mean Gaussian white noise.
+When this assumption is violated, one has to first measure the noise coloring and use this knowledge to predistort the input to account for the noise coloring.
+\end{assumption}
 
@@
 The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.
-%TODO: please define the meaning of "robustness"
 
@@
 Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
-To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.
+To properly identify the system $G$, excitation is required such that all sub-systems are properly excited, regardless of their individual resonance frequencies.
 %TODO: very limited model (K=1). Comment.
@@
 Each term in \eqref{eq:excitation:PFE} represents a \term{sub-system} of the system $G(s)$.
-  Within these sub-systems, we can distinguish first-order subsystems and second-order subsystems, the latter of which describe resonant phenomena.
+  Within these sub-systems, we can distinguish first-order sub-systems and second-order sub-systems, the latter of which describe resonant phenomena.
   Since such resonances are often a limiting factor, we first focus on these resonant sub-systems.
@@
 
-Consider the second-order subsystem with multiplicity $\multiplicity$:
+Consider the second-order sub-system with multiplicity $\multiplicity$:
 \begin{equation}
   G_2(s, \theta) = \frac{\dc \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
-\label{eq:excitation:secondOrderSubsystem}
+\label{eq:excitation:secondOrdersub-system}
 \end{equation}
@@
   \caption[Derivatives of a second-order sub-system towards each of its parameters.]{Bode plots of the elements of $\PartialDerivative{G_2}{\theta}$ for small $\damping$. 
-  % The numbers indicate the (asymptotic) slope as a multiple of $20 \unit{dB/\decade}$.
   The roll-off near $\wn$ is significant and depends strongly on $\damping$.
@@
 \begin{assumption} 
-The sub-systems in \eqref{eq:excitation:PFE} all are either lightly damped ($\damping \ll \sqrt{1/2}$) or are not of interest to the user.
+The sub-systems in \eqref{eq:excitation:PFE} all are either lightly damped ($\damping \ll \sqrt{1/2}$) or are not of interest.
 \end{assumption}
@@
 \begin{assumption}
-The resonance frequencies $\wn[i]$ and $\wn[j]$ of all the different sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain. %TODO: how well-separated?
+The resonance frequencies $\wn[i]$ of all the sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain such that there is little modal overlap, i.e. $\modalOverlap \ll 1$.
 \end{assumption}
+
+\begin{assumption}
+It is assumed that the excitation signal contains many more frequency lines than parameters required to describe the system under test well.
+Hence, we can neglect the bias of the estimate and focus on its variance error by assuming that a proper model order can be chosen and fitted from the data.
+\end{assumption}
+
+\begin{remark}
+The modal overlap $\modalOverlap$ is given~\citep{Ege2009} as the ratio of the average $3\unit{dB}$ bandwidth to the average difference in resonance frequencies for all resonances in the frequency band of interest.
+Often, the modal overlap is linked to the model density $\modalOverlap(\omega) = \wdB \modalDensity{\omega}$.
+In acoustic and structural engineering, expressions exist for the theoretical modal density $\modalDensity{f}$ in specific geometries such as beams, plates, square volumes~\citep{Hart1971,Bies2009}.
+Specifically, beams exhibit a modal density $\modalDensity{\omega} = \bigO{\omega^{-1/2}}$, for plates this becomes $\modalDensity{\omega} = \bigO{1}$, and for volumes $\modalDensity{\omega} = \bigO{\omega}$.
+As such, the previous assumption practically limits the use of the excitation signals to beams or the low-frequency region of plates and volumes~\citep{Ege2009}.
+\end{remark}
 
@@
 
-  To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
+  To excite the system under test we consider a generalization of multisine excitations~\citep{Pintelon2012}:
   \begin{definition}[Generalized multisine] \label{def:excitation:generalized-MS}
@@
   \subsubsection[Exploiting the grid misalignment]{Exploiting the grid misalignment between the system and the grid}
-  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrderSubsystem} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
+  Denote $G(\omega; \wn)$ a second-order sub-system as in \eqref{eq:excitation:secondOrdersub-system} with natural frequency $\wn$, damping ratio $\damping$ and static gain $\dc$, and zero at $\wz$.
   Similarly, $G(\omega; m\wn)$ where $m \in \RealNumbersWithoutZero$ is a second order sub-system that shares the same parameters, except its natural frequency which is situated at $m\wn$.
 
-  If one calculates their \glspl{FRF} by evaluating \eqref{eq:excitation:secondOrderSubsystem}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
+  If one calculates their \glspl{FRF} by evaluating \eqref{eq:excitation:secondOrdersub-system}, one sees that $G(\omega; \wn)$ and $G(m\omega; m\wn)$ yield the same numerical values for any value of the pulsation $\omega$.
   Both \glspl{FRF} share the same `shape', but are `located' at different frequencies.
@@
 
-   As such, the free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$.
-
-  % When we now take a closer look at the general second order system \eqref{eq:excitation:secondOrderSubsystem}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
-  % Note that $\dc$ is a scaling factor for the FRF.
-  % Hence the results for different values of $\dc$ only differ by a scaling factor.
-  % So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.
+   The free parameters $(\dc, \damping, \wn, \wz)$ of the sub-system are reduced to only $(\damping, \wn)$ and the others are fixed during our experiments: $\dc = 1$ and $\wz \to \infty$. 
+   \begin{remark}
+   Implicitly, this considers a design where each of the sub-systems have an equal gain $\dc=1$ and residue $\wz \to\infty$.
+   In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
+   Concretely, using a first experiment with the proposed signal, one can estimate the different parameters of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
+   \end{remark}
 
@@
 
+  \begin{remark}
+  From \figref{fig:excitation:worstCaseAlpha}, it can also be deduced that when a logarithmic multisine with $\alpha = 1 + \damping[\min]$ is used, that resonant  sub-systems with a damping $\damping[] \geq \damping[\min]$ can be well-identified using such a signal.
+  Hence, the signal is well-suited not only to observe sub-systems with a common damping, but also sub-systems that are more damped than $\damping[\min]$.   
+  \end{remark}
+
   If we determine the effect of the misalignment factor $\beta$ for a grid with frequency ratio $\alpha^{\star}$, we see that misalignment has a negligible effect on the uncertainty as shown by the dashed lines in \figref{fig:excitation:worstCaseBeta} for each of the prototype systems.
@@
   In this section, we have shown that signals with a logarithmic frequency spacing allow to identify systems with equal damping equally well, when the frequency spacing is dense enough.
-  Practically, four frequency lines in the $3\unit{dB}$ bandwidth of each second order subsystem suffice to suppress the effect of misalignment of such a subsystem and the frequency grid of the excitation signal.
+  Practically, four frequency lines in the $3\unit{dB}$ bandwidth of each second order sub-system suffice to suppress the effect of misalignment of such a sub-system and the frequency grid of the excitation signal.
 
@@
 
-  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrderSubsystem}.
+  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrdersub-system}.
 
@@
     One can see that the performance of both uncompensated quasi-log and pink quasi-log multisines is practically identical.
-    This can be explained by the fact that in this experiment, $f_0$ was chosen low enough to ensure that all the second-order subsystems had their $3\unit{dB}$ bandwidth within the bulk of logarithmic part of the excited grid.
+    This can be explained by the fact that in this experiment, $f_0$ was chosen low enough to ensure that all the second-order sub-systems had their $3\unit{dB}$ bandwidth within the bulk of logarithmic part of the excited grid.
     This observation also shows that in this practical application, the increase in uncertainty between the uncompensated and compensated quasi-log multisines is negligible, as was observed earlier in the simulations.
@@
 The presented method allows to select a maximal value for the frequency ratio $\alpha = 1 + \damping$ for which the performance will not suffer from the unavoidable misalignment of the system with respect to the excited frequencies.
-In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order subsystem.
+In practice we advise to use an excitation signal with approximately four excited lines within the $3\unit{dB}$ bandwidth of each second-order sub-system.
+
+\begin{remark}
+The proposed design can be adapted quite straightforwardly to also account for the high-frequency regions of e.g.
+plates by increasing the number of frequency lines where the modal overlap becomes more important.
+In practice, this will boil down to linearly spaced multisines.
+For measurement of the transfer characteristics of volumes (e.g. rooms), more specialized techniques are required to describe the high-frequency behavior such as the ones discussed by \citet{Ege2009}.
+\end{remark}
 
 \begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
-  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality.
+  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality when the modal overlap remains limited.
 \end{guideline}

### 2016-07-13 ch05-initvals/initial-values.tex
Small changes, mostly removal of TODOs
Small changes + improve some figures

@@
 
-%TODO: more references, further back than Ljung
 \section{Introduction}
@@
 \begin{itemize}
-    \item $\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
+    \item $\model{\true{}}$ via the true model $\true{G}$ as an initial estimate,
     \item $\model{exist}$ is obtained via \gls{GTLS} and \gls{BTLS},
@@
 The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear optimization algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e.
-$\model{\trueSymbol}$.
+$\model{\true{}}$.
 \end{conjecture}
@@
 \successRate_{\bullet} = 
-  \Prob{  \model{\bullet} \approx \model{\trueSymbol}  }
+  \Prob{  \model{\bullet} \approx \model{\true{}}  }
 \text{.}
@@
 \begin{equation}\label{eq:successrateTol}
-\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance}
+\successRate_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\true{}}} < \absoluteTolerance}
 \end{equation}
@@
 \begin{equation}
-\successRate_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < \relativeTolerance  \norm[2]{\true{G}}}
+\successRate_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\true{}}} < \relativeTolerance  \norm[2]{\true{G}}}
 \text{.}
@@
 \subsection{Comparison of Successful and Failed Estimates}
- \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black and different estimates $\model{exist}$ that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
+ \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black and different estimates $\model{exist}$ that may or may not approximate $\model{\true{}}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
  The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, which are discussed later on in this chapter.
@@
 In particular, the simulation for each pair $(\mathrm{SNR}, \nBW)$ yields 200 estimates per initial value strategy.
-This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ are shown for the different strategies, and sorted by an ascending norm.
-This effectively shows an empirical cumulative distribution function of the distance measure $\norm[2]{\model{\bullet} - \model{\trueSymbol}}$ as sampled by the Monte Carlo algorithm.%}
+This is illustrated graphically in \figref{fig:single-sim} for the value-pair $(-1.1\unit{dB},48)$ of the system with $Q = 6 \unit{dB}$, where the obtained distances $\norm[2]{\model{\bullet} - \model{\true{}}}$ are shown for the different strategies, and sorted by an ascending norm.
+This effectively shows an empirical cumulative distribution function of the distance measure $\norm[2]{\model{\bullet} - \model{\true{}}}$ as sampled by the Monte Carlo algorithm.%}
 
@@
 \begin{itemize}
-\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\model{\trueSymbol}$.
+\item The actual parametric estimates, based on the different initial estimates, have distinct behaviors with respect to their distance from $\model{\true{}}$.
 Two major classifications can be made:
 \begin{enumerate}
-  \item `good' estimates which have $\norm[2]{\model{\bullet} - \model{\trueSymbol}} < \absoluteTolerance \approx 6 \cdot 10^{-5}$,
-  \item `poor' estimates which are much further from $\model{\trueSymbol}$.  This is caused by the local optima.
+  \item `good' estimates which have $\norm[2]{\model{\bullet} - \model{\true{}}} < \absoluteTolerance \approx 6 \cdot 10^{-5}$,
+  \item `poor' estimates which are much further from $\model{\true{}}$.  This is caused by the local optima.
 \end{enumerate}
@@
   \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
- \caption[Simulated model \glsentryshort{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
+ \caption[Simulated model \glsentryshort{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\model{\true{}}$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\true{}}$ approximates the true system $\true{G}$.
  In the bottom plot, the difference between both is shown.
- Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
+ Consequently, it makes sense to examine the behavior of the models in terms of $\model{\true}$ as long as this RMSE meets the user's requirements.}
   \label{fig:RMSE}
@@
 \paragraph*{Remark about the model quality}
-In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\trueSymbol}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\trueSymbol}$ itself might be ill-suited.
-A straightforward tool to analyze the error associated with $\model{\trueSymbol}$ is to examine its relative \gls{RMS} error, with respect to the true system $\true{G}$, over different realizations of the experiment.
+In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\true{}}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\true{}}$ itself might be ill-suited.
+A straightforward tool to analyze the error associated with $\model{\true{}}$ is to examine its relative \gls{RMS} error, with respect to the true system $\true{G}$, over different realizations of the experiment.
 In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the \gls{SNR} of the signals and the quality of the estimated parametric model.
@@
 \begin{equation}
-    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm[2]{\true{G}}}{\SNR} 
+    \RMSE(\model{\true{}}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm[2]{\true{G}}}{\SNR} 
     \label{eq:heur-RMSE}
@@
 where $n_{\theta}=5$ is the number of estimated parameters in this case.
-In \figref{fig:RMSE}, the empirical $\RMSE(\model{\trueSymbol})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
+In \figref{fig:RMSE}, the empirical $\RMSE(\model{\true{}})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
 It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the \gls{RMSE} of the parametric estimate.
@@
   Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\VXI} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
-  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
+  This means that in our limited experimental study, the performance degradation of choosing \glsentryshort{RFIR} to produce initial values over the studied alternatives is small.}
   \label{fig:overview}
@@
 
-In particular for RFIR, a simulation study in~\citep{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
-For LPM (with or without time-truncation), no comparable studies are available to our knowledge, but the LPM itself has been used successfully in diverse practical applications.
+In particular for \gls{RFIR}, a simulation study in~\citep{Chen2013} suggests that RFIR handles systems with model orders up to at least $30$, even for small datasets $N\leq 500$.
+For \gls{LPM} (with or without time-truncation), no comparable studies are available to our knowledge, but the \gls{LPM} itself has been used successfully in diverse practical applications.
 
@@
 Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
-The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/s}$. 
+The low-pass and high-pass filters have a cross-over frequency of $\frac{\pi}{2} \unit{rad/s}$. 
 The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/s}$.
@@
   The fact that for cases 8 and 12, the `ideal' starting value \model{0} also provides poor models means the data is not informative enough to reasonably fit a good model.
-  \item In all cases except 10 and 12, the RFIR performed as well or better than the existing methods.
-  \item In case 10, the model quality of the RFIR is slightly worse than the already poor existing techniques.
-  This is an underlying limitation of the RFIR used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
-  Essentially, the particular RFIR used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
-  \item The RFIR performs (significantly) better than the existing methods in various cases (4--7, 9, 11).
+  \item In all cases except 10 and 12, the \gls{RFIR} performed as well or better than the existing methods.
+  \item In case 10, the model quality of the \gls{RFIR} is slightly worse than the already poor existing techniques.
+  This is an underlying limitation of the \gls{RFIR} used: $n_g=200$ taps was used, however the true impulse response has not decayed significantly in that interval.
+  Essentially, the particular \gls{RFIR} used introduces a significant bias in the non-parametric description of the filter and hence the obtained initial value is unreliable.
+  \item The \gls{RFIR} performs (significantly) better than the existing methods in various cases (4--7, 9, 11).
   \item Since the `best' method \legref{leg:dist:modelBest} yields better models more often than a single method, e.g.
@@
   Particularly, case 2 implies that \model{best} contains initial estimates of all different techniques.
-  \item For all of the tested systems (except possibly for case 2), the truncated LPM is not advisable over the existing methods.
+  \item For all of the tested systems (except possibly for case 2), the truncated \gls{LPM} is not advisable over the existing methods.
 \end{itemize}
@@
 There are no cases where using the smoothing to obtain initial values worsens the obtained model quality when the candidate model with the lowest cost function value is used (as in \eqref{eq:selectBest}).
-On the contrary, significant improvements were often achieved by including the initial values from the smoothed FRF and by combining different strategies.
+On the contrary, significant improvements were often achieved by including the initial values from the smoothed \gls{FRF} and by combining different strategies.
 

### 2016-07-13 config/styles.inc.tex
Small changes + improve some figures

@@
 
-\pgfplotsset{individualSamples/.append style={mark size=0.5pt,opacity=0.7,draw=none,solid,only marks}}
+\pgfplotsset{individualSamples/.append style={mark size=0.75pt,opacity=0.7,draw=none,solid,only marks}}
 \pgfplotsset{boxplotBox/.append style={area legend,solid,draw=none,opacity=0.7}}
 \pgfplotsset{boxplotBoxInit/.append style={area legend,solid,draw=none,opacity=0.15}}
-\pgfplotsset{boxplotQuantiles/.append style={solid}}
+\pgfplotsset{boxplotQuantiles/.append style={solid,line width=0.75pt}}
 
@@
 \pgfplotsset{bandwidth/.style={area style,fill=TangoButter1,draw=TangoButter2,fill opacity=0.5}}
-\pgfplotsset{goodestimate/.style={color=TangoChameleon2,line join=round}}
-\pgfplotsset{badestimate/.style={color=TangoScarletRed2,solid,line join=round}}
+\pgfplotsset{goodestimate/.style={color=TangoChameleon2,line join=round,line width=0.75pt}}
+\pgfplotsset{badestimate/.style={color=TangoScarletRed2,solid,line join=round,line width=0.75pt}}
 \pgfplotsset{exact/.style={color=black,dashed,line width=0.75pt,line join=round}}

### 2016-07-14 ch02-qlogms/excitation-design.tex
Assumptions + some references

@@
 \begin{assumption}
-The resonance frequencies $\wn[i]$ of all the sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain such that there is little modal overlap, i.e. $\modalOverlap \ll 1$.
+The resonance frequencies $\wn[i]$ of all the sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain:
+\begin{equation}
+  \forall i,j \in \NaturalNumbers, i \neq j : \abs{\wn[i] - \wn[j]} >  \frac{\BW_i + \BW_j}{2},
+\end{equation}
+where $\BW_{i} \approx 2 \damping[i]\wn[i]$ denotes the $3\unit{dB}$ bandwidth of the $i^{\text{th}}$ resonant sub-system. 
 \end{assumption}
 
-\begin{assumption}
-It is assumed that the excitation signal contains many more frequency lines than parameters required to describe the system under test well.
-Hence, we can neglect the bias of the estimate and focus on its variance error by assuming that a proper model order can be chosen and fitted from the data.
-\end{assumption}
-
 \begin{remark}
+The aforementioned assumption practically implies that there is no overlap between different resonances and hence there is little so-called `modal overlap'.
 The modal overlap $\modalOverlap$ is given~\citep{Ege2009} as the ratio of the average $3\unit{dB}$ bandwidth to the average difference in resonance frequencies for all resonances in the frequency band of interest.
@@
 \end{remark}
+
+\begin{assumption}
+It is assumed that the excitation signal contains many more frequency lines than parameters required to describe the system under test well.
+Hence, we can neglect the bias of the estimate and focus on its variance error by assuming that a proper model order can be chosen and fitted from the data.
+\end{assumption}
 
@@
     The~\citet{HP3562A} has a logarithmic measurement mode that ensures that each decade is covered by $F_{\decade} = 80$ lines~ to measure an \gls{FRF}.
-    %TODO: make sure "\gls{FRF}" has already been used before this point
     This is equivalent to a grid spacing $\alpha = \sqrt[80]{10} \approx 1.029$.
@@
    In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
-   Concretely, using a first experiment with the proposed signal, one can estimate the different parameters of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
+   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
    \end{remark}

### 2016-07-14 ch05-initvals/initial-values.tex
Assumptions + some references

@@
 
-Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998,Soderstrom1989,Goodwin1977,Brillinger1981,Sanathanan1963,McKelvey2002}.
+Parametric identification of \gls{LTI} systems from either input/output data or non-parametric frequency response data, has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998,Soderstrom1989,Goodwin1977,Brillinger1981,Sanathanan1963,McKelvey2002,Peeters2004}.
 Many of such parametric identification algorithms, however, require solving non-linear or non-convex optimization problems.

### 2016-07-15 ch02-qlogms/excitation-design.tex
Use B5 format
Some minor formatting things

@@
 \label{sec:excitation}
+\chapterBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}
 \def\thisDir{ch02-qlogms}
 \tikzsetfigurename{ch02fig}
-\glsresetall
+\glsresetall{}
 \myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
-\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}
 
@@
   \end{equation}
-
   This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrdersub-system}.
@@
       \centering
-      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter with center frequency $\wc$.}
+      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter around $\wc$.}
       \label{tbl:excitation:bk1613:poles}

### 2016-07-15 front-and-back-matter/summary.inc.tex
Add thumb index
Small changes Conclusions + Summary
Some minor formatting things

@@
 \chapter{Summary}
+\vspace{-2em}
 To understand, simulate and control physical systems, good mathematical models are required. 
@@
 \begin{enumerate}
-\item perform experiments to observe the system in a meaningful way,
-\item suppress unwanted effects and extract the features of interest from the measurements,
-\item fit a model to the measurements.
+\vspace{-0.5em}\item perform experiments to observe the system in a meaningful way,
+\vspace{-0.5em}\item suppress unwanted effects and extract the features of interest from the measurements,
+\vspace{-0.5em}\item fit a model to the measurements.
 \end{enumerate}
@@
 The final part of the thesis considers the use of FRF smoothers to obtain better initial values to fit parametric models to the measurement data. 
-In particular for low signal-to-noise ratios, local modeling or regularization provide a considerable improvements. 
+In particular for low signal-to-noise ratios, local modeling or regularization provide considerable improvements. 
 This allows users to obtain better models, even from poor measurements.

### 2016-07-15 ch02-qlogms/excitation-design.tex
Some Formatting

@@
 
-\section{Simulations} \label{sec:excitation:simulation}
+\section{Simulations} 
+\label{sec:excitation:simulation}
 In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
@@
 
-\begin{guideline}[Use a sufficient grid resolution for each resonance: $2 \pi \Delta f \leq (\damping - \damping^2) \wn$]
+\begin{guideline}[Use a sufficient grid resolution for each resonance]
 \label{guide:excitation:systemInBulk:tuned}

### 2016-07-15 ch04-lrmhinf/lrmhinf.tex
Some minor formatting things
Some formatting + OE figures

@@
 \label{sec:hinf}
+\chapterBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
 \def\thisDir{ch04-lrmhinf}
@@
 \myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
-\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
 \glsresetall{}
@@
 
+\section{Introduction}
+\label{sec:lrmhinf:intro}
 For mechatronic design and many other engineering disciplines it is important to obtain good  models that approximate the physical reality.
@@
   \begin{subfigure}[b]{0.49\columnwidth}
+   \centering
     \input{\thisDir/figs/vibrationisolation-classical.tikz}
@@
   \end{subfigure}
+  \hfill
   \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
     \input{\thisDir/figs/vibrationisolation-skyhook.tikz}

### 2016-07-15 ch01-intro/introduction.tex
Two groups of users -> range of users

@@
 The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
-In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
-%TODO: more groups ("two groups")
-\begin{itemize}
-  \item novices, without formal training in system identification, optimization, \ldots and,
-  \item well-seasoned identification practitioners that are already able to build good models.
-\end{itemize}
+In this context, `user-friendly' should be understood as being easy to use for users ranging from novices to well-seasoned identification specialists.
+
 Concretely, for novice users it is important to have straightforward techniques that require little interaction.

### 2016-07-15 ch02-qlogms/excitation-design.tex
Some clarifications on notation

@@
 
-  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$) as shown in \eqref{eq:excitation:varPeak} for a coarse grid.
-  %TODO: clarify previous sentence
+  We then calculate the theoretical variance on the magnitude of the peak in the \gls{FRF} ($\abs{ G\left( \wM \right) }$), as shown in \eqref{eq:excitation:varPeak}, for a coarse grid.
   A coarse grid was chosen with $\tilde{\alpha} = 10$; this means that the spacing between the excited lines around the resonance are much larger than the system bandwidth.

### 2016-07-15 ch04-lrmhinf/lrmhinf.tex
Some clarifications on notation

@@
 by retaining the largest of both.
-%TODO: remark that this notation is deceiving: there is no $\Delta_{\LMM}$, and hence, its Hinf norm does not exist. Both notations are just to indicate
 It follows that
 \begin{align}
-  \widehat{\infnorm{\Delta_{\LMM}}}
+  \widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}
     & \isdef
@@
 The construction of $ \svdMax{\Delta_{\LMM}(\omega)}$  makes it more involved to implement the interpolation approach in an efficient and/or parallel fashion.
+\end{remark}
+
+\begin{remark}
+The notions $\svdMax{\Delta_{\LMM}(\omega)}$ and the ensuing  $\widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}$  should be regarded as notational convenience to denote that local models are used to estimate the maximal singular value and $\Hinf{}$ norm, respectively.
+In reality, there is no tangible `$\Delta_{\LMM}$' that is constructed: neighboring local models are stitched together using the `$\max$' operator.
 \end{remark}

### 2016-07-16 ch04-lrmhinf/lrmhinf.tex
Change spacing around headings, epigraphs, ...

@@
 
-\begin{remark}
+\begin{remark}1
 The notions $\svdMax{\Delta_{\LMM}(\omega)}$ and the ensuing  $\widehat{\phantom{_\infty}\infnorm{\Delta_{\LMM}}}$  should be regarded as notational convenience to denote that local models are used to estimate the maximal singular value and $\Hinf{}$ norm, respectively.

### 2016-07-17 ch04-lrmhinf/lrmhinf.tex
Define T(P,C), adjust some figures

@@
 The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
-%TODO: define T(P,C) formally
 The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
@@
 the \glspl{RCF} are constructed such that
-$
+\begin{equation}
   \worstCase\Crit \left( \ModelSet[], \experimental\Controller \right)
@@
   + \gamma
-$
+\end{equation}
 where $\worstCase\Crit(\ModelSet[],C) \isdef \sup_{P\in\ModelSet[]} \Crit(P,C)$~\citep{Oomen2012SIRP}.
+$\ClosedLoop{\Plant,\Controller}$ denotes the closed loop transfer function from the loop inputs $\mat{r_2 & r_1}^{\TT}$ to the output and input of the plant $\mat{y & u}^{\TT}$ as schematically in \figref{fig:lrmhinf:tpc}.
+This can be expressed symbolically, as in \citet{Oomen2012SIRP}, by
+\begin{equation}
+\ClosedLoop{\Plant, \Controller} \isdef
+\begin{bmatrix}
+  \Plant\\
+  \I
+\end{bmatrix}
+\left(\I + \Controller \Plant \right)^{-1}
+\begin{bmatrix}
+\Controller & \I
+\end{bmatrix}
+\label{eq:lrmhinf:closedLoop}
+\text{.}
+\end{equation}
 % Obviously, $\Crit( \true\Plant, \experimental\Controller) \leq \worstCase\Crit ( \ModelSet[], \experimental\Controller )$ is guaranteed when $\true\Plant \in \ModelSet[]$.

### 2016-07-18 ch04-lrmhinf/lrmhinf.tex
Stub: robust control

@@
 \label{par:lrmhinf:toc}
+In \secref{sec:lrmhinf:robust-control-basics}, a short introduction to robust control is linked to the work in this chapter.
 The problem is formulated in \secref{sec:lrmhinf:Problem}.
@@
 Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.
+
+\section{Intermezzo: Basics of Robust Control}
+\label{sec:lrmhinf:robust-control-basics}
+When designing a feedback controller $\Controller$ (as in \figref{fig:lrmhinf:tpc:nominal}), the goal is to design $\Controller$ such that the output $y$ of a plant $\true{\Plant}$ follows the command signal $r_2$ with some additional constraints on the performance of the whole closed-loop system (e.g.
+limited overshoot, short response times, good disturbance suppression, limited controller effort, \ldots).
+This obviously requires knowledge of the actual plant $\true{\Plant}$ that is to be controlled.
+Such knowledge can be obtained by means of modeling, be it first-principles modeling or system identification or a combination of modeling approaches, which provides an approximate model $\estimated{\Plant}$.
+
+\begin{figure}[h]
+ \centering
+ \input{\thisDir/figs/tpc.tikz}
+ \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\true{\Plant},\Controller}$.}
+ \label{fig:lrmhinf:tpc:nominal}
+\end{figure}
+
+In classical control, the working assumption is that $\estimated{\Plant} = \true{\Plant}$ and hence the design of the controller is carried out on the estimated plant model.
+This has the downside that if such a controller is not designed conservatively, errors in the model may produce instability or unwanted performance degradation.
+
+\begin{figure}%[10]{R}[1em]{5cm}
+  \centering
+  \input{\thisDir/figs/modelset.tikz}
+  \caption{The plant model set.}
+  \label{fig:lrmhinf:modelset}
+\end{figure}
+
+In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
+This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
+Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
+The design process thus guarantees performance and stability for the whole set instead of for a single model.
+However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model uncertainty $\Delta(\estimated{\Plant}, \true{\Plant})$.
+A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
+\begin{equation}
+  \ModelSet[]_{\mathrm{generic}} 
+  \isdef 
+  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
+  \equiv
+  \Set{ \Plant(\estimated{\Plant}, \Delta) | \norm{\Delta} \leq \gamma}
+  \label{eq:lrmhinf:model-set:generic}
+\end{equation}
+where both the norm and the concrete function $\Delta(\estimated{\Plant}, \Plant)$ are a choice for the control engineer.
+An example of such a model set is easily imagined for additive uncertainty ($\Plant(\estimated{\Plant}, \Delta) = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
+\begin{equation}
+  \ModelSet[]_{\mathrm{additive,2}} = \Set{ \Plant | \norm[2]{\estimated{\Plant} - \Plant} \leq \gamma}
+  \text{,}
+\end{equation}
+which is a multidimensional ball with radius $\gamma$.
+Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.
+
+Building a good model set $\ModelSet[]$ as in \eqref{eq:lrmhinf:model-set:generic}, hence requires estimating a good value of the overbound $\gamma$ to define the size of the set.
+This overbound has important practical implications for the robust controller design.
+Specifically, let us denote $\true{\gamma} \isdef \norm{\true\Delta} \isdef \norm{\Delta(\estimated{\Plant}, \true{\Plant})}$.
+For an estimation procedure that yields the estimate $\estimated{\gamma}$ of the overbound, a few situations can hence occur.
+\begin{itemize}
+  \item $\estimated\gamma < \true{\gamma}$: the model set $\ModelSet[]$ is too small and hence $\true{\Plant} \not\in \ModelSet[]$.
+  Based on such an estimate, the robust controller may fail to stabilize and perform well for the actual plant $\true{\Plant}$.
+  \item $\estimated\gamma \gg \true{\gamma}$: the model set $\ModelSet[]$ is too big such that the robust controller is overly conservative.
+  Consequently, the plant is still stabilized by the controller, but the performance of the system may be degraded.
+  This  the actual plant is still stabilized by the controller, this can degrade the performance of the control system since it accounts for too many possible plants.
+    \item $\estimated\gamma = \true{\gamma}$: the model set is just large enough to contain $\true{\Plant}$ such that both stability and performance are satisfied.
+\end{itemize}
+
+In robust control, it is most common to use a (possibly weighted) $\Hinf{}$ norm in the description of the plant model set~\citep{Skogestad2005,Zhou1996} such that
+\begin{equation}
+\ModelSet[] = \Set{ \Plant(\Delta, \estimated{\Plant}) | \norm[\infty]{\Delta 
+} \leq \gamma}
+  \text{,}
+  \label{eq:lrmhinf:model-set:hinf}
+\end{equation}
+which is also the approach we follow in this chapter.
+This $\Hinf{}$ norm can be interpreted as the peak gain of the model error $\Delta$, i.e. its maximum amplitude over the frequencies.
+In control it is a common practice to use low-order models $\estimated{\Plant}$ to keep the controller design feasible, this means that $\Delta$ is often littered with unmodeled dynamics.
+When those dynamics are resonant, it can be cumbersome to detect the respective peak amplitudes reliably from a short measurement dataset.
+In this chapter, this problem will be tackled by exploiting the local models.
 

### 2016-07-18 ch04-lrmhinf/lrmhinf.tex
Add section to link robust control and peak model

@@
 The design process thus guarantees performance and stability for the whole set instead of for a single model.
-However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model uncertainty $\Delta(\estimated{\Plant}, \true{\Plant})$.
+However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model error $\Delta(\estimated{\Plant}, \true{\Plant})$.
 A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
@@
   \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
-  \equiv
-  \Set{ \Plant(\estimated{\Plant}, \Delta) | \norm{\Delta} \leq \gamma}
   \label{eq:lrmhinf:model-set:generic}
 \end{equation}
-where both the norm and the concrete function $\Delta(\estimated{\Plant}, \Plant)$ are a choice for the control engineer.
-An example of such a model set is easily imagined for additive uncertainty ($\Plant(\estimated{\Plant}, \Delta) = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
+where both the norm and the exact uncertainty description $\Delta(\estimated{\Plant}, \Plant)$, can be chosen by the control engineer.
+An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
 \begin{equation}
-  \ModelSet[]_{\mathrm{additive,2}} = \Set{ \Plant | \norm[2]{\estimated{\Plant} - \Plant} \leq \gamma}
+  \ModelSet[]_{\mathrm{additive,2}} 
+  = 
+  \Set{ \Plant | \Bignorm[2]{ \ezbrace{\Plant - \estimated{\Plant}}{\Delta(\estimated{\Plant}, \Plant)}  } \leq \gamma}
+  \equiv
+  \Set{  \ezbrace{\estimated{\Plant}  + \Delta}{\Plant(\estimated{\Plant}, \Delta)}  | \norm[2]{\Delta} \leq \gamma}
   \text{,}
 \end{equation}
-which is a multidimensional ball with radius $\gamma$.
+which is a multidimensional ball with radius $\gamma$ centered around $\estimated{\Plant}$.
 Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.

### 2016-07-22 ch04-lrmhinf/lrmhinf.tex
Fix broken sentence in robust control intermezzo

@@
   \item $\estimated\gamma \gg \true{\gamma}$: the model set $\ModelSet[]$ is too big such that the robust controller is overly conservative.
-  Consequently, the plant is still stabilized by the controller, but the performance of the system may be degraded.
-  This  the actual plant is still stabilized by the controller, this can degrade the performance of the control system since it accounts for too many possible plants.
+  Consequently, the actual plant is still stabilized by the controller, but the performance of the system may be degraded as the controller design accounts for too many possible plants.
     \item $\estimated\gamma = \true{\gamma}$: the model set is just large enough to contain $\true{\Plant}$ such that both stability and performance are satisfied.

### 2016-07-22 ch03-lrm/leakage.tex
Stub: intro leakage

\section{Transients and Leakage in the Frequency Domain}
\label{app:nparam:leakage}

\disclaimer{
This appendix is based on multiple expositions regarding transient contributions in the frequency domain.
For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3 and 6.3.2]{Pintelon2012}.
}

\TODO{derive transient contributions}

\TODO{illustrate the smoothness of leakage}

\TODO{make figures}

### 2016-07-25 ch04-lrmhinf/lrmhinf.tex
Small changes in control intermezzo

@@
 When designing a feedback controller $\Controller$ (as in \figref{fig:lrmhinf:tpc:nominal}), the goal is to design $\Controller$ such that the output $y$ of a plant $\true{\Plant}$ follows the command signal $r_2$ with some additional constraints on the performance of the whole closed-loop system (e.g.
-limited overshoot, short response times, good disturbance suppression, limited controller effort, \ldots).
+limited overshoot, short response times, good disturbance suppression, limited controller effort $u_c$, \ldots).
 This obviously requires knowledge of the actual plant $\true{\Plant}$ that is to be controlled.
@@
 where both the norm and the exact uncertainty description $\Delta(\estimated{\Plant}, \Plant)$, can be chosen by the control engineer.
-An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
+An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $2$-norm is used, in that case one obtains
 \begin{equation}

### 2016-08-02 ch03-lrm/nonparametric.tex
Some Formatting
Some formatting + OE figures
Change spacing around headings, epigraphs, ...
Small changes for formatting
 - Moving labels in figures
 - Some negative spaces in formulas
Define T(P,C), adjust some figures
Stub: intro leakage
*_0 -> \true{*}

@@
 \end{itemize}
-The main term of interest, however, is the transfer function $\true{G}$ and the noise variance $\sigma^2_{V}$.
+The main terms of interest are the transfer function $\true{G}$ and the noise variance $\sigma^2_{V}$.
 
@@
    \begin{bmatrix}
-    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } \!\!\!\!\!\!&
     \deemph{0} & 
@@
     \deemph{0} &
-    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
+    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } \!\!\!\!\!\!& 
     \deemph{0} \\
@@
     \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C } 
-  \end{bmatrix}^{-1}
-  \!\!\!=
+  \end{bmatrix}^{\!-1}
+  \!\!=
   \begin{bmatrix}
-    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A }\right)^{-1} &
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A }\right)^{\!-1} \!\!\!\!\!\!&
     \deemph{0} & 
     \deemph{0} \\
-    \deemph{0} &
-    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B }\right)^{-1} & 
+    \deemph{0} & \!\!\!\!\!\!
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B }\right)^{\!-1} \!\!\!\!\!\!& 
     \deemph{0} \\
     \deemph{0} &
-    \deemph{0} & 
-    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }\right)^{-1}
+    \deemph{0} & \!\!\!\!\!\!
+    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }\right)^{\!-1} \!
   \end{bmatrix}
@@
 \label{sec:nonparametric:truncation}
-\researchBasedOn[This section]{Lumori2014TIM}
+\sectionBasedOn{Lumori2014TIM}
 
@@
 \begin{equation}\label{eq:nparam:trunc:LPM:TD}
-y(t)=\true{G}(q)u_0(t)+\true{H}(q)e(t)=\true{G}(q)u_0(t)+v(t)
-\end{equation}
-where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backward shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
+y(t)=\true{G}(q)\true{u}(t)+\true{H}(q)e(t)=\true{G}(q)\true{u}(t)+v(t)
+\end{equation}
+where $\true{G}(q)$ represents the dynamics of the system to be estimated, $\true{u}(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backward shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).
 
@@
 
-These \gls{FRF} estimates are also compared with the true \gls{LTI} system ${G}_0(\omega_k)$.
+These \gls{FRF} estimates are also compared with the true \gls{LTI} system $\true{G}(\omega_k)$.
 Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.
@@
 % \begin{assumption}
-% The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
+% The measured output signal is $y(t) = \true{y}(t) + v(t)$ with the exact input signal $\true{u}(t)$ known. 
 % The filtered white noise $v(t) = \true{H}(q)e(t)$ is the disturbing noise source at the output.
@@
 \begin{align}
-y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
-y(t)       &= y_0(t) + e(t),
+\true{y}(t)  &= 1.5371\true{y}(t-1)    -0.9025 \true{y}(t-2) + u(t)\\
+y(t)       &= \true{y}(t) + e(t),
 \end{align}
@@
 \begin{equation}
-y_0(t) = 2.583y_0(t - 1) -2.176y_0(t - 2)+0.592y_0(t-3) + u(t)
-\end{equation}
-
-The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
+\true{y}(t) = 2.583\true{y}(t - 1) -2.176\true{y}(t - 2)+0.592\true{y}(t-3) + u(t)
+\end{equation}
+
+The measured signal was disturbed by random white noise, $y(t) = \true{y}(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
 The result is depicted in \figref{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}. 
@@
     \setlength\figurewidth{0.85\columnwidth}
-    \setlength\figureheight{0.68\figurewidth}
+    \setlength\figureheight{0.62\figurewidth}
     \input{\thisDir/figs/figLPMvsTRunc.tikz}
@@
 
+\begin{subappendices}
+  \input{\thisDir/leakage.tex}
+\end{subappendices}
+
 % \input{\thisDir/proofLOOCV.tex}

### 2016-08-02 ch05-initvals/initial-values.tex
Some minor formatting things
Some formatting + OE figures
Small changes for formatting
 - Moving labels in figures
 - Some negative spaces in formulas
*_0 -> \true{*}

@@
 \label{sec:initvals}
+\chapterBasedOn{Geerardyn2015TIM}
 \myEpigraph{Everything starts somewhere, though many physicists disagree.
@@
 \tikzsetfigurename{ch05fig}
-\glsresetall
-\researchBasedOn{Geerardyn2015TIM}
+\glsresetall{}
 
@@
 This problem is solved using \mcode{fmincon} in \MATLAB.
-%TODO: check convexity of this problem
 
@@
   \input{\thisDir/figs/MC-SNR1.1dB-NBW36-Q6dB.tikz}
- \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
+ \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \model{\true{}} \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{\true{}}$) shows that the smoothers help the estimate to converge to $\model{\true{}}$.
  The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
- $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
+ $\norm[2]{\true{G} - \model{\true{}}}$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
   \label{fig:single-sim}
@@
 
-The input excitation and the disturbing output noise were $N=1\,024$ samples of white Gaussian noise such that an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
-Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
-
 \begin{table}
@@
 \end{table}
+
+The input excitation and the disturbing output noise were $N=1\,024$ samples of white Gaussian noise such that an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
+Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.
 
@@
 
-%TODO: TM: maybe look into power consumption aspects?
-
 \begin{guideline}[Try regularization to improve convergence]

### 2016-08-02 cover/coverfigure.tex
Add Cover Figure

% arara: clean: { files: [coverfigure.auxlock, coverfigure.log] }
% arara: lualatex: { shell : yes, action : nonstopmode, options : "-8bit -file-line-error -halt-on-error" }
% arara: clean: { files: [coverfigure.aux, coverfigure.out] }

\RequirePackage{luatex85} %http://tex.stackexchange.com/questions/315025/lualatex-texlive-2016-standalone-undefined-control-sequence
\documentclass[crop=true,tikz=true,border=0.5cm]{standalone}

\usepackage{amsmath}
\input{config/definitions.tex}
\input{config/graphics.inc.tex}
\tikzexternaldisable
% \input{config/styles.inc.tex}

% \pagecolor{TangoSkyBlue3}

\colorlet{LRM}{TangoScarletRed2}
\colorlet{LRMemph}{TangoScarletRed3}
\colorlet{validation}{TangoChameleon1}

\colorlet{validation}{white}

\tikzset{line cap=round}
\tikzset{line join=round}
\tikzset{miter limit=20}

\pgfplotsset{frf/.style={color=frf,solid,mark options={solid},mark size=2pt}}
\pgfplotsset{interpol/.style={line width=3pt,solid,mark options={solid}}}

\pgfplotsset{LRMgrid/.style={color=LRM,mark size=4pt,only marks,mark=*,mark options={solid,color=LRMemph}}}

\pgfplotsset{validation/.style={color=validation,only marks,mark=square*,mark size=4pt,line width=2pt,mark options={solid,line width=2.5pt}}}

\pgfplotsset{clip mode=individual,}

\def\thisDir{ch04-lrmhinf}
% \newlength\figureheight
% \newlength\figurewidth
\setlength{\figurewidth}{36.2cm}
\setlength{\figureheight}{20cm}

\begin{document}
  \input{avis4.tikz}
  % \newpage
  % \input{avis-delta-full.tikz}
\end{document}

### 2016-08-14 ch03-lrm/leakage.tex
Stub: leakage

@@
 This appendix is based on multiple expositions regarding transient contributions in the frequency domain.
-For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3 and 6.3.2]{Pintelon2012}.
+For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3, 6.3.2 and Appendix 6.B]{Pintelon2012}.
 }
+
+This appendix derives the transient contributions in the frequency domain when a \gls{LTI} system is observed during a finite measurement window (i.e.
+$t \in {0, \ldots, N-1}$) using the same approach as in \citet[Appendix 6.B]{Pintelon2012}.
+
+Consider the ordinary difference equation
+\begin{equation}
+  \sum_{n=0}^{\order{A}} a_n y(t-n)
+  =
+  \sum_{m=0}^{\order{B}} b_m u(t-m)
+  \qquad 
+  \forall 
+  t \in \Integers
+  \label{eq:nparam:leakage:diffeq}
+\end{equation}
+where the coefficients $a_n$ and $b_m$ can be either real or complex coefficients for all values of their subscripts $n \in \set{0, \ldots, \order{A}}$ and $m \in \set{0, \ldots, \order{B}}$.
+Such a difference equation can be used to describe any discrete-time \gls{LTI} system (except those with arbitrary delays).
+
+To describe this system in the frequency domain, we first introduce the (one-sided) $\ZT$-transform of the signals $x \in \set{u,y}$:
+\begin{equation}
+  X(z) 
+  \isdef 
+  \ZTransform{x(t)} 
+  \isdef \sum_{t=0}^{\infty} x(t) z^{-t}
+\end{equation}
+which reduces to the \gls{DTFT} when $z = e^{j\omega}$ is examined~\citep[Chapter 10]{Oppenheim1996}.
+
+First, we revisit two pertinent properties of the $\ZT$-transform that are necessary to allow one to compute the $\ZT$-transform of difference equation~\eqref{eq:nparam:leakage:diffeq}.
+\begin{property}
+The $\ZT$-transform is a linear transform: $\ZTransform{ay(t) + bu(t)} = a \ZTransform{y(t)} + b \ZTransform{u(t)}= aY(z) + bU(z)$ when $a$ and $b$ are finite constants~\citep[Section 10.5.1]{Oppenheim1996}.
+\end{property}
+\begin{property}
+The $\ZT$-transform of a shifted signal can be related to the $\ZT$-transform of the unshifted signal~\citep[Section 10.5.2]{Oppenheim1996} as
+\begin{align}
+  \ZTransform{x(t-n)} 
+  &= \sum_{t=0}^{+\infty} x(t-n) z^{-t} \\
+  &= \sum_{\tau = -n}^{+\infty} x(\tau) z^{-(\tau + n)} \quad \text{ where } \tau = t - n\\
+  &= z^{-n} \sum_{\tau = 0}^{+\infty} x(\tau) z^{-\tau} +  \sum_{\tau = -n}^{-1} x(\tau) z^{-\tau-n}\\
+  \ZTransform{x(t-n)} &= z^{-n} \left( \ZTransform{x(t)} + \sum_{\tau = -n}^{-1} x(\tau) z^{-\tau} \right)
+  \text{.}
+\end{align}
+\end{property}
+
+By using both properties, we compute the $\ZT$-transform of the left hand side of \eqref{eq:nparam:leakage:diffeq}:
+\begin{align}
+  \ZTransform{\sum_{n=0}^{\order{A}} a_n y(t-n)}
+  &=
+  \sum_{n=0}^{\order{A}} a_n \ZTransform{y(t-n)}
+  +\sum_{n=0}^{\order{A}} a_n z^{-n} \\
+  &=
+  \sum_{n=0}^{\order{A}} a_n  z^{-n} Y(z)\\
+  &=
+  A(z^{-1}) Y(z)
+\end{align}
+where $A(z^{-1})$ is a polynomial in the variable $z^{-1}$.
+For the right hand side, the derivation is analogous and yields
+\begin{equation}
+  \ZTransform{\sum_{m=0}^{\order{B}} B_m y(t-m)} =
+  B(z^{-1}) U(z) + I_{B}(z)
+  \text{.}
+\end{equation}
+Combining both expressions, one obtains the $\ZT$-transform of \eqref{eq:nparam:leakage:diffeq}:
+\TODO{write out}.
 
@@
 
-\TODO{make figures}
+\TODO{make figures to illustrate the leakage}
+
+\begin{remark}
+The derivation of the leakage has been proven here for discrete-time systems.
+For lumped continuous-time \gls{LTI} and diffusive systems, the derivations are similar and elaborated in \citet[Appendix 6.B]{Pintelon2012}.
+Most importantly, the observation that the transient contribution $T$ is described in the frequency domain by a polynomial of finite degree (and hence smooth), remains valid for such systems.
+\end{remark}

### 2016-08-14 presentation/runSuspension.m
Some figures for presentation

@@ -1,0 +1,84 @@
+addpath(fullfile(fileparts(mfilename('full')),'code'));
+
+sim('suspension.slx');
+data = sldemo_suspn_output;
+
+h = data.get('h'); h = h.Values;
+z = data.get('Z'); z = z.Values;
+t = h.Time;
+h = h.Data;
+z = z.Data;
+
+%% plots
+figure;
+tocm = @(x) x*100;
+hAx(2) = subplot(2,1,2);
+plot(t, tocm(h),'Color',tango('purple',3));
+xlabel('');
+ylabel('h [cm]');
+title('')
+set(gca,'YTick',[0 1]);
+ylim(gca,[-0.1 1.1]);
+
+hAx(1) = subplot(2,1,1);
+plot(t, tocm(-z),'Color',tango('red',2));
+ylabel('x [cm]');
+title('')
+set(gca,'YTick',[12 13])
+set(get(gca,'YLabel'),'Rotation',90)
+ylim(gca,[11.9 round((max(tocm(-z))+0.1)/0.1)*0.1]);
+
+set(hAx,'box','off')
+
+set(findobj(gcf,'type','line'), 'LineWidth', 3)
+set(hAx,'Color','none')
+xlabel(hAx(2),'Time [s]');
+
+
+%% export
+matlab2tikz('suspn.tex','width','7cm','height','5cm')
+
+%% 
+% use Simulink Linearization Tool to export SS model h->z
+if ~exist('linsys2','var')
+    linsys2 = tf(NaN);
+end
+f = logspace(-1, 1, 100);
+w = 2*pi*f;
+FRF = squeeze(freqresp(linsys2, w));
+
+figure;
+plot(f, db(FRF),'LineWidth', 3,'Color', tango('blue',2));
+set(gca,'XScale','log');
+ylabel('|G| [dB]');
+xlabel('Frequency [Hz]');
+set(gca,'Color','none');
+
+matlab2tikz('bode.tex','width','7cm','height','5cm')
+
+%% plot sine
+figure;
+
+idx = find(abs(FRF) == max(abs(FRF)),1);
+f0  = f(idx);
+k = 2; % extra scaling
+
+hAx(1) = subplot(2,1,1);
+plot(t, k*2*real(-(FRF(idx))*sin(2*pi*f0*t)),'Color',tango('red',2));
+ylabel('x [cm]');
+title('')
+
+hAx(2) = subplot(2,1,2);
[…]

### 2016-08-15 ch03-lrm/nonparametric.tex
Update Copyright page, add notion of leakage in response

@@
 In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
-On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
+On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency (see \appref{app:nparam:leakage}).
 As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:

### 2016-08-15 ch03-lrm/leakage.tex
Update Copyright page, add notion of leakage in response
Derivation leakage finalized

@@
 
-To describe this system in the frequency domain, we first introduce the (one-sided) $\ZT$-transform of the signals $x \in \set{u,y}$:
+To describe this system in the frequency domain, we first introduce the (one-sided) $\ZT$-transform of the signals $x \in \set{u,y}$ and $X \in \set{U,Y}$, respectively:
 \begin{equation}
@@
   \sum_{n=0}^{\order{A}} a_n \ZTransform{y(t-n)}
-  +\sum_{n=0}^{\order{A}} a_n z^{-n} \\
+  +\sum_{n=0}^{\order{A}} a_n z^{-n}  \sum_{\tau = -n}^{-1} y(\tau) z^{-\tau}  \\
   &=
-  \sum_{n=0}^{\order{A}} a_n  z^{-n} Y(z)\\
-  &=
-  A(z^{-1}) Y(z)
+  A(z^{-1}) Y(z) + I_A(z^{-1})
 \end{align}
-where $A(z^{-1})$ is a polynomial in the variable $z^{-1}$.
+where
+\begin{align}
+  A(z^{-1}) &= \sum_{n=0}^{\order{A}} a_n z^{-n} \\
+  I_A(z^{-1}) &= \sum_{n=1}^{\order{A}} \sum_{\tau = -n}^{-1} y(\tau) a_n z^{-\tau-n}
+\end{align}
+are polynomials in $z^{-1}$ of respective degrees $\order{A}$ and  $\order{A}-1$ (at most).
+Note that $I_A(z^{-1})$ depends on $y(\tau)$ where $\tau \in \set{-1, \ldots, -\order{A}}$, i.e. samples before the beginning of the measurement record.
+
 For the right hand side, the derivation is analogous and yields
+\begin{align}
+  \ZTransform{\sum_{m=0}^{\order{B}} B_m y(t-m)} &=
+  B(z^{-1}) U(z) + I_{B}(z)\\
+  B(z^{-1}) &= \sum_{m=0}^{\order{B}} b_m z^{-m} \\
+  I_B(z^{-1}) &= \sum_{m=1}^{\order{B}} \sum_{\tau = -m}^{-1} u(\tau) b_m z^{-\tau-m}
+  \text{,}
+\end{align}
+where the degrees of the polynomials are respectively $\order{B}$ and $\order{B}-1$ (at most).
+
+Combining both expressions, one obtains the $\ZT$-transform of the complete expression \eqref{eq:nparam:leakage:diffeq}:
+\begin{align}
+  A(z^{-1}) Y(z)= B(z^{-1}) Y(z) + \ezbrace{I_B(z^{-1}) -  I_A(z^{-1})}{I_{BA}(z^-1)}
+  \label{eq:nparam:leakage:icAccounted}
+\end{align}
+where $I_{BA}(z^{-1})$ is a polynomial of degree at most $\max\set{\order{A}, \order{B}} -1$.
+Since $I_{BA}$ depends on $u(\tau)$ and $y(\tau)$ for $\tau < 0$, it accounts for the initial conditions of the experiment.
+
+Also notice that \eqref{eq:nparam:leakage:icAccounted} cannot be evaluated generally without the knowledge of $u(T)$ and $y(T)$ for $T \geq N$, which are not available in experimental conditions.
+In particular, we are interested in the evaluation on the unit circle, i.e. $z = e^{j\omega}$ where one could hope to evaluate the \gls{DTFT}.
+To overcome this problem, the samples $y(T)$ and $u(T)$ for $T \geq N$ need to be eliminated from the equation.
+This can be done, as in \citet[Appendix 6.B.1]{Pintelon2012}, by multiplying \eqref{eq:nparam:leakage:diffeq} such that one can eventually rewrite
 \begin{equation}
-  \ZTransform{\sum_{m=0}^{\order{B}} B_m y(t-m)} =
-  B(z^{-1}) U(z) + I_{B}(z)
+   A(z^-1) Y_{N,\infty}(z) = B(z^-1) U_{N,\infty}(z) + z^{-N}\ezbrace{(E_{B}(z^{-1}) - E_A(z^{-1}))}{E_{BA}(z^{-1})}
+   \label{eq:nparam:leakage:ecAccounted}
+ \end{equation}
+ where
+\begin{align}
+  X_{N,\infty}(z) 
+  &= \sum_{t=N}^{\infty} x(t)z^{-t}\\
+  E_{B}(z^{-1}) 
+  &= \sum_{m=1}^{\order{B}} \sum_{\tau = -m}^{-1} u(N+\tau) b_m z^{N-\tau-m}\\
+  E_A(z^{-1}) 
+  &= \sum_{n=1}^{\order{A}} \sum_{\tau = -n}^{-1} y(N+\tau) a_n z^{N-\tau-n}
+  \text{.}
+\end{align}
+Note that $E_{B}$ depends on the last $\order{B}-1$ samples of the measurement record: it represents the final conditions of the experiment.
+
+Subtracting \eqref{eq:nparam:leakage:ecAccounted} from \eqref{eq:nparam:leakage:icAccounted} and denoting $X_N(z) = X(z) - X_{N,\infty}(z)$ then yields
+\begin{equation}
+  A(z^-1)Y_N(z) = B(z^{-1}) U_N(z) + I_{BA}(z^{-1}) - z^{-N}E_{BA}(z^{-1})
+\end{equation}
+which no longer depends on the samples of $u(t)$ and $y(t)$ outside the acquired measurement record where $t \in \set{0,\ldots,N-1}$.
+
+The latter expression can hence be evaluated on the unit circle.
+More specifically, by substituting the \gls{DFT} frequencies $z_k = e^{j2\pi k N^{-1}}$ for $k \in\set{0,\ldots,N-1}$, one retrieves
+\begin{equation}
+  A(z_k^{-1}) Y_{\DFT}(k) = B(z_k^{-1}) U_{\DFT}(k) + T(z_k^{-1})
+\end{equation}
+with 
+\begin{equation}
+T(z^{-1}) = \frac{I_{BA}(z^{-1}) - E_{BA}(z^{-1})}{\sqrt{N}}
+\end{equation}
+the transient (or leakage) contribution that is a polynomial of order $\max\set{\order{B}, \order{A}} -1$ (at most), and the $N$-points \gls{DFT} spectrum of $x(n)$ given by
+\begin{equation}
+  X_{\DFT}(k) \isdef \frac{1}{\sqrt{N}} \sum_{n=0}^{N-1} x(n) e^{j 2 \pi k n N^{-1}} = \frac{1}{\sqrt{N}} X_N(z_k)
   \text{.}
 \end{equation}
-Combining both expressions, one obtains the $\ZT$-transform of \eqref{eq:nparam:leakage:diffeq}:
-\TODO{write out}.
 
-\TODO{derive transient contributions}
+Note that since $T(z^{-1})$ is a polynomial, $T(z_k^{-1})$ is a smooth function of the frequency, hence illustrating that the transient/leakage contribution at the \gls{DFT} frequencies is a smooth function that encapsulates the difference between the initial conditions $I_{BA}$ and end conditions $E_{BA}$ of the measurement record.
 
-\TODO{illustrate the smoothness of leakage}
-
-\TODO{make figures to illustrate the leakage}
+\begin{remark}
+Note that in the remainder of this dissertation, the \gls{DFT} spectra are typically denoted without the subscript $\DFT$, but the subscript is added here to emphasize the fact that the final expression is valid for the \gls{DFT} spectra of the input and output.
+\end{remark}
 

### 2016-08-16 ch02-qlogms/excitation-design.tex
Small changes for formatting
 - Moving labels in figures
 - Some negative spaces in formulas
Tweak for better pagination

@@
 To properly identify the system $G$, excitation is required such that all sub-systems are properly excited, regardless of their individual resonance frequencies.
-%TODO: very limited model (K=1). Comment.
 
@@
 \input{\thisDir/figs/coupling.tikz}
-\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
+\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
          The different plots are for different separations of the resonance frequencies, from $4\wdB$ to $64\wdB$.
@@
     \input{\thisDir/figs/misalign.tikz}
-    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
+    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
     The $3\unit{dB}$ bandwidth ($\wdB$) around the peak frequency $\wM$ of the system is highlighted.}
@@
     \centering
-      \setlength\figurewidth{0.75\columnwidth}
-      \setlength\figureheight{0.68\figurewidth}
+      \setlength\figurewidth{0.7\columnwidth}
+      \setlength\figureheight{0.62\figurewidth}
     \input{\thisDir/figs/betaWC.tikz}
@@
     \label{fig:excitation:worstCaseBeta}
+    \vspace{-0.5em} % to make the figures fit on a page
+  \end{figure}
+
+    \begin{figure}
+    \vspace{-0.5em} % to make the figures fit on a page
+    \centering
+      \setlength\figurewidth{0.7\columnwidth}
+      \setlength\figureheight{0.62\figurewidth}
+    \input{\thisDir/figs/alphaWC.tikz}
+    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic grid multisines and systems with different peak amplitudes.}
+    \label{fig:excitation:worstCaseAlpha}
   \end{figure}
@@
   The results are displayed in \figref{fig:excitation:worstCaseAlpha}, where the marked points correspond to the marked points in \figref{fig:excitation:worstCaseBeta}.
-
-  \begin{figure}
-    \centering
-      \setlength\figurewidth{0.75\columnwidth}
-      \setlength\figureheight{0.68\figurewidth}
-    \input{\thisDir/figs/alphaWC.tikz}
-    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
-             grid multisines and systems with different peak amplitudes.}
-    \label{fig:excitation:worstCaseAlpha}
-  \end{figure}
 
@@
   The $3\unit{dB}$ bandwidth of the system is highlighted in gray together with the excited frequency lines that lie within that bandwidth.
-
-  \begin{figure}%
-    \centering
-      \setlength\figurewidth{0.5\columnwidth}
-      \setlength\figureheight{0.68\figurewidth}
-    \input{\thisDir/figs/SignalAndSystem.tikz}
-    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$.
-The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
-    \label{fig:excitation:signalAndSystem}
-  \end{figure}
 
@@
     \input{\thisDir/figs/damping02-cmp.tikz}
-    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
+    \caption[Simulated \glsentryshortpl{FRF} of systems (damping $\xi=0.2$) for different excitations.]{%
        \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
@@
     \input{\thisDir/figs/damping005-cmp.tikz}
-    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
+    \caption[Simulated \glsentryshortpl{FRF} of systems (damping $\xi=0.05$) for different excitations.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies.
     Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
@@
 
-    \begin{figure}%
+    \begin{figure}[t]
     \centering
-      \setlength\figurewidth{0.8\columnwidth}
-      \setlength\figureheight{0.68\figurewidth}
+      \setlength\figurewidth{0.75\columnwidth}
+      \setlength\figureheight{0.62\figurewidth}
     \input{\thisDir/figs/qlog_a050mall.tikz}

### 2016-08-16 ch03-lrm/nonparametric.tex
Tweak for better pagination

@@
   \input{\thisDir/figs/MC-SNR-60.tikz}
-  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. The shaded area denotes the noise floor.}
+  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. \\
+  The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:hiSNR}
@@
   \input{\thisDir/figs/MC-SNR-40.tikz}
-  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. The shaded area denotes the noise floor.}
+  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. \\
+  The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:midSNR}
@@
   \input{\thisDir/figs/MC-SNR-20.tikz}
-  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.
+  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.\\
   The shaded area denotes the noise floor.}
@@
   \input{\thisDir/figs/MC-SNR-10.tikz}
- \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. The shaded area denotes the noise floor.}
+ \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. \\
+ The shaded area denotes the noise floor.}
   \label{fig:nparam:comparison:terribleSNR}
@@
 
+\newpage
 \section{Smoothing the \glsentryshort{FRF} by Impulse Response Truncation}

### 2016-08-16 ch05-initvals/initial-values.tex
Tweak for better pagination

@@
   \input{\thisDir/figs/successRates.tikz}
- \caption[Simulated success rate of the different initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e.
+ \caption[Simulated success rate of the initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e.
 $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems.
@@
   \input{\thisDir/figs/special-histogram.tikz}
-  \caption[Performance degradation/enhancement for selecting the second best model.]{
+  \caption[Performance penalty for selecting the second best model.]{
   Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.

### 2016-08-16 front-and-back-matter/acknowledgements.inc.tex
Add epigraphs
Lots of work on CH03
Uniform commands: part 1
Improved MC figures
First part of acks

@@
-\chapter{Acknowledgements}
-%TODO m2t team
-%TODO ELEC
-%TODO proffen, technici, secretaressen
-%TODO anna/maarten
-%TODO office mates
-%TODO EIT people
-%TODO jury
-%TODO christian larsson, istvan, MST
-%TODO mikaya
-%TODO CST
-%TODO Rick, Annemiek, Matthijs, Frank
-%TODO Johan
-%TODO Tom
-%TODO family
-%TODO family-in-law
-%TODO alexandra
-%TODO pixie
+\chapter{Acknowledgments}
+\myEpigraph{We're all going to die, all of us, what a circus! That alone should make us love each other but it doesn't. \\
+We are terrorized and flattened by trivialities, we are eaten up by nothing.}{Charles Bukowski}{The Captain is Out to Lunch and \\ the Sailors have taken over the Ship}
+% \myEpigraph{In the End, we will remember not the words of our enemies, but the silence of our friends.}{Martin Luther King Jr.}{}
+
+While the preparation of a PhD is for a large part an endeavor of a single person, it is by no means a solitary experience.
+Research without collaboration is unthinkable and is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.
+
+In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering and leisure.
+In particular, I am grateful for the great atmosphere in my office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
+%FIXME anna/maarten SA
+%FIXME: adam -> nobody expects the cauchy distribution
+
+%FIXME EIT people: Matthias, Evi, Dave, Hans
+%FIXME NnF people
+
+%FIXME proffen, technici, secretaressen
+
+%FIXME mikaya, John
+%FIXME christian larsson, istvan
+
+%FIXME Johan
+%FIXME Tom
+
+%FIXME Matthijs
+%FIXME CST
+%FIXME Rick, Annemiek, Frank, Rolf, MST
+
+%FIXME jury
+
+%FIXME m2t team
+
+%FIXME family
+%FIXME family-in-law
+%FIXME alexandra
+
+And last but not least, I would like to thank our cat Pixie for being an enjoyably crazy critter and for his enthusiasm when bringing home little presents and leaving them either on the floor or even on my pillow while I'm fast asleep.
+His intent has been duly noted and appreciated (the nightly hours and contents of those presents, however, were not always equally well-received).

### 2016-08-16 ch01-intro/introduction.tex
Change spacing around headings, epigraphs, ...
Tweak for better pagination
Comments from Johan

@@
   \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
-  \caption[System identification loop]{System identification loop. \disclaimer{Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}
+  \caption[System identification loop]{System identification loop. \disclaimer{{\footnotesize Adapted from \citep[Figure 1.10]{Ljung1999} and \citep{Mehra1981}.}}}
   \label{fig:intro:identification-cycle}
@@
 This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
-However, since most nonparametric estimators enforce very little prior knowledge about the system, it can sometimes be problematic to clearly distinguish noise in the measurements and the actual systematic behavior.
+However, since most nonparametric estimators enforce very little prior knowledge about the system, it can sometimes be problematic to clearly distinguish noise in the measurements from the actual systematic behavior.
 
@@
 
+\newpage
 \section{User-Friendly System Identification}
@@
 
+\newpage
 \subsection{Contributions}
@@
 
+\newpage
 \subsection{Outline and Publications}

### 2016-08-16 ch02-qlogms/excitation-design.tex
Comments from Johan

@@
 \begin{assumption}
-The noise filter $H(s,\vartheta)$ is assumed to be independently parametrized from the plant $G(s,\theta)$, i.e. $\vartheta$ and $\theta$ are independent.
+The noise filter $H(s,\vartheta)$ is assumed to be independently parametrized from the plant $G(s,\theta)$.
 \end{assumption}
@@
    In practice, this is often not a reasonable assumption, but the design can be adapted in a straightforward manner.
-   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa}.
+   Concretely, using a first experiment with the proposed signal, one can estimate the different gains of the sub-systems and optimize the amplitude spectrum of the signal to take those into account: for sub-systems where $\dc$ is lower than on average, the amplitude spectrum needs to be increased near the resonance frequency and \latin{vice versa} if the uncertainty of the parameters is required to be constant.
+   Of course, the appropriate actions to compensate for differing $\dc=1$ depend on the actual goal of the model.
    \end{remark}

### 2016-08-16 ch03-lrm/leakage.tex
Comments from Johan

@@
 This appendix is based on multiple expositions regarding transient contributions in the frequency domain.
-For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3, 6.3.2 and Appendix 6.B]{Pintelon2012}.
+For a more in-depth discussion, we refer to \citep{Pintelon1997ARB}, \citep{Pintelon1997Transient}, \citep{Schoukens1999}, \citep{McKelvey2002}, \citep[Section 2]{McKelvey2012LRM}, and \citep[Sections 2.6.3, 6.3.2 and Appendix 6.B]{Pintelon2012}.
 }
 
-This appendix derives the transient contributions in the frequency domain when a \gls{LTI} system is observed during a finite measurement window (i.e.
-$t \in {0, \ldots, N-1}$) using the same approach as in \citet[Appendix 6.B]{Pintelon2012}.
+This appendix derives the transient contributions in the frequency domain when a \gls{LTI} system is observed during a finite measurement window (i.e. $t \in {0, \ldots, N-1}$).
+The following derivations are repeated from \citep[Appending 6.B]{Pintelon2012}, but have been adapted in notation.
 

### 2016-08-16 ch05-initvals/initial-values.tex
Comments from Johan

@@
 
-The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is defined as the probability that it reaches the \emph{best local optimum}, i.e.
-\begin{equation}
-\successRate_{\bullet} = 
-  \Prob{  \model{\bullet} \approx \model{\true{}}  }
-\text{.}
-\end{equation}
-In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is implemented practically as
+The success rate $\successRate_{\bullet}$ of an initialization scheme $\bullet$ is defined as the probability that it reaches the \emph{best local optimum}.
+In practice, and since the iterative algorithm usually does not reach the local optimum precisely, this is implemented practically as
 \begin{equation}\label{eq:successrateTol}

### 2016-08-16 ch06-concl/conclusions.tex
Comments from Johan

@@
     E.g. in electrochemistry it is common~\citep{Wang1987} to describe diffusion phenomena using Warburg impedances which are proportional to $\sqrt{s}$ (with $s$ the Laplace variable).
+    In such diffusion problems, it can be shown~\citep[p.
+181]{Pintelon2012} that the system transients dampen as an $\bigO{t^{3/2}}$, which is considerable slower than for lumped continuous-time systems and discrete-time where the impulse decays as an $\bigO{e^{0t}}$.
+As a result, estimating diffusion transients is an even more important task than the setting discussed in this dissertation.
     On the other hand, in microwave engineering~\citep{Rizzi1988,Pozar2005}, commensurate filters are easily described using Richard's variable $R=\tanh (\tau s)$ with $\tau$ the delay of the considered transmission lines.

### 2016-08-16 front-and-back-matter/acknowledgements.inc.tex
Re-include figure
Mistaken by accident this morning...
Acks: part 2

@@
-\chapter{Acknowledgments}
+\chapter*{Acknowledgments}
 \myEpigraph{We're all going to die, all of us, what a circus! That alone should make us love each other but it doesn't. \\
@@
 
-In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering and leisure.
-In particular, I am grateful for the great atmosphere in my office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
-%FIXME anna/maarten SA
-%FIXME: adam -> nobody expects the cauchy distribution
+In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering, science, and leisure.
+In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
+I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and watching the local wildlife.
+I have also enjoyed the no-frills company of Adam, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
+On the diametrical opposite side of the spectrum, but not less agreeable, were my interactions with Matthias.
+I really appreciate his deep knowledge and his frankness, which often came into play when the both of us were having rougher times.
 
-%FIXME EIT people: Matthias, Evi, Dave, Hans
-%FIXME NnF people
+Next to research, quite a considerable amount of my time was spent on teaching assignments.
+In particular, the many hours we toiled in the `mines of Moria' to aid bachelor students to control pingpong balls went like a breeze thanks to the great company of able-minded colleagues such as Matthias, Evi, Dave, Hans, Sven and Jens.
+The great technical and administrative support of Gerd, Johan and Luc have also certainly helped in creating a productive setting for those labs.
+While exhausting, I have immensely enjoyed and benefited from those labs that force you to revise basic concepts that I have come to take for granted over the years.
+
+For the circuits and filters course, I have been really lucky to have had a great predecessor in John whom was always available to help out during the first year when I took over the course project together with Laurent in the first year of my PhD.
+I have really enjoyed this collaboration since both of us brought very complementary skills to the project.
+I am also very grateful for Alexander and Dries for being great colleagues and taking over a larger chunk of this workload when I started writing my dissertation.
 
@@
 %FIXME mikaya, John
-%FIXME christian larsson, istvan
+%FIXME istvan
 
@@
 %FIXME CST
-%FIXME Rick, Annemiek, Frank, Rolf, MST
+%FIXME Rick, Annemiek, Frank,  MST
 
-%FIXME jury
+I would also like to express my sincere gratitude for my jury member for their flexibility and great effort in aiding me to ameliorate this dissertation and my understanding of connections of my work to other fields of science and engineering.
+In retrospect, I have absolutely enjoyed discussing with them during my private defense and the few hours afterwards.
+In particular, I have been astounded by the huge amount of work that Koen put into being the best secretary that I would not even have dared dreaming of.
+Also, I appreciate Tomas for taking the time to go through the draft version of this dissertation with me in painstaking detail in the hours after my private defense.
 
-%FIXME m2t team
+This book also would not have been possible without my fellow members of the matlab2tikz team: Nico, Oleg, Peter, Michael and a handful of incidental other helpers.
+Most of the graphs in this text have, at one point or another, passed through the matlab2tikz codebase.
+I have been really enjoying our collaboration, getting-things-done attitude, and discussions regarding good coding practices in \MATLAB{} and the future directions of the matlab2tikz project.
 
-%FIXME family
+%FIXME family: oma, opa, oma spanje, mama, papa, lara, youri
 %FIXME family-in-law
@@
 
-And last but not least, I would like to thank our cat Pixie for being an enjoyably crazy critter and for his enthusiasm when bringing home little presents and leaving them either on the floor or even on my pillow while I'm fast asleep.
+And last, but not least, I would like to thank our cat Pixie for being an enjoyably crazy critter and for his sounding enthusiasm when bringing home \emph{little presents} and leaving them either on the floor or on my pillow while I'm fast asleep.
 His intent has been duly noted and appreciated (the nightly hours and contents of those presents, however, were not always equally well-received).

### 2016-08-17 front-and-back-matter/acknowledgements.inc.tex
Acknowledgments: almost finished

@@
 
-While the preparation of a PhD is for a large part an endeavor of a single person, it is by no means a solitary experience.
-Research without collaboration is unthinkable and is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.
+While a PhD only has a single author, it is by no means a solitary experience.
+Research without collaboration is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.
+Hence, I am very grateful for the scientific interactions that have improved and deepened this work.
 
@@
 In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
-I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and watching the local wildlife.
-I have also enjoyed the no-frills company of Adam, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
+I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and going on a safari to see the local wildlife and smell the wild lavender.
+I have also enjoyed the no-frills company of \textsc{Adam}, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
 On the diametrical opposite side of the spectrum, but not less agreeable, were my interactions with Matthias.
-I really appreciate his deep knowledge and his frankness, which often came into play when the both of us were having rougher times.
+I really appreciate his deep knowledge and his frankness, especially when the both of us were having rougher times.
 
@@
 
+During the few summers that I spent at ELEC, I have been fortunate enough to have collaborated with Mikaya and John, on what has become a considerable part of this dissertation.
+I really admire Mikaya's \latin{joie de vivre}, which really made his visits to Brussels a time to look forward to each year.
+Most of the work happened under supervision from John, who is an excellent researcher and, I think, what a future professor should look like: scientifically correct, but with a humane management style.
+
 %FIXME proffen, technici, secretaressen
 
-%FIXME mikaya, John
-%FIXME istvan
+During my first real international conference, I was happy to meet with István Kollár, who has unfortunately passed away recently. 
+I have really enjoyed our scientific discussions, grabbing some beers, and the view he offered into the foregone era of the Iron Curtain.
 
 %FIXME Johan
-%FIXME Tom
 
-%FIXME Matthijs
-%FIXME CST
-%FIXME Rick, Annemiek, Frank,  MST
+In the second year of my PhD, I have been a visiting researcher in the Control Systems Theory group of prof. Maarten Steinbuch.
+I remember my first encounter with Maarten as a friendly, but rather critical, meeting which took me aback for a few minutes.
+I have great admiration for Maarten's very enjoyable mix of scientific accuracy, critical business acumen and lightheartedness.
+During these months at the CST group, I much enjoyed the company of Matthijs, Frank, Annemiek and Rick.
+I was very happy to have had the chance to interact with Rick who had an excellent understanding of the set-up that I was working on and who was always available to discuss or joke around.
+Also, I took great pleasure in interacting with Matthijs: during his time at ELEC, my time at CST, and all of the times we hung out as colleagues or as friends.
+Overall, I would like to thank all the people (PhD students, professors, secretaries, ...) at CST for their open and warm atmosphere.
+
+However, my main scientific interactions in Eindhoven have been with Tom, who eventually became my promotor.
+I have always enjoyed our discussions and the broad and deep scientific knowledge he masters and yet is able to explain with clarity.
+Thanks to his very open attitude, I was able to learn a whole lot in quite a short time.
 
@@
 In retrospect, I have absolutely enjoyed discussing with them during my private defense and the few hours afterwards.
-In particular, I have been astounded by the huge amount of work that Koen put into being the best secretary that I would not even have dared dreaming of.
+In particular, I have been astounded by the huge amount of work that Koen put into being a great secretary.
 Also, I appreciate Tomas for taking the time to go through the draft version of this dissertation with me in painstaking detail in the hours after my private defense.
@@
 This book also would not have been possible without my fellow members of the matlab2tikz team: Nico, Oleg, Peter, Michael and a handful of incidental other helpers.
-Most of the graphs in this text have, at one point or another, passed through the matlab2tikz codebase.
-I have been really enjoying our collaboration, getting-things-done attitude, and discussions regarding good coding practices in \MATLAB{} and the future directions of the matlab2tikz project.
+Most of the graphs in this booklet have passed through the matlab2tikz codebase.
+I have been really enjoying our collaboration, getting-things-done attitude, and discussions regarding good practices for making figures and coding in \MATLAB{}, and the future directions of the project.
 

### 2016-08-17 front-and-back-matter/acknowledgements.inc.tex
Last part of acknowledgements

@@
 \chapter*{Acknowledgments}
+\vspace{-1em}
 \myEpigraph{We're all going to die, all of us, what a circus! That alone should make us love each other but it doesn't. \\
 We are terrorized and flattened by trivialities, we are eaten up by nothing.}{Charles Bukowski}{The Captain is Out to Lunch and \\ the Sailors have taken over the Ship}
-% \myEpigraph{In the End, we will remember not the words of our enemies, but the silence of our friends.}{Martin Luther King Jr.}{}
+\vspace{-1.5em}
+
+% \small{
+{
+\small
+\sffamily
 
@@
 Research without collaboration is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.
-Hence, I am very grateful for the scientific interactions that have improved and deepened this work.
 
 In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering, science, and leisure.
-In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
+In particular, I am grateful for the great atmosphere in the office and for my office mates over the last few years: \textsc{Adam}, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
 I have fond memories of the time Alexandra and I spend together with Anna and Maarten on our road trip in South Africa and going on a safari to see the local wildlife and smell the wild lavender.
 I have also enjoyed the no-frills company of \textsc{Adam}, his overall good taste as an engineer and dry sense of humor (`nobody expects the Cauchy distribution' was a sparkle of laughter after barren days).
-On the diametrical opposite side of the spectrum, but not less agreeable, were my interactions with Matthias.
-I really appreciate his deep knowledge and his frankness, especially when the both of us were having rougher times.
+I really appreciate Matthias's deep knowledge and his frankness, especially when the both of us were having rougher times.
+Also, the interaction I had with Cedric, often concerning good microcontroller code, have always enlightened my day.
+Apart from the actual research, I had a very good time on social activities with Péter who guided us through Vienna, David who was one of the main organizers of many social activities, and many of the other people at ELEC.
 
@@
 I really admire Mikaya's \latin{joie de vivre}, which really made his visits to Brussels a time to look forward to each year.
-Most of the work happened under supervision from John, who is an excellent researcher and, I think, what a future professor should look like: scientifically correct, but with a humane management style.
+Also, I really love the well-balanced way in which John oversaw this work; I am convinced that in academia, more people like John are needed.
 
-%FIXME proffen, technici, secretaressen
+In general, I would like to thank the professors of ELEC: Rik, Yves, Gerd, Ivan, and Leo.
+Over the last years, I have come to learn Rik as one of the most intelligent, correct and friendly people of ELEC.
+Gerd is a scientific jack-of-all trades with whom I share a strong love for beer, barbecues and finding practical solutions in the lab.
+And Yves is one of the people without whom I would not have even started working towards a PhD.
+I have dearly enjoyed our discussions on software design and philosophy, your very critical --yet constructive-- view on some of my papers, and your fascination in the color of my beverages during lunch.
+Too often, we tend to forget that people in supporting roles are invisible most of the time.
+So I would like to take this space to also thank our secretaries (Ann, Bea and Annick), our technician Johan and system administrator Sven for running a tight ship most of the time.
+I also would like to thank Leo, for his political courage and taking on responsibilities when the times call for it.
+I genuinely appreciate his efforts to provide a stable environment in the department such that research can be done.
 
@@
 
-%FIXME Johan
+During these last few years, I have been working under the close supervision of my promotor Johan.
+Although our personalities differ wildly, I truly appreciate Johan for his often refreshing views on the technical content, for his broad overview of engineering and the interesting discussion we have had over the years.
+I am really grateful, since many of the encounters I had over these last few years, were either enabled and/or strongly encouraged by him.
 
 In the second year of my PhD, I have been a visiting researcher in the Control Systems Theory group of prof. Maarten Steinbuch.
-I remember my first encounter with Maarten as a friendly, but rather critical, meeting which took me aback for a few minutes.
+I remember my first encounter with Maarten as a friendly, but rather critical, meeting which took me aback at first.
 I have great admiration for Maarten's very enjoyable mix of scientific accuracy, critical business acumen and lightheartedness.
@@
 
-However, my main scientific interactions in Eindhoven have been with Tom, who eventually became my promotor.
+However, my main scientific interactions in Eindhoven have been with Tom, who eventually became my second promotor.
 I have always enjoyed our discussions and the broad and deep scientific knowledge he masters and yet is able to explain with clarity.
@@
 
-I would also like to express my sincere gratitude for my jury member for their flexibility and great effort in aiding me to ameliorate this dissertation and my understanding of connections of my work to other fields of science and engineering.
+I would also like to express my sincere gratitude towards my jury member for their flexibility and great effort in aiding me to ameliorate this dissertation, and my understanding of connections of my work to other fields of science and engineering.
 In retrospect, I have absolutely enjoyed discussing with them during my private defense and the few hours afterwards.
@@
 
-%FIXME family: oma, opa, oma spanje, mama, papa, lara, youri
-%FIXME family-in-law
-%FIXME alexandra
+During my time as a bachelor and master student, I have always enjoyed working together with Jeroen.
+During both our PhD's at different locations, I have greatly valued how we kept in touch and tried to boost each other's spirits during the darker days of our academic activities and sometimes personal struggles.
+
+% \newpage
+At home, I would like to thank my family: my mom and dad for providing a stable yet warm environment, even though not everything has been clear sailing.
+I really appreciate how the both of you have always found a way to make the best out of it and how I could always count on you.
+Also my sister Lara and her husband Youri, for being nice people on whom you can always count.
+Although we are completely different in our professions and thinking, I place great value in getting along very well, despite those differences.
+I would also like to thank my grandparents (Jo and Ria) for on the one hand bringing me into contact with mathematics from a young age, and for their supportiveness.
+Also, I really appreciate the great lengths my other grandmother goes through to physically unite the greater Geerardyn family on numerous occasions.
+
+Next to my ``original'' family, I am very grateful to my family `in-law' (despite not being married): Linda and Dirk and their kin.
+As with my own parents, I was able to count on the both of you when times got tough (or when barbecues were involved).
+
+The last person I would like to thank is my girlfriend Alexandra.
+Without her encouragement, I am convinced I would never have finished my PhD.
+I am grateful that you pushed me to not quit and that you did everything possible to bring this chapter in our lives to a good end, even though you yourself have also been void of concerns about your PhD.
 
@@
 His intent has been duly noted and appreciated (the nightly hours and contents of those presents, however, were not always equally well-received).
+}

### 2016-09-05 front-and-back-matter/acknowledgements.inc.tex
Fix typo in acks

@@
 Without her encouragement, I am convinced I would never have finished my PhD.
-I am grateful that you pushed me to not quit and that you did everything possible to bring this chapter in our lives to a good end, even though you yourself have also been void of concerns about your PhD.
+I am grateful that you pushed me to not quit and that you did everything possible to bring this chapter in our lives to a good end, even though you yourself have not been void of concerns about your PhD.
 
